### 2015-10-01 paper.old.tex
test

%\documentclass[prl,twocolumn,amsmath,amsfonts,amssymb,showpacs,usenatbib]{revtex4} 
%\documentclass[useAMS,usenatbib]{mn2e}
%\usepackage{epsfig,psfrag,graphicx,xspace}
%\usepackage[normalem]{ulem}
%\usepackage{txfonts}
%\usepackage{natbib}
%\usepackage{amsfonts,amssymb}
%\usepackage{amsmath,amssymb}
%\usepackage{graphicx}

\documentclass[useAMS,usenatbib]{mn2e}
\usepackage{epsfig,psfrag,txfonts,xspace}
\usepackage[normalem]{ulem}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{amsfonts,amsbsy,amssymb}

% --- journals --- %
\newcommand{\aap}{A{\&}A}
\newcommand{\aaps}{A{\&}AS}
\newcommand{\aapr}{AAPR}
\newcommand{\aj}{AJ}
\newcommand{\apj}{ApJ}
\newcommand{\apjl}{ApJL}
\newcommand{\apjs}{ApJS}
\newcommand{\apss}{Ap{\&}SS}
\newcommand{\araa}{ARA{\&}A}
\newcommand{\memsai}{{Mem.~Soc.~Astron.~Italiana}}
\newcommand{\mnras}{MNRAS}
\newcommand{\ssr}{SSRv}
\newcommand{\physrep}{Phys.~Rep.}
\newcommand{\jcomp}{J.~Comput.~Phys.}
\newcommand{\jgr}{JGR}
\newcommand{\grl}{GRL}
\newcommand{\Mstream}{{\it M-streaming}\xspace}
\newcommand{\Mflatturb}{{\it M-turbulence}\xspace}
\newcommand{\Mprimary}{{\it M-primaries}\xspace}

% --- macros --- %
\newcommand{\dd}{\mathrm{d}}
%\newcommand{\rmn}{\mathrm}
\newcommand{\Vph}{V_\mathrm{ph}}
\newcommand{\mug}{\mu G}

\def\del#1{{}}
%\def\del#1{{\bf (DELETED TEXT)}}
\def\C#1{{\bf #1}}
\def\AP#1{{\bf  AP: #1}}
\def\SPO#1{{\bf SPO: #1}}
\def\CP#1{{\bf  #1}}

%\voffset.6in

\title[Origin of Seed Electrons]{Turbulence and Particle Acceleration in Giant Radio Halos: the Origin of Seed Electrons}

\author[A. Pinzke, S. Peng Oh and C. Pfrommer] 
{Anders Pinzke$^{1,2}$\thanks{apinzke@fysik.su.se (AP); peng@physics.ucsb.edu (PO); christoph.pfrommer@h-its.org (CP)}, S. Peng Oh$^{3}$ and Christoph Pfrommer$^{4}$\footnotemark[1]\\
$^{1}$The Oskar Klein Centre for Cosmoparticle Physics, Department
  of Physics, Stockholm University, AlbaNova University Center, SE - 106 91
  Stockholm, Sweden\\
$^{2}$Dark Cosmology Center, University of Copenhagen,
  Juliane Maries Vej 30, DK-2100 Copenhagen, Denmark\\
  $^{3}$University of California - Santa Barbara,
  Department of Physics, CA 93106-9530, USA\\
$^{4}$Heidelberg Institute for Theoretical Studies
  (HITS), Schloss-Wolfsbrunnenweg 35, 69118 Heidelberg, Germany}

\begin{document}
\pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{2015}
\maketitle
\label{firstpage}

%\date{\today}

%\pacs{98.65.Cw, 98.70.Sa, 95.85.Bh, 95.30.Qd, 95.30.Cq, 94.05.Lk, 94.05.Pt}

\begin{abstract}
About $1/3$ of X-ray-luminous clusters show smooth, unpolarized radio
emission on $\sim$Mpc scales, known as giant radio halos. One
promising model for radio halos is Fermi II acceleration of seed
relativistic electrons by turbulence of the intracluster medium (ICM);
Coulomb losses prohibit acceleration from the thermal pool. However,
the origin of seed electrons has never been fully explored. Here, we
integrate the Fokker-Planck equation of the cosmic ray (CR) electron
and proton distributions in a cosmological simulations of cluster
formation. For standard assumptions, structure formation shocks lead
to a seed electron population which produces too centrally
concentrated radio emission. Instead, we present three realistic
scenarios that each can reproduce the spatially flat radio emission
observed in the Coma cluster: (1) the ratio of injected turbulent
energy density to thermal energy density increase significantly with
radius, as seen in cosmological simulations. This generates a flat
radio profile even if the seed population of CRs is steep with
radius. (2) Self-confinement of energetic CR protons can be
inefficient, and CR protons may stream at the Alfv{\'e}n speed to the
cluster outskirts when the ICM is relatively quiescent. A spatially
flat CR proton distribution develops and produces the required
population of secondary seed electrons. (3) The CR proton to electron
acceleration efficiency $K_{ep} \sim 0.1$ is assumed to be larger than
in our Galaxy ($K_{ep} \sim 10^{-2}$), due to the magnetic geometry at
the shock. The resulting primary electron population dominates. Due to
their weaker density dependence compared to secondary electrons, these
primaries can also reproduce radio observations.  These competing
non-trivial solutions provide incisive probes of non thermal processes
in the high-$\beta$ ICM.
\end{abstract}

% --- keywords --- %
\begin{keywords}
  magnetic fields, cosmic rays, radiation mechanisms: non-thermal, elementary
  particles, galaxies: cluster: general, Galaxy: fundamental parameters
\end{keywords}
%\maketitle

% --- section: Introduction --- %
\section{Introduction}
About one third of X-ray-luminous clusters show smooth, unpolarized
radio emission on $\sim$Mpc scales, known as giant radio halos (RHs)
\citep{2014IJMPD..2330007B}. They appear only in disturbed, merging
clusters and the RH luminosity correlates with the X-ray luminosity
\citep{2001A&A...369..441G,2012A&ARv..20...54F} and the Compton
$y$-parameter \citep{2013A&A...554A.140P}. The RHs show that CRs and
magnetic fields permeate a large volume fraction of the intra-cluster
medium (ICM). The dominant CR source, given the smoothness and
enormous extent of RHs, is thought to be structure formation shocks
\citep{miniati01,pfrommer08}. At the same time, plasma processes, the
origin of magnetic fields and particle acceleration in a turbulent,
high-$\beta$ plasma like the ICM are not well understood. Radio halos
thus provide an incisive probe of non-thermal processes in the ICM.

One promising model for RHs is re-energetization of seed suprathermal
electrons by Fermi II acceleration when ICM turbulence becomes transonic during
mergers \citep{2001MNRAS.320..365B,brunetti07}. Due to the short radiative
cooling time of high-energy relativistic electrons, the cluster synchrotron
emission quickly fades away after a merger, which naturally explains the
observed bimodality of RHs \cite[see
 e.g.][]{2013MNRAS.429.3564D,2014MNRAS.443.3564D}.

However, there is a salient piece missing in the turbulent
reacceleration model. It relies heavily on the assumption of an
abundant, volume-filling population of seed suprathermal electrons;
direct Fermi II acceleration from the thermal pool is precluded by
strong Coulomb losses
\citep{2008ApJ...682..175P,2012ApJ...759..113C}. These seeds are
presumed to be either fossil CR electrons (CRes) accelerated by
diffusive shock acceleration (DSA) during structure formation
\citep{1999ApJ...520..529S}, or secondaries injected by hadronic
interaction of CR protons (CRps) with thermal protons
\citep{brunetti11}. While analytic estimates have been made, there has
been no ab initio demonstration that structure formation can lead to
the required abundance of seed electrons with the correct spatial and
spectral characteristics. This is a non-trivial requirement: Coulomb
cooling in dense cluster cores is severe, and DSA fossil electrons may
not survive. On the other hand, for secondaries to constitute the seed
population, the CRp population required in the best-studied case of
the Coma cluster must have a very broad and flat (or even slightly
inverted) spatial profile \citep{brunetti12}, in contrast with the
thermal plasma whose energy density declines steeply with radius. In
Fig.~\ref{fig:Edens} we show that such a distribution is not predicted by
cosmological simulations \cite[see
  also][]{pinzke10,2014MNRAS.439.2662V}.
\begin{figure}
  \begin{minipage}{1.0\columnwidth}
    \includegraphics[width=1.0\columnwidth]{figures/fCR.radius.coma.g72a.Rad14.2400p.z0.NL.xKR.eb23.eI066.DII.140.v5.halo.test5.eps}
    \caption{Spatial distribution of cosmic ray proton (CRp) energy
      density in Coma cluster. The red dash-dotted line shows the
      required distribution of seed CRps that generate secondary
      electrons via p-p collisions required to reproduce Coma radio
      brightness observations after Fermi-II reacceleration
      \citet{brunetti12}. The blue solid line shows the distribution of
      fossil CRps found in cosmological simulations, which disagrees
      with the required profile. We normalize the required distribution
      of CRps by fixing the total CRp energy $E_p$ to 0.3 percent of the
      total thermal energy, consistent with observations
      \citet{2014ApJ...787...18A,2012ApJ...757..123A}.}
    \label{fig:Edens}
  \end{minipage}
\end{figure}
Indeed, arriving at a seed population with the required
characteristics is highly constraining, and has the potential to teach
us much about the origin of CRps/CRes in clusters. \AP{In this paper
  we consider 3 new scenarios that individually or combined can
  reproduce the observed radio profiles and spectrum in the Coma
  cluster without violating gamma-ray constraints:} (i) Our model
\Mflatturb: a significantly spatially flatter turbulent profile than
what was adopted in \citep{brunetti12}, which allows seed CRps to
follow the steep profile that is suggested by structure formation
simulations. (ii) Our model \Mstream: streaming CRps that produce flat
distributions of CRs in the ICM
\citep{ensslin11,wiener13,2014MNRAS.438..124Z}, which also flattens
the secondary electron distribution. (iii) Our model \Mprimary: if the
acceleration efficiency of CRps is below about $0.1$~{\%} in weak
(perpendicular) shocks and the ratio of injected electrons-to-protons
$K_{\rmn{ep}} \sim 0.1$, this yields a dominant primary population
with a flat spatial distribution, since primaries have a weaker
density dependence than secondaries.

\AP{To pursue these three possibilities further, we employ cosmological
  simulations of CRs in clusters. In tandem with new insights from our
  recent work on DSA generated fossil electrons \citep{pinzke13}, we
  generate the first quantitative calculation of primary and secondary
  seed electrons and compare to observations.}

\sout{In this work we pursue these three possibilities further. We
  employ cosmological simulations of CRs in clusters, in tandem with
  new insights from our recent work on DSA generated fossil electrons
  %\citep{pinzke13}, to generate the first quantitative calculation of
  , to generate the first quantitative calculation of
  primary and secondary seed electrons.}

% --- section: Method --- %
{\bf Method.}  The transport of relativistic electrons and protons in
the ICM is a complex process that depends both on the details of the
thermal component (gas density, temperature, and pressure) as well as
non-thermal component (turbulence, magnetic fields, fossil CRs). We
use high resolution galaxy cluster simulations to derive the thermal
and fossil CR properties (shock accelerated primary CRes and CRps, as
well as secondary CRes produced in p-p collisions)
\citep{2007MNRAS.378..385P,pfrommer08,pinzke10,pinzke13}. In this
paper we focus on our simulated cluster, g72a, which is a massive
$1.6\times10^{15}\,M_\odot$ cluster that experienced a merger about
1-2 Gyrs ago \citep{2009MNRAS.399..497D}. Since the cluster mass,
density and temperature profiles are all similar to the well studied
Coma cluster \citep{2007MNRAS.378..385P,pinzke10}, we will compare our
calculations to radio and gamma-ray observations of Coma.

In our Galaxy, the CRe-to-CRp ratio at a few GeV is $K_{\rmn{ep}} \sim
10^{-2}$. Hence, we adopt this as a fiducial value for the CRe-to-CRp
acceleration efficiency (see \citep{pinzke13} for more
discussion). However, as recent PIC simulations have shown, this is
likely very different at weak shocks, with electrons efficiently
accelerated at perpendicular shocks
\citep{2014ApJ...794..153G,2014ApJ...797...47G}, and ions efficiently
accelerated at parallel shocks \citep{2014ApJ...783...91C}. Thus,
depending on magnetic geometry, $K_{\rmn{ep}}$ could be either larger
or smaller. \AP{In this work we use a simple test-particle model for
  the CRp acceleration, where we adopt a fit to Monte Carlo
  simulations of the thermal leakage process that relates the momentum
  of injected protons to the thermal energy of the shocked plasma
  \citep{kang11}. We set an upper limit on the ratio of accelerated
  proton-to-dissipated energy in the downstream of strong shocks that
  varies from 1-10\%, depending on the adopted model (for more
  details, see the Results section). In order not to violate energy
  conservation with a fixed limit for the acceleration efficiency, we
  steepen the spectral index of the accelerated CRps at the limit
  \citep{pinzke13}. For weak shocks the efficiency is a factor 10-100
  lower and well below the limit. Some observations of radio relics
  suggest high values of $K_{\rmn{ep}}$, due to the absence of
  gamma-ray emission, which probes the CRp population
  \citep{2014MNRAS.437.2291V}. This suggests primary CRes as a viable
  alternative scenario to secondary CRes as seeds for the giant
  RHs. In our {\it M-primaries} scenario, we assume that the momentum
  of injected electrons and protons are equal, and in addition we
  adopt a $K_{\rmn{ep}} =0.1$ (viable for primarily perpendicular
  shocks). While this appears to contradict the radial bias of
  magnetic fields in the bulk of the ICM as suggested by observations
  \citep{2010NatPh...6..520P} and cluster simulations
  \citep{2011ApJ...740...81R}, it does not necessarily apply to the
  accretion shock regions, which show a field geometry with a net
  perpendicular bias with respect to the shock normal---at least for
  giant radio relics \citep{2010Sci...330..347V}. We leave further
  exploration of parameter space to future work.}

As previously noted, secondaries produced by shock accelerated CRp
have the wrong spatial profile to explain RH observations; because
they arise from a two body process, they are too centrally
concentrated. They also produce $\gamma$-ray emission in excess of
Fermi-LAT upper limits
\citep{2012ApJ...757..123A,brunetti12,2014ApJ...787...18A}. However,
if CRps stream in the ICM, then their spatial profile could
potentially flatten sufficiently \citep{ensslin11,wiener13}. This
scenario is very attractive: it generates seed electrons with the
right spatial footprint, and by removing CRps from the core, obeys
gamma-ray constraints. Turbulence plays two opposing roles:
Alfv{\'e}nic turbulence damps waves generated by the CR streaming
instability \citep{yan02,farmer04}, thus reducing self-confinement;
but compressible fast modes scatter CRs directly. Turbulent damping is
still efficient for highly subsonic conditions \citep{wiener13}, while
we assume compressible fast modes only provide effective spatial
confinement during the periods of transonic, highly super-Alfv{\'e}nic
($M_{\rm A} \sim 5$) turbulence associated with mergers. Thus, CRs can
stream out when the cluster is kinematically quiescent. Furthermore,
even Alfv{\'e}nic streaming timescales are relatively short ($\sim
0.1-0.5$ Gyr; \cite{wiener13}) compared to the timescale on which the
CRp population is built up. Based on these findings, we adopt a toy
model for our \Mstream scenario in which CR streaming quickly produces
flat CRp profiles. We assume that CRs cannot
stream significantly past perpendicular $B$-fields at the accretion
shock, so that the total number of CRs is conserved. \AP{Note that the seed CRps that are
  Fermi-II reaccelerated, and produce secondary electrons that emit
  radio emission with frequencies $\gtrsim 350$~MHz, have relatively
  high energies $\gtrsim 10$~GeV and stream more efficiently than low
  energy CRs \citep{wiener13}.}

Given a seed population of CRs, we adopt essentially the same set of
plasma physics assumptions as the reacceleration model for RHs
\citep{brunetti07,brunetti11}, leaving exploration of parameter space
to future work. We solve the isotropic, gyro-phase averaged
Fokker-Planck equation (via a Crank-Nicholson scheme) for the time
evolution of the CRe distribution in the Lagrangian frame
\citep{brunetti07,brunetti11}:
\begin{eqnarray}
{{d f_{\rmn{e}}(p,t)}\over{d t}} &\!=&
\frac{\partial}{\partial p}
\left\{
f_{\rmn{e}}(p,t)\left[
\left|{{dp}\over{dt}}\right|_{\rm C} 
+ \frac{p}{3}\left(\vec{\nabla}\cdot \vec{\upsilon}\right)\right.\right.
\nonumber\\
&+& \left.\left. \left|{{dp}\over{dt}}\right|_{\rm r}
- {1\over{p^2}}{{\partial }\over{\partial p}}\left(p^2 D_{pp}\right) 
\right]\right\} - \left(\vec{\nabla}\cdot \vec{\upsilon}\right) f_{\rmn{e}}(p,t)
\nonumber\\
&+& {{\partial^2 }\over{\partial p^2}}
\left[
D_{pp} f_{\rmn{e}}(p,t) \right]+ Q_{\rmn{e}}\left[p,t;f_{\rmn{p}}(p,t)\right]   \, .
\label{elettroni}
\end{eqnarray}
Here $f_{\rmn{e}}$ is the one-dimensional distribution in position $x$
(suppressed for clarity), momentum $p$ and time $t$ (which is
normalized such that the number density is given by
$n_{\rmn{e}}(t)=\int d p f_{\rmn{e}}(p,t)$), $d/dt=\partial/\partial
t+\vec{\upsilon}\cdot \vec{\nabla}$ is the Lagrangian derivative,
$\vec{\upsilon}$ is the gas velocity, $|dp/dt|$ represents radiative
(r) and Coulomb (C) losses, $D_{pp}$ is the momentum space diffusion
coefficient, and $Q_{\rmn{e}}$ denotes the injection rate of primary
and secondary electrons in the ICM. The $\vec{\nabla}\cdot
\vec{\upsilon}$ terms represent adiabatic gains and losses. During
post-processing of our Coma-like cluster simulation, we solve the
Fokker-Planck equation over a redshift interval from $z=5$ to 0. The
simulated cluster undergoes a major merger over the last 1-2~Gyrs that
injects large turbulent eddies. After about 1~Gyr those have decayed
down to the scale needed to reaccelerate particles \AP{and the radio
  halo turns on shortly after. This naturally explains why giant radio
  halos are only seen in a fraction of all merging clusters.} In all
our calculations we assume that turbulent reacceleration is
efficiently accelerating particles for 650 Myrs and that during this
turbulent phase CR streaming and spatial diffusion can be
neglected. In our \Mstream model, CR streaming and diffusion are
incorporated separately during kinematically quiescent times that
precede the merger. As a result, flat CRp profiles are produced on
relatively short timescales ($\sim 0.1-0.5$ Gyr).

The time evolution of the spectral energy distribution of CRps,
$f_{\rmn{p}}$, is similarly given by:
\begin{eqnarray}
{{d f_{\rmn{p}}(p,t)}\over{d t}} &=
{{\partial }\over{\partial p}}
\left\{
f_{\rmn{p}}(p,t)\left[ \left|{{dp}\over{dt}}\right|_{\rm C}
+ \frac{p}{3}\left(\vec{\nabla}\cdot \vec{\upsilon}\right)\right.\right.
\nonumber\\
&-\left.\left. {1\over{p^2}}{{\partial }\over{\partial p}}\left(p^2 D_{pp}\right)
\right]\right\} - \left(\vec{\nabla}\cdot \vec{\upsilon}\right) f_{\rmn{p}}(p,t)
\nonumber\\
&+ {{\partial^2 }\over{\partial p^2}}
\left[ D_{pp} f_{\rmn{p}}(p,t) \right] - {{f_{\rmn{p}}(p,t)}\over{\tau_{\rm had}(p)}}
+ Q_{\rmn{p}}(p,t)\, ,
\label{eq:FP_p}
\end{eqnarray}
where $Q_{\rmn{p}}(p,t)$ denotes the injection rate of shock
accelerated CRps as a function of momentum $p$ and time $t$, and
$\tau_{\rm had}$ is the timescale of hadronic losses that produce
pions via CRp collisions with thermal protons of the ICM
\cite[e.g.][]{brunetti11}.  We incorporate momentum diffusion for
electrons and protons from transit-time-damping (TTD) resonance with
compressible magneto-hydrodynamic (MHD) turbulence, to model Fermi-II
reacceleration \citep{brunetti07,brunetti11}. The TTD resonance
requires the wave frequency $\omega=k_\parallel\upsilon_\parallel$,
where $k_\parallel$ and $\upsilon_\parallel$ are the parallel
(projected along the magnetic field) wavenumber and particle velocity,
respectively. This implies that the particle transit time across the
confining wave region matches the wave period,
$\lambda_{\parallel}/v_{\parallel}=T$. The resonance changes the
component of particle momentum parallel to seed magnetic fields, which
over time leads to increasing anisotropy in the particle distribution
that decreases the efficiency of reacceleration with time. As in
ref.{\ }\cite{brunetti11}, we assume that there exists a
mechanism---such as the firehose instability---that isotropizes the CR
distribution function at the gyroscale and on the reacceleration time
scale, which ensures sustained efficient reacceleration with time. The
particle pitch-angle averaged momentum-diffusion coefficient of
isotropic particles that couple to fast magnetosonic modes via TTD
resonance is \cite{brunetti07} (Eqn. 47):
\begin{eqnarray}
  D_{pp}(p,t) = \frac{\pi}{16} \frac{p^2}{c\,\rho}
  \left\langle\frac{\beta |B_k|^2}{16 \pi \,W}\right\rangle
  I_\theta
  \int_{k_\rmn{cut}}\mathcal{W}(k)k\,d k\,,
\label{eq:dpp}
\end{eqnarray}
where $\beta$ is the thermal-to-magnetic pressure ratio, and $c$
is the speed of light. The energy density $W$ of a mode in a
magnetized plasma stems from both electromagnetic fields and resonant
particles. For a high-$\beta$ plasma, the pitch angle averaged ratio of
beta-weighted magnetic-to-total energy density saturates to $\langle\beta
|B_k|^2/2W\rangle\approx 10^{1.4}$ (see figure 2 in
\cite{brunetti07}). The pitch angle of the CR momentum with the
magnetic field orientation is given by $\theta$, and
$I_\theta=\int_0^{\arccos(\Vph/c)} d\theta {\frac{ \sin^3 \theta }{
    |\cos \theta | }}
\left[1+\left(\frac{\Vph}{c\,\cos{\theta}}\right)^2\right]^2$. Here
$V_\rmn{ph}$ is the phase velocity of the fast magnetosonic waves
given approximately by the sound speed, $\Vph \sim c_\rmn{s}$. For a sound
speed typical for the ICM of 1000~km/s, $I_\theta\approx5$. As in
\cite{brunetti07}, we initially assume that the velocity of turbulent
eddies is $V_0\approx 0.47 c_\rmn{s}$ throughout the cluster. This gives a
turbulent acceleration time scale, $\tau_{pp} = p^2/4D_{pp}$, that is
typically few 100 Myrs in the ICM.

We adopt a simplified isotropic Kraichnan MHD turbulent spectrum for
the fast modes per elemental range $dk$ of the form $\mathcal{W}(k) =
\sqrt{2/7\,I_0\,\rho\,\langle \Vph \rangle}\,k^{-3/2}\,,$ for
$k_0<k<k_\rmn{cut}$, where we assume an injection scale for the
turbulence, $k_0= 2\pi/(100~\mbox{kpc})$. The volumetric injection
rate of turbulent energy, $I_0$, is fixed by requiring that the total
turbulent energy density on the largest scales
$\epsilon_\rmn{turb}=\int \mathcal{W}(k) dk \approx 0.2
\epsilon_\rmn{th}$, where $\epsilon_\rmn{th}$ is the thermal energy
density \citep{brunetti07,brunetti11}. In this work we investigate
different spatial models for injected turbulence. We assume that
$\epsilon_\rmn{turb} \propto \epsilon_\rmn{th}^{\alpha_\rmn{tu}}$,
where $\alpha_\rmn{tu}= 0.66$ for \Mflatturb, $\alpha_\rmn{tu}= 0.81$
for \Mstream, and $\alpha_\rmn{tu}= 0.88$ for \Mprimary (note that in
previous work \AP{on the Coma cluster, $\alpha_\rmn{tu}= 1$ was
  adopted \citep{brunetti12}, which together with the different
  distributions for CRs constitute the main differences compared to
  our work}). Our flatter turbulent profiles are motivated by fits to
cosmological simulations
\citep{2009ApJ...705.1129L,2010ApJ...725.1452S,2012ApJ...758...74B}
and the range indicates uncertainties of the turbulent profile in
Coma. Future observations (by Astro-H) and simulations will help to
clarify this issue. Provided dissipation of turbulence in the ICM is
collisionless, turbulent cascades of compressible modes become
suppressed when thermal and relativistic particles resonantly interact
with magnetosonic waves via TTD on a timescale $\Gamma^{-1}$ that is
approaching the cascading timescale given by $\tau_{kk} \approx
k^2/D_{kk}$. Here the wave-wave diffusion coefficient of magnetosonic
modes is given by $D_{kk} \approx \Vph k^4
\left(\frac{\mathcal{W}(k)}{\rho\,\Vph^2}\right)\,.$ Thus, the cascade
is suppressed for wave numbers above:
\begin{equation}
\label{eq:kc}
  k_\rmn{cut} \approx \frac{81}{14} \frac{I_0}{\rho \langle \Vph \rangle}
  \left(\frac{\langle\sum_i \Gamma_i(k,\theta)\rangle}{k}\right)^{-2}\,.
\end{equation}
where $2\pi/k_\rmn{cut}\sim 0.1-1$~kpc in the ICM. This constitutes an
effective mean free path for CRs, unless plasma instabilities can
mediate interactions between turbulence and particles on smaller
scales \citep{brunetti11}. In this work we only consider damping via
TTD due to thermal electrons, and neglect subdominant damping with
thermal protons and relativistic particles. The latter will be
subdominant in the ICM for a CR-to-thermal energy density ratio
$\lesssim 10 \%$ \citep{brunetti07}, which is always satisfied \AP{in our models}. The
azimuthally averaged turbulent damping rate from thermal electrons
\citep{brunetti07} in a high-$\beta$ plasma is $
\langle\Gamma_{\rmn{e}}\rangle \approx \langle k\,\Vph\,\sqrt{3\pi
  x/20}\exp(-5x/3)\sin^2{\theta}\rangle\approx 0.0435k\,\Vph$, where
$x=(m_{\rmn{e}}/m_{\rmn{p}})/\cos^2{\theta}$. To compute the
synchrotron surface brightness profiles, we use the profile of the
$\sim\mug$ magnetic field strength derived from Faraday rotation
observations of Coma \citep{bonafede10} in combination with the density
profile derived from X-ray measurements \citep{1992A&A...259L..31B}.

\sout{We quantify the conditions under which a primary or secondary
  origin for the seed electrons dominates, and elucidate an
  observational discriminant. One possibility is to use high-frequency
  radio observations (with the Jansky VLA and Sardina radio
  telescopes) when turbulent reacceleration (which has a high energy
  cutoff) is no longer efficient. A stacked radio spectrum may reveal
  the glow of radio emission due to steady state secondary
  population. Due to the much more intermittent nature of DSA
  injection, primary CRe will instead a sharp cutoff at high energies
  due to cooling, and will not be visible at high frequencies.}

% --- section: Results and discussion --- %
{\bf Results and Discussion.} After turbulent reacceleration, the
volume-weighted, relative CRp energy density and CRp number density
inside the RH for \Mflatturb (\Mstream), are found to be 3 (2) \% and
$3.0\times10^{-8}$ ($4.5\times10^{-8}$), respectively. As we will see
later, these densities are just of the right order of magnitude to
reproduce radio observations in the Coma cluster. \AP{In addition we
  predict the gamma-ray flux within the virial radius of the Coma
  cluster from CRps that produce decaying neutral pions for \Mflatturb
  (\Mstream) with $F_\gamma(>500\,\rmn{MeV})=4.8\times10^{-10}
  (2.3\times10^{-10}) \mathrm{ \,ph\, s}^{-1}\mathrm{cm}^{-2}$. We
  predict fluxes from these models that are slightly larger than in
  \cite{brunetti12}, where the differences comes from our steeper CRp
  profiles in addition to simulation based formalism we rely on that
  accounts for both Coulomb and hadronic losses during the build up of
  the CR distribution in contrast to the scaling relations adopted in
  their paper. Interestingly the gamma-ray flux from both our
  scenarios are just below recent Fermi-LAT limits derived from a
  gamma-ray profile similar to \Mflatturb where
  $F_\gamma(>500\,\rmn{MeV})<5.3\times10^{-10} \mathrm{ \,ph\,
    s}^{-1}\mathrm{cm}^{-2}$ \footnote{Fabio Zandanel, private
    communication. See also
    \citep{2014MNRAS.440..663Z,2014ApJ...787...18A}.} and will be
  probed in the next few years by Fermi-LAT. } The spectral index of
the CRp distribution is relatively steep $\alpha_{\rmn{p}}\sim2.6$ for
the CRp energies $E \gtrsim 10$~GeV that are relevant for the
injection of radio-emitting secondary CRes.  The steep spectrum is
ultimately a consequence of our test particle model for Fermi-I
acceleration \citep{pinzke13}, where we steepen the spectral index to
avoid acceleration efficiencies above $\zeta_{\rmn{p}} \sim 10\%$.

In Fig.~\ref{fig:sync_profile}, we find that all three scenarios in
which the seeds undergo Fermi-II reacceleration can reproduce the Coma
RH profile at 352~MHz. In the panel {\it Brunetti et al. (2012)} we
show that without CR streaming or a flat turbulent profile, our
simulations of reaccelerated CRs produce radio profiles that are too
steep. Indeed, even using the assumptions of previous work -- where
complete freedom in the seed population was allowed -- it is not
possible to reproduce observations in both frequencies. \AP{This
  signals that the problem is generic and requires either additional
  modifications to the plasma physics of acceleration or a better
  understanding of potential observational systematics. In addition
  there are differences in the simulated density and temperature
  profiles in comparison to the observed profile in Coma that impact
  the CR abundance as well as cooling and reacceleration.}

In principle, reacceleration via TTD leads to spectral steepening with
particle energy due to the inefficiency of the acceleration process to
counter the stronger cooling losses with increasing energy. Since
synchrotron emission peaks at frequency $\nu_\rmn{syn}\simeq 1\,
B/\mu\rmn{G} (\gamma/10^4)^2\,\rmn{GHz}$, this translates into a
spectral steepening of the total radio spectrum (see
Fig.~\ref{fig:sync_spectrum}). A given radio window samples higher
energy electrons for a decreasing field strength in the cluster
outskirts. Hence, the spectral steepening with energy should translate
into a radial spectral steepening \citep{brunetti12}. However, because
of the weak dependence of the electron Lorentz factor on emission
frequency ($\gamma\propto\sqrt{\nu_\rmn{syn}}$), this effect is only
visible in our simulations for $\nu_\rmn{syn}\gtrsim5$~GHz. Most
importantly, our simulated fluid elements at a given radius sample a
broad distribution of shock history, density and temperature, which
implies very similar synchrotron brightness profiles at
$\nu_\rmn{syn}=352$~MHz and 1.4 GHz. The discrepancy of the observed
and simulated 1.4 GHz profiles could instead be due to systematic flux
calibration error in single dish observations. Interestingly, we can
match the 1.4 GHz data if we reduce the zero point by adding 10\% of
the central flux to every data point; this flattens the outer
profile \footnote{Lawrence Rudnick, private communication.}.  \AP{Note
  that decreasing acceleration efficiency with radius does not change
  this conclusion much because of the weak radial dependence of
  $D_\rmn{pp}(R)\propto \epsilon_\rmn{th}(R)^{(\alpha_\rmn{tu}+1)/2}/\sqrt{T(R)}$.}
Alternatively, this may point to weaknesses in the theoretical
modeling of the particle acceleration process and may require a
stronger cutoff in the particle energy spectrum.

\begin{figure*}
\begin{minipage}{1\columnwidth}
  \begin{center}\LARGE{\Mflatturb:}\\ 
    \includegraphics[width=\columnwidth]{figures/sbright.nu.DIIcomp.I0.g72a.Rad14.2400p.z0.NL.xKR.eb23.eI066.140.v5.halo.test5.eps}
  \end{center}
\end{minipage}
\begin{minipage}{1\columnwidth}
   \begin{center}\LARGE{\Mstream:}\\
     \includegraphics[width=\columnwidth]{figures/sbright.nu.DIIcomp.flatCR.g72a.Rad14.2400p.z0.NL.xKR.eb23.eI081.flatCR.140.v5.halo.test5.eps}
   \end{center}
\end{minipage}
\\
\begin{minipage}{1\columnwidth}
   \begin{center}\LARGE{\Mprimary:}\\
     \includegraphics[width=\columnwidth]{figures/sbright.nu.DIIcomp.Pri.g72a.Rad14.2400p.z0.NL.xKR.eb23.eI088.140.v5.halo.test5.eps}
   \end{center}
\end{minipage}
\begin{minipage}{1\columnwidth}
   \begin{center}\LARGE{\it Brunetti et al. (2012)}:\\
     \includegraphics[width=\columnwidth]{figures/sbright.nu.DIIcomp.Brunetti.g72a.Rad14.2400p.z0.NL.xKR.eb23.140.v5.halo.test5.eps}
   \end{center}
\end{minipage}
\caption{Radio surface brightness profiles of Fermi-II reaccelerated
    CR electrons of a simulated post-merging cluster similar to
    Coma. We compare profiles at 352~MHz (blue lines and crosses
    \citet{brown11}) to those at 1.4~GHz (green lines and crosses
    \citet{deiss97}). The red crosses show the reprocessed 1.4~GHz
    data, where a zero level of about 10 \% of the central value is
    adopted. The solid lines show predicted emission from a
    reaccelerated fossil population, while dotted lines show emission
    from a fossil population without reacceleration. The panels show
    the emission of our models \Mflatturb (upper left panel), \Mstream
    (upper right panel), \Mprimary (lower left panel), and simulated
    secondary electrons together with previous estimates
    \citet{brunetti12} for the Coma cluster (lower right panel).}
  \label{fig:sync_profile}
\end{figure*}

In Fig.~\ref{fig:sync_spectrum} we show that our three models that
include Fermi-II reacceleration can individually reproduce the
convexly curved total radio spectrum found in the Coma cluster. Seed
CRs that do not experience turbulent reacceleration have a power-law
spectrum in disagreement with observations. In order to match both the
spatial and spectral profiles in Coma, we can constrain the
acceleration efficiency for the strongest shocks in our three models
\Mstream, \Mflatturb, and \Mprimary to $\zeta_{\rmn{p}} < 0.15$,
$\zeta_{\rmn{p}}<0.05$, and $\zeta_{\rmn{e}} <0.004$,
respectively. Following the Mach number ($\mathcal{M}$)-dependence of
the acceleration efficiency suggested in \cite{pinzke13}, the
efficiency in weak shocks ($\mathcal{M}\sim 2.5-3.5$) that dominates
the CR distribution function, has an acceleration efficiency for
protons $\zeta_{\rmn{p}}\sim0.0001-0.01$, and for electrons
$\zeta_{\rmn{e}}\sim 0.001$.

\begin{figure}
  \includegraphics[width=0.99\columnwidth]{figures/sync.spec.g72a.140.v5.halo.test5.eps}
  \caption{Radio synchrotron spectra. Red lines are derived from
    simulations, while the black crosses are compiled from
    observations \citet{2010PhDT.......259P}. The lines show the
    emission of our models \Mstream (solid line), \Mflatturb (dashed
    line), and \Mprimary (dash-dotted line). We contrast the
    reaccelerated populations to a population of DSA accelerated CR
    protons that produce secondaries (dotted line).}
  \label{fig:sync_spectrum}
\end{figure}

% --- section: Conclusions --- %
{\bf Conclusions.}  The standard reacceleration model for RHs requires
a population of seed electrons to undergo turbulent
reacceleration. These seeds are generally thought to be secondary
electrons from hadronic CRp interactions. In this work we use
cosmological simulations to derive a population of seed CRps
originating from structure formation shocks and merger shocks during
the cluster build up. The resulting secondary population is
inconsistent with RH observations. \AP{We propose 3 possible solutions
  that all produce gamma-ray emission below current upper limits and
  that reproduce both, the spectrum and the surface brightness
  profiles of the Coma radio halo: (i) CRps that stream out of the
  central core and produce flat CR profiles. (ii) Alternatively, if
  indeed the acceleration efficiency of CRps is below about $0.1$ {\%}
  in weak shocks and the ratio of injected electrons and protons
  $K_{ep} \sim 10^{-1}$, CR electrons accelerated directly in shocks
  dominate over secondaries.  This seed population of CRes also has
  the correct spatial and spectral features alone, or potentially
  complements secondaries to explain radio observations. (iii)
  Finally, injected turbulence that is flatter than in previously
  adopted models, which allows seed CRps to follow the steep profile
  that is suggested by structure formation. We will pursue further
  implications and distinguishing characteristics of these competing
  models in future work.} \sout{We propose 3 possible solutions that
  all produce gamma-ray emission below current upper limits and that
  reproduce both the spectrum and the surface brightness profiles of
  the Coma RH: (i) injected turbulence that is flatter than in
  previously adopted models, (ii) streaming CRs, (iii) shock
  accelerated CR electrons injected with $K_{\rmn{ep}} \sim 0.1$. We
  will pursue further implications and distinguishing characteristics
  of these competing models in future work.}

{\bf Acknowledgments.} We thank Josh Wiener for discussions on CR
streaming. We are also grateful to Lawrence Rudnick for discussion on
uncertainties in the 1.4 GHz radio data. Finally, we thank Fabio
Zandanel for recalculating gamma-ray limits and Gianfranco Brunetti
for providing the radio profiles for his model. A.P. is
grateful to the Swedish research council for financial
support. S.P.O. thanks NASA grant NNX12AG73G for
support. C.P.~gratefully acknowledges financial support of the Klaus
Tschira Foundation.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-0.7cm}

\bibliography{bibtex/paper}
\bibliographystyle{mn2e}

\end{document}

### 2015-10-01 paper.tex
test

--- 2015-10-01 paper.old.tex
@@
-%\documentclass[prl,twocolumn,amsmath,amsfonts,amssymb,showpacs,usenatbib]{revtex4} 
-%\documentclass[useAMS,usenatbib]{mn2e}
-%\usepackage{epsfig,psfrag,graphicx,xspace}
-%\usepackage[normalem]{ulem}
-%\usepackage{txfonts}
-%\usepackage{natbib}
-%\usepackage{amsfonts,amssymb}
-%\usepackage{amsmath,amssymb}
-%\usepackage{graphicx}
-
 \documentclass[useAMS,usenatbib]{mn2e}
@@
 \usepackage[normalem]{ulem}
-\usepackage{graphicx}
+\usepackage{graphicx,color}
 \usepackage{natbib}
@@
 \newcommand{\grl}{GRL}
+\newcommand{\nat}{Nature}
 \newcommand{\Mstream}{{\it M-streaming}\xspace}
@@
 \newcommand{\dd}{\mathrm{d}}
-%\newcommand{\rmn}{\mathrm}
 \newcommand{\Vph}{V_\mathrm{ph}}
 \newcommand{\mug}{\mu G}
-
-\def\del#1{{}}
-%\def\del#1{{\bf (DELETED TEXT)}}
-\def\C#1{{\bf #1}}
-\def\AP#1{{\bf  AP: #1}}
-\def\SPO#1{{\bf SPO: #1}}
-\def\CP#1{{\bf  #1}}
 
@@
 \author[A. Pinzke, S. Peng Oh and C. Pfrommer] 
-{Anders Pinzke$^{1,2}$\thanks{apinzke@fysik.su.se (AP); peng@physics.ucsb.edu (PO); christoph.pfrommer@h-its.org (CP)}, S. Peng Oh$^{3}$ and Christoph Pfrommer$^{4}$\footnotemark[1]\\
+{Anders Pinzke$^{1,2}$\thanks{apinzke@fysik.su.se (AP); peng@physics.ucsb.edu (SPO); christoph.pfrommer@h-its.org (CP)}, S. Peng Oh$^{3}$ and Christoph Pfrommer$^{4}$\footnotemark[1]\\
 $^{1}$The Oskar Klein Centre for Cosmoparticle Physics, Department
@@
 \begin{abstract}
-About $1/3$ of X-ray-luminous clusters show smooth, unpolarized radio
-emission on $\sim$Mpc scales, known as giant radio halos. One
+  About one third of X-ray-luminous clusters show smooth, unpolarized
+  radio emission on $\sim$Mpc scales, known as giant radio halos. One
   promising model for radio halos is Fermi II acceleration of seed
-relativistic electrons by turbulence of the intracluster medium (ICM);
-Coulomb losses prohibit acceleration from the thermal pool. However,
-the origin of seed electrons has never been fully explored. Here, we
-integrate the Fokker-Planck equation of the cosmic ray (CR) electron
-and proton distributions in a cosmological simulations of cluster
-formation. For standard assumptions, structure formation shocks lead
-to a seed electron population which produces too centrally
-concentrated radio emission. Instead, we present three realistic
-scenarios that each can reproduce the spatially flat radio emission
-observed in the Coma cluster: (1) the ratio of injected turbulent
-energy density to thermal energy density increase significantly with
-radius, as seen in cosmological simulations. This generates a flat
-radio profile even if the seed population of CRs is steep with
-radius. (2) Self-confinement of energetic CR protons can be
-inefficient, and CR protons may stream at the Alfv{\'e}n speed to the
+  relativistic electrons by turbulence in the intracluster medium
+  (ICM); Coulomb losses prohibit acceleration from the thermal
+  pool. However, the origin of seed electrons has never been fully
+  explored. Here, we integrate the Fokker-Planck equation of the
+  cosmic ray (CR) electron and proton distributions in cosmological
+  simulations of cluster formation. For standard assumptions,
+  structure formation shocks lead to a seed electron population which
+  produces too centrally concentrated radio emission. Instead, we
+  present three plausible scenarios for the seed CRs that each
+  can reproduce the spatially flat radio emission observed in the Coma
+  cluster. (1) The CR proton to electron acceleration efficiency
+  $K_\rmn{ep} \sim 0.1$ is assumed to be larger than in our Galaxy
+  ($K_\rmn{ep} \sim 10^{-2}$), due to the magnetic geometry at the
+  shock. The resulting primary electrons dominate the radio emission,
+  which is more extended in comparison to radio emission from
+  secondary electrons that result from hadronic CR interactions in the
+  ICM. (2) CR protons may stream at the Alfv{\'e}n speed to the
   cluster outskirts when the ICM is relatively quiescent. A spatially
   flat CR proton distribution develops and produces the required
-population of secondary seed electrons. (3) The CR proton to electron
-acceleration efficiency $K_{ep} \sim 0.1$ is assumed to be larger than
-in our Galaxy ($K_{ep} \sim 10^{-2}$), due to the magnetic geometry at
-the shock. The resulting primary electron population dominates. Due to
-their weaker density dependence compared to secondary electrons, these
-primaries can also reproduce radio observations.  These competing
-non-trivial solutions provide incisive probes of non thermal processes
-in the high-$\beta$ ICM.
+  population of secondary seed electrons. (3) The ratio of injected
+  turbulent energy density to thermal energy density increase
+  significantly with radius, as seen in cosmological simulations. This
+  generates a flat radio profile when CRs are reaccelerated even
+  if the seed population of CRs is steep with radius. These competing
+  non-trivial solutions provide incisive probes of non thermal
+  processes in the high-$\beta$ ICM.
 \end{abstract}
 
-% --- keywords --- %
-\begin{keywords}
-  magnetic fields, cosmic rays, radiation mechanisms: non-thermal, elementary
-  particles, galaxies: cluster: general, Galaxy: fundamental parameters
-\end{keywords}
-%\maketitle
+%% --- keywords --- %
+%\begin{keywords}
+%  magnetic fields, cosmic rays, radiation mechanisms: non-thermal, elementary
+%  particles, galaxies: cluster: general, Galaxy: fundamental parameters
+%\end{keywords}
+%%\maketitle
 
@@
 
-One promising model for RHs is re-energetization of seed suprathermal
-electrons by Fermi II acceleration when ICM turbulence becomes transonic during
-mergers \citep{2001MNRAS.320..365B,brunetti07}. Due to the short radiative
-cooling time of high-energy relativistic electrons, the cluster synchrotron
-emission quickly fades away after a merger, which naturally explains the
-observed bimodality of RHs \cite[see
+There have been two competing models proposed to explain RHs.  The
+radio emitting electrons in the ``hadronic model'' are produced in
+inelastic (hadronic) CR proton interactions with protons of the
+ambient thermal ICM
+(\citealp{1980ApJ...239L..93D,1999APh....12..169B,2001ApJ...562..233M,
+  2004A&A...413...17P,2008MNRAS.385.1211P,ensslin11}). CR protons and
+heavier nuclei may have been accelerated and injected into the ICM by
+structure formation shocks, active galactic nuclei and galactic
+winds. However, the strong bimodality that separates X-ray luminous
+clusters into radio-active and radio-quite clusters (and requires a
+fast switch on/off mechanism of the RH emission) and the very extended
+RH emission at low frequencies in Coma (352~MHz) represent a major
+challenge to this model class \citep{brunetti12,2014MNRAS.438..124Z}.
+
+The alternative model for RHs is re-energization of seed
+suprathermal electrons by Fermi II acceleration when ICM turbulence
+becomes transonic during mergers
+\citep{1987A&A...182...21S,1993ApJ...406..399G,2001MNRAS.320..365B,
+  2004MNRAS.350.1174B,brunetti07,brunetti11}. Due to the short
+radiative cooling time of high-energy relativistic electrons, the
+cluster synchrotron emission quickly fades away after a merger, which
+naturally explains the observed bimodality of RHs \cite[see
   e.g.][]{2013MNRAS.429.3564D,2014MNRAS.443.3564D}.
@@
   also][]{pinzke10,2014MNRAS.439.2662V}.
-\begin{figure}
-  \begin{minipage}{1.0\columnwidth}
+\begin{figure*}
   \includegraphics[width=1.0\columnwidth]{figures/fCR.radius.coma.g72a.Rad14.2400p.z0.NL.xKR.eb23.eI066.DII.140.v5.halo.test5.eps}
-    \caption{Spatial distribution of cosmic ray proton (CRp) energy
-      density in Coma cluster. The red dash-dotted line shows the
-      required distribution of seed CRps that generate secondary
-      electrons via p-p collisions required to reproduce Coma radio
-      brightness observations after Fermi-II reacceleration
-      \citet{brunetti12}. The blue solid line shows the distribution of
-      fossil CRps found in cosmological simulations, which disagrees
-      with the required profile. We normalize the required distribution
-      of CRps by fixing the total CRp energy $E_p$ to 0.3 percent of the
-      total thermal energy, consistent with observations
-      \citet{2014ApJ...787...18A,2012ApJ...757..123A}.}
+  \includegraphics[width=1.0\columnwidth]{figures/turb_profile_ratio.eps}
+  \caption{Left: spatial distribution of CRp energy density in the
+    Coma cluster. The red dash-dotted line shows the required
+    distribution of seed CRps that generate secondary electrons via
+    p-p collisions required to reproduce Coma radio brightness
+    observations after Fermi-II reacceleration \citep{brunetti12}. The
+    blue solid line shows the distribution of fossil CRps found in
+    cosmological simulations, which disagrees with the required
+    profile. We normalize the required distribution of CRps by fixing
+    the total CRp energy $E_\rmn{p}$ to 0.3 percent of the total
+    thermal energy, consistent with observations
+    \citep{2014ApJ...787...18A,2012ApJ...757..123A}. Right: the ratio
+    of turbulent-to-thermal energy densities in our three models which
+    is parametrised as $\epsilon_\rmn{turb} \propto
+    \epsilon_\rmn{th}^{\alpha_{\rmn{tu}}}$. They are normalized such
+      that the total turbulent energy for each scenario makes up 20\%
+      of the total thermal energy inside the radio halo. Solid lines
+      show the median ratio, while the dotted lines show the 68
+      percentiles.}
     \label{fig:Edens}
-  \end{minipage}
-\end{figure}
+\end{figure*}
+
 Indeed, arriving at a seed population with the required
 characteristics is highly constraining, and has the potential to teach
-us much about the origin of CRps/CRes in clusters. \AP{In this paper
-  we consider 3 new scenarios that individually or combined can
-  reproduce the observed radio profiles and spectrum in the Coma
-  cluster without violating gamma-ray constraints:} (i) Our model
-\Mflatturb: a significantly spatially flatter turbulent profile than
-what was adopted in \citep{brunetti12}, which allows seed CRps to
-follow the steep profile that is suggested by structure formation
-simulations. (ii) Our model \Mstream: streaming CRps that produce flat
-distributions of CRs in the ICM
-\citep{ensslin11,wiener13,2014MNRAS.438..124Z}, which also flattens
-the secondary electron distribution. (iii) Our model \Mprimary: if the
-acceleration efficiency of CRps is below about $0.1$~{\%} in weak
-(perpendicular) shocks and the ratio of injected electrons-to-protons
-$K_{\rmn{ep}} \sim 0.1$, this yields a dominant primary population
-with a flat spatial distribution, since primaries have a weaker
+us much about the origin of CRps/CRes in clusters. In this paper we
+consider three new scenarios that individually or combined can
+reproduce the observed radio profiles and spectrum in the Coma cluster
+without violating gamma-ray constraints:
+\begin{enumerate}
+\item {\bf Model {\em M-primaries}.} If the acceleration efficiency of CRps is below
+  about $0.1$~{\%} in weak (perpendicular) shocks and the ratio of injected
+  electrons-to-protons $K_{\rmn{ep}} \sim 0.1$, this yields a dominant primary
+  population with a flat spatial distribution, since primaries have a weaker
   density dependence than secondaries.
+\item {\bf Model {\em M-streaming}.} Here, we account for streaming CRps that
+  produce flat distributions of CRps in the ICM
+  \citep{ensslin11,wiener13,2014MNRAS.438..124Z}, which also flattens the
+  secondary electron distribution.
+\item {\bf Model {\em M-turbulence}.} Here, we adopt a significantly spatially
+  flatter turbulent profile than what was adopted in \citet{brunetti12},
+  but where seed CRps follow the steep profile that is suggested by
+  structure formation simulations.
+\end{enumerate}
 
-\AP{To pursue these three possibilities further, we employ cosmological
+To pursue these three possibilities further, we employ cosmological
 simulations of CRs in clusters. In tandem with new insights from our
@@
 generate the first quantitative calculation of primary and secondary
-  seed electrons and compare to observations.}
-
-\sout{In this work we pursue these three possibilities further. We
-  employ cosmological simulations of CRs in clusters, in tandem with
-  new insights from our recent work on DSA generated fossil electrons
-  %\citep{pinzke13}, to generate the first quantitative calculation of
-  , to generate the first quantitative calculation of
-  primary and secondary seed electrons.}
+seed electrons and compare to observations in the Coma cluster. For
+the most part, we adopt parameters that are used in previous work: for
+turbulence, see \citet[][ including turbulent spectrum, injection
+  scale, energy density of turbulence]{brunetti07,brunetti11},
+for CR acceleration in shocks, see \citet[][ in particular
+  $K_{\rmn{ep}}$, acceleration efficiency]{pinzke13}, and for
+cosmological simulations, see \citet[][ i.e., shock history,
+  temperature profile, density profile, magnetic field
+  profile]{pinzke10}. All these parameters are uncertain, and could
+potentially change our predictions. We leave exploration of parameter
+space and the interaction between free parameters to future work.
 
 % --- section: Method --- %
-{\bf Method.}  The transport of relativistic electrons and protons in
+\section{Method}
+
+The transport of relativistic electrons and protons in
 the ICM is a complex process that depends both on the details of the
@@
 
+\subsection{Acceleration}
+
 In our Galaxy, the CRe-to-CRp ratio at a few GeV is $K_{\rmn{ep}} \sim
 10^{-2}$. Hence, we adopt this as a fiducial value for the CRe-to-CRp
-acceleration efficiency (see \citep{pinzke13} for more
+acceleration efficiency (see \citet{pinzke13} for more
 discussion). However, as recent PIC simulations have shown, this is
@@
 depending on magnetic geometry, $K_{\rmn{ep}}$ could be either larger
-or smaller. \AP{In this work we use a simple test-particle model for
-  the CRp acceleration, where we adopt a fit to Monte Carlo
-  simulations of the thermal leakage process that relates the momentum
-  of injected protons to the thermal energy of the shocked plasma
-  \citep{kang11}. We set an upper limit on the ratio of accelerated
-  proton-to-dissipated energy in the downstream of strong shocks that
-  varies from 1-10\%, depending on the adopted model (for more
-  details, see the Results section). In order not to violate energy
-  conservation with a fixed limit for the acceleration efficiency, we
-  steepen the spectral index of the accelerated CRps at the limit
-  \citep{pinzke13}. For weak shocks the efficiency is a factor 10-100
+or smaller. In this work we use a simple test-particle model for the
+CRp acceleration, where we adopt a fit to Monte Carlo simulations of
+the thermal leakage process that relates the momentum of injected
+protons to the thermal energy of the shocked plasma \citep{kang11}. We
+set an upper limit on the ratio of accelerated proton-to-dissipated
+energy in the downstream of strong shocks that varies from 1-10\%,
+depending on the adopted model (for more details, see Section
+\ref{sec:results}). In order not to violate energy conservation with a
+fixed limit for the acceleration efficiency, we steepen the spectral
+index of the accelerated CRps at the limit \citep{pinzke13}, which
+mimics the non-linear CR modification of the shock
+\citep{ellison00}. For weak shocks the efficiency is a factor 10-100
 lower and well below the limit. Some observations of radio relics
-  suggest high values of $K_{\rmn{ep}}$, due to the absence of
-  gamma-ray emission, which probes the CRp population
+suggest high values of $K_{\rmn{ep}}$, due to the absence of gamma-ray
+emission, which probes the CRp population
 \citep{2014MNRAS.437.2291V}. This suggests primary CRes as a viable
-  alternative scenario to secondary CRes as seeds for the giant
-  RHs. In our {\it M-primaries} scenario, we assume that the momentum
-  of injected electrons and protons are equal, and in addition we
-  adopt a $K_{\rmn{ep}} =0.1$ (viable for primarily perpendicular
-  shocks). While this appears to contradict the radial bias of
-  magnetic fields in the bulk of the ICM as suggested by observations
-  \citep{2010NatPh...6..520P} and cluster simulations
-  \citep{2011ApJ...740...81R}, it does not necessarily apply to the
-  accretion shock regions, which show a field geometry with a net
-  perpendicular bias with respect to the shock normal---at least for
-  giant radio relics \citep{2010Sci...330..347V}. We leave further
-  exploration of parameter space to future work.}
+alternative scenario to secondary CRes as seeds for the giant RHs. In
+our {\em M-primaries} scenario, the injected distribution of CRes is
+derived in the same way as for the CRps. Once they have been
+accelerated to relativistic energies, injected electrons and protons
+are indistinguishable. We therefore assume that CRp and CRe have the
+same distribution function $f_\rmn{CRe}(p) = K_\rmn{ep}
+f_\rmn{CRp}(p)$, with a different normalization (due to differing
+acceleration efficiencies) $K_\rmn{ep}=0.1$ (viable for primarily
+perpendicular shocks; \citet{2014ApJ...794..153G}). While this
+appears to contradict the radial bias of magnetic fields in the bulk
+of the ICM as suggested by observations \citep{2010NatPh...6..520P}
+and cluster simulations \citep{2011ApJ...740...81R}, it does not
+necessarily apply to the accretion shock regions, which show a field
+geometry with a net perpendicular bias with respect to the shock
+normal---at least for giant radio relics \citep{2010Sci...330..347V}.
 
+\subsection{Cosmic ray transport}
 As previously noted, secondaries produced by shock accelerated CRp
@@
 stream out when the cluster is kinematically quiescent. Furthermore,
-even Alfv{\'e}nic streaming timescales are relatively short ($\sim
-0.1-0.5$ Gyr; \cite{wiener13}) compared to the timescale on which the
-CRp population is built up. Based on these findings, we adopt a toy
-model for our \Mstream scenario in which CR streaming quickly produces
-flat CRp profiles. We assume that CRs cannot
-stream significantly past perpendicular $B$-fields at the accretion
-shock, so that the total number of CRs is conserved. \AP{Note that the seed CRps that are
-  Fermi-II reaccelerated, and produce secondary electrons that emit
-  radio emission with frequencies $\gtrsim 350$~MHz, have relatively
-  high energies $\gtrsim 10$~GeV and stream more efficiently than low
-  energy CRs \citep{wiener13}.}
+even Alfv{\'e}nic streaming timescales are relatively short
+\cite[$\sim 0.1-0.5$ Gyr;][]{wiener13} compared to the timescale on
+which the CRp population is built up. Based on these findings, we
+adopt a toy model for our \Mstream scenario in which CR streaming
+quickly produces flat CRp profiles. We assume that CRs cannot stream
+significantly past perpendicular $B$-fields at the accretion shock, so
+that the total number of CRs is conserved within the galaxy cluster
+during the streaming process.
 
@@
 plasma physics assumptions as the reacceleration model for RHs
-\citep{brunetti07,brunetti11}, leaving exploration of parameter space
-to future work. We solve the isotropic, gyro-phase averaged
-Fokker-Planck equation (via a Crank-Nicholson scheme) for the time
-evolution of the CRe distribution in the Lagrangian frame
+\citep{brunetti07,brunetti11}. We solve the isotropic, gyro-phase
+averaged Fokker-Planck equation (via a Crank-Nicholson scheme) for the
+time evolution of the CRe distribution in the Lagrangian frame
 \citep{brunetti07,brunetti11}:
@@
 injects large turbulent eddies. After about 1~Gyr those have decayed
-down to the scale needed to reaccelerate particles \AP{and the radio
-  halo turns on shortly after. This naturally explains why giant radio
-  halos are only seen in a fraction of all merging clusters.} In all
-our calculations we assume that turbulent reacceleration is
-efficiently accelerating particles for 650 Myrs and that during this
-turbulent phase CR streaming and spatial diffusion can be
-neglected. In our \Mstream model, CR streaming and diffusion are
-incorporated separately during kinematically quiescent times that
-precede the merger. As a result, flat CRp profiles are produced on
-relatively short timescales ($\sim 0.1-0.5$ Gyr).
+down to the scale needed to reaccelerate particles and the radio halo
+turns on shortly after. This delay naturally explains why giant radio
+halos are only seen in a fraction of all merging clusters. In all our
+calculations we assume that turbulent reacceleration efficiently
+accelerates particles for 650 Myrs (which is roughly the cascade time
+on which turbulence is damped) and that during this turbulent phase CR
+streaming and spatial diffusion can be neglected. In our \Mstream
+model, CR streaming and diffusion are incorporated separately during
+kinematically quiescent times that precede the merger. As a result,
+flat CRp profiles are produced on relatively short timescales ($\sim
+0.1-0.5$ Gyr).
 
@@
 \begin{eqnarray}
-{{d f_{\rmn{p}}(p,t)}\over{d t}} &=
+{{d f_{\rmn{p}}(p,t)}\over{d t}} &=&
 {{\partial }\over{\partial p}}
@@
 \nonumber\\
-&-\left.\left. {1\over{p^2}}{{\partial }\over{\partial p}}\left(p^2 D_{pp}\right)
+&-&\left.\left. {1\over{p^2}}{{\partial }\over{\partial p}}\left(p^2 D_{pp}\right)
 \right]\right\} - \left(\vec{\nabla}\cdot \vec{\upsilon}\right) f_{\rmn{p}}(p,t)
 \nonumber\\
-&+ {{\partial^2 }\over{\partial p^2}}
+&+& {{\partial^2 }\over{\partial p^2}}
 \left[ D_{pp} f_{\rmn{p}}(p,t) \right] - {{f_{\rmn{p}}(p,t)}\over{\tau_{\rm had}(p)}}
@@
 pions via CRp collisions with thermal protons of the ICM
-\cite[e.g.][]{brunetti11}.  We incorporate momentum diffusion for
-electrons and protons from transit-time-damping (TTD) resonance with
-compressible magneto-hydrodynamic (MHD) turbulence, to model Fermi-II
+\cite[e.g.][]{brunetti11}.
+
+\subsection{Turbulent reacceleration}
+
+We incorporate momentum diffusion for electrons and protons from
+transit-time-damping (TTD) resonance with compressible
+magneto-hydrodynamic (MHD) turbulence, to model Fermi-II
 reacceleration \citep{brunetti07,brunetti11}. The TTD resonance
@@
 confining wave region matches the wave period,
-$\lambda_{\parallel}/v_{\parallel}=T$. The resonance changes the
-component of particle momentum parallel to seed magnetic fields, which
-over time leads to increasing anisotropy in the particle distribution
-that decreases the efficiency of reacceleration with time. As in
-ref.{\ }\cite{brunetti11}, we assume that there exists a
-mechanism---such as the firehose instability---that isotropizes the CR
-distribution function at the gyroscale and on the reacceleration time
-scale, which ensures sustained efficient reacceleration with time. The
-particle pitch-angle averaged momentum-diffusion coefficient of
-isotropic particles that couple to fast magnetosonic modes via TTD
-resonance is \cite{brunetti07} (Eqn. 47):
+$\lambda_{\parallel}/v_{\parallel}=T$. Note, the CRs' gyroradius does
+not enter the resonance condition. Hence the CRs that are in resonance
+with compressible waves experience Fermi-II acceleration
+irrespectively of the length scale of the perturbation.
+
+However, the resonance changes the component of particle momentum
+parallel to seed magnetic fields, which over time leads to increasing
+anisotropy in the particle distribution that decreases the efficiency
+of reacceleration with time. As in \citet{brunetti11}, we assume that
+there exists a mechanism---such as the firehose instability---that
+isotropizes the CR distribution function at the gyroscale and on the
+reacceleration time scale, which ensures sustained efficient
+reacceleration with time. The particle pitch-angle averaged
+momentum-diffusion coefficient of isotropic particles that couple to
+fast magnetosonic modes via TTD resonance is \cite{brunetti07}
+(Eqn. 47):
 \begin{eqnarray}
@@
 beta-weighted magnetic-to-total energy density saturates to $\langle\beta
-|B_k|^2/2W\rangle\approx 10^{1.4}$ (see figure 2 in
-\cite{brunetti07}). The pitch angle of the CR momentum with the
+|B_k|^2/2W\rangle\approx 10^{1.4}$ (see Figure 2 in
+\citealt{brunetti07}). The pitch angle of the CR momentum with the
 magnetic field orientation is given by $\theta$, and
-$I_\theta=\int_0^{\arccos(\Vph/c)} d\theta {\frac{ \sin^3 \theta }{
+\begin{equation}
+  \label{eq:I_theta}
+  I_\theta=\int_0^{\arccos(\Vph/c)} d\theta {\frac{ \sin^3 \theta }{
     |\cos \theta | }}
-\left[1+\left(\frac{\Vph}{c\,\cos{\theta}}\right)^2\right]^2$. Here
-$V_\rmn{ph}$ is the phase velocity of the fast magnetosonic waves
-given approximately by the sound speed, $\Vph \sim c_\rmn{s}$. For a sound
-speed typical for the ICM of 1000~km/s, $I_\theta\approx5$. As in
-\cite{brunetti07}, we initially assume that the velocity of turbulent
-eddies is $V_0\approx 0.47 c_\rmn{s}$ throughout the cluster. This gives a
-turbulent acceleration time scale, $\tau_{pp} = p^2/4D_{pp}$, that is
-typically few 100 Myrs in the ICM.
+\left[1+\left(\frac{\Vph}{c\,\cos{\theta}}\right)^2\right]^2.
+\end{equation}
+Here $V_\rmn{ph}$ is the phase velocity of the fast magnetosonic waves given
+approximately by the sound speed, $\Vph \sim c_\rmn{s}$. For a sound speed
+typical for the ICM of 1000~km/s, $I_\theta\approx5$. As in \cite{brunetti07},
+we initially assume that the velocity of turbulent eddies is $V_0\approx 0.47
+c_\rmn{s}$ throughout the cluster. This gives a turbulent acceleration time
+scale, $\tau_{pp} = p^2/4D_{pp}$, that is typically few 100 Myrs in the ICM.
 
-We adopt a simplified isotropic Kraichnan MHD turbulent spectrum for
-the fast modes per elemental range $dk$ of the form $\mathcal{W}(k) =
-\sqrt{2/7\,I_0\,\rho\,\langle \Vph \rangle}\,k^{-3/2}\,,$ for
-$k_0<k<k_\rmn{cut}$, where we assume an injection scale for the
+We adopt a simplified isotropic MHD turbulent spectrum for the fast
+modes per elemental range $dk$ of the form
+\begin{equation}
+  \label{eq:Wk}
+  \mathcal{W}(k) =
+\sqrt{2/7\,I_0\,\rho\,\langle \Vph \rangle}\,k^{-3/2},
+\end{equation}
+for $k_0<k<k_\rmn{cut}$, where we assume an injection scale for the
 turbulence, $k_0= 2\pi/(100~\mbox{kpc})$. The volumetric injection
 rate of turbulent energy, $I_0$, is fixed by requiring that the total
-turbulent energy density on the largest scales
-$\epsilon_\rmn{turb}=\int \mathcal{W}(k) dk \approx 0.2
-\epsilon_\rmn{th}$, where $\epsilon_\rmn{th}$ is the thermal energy
-density \citep{brunetti07,brunetti11}. In this work we investigate
-different spatial models for injected turbulence. We assume that
-$\epsilon_\rmn{turb} \propto \epsilon_\rmn{th}^{\alpha_\rmn{tu}}$,
-where $\alpha_\rmn{tu}= 0.66$ for \Mflatturb, $\alpha_\rmn{tu}= 0.81$
-for \Mstream, and $\alpha_\rmn{tu}= 0.88$ for \Mprimary (note that in
-previous work \AP{on the Coma cluster, $\alpha_\rmn{tu}= 1$ was
-  adopted \citep{brunetti12}, which together with the different
-  distributions for CRs constitute the main differences compared to
-  our work}). Our flatter turbulent profiles are motivated by fits to
-cosmological simulations
+turbulent energy on the largest scales $E_\rmn{turb}=\int \int
+\mathcal{W}(k) \rmn{d}k \rmn{d}V \approx 0.2 E_\rmn{th}$, where
+$E_\rmn{th}$ is the total thermal energy \citep{brunetti07,brunetti11}
+within the radio halo. In this work we investigate different spatial
+models for injected turbulence. We assume that turbulent energy
+density $\epsilon_\rmn{turb} \propto
+\epsilon_\rmn{th}^{\alpha_\rmn{tu}}$, where $\alpha_\rmn{tu}= 0.66$
+for \Mflatturb, $\alpha_\rmn{tu}= 0.81$ for \Mstream, and
+$\alpha_\rmn{tu}= 0.88$ for \Mprimary (note that in previous work on
+the Coma cluster, $\alpha_\rmn{tu}= 1$ was adopted \citep{brunetti12},
+which together with the different distributions for seed CRes
+constitute the main differences compared to our work). Our flatter
+turbulent profiles are motivated by fits to cosmological simulations
 \citep{2009ApJ...705.1129L,2010ApJ...725.1452S,2012ApJ...758...74B}
@@
 suppressed when thermal and relativistic particles resonantly interact
-with magnetosonic waves via TTD on a timescale $\Gamma^{-1}$ that is
-approaching the cascading timescale given by $\tau_{kk} \approx
+with magnetosonic waves via TTD on a timescale $\Gamma^{-1}$ that
+approaches the cascading timescale given by $\tau_{kk} \approx
 k^2/D_{kk}$. Here the wave-wave diffusion coefficient of magnetosonic
-modes is given by $D_{kk} \approx \Vph k^4
-\left(\frac{\mathcal{W}(k)}{\rho\,\Vph^2}\right)\,.$ Thus, the cascade
-is suppressed for wave numbers above:
+modes is given by
+\begin{equation}
+\label{eq:Dkk}
+D_{kk} \approx \Vph k^4
+\left(\frac{\mathcal{W}(k)}{\rho\,\Vph^2}\right).
+\end{equation}
+Thus, the cascade is suppressed for wave numbers above
 \begin{equation}
@@
   k_\rmn{cut} \approx \frac{81}{14} \frac{I_0}{\rho \langle \Vph \rangle}
-  \left(\frac{\langle\sum_i \Gamma_i(k,\theta)\rangle}{k}\right)^{-2}\,.
+  \left(\frac{\langle\sum_i \Gamma_i(k,\theta)\rangle}{k}\right)^{-2}\,,
 \end{equation}
@@
 mediate interactions between turbulence and particles on smaller
-scales \citep{brunetti11}. In this work we only consider damping via
-TTD due to thermal electrons, and neglect subdominant damping with
-thermal protons and relativistic particles. The latter will be
-subdominant in the ICM for a CR-to-thermal energy density ratio
-$\lesssim 10 \%$ \citep{brunetti07}, which is always satisfied \AP{in our models}. The
+scales \citep{brunetti11}. In this work we only consider damping of
+the turbulence via TTD due to thermal electrons, and neglect
+subdominant damping with thermal protons and relativistic particles
+(conversely, the turbulence has important effects on the
+reacceleration of CRs). The latter will be subdominant in the ICM for
+a CR-to-thermal energy density ratio $\lesssim 10 \%$
+\citep{brunetti07}, which is always satisfied in our models. The
 azimuthally averaged turbulent damping rate from thermal electrons
-\citep{brunetti07} in a high-$\beta$ plasma is $
+\citep{brunetti07} in a high-$\beta$ plasma is
+\begin{equation}
+\label{eq:Gamma_e}
 \langle\Gamma_{\rmn{e}}\rangle \approx \langle k\,\Vph\,\sqrt{3\pi
-  x/20}\exp(-5x/3)\sin^2{\theta}\rangle\approx 0.0435k\,\Vph$, where
-$x=(m_{\rmn{e}}/m_{\rmn{p}})/\cos^2{\theta}$. To compute the
+  x/20}\exp(-5x/3)\sin^2{\theta}\rangle\approx 0.0435k\,\Vph, 
+\end{equation}
+where $x=(m_{\rmn{e}}/m_{\rmn{p}})/\cos^2{\theta}$. To compute the
 synchrotron surface brightness profiles, we use the profile of the
-$\sim\mug$ magnetic field strength derived from Faraday rotation
-observations of Coma \citep{bonafede10} in combination with the density
-profile derived from X-ray measurements \citep{1992A&A...259L..31B}.
-
-\sout{We quantify the conditions under which a primary or secondary
-  origin for the seed electrons dominates, and elucidate an
-  observational discriminant. One possibility is to use high-frequency
-  radio observations (with the Jansky VLA and Sardina radio
-  telescopes) when turbulent reacceleration (which has a high energy
-  cutoff) is no longer efficient. A stacked radio spectrum may reveal
-  the glow of radio emission due to steady state secondary
-  population. Due to the much more intermittent nature of DSA
-  injection, primary CRe will instead a sharp cutoff at high energies
-  due to cooling, and will not be visible at high frequencies.}
+magnetic field strengths derived from Faraday rotation observations of
+Coma \citep{bonafede10} in combination with the density profile
+derived from X-ray measurements \citep{1992A&A...259L..31B}.
 
 % --- section: Results and discussion --- %
-{\bf Results and Discussion.} After turbulent reacceleration, the
-volume-weighted, relative CRp energy density and CRp number density
-inside the RH for \Mflatturb (\Mstream), are found to be 3 (2) \% and
-$3.0\times10^{-8}$ ($4.5\times10^{-8}$), respectively. As we will see
-later, these densities are just of the right order of magnitude to
-reproduce radio observations in the Coma cluster. \AP{In addition we
-  predict the gamma-ray flux within the virial radius of the Coma
-  cluster from CRps that produce decaying neutral pions for \Mflatturb
-  (\Mstream) with $F_\gamma(>500\,\rmn{MeV})=4.8\times10^{-10}
-  (2.3\times10^{-10}) \mathrm{ \,ph\, s}^{-1}\mathrm{cm}^{-2}$. We
-  predict fluxes from these models that are slightly larger than in
-  \cite{brunetti12}, where the differences comes from our steeper CRp
-  profiles in addition to simulation based formalism we rely on that
-  accounts for both Coulomb and hadronic losses during the build up of
-  the CR distribution in contrast to the scaling relations adopted in
-  their paper. Interestingly the gamma-ray flux from both our
-  scenarios are just below recent Fermi-LAT limits derived from a
-  gamma-ray profile similar to \Mflatturb where
+
+\section{Results and Discussion} 
+\label{sec:results}
+
+After turbulent reacceleration, the volume-weighted, relative CRp
+energy density and CRp number density inside the RH for \Mflatturb
+(\Mstream), are found to be 3 (2) \% and $3.0\times10^{-8}$
+($4.5\times10^{-8}$), respectively. As we will see later, these
+densities are just of the right order of magnitude to reproduce radio
+observations in the Coma cluster. The gamma-ray emission from CRps
+that produce decaying neutral pions could be substantial if the CRps
+are reaccelerated efficiently enough, hence it is interesting to
+estimate this emission for our models and compare to upper limits. We
+predict the gamma-ray emission from \Mflatturb (\Mstream) with
+$F_\gamma(>500\,\rmn{MeV})=4.8\times10^{-10} (2.3\times10^{-10})
+\mathrm{ \,ph\, s}^{-1}\mathrm{cm}^{-2}$. The fluxes from these
+models are slightly larger than in \cite{brunetti12}, where the
+differences comes from our steeper CRp profiles in addition to
+simulation based formalism we rely on that accounts for both Coulomb
+and hadronic losses during the build up of the CR distribution in
+contrast to the scaling relations adopted in their
+paper. Interestingly the gamma-ray flux from both our scenarios are
+just below recent Fermi-LAT limits derived from a gamma-ray profile
+similar to \Mflatturb where
 $F_\gamma(>500\,\rmn{MeV})<5.3\times10^{-10} \mathrm{ \,ph\,
@@
   communication. See also
-    \citep{2014MNRAS.440..663Z,2014ApJ...787...18A}.} and will be
-  probed in the next few years by Fermi-LAT. } The spectral index of
-the CRp distribution is relatively steep $\alpha_{\rmn{p}}\sim2.6$ for
-the CRp energies $E \gtrsim 10$~GeV that are relevant for the
-injection of radio-emitting secondary CRes.  The steep spectrum is
-ultimately a consequence of our test particle model for Fermi-I
-acceleration \citep{pinzke13}, where we steepen the spectral index to
-avoid acceleration efficiencies above $\zeta_{\rmn{p}} \sim 10\%$.
+  \citet{2014MNRAS.440..663Z,2014ApJ...787...18A}. and will be probed
+  in the next few years by Fermi-LAT. } The spectral index of the CRp
+distribution is relatively steep ($\alpha_{\rmn{p}}\sim2.6$) for the
+CRp energies $E \gtrsim 10$~GeV that are relevant for the injection of
+radio-emitting secondary CRes. The steep spectrum is ultimately a
+consequence of our test particle model for Fermi-I acceleration
+\citep{pinzke13}, where we steepen the spectral index to avoid
+acceleration efficiencies above $\zeta_{\rmn{p}} \sim 10\%$.
 
@@
 complete freedom in the seed population was allowed -- it is not
-possible to reproduce observations in both frequencies. \AP{This
+possible to reproduce observations in both frequencies in any
+model. Note that decreasing acceleration efficiency with radius does
+not change this conclusion much because of the weak radial dependence
+of $D_\rmn{pp}(R)\propto
+\epsilon_\rmn{th}(R)^{(\alpha_\rmn{tu}+1)/2}/\sqrt{T(R)}$. This
 signals that the problem is generic and requires either additional
@@
 there are differences in the simulated density and temperature
-  profiles in comparison to the observed profile in Coma that impact
-  the CR abundance as well as cooling and reacceleration.}
+profiles in comparison to the observed profile in Coma that impact the
+CR abundance as well as cooling and reacceleration.
 
@@
 B/\mu\rmn{G} (\gamma/10^4)^2\,\rmn{GHz}$, this translates into a
-spectral steepening of the total radio spectrum (see
+spectral steepening of the radio spectrum (see
 Fig.~\ref{fig:sync_spectrum}). A given radio window samples higher
@@
 and simulated 1.4 GHz profiles could instead be due to systematic flux
-calibration error in single dish observations. Interestingly, we can
-match the 1.4 GHz data if we reduce the zero point by adding 10\% of
-the central flux to every data point; this flattens the outer
-profile \footnote{Lawrence Rudnick, private communication.}.  \AP{Note
-  that decreasing acceleration efficiency with radius does not change
-  this conclusion much because of the weak radial dependence of
-  $D_\rmn{pp}(R)\propto \epsilon_\rmn{th}(R)^{(\alpha_\rmn{tu}+1)/2}/\sqrt{T(R)}$.}
+calibration error in single dish observations. These could arise, for
+instance, due to errors in point source subtraction. Interestingly, we
+can match the 1.4 GHz data if we reduce the zero point by adding 10\%
+of the central flux to every data point; this flattens the outer
+profile \footnote{Lawrence Rudnick, private communication.}.
 Alternatively, this may point to weaknesses in the theoretical
@@
 \begin{minipage}{1\columnwidth}
-  \begin{center}\LARGE{\Mflatturb:}\\ 
-    \includegraphics[width=\columnwidth]{figures/sbright.nu.DIIcomp.I0.g72a.Rad14.2400p.z0.NL.xKR.eb23.eI066.140.v5.halo.test5.eps}
+   \begin{center}\Large{\Mprimary:}\\
+     \includegraphics[width=\columnwidth]{figures/sbright.nu.DIIcomp.Pri.g72a.Rad14.2400p.z0.NL.xKR.eb23.eI088.140.v5.halo.test5.eps}
    \end{center}
@@
 \begin{minipage}{1\columnwidth}
-   \begin{center}\LARGE{\Mstream:}\\
+   \begin{center}\Large{\Mstream:}\\
      \includegraphics[width=\columnwidth]{figures/sbright.nu.DIIcomp.flatCR.g72a.Rad14.2400p.z0.NL.xKR.eb23.eI081.flatCR.140.v5.halo.test5.eps}
@@
 \begin{minipage}{1\columnwidth}
-   \begin{center}\LARGE{\Mprimary:}\\
-     \includegraphics[width=\columnwidth]{figures/sbright.nu.DIIcomp.Pri.g72a.Rad14.2400p.z0.NL.xKR.eb23.eI088.140.v5.halo.test5.eps}
+  \begin{center}\Large{\Mflatturb:}\\ 
+    \includegraphics[width=\columnwidth]{figures/sbright.nu.DIIcomp.I0.g72a.Rad14.2400p.z0.NL.xKR.eb23.eI066.140.v5.halo.test5.eps}
   \end{center}
@@
 \begin{minipage}{1\columnwidth}
-   \begin{center}\LARGE{\it Brunetti et al. (2012)}:\\
+   \begin{center}\Large{\it Brunetti et al. (2012)}:\\
      \includegraphics[width=\columnwidth]{figures/sbright.nu.DIIcomp.Brunetti.g72a.Rad14.2400p.z0.NL.xKR.eb23.140.v5.halo.test5.eps}
@@
 \caption{Radio surface brightness profiles of Fermi-II reaccelerated
-    CR electrons of a simulated post-merging cluster similar to
-    Coma. We compare profiles at 352~MHz (blue lines and crosses
-    \citet{brown11}) to those at 1.4~GHz (green lines and crosses
-    \citet{deiss97}). The red crosses show the reprocessed 1.4~GHz
-    data, where a zero level of about 10 \% of the central value is
-    adopted. The solid lines show predicted emission from a
-    reaccelerated fossil population, while dotted lines show emission
-    from a fossil population without reacceleration. The panels show
-    the emission of our models \Mflatturb (upper left panel), \Mstream
-    (upper right panel), \Mprimary (lower left panel), and simulated
-    secondary electrons together with previous estimates
-    \citet{brunetti12} for the Coma cluster (lower right panel).}
+  CR electrons of a simulated post-merging cluster similar to Coma. We
+  compare profiles at 352~MHz (blue lines and crosses \citet{brown11})
+  to those at 1.4~GHz (green lines and crosses \citet{deiss97}). The
+  red crosses show the reprocessed 1.4~GHz data, where a zero level of
+  about 10~\% of the central value is adopted. The solid lines show
+  predicted emission from a reaccelerated fossil population, while
+  dotted lines show emission from a fossil population without
+  reacceleration. The panels show the emission of our models \Mprimary
+  (upper left panel), \Mstream (upper right panel), \Mflatturb (lower
+  left panel), and simulated secondary electrons together with
+  previous estimates \citet{brunetti12} for the Coma cluster (lower
+  right panel).}
   \label{fig:sync_profile}
@@
 convexly curved total radio spectrum found in the Coma cluster. Seed
-CRs that do not experience turbulent reacceleration have a power-law
-spectrum in disagreement with observations. In order to match both the
-spatial and spectral profiles in Coma, we can constrain the
-acceleration efficiency for the strongest shocks in our three models
-\Mstream, \Mflatturb, and \Mprimary to $\zeta_{\rmn{p}} < 0.15$,
-$\zeta_{\rmn{p}}<0.05$, and $\zeta_{\rmn{e}} <0.004$,
-respectively. Following the Mach number ($\mathcal{M}$)-dependence of
-the acceleration efficiency suggested in \cite{pinzke13}, the
-efficiency in weak shocks ($\mathcal{M}\sim 2.5-3.5$) that dominates
-the CR distribution function, has an acceleration efficiency for
-protons $\zeta_{\rmn{p}}\sim0.0001-0.01$, and for electrons
-$\zeta_{\rmn{e}}\sim 0.001$.
+CRs in \Mstream and \Mflatturb that do not experience turbulent
+reacceleration have a power-law spectrum in disagreement with
+observations. In order to match both the spatial and spectral profiles
+in Coma, we adopt an acceleration efficiency for the strongest shocks
+in our three models \Mprimary, \Mstream, and \Mflatturb to
+$\zeta_{\rmn{e}} <0.002$, $\zeta_{\rmn{p}} < 0.1$, and
+$\zeta_{\rmn{p}}<0.025$, respectively. Following the Mach number
+($\mathcal{M}$)-dependence of the acceleration efficiency suggested in
+\cite{pinzke13}, the efficiency in weak shocks ($\mathcal{M}\sim
+2.5-3.5$) that dominates the CR distribution function, has an
+acceleration efficiency for protons $\zeta_{\rmn{p}}\sim0.0001-0.01$,
+and for electrons $\zeta_{\rmn{e}}\sim 0.001$. Interestingly, we find
+that the radio luminosity from clusters in the OFF-state (DSA only)
+and ON-state (DSA and reacceleration) differ by about a factor 10 in
+all our three models. However, note that for \Mprimary, the primary
+CRes that generate most of the radio emission from the cluster in the
+OFF-state are dominated by only a small fraction of the CRes. These
+electrons are injected very recently and have not had time to cool
+yet. Hence we expect there to be a large variance in the OFF-state of
+different simulated clusters.
 
-\begin{figure}
-  \includegraphics[width=0.99\columnwidth]{figures/sync.spec.g72a.140.v5.halo.test5.eps}
-  \caption{Radio synchrotron spectra. Red lines are derived from
+While the radio surface brightness has an approximate linear
+dependence on the acceleration efficiency, it has a strong non-linear
+dependence on the level of turbulence. Below a critical level ($X =
+E_\rmn{turb}/E_\rmn{th} \sim 0.15$ in our fiducial model), turbulent
+reacceleration is negligible, while it rises sharply above this
+threshold. For instance, for $X>0.15$, a factor 2 change in $X$
+changes the radio surface brightness by $\sim 10-100$. In principle
+this threshold behavior allows us to provide a strict lower bound on
+turbulence in radio halos. An even more stringent bound on $X$ can be
+inferred from combining radio observations with the gamma-ray
+observations where the predicted fluxes from both \Mstream and
+\Mflatturb are close to the upper limits set by Fermi-LAT. If $X$ is
+smaller than in our adopted models (where we assume $X=0.2$), then the
+efficiency of DSA has to be larger than $\zeta_\rmn{p}\sim 0.1$ for
+the secondary CRes to reproduce the radio observations. However, since
+the turbulent reacceleration acts on both the secondary CRes and the
+CRps, while $\zeta_\rmn{p}$ only affects the CRps, these models would
+produce too much gamma-rays. Hence we conclude that $X\gtrsim0.2$ if
+all other parameters are kept fixed. We will explore this parameter
+space further in future work.
+
+\begin{figure*}
+  \includegraphics[width=1.0\columnwidth]{figures/sync.spec.pri.g72a.140.v5.halo.test5.eps}
+  \includegraphics[width=1.0\columnwidth]{figures/sync.spec.sec.g72a.140.v5.halo.test5.eps}
+  \caption{Radio synchrotron spectra. Lines are derived from
     simulations, while the black crosses are compiled from
-    observations \citet{2010PhDT.......259P}. The lines show the
-    emission of our models \Mstream (solid line), \Mflatturb (dashed
-    line), and \Mprimary (dash-dotted line). We contrast the
-    reaccelerated populations to a population of DSA accelerated CR
-    protons that produce secondaries (dotted line).}
+    observations \citet{2010PhDT.......259P}. The solid lines show the
+    DSA and reaccelerated CRs (On-state of the radio halo), while the
+    dotted lines show CRs accelerated only by DSA (Off-state of the
+    radio halo). The left figure shows the radio emission induced by
+    primary CRes and the right figure shows the emission from
+    secondary CRes. The different line colors represent our different
+    models, \Mprimary (red line), \Mstream (blue line), and \Mflatturb
+    (green line).}
   \label{fig:sync_spectrum}
-\end{figure}
+\end{figure*}
 
 % --- section: Conclusions --- %
-{\bf Conclusions.}  The standard reacceleration model for RHs requires
+\section{Conclusions}
+\label{sec:conclusions}
+
+The standard reacceleration model for radio halos (RHs) requires
 a population of seed electrons to undergo turbulent
 reacceleration. These seeds are generally thought to be secondary
-electrons from hadronic CRp interactions. In this work we use
-cosmological simulations to derive a population of seed CRps
-originating from structure formation shocks and merger shocks during
-the cluster build up. The resulting secondary population is
-inconsistent with RH observations. \AP{We propose 3 possible solutions
-  that all produce gamma-ray emission below current upper limits and
-  that reproduce both, the spectrum and the surface brightness
-  profiles of the Coma radio halo: (i) CRps that stream out of the
-  central core and produce flat CR profiles. (ii) Alternatively, if
-  indeed the acceleration efficiency of CRps is below about $0.1$ {\%}
-  in weak shocks and the ratio of injected electrons and protons
-  $K_{ep} \sim 10^{-1}$, CR electrons accelerated directly in shocks
-  dominate over secondaries.  This seed population of CRes also has
-  the correct spatial and spectral features alone, or potentially
-  complements secondaries to explain radio observations. (iii)
-  Finally, injected turbulence that is flatter than in previously
-  adopted models, which allows seed CRps to follow the steep profile
-  that is suggested by structure formation. We will pursue further
-  implications and distinguishing characteristics of these competing
-  models in future work.} \sout{We propose 3 possible solutions that
-  all produce gamma-ray emission below current upper limits and that
-  reproduce both the spectrum and the surface brightness profiles of
-  the Coma RH: (i) injected turbulence that is flatter than in
-  previously adopted models, (ii) streaming CRs, (iii) shock
-  accelerated CR electrons injected with $K_{\rmn{ep}} \sim 0.1$. We
-  will pursue further implications and distinguishing characteristics
-  of these competing models in future work.}
+electrons from hadronic cosmic ray proton (CRp) interactions. In
+this work we use cosmological simulations to derive a population of
+seed CR protons originating from structure formation shocks and merger
+shocks during the cluster build up. The resulting secondary population
+is inconsistent with RH observations. We propose three possible
+solutions that all produce gamma-ray emission below current upper
+limits and that reproduce both, the spectrum and the surface
+brightness profiles of the Coma radio halo:
+
+\begin{enumerate}
+\item {\bf Model {\em M-primaries}.} If indeed the acceleration
+  efficiency of CRps is below about $0.1$ {\%} in weak shocks and the
+  ratio of injected electrons and protons is $K_{\rmn{ep}} \sim
+  10^{-1}$, CR electrons accelerated directly in shocks dominate over
+  secondaries.
+\item {\bf Model {\em M-streaming}.} Alternatively, CRps could stream
+  out of the central core and produce flat CR profiles. This seed
+  population of secondary CRes also has the correct spatial and
+  spectral features alone, or potentially complements primaries to
+  explain radio observations.
+\item {\bf Model {\em M-turbulence}.}  Finally, injected turbulence
+  that is flatter than in previously adopted models, which allows seed
+  CRps to follow the steep radial profile that is suggested by
+  structure formation simulations.
+\end{enumerate}
+
+Combining radio observations with gamma-ray constraints can be very
+useful to learn about the plasma of the intracluster medium. Our
+models (ii) and (iii) relies on CRps to induce secondary CRes that
+produce the observed radio emission. In addition proton-proton
+collisions produce neutral pions that decay into gamma rays. Since
+turbulent reacceleration acts on both CRes and CRps, while the DSA
+acceleration efficiency ($\zeta_p$) only acts on the CRps, radio
+observations fix the relation between $X$ (the ratio of the total
+turbulent energy to the thermal energy) and the acceleration
+efficiency. With the addition of gamma-ray constraints from Fermi-LAT,
+we can derive a lower limit to $X\gtrsim0.2$ and a upper limit to the
+acceleration efficiencies of $\zeta_p\lesssim 10\%$ ($\zeta_p\lesssim
+2.5\%$) for the two models, respectively, for our current choices of
+other parameters.
+
+How could we distinguish the different possibilities of a dominating
+primary or secondary seed population of electrons observationally?
+One possibility that is relative insensitive to adopted parameters in
+our models is to use high-frequency radio observations (with e.g., the
+Jansky Very Large Array) where turbulent reacceleration (which has a
+high energy cutoff) is no longer efficient (see
+Fig.~\ref{fig:sync_spectrum}). The negative flux bowl of the
+Sunyaev-Zel'dovich effect introduces a cutoff of the RH spectrum at
+frequencies above $\gtrsim 10$~GHz \citep[][ depending on cluster mass
+  and redshift]{2002A&A...396L..17E,Pfrommer:2003mk}. Hence the
+subdominant hadronic radio emission may only be detectable in steep
+spectrum radio sources \citep{2008Natur.455..944B}, which exhibit a
+cutoff at lower radio frequencies and are thought to represent dying
+RHs as a result of the decaying turbulence after a
+merger. Alternatively, one could attempt to reconstruct the intrinsic
+high-frequency RH spectrum by filling in the missing flux due to the
+Sunyaev-Zel'dovich effect by precise measurements of the Compton-$y$
+parameter at microwave frequencies. Another possibility would consist
+in stacking the radio data of radio-quiet clusters that due not
+exhibit RH emission \citep{2011ApJ...740L..28B}. This may reveal the
+glow of radio emission due to steady state secondary
+population. Emission from faint secondary electrons should still be
+visible, whereas due to the much more intermittent nature of DSA
+injection, primary CRe will instead show a sharp cutoff due to
+cooling, and will not be visible at high energies (see
+Fig.~\ref{fig:sync_spectrum}). We will pursue further implications and
+distinguishing characteristics of these competing models in future
+work.
 
@@
 Zandanel for recalculating gamma-ray limits and Gianfranco Brunetti
-for providing the radio profiles for his model. A.P. is
-grateful to the Swedish research council for financial
-support. S.P.O. thanks NASA grant NNX12AG73G for
+for useful discussions. A.P. is grateful to the Swedish research
+council for financial support. S.P.O. thanks NASA grant NNX12AG73G for
 support. C.P.~gratefully acknowledges financial support of the Klaus

### 2016-03-24 paper.tex
test
Added files via upload

@@
 \newcommand{\mug}{\mu G}
+\newcommand{\RH}{R_\rmn{RH}}
 
 %\voffset.6in
+
+\definecolor{mygreen}{rgb}{0.,0.5,0.}
+\def\del#1{{}}
+%\def\del#1{{\bf (DELETED TEXT)}}
+\def\C#1{{\bf #1}}
+\def\AP#1{{\bf  AP: #1}}
+\def\APP#1{{\bf {\color{red} AP2: #1}}}
+\def\SPO#1{{\bf {\color{blue} SPO: #1}}}
+\def\CP#1{{\bf {\color{mygreen} CP: #1}}}
 
@@
 
-The alternative model for RHs is re-energization of seed
-suprathermal electrons by Fermi II acceleration when ICM turbulence
-becomes transonic during mergers
+The alternative model for RHs is re-energization of seed suprathermal
+electrons by Fermi II acceleration when ICM turbulence becomes
+transonic during mergers
 \citep{1987A&A...182...21S,1993ApJ...406..399G,2001MNRAS.320..365B,
-  2004MNRAS.350.1174B,brunetti07,brunetti11}. Due to the short
-radiative cooling time of high-energy relativistic electrons, the
-cluster synchrotron emission quickly fades away after a merger, which
-naturally explains the observed bimodality of RHs \cite[see
-  e.g.][]{2013MNRAS.429.3564D,2014MNRAS.443.3564D}.
+  2004MNRAS.350.1174B,brunetti07,brunetti11,2015ApJ...800...60M}. Due
+to the short radiative cooling time of high-energy relativistic
+electrons, the cluster synchrotron emission quickly fades away after a
+merger, which naturally explains the observed bimodality of RHs
+\cite[see e.g.][]{2013MNRAS.429.3564D,2014MNRAS.443.3564D}.
 
@@
 thermal plasma whose energy density declines steeply with radius. In
-Fig.~\ref{fig:Edens} we show that such a distribution is not predicted by
-cosmological simulations \cite[see
+\AP{the left panel of} Fig.~\ref{fig:Edens} we show that such a
+distribution is not predicted by cosmological simulations \cite[see
   also][]{pinzke10,2014MNRAS.439.2662V}.
 \begin{figure*}
-  \includegraphics[width=1.0\columnwidth]{figures/fCR.radius.coma.g72a.Rad14.2400p.z0.NL.xKR.eb23.eI066.DII.140.v5.halo.test5.eps}
-  \includegraphics[width=1.0\columnwidth]{figures/turb_profile_ratio.eps}
+  \includegraphics[width=1.0\columnwidth]{figures/fCR.radius.coma.g72a.Rad14.2400p.z0.NL.xKR.eb23.eI067.DII.140.v6.eps}
+  \includegraphics[width=1.0\columnwidth]{figures/turb_profile_ratio_tot.eps}
   \caption{Left: spatial distribution of CRp energy density in the
@@
     cosmological simulations, which disagrees with the required
-    profile. We normalize the required distribution of CRps by fixing
-    the total CRp energy $E_\rmn{p}$ to 0.3 percent of the total
-    thermal energy, consistent with observations
-    \citep{2014ApJ...787...18A,2012ApJ...757..123A}. Right: the ratio
-    of turbulent-to-thermal energy densities in our three models which
-    is parametrised as $\epsilon_\rmn{turb} \propto
-    \epsilon_\rmn{th}^{\alpha_{\rmn{tu}}}$. They are normalized such
-      that the total turbulent energy for each scenario makes up 20\%
-      of the total thermal energy inside the radio halo. Solid lines
-      show the median ratio, while the dotted lines show the 68
-      percentiles.}
+    profile. \AP{To better compare the two models in this figure, we
+      normalize the required distribution of CRps by fixing the total
+      CRp energy $E_\rmn{CR}$ to 0.3 percent of the total thermal
+      energy, consistent with observations
+      \citep{2014ApJ...787...18A,2012ApJ...757..123A}. Right: the
+      ratio of turbulent-to-thermal energy densities (solid lines) and
+      cumulative energies (dotted lines) in our three models. The
+      energy densities are parametrized as $\epsilon_\rmn{turb}
+      \propto \epsilon_\rmn{th}^{(\alpha_{\rmn{tu}}+1)/2}/T^{1/4}$ and
+      normalized such that the total turbulent energy in compressible
+      modes $E_\rmn{turb}$ for each scenario makes up about 6\% of the
+      total thermal energy $E_\rmn{th}$ inside the radio halo
+      ($R_\rmn{RH}\approx0.6R_{200}$). The turbulent profiles explore
+      the uncertainty in the cluster turbulence and are motivated by
+      the cosmological simulation in
+      \citep{2009ApJ...705.1129L,2010ApJ...725.1452S,2011A&A...529A..17V}.}}
   \label{fig:Edens}
@@
 
-Indeed, arriving at a seed population with the required
-characteristics is highly constraining, and has the potential to teach
-us much about the origin of CRps/CRes in clusters. In this paper we
-consider three new scenarios that individually or combined can
-reproduce the observed radio profiles and spectrum in the Coma cluster
-without violating gamma-ray constraints:
+\CP{Could you add a comparison to Miniati's work here and discuss the
+  right panel of figure 1 and table 1? Do we want to move the figure
+  to a later section?}  Indeed, arriving at a seed population with the
+required characteristics is highly constraining, and has the potential
+to teach us much about the origin of CRps/CRes in clusters. \AP{For
+  both the turbulence and magnetic fields we adopt stationary models,
+  parameterized in terms of thermal quantities derived from our
+  simulations.} In this paper we consider three new scenarios that
+individually or combined can reproduce the observed radio profiles and
+spectrum in the Coma cluster without violating gamma-ray constraints:
 \begin{enumerate}
@@
 seed electrons and compare to observations in the Coma cluster. For
-the most part, we adopt parameters that are used in previous work: for
-turbulence, see \citet[][ including turbulent spectrum, injection
-  scale, energy density of turbulence]{brunetti07,brunetti11},
-for CR acceleration in shocks, see \citet[][ in particular
+the most part, we adopt parameters that are used in previous work:
+\AP{for details, see \citep[][ turbulent
+    spectrum]{brunetti07,brunetti11}, \citep[][ injection scale of
+    turbulens]{2015ApJ...800...60M}, \citep[][ energy density of
+    turbulence]{2009ApJ...705.1129L,2010ApJ...725.1452S,2011A&A...529A..17V},
+  for CR acceleration in shocks, \citep[][ in particular
     $K_{\rmn{ep}}$, acceleration efficiency]{pinzke13}, and for
-cosmological simulations, see \citet[][ i.e., shock history,
-  temperature profile, density profile, magnetic field
-  profile]{pinzke10}. All these parameters are uncertain, and could
-potentially change our predictions. We leave exploration of parameter
-space and the interaction between free parameters to future work.
+  cosmological simulations, \citep[][ i.e., shock history, temperature
+    profile, density profile, magnetic field profile]{pinzke10}.} All
+these parameters are uncertain, and could potentially change our
+predictions. We leave exploration of parameter space and the
+interaction between free parameters to future work.
 
@@
 10^{-2}$. Hence, we adopt this as a fiducial value for the CRe-to-CRp
-acceleration efficiency (see \citet{pinzke13} for more
+acceleration efficiency (see \cite{pinzke13} for more
 discussion). However, as recent PIC simulations have shown, this is
@@
 f_\rmn{CRp}(p)$, with a different normalization (due to differing
-acceleration efficiencies) $K_\rmn{ep}=0.1$ (viable for primarily
-perpendicular shocks; \citet{2014ApJ...794..153G}). While this
+acceleration efficiencies) $K_\rmn{ep}=0.1$ \citep[viable for primarily
+perpendicular shocks]{2014ApJ...794..153G}. While this
 appears to contradict the radial bias of magnetic fields in the bulk
@@
 adopt a toy model for our \Mstream scenario in which CR streaming
-quickly produces flat CRp profiles. We assume that CRs cannot stream
-significantly past perpendicular $B$-fields at the accretion shock, so
-that the total number of CRs is conserved within the galaxy cluster
-during the streaming process.
+instantaniously produces flat CRp profiles. \sout{We assume that CRs cannot
+stream significantly past perpendicular $B$-fields at the accretion
+shock, so that the total number of CRs is conserved within the galaxy
+cluster during the streaming process.}
 
@@
 \left|{{dp}\over{dt}}\right|_{\rm C} 
-+ \frac{p}{3}\left(\vec{\nabla}\cdot \vec{\upsilon}\right)\right.\right.
++ \frac{p}{3}\left(\vec{\nabla}\cdot \vec{\upsilon}\right)
++ \left|{{dp}\over{dt}}\right|_{\rm r}\right.\right.
 \nonumber\\
-&+& \left.\left. \left|{{dp}\over{dt}}\right|_{\rm r}
-- {1\over{p^2}}{{\partial }\over{\partial p}}\left(p^2 D_{pp}\right) 
+&-& \left.\left.{1\over{p^2}}{{\partial }\over{\partial p}}\left(p^2 D_{pp}\right) 
 \right]\right\} - \left(\vec{\nabla}\cdot \vec{\upsilon}\right) f_{\rmn{e}}(p,t)
+- \vec{\nabla}\cdot \vec{F}_\rmn{stream}
 \nonumber\\
@@
 and secondary electrons in the ICM. The $\vec{\nabla}\cdot
-\vec{\upsilon}$ terms represent adiabatic gains and losses. During
-post-processing of our Coma-like cluster simulation, we solve the
-Fokker-Planck equation over a redshift interval from $z=5$ to 0. The
-simulated cluster undergoes a major merger over the last 1-2~Gyrs that
-injects large turbulent eddies. After about 1~Gyr those have decayed
-down to the scale needed to reaccelerate particles and the radio halo
-turns on shortly after. This delay naturally explains why giant radio
-halos are only seen in a fraction of all merging clusters. In all our
+\vec{\upsilon}$ terms represent adiabatic gains and losses \AP{and the
+  $\vec{\nabla}\cdot \vec{F}_\rmn{stream}$ terms represent
+  super-Alfv{\'e}nic CR streaming. For details about $F_\rmn{stream}$
+  please see \citet{wiener13}.} During post-processing of our
+Coma-like cluster simulation, we solve the Fokker-Planck equation over
+a redshift interval from $z=5$ to 0. The simulated cluster undergoes a
+major merger over the last 1-2~Gyrs that \AP{is thought to inject
+  large turbulent eddies. Following \citet{brunetti07,brunetti11}
+  \citep[see also][]{2004ApJ...614..757Y,2015ApJ...800...60M} we
+  assume that about one Gyr after core passage the fields have decayed
+  down to the smallest scales where reacceleration is most efficient
+  ($D_{pp}\sim k_\rmn{cut}$) and the radio halo turns on shortly
+  after. Note that the exact decay time of the turbulens is of minor
+  importance, since the thermal and CR quantities are very similar a
+  few 100 Myrs before and after $z=0$ where we have chosen to evaluate
+  the simulations.}  \sout{injects large turbulent eddies. After about
+  1~Gyr those have decayed down to the scale needed to reaccelerate
+  particles.} This delay naturally explains why giant radio halos are
+only seen in a fraction of all merging clusters. In all our
 calculations we assume that turbulent reacceleration efficiently
-accelerates particles for 650 Myrs (which is roughly the cascade time
-on which turbulence is damped) and that during this turbulent phase CR
-streaming and spatial diffusion can be neglected. In our \Mstream
-model, CR streaming and diffusion are incorporated separately during
-kinematically quiescent times that precede the merger. As a result,
-flat CRp profiles are produced on relatively short timescales ($\sim
-0.1-0.5$ Gyr).
+accelerates particles for $\tau_D\sim650$~Myrs (which is roughly the
+cascade time on which turbulence is damped) and that during this
+turbulent phase CR streaming and spatial diffusion can be
+neglected. In our \Mstream model, CR streaming and diffusion are
+incorporated separately during kinematically quiescent times that
+precede the merger. As a result, flat CRp profiles are produced on
+relatively short timescales ($\sim 0.1-0.5$ Gyr). \AP{This allows us
+  to implicitly solve for CR streaming in our calculations, where we
+  adopt a toy model that enforce a flat CRp profile at all quiescent
+  times \citep{wiener13}. We assume that CRs cannot stream
+  significantly past perpendicular $B$-fields at the accretion shock,
+  so that the total number of CRs is conserved within the virial
+  radius during the streaming process. Finally, since streaming is
+  much more efficient for the CRps, we can ignore this effect for the
+  CRes.}
 
@@
 \right]\right\} - \left(\vec{\nabla}\cdot \vec{\upsilon}\right) f_{\rmn{p}}(p,t)
+- \vec{\nabla}\cdot \vec{F}_\rmn{stream}
 \nonumber\\
@@
 momentum-diffusion coefficient of isotropic particles that couple to
-fast magnetosonic modes via TTD resonance is \cite{brunetti07}
-(Eqn. 47):
+fast magnetosonic modes via TTD resonance is \citep[][ Eqn. 47]{brunetti07}:
 \begin{eqnarray}
@@
 \end{equation}
-Here $V_\rmn{ph}$ is the phase velocity of the fast magnetosonic waves given
-approximately by the sound speed, $\Vph \sim c_\rmn{s}$. For a sound speed
-typical for the ICM of 1000~km/s, $I_\theta\approx5$. As in \cite{brunetti07},
-we initially assume that the velocity of turbulent eddies is $V_0\approx 0.47
-c_\rmn{s}$ throughout the cluster. This gives a turbulent acceleration time
-scale, $\tau_{pp} = p^2/4D_{pp}$, that is typically few 100 Myrs in the ICM.
+Here $V_\rmn{ph}$ is the phase velocity of the fast magnetosonic waves
+given approximately by the sound speed, $\Vph \sim c_\rmn{s}$. For a
+sound speed typical for the ICM of 1000~km/s, $I_\theta\approx5$. As
+in \cite{brunetti07}, we initially assume that the velocity of
+turbulent eddies is $V_0\approx 0.47 c_\rmn{s}$ throughout the
+cluster. This gives a turbulent acceleration time scale, $\tau_{D} =
+p^2/4D_{pp}$, that is typically few 100 Myrs in the ICM (see
+Tab.~\ref{tab:timescales} for more details).
 
-We adopt a simplified isotropic MHD turbulent spectrum for the fast
-modes per elemental range $dk$ of the form
+\AP{We focus on a scenario where the turbulence is injected at the
+  largest scale that is driven by the merging cluster and accreting
+  matter. The diffusion equation for isotropic MHD turbulence in
+  $k$--space is given by}
+\begin{eqnarray}
+&{{\partial {\mathcal W}(k,t) }\over{\partial t}}
+=
+{{\partial}\over{\partial k}}
+\left[
+k^2 D_{kk}
+{{\partial}\over{\partial k}}
+\left( {{ {\mathcal W}(k,t) }\over{k^2}} \right)
+\right]
+- \sum_i \Gamma_i (k,t) {\mathcal W}(k,t)
++ I(k,t)\nonumber\\
+&
+\label{modes_kinetic}
+\end{eqnarray}
+\AP{where we assume that the volumetric injection rate of turbulence
+  $I(k,t)$ is constant over time with a fixed rate $I_0$ so that
+  $I(k,t) \equiv I(k) = I_0\,\delta (k - k_o)$. The different damping
+  terms are given by $\Gamma_i(k,t)$ and $D_{kk}$ is the wave--wave diffusion
+  coefficient of magnetosonic waves in the $k$--space represented by
+  \begin{equation}
+    \label{eq:Dkk}
+    D_{kk} \approx \Vph k^4
+    \left(\frac{\mathcal{W}(k)}{\rho\,\Vph^2}\right)\,.
+  \end{equation}
+}
+
+We adopt a simplified isotropic MHD turbulent spectrum \AP{based on
+Kraichnan's picture} for the fast modes per elemental range $dk$ of
+  the form
 \begin{equation}
@@
 \end{equation}
-for $k_0<k<k_\rmn{cut}$, where we assume an injection scale for the
-turbulence, $k_0= 2\pi/(100~\mbox{kpc})$. The volumetric injection
-rate of turbulent energy, $I_0$, is fixed by requiring that the total
-turbulent energy on the largest scales $E_\rmn{turb}=\int \int
-\mathcal{W}(k) \rmn{d}k \rmn{d}V \approx 0.2 E_\rmn{th}$, where
-$E_\rmn{th}$ is the total thermal energy \citep{brunetti07,brunetti11}
-within the radio halo. In this work we investigate different spatial
-models for injected turbulence. We assume that turbulent energy
-density $\epsilon_\rmn{turb} \propto
-\epsilon_\rmn{th}^{\alpha_\rmn{tu}}$, where $\alpha_\rmn{tu}= 0.66$
-for \Mflatturb, $\alpha_\rmn{tu}= 0.81$ for \Mstream, and
-$\alpha_\rmn{tu}= 0.88$ for \Mprimary (note that in previous work on
-the Coma cluster, $\alpha_\rmn{tu}= 1$ was adopted \citep{brunetti12},
-which together with the different distributions for seed CRes
-constitute the main differences compared to our work). Our flatter
-turbulent profiles are motivated by fits to cosmological simulations
-\citep{2009ApJ...705.1129L,2010ApJ...725.1452S,2012ApJ...758...74B}
+for $k_0<k<k_\rmn{cut}$. \AP{Here we adopt an injection scale of the
+  turbulens, $k_0= 2\pi/(1~\mbox{Mpc})$, motivated by recent
+  state-of-art simulations
+  \citep{2009A&A...504...33V,2011A&A...529A..17V,2015ApJ...800...60M}. \sout{At
+    the same time we note that there is a large uncertainty in $k_0$,
+    that is degenerate with the level of turbulence in compressible
+    modes ($X_\rmn{tu}$) which is also highly uncertain. Increasing
+    one of the parameters, allow us to decrease the other in order to
+    keep $D_{pp}$ at the value needed to explain
+    observations.}}\sout{, where we assume an injection scale for the
+  turbulence, $k_0= 2\pi/(100~\mbox{kpc})$.} \AP{The profile of
+  injected turbulence is also highly uncertain, however we assume it
+  correlates to the thermal energy density to some power of the
+  merging clusters. Hence we assume volumetric injection rate of
+  turbulent energy, $I_0\propto \epsilon_\rmn{th}^{\alpha_\rmn{tu}}$,
+  and determine the normalization by requiring that the turbulent
+  energy in compressible modes $E_\rmn{turb}=\int \int \mathcal{W}(k)
+  \rmn{d}k \rmn{d}V = X_\rmn{tu} E_\rmn{th}$, where $E_\rmn{th}$ is
+  the total thermal energy. We adopt a turbulent energy
+  ratio\footnote{Simulations show that the compressible modes
+    contribute a factor $0.2-0.4$ to the total turbulent energy
+    \citep{2013ApJ...771..131B,2015ApJ...800...60M}. Furthermore, the
+    total turbulent energy is typically $10-30$\% of the thermal
+    energy in a cluster which is in agreement with our adopted value
+    of $X_\rmn{tu}$.}  $X_\rmn{tu}=0.06$ within the radio halo.} In
+this work we investigate different spatial models for injected
+turbulence. With the above choice of normalization, the turbulent
+energy density becomes $\epsilon_\rmn{turb} \propto
+\epsilon_\rmn{th}^{\alpha_\rmn{tu}}/T^{1/4}$, where $T$ is the
+temperature of the gas, $\alpha_\rmn{tu}= 0.67$ for \Mflatturb,
+$\alpha_\rmn{tu}= 0.82$ for \Mstream, and $\alpha_\rmn{tu}= 0.88$ for
+\Mprimary. Note that in previous work on the Coma cluster,
+$\epsilon_\rmn{turb} \propto \epsilon_\rmn{th}$ was adopted which
+roughly corresponds to $\alpha_\rmn{tu}= 1$ \citep{brunetti12} and
+together with the different distributions for seed CRes constitute the
+main differences compared to our work. Our flatter turbulent profiles
+are motivated by fits to cosmological simulations
+\citep{2009ApJ...705.1129L,2010ApJ...725.1452S,2011A&A...529A..17V,2012ApJ...758...74B}
 and the range indicates uncertainties of the turbulent profile in
@@
 approaches the cascading timescale given by $\tau_{kk} \approx
-k^2/D_{kk}$. Here the wave-wave diffusion coefficient of magnetosonic
-modes is given by
-\begin{equation}
-\label{eq:Dkk}
-D_{kk} \approx \Vph k^4
-\left(\frac{\mathcal{W}(k)}{\rho\,\Vph^2}\right).
-\end{equation}
-Thus, the cascade is suppressed for wave numbers above
+k^2/D_{kk}$. Thus, the cascade is suppressed for wave numbers above
 \begin{equation}
@@
 
+\AP{For reference we show in \ref{tab:timescales} both the thermal
+  quantities and the timescales for CR cooling and (re)acceleration
+  for three different spatial regions of the RH. Interestingly the
+  reacceleration timescale $\tau_D$ is very similar between our three
+  models, where the difference comes from turbulent profile
+  parameterized with $\alpha_\rmn{tu}$. This implies that even small
+  differences in the turbulent profile could impact the seed CRs
+  significantly.}
+
+\begin{table}
+  \caption{Thermal quantities and timescales for different spatial
+    regions in a Coma like cluster.}
+\begin{tabular}{l c  c c}
+\hline
+\hline
+& & spatial regions & \\
+ & $0.1\,\RH^{(2)}$ &  $0.3\,\RH^{(2)}$  &  $\RH^{(2)}$   \\
+\hline
+THERMAL QUANTITIES$^{(1)}$ & & & \\
+$\rho$ [$10^{-27}$ g cm$^{-3}$] & 3.0 & 1.6 & 0.15 \\
+$T$ [$10^{8}$ K] & 1.4 & 1.0 & 0.58 \\
+\hline
+TIMESCALES$^{(1)}$ & & & \\
+$\tau_\rmn{D}$(\Mprimary)$^{(3)}$ [Gyr] & 0.29 & 0.36 & 0.52 \\
+$\tau_\rmn{D}$(\Mstream)$^{(3)}$  [Gyr] & 0.29 & 0.36 & 0.51 \\
+$\tau_\rmn{D}$(\Mflatturb)$^{(3)}$  [Gyr] & 0.29 & 0.37 & 0.49 \\
+$\tau_\rmn{IC/sync}(P=10^4\,m_ec)^{(4)}$ [Gyr] & 0.11 & 0.10 & 0.09 \\
+$\tau_\rmn{pp}(P=100\,m_pc)^{(5)}$ [Gyr] & 2.4 & 4.5 & 44 \\
+$\tau_\rmn{coul}(P=\,m_ec)^{(6)}$  [Gyr] & 0.0092 & 0.017 & 0.16 \\
+\hline
+\end{tabular}
+\begin{quote}
+ Notes: \\ 
+ (1) Median quantities from our simulated post-merging cluster g72a.\\
+ (2) Radius of the giant radio halo in Coma where $\RH\approx0.6\,R_{200}$.\\
+ (3) Fermi-II reacceleration for both electrons and protons at all energies.\\
+ (4) Inverse Compton and Synchrotron cooling for electrons.\\
+ (5) Catastrophic losses for protons.\\
+ (6) Coulomb cooling for electrons (protons factor $m_e/m_p$ smaller).\\
+
+ \label{tab:timescales}
+  \end{quote}
+\end{table}
+
 % --- section: Results and discussion --- %
@@
 \label{sec:results}
+\AP{In this section we show that our three models individually
+  reproduce the observed Coma radio halo without violating gamma-ray
+  bounds. The level of emission is mainly driven by how efficient the
+  CRs are reaccelerated and for how long. The diffusion constant,
+  $D_\rmn{pp}\propto I_0/\rho c_s \propto
+  X_\rmn{tu}^2k_0\epsilon_\rmn{tu}^{\alpha_\rmn{tu}-1}\sqrt{T}$, where
+  we adopt the same level of compressible turbulence,
+  $X_\rmn{tu}=0.06$, for all models. The reaccelerated CRs are
+  super-exponentially dependent on this parameter as long as $\tau_D >
+  \tau_\rmn{cl}$, where $\tau_\rmn{cl}$ represent the duration of
+  reacceleration of the merger which we assume to be 650~Myrs
+  long. Note that a fixed $D_\rmn{pp}$ allow us to relate
+  $\tau_\rmn{cl} \propto X_\rmn{tu}^2 \propto k_0$ that ultimately set
+  the normalization for $D_\rmn{pp}$. We also exploit the large
+  uncertainty in the turbulent profile and adjust $\alpha_\rmn{tu}$
+  for each model so that the CRs have the correct spatial profile to
+  match the radio emission. The shape of the spectrum for each of
+  model is more complicated and is determined both from reacceleration
+  and as well as the gains and losses during the formation of the
+  cluster. It depends only weakly on the specifics of the CR injection
+  at the shocks (where the Mach number distribution of the shocks is
+  the most important quantity). The normalization of the spectrum is
+  mainly determined from the maximum acceleration efficiency (together
+  with the uncertain parameters $X_\rmn{tu}$, $\tau_\rmn{cl}$, and
+  $k_0$). Given the freedom in the turbulens, it might not be
+  surprising that we match the radio profile in Coma. Although,
+  matching the spectrum without violating gamma-ray bounds for each of
+  our three models is more surprising and is not a consequence of
+  parameter fitting. We believe that it is ultimately a consequence of
+  the adopted physics and hint that reacceleration is a viable
+  explanation for giant radio halos. Below we discuss in more detail
+  the different emission components of Coma.}
 
+\subsection{Gamma-rays}
 After turbulent reacceleration, the volume-weighted, relative CRp
-energy density and CRp number density inside the RH for \Mflatturb
-(\Mstream), are found to be 3 (2) \% and $3.0\times10^{-8}$
-($4.5\times10^{-8}$), respectively. As we will see later, these
+energy density and relative CRp number density inside the RH for
+\Mflatturb (\Mstream), are found to be 2 (3) \% and $2\times10^{-8}$
+($5\times10^{-8}$), respectively. As we will see later, these
 densities are just of the right order of magnitude to reproduce radio
@@
 predict the gamma-ray emission from \Mflatturb (\Mstream) with
-$F_\gamma(>500\,\rmn{MeV})=4.8\times10^{-10} (2.3\times10^{-10})
-\mathrm{ \,ph\, s}^{-1}\mathrm{cm}^{-2}$. The fluxes from these
-models are slightly larger than in \cite{brunetti12}, where the
-differences comes from our steeper CRp profiles in addition to
-simulation based formalism we rely on that accounts for both Coulomb
-and hadronic losses during the build up of the CR distribution in
-contrast to the scaling relations adopted in their
-paper. Interestingly the gamma-ray flux from both our scenarios are
-just below recent Fermi-LAT limits derived from a gamma-ray profile
-similar to \Mflatturb where
+$F_\gamma(>500\,\rmn{MeV})=4\times10^{-10} (5\times10^{-10}) \mathrm{
+  \,ph\, s}^{-1}\mathrm{cm}^{-2}$. The fluxes from these models are
+slightly larger than in \cite{brunetti12}, where the differences comes
+from our steeper CRp profiles in addition to simulation based
+formalism we rely on that accounts for both Coulomb and hadronic
+losses during the build up of the CR distribution in contrast to the
+scaling relations adopted in their paper. Interestingly the gamma-ray
+flux from both our scenarios are just below recent Fermi-LAT limits
+derived from a gamma-ray profile similar to \Mflatturb where
 $F_\gamma(>500\,\rmn{MeV})<5.3\times10^{-10} \mathrm{ \,ph\,
@@
 radio-emitting secondary CRes. The steep spectrum is ultimately a
-consequence of our test particle model for Fermi-I acceleration
+consequence \AP{of the shock history of the simulated cluster, with a
+  weak dependence on} our test particle model for Fermi-I acceleration
 \citep{pinzke13}, where we steepen the spectral index to avoid
@@
 
+\subsection{Radio profile}
 In Fig.~\ref{fig:sync_profile}, we find that all three scenarios in
@@
 of $D_\rmn{pp}(R)\propto
-\epsilon_\rmn{th}(R)^{(\alpha_\rmn{tu}+1)/2}/\sqrt{T(R)}$. This
+\epsilon_\rmn{th}(R)^{\alpha_\rmn{tu}-1}\sqrt{T(R)}$. This
 signals that the problem is generic and requires either additional
@@
    \begin{center}\Large{\Mprimary:}\\
-     \includegraphics[width=\columnwidth]{figures/sbright.nu.DIIcomp.Pri.g72a.Rad14.2400p.z0.NL.xKR.eb23.eI088.140.v5.halo.test5.eps}
+     \includegraphics[width=\columnwidth]{figures/sbright.nu.DIIcomp.Pri.g72a.Rad14.2400p.z0.NL.xKR.eb23.eI088.140.v6.eps}
    \end{center}
@@
    \begin{center}\Large{\Mstream:}\\
-     \includegraphics[width=\columnwidth]{figures/sbright.nu.DIIcomp.flatCR.g72a.Rad14.2400p.z0.NL.xKR.eb23.eI081.flatCR.140.v5.halo.test5.eps}
+     \includegraphics[width=\columnwidth]{figures/sbright.nu.DIIcomp.flatCR.g72a.Rad14.2400p.z0.NL.xKR.eb23.eI082.flatCR.140.v6.eps}
    \end{center}
@@
   \begin{center}\Large{\Mflatturb:}\\ 
-    \includegraphics[width=\columnwidth]{figures/sbright.nu.DIIcomp.I0.g72a.Rad14.2400p.z0.NL.xKR.eb23.eI066.140.v5.halo.test5.eps}
+    \includegraphics[width=\columnwidth]{figures/sbright.nu.DIIcomp.I0.g72a.Rad14.2400p.z0.NL.xKR.eb23.eI067.140.v6.eps}
   \end{center}
@@
    \begin{center}\Large{\it Brunetti et al. (2012)}:\\
-     \includegraphics[width=\columnwidth]{figures/sbright.nu.DIIcomp.Brunetti.g72a.Rad14.2400p.z0.NL.xKR.eb23.140.v5.halo.test5.eps}
+     \includegraphics[width=\columnwidth]{figures/sbright.nu.DIIcomp.Brunetti.g72a.Rad14.2400p.z0.NL.xKR.eb23.140.v6.eps}
    \end{center}
@@
   CR electrons of a simulated post-merging cluster similar to Coma. We
-  compare profiles at 352~MHz (blue lines and crosses \citet{brown11})
-  to those at 1.4~GHz (green lines and crosses \citet{deiss97}). The
-  red crosses show the reprocessed 1.4~GHz data, where a zero level of
-  about 10~\% of the central value is adopted. The solid lines show
-  predicted emission from a reaccelerated fossil population, while
-  dotted lines show emission from a fossil population without
-  reacceleration. The panels show the emission of our models \Mprimary
-  (upper left panel), \Mstream (upper right panel), \Mflatturb (lower
-  left panel), and simulated secondary electrons together with
-  previous estimates \citet{brunetti12} for the Coma cluster (lower
-  right panel).}
+  compare profiles at 352~MHz \citep[blue lines and
+    crosses,][]{brown11} to those at 1.4~GHz \citep[green lines and
+    crosses,][]{deiss97}. The red crosses show the reprocessed 1.4~GHz
+  data, where a zero level of about 10~\% of the central value is
+  adopted. The solid lines show predicted emission from a
+  reaccelerated fossil population, while dotted lines show emission
+  from a fossil population without reacceleration. The panels show the
+  emission of our models \Mprimary (upper left panel), \Mstream (upper
+  right panel), \Mflatturb (lower left panel), and simulated secondary
+  electrons together with previous estimates \citep{brunetti12} for
+  the Coma cluster (lower right panel).}
   \label{fig:sync_profile}
@@
 
+\subsection{Radio spectrum}
 In Fig.~\ref{fig:sync_spectrum} we show that our three models that
@@
 in our three models \Mprimary, \Mstream, and \Mflatturb to
-$\zeta_{\rmn{e}} <0.002$, $\zeta_{\rmn{p}} < 0.1$, and
-$\zeta_{\rmn{p}}<0.025$, respectively. Following the Mach number
+$\zeta_{\rmn{e}} <0.003$, $\zeta_{\rmn{p}} < 0.1$, and
+$\zeta_{\rmn{p}}<0.03$, respectively. Following the Mach number
 ($\mathcal{M}$)-dependence of the acceleration efficiency suggested in
@@
 dependence on the acceleration efficiency, it has a strong non-linear
-dependence on the level of turbulence. Below a critical level ($X =
-E_\rmn{turb}/E_\rmn{th} \sim 0.15$ in our fiducial model), turbulent
-reacceleration is negligible, while it rises sharply above this
-threshold. For instance, for $X>0.15$, a factor 2 change in $X$
-changes the radio surface brightness by $\sim 10-100$. In principle
-this threshold behavior allows us to provide a strict lower bound on
-turbulence in radio halos. An even more stringent bound on $X$ can be
-inferred from combining radio observations with the gamma-ray
-observations where the predicted fluxes from both \Mstream and
-\Mflatturb are close to the upper limits set by Fermi-LAT. If $X$ is
-smaller than in our adopted models (where we assume $X=0.2$), then the
-efficiency of DSA has to be larger than $\zeta_\rmn{p}\sim 0.1$ for
-the secondary CRes to reproduce the radio observations. However, since
-the turbulent reacceleration acts on both the secondary CRes and the
-CRps, while $\zeta_\rmn{p}$ only affects the CRps, these models would
-produce too much gamma-rays. Hence we conclude that $X\gtrsim0.2$ if
-all other parameters are kept fixed. We will explore this parameter
-space further in future work.
+dependence on the level of compressible turbulence. Below a critical
+level ($X_\rmn{thres,tu} = 
+\frac{400\,\rmn{Myrs}}{\tau_\rmn{cl}} X_\rmn{tu}\approx 0.04$ in our fiducial model),
+turbulent reacceleration is negligible, while it rises sharply above
+this threshold. For instance, for $X_\rmn{tu}\gtrsim0.04$, a factor 2 change
+in $X_\rmn{tu}$ changes the radio surface brightness by $\sim
+10-100$. In principle this threshold behavior allows us to provide a
+strict lower bound on turbulence in radio halos. An even more
+stringent bound on $X_\rmn{tu}$ can be inferred from combining radio
+observations with the gamma-ray observations where the predicted
+fluxes from both \Mstream and \Mflatturb are close to the upper limits
+set by Fermi-LAT. If $X_\rmn{tu}$ is smaller than in our adopted
+models (where we assume $X_\rmn{tu}=0.06$), then the efficiency of DSA
+has to be larger than $\zeta_\rmn{p}\sim 0.1$ for the secondary CRes
+to reproduce the radio observations. However, since the turbulent
+reacceleration acts on both the secondary CRes and the CRps, while
+$\zeta_\rmn{p}$ only affects the CRps, these models would produce too
+much gamma-rays. Hence we conclude that $X_\rmn{tu}\gtrsim0.06$ if all
+other parameters are kept fixed. \AP{Although, we caution the reader
+  to take this limit too stringent since there are degeneracies between
+  the uncertain parameters
+  $X_\rmn{tu}\propto\sqrt{\tau_\rmn{D}}\propto \sqrt{k_0}$.} We will
+explore this parameter space further in future work.
 
 \begin{figure*}
-  \includegraphics[width=1.0\columnwidth]{figures/sync.spec.pri.g72a.140.v5.halo.test5.eps}
-  \includegraphics[width=1.0\columnwidth]{figures/sync.spec.sec.g72a.140.v5.halo.test5.eps}
+  \includegraphics[width=1.0\columnwidth]{figures/sync.spec.pri.g72a.140.v6.eps}
+  \includegraphics[width=1.0\columnwidth]{figures/sync.spec.sec.g72a.140.v6.eps}
   \caption{Radio synchrotron spectra. Lines are derived from
@@
 
-The standard reacceleration model for radio halos (RHs) requires
-a population of seed electrons to undergo turbulent
+The standard reacceleration model for radio halos (RHs) requires a
+population of seed electrons to undergo turbulent
 reacceleration. These seeds are generally thought to be secondary
-electrons from hadronic cosmic ray proton (CRp) interactions. In
-this work we use cosmological simulations to derive a population of
-seed CR protons originating from structure formation shocks and merger
-shocks during the cluster build up. The resulting secondary population
-is inconsistent with RH observations. We propose three possible
-solutions that all produce gamma-ray emission below current upper
-limits and that reproduce both, the spectrum and the surface
-brightness profiles of the Coma radio halo:
+electrons from hadronic cosmic ray proton (CRp) interactions. In this
+work we use cosmological simulations to derive a population of seed CR
+protons originating from structure formation shocks and merger shocks
+during the cluster build up. The resulting secondary population is
+inconsistent with RH observations. We propose three possible solutions
+where all reaccelerated CRs produce gamma-ray emission below current
+upper limits. Additionally, they reproduce both the spectrum and the
+surface brightness profiles of the Coma radio halo:
 
@@
 acceleration efficiency ($\zeta_p$) only acts on the CRps, radio
-observations fix the relation between $X$ (the ratio of the total
-turbulent energy to the thermal energy) and the acceleration
-efficiency. With the addition of gamma-ray constraints from Fermi-LAT,
-we can derive a lower limit to $X\gtrsim0.2$ and a upper limit to the
-acceleration efficiencies of $\zeta_p\lesssim 10\%$ ($\zeta_p\lesssim
-2.5\%$) for the two models, respectively, for our current choices of
-other parameters.
+observations fix the relation between $X_\rmn{tu}$ (the ratio of the
+total turbulent energy in compressional modes to the total thermal
+energy) and the acceleration efficiency. With the addition of
+gamma-ray constraints from Fermi-LAT, we can derive a lower limit to
+$X_\rmn{tu}\gtrsim0.06$ and a upper limit to the acceleration
+efficiencies of $\zeta_p\lesssim 10\%$ ($\zeta_p\lesssim 3\%$) for
+the two models, respectively, for our current choices of other
+parameters.
 

### 2016-03-24 paper.tex
Added files via upload

@@
 TIMESCALES$^{(1)}$ & & & \\
-$\tau_\rmn{D}$(\Mprimary)$^{(3)}$ [Gyr] & 0.29 & 0.36 & 0.52 \\
-$\tau_\rmn{D}$(\Mstream)$^{(3)}$  [Gyr] & 0.29 & 0.36 & 0.51 \\
-$\tau_\rmn{D}$(\Mflatturb)$^{(3)}$  [Gyr] & 0.29 & 0.37 & 0.49 \\
-$\tau_\rmn{IC/sync}(P=10^4\,m_ec)^{(4)}$ [Gyr] & 0.11 & 0.10 & 0.09 \\
-$\tau_\rmn{pp}(P=100\,m_pc)^{(5)}$ [Gyr] & 2.4 & 4.5 & 44 \\
-$\tau_\rmn{coul}(P=\,m_ec)^{(6)}$  [Gyr] & 0.0092 & 0.017 & 0.16 \\
+$\tau_\rmn{D}$(\Mprimary)$^{(3)}$ [Gyr] & 0.45 & 0.44 & 0.39 \\
+$\tau_\rmn{D}$(\Mstream)$^{(3)}$  [Gyr] & 0.50 & 0.47 & 0.34 \\
+$\tau_\rmn{D}$(\Mflatturb)$^{(3)}$  [Gyr] & 0.69 & 0.56 & 0.27 \\
+$\tau_\rmn{IC/sync}(P=10^4\,m_ec)^{(4)}$ [Gyr] & 0.11 & 0.15 & 0.22 \\
+$\tau_\rmn{pp}(P=100\,m_pc)^{(5)}$ [Gyr] & 2.4 & 4.5 & 47 \\
+$\tau_\rmn{coul}(P=\,m_ec)^{(6)}$  [Gyr] & 0.0092 & 0.017 & 0.17 \\
 \hline

### 2016-04-05 paper.tex
changes to intro

@@
-\documentclass[useAMS,usenatbib]{mn2e}
-\usepackage{epsfig,psfrag,txfonts,xspace}
+\documentclass[a4paper,fleqn,usenatbib]{mnras}
+\usepackage{txfonts}
+\usepackage[T1]{fontenc}
+\usepackage{ae,aecompl}
+\usepackage{graphicx,color}	% Including figure files
+%\usepackage{amsmath}	% Advanced maths commands
+\usepackage{amssymb}	% Extra maths symbols
+\usepackage{amsbsy}
 \usepackage[normalem]{ulem}
-\usepackage{graphicx,color}
-\usepackage{natbib}
-\usepackage{amsfonts,amsbsy,amssymb}
+\usepackage{mathrsfs,bm,xspace}
+\newcommand{\bcdot}{\ensuremath{%
+  \mathchoice%
+   {\mskip\thinmuskip\lower0.2ex\hbox{\scalebox{1.5}{$\cdot$}}\mskip\thinmuskip}}%
+   {\mskip\thinmuskip\lower0.2ex\hbox{\scalebox{1.5}{$\cdot$}}\mskip\thinmuskip}%        
+   {\lower0.3ex\hbox{\scalebox{1.2}{$\cdot$}}}%  
+   {\lower0.3ex\hbox{\scalebox{1.2}{$\cdot$}}}%
+}
 
-% --- journals --- %
-\newcommand{\aap}{A{\&}A}
-\newcommand{\aaps}{A{\&}AS}
-\newcommand{\aapr}{AAPR}
-\newcommand{\aj}{AJ}
-\newcommand{\apj}{ApJ}
-\newcommand{\apjl}{ApJL}
-\newcommand{\apjs}{ApJS}
-\newcommand{\apss}{Ap{\&}SS}
-\newcommand{\araa}{ARA{\&}A}
-\newcommand{\memsai}{{Mem.~Soc.~Astron.~Italiana}}
-\newcommand{\mnras}{MNRAS}
-\newcommand{\ssr}{SSRv}
-\newcommand{\physrep}{Phys.~Rep.}
-\newcommand{\jcomp}{J.~Comput.~Phys.}
-\newcommand{\jgr}{JGR}
-\newcommand{\grl}{GRL}
-\newcommand{\nat}{Nature}
+% --- macros --- %
 \newcommand{\Mstream}{{\it M-streaming}\xspace}
@@
 
-% --- macros --- %
+\renewcommand{\vec}{\ensuremath{\mathbfit}}
 \newcommand{\dd}{\mathrm{d}}
@@
 \newcommand{\RH}{R_\rmn{RH}}
+\newcommand{\bvel}{\ensuremath{\boldsymbol{\varv}}}
+\newcommand{\bnabla}{\ensuremath{\boldsymbol{\nabla}}}
 
@@
   promising model for radio halos is Fermi II acceleration of seed
-  relativistic electrons by turbulence in the intracluster medium
-  (ICM); Coulomb losses prohibit acceleration from the thermal
-  pool. However, the origin of seed electrons has never been fully
-  explored. Here, we integrate the Fokker-Planck equation of the
-  cosmic ray (CR) electron and proton distributions in cosmological
-  simulations of cluster formation. For standard assumptions,
-  structure formation shocks lead to a seed electron population which
-  produces too centrally concentrated radio emission. Instead, we
-  present three plausible scenarios for the seed CRs that each
-  can reproduce the spatially flat radio emission observed in the Coma
-  cluster. (1) The CR proton to electron acceleration efficiency
-  $K_\rmn{ep} \sim 0.1$ is assumed to be larger than in our Galaxy
-  ($K_\rmn{ep} \sim 10^{-2}$), due to the magnetic geometry at the
-  shock. The resulting primary electrons dominate the radio emission,
-  which is more extended in comparison to radio emission from
-  secondary electrons that result from hadronic CR interactions in the
-  ICM. (2) CR protons may stream at the Alfv{\'e}n speed to the
-  cluster outskirts when the ICM is relatively quiescent. A spatially
-  flat CR proton distribution develops and produces the required
-  population of secondary seed electrons. (3) The ratio of injected
-  turbulent energy density to thermal energy density increase
+  relativistic electrons by compressible turbulence in the
+  intracluster medium (ICM); Coulomb losses prohibit acceleration from
+  the thermal pool. However, the origin of seed electrons has never
+  been fully explored. Here, we integrate the Fokker-Planck equation
+  of the cosmic ray (CR) electron and proton distributions in
+  cosmological simulations of cluster formation. For standard
+  assumptions, structure formation shocks lead to a seed electron
+  population which produces too centrally concentrated radio
+  emission. Instead, we present three plausible scenarios for the seed
+  CRs that each can reproduce the spatially flat radio emission
+  observed in the Coma cluster. (1) The CR proton-to-electron
+  acceleration efficiency $K_\rmn{ep} \sim 0.1$ is assumed to be
+  larger than in our Galaxy ($K_\rmn{ep} \sim 10^{-2}$), due to the
+  magnetic geometry at the shock. The resulting primary electrons
+  dominate the radio emission, which is more extended in comparison to
+  radio emission from secondary electrons that result from hadronic CR
+  interactions in the ICM. (2) CR protons may stream at the Alfv{\'e}n
+  speed to the cluster outskirts when the ICM is relatively
+  quiescent. A spatially flat CR proton distribution develops and
+  produces the required population of secondary seed electrons. (3)
+  The ratio of injected turbulent-to-thermal energy density increases
   significantly with radius, as seen in cosmological simulations. This
-  generates a flat radio profile when CRs are reaccelerated even
-  if the seed population of CRs is steep with radius. These competing
+  generates a flat radio profile when CRs are reaccelerated even if
+  the seed population of CRs is steep with radius. These competing
   non-trivial solutions provide incisive probes of non thermal
@@
 \citep{2001A&A...369..441G,2012A&ARv..20...54F} and the Compton
-$y$-parameter \citep{2013A&A...554A.140P}. The RHs show that CRs and
-magnetic fields permeate a large volume fraction of the intra-cluster
-medium (ICM). The dominant CR source, given the smoothness and
-enormous extent of RHs, is thought to be structure formation shocks
-\citep{miniati01,pfrommer08}. At the same time, plasma processes, the
-origin of magnetic fields and particle acceleration in a turbulent,
-high-$\beta$ plasma like the ICM are not well understood. Radio halos
-thus provide an incisive probe of non-thermal processes in the ICM.
+$y$-parameter \citep{2012MNRAS.421L.112B,2013A&A...554A.140P}. The RHs
+show that CR electrons and magnetic fields permeate a large volume
+fraction of the intra-cluster medium (ICM). The dominant CR source,
+given the smoothness and enormous extent of RHs, is thought to be
+structure formation shocks \citep{miniati01,pfrommer08}. At the same
+time, plasma processes, the origin of magnetic fields and particle
+acceleration in a turbulent, high-$\beta$ plasma like the ICM are not
+well understood. Radio halos thus provide an incisive probe of
+non-thermal processes in the ICM.
 
@@
 distribution is not predicted by cosmological simulations \cite[see
-  also][]{pinzke10,2014MNRAS.439.2662V}.
+  also][]{pinzke10,2014MNRAS.439.2662V}. \CP{Explain Fig 1: why is
+  simulated profile steep? transport, secondaries, \ldots}
+
 \begin{figure*}
-  \includegraphics[width=1.0\columnwidth]{figures/fCR.radius.coma.g72a.Rad14.2400p.z0.NL.xKR.eb23.eI067.DII.140.v6.eps}
-  \includegraphics[width=1.0\columnwidth]{figures/turb_profile_ratio_tot.eps}
+  \includegraphics[width=1.0\columnwidth]{fCR.radius.coma.g72a.Rad14.2400p.z0.NL.xKR.eb23.eI067.DII.140.v6.eps}
+  \includegraphics[width=1.0\columnwidth]{turb_profile_ratio_tot.eps}
   \caption{Left: spatial distribution of CRp energy density in the
@@
 
-\CP{Could you add a comparison to Miniati's work here and discuss the
-  right panel of figure 1 and table 1? Do we want to move the figure
-  to a later section?}  Indeed, arriving at a seed population with the
-required characteristics is highly constraining, and has the potential
-to teach us much about the origin of CRps/CRes in clusters. \AP{For
-  both the turbulence and magnetic fields we adopt stationary models,
-  parameterized in terms of thermal quantities derived from our
-  simulations.} In this paper we consider three new scenarios that
+Indeed, arriving at a seed population with the required
+characteristics is highly constraining, and has the potential to teach
+us much about the origin of CRps/CRes in clusters.  \CP{We use our
+  simuations to generate distribution function of seed population,
+  resolve injection and loss processes for CRs and integrate the
+  Fokker-Planck equation along Lagrangian particle trajectories to
+  obtain a momentum spectrum of CRs. However, we assume a simplified
+  turbulent model. So our approach is orthogonal (and complementary)
+  to e.g. Miniati 2015.}  \AP{For both the turbulence and magnetic
+  fields we adopt stationary models, parameterized in terms of thermal
+  quantities derived from our simulations.}
+
+In this paper we consider three new scenarios that
 individually or combined can reproduce the observed radio profiles and
@@
   secondary electron distribution.
-\item {\bf Model {\em M-turbulence}.} Here, we adopt a significantly spatially
+\item {\bf Model {\em M-turbulence}.} Here, we adopt a spatially
   flatter turbulent profile than what was adopted in \citet{brunetti12},
@@
 f_\rmn{CRp}(p)$, with a different normalization (due to differing
-acceleration efficiencies) $K_\rmn{ep}=0.1$ \citep[viable for primarily
-perpendicular shocks]{2014ApJ...794..153G}. While this
+acceleration efficiencies) $K_\rmn{ep}=0.1$ \citep[which is viable for
+  primarily perpendicular shocks][]{2014ApJ...794..153G}. While this
 appears to contradict the radial bias of magnetic fields in the bulk
@@
 still efficient for highly subsonic conditions \citep{wiener13}, while
-we assume compressible fast modes only provide effective spatial
+we assume compressible fast modes to only provide effective spatial
 confinement during the periods of transonic, highly super-Alfv{\'e}nic
@@
 adopt a toy model for our \Mstream scenario in which CR streaming
-instantaniously produces flat CRp profiles. \sout{We assume that CRs cannot
+instantaneously produces flat CRp profiles. \sout{We assume that CRs cannot
 stream significantly past perpendicular $B$-fields at the accretion
@@
 \left|{{dp}\over{dt}}\right|_{\rm C} 
-+ \frac{p}{3}\left(\vec{\nabla}\cdot \vec{\upsilon}\right)
++ \frac{p}{3}\left(\bnabla\bcdot \bvel\right)
 + \left|{{dp}\over{dt}}\right|_{\rm r}\right.\right.
@@
 &-& \left.\left.{1\over{p^2}}{{\partial }\over{\partial p}}\left(p^2 D_{pp}\right) 
-\right]\right\} - \left(\vec{\nabla}\cdot \vec{\upsilon}\right) f_{\rmn{e}}(p,t)
-- \vec{\nabla}\cdot \vec{F}_\rmn{stream}
+\right]\right\} - \left(\bnabla\bcdot \bvel\right) f_{\rmn{e}}(p,t)
+- \bnabla\bcdot \vec{F}_\rmn{stream}
 \nonumber\\
@@
 $n_{\rmn{e}}(t)=\int d p f_{\rmn{e}}(p,t)$), $d/dt=\partial/\partial
-t+\vec{\upsilon}\cdot \vec{\nabla}$ is the Lagrangian derivative,
-$\vec{\upsilon}$ is the gas velocity, $|dp/dt|$ represents radiative
-(r) and Coulomb (C) losses, $D_{pp}$ is the momentum space diffusion
-coefficient, and $Q_{\rmn{e}}$ denotes the injection rate of primary
-and secondary electrons in the ICM. The $\vec{\nabla}\cdot
-\vec{\upsilon}$ terms represent adiabatic gains and losses \AP{and the
-  $\vec{\nabla}\cdot \vec{F}_\rmn{stream}$ terms represent
-  super-Alfv{\'e}nic CR streaming. For details about $F_\rmn{stream}$
-  please see \citet{wiener13}.} During post-processing of our
-Coma-like cluster simulation, we solve the Fokker-Planck equation over
-a redshift interval from $z=5$ to 0. The simulated cluster undergoes a
-major merger over the last 1-2~Gyrs that \AP{is thought to inject
-  large turbulent eddies. Following \citet{brunetti07,brunetti11}
-  \citep[see also][]{2004ApJ...614..757Y,2015ApJ...800...60M} we
-  assume that about one Gyr after core passage the fields have decayed
-  down to the smallest scales where reacceleration is most efficient
-  ($D_{pp}\sim k_\rmn{cut}$) and the radio halo turns on shortly
-  after. Note that the exact decay time of the turbulens is of minor
-  importance, since the thermal and CR quantities are very similar a
-  few 100 Myrs before and after $z=0$ where we have chosen to evaluate
-  the simulations.}  \sout{injects large turbulent eddies. After about
-  1~Gyr those have decayed down to the scale needed to reaccelerate
-  particles.} This delay naturally explains why giant radio halos are
-only seen in a fraction of all merging clusters. In all our
-calculations we assume that turbulent reacceleration efficiently
-accelerates particles for $\tau_D\sim650$~Myrs (which is roughly the
-cascade time on which turbulence is damped) and that during this
-turbulent phase CR streaming and spatial diffusion can be
-neglected. In our \Mstream model, CR streaming and diffusion are
-incorporated separately during kinematically quiescent times that
-precede the merger. As a result, flat CRp profiles are produced on
-relatively short timescales ($\sim 0.1-0.5$ Gyr). \AP{This allows us
-  to implicitly solve for CR streaming in our calculations, where we
-  adopt a toy model that enforce a flat CRp profile at all quiescent
-  times \citep{wiener13}. We assume that CRs cannot stream
-  significantly past perpendicular $B$-fields at the accretion shock,
-  so that the total number of CRs is conserved within the virial
-  radius during the streaming process. Finally, since streaming is
-  much more efficient for the CRps, we can ignore this effect for the
-  CRes.}
+t+\bvel\bcdot\bnabla$ is the Lagrangian derivative, $\bvel$ is the gas
+velocity, $|dp/dt|$ represents radiative (r) and Coulomb (C) losses,
+$D_{pp}$ is the momentum space diffusion coefficient, and
+$Q_{\rmn{e}}$ denotes the injection rate of primary and secondary
+electrons in the ICM. The $\bnabla\bcdot \bvel$ terms represent
+adiabatic gains and losses \AP{and the $\bnabla\bcdot
+  \vec{F}_\rmn{stream}$ terms represent super-Alfv{\'e}nic CR
+  streaming. For details about $F_\rmn{stream}$ please see
+  \citet{wiener13}.} During post-processing of our Coma-like cluster
+simulation, we solve the Fokker-Planck equation over a redshift
+interval from $z=5$ to 0. The simulated cluster undergoes a major
+merger over the last 1-2~Gyrs that \AP{is thought to inject large
+  turbulent eddies. Following \citet{brunetti07,brunetti11} \citep[see
+    also][]{2004ApJ...614..757Y,2015ApJ...800...60M} we assume that
+  about one Gyr after core passage the fields have decayed down to the
+  smallest scales where reacceleration is most efficient ($D_{pp}\sim
+  k_\rmn{cut}$) and the radio halo turns on shortly after. Note that
+  the exact decay time of the turbulens is of minor importance, since
+  the thermal and CR quantities are very similar a few 100 Myrs before
+  and after $z=0$ where we have chosen to evaluate the simulations.}
+\sout{injects large turbulent eddies. After about 1~Gyr those have
+  decayed down to the scale needed to reaccelerate particles.} This
+delay naturally explains why giant radio halos are only seen in a
+fraction of all merging clusters. In all our calculations we assume
+that turbulent reacceleration efficiently accelerates particles for
+$\tau_D\sim650$~Myrs (which is roughly the cascade time on which
+turbulence is damped) and that during this turbulent phase CR
+streaming and spatial diffusion can be neglected. In our \Mstream
+model, CR streaming and diffusion are incorporated separately during
+kinematically quiescent times that precede the merger. As a result,
+flat CRp profiles are produced on relatively short timescales ($\sim
+0.1-0.5$ Gyr). \AP{This allows us to implicitly solve for CR streaming
+  in our calculations, where we adopt a toy model that enforce a flat
+  CRp profile at all quiescent times \citep{wiener13}. We assume that
+  CRs cannot stream significantly past perpendicular $B$-fields at the
+  accretion shock, so that the total number of CRs is conserved within
+  the virial radius during the streaming process. Finally, since
+  streaming is much more efficient for the CRps, we can ignore this
+  effect for the CRes.}
 
@@
 f_{\rmn{p}}(p,t)\left[ \left|{{dp}\over{dt}}\right|_{\rm C}
-+ \frac{p}{3}\left(\vec{\nabla}\cdot \vec{\upsilon}\right)\right.\right.
++ \frac{p}{3}\left(\bnabla\bcdot \bvel\right)\right.\right.
 \nonumber\\
 &-&\left.\left. {1\over{p^2}}{{\partial }\over{\partial p}}\left(p^2 D_{pp}\right)
-\right]\right\} - \left(\vec{\nabla}\cdot \vec{\upsilon}\right) f_{\rmn{p}}(p,t)
-- \vec{\nabla}\cdot \vec{F}_\rmn{stream}
+\right]\right\} - \left(\bnabla\bcdot \bvel\right) f_{\rmn{p}}(p,t)
+- \bnabla\bcdot \vec{F}_\rmn{stream}
 \nonumber\\
@@
 for $k_0<k<k_\rmn{cut}$. \AP{Here we adopt an injection scale of the
-  turbulens, $k_0= 2\pi/(1~\mbox{Mpc})$, motivated by recent
+  turbulence, $k_0= 2\pi/(1~\mbox{Mpc})$, motivated by recent
   state-of-art simulations
@@
 
-\AP{For reference we show in \ref{tab:timescales} both the thermal
+\AP{For reference we show in Table~\ref{tab:timescales} both the thermal
   quantities and the timescales for CR cooling and (re)acceleration
@@
 \hline
-THERMAL QUANTITIES$^{(1)}$ & & & \\
+thermal quantities$^{(1)}$ & & & \\
 $\rho$ [$10^{-27}$ g cm$^{-3}$] & 3.0 & 1.6 & 0.15 \\
@@
 \hline
-TIMESCALES$^{(1)}$ & & & \\
+timescales$^{(1)}$ & & & \\
 $\tau_\rmn{D}$(\Mprimary)$^{(3)}$ [Gyr] & 0.45 & 0.44 & 0.39 \\
@@
   reacceleration of the merger which we assume to be 650~Myrs
-  long. Note that a fixed $D_\rmn{pp}$ allow us to relate
-  $\tau_\rmn{cl} \propto X_\rmn{tu}^2 \propto k_0$ that ultimately set
+  long. Note that  fixing $D_\rmn{pp}$ allows us to relate
+  $\tau_\rmn{cl} \propto X_\rmn{tu}^2 \propto k_0$ that ultimately sets
   the normalization for $D_\rmn{pp}$. We also exploit the large
@@
 of the central flux to every data point; this flattens the outer
-profile \footnote{Lawrence Rudnick, private communication.}.
+profile\footnote{Lawrence Rudnick, private communication.}.
 Alternatively, this may point to weaknesses in the theoretical
@@
    \begin{center}\Large{\Mprimary:}\\
-     \includegraphics[width=\columnwidth]{figures/sbright.nu.DIIcomp.Pri.g72a.Rad14.2400p.z0.NL.xKR.eb23.eI088.140.v6.eps}
+     \includegraphics[width=\columnwidth]{sbright.nu.DIIcomp.Pri.g72a.Rad14.2400p.z0.NL.xKR.eb23.eI088.140.v6.eps}
    \end{center}
@@
    \begin{center}\Large{\Mstream:}\\
-     \includegraphics[width=\columnwidth]{figures/sbright.nu.DIIcomp.flatCR.g72a.Rad14.2400p.z0.NL.xKR.eb23.eI082.flatCR.140.v6.eps}
+     \includegraphics[width=\columnwidth]{sbright.nu.DIIcomp.flatCR.g72a.Rad14.2400p.z0.NL.xKR.eb23.eI082.flatCR.140.v6.eps}
    \end{center}
@@
   \begin{center}\Large{\Mflatturb:}\\ 
-    \includegraphics[width=\columnwidth]{figures/sbright.nu.DIIcomp.I0.g72a.Rad14.2400p.z0.NL.xKR.eb23.eI067.140.v6.eps}
+    \includegraphics[width=\columnwidth]{sbright.nu.DIIcomp.I0.g72a.Rad14.2400p.z0.NL.xKR.eb23.eI067.140.v6.eps}
   \end{center}
@@
    \begin{center}\Large{\it Brunetti et al. (2012)}:\\
-     \includegraphics[width=\columnwidth]{figures/sbright.nu.DIIcomp.Brunetti.g72a.Rad14.2400p.z0.NL.xKR.eb23.140.v6.eps}
+     \includegraphics[width=\columnwidth]{sbright.nu.DIIcomp.Brunetti.g72a.Rad14.2400p.z0.NL.xKR.eb23.140.v6.eps}
    \end{center}
@@
 \begin{figure*}
-  \includegraphics[width=1.0\columnwidth]{figures/sync.spec.pri.g72a.140.v6.eps}
-  \includegraphics[width=1.0\columnwidth]{figures/sync.spec.sec.g72a.140.v6.eps}
+  \includegraphics[width=1.0\columnwidth]{sync.spec.pri.g72a.140.v6.eps}
+  \includegraphics[width=1.0\columnwidth]{sync.spec.sec.g72a.140.v6.eps}
   \caption{Radio synchrotron spectra. Lines are derived from
@@
 
-\bibliography{bibtex/paper}
-\bibliographystyle{mn2e}
+\bibliography{paper}
+\bibliographystyle{mnras}
 

### 2016-04-06 paper.tex
intro modified

@@
 inelastic (hadronic) CR proton interactions with protons of the
-ambient thermal ICM
+ambient thermal ICM, which generates pions that eventually decay into
+electrons and positrons, depending of the charge of the initial pion
 (\citealp{1980ApJ...239L..93D,1999APh....12..169B,2001ApJ...562..233M,
@@
 distribution is not predicted by cosmological simulations \cite[see
-  also][]{pinzke10,2014MNRAS.439.2662V}. \CP{Explain Fig 1: why is
-  simulated profile steep? transport, secondaries, \ldots}
+  also][]{pinzke10,2014MNRAS.439.2662V}. \CP{If CRps are predominantly
+  advected with the cluster plasma, their distribution will be peaked
+  towards the cluster center and shows a similar characteristics as
+  the thermal plasma. As a consequence, the distribution of secondary
+  electrons and the resulting radio synchrotron emission is also
+  peaked since the hadronic reaction is a two-body scattering process
+  (see Fig.~Fig.~\ref{fig:Edens}). Hence, the simulated emission falls
+  short of the observed extended and flat radio profile of the Coma
+  cluster.}
 
@@
 characteristics is highly constraining, and has the potential to teach
-us much about the origin of CRps/CRes in clusters.  \CP{We use our
-  simuations to generate distribution function of seed population,
-  resolve injection and loss processes for CRs and integrate the
-  Fokker-Planck equation along Lagrangian particle trajectories to
-  obtain a momentum spectrum of CRs. However, we assume a simplified
-  turbulent model. So our approach is orthogonal (and complementary)
-  to e.g. Miniati 2015.}  \AP{For both the turbulence and magnetic
-  fields we adopt stationary models, parameterized in terms of thermal
-  quantities derived from our simulations.}
+us much about the origin of CRps/CRes in clusters.  \CP{In this work,
+  we use our hydrodynamical zoom simulations of galaxy clusters in a
+  cosmological setting to follow the distribution functions of seed
+  CRp and CRe population and integrate the Fokker-Planck equation of
+  CR transport along Lagrangian particle trajectories. We resolve
+  injection at structure formation shocks, account for various loss
+  processes of CRs, and -- most importantly -- model second-order
+  Fermi acceleration by CR interactions with magnetised
+  turbulence. However, we assume a simplified and stationary model for
+  magnetic fields and turbulence. We do not account for the
+  time-varying energy density in compressible waves, which are thought
+  to be necessary for the acceleration process
+  \citep{brunetti07,brunetti11}, as the cluster merger proceeds.  So
+  our approach is orthogonal (and complementary) to e.g.,
+  \citealp{2015ApJ...800...60M}. This enables us to vary parameters
+  associated with the unknown continuation of magneto-hydrodynamical
+  turbulence below the MHD scale and the overall amplitude of
+  compressible waves.}
 
@@
 We incorporate momentum diffusion for electrons and protons from
-transit-time-damping (TTD) resonance with compressible
-magneto-hydrodynamic (MHD) turbulence, to model Fermi-II
-reacceleration \citep{brunetti07,brunetti11}. The TTD resonance
-requires the wave frequency $\omega=k_\parallel\upsilon_\parallel$,
-where $k_\parallel$ and $\upsilon_\parallel$ are the parallel
-(projected along the magnetic field) wavenumber and particle velocity,
-respectively. This implies that the particle transit time across the
-confining wave region matches the wave period,
-$\lambda_{\parallel}/v_{\parallel}=T$. Note, the CRs' gyroradius does
-not enter the resonance condition. Hence the CRs that are in resonance
-with compressible waves experience Fermi-II acceleration
-irrespectively of the length scale of the perturbation.
+transit-time-damping (TTD) resonance with compressible MHD turbulence,
+to model Fermi-II reacceleration \citep{brunetti07,brunetti11}. The
+TTD resonance requires the wave frequency
+$\omega=k_\parallel\upsilon_\parallel$, where $k_\parallel$ and
+$\upsilon_\parallel$ are the parallel (projected along the magnetic
+field) wavenumber and particle velocity, respectively. This implies
+that the particle transit time across the confining wave region
+matches the wave period, $\lambda_{\parallel}/v_{\parallel}=T$. Note,
+the CRs' gyroradius does not enter the resonance condition. Hence the
+CRs that are in resonance with compressible waves experience Fermi-II
+acceleration irrespectively of the length scale of the perturbation.
 

### 2016-04-08 paper.tex
Added files via upload

@@
 \newcommand{\bnabla}{\ensuremath{\boldsymbol{\nabla}}}
+\newcommand\eb{\epsilon_\rmn{B}}
 
@@
 
+\AP{We use a simple test-particle model for the CR acceleration and
+  injection, where each shock inject CRs that trace a power-law in
+  momentum,
+  \begin{equation}
+    f(p,t) = C(t)\,p^{\alpha_\rmn{inj}}\,,
+  \end{equation}
+  determined by the normalization $C(t)$ and the spectral index
+  $\alpha_\rmn{inj}=\frac{(\gamma_\rmn{ad}+1)\mathcal{M}^2}{(\gamma_\rmn{ad}-1)\mathcal{M}^2+2}$
+  that depends on the adiabatic index $\gamma_\rmn{ad} = 5/3$ and the
+  Mach number of the shock $\mathcal{M}$. It is given by the ratio of
+  the upstream velocity ($u_2$) and the sound speed ($c_s$). The CR
+  number density and CR energy density are derived from $n_\rmn{CR} =
+  \int_{p_\rmn{inj}}^\infty \dd p\, f(p)$ and $\epsilon_\rmn{CR} =
+  \int_{p_\rmn{inj}}^\infty \dd p\, f(p) \,T(p)$, respectively, where
+  $T(p) = (\sqrt{1+p^2} -1)\, m\,c^2$ is the kinetic energy of a
+  particle with momentum $p$. We adopt a fit to Monte Carlo
+  simulations of the thermal leakage process that relates the momentum
+  of injected protons ($p_\rmn{inj}$) to the thermal energy
+  ($p_\rmn{th}$) of the shocked plasma \citep{kang11}:
+  \begin{eqnarray}
+  \label{eq:qinj}
+  p_\rmn{inj} &=& x_\rmn{inj} p_\rmn{th} = x_\rmn{inj} \sqrt{\frac{2 \,k T_2}{m c^2}}\,, \nonumber \\
+  \rmn{where}\quad x_\rmn{inj} &\approx& 1.17 \frac{u_2}{p_{\rmn th}\,c} \left(1+
+  \frac{1.07}{\epsilon_B}\right) \left(\frac{\mathcal{M}}{3}\right)^{0.1}\,.
+  \end{eqnarray}
+Here $\eb = B_0/B_{\perp}$, $B_0$ is the amplitude of the downstream
+MHD wave turbulence, and $B_{\perp}$ is the magnetic field along the
+shock normal. The physical range of $\eb$ is quite uncertain due to
+complex plasma interactions. In this paper, we adopt $\eb = 0.23$,
+which we will later see corresponds to a conservative maximum energy
+acceleration efficiency for protons of $10\%$. To derive the
+acceleration efficiency, $\zeta_{\rmn inj}$, we first have to infer the
+particle injection efficiency, which is the fraction of downstream
+thermal gas particles which experience diffusive shock acceleration
+\citep[for details see ][]{pinzke13},
+\begin{equation}
+  \label{eq:eta}
+  \eta_\rmn{CR,lin} =
+  \frac{4}{\sqrt{\upi}}\,\frac{x_\rmn{inj}^3}{\alpha_\rmn{inj}-1}\,
+  \rmn{e}^{-x_\rmn{inj}^2}.
+\end{equation}
+The particle injection efficiency is a strong function of
+$x_\rmn{inj}$ that depends on both $\mathcal{M}$ and $\eb$. The
+energy density of CRs that are injected and accelerated at the shock
+(neglecting the CR back reaction on the shock) is given by
+\begin{equation}
+\label{eq:CR_energy} 
+  \Delta\epsilon_\rmn{CR,lin} =
+  \eta_\rmn{CR,lin}(\mathcal{M})\,T_\rmn{CR}(\mathcal{M},p_\rmn{inj})\,n_\rmn{th}(T_2),
+\end{equation}
+and the CR energy injection and acceleration efficiency is:
+\begin{equation}
+  \zeta_\rmn{lin} =
+  \frac{\Delta\epsilon_\rmn{CR,lin}}{\Delta\epsilon_\rmn{diss}},
+   \quad\mbox{where}\quad
+  \Delta\epsilon_\rmn{diss} = \epsilon_\rmn{th2} - \epsilon_\rmn{th0}\,\left(\frac{\rho_2}{\rho_0}\right)^{\gamma_\rmn{ad}}\,.
+\label{eqn:energy_frac}  
+\end{equation}
+The dissipated energy density in the downstream regime,
+$\Delta\epsilon_\rmn{diss}$, is given by the difference of the thermal
+energy densities in the pre- and post-shock regimes, corrected for the
+adiabatic energy increase due to gas compression.}
+
+\AP{We limit the acceleration efficiency to $\zeta_{\rmn max}$ by
+  steepening the spectral index of the injected population
+  $\alpha_\rmn{inj}$ to $\alpha_\rmn{sub}$ so that $\zeta_{\rmn lin}
+  \leq \zeta_{\rmn max}$ is always fulfilled. The slope
+  $\alpha_\rmn{inj}$ impact $\zeta_{\rmn inj}$ via the mean energy per
+  particle given by $T_\rmn{CR} = \epsilon_\rmn{CR}/n_\rmn{CR}$. This
+  procedure conserves energy and is motivated by models of non-linear
+  shock acceleration where a sub-shock with a lower compression ratio
+  (and hence steeper spectral index) forms
+  \citep[e.g.,][]{2000ApJ...540..292E}. Given our assumed $\eb=0.23$,
+  we find that for strong shocks where $\alpha \lesssim 2.3$ the
+  spectral slope is steepened by a maximum of $\sim 10$ per cent in
+  low temperature regimes ($kT\sim 0.1$~keV), while the steepening is
+  much smaller for high temperature regimes ($kT\sim 10$~keV) that are
+  more relevant for clusters. Since $p_{\rm inj}$ remains fixed, so
+  does the CR number density $n_\rmn{CR}$. Hence we can solve for the
+  renormalized normalization constant $C_\rmn{sub}$ using $n_\rmn{CR}$
+  and Eqn.~\ref{eq:eta}:
+\begin{equation}
+  \label{eq:Cp_sub}
+  C_\rmn{sub}=\eta_\rmn{CR,lin}\,(\alpha_\rmn{sub}-1)\,p_\rmn{inj}^{\alpha_\rmn{sub}-1}\,,
+\end{equation}
+where the new distribution function is given by $f(p,t)= C_\rmn{sub}
+p^{-\alpha_\rmn{sub}}$.} We set an upper limit on the ratio of
+accelerated proton-to-dissipated energy in the downstream of strong
+shocks that varies from $\zeta_{\rmn max} \sim 1-10\%$, depending on
+the adopted model (for more details, see Section \ref{sec:results}).
+
 In our Galaxy, the CRe-to-CRp ratio at a few GeV is $K_{\rmn{ep}} \sim
@@
 depending on magnetic geometry, $K_{\rmn{ep}}$ could be either larger
-or smaller. In this work we use a simple test-particle model for the
-CRp acceleration, where we adopt a fit to Monte Carlo simulations of
-the thermal leakage process that relates the momentum of injected
-protons to the thermal energy of the shocked plasma \citep{kang11}. We
-set an upper limit on the ratio of accelerated proton-to-dissipated
-energy in the downstream of strong shocks that varies from 1-10\%,
-depending on the adopted model (for more details, see Section
-\ref{sec:results}). In order not to violate energy conservation with a
+or smaller. \sout{In order not to violate energy conservation with a
   fixed limit for the acceleration efficiency, we steepen the spectral
-index of the accelerated CRps at the limit \citep{pinzke13}, which
-mimics the non-linear CR modification of the shock
-\citep{ellison00}. For weak shocks the efficiency is a factor 10-100
-lower and well below the limit. Some observations of radio relics
+  index of the accelerated CRps at the limit %\citep{pinzke13}
+, which  mimics the non-linear CR modification of the shock
+  %\citep{ellison00}
+  . For weak shocks the efficiency is a factor 10-100
+  lower and well below the limit.} Some observations of radio relics
 suggest high values of $K_{\rmn{ep}}$, due to the absence of gamma-ray

### 2016-04-16 paper.tex
restructured
Added files via upload

@@
 thermal plasma whose energy density declines steeply with radius. In
-\AP{the left panel of} Fig.~\ref{fig:Edens} we show that such a
+the left panel of Fig.~\ref{fig:Edens} we show that such a
 distribution is not predicted by cosmological simulations \cite[see
-  also][]{pinzke10,2014MNRAS.439.2662V}. \CP{If CRps are predominantly
+  also][]{pinzke10,2014MNRAS.439.2662V}. If CRps are predominantly
 advected with the cluster plasma, their distribution will be peaked
-  towards the cluster center and shows a similar characteristics as
-  the thermal plasma. As a consequence, the distribution of secondary
-  electrons and the resulting radio synchrotron emission is also
-  peaked since the hadronic reaction is a two-body scattering process
-  (see Fig.~Fig.~\ref{fig:Edens}). Hence, the simulated emission falls
-  short of the observed extended and flat radio profile of the Coma
-  cluster.}
+towards the cluster center and shows a similar characteristics as the
+thermal plasma. As a consequence, the distribution of secondary
+electrons and the resulting radio synchrotron emission is also peaked
+since the hadronic reaction is a two-body scattering process (see
+Fig.~Fig.~\ref{fig:Edens}). Hence, the simulated emission falls short
+of the observed extended and flat radio profile of the Coma cluster.
 
@@
   \includegraphics[width=1.0\columnwidth]{fCR.radius.coma.g72a.Rad14.2400p.z0.NL.xKR.eb23.eI067.DII.140.v6.eps}
-  \includegraphics[width=1.0\columnwidth]{turb_profile_ratio_tot.eps}
-  \caption{Left: spatial distribution of CRp energy density in the
-    Coma cluster. The red dash-dotted line shows the required
-    distribution of seed CRps that generate secondary electrons via
-    p-p collisions required to reproduce Coma radio brightness
-    observations after Fermi-II reacceleration \citep{brunetti12}. The
-    blue solid line shows the distribution of fossil CRps found in
-    cosmological simulations, which disagrees with the required
-    profile. \AP{To better compare the two models in this figure, we
-      normalize the required distribution of CRps by fixing the total
-      CRp energy $E_\rmn{CR}$ to 0.3 percent of the total thermal
-      energy, consistent with observations
-      \citep{2014ApJ...787...18A,2012ApJ...757..123A}. Right: the
-      ratio of turbulent-to-thermal energy densities (solid lines) and
-      cumulative energies (dotted lines) in our three models. The
-      energy densities are parametrized as $\epsilon_\rmn{turb}
-      \propto \epsilon_\rmn{th}^{(\alpha_{\rmn{tu}}+1)/2}/T^{1/4}$ and
-      normalized such that the total turbulent energy in compressible
-      modes $E_\rmn{turb}$ for each scenario makes up about 6\% of the
-      total thermal energy $E_\rmn{th}$ inside the radio halo
-      ($R_\rmn{RH}\approx0.6R_{200}$). The turbulent profiles explore
-      the uncertainty in the cluster turbulence and are motivated by
-      the cosmological simulation in
-      \citep{2009ApJ...705.1129L,2010ApJ...725.1452S,2011A&A...529A..17V}.}}
+  \caption{Spatial distribution of CRp energy density in the Coma
+    cluster. The red dash-dotted line shows the required distribution
+    of seed CRps that generate secondary electrons via p-p collisions
+    required to reproduce Coma radio brightness observations after
+    Fermi-II reacceleration \citep{brunetti12}. The blue solid line
+    shows the distribution of fossil CRps found in cosmological
+    simulations, which disagrees with the required profile. To better
+    compare the two models in this figure, we normalize the required
+    distribution of CRps by fixing the total CRp energy $E_\rmn{CR}$
+    to 0.3 percent of the total thermal energy, consistent with
+    observations \citep{2014ApJ...787...18A,2012ApJ...757..123A}.}
   \label{fig:Edens}
@@
 characteristics is highly constraining, and has the potential to teach
-us much about the origin of CRps/CRes in clusters.  \CP{In this work,
-  we use our hydrodynamical zoom simulations of galaxy clusters in a
-  cosmological setting to follow the distribution functions of seed
-  CRp and CRe population and integrate the Fokker-Planck equation of
-  CR transport along Lagrangian particle trajectories. We resolve
-  injection at structure formation shocks, account for various loss
-  processes of CRs, and -- most importantly -- model second-order
-  Fermi acceleration by CR interactions with magnetised
-  turbulence. However, we assume a simplified and stationary model for
-  magnetic fields and turbulence. We do not account for the
-  time-varying energy density in compressible waves, which are thought
-  to be necessary for the acceleration process
-  \citep{brunetti07,brunetti11}, as the cluster merger proceeds.  So
-  our approach is orthogonal (and complementary) to e.g.,
+us much about the origin of CRps/CRes in clusters.  In this work, we
+use our hydrodynamical zoom simulations of galaxy clusters in a
+cosmological setting to follow the distribution functions of seed CRp
+and CRe population and integrate the Fokker-Planck equation of CR
+transport along Lagrangian particle trajectories. We resolve injection
+at structure formation shocks, account for various loss processes of
+CRs, and -- most importantly -- model second-order Fermi acceleration
+by CR interactions with magnetised turbulence. However, we assume a
+simplified and stationary model for magnetic fields and turbulence. We
+do not account for the time-varying energy density in compressible
+waves, which are thought to be necessary for the acceleration process
+\citep{brunetti07,brunetti11}, as the cluster merger proceeds.  So our
+approach is orthogonal (and complementary) to e.g.,
 \citealp{2015ApJ...800...60M}. This enables us to vary parameters
@@
 turbulence below the MHD scale and the overall amplitude of
-  compressible waves.}
+compressible waves.
 
@@
 seed electrons and compare to observations in the Coma cluster. For
-the most part, we adopt parameters that are used in previous work:
-\AP{for details, see \citep[][ turbulent
-    spectrum]{brunetti07,brunetti11}, \citep[][ injection scale of
-    turbulens]{2015ApJ...800...60M}, \citep[][ energy density of
+the most part, we adopt parameters that are used in previous work: for
+details, see \citep[][ turbulent spectrum]{brunetti07,brunetti11},
+\citep[][ injection scale of turbulens]{2015ApJ...800...60M},
+\citep[][ energy density of
   turbulence]{2009ApJ...705.1129L,2010ApJ...725.1452S,2011A&A...529A..17V},
-  for CR acceleration in shocks, \citep[][ in particular
-    $K_{\rmn{ep}}$, acceleration efficiency]{pinzke13}, and for
-  cosmological simulations, \citep[][ i.e., shock history, temperature
-    profile, density profile, magnetic field profile]{pinzke10}.} All
-these parameters are uncertain, and could potentially change our
+for CR acceleration in shocks, \citep[][ in particular $K_{\rmn{ep}}$,
+  acceleration efficiency]{pinzke13}, and for cosmological
+simulations, \citep[][ i.e., shock history, temperature profile,
+  density profile, magnetic field profile]{pinzke10}. All these
+parameters are uncertain, and could potentially change our
 predictions. We leave exploration of parameter space and the
@@
 well as secondary CRes produced in p-p collisions)
-\citep{2007MNRAS.378..385P,pfrommer08,pinzke10,pinzke13}. In this
+\citep{2007MNRAS.378..385P,pfrommer08,pinzke10,pinzke13}.
+
+[explain overall picture, $\tau_\rmn{d}$ vs. $\tau_{\rmn{cl}}$]
+
+\subsection{Cosmic ray transport}
+As previously noted, secondaries produced by shock accelerated CRp
+have the wrong spatial profile to explain RH observations; because
+they arise from a two body process, they are too centrally
+concentrated. They also produce $\gamma$-ray emission in excess of
+Fermi-LAT upper limits
+\citep{2012ApJ...757..123A,brunetti12,2014ApJ...787...18A}. However,
+if CRps stream in the ICM, then their spatial profile could
+potentially flatten sufficiently \citep{ensslin11,wiener13}. This
+scenario is very attractive: it generates seed electrons with the
+right spatial footprint, and by removing CRps from the core, obeys
+gamma-ray constraints. Turbulence plays two opposing roles:
+Alfv{\'e}nic turbulence damps waves generated by the CR streaming
+instability \citep{yan02,farmer04}, thus reducing self-confinement;
+but compressible fast modes scatter CRs directly. Turbulent damping is
+still efficient for highly subsonic conditions \citep{wiener13}, while
+we assume compressible fast modes to only provide effective spatial
+confinement during the periods of transonic, highly super-Alfv{\'e}nic
+($M_{\rm A} \sim 5$) turbulence associated with mergers. Thus, CRs can
+stream out when the cluster is kinematically quiescent. Furthermore,
+even Alfv{\'e}nic streaming timescales are relatively short
+\cite[$\sim 0.1-0.5$ Gyr;][]{wiener13} compared to the timescale on
+which the CRp population is built up. Based on these findings, we
+adopt a toy model for our \Mstream scenario in which CR streaming
+instantaneously produces flat CRp profiles. \sout{We assume that CRs cannot
+stream significantly past perpendicular $B$-fields at the accretion
+shock, so that the total number of CRs is conserved within the galaxy
+cluster during the streaming process.}
+
+Given a seed population of CRs, we adopt essentially the same set of
+plasma physics assumptions as the reacceleration model for RHs
+\citep{brunetti07,brunetti11}. We solve the isotropic, gyro-phase
+averaged Fokker-Planck equation (via a Crank-Nicholson scheme) for the
+time evolution of the CRe distribution in the Lagrangian frame
+\citep{brunetti07,brunetti11}:
+\begin{eqnarray}
+{{d f_{\rmn{e}}(p,t)}\over{d t}} &\!=&
+\frac{\partial}{\partial p}
+\left\{
+f_{\rmn{e}}(p,t)\left[
+\left|{{dp}\over{dt}}\right|_{\rm C} 
++ \frac{p}{3}\left(\bnabla\bcdot \bvel\right)
++ \left|{{dp}\over{dt}}\right|_{\rm r}\right.\right.
+\nonumber\\
+&-& \left.\left.{1\over{p^2}}{{\partial }\over{\partial p}}\left(p^2 D_{pp}\right) 
+\right]\right\} - \left(\bnabla\bcdot \bvel\right) f_{\rmn{e}}(p,t)
+- \bnabla\bcdot \vec{F}_\rmn{stream}
+\nonumber\\
+&+& {{\partial^2 }\over{\partial p^2}}
+\left[
+D_{pp} f_{\rmn{e}}(p,t) \right]+ Q_{\rmn{e}}\left[p,t;f_{\rmn{p}}(p,t)\right]   \, .
+\label{elettroni}
+\end{eqnarray}
+Here $f_{\rmn{e}}$ is the one-dimensional distribution in position $x$
+(suppressed for clarity), momentum $p$ and time $t$ (which is
+normalized such that the number density is given by
+$n_{\rmn{e}}(t)=\int d p f_{\rmn{e}}(p,t)$), $d/dt=\partial/\partial
+t+\bvel\bcdot\bnabla$ is the Lagrangian derivative, $\bvel$ is the gas
+velocity, $|dp/dt|$ represents radiative (r) and Coulomb (C) losses,
+$D_{pp}$ is the momentum space diffusion coefficient, and
+$Q_{\rmn{e}}$ denotes the injection rate of primary and secondary
+electrons in the ICM. The $\bnabla\bcdot \bvel$ terms represent
+adiabatic gains and losses and the $\bnabla\bcdot
+\vec{F}_\rmn{stream}$ terms represent super-Alfv{\'e}nic CR
+streaming. For details about $F_\rmn{stream}$ please see
+\citet{wiener13}. During post-processing of our Coma-like cluster
+simulation, we solve the Fokker-Planck equation over a redshift
+interval from $z=5$ to 0. The simulated cluster undergoes a major
+merger over the last 1-2~Gyrs that is thought to inject large
+turbulent eddies. Following \citet{brunetti07,brunetti11} \citep[see
+  also][]{2004ApJ...614..757Y,2015ApJ...800...60M} we assume that
+about one Gyr after core passage the fields have decayed down to the
+smallest scales where reacceleration is most efficient ($D_{pp}\sim
+k_\rmn{cut}$) and the radio halo turns on shortly after. Note that the
+exact decay time of the turbulens is of minor importance, since the
+thermal and CR quantities are very similar a few 100 Myrs before and
+after $z=0$ where we have chosen to evaluate the simulations. This
+delay naturally explains why giant radio halos are only seen in a
+fraction of all merging clusters. In all our calculations we assume
+that turbulent reacceleration efficiently accelerates particles for
+$\tau_\rmn{cl}\sim650$~Myrs (which is roughly the cascade time on which
+turbulence is damped) and that during this turbulent phase CR
+streaming and spatial diffusion can be neglected. In our \Mstream
+model, CR streaming and diffusion are incorporated separately during
+kinematically quiescent times that precede the merger. As a result,
+flat CRp profiles are produced on relatively short timescales ($\sim
+0.1-0.5$ Gyr). This allows us to implicitly solve for CR streaming in
+our calculations, where we adopt a toy model that enforce a flat CRp
+profile at all quiescent times \citep{wiener13}. We assume that CRs
+cannot stream significantly past perpendicular $B$-fields at the
+accretion shock, so that the total number of CRs is conserved within
+the virial radius during the streaming process. Finally, since
+streaming is much more efficient for the CRps, we can ignore this
+effect for the CRes.
+
+The time evolution of the spectral energy distribution of CRps,
+$f_{\rmn{p}}$, is similarly given by:
+\begin{eqnarray}
+{{d f_{\rmn{p}}(p,t)}\over{d t}} &=&
+{{\partial }\over{\partial p}}
+\left\{
+f_{\rmn{p}}(p,t)\left[ \left|{{dp}\over{dt}}\right|_{\rm C}
++ \frac{p}{3}\left(\bnabla\bcdot \bvel\right)\right.\right.
+\nonumber\\
+&-&\left.\left. {1\over{p^2}}{{\partial }\over{\partial p}}\left(p^2 D_{pp}\right)
+\right]\right\} - \left(\bnabla\bcdot \bvel\right) f_{\rmn{p}}(p,t)
+- \bnabla\bcdot \vec{F}_\rmn{stream}
+\nonumber\\
+&+& {{\partial^2 }\over{\partial p^2}}
+\left[ D_{pp} f_{\rmn{p}}(p,t) \right] - {{f_{\rmn{p}}(p,t)}\over{\tau_{\rm had}(p)}}
++ Q_{\rmn{p}}(p,t)\, ,
+\label{eq:FP_p}
+\end{eqnarray}
+where $Q_{\rmn{p}}(p,t)$ denotes the injection rate of shock
+accelerated CRps as a function of momentum $p$ and time $t$, and
+$\tau_{\rm had}$ is the timescale of hadronic losses that produce
+pions via CRp collisions with thermal protons of the ICM
+\cite[e.g.][]{brunetti11}.
+
+\subsection{Turbulent reacceleration}
+
+We incorporate momentum diffusion for electrons and protons from
+transit-time-damping (TTD) resonance with compressible MHD turbulence,
+to model Fermi-II reacceleration \citep{brunetti07,brunetti11}. The
+TTD resonance requires the wave frequency
+$\omega=k_\parallel\upsilon_\parallel$, where $k_\parallel$ and
+$\upsilon_\parallel$ are the parallel (projected along the magnetic
+field) wavenumber and particle velocity, respectively. This implies
+that the particle transit time across the confining wave region
+matches the wave period, $\lambda_{\parallel}/v_{\parallel}=T$. Note,
+the CRs' gyroradius does not enter the resonance condition. Hence the
+CRs that are in resonance with compressible waves experience Fermi-II
+acceleration irrespectively of the length scale of the perturbation.
+
+However, the resonance changes the component of particle momentum
+parallel to seed magnetic fields, which over time leads to increasing
+anisotropy in the particle distribution that decreases the efficiency
+of reacceleration with time. As in \citet{brunetti11}, we assume that
+there exists a mechanism---such as the firehose instability---that
+isotropizes the CR distribution function at the gyroscale and on the
+reacceleration time scale, which ensures sustained efficient
+reacceleration with time. The particle pitch-angle averaged
+momentum-diffusion coefficient of isotropic particles that couple to
+fast magnetosonic modes via TTD resonance is \citep[][ Eqn. 47]{brunetti07}:
+\begin{eqnarray}
+  D_{pp}(p,t) = \frac{\pi}{16} \frac{p^2}{c\,\rho}
+  \left\langle\frac{\beta |B_k|^2}{16 \pi \,W}\right\rangle
+  I_\theta
+  \int_{k_\rmn{cut}}\mathcal{W}(k)k\,d k\,,
+\label{eq:dpp}
+\end{eqnarray}
+where $\beta$ is the thermal-to-magnetic pressure ratio, and $c$
+is the speed of light. The energy density $W$ of a mode in a
+magnetized plasma stems from both electromagnetic fields and resonant
+particles. For a high-$\beta$ plasma, the pitch angle averaged ratio of
+beta-weighted magnetic-to-total energy density saturates to $\langle\beta
+|B_k|^2/2W\rangle\approx 10^{1.4}$ (see Figure 2 in
+\citealt{brunetti07}). The pitch angle of the CR momentum with the
+magnetic field orientation is given by $\theta$, and
+\begin{equation}
+  \label{eq:I_theta}
+  I_\theta=\int_0^{\arccos(\Vph/c)} d\theta {\frac{ \sin^3 \theta }{
+    |\cos \theta | }}
+\left[1+\left(\frac{\Vph}{c\,\cos{\theta}}\right)^2\right]^2.
+\end{equation}
+Here $V_\rmn{ph}$ is the phase velocity of the fast magnetosonic waves
+given approximately by the sound speed, $\Vph \sim c_\rmn{s}$. For a
+sound speed typical for the ICM of 1000~km/s, $I_\theta\approx5$. As
+in \cite{brunetti07}, we initially assume that the velocity of
+turbulent eddies is $V_0\approx 0.47 c_\rmn{s}$ throughout the
+cluster. This gives a turbulent acceleration time scale, $\tau_{D} =
+p^2/4D_{pp}$, that is typically few 100 Myrs in the ICM (see
+Tab.~\ref{tab:timescales} for more details).
+
+We focus on a scenario where the turbulence is injected at the largest
+scale that is driven by the merging cluster and accreting matter. The
+diffusion equation for isotropic MHD turbulence in $k$--space is given
+by
+\begin{eqnarray}
+&{{\partial {\mathcal W}(k,t) }\over{\partial t}}
+=
+{{\partial}\over{\partial k}}
+\left[
+k^2 D_{kk}
+{{\partial}\over{\partial k}}
+\left( {{ {\mathcal W}(k,t) }\over{k^2}} \right)
+\right]
+- \sum_i \Gamma_i (k,t) {\mathcal W}(k,t)
++ I(k,t)\nonumber\\
+&
+\label{modes_kinetic}
+\end{eqnarray}
+where we assume that the volumetric injection rate of turbulence
+$I(k,t)$ is constant over time with a fixed rate $I_0$ so that $I(k,t)
+\equiv I(k) = I_0\,\delta (k - k_o)$. The different damping terms are
+given by $\Gamma_i(k,t)$ and $D_{kk}$ is the wave--wave diffusion
+coefficient of magnetosonic waves in the $k$--space represented by
+\begin{equation}
+  \label{eq:Dkk}
+  D_{kk} \approx \Vph k^4
+  \left(\frac{\mathcal{W}(k)}{\rho\,\Vph^2}\right)\,.
+\end{equation}
+
+We adopt a simplified isotropic MHD turbulent spectrum based on
+Kraichnan's picture for the fast modes per elemental range $dk$ of the
+form
+\begin{equation}
+  \label{eq:Wk}
+  \mathcal{W}(k) =
+\sqrt{2/7\,I_0\,\rho\,\langle \Vph \rangle}\,k^{-3/2},
+\end{equation}
+for $k_0<k<k_\rmn{cut}$. Here we adopt an injection scale of the
+turbulence, $k_0= 2\pi/(1~\mbox{Mpc})$, motivated by recent
+state-of-art simulations
+\citep{2009A&A...504...33V,2011A&A...529A..17V,2015ApJ...800...60M}.
+The profile of injected turbulence is also highly uncertain, however
+we assume it correlates to the thermal energy density to some power of
+the merging clusters. Hence we assume volumetric injection rate of
+turbulent energy, $I_0\propto \epsilon_\rmn{th}^{\alpha_\rmn{tu}}$,
+and determine the normalization by requiring that the turbulent energy
+in compressible modes $E_\rmn{turb}=\int \int \mathcal{W}(k) \rmn{d}k
+\rmn{d}V = X_\rmn{tu} E_\rmn{th}$, where $E_\rmn{th}$ is the total
+thermal energy. We adopt a turbulent energy ratio\footnote{Simulations
+  show that the compressible modes contribute a factor $0.2-0.4$ to
+  the total turbulent energy
+  \citep{2013ApJ...771..131B,2015ApJ...800...60M}. Furthermore, the
+  total turbulent energy is typically $10-30$\% of the thermal energy
+  in a cluster which is in agreement with our adopted value of
+  $X_\rmn{tu}$.}  $X_\rmn{tu}=0.06$ within the radio halo. In this
+work we investigate different spatial models for injected
+turbulence. With the above choice of normalization, the turbulent
+energy density becomes $\epsilon_\rmn{turb} \propto
+\epsilon_\rmn{th}^{(\alpha_\rmn{tu}+1)/2}/T^{1/4}$, where $T$ is the
+temperature of the gas, $\alpha_\rmn{tu}= 0.67$ for \Mflatturb,
+$\alpha_\rmn{tu}= 0.82$ for \Mstream, and $\alpha_\rmn{tu}= 0.88$ for
+\Mprimary. Note that in previous work on the Coma cluster,
+$\epsilon_\rmn{turb} \propto \epsilon_\rmn{th}$ was adopted which
+roughly corresponds to $\alpha_\rmn{tu}= 1$ \citep{brunetti12} and
+together with the different distributions for seed CRes constitute the
+main differences compared to our work. Our flatter turbulent profiles
+are motivated by fits to cosmological simulations
+\citep{2009ApJ...705.1129L,2010ApJ...725.1452S,2011A&A...529A..17V,2012ApJ...758...74B}
+and the range indicates uncertainties of the turbulent profile in
+Coma. Future observations (by Astro-H) and simulations will help to
+clarify this issue. Provided dissipation of turbulence in the ICM is
+collisionless, turbulent cascades of compressible modes become
+suppressed when thermal and relativistic particles resonantly interact
+with magnetosonic waves via TTD on a timescale $\Gamma^{-1}$ that
+approaches the cascading timescale given by $\tau_{kk} \approx
+k^2/D_{kk}$. Thus, the cascade is suppressed for wave numbers above
+\begin{equation}
+\label{eq:kc}
+  k_\rmn{cut} \approx \frac{81}{14} \frac{I_0}{\rho \langle \Vph \rangle}
+  \left(\frac{\langle\sum_i \Gamma_i(k,\theta)\rangle}{k}\right)^{-2}\,,
+\end{equation}
+where $2\pi/k_\rmn{cut}\sim 0.1-1$~kpc in the ICM. This constitutes an
+effective mean free path for CRs, unless plasma instabilities can
+mediate interactions between turbulence and particles on smaller
+scales \citep{brunetti11}. In this work we only consider damping of
+the turbulence via TTD due to thermal electrons, and neglect
+subdominant damping with thermal protons and relativistic particles
+(conversely, the turbulence has important effects on the
+reacceleration of CRs). The latter will be subdominant in the ICM for
+a CR-to-thermal energy density ratio $\lesssim 10 \%$
+\citep{brunetti07}, which is always satisfied in our models. The
+azimuthally averaged turbulent damping rate from thermal electrons
+\citep{brunetti07} in a high-$\beta$ plasma is
+\begin{equation}
+\label{eq:Gamma_e}
+\langle\Gamma_{\rmn{e}}\rangle \approx \langle k\,\Vph\,\sqrt{3\pi
+  x/20}\exp(-5x/3)\sin^2{\theta}\rangle\approx 0.0435k\,\Vph, 
+\end{equation}
+where $x=(m_{\rmn{e}}/m_{\rmn{p}})/\cos^2{\theta}$. To compute the
+synchrotron surface brightness profiles, we use the profile of the
+magnetic field strengths derived from Faraday rotation observations of
+Coma \citep{bonafede10} in combination with the density profile
+derived from X-ray measurements \citep{1992A&A...259L..31B}.
+
+\begin{figure*}
+  \includegraphics[width=1.0\columnwidth]{turb_profile_ratio_tot.eps}
+  \caption{The ratio of turbulent-to-thermal energy densities (solid
+    lines) and cumulative energies (dotted lines) in our three
+    models. The energy densities are parametrized as
+    $\epsilon_\rmn{turb} \propto
+    \epsilon_\rmn{th}^{(\alpha_{\rmn{tu}}+1)/2}/T^{1/4}$ and
+    normalized such that the total turbulent energy in compressible
+    modes $E_\rmn{turb}$ for each scenario makes up about 6\% of the
+    total thermal energy $E_\rmn{th}$ inside the radio halo
+    ($R_\rmn{RH}\approx0.6R_{200}$). The turbulent profiles explore
+    the uncertainty in the cluster turbulence and are motivated by the
+    cosmological simulation in
+    \citep{2009ApJ...705.1129L,2010ApJ...725.1452S,2011A&A...529A..17V}.}
+  \label{fig:Edens}
+\end{figure*}
+
+For reference we show in Table~\ref{tab:timescales} both the thermal
+quantities and the timescales for CR cooling and (re)acceleration for
+three different spatial regions of the RH. Interestingly the
+reacceleration timescale $\tau_D$ is very similar between our three
+models, where the difference comes from turbulent profile
+parameterized with $\alpha_\rmn{tu}$. This implies that even small
+differences in the turbulent profile could impact the seed CRs
+significantly.
+
+\begin{table}
+  \caption{Thermal quantities and timescales for different spatial
+    regions in a Coma like cluster.}
+\begin{tabular}{l c  c c}
+\hline
+\hline
+& & spatial regions & \\
+ & $0.1\,\RH^{(2)}$ & $0.3\,\RH^{(2)}$ & $\RH^{(2)}$   \\
+\hline
+thermal quantities$^{(1)}$ & & & \\
+$\rho$ [$10^{-27}$ g cm$^{-3}$] & 3.0 & 1.6 & 0.15 \\
+$T$ [$10^{8}$ K] & 1.4 & 1.0 & 0.58 \\
+\hline
+timescales$^{(1)}$ & & & \\
+$\tau_\rmn{D}$(\Mprimary)$^{(3)}$ [Gyr] & 0.45 & 0.44 & 0.39 \\
+$\tau_\rmn{D}$(\Mstream)$^{(3)}$  [Gyr] & 0.50 & 0.47 & 0.34 \\
+$\tau_\rmn{D}$(\Mflatturb)$^{(3)}$  [Gyr] & 0.69 & 0.56 & 0.27 \\
+$\tau_\rmn{IC/sync}(P=10^4\,m_ec)^{(4)}$ [Gyr] & 0.11 & 0.15 & 0.22 \\
+$\tau_\rmn{pp}(P=100\,m_pc)^{(5)}$ [Gyr] & 2.4 & 4.5 & 47 \\
+$\tau_\rmn{coul}(P=\,m_ec)^{(6)}$  [Gyr] & 0.0092 & 0.017 & 0.17 \\
+\hline
+\end{tabular}
+\begin{quote}
+ Notes: \\ 
+ (1) Median quantities from our simulated post-merging cluster g72a.\\
+ (2) Radius of the giant radio halo in Coma where $\RH\approx0.6\,R_{200}$.\\
+ (3) Fermi-II reacceleration for both electrons and protons at all energies.\\
+ (4) Inverse Compton and Synchrotron cooling for electrons.\\
+ (5) Catastrophic losses for protons.\\
+ (6) Coulomb cooling for electrons (protons factor $m_e/m_p$ smaller).\\
+
+ \label{tab:timescales}
+  \end{quote}
+\end{table}
+
+\subsection{Spherically symmetric models}
+
+[Anders, your analytical methodology should go here]
+
+\subsection{Cosmological simulation methodology}
+
+In this
 paper we focus on our simulated cluster, g72a, which is a massive
@@
 
-\subsection{Acceleration}
-
-\AP{We use a simple test-particle model for the CR acceleration and
+We use a simple test-particle model for the CR acceleration and
 injection, where each shock inject CRs that trace a power-law in
@@
 energy densities in the pre- and post-shock regimes, corrected for the
-adiabatic energy increase due to gas compression.}
-
-\AP{We limit the acceleration efficiency to $\zeta_{\rmn max}$ by
+adiabatic energy increase due to gas compression.
+
+We limit the acceleration efficiency to $\zeta_{\rmn max}$ by
 steepening the spectral index of the injected population
@@
 (and hence steeper spectral index) forms
-  \citep[e.g.,][]{2000ApJ...540..292E}. Given our assumed $\eb=0.23$,
-  we find that for strong shocks where $\alpha \lesssim 2.3$ the
-  spectral slope is steepened by a maximum of $\sim 10$ per cent in
-  low temperature regimes ($kT\sim 0.1$~keV), while the steepening is
-  much smaller for high temperature regimes ($kT\sim 10$~keV) that are
-  more relevant for clusters. Since $p_{\rm inj}$ remains fixed, so
-  does the CR number density $n_\rmn{CR}$. Hence we can solve for the
+\citep[e.g.,][]{2000ApJ...540..292E}. Given our assumed $\eb=0.23$, we
+find that for strong shocks where $\alpha \lesssim 2.3$ the spectral
+slope is steepened by a maximum of $\sim 10$ per cent in low
+temperature regimes ($kT\sim 0.1$~keV), while the steepening is much
+smaller for high temperature regimes ($kT\sim 10$~keV) that are more
+relevant for clusters. Since $p_{\rm inj}$ remains fixed, so does the
+CR number density $n_\rmn{CR}$. Hence we can solve for the
 renormalized normalization constant $C_\rmn{sub}$ using $n_\rmn{CR}$
@@
 where the new distribution function is given by $f(p,t)= C_\rmn{sub}
-p^{-\alpha_\rmn{sub}}$.} We set an upper limit on the ratio of
+p^{-\alpha_\rmn{sub}}$. We set an upper limit on the ratio of
 accelerated proton-to-dissipated energy in the downstream of strong
@@
 depending on magnetic geometry, $K_{\rmn{ep}}$ could be either larger
-or smaller. \sout{In order not to violate energy conservation with a
-  fixed limit for the acceleration efficiency, we steepen the spectral
-  index of the accelerated CRps at the limit %\citep{pinzke13}
-, which  mimics the non-linear CR modification of the shock
-  %\citep{ellison00}
-  . For weak shocks the efficiency is a factor 10-100
-  lower and well below the limit.} Some observations of radio relics
-suggest high values of $K_{\rmn{ep}}$, due to the absence of gamma-ray
-emission, which probes the CRp population
-\citep{2014MNRAS.437.2291V}. This suggests primary CRes as a viable
-alternative scenario to secondary CRes as seeds for the giant RHs. In
-our {\em M-primaries} scenario, the injected distribution of CRes is
-derived in the same way as for the CRps. Once they have been
-accelerated to relativistic energies, injected electrons and protons
-are indistinguishable. We therefore assume that CRp and CRe have the
-same distribution function $f_\rmn{CRe}(p) = K_\rmn{ep}
-f_\rmn{CRp}(p)$, with a different normalization (due to differing
-acceleration efficiencies) $K_\rmn{ep}=0.1$ \citep[which is viable for
-  primarily perpendicular shocks][]{2014ApJ...794..153G}. While this
-appears to contradict the radial bias of magnetic fields in the bulk
-of the ICM as suggested by observations \citep{2010NatPh...6..520P}
-and cluster simulations \citep{2011ApJ...740...81R}, it does not
-necessarily apply to the accretion shock regions, which show a field
-geometry with a net perpendicular bias with respect to the shock
-normal---at least for giant radio relics \citep{2010Sci...330..347V}.
-
-\subsection{Cosmic ray transport}
-As previously noted, secondaries produced by shock accelerated CRp
-have the wrong spatial profile to explain RH observations; because
-they arise from a two body process, they are too centrally
-concentrated. They also produce $\gamma$-ray emission in excess of
-Fermi-LAT upper limits
-\citep{2012ApJ...757..123A,brunetti12,2014ApJ...787...18A}. However,
-if CRps stream in the ICM, then their spatial profile could
-potentially flatten sufficiently \citep{ensslin11,wiener13}. This
-scenario is very attractive: it generates seed electrons with the
-right spatial footprint, and by removing CRps from the core, obeys
-gamma-ray constraints. Turbulence plays two opposing roles:
-Alfv{\'e}nic turbulence damps waves generated by the CR streaming
-instability \citep{yan02,farmer04}, thus reducing self-confinement;
-but compressible fast modes scatter CRs directly. Turbulent damping is
-still efficient for highly subsonic conditions \citep{wiener13}, while
-we assume compressible fast modes to only provide effective spatial
-confinement during the periods of transonic, highly super-Alfv{\'e}nic
-($M_{\rm A} \sim 5$) turbulence associated with mergers. Thus, CRs can
-stream out when the cluster is kinematically quiescent. Furthermore,
-even Alfv{\'e}nic streaming timescales are relatively short
-\cite[$\sim 0.1-0.5$ Gyr;][]{wiener13} compared to the timescale on
-which the CRp population is built up. Based on these findings, we
-adopt a toy model for our \Mstream scenario in which CR streaming
-instantaneously produces flat CRp profiles. \sout{We assume that CRs cannot
-stream significantly past perpendicular $B$-fields at the accretion
-shock, so that the total number of CRs is conserved within the galaxy
-cluster during the streaming process.}
-
-Given a seed population of CRs, we adopt essentially the same set of
-plasma physics assumptions as the reacceleration model for RHs
-\citep{brunetti07,brunetti11}. We solve the isotropic, gyro-phase
-averaged Fokker-Planck equation (via a Crank-Nicholson scheme) for the
-time evolution of the CRe distribution in the Lagrangian frame
-\citep{brunetti07,brunetti11}:
-\begin{eqnarray}
-{{d f_{\rmn{e}}(p,t)}\over{d t}} &\!=&
-\frac{\partial}{\partial p}
-\left\{
-f_{\rmn{e}}(p,t)\left[
-\left|{{dp}\over{dt}}\right|_{\rm C} 
-+ \frac{p}{3}\left(\bnabla\bcdot \bvel\right)
-+ \left|{{dp}\over{dt}}\right|_{\rm r}\right.\right.
-\nonumber\\
-&-& \left.\left.{1\over{p^2}}{{\partial }\over{\partial p}}\left(p^2 D_{pp}\right) 
-\right]\right\} - \left(\bnabla\bcdot \bvel\right) f_{\rmn{e}}(p,t)
-- \bnabla\bcdot \vec{F}_\rmn{stream}
-\nonumber\\
-&+& {{\partial^2 }\over{\partial p^2}}
-\left[
-D_{pp} f_{\rmn{e}}(p,t) \right]+ Q_{\rmn{e}}\left[p,t;f_{\rmn{p}}(p,t)\right]   \, .
-\label{elettroni}
-\end{eqnarray}
-Here $f_{\rmn{e}}$ is the one-dimensional distribution in position $x$
-(suppressed for clarity), momentum $p$ and time $t$ (which is
-normalized such that the number density is given by
-$n_{\rmn{e}}(t)=\int d p f_{\rmn{e}}(p,t)$), $d/dt=\partial/\partial
-t+\bvel\bcdot\bnabla$ is the Lagrangian derivative, $\bvel$ is the gas
-velocity, $|dp/dt|$ represents radiative (r) and Coulomb (C) losses,
-$D_{pp}$ is the momentum space diffusion coefficient, and
-$Q_{\rmn{e}}$ denotes the injection rate of primary and secondary
-electrons in the ICM. The $\bnabla\bcdot \bvel$ terms represent
-adiabatic gains and losses \AP{and the $\bnabla\bcdot
-  \vec{F}_\rmn{stream}$ terms represent super-Alfv{\'e}nic CR
-  streaming. For details about $F_\rmn{stream}$ please see
-  \citet{wiener13}.} During post-processing of our Coma-like cluster
-simulation, we solve the Fokker-Planck equation over a redshift
-interval from $z=5$ to 0. The simulated cluster undergoes a major
-merger over the last 1-2~Gyrs that \AP{is thought to inject large
-  turbulent eddies. Following \citet{brunetti07,brunetti11} \citep[see
-    also][]{2004ApJ...614..757Y,2015ApJ...800...60M} we assume that
-  about one Gyr after core passage the fields have decayed down to the
-  smallest scales where reacceleration is most efficient ($D_{pp}\sim
-  k_\rmn{cut}$) and the radio halo turns on shortly after. Note that
-  the exact decay time of the turbulens is of minor importance, since
-  the thermal and CR quantities are very similar a few 100 Myrs before
-  and after $z=0$ where we have chosen to evaluate the simulations.}
-\sout{injects large turbulent eddies. After about 1~Gyr those have
-  decayed down to the scale needed to reaccelerate particles.} This
-delay naturally explains why giant radio halos are only seen in a
-fraction of all merging clusters. In all our calculations we assume
-that turbulent reacceleration efficiently accelerates particles for
-$\tau_D\sim650$~Myrs (which is roughly the cascade time on which
-turbulence is damped) and that during this turbulent phase CR
-streaming and spatial diffusion can be neglected. In our \Mstream
-model, CR streaming and diffusion are incorporated separately during
-kinematically quiescent times that precede the merger. As a result,
-flat CRp profiles are produced on relatively short timescales ($\sim
-0.1-0.5$ Gyr). \AP{This allows us to implicitly solve for CR streaming
-  in our calculations, where we adopt a toy model that enforce a flat
-  CRp profile at all quiescent times \citep{wiener13}. We assume that
-  CRs cannot stream significantly past perpendicular $B$-fields at the
-  accretion shock, so that the total number of CRs is conserved within
-  the virial radius during the streaming process. Finally, since
-  streaming is much more efficient for the CRps, we can ignore this
-  effect for the CRes.}
-
-The time evolution of the spectral energy distribution of CRps,
-$f_{\rmn{p}}$, is similarly given by:
-\begin{eqnarray}
-{{d f_{\rmn{p}}(p,t)}\over{d t}} &=&
-{{\partial }\over{\partial p}}
-\left\{
-f_{\rmn{p}}(p,t)\left[ \left|{{dp}\over{dt}}\right|_{\rm C}
-+ \frac{p}{3}\left(\bnabla\bcdot \bvel\right)\right.\right.
-\nonumber\\
-&-&\left.\left. {1\over{p^2}}{{\partial }\over{\partial p}}\left(p^2 D_{pp}\right)
-\right]\right\} - \left(\bnabla\bcdot \bvel\right) f_{\rmn{p}}(p,t)
-- \bnabla\bcdot \vec{F}_\rmn{stream}
-\nonumber\\
-&+& {{\partial^2 }\over{\partial p^2}}
-\left[ D_{pp} f_{\rmn{p}}(p,t) \right] - {{f_{\rmn{p}}(p,t)}\over{\tau_{\rm had}(p)}}
-+ Q_{\rmn{p}}(p,t)\, ,
-\label{eq:FP_p}
-\end{eqnarray}
-where $Q_{\rmn{p}}(p,t)$ denotes the injection rate of shock
-accelerated CRps as a function of momentum $p$ and time $t$, and
-$\tau_{\rm had}$ is the timescale of hadronic losses that produce
-pions via CRp collisions with thermal protons of the ICM
-\cite[e.g.][]{brunetti11}.
-
-\subsection{Turbulent reacceleration}
-
-We incorporate momentum diffusion for electrons and protons from
-transit-time-damping (TTD) resonance with compressible MHD turbulence,
-to model Fermi-II reacceleration \citep{brunetti07,brunetti11}. The
-TTD resonance requires the wave frequency
-$\omega=k_\parallel\upsilon_\parallel$, where $k_\parallel$ and
-$\upsilon_\parallel$ are the parallel (projected along the magnetic
-field) wavenumber and particle velocity, respectively. This implies
-that the particle transit time across the confining wave region
-matches the wave period, $\lambda_{\parallel}/v_{\parallel}=T$. Note,
-the CRs' gyroradius does not enter the resonance condition. Hence the
-CRs that are in resonance with compressible waves experience Fermi-II
-acceleration irrespectively of the length scale of the perturbation.
-
-However, the resonance changes the component of particle momentum
-parallel to seed magnetic fields, which over time leads to increasing
-anisotropy in the particle distribution that decreases the efficiency
-of reacceleration with time. As in \citet{brunetti11}, we assume that
-there exists a mechanism---such as the firehose instability---that
-isotropizes the CR distribution function at the gyroscale and on the
-reacceleration time scale, which ensures sustained efficient
-reacceleration with time. The particle pitch-angle averaged
-momentum-diffusion coefficient of isotropic particles that couple to
-fast magnetosonic modes via TTD resonance is \citep[][ Eqn. 47]{brunetti07}:
-\begin{eqnarray}
-  D_{pp}(p,t) = \frac{\pi}{16} \frac{p^2}{c\,\rho}
-  \left\langle\frac{\beta |B_k|^2}{16 \pi \,W}\right\rangle
-  I_\theta
-  \int_{k_\rmn{cut}}\mathcal{W}(k)k\,d k\,,
-\label{eq:dpp}
-\end{eqnarray}
-where $\beta$ is the thermal-to-magnetic pressure ratio, and $c$
-is the speed of light. The energy density $W$ of a mode in a
-magnetized plasma stems from both electromagnetic fields and resonant
-particles. For a high-$\beta$ plasma, the pitch angle averaged ratio of
-beta-weighted magnetic-to-total energy density saturates to $\langle\beta
-|B_k|^2/2W\rangle\approx 10^{1.4}$ (see Figure 2 in
-\citealt{brunetti07}). The pitch angle of the CR momentum with the
-magnetic field orientation is given by $\theta$, and
-\begin{equation}
-  \label{eq:I_theta}
-  I_\theta=\int_0^{\arccos(\Vph/c)} d\theta {\frac{ \sin^3 \theta }{
-    |\cos \theta | }}
-\left[1+\left(\frac{\Vph}{c\,\cos{\theta}}\right)^2\right]^2.
-\end{equation}
-Here $V_\rmn{ph}$ is the phase velocity of the fast magnetosonic waves
-given approximately by the sound speed, $\Vph \sim c_\rmn{s}$. For a
-sound speed typical for the ICM of 1000~km/s, $I_\theta\approx5$. As
-in \cite{brunetti07}, we initially assume that the velocity of
-turbulent eddies is $V_0\approx 0.47 c_\rmn{s}$ throughout the
-cluster. This gives a turbulent acceleration time scale, $\tau_{D} =
-p^2/4D_{pp}$, that is typically few 100 Myrs in the ICM (see
-Tab.~\ref{tab:timescales} for more details).
-
-\AP{We focus on a scenario where the turbulence is injected at the
-  largest scale that is driven by the merging cluster and accreting
-  matter. The diffusion equation for isotropic MHD turbulence in
-  $k$--space is given by}
-\begin{eqnarray}
-&{{\partial {\mathcal W}(k,t) }\over{\partial t}}
-=
-{{\partial}\over{\partial k}}
-\left[
-k^2 D_{kk}
-{{\partial}\over{\partial k}}
-\left( {{ {\mathcal W}(k,t) }\over{k^2}} \right)
-\right]
-- \sum_i \Gamma_i (k,t) {\mathcal W}(k,t)
-+ I(k,t)\nonumber\\
-&
-\label{modes_kinetic}
-\end{eqnarray}
-\AP{where we assume that the volumetric injection rate of turbulence
-  $I(k,t)$ is constant over time with a fixed rate $I_0$ so that
-  $I(k,t) \equiv I(k) = I_0\,\delta (k - k_o)$. The different damping
-  terms are given by $\Gamma_i(k,t)$ and $D_{kk}$ is the wave--wave diffusion
-  coefficient of magnetosonic waves in the $k$--space represented by
-  \begin{equation}
-    \label{eq:Dkk}
-    D_{kk} \approx \Vph k^4
-    \left(\frac{\mathcal{W}(k)}{\rho\,\Vph^2}\right)\,.
-  \end{equation}
-}
-
-We adopt a simplified isotropic MHD turbulent spectrum \AP{based on
-Kraichnan's picture} for the fast modes per elemental range $dk$ of
-  the form
-\begin{equation}
-  \label{eq:Wk}
-  \mathcal{W}(k) =
-\sqrt{2/7\,I_0\,\rho\,\langle \Vph \rangle}\,k^{-3/2},
-\end{equation}
-for $k_0<k<k_\rmn{cut}$. \AP{Here we adopt an injection scale of the
-  turbulence, $k_0= 2\pi/(1~\mbox{Mpc})$, motivated by recent
-  state-of-art simulations
-  \citep{2009A&A...504...33V,2011A&A...529A..17V,2015ApJ...800...60M}. \sout{At
-    the same time we note that there is a large uncertainty in $k_0$,
-    that is degenerate with the level of turbulence in compressible
-    modes ($X_\rmn{tu}$) which is also highly uncertain. Increasing
-    one of the parameters, allow us to decrease the other in order to
-    keep $D_{pp}$ at the value needed to explain
-    observations.}}\sout{, where we assume an injection scale for the
-  turbulence, $k_0= 2\pi/(100~\mbox{kpc})$.} \AP{The profile of
-  injected turbulence is also highly uncertain, however we assume it
-  correlates to the thermal energy density to some power of the
-  merging clusters. Hence we assume volumetric injection rate of
-  turbulent energy, $I_0\propto \epsilon_\rmn{th}^{\alpha_\rmn{tu}}$,
-  and determine the normalization by requiring that the turbulent
-  energy in compressible modes $E_\rmn{turb}=\int \int \mathcal{W}(k)
-  \rmn{d}k \rmn{d}V = X_\rmn{tu} E_\rmn{th}$, where $E_\rmn{th}$ is
-  the total thermal energy. We adopt a turbulent energy
-  ratio\footnote{Simulations show that the compressible modes
-    contribute a factor $0.2-0.4$ to the total turbulent energy
-    \citep{2013ApJ...771..131B,2015ApJ...800...60M}. Furthermore, the
-    total turbulent energy is typically $10-30$\% of the thermal
-    energy in a cluster which is in agreement with our adopted value
-    of $X_\rmn{tu}$.}  $X_\rmn{tu}=0.06$ within the radio halo.} In
-this work we investigate different spatial models for injected
-turbulence. With the above choice of normalization, the turbulent
-energy density becomes $\epsilon_\rmn{turb} \propto
-\epsilon_\rmn{th}^{\alpha_\rmn{tu}}/T^{1/4}$, where $T$ is the
-temperature of the gas, $\alpha_\rmn{tu}= 0.67$ for \Mflatturb,
-$\alpha_\rmn{tu}= 0.82$ for \Mstream, and $\alpha_\rmn{tu}= 0.88$ for
-\Mprimary. Note that in previous work on the Coma cluster,
-$\epsilon_\rmn{turb} \propto \epsilon_\rmn{th}$ was adopted which
-roughly corresponds to $\alpha_\rmn{tu}= 1$ \citep{brunetti12} and
-together with the different distributions for seed CRes constitute the
-main differences compared to our work. Our flatter turbulent profiles
-are motivated by fits to cosmological simulations
-\citep{2009ApJ...705.1129L,2010ApJ...725.1452S,2011A&A...529A..17V,2012ApJ...758...74B}
-and the range indicates uncertainties of the turbulent profile in
-Coma. Future observations (by Astro-H) and simulations will help to
-clarify this issue. Provided dissipation of turbulence in the ICM is
-collisionless, turbulent cascades of compressible modes become
-suppressed when thermal and relativistic particles resonantly interact
-with magnetosonic waves via TTD on a timescale $\Gamma^{-1}$ that
-approaches the cascading timescale given by $\tau_{kk} \approx
-k^2/D_{kk}$. Thus, the cascade is suppressed for wave numbers above
-\begin{equation}
-\label{eq:kc}
-  k_\rmn{cut} \approx \frac{81}{14} \frac{I_0}{\rho \langle \Vph \rangle}
-  \left(\frac{\langle\sum_i \Gamma_i(k,\theta)\rangle}{k}\right)^{-2}\,,
-\end{equation}
-where $2\pi/k_\rmn{cut}\sim 0.1-1$~kpc in the ICM. This constitutes an
-effective mean free path for CRs, unless plasma instabilities can
-mediate interactions between turbulence and particles on smaller
-scales \citep{brunetti11}. In this work we only consider damping of
-the turbulence via TTD due to thermal electrons, and neglect
-subdominant damping with thermal protons and relativistic particles
-(conversely, the turbulence has important effects on the
-reacceleration of CRs). The latter will be subdominant in the ICM for
-a CR-to-thermal energy density ratio $\lesssim 10 \%$
-\citep{brunetti07}, which is always satisfied in our models. The
-azimuthally averaged turbulent damping rate from thermal electrons
-\citep{brunetti07} in a high-$\beta$ plasma is
-\begin{equation}
-\label{eq:Gamma_e}
-\langle\Gamma_{\rmn{e}}\rangle \approx \langle k\,\Vph\,\sqrt{3\pi
-  x/20}\exp(-5x/3)\sin^2{\theta}\rangle\approx 0.0435k\,\Vph, 
-\end{equation}
-where $x=(m_{\rmn{e}}/m_{\rmn{p}})/\cos^2{\theta}$. To compute the
-synchrotron surface brightness profiles, we use the profile of the
-magnetic field strengths derived from Faraday rotation observations of
-Coma \citep{bonafede10} in combination with the density profile
-derived from X-ray measurements \citep{1992A&A...259L..31B}.
-
-\AP{For reference we show in Table~\ref{tab:timescales} both the thermal
-  quantities and the timescales for CR cooling and (re)acceleration
-  for three different spatial regions of the RH. Interestingly the
-  reacceleration timescale $\tau_D$ is very similar between our three
-  models, where the difference comes from turbulent profile
-  parameterized with $\alpha_\rmn{tu}$. This implies that even small
-  differences in the turbulent profile could impact the seed CRs
-  significantly.}
-
-\begin{table}
-  \caption{Thermal quantities and timescales for different spatial
-    regions in a Coma like cluster.}
-\begin{tabular}{l c  c c}
-\hline
-\hline
-& & spatial regions & \\
- & $0.1\,\RH^{(2)}$ & $0.3\,\RH^{(2)}$ & $\RH^{(2)}$   \\
-\hline
-thermal quantities$^{(1)}$ & & & \\
-$\rho$ [$10^{-27}$ g cm$^{-3}$] & 3.0 & 1.6 & 0.15 \\
-$T$ [$10^{8}$ K] & 1.4 & 1.0 & 0.58 \\
-\hline
-timescales$^{(1)}$ & & & \\
-$\tau_\rmn{D}$(\Mprimary)$^{(3)}$ [Gyr] & 0.45 & 0.44 & 0.39 \\
-$\tau_\rmn{D}$(\Mstream)$^{(3)}$  [Gyr] & 0.50 & 0.47 & 0.34 \\
-$\tau_\rmn{D}$(\Mflatturb)$^{(3)}$  [Gyr] & 0.69 & 0.56 & 0.27 \\
-$\tau_\rmn{IC/sync}(P=10^4\,m_ec)^{(4)}$ [Gyr] & 0.11 & 0.15 & 0.22 \\
-$\tau_\rmn{pp}(P=100\,m_pc)^{(5)}$ [Gyr] & 2.4 & 4.5 & 47 \\
-$\tau_\rmn{coul}(P=\,m_ec)^{(6)}$  [Gyr] & 0.0092 & 0.017 & 0.17 \\
-\hline
-\end{tabular}
-\begin{quote}
- Notes: \\ 
- (1) Median quantities from our simulated post-merging cluster g72a.\\
- (2) Radius of the giant radio halo in Coma where $\RH\approx0.6\,R_{200}$.\\
- (3) Fermi-II reacceleration for both electrons and protons at all energies.\\
- (4) Inverse Compton and Synchrotron cooling for electrons.\\
- (5) Catastrophic losses for protons.\\
- (6) Coulomb cooling for electrons (protons factor $m_e/m_p$ smaller).\\
-
- \label{tab:timescales}
-  \end{quote}
-\end{table}
-
-% --- section: Results and discussion --- %
-
-\section{Results and Discussion} 
+or smaller. Some observations of radio relics suggest high values of
+$K_{\rmn{ep}}$, due to the absence of gamma-ray emission, which probes
+the CRp population \citep{2014MNRAS.437.2291V}. This suggests primary
+CRes as a viable alternative scenario to secondary CRes as seeds for
+the giant RHs. In our {\em M-primaries} scenario, the injected
+distribution of CRes is derived in the same way as for the CRps. Once
+they have been accelerated to relativistic energies, injected
+electrons and protons are indistinguishable. We therefore assume that
+CRp and CRe have the same distribution function $f_\rmn{CRe}(p) =
+K_\rmn{ep} f_\rmn{CRp}(p)$, with a different normalization (due to
+differing acceleration efficiencies) $K_\rmn{ep}=0.1$ \citep[which is
+  viable for primarily perpendicular
+  shocks][]{2014ApJ...794..153G}. While this appears to contradict the
+radial bias of magnetic fields in the bulk of the ICM as suggested by
+observations \citep{2010NatPh...6..520P} and cluster simulations
+\citep{2011ApJ...740...81R}, it does not necessarily apply to the
+accretion shock regions, which show a field geometry with a net
+perpendicular bias with respect to the shock normal---at least for
+giant radio relics \citep{2010Sci...330..347V}.
+
+% --- section: Analytical Results and discussion --- %
+
+\section{Parameter space exploration with spherical models}
+...
+\begin{figure*}
+\begin{minipage}{1\columnwidth}
+   \begin{center}\Large{Radio profiles}\\
+     \includegraphics[width=\columnwidth]{prof.comp.Xtu.eps}
+   \end{center}
+\end{minipage}
+\begin{minipage}{1\columnwidth}
+   \begin{center}\Large{Radio spectra}\\
+     \includegraphics[width=\columnwidth]{spec.comp.Xtu.eps}
+   \end{center}
+\end{minipage}
+\\
+\begin{minipage}{1\columnwidth}
+  \begin{center}%\Large{\Mflatturb:}\\ 
+    \includegraphics[width=\columnwidth]{prof.comp.aCR.eps}
+  \end{center}
+\end{minipage}
+\begin{minipage}{1\columnwidth}
+   \begin{center}%\Large{\it Brunetti et al. (2012)}:\\
+     \includegraphics[width=\columnwidth]{spec.comp.aCR.eps}
+   \end{center}
+\end{minipage}
+\\
+\begin{minipage}{1\columnwidth}
+  \begin{center}%\Large{\Mflatturb:}\\ 
+    \includegraphics[width=\columnwidth]{prof.comp.aI0.eps}
+  \end{center}
+\end{minipage}
+\begin{minipage}{1\columnwidth}
+   \begin{center}%\Large{\it Brunetti et al. (2012)}:\\
+     \includegraphics[width=\columnwidth]{spec.comp.aI0.eps}
+   \end{center}
+\end{minipage}
+\caption{...}
+  \label{fig:param_comp}
+\end{figure*}
+
+% --- section: Simulation Results and discussion --- %
+
+\section{Results of cosmological simulations}
 \label{sec:results}
-\AP{In this section we show that our three models individually
-  reproduce the observed Coma radio halo without violating gamma-ray
-  bounds. The level of emission is mainly driven by how efficient the
-  CRs are reaccelerated and for how long. The diffusion constant,
+In this section we show that our three models individually reproduce
+the observed Coma radio halo without violating gamma-ray bounds. The
+level of emission is mainly driven by how efficient the CRs are
+reaccelerated and for how long. The diffusion constant,
 $D_\rmn{pp}\propto I_0/\rho c_s \propto
-  X_\rmn{tu}^2k_0\epsilon_\rmn{tu}^{\alpha_\rmn{tu}-1}\sqrt{T}$, where
-  we adopt the same level of compressible turbulence,
-  $X_\rmn{tu}=0.06$, for all models. The reaccelerated CRs are
-  super-exponentially dependent on this parameter as long as $\tau_D >
-  \tau_\rmn{cl}$, where $\tau_\rmn{cl}$ represent the duration of
-  reacceleration of the merger which we assume to be 650~Myrs
-  long. Note that  fixing $D_\rmn{pp}$ allows us to relate
-  $\tau_\rmn{cl} \propto X_\rmn{tu}^2 \propto k_0$ that ultimately sets
-  the normalization for $D_\rmn{pp}$. We also exploit the large
-  uncertainty in the turbulent profile and adjust $\alpha_\rmn{tu}$
-  for each model so that the CRs have the correct spatial profile to
-  match the radio emission. The shape of the spectrum for each of
-  model is more complicated and is determined both from reacceleration
-  and as well as the gains and losses during the formation of the
-  cluster. It depends only weakly on the specifics of the CR injection
-  at the shocks (where the Mach number distribution of the shocks is
-  the most important quantity). The normalization of the spectrum is
-  mainly determined from the maximum acceleration efficiency (together
-  with the uncertain parameters $X_\rmn{tu}$, $\tau_\rmn{cl}$, and
-  $k_0$). Given the freedom in the turbulens, it might not be
-  surprising that we match the radio profile in Coma. Although,
-  matching the spectrum without violating gamma-ray bounds for each of
-  our three models is more surprising and is not a consequence of
-  parameter fitting. We believe that it is ultimately a consequence of
-  the adopted physics and hint that reacceleration is a viable
-  explanation for giant radio halos. Below we discuss in more detail
-  the different emission components of Coma.}
+X_\rmn{tu}^2k_0\epsilon_\rmn{th}^{\alpha_\rmn{tu}-1}\sqrt{T}$, where
+we adopt the same level of compressible turbulence, $X_\rmn{tu}=0.06$,
+for all models. The reaccelerated CRs are super-exponentially
+dependent on this parameter as long as $\tau_D > \tau_\rmn{cl}$, where
+$\tau_\rmn{cl}$ represent the duration of reacceleration of the merger
+which we assume to be 650~Myrs long. Note that fixing $D_\rmn{pp}$
+allows us to relate $\tau_\rmn{cl} \propto X_\rmn{tu}^2 \propto k_0$
+that ultimately sets the normalization for $D_\rmn{pp}$. We also
+exploit the large uncertainty in the turbulent profile and adjust
+$\alpha_\rmn{tu}$ for each model so that the CRs have the correct
+spatial profile to match the radio emission. The shape of the spectrum
+for each of model is more complicated and is determined both from
+reacceleration and as well as the gains and losses during the
+formation of the cluster. It depends only weakly on the specifics of
+the CR injection at the shocks (where the Mach number distribution of
+the shocks is the most important quantity). The normalization of the
+spectrum is mainly determined from the maximum acceleration efficiency
+(together with the uncertain parameters $X_\rmn{tu}$, $\tau_\rmn{cl}$,
+and $k_0$). Given the freedom in the turbulens, it might not be
+surprising that we match the radio profile in Coma. Although, matching
+the spectrum without violating gamma-ray bounds for each of our three
+models is more surprising and is not a consequence of parameter
+fitting. We believe that it is ultimately a consequence of the adopted
+physics and hint that reacceleration is a viable explanation for giant
+radio halos. Below we discuss in more detail the different emission
+components of Coma.
 
@@
 dependence on the level of compressible turbulence. Below a critical
-level ($X_\rmn{thres,tu} = 
-\frac{400\,\rmn{Myrs}}{\tau_\rmn{cl}} X_\rmn{tu}\approx 0.04$ in our fiducial model),
-turbulent reacceleration is negligible, while it rises sharply above
-this threshold. For instance, for $X_\rmn{tu}\gtrsim0.04$, a factor 2 change
-in $X_\rmn{tu}$ changes the radio surface brightness by $\sim
+level ($X_\rmn{thres,tu} = \frac{400\,\rmn{Myrs}}{\tau_\rmn{cl}}
+X_\rmn{tu}\approx 0.04$ in our fiducial model), turbulent
+reacceleration is negligible, while it rises sharply above this
+threshold. For instance, for $X_\rmn{tu}\gtrsim0.04$, a factor 2
+change in $X_\rmn{tu}$ changes the radio surface brightness by $\sim
 10-100$. In principle this threshold behavior allows us to provide a
@@
 much gamma-rays. Hence we conclude that $X_\rmn{tu}\gtrsim0.06$ if all
-other parameters are kept fixed. \AP{Although, we caution the reader
-  to take this limit too stringent since there are degeneracies between
-  the uncertain parameters
-  $X_\rmn{tu}\propto\sqrt{\tau_\rmn{D}}\propto \sqrt{k_0}$.} We will
-explore this parameter space further in future work.
+other parameters are kept fixed. Although, we caution the reader to
+take this limit too stringent since there are degeneracies between the
+uncertain parameters $X_\rmn{tu}\propto\sqrt{\tau_\rmn{D}}\propto
+\sqrt{k_0}$. We will explore this parameter space further in future
+work.
 

### 2016-04-18 paper.tex
Update paper.tex

@@
    \begin{center}\Large{Radio profiles}\\
-     \includegraphics[width=\columnwidth]{prof.comp.Xtu.eps}
+     \includegraphics[width=\columnwidth]{prof.comp.KrTTDth.Xtu.eps}
    \end{center}
@@
    \begin{center}\Large{Radio spectra}\\
-     \includegraphics[width=\columnwidth]{spec.comp.Xtu.eps}
+     \includegraphics[width=\columnwidth]{spec.comp.KrTTDth.Xtu.eps}
    \end{center}
@@
   \begin{center}%\Large{\Mflatturb:}\\ 
-    \includegraphics[width=\columnwidth]{prof.comp.aCR.eps}
+    \includegraphics[width=\columnwidth]{prof.comp.KrTTDth.aCR.eps}
   \end{center}
@@
    \begin{center}%\Large{\it Brunetti et al. (2012)}:\\
-     \includegraphics[width=\columnwidth]{spec.comp.aCR.eps}
+     \includegraphics[width=\columnwidth]{spec.comp.KrTTDth.aCR.eps}
    \end{center}
@@
   \begin{center}%\Large{\Mflatturb:}\\ 
-    \includegraphics[width=\columnwidth]{prof.comp.aI0.eps}
+    \includegraphics[width=\columnwidth]{prof.comp.KrTTDth.aI0.eps}
   \end{center}
@@
    \begin{center}%\Large{\it Brunetti et al. (2012)}:\\
-     \includegraphics[width=\columnwidth]{spec.comp.aI0.eps}
+     \includegraphics[width=\columnwidth]{spec.comp.KrTTDth.aI0.eps}
    \end{center}

### 2016-04-20 paper.tex
Added files via upload

@@
 {Anders Pinzke$^{1,2}$\thanks{apinzke@fysik.su.se (AP); peng@physics.ucsb.edu (SPO); christoph.pfrommer@h-its.org (CP)}, S. Peng Oh$^{3}$ and Christoph Pfrommer$^{4}$\footnotemark[1]\\
-$^{1}$The Oskar Klein Centre for Cosmoparticle Physics, Department
-  of Physics, Stockholm University, AlbaNova University Center, SE - 106 91
+$^{1}$The Oskar Klein Centre for Cosmoparticle Physics, Stockholm University, AlbaNova University Center, SE - 106 91
   Stockholm, Sweden\\
@@
 
-\begin{figure*}
+\begin{figure}
   \includegraphics[width=1.0\columnwidth]{fCR.radius.coma.g72a.Rad14.2400p.z0.NL.xKR.eb23.eI067.DII.140.v6.eps}
@@
   \label{fig:Edens}
-\end{figure*}
+\end{figure}
 
@@
 
-\begin{figure*}
+\begin{figure}
   \includegraphics[width=1.0\columnwidth]{turb_profile_ratio_tot.eps}
@@
  (3) Fermi-II reacceleration for both electrons and protons at all energies.\\
- (4) Inverse Compton and Synchrotron cooling for electrons.\\
+ (4) Inverse Compton and synchrotron cooling for electrons.\\
  (5) Catastrophic losses for protons.\\
@@
 \section{Parameter space exploration with spherical models}
-...
+In this section we explore the robustness of our models to crucial
+parameters. We do not trace single Lagrangian particles in the
+cluster, instead we use a more simple approach where we solve the
+Fokker-Plack equation in static spherical shells for injection,
+reacceleration, and losses of the CRs. Once the CRs have been
+reaccelerated for $\tau_\rmn{cl} = 650\,\rmn{Myr}$, we calculate the
+radio emission and compare the profile and spectra for different
+parametrizations.
+
+We adopt both the density \cite{1992A&A...259L..31B} and temperature
+\cite{2009ApJ...696.1886B,2001A&A...365L..67A} profiles derived from
+X-ray observations of the Coma cluster. They are given by:
+\begin{eqnarray}
+n_e = \frac{3.4\times10^{-3}}{\left[1+\left(R/294\,\rmn{kpc}\right)^2\right]^{1.125}}\nonumber\\
+T k_B = 8.25\,\rmn{keV} \left[1+\left(R/0.5R_{200}\right)^2\right]^{-0.32}\,.
+\end{eqnarray}
+The virial radius of Coma is given by $R_{200} = 2300\,\rmn{kpc}$.  The
+bulk of the CRps are injected by relatively low Mach number shocks and
+parametrized by $f_\rmn{CRp,inj}(p) = C_\rmn{CRp,inj}\,p^(-2.5)$. The
+CRps trace the thermal gas with $C_\rmn{CRp,inj} \propto
+\epsilon_\rmn{th}^{\alpha_\rmn{CR,spat}}$ where the normalization is fixed
+by assuming that the injected CR energy in the last 650~Myrs make up
+0.03\% of the thermal energy inside the virial radius, i.e.
+$\int\epsilon_\rmn{CRp,inj} d\rmn{V}/\int\epsilon_\rmn{th} d\rmn{V} =
+0.0003$. The spectrum of the initial CRp distibtion is determined by
+is given by the steady state between injection and cooling,
+\begin{equation}
+ f_{CRp,0} \approx \frac{\int_p^\infty f_\rmn{CRp,inj}(p') 
+\rmn{d}p'}{\left|{{dp}\over{dt}}\right|_{\rm C}+\frac{p}{\tau_{\rm had}}}\,,
+\end{equation}
+where the normalization is determined from $\int\epsilon_\rmn{CRp,inj}
+d\rmn{V}/\int\epsilon_\rmn{th} d\rmn{V} = 0.003$. Similarly, the
+initial CRe distribution is given by the steady state between cooling
+(Coulomb, invers Compton, and synchroton) and injection from
+$f_{CRp,0}$. We also include the contineous injection of secondary
+CRes during $\tau_\rmn{cl}$.
+
+The compressible turbulence responsible for reacceleating both the CRps and
+CRes is parametrized by $I_0 \propto X_\rmn{tu} (n_e
+T)^\alpha_\rmn{tu}$. The diffusion constant $D_\rmn{pp}$ is 
+calculated for each radial bin using
+Eqns.~\ref{eq:Gamma_e}-\ref{eq:dpp}.
+
+In Fig.~\ref{fig:param_comp} we show how assumptions about turbulence
+and CRs impact the radio emission. We find that the level of
+turbulence has a large impact on both radio spectra and profile, while
+the parameter $\alpha_\rmn{tu}$ that determines the spatial profile of
+turbulence mainly influence the radio profiles. Interestingly,
+assumptions about CRs have less impact on radio emission. This can be
+understood by again looking at the scaling of parameters to the
+reacceleration timescale, where $\tau_\rmn{D} \propto
+X_\rmn{tu}^2$. The CRps approximately gain a factor $\Delta
+C_\rmn{reacc.} \sim
+\exp{\frac{(2+\alpha)(1-\alpha)}{4}\frac{\tau_\rmn{cl}}{\tau_\rmn{D}}}$
+during reacceleration if injection and cooling are neglected. The CRes
+gain a similar factor from reacceleration, however in the region
+around $0.1\,R_{200}$ the Coulomb cooling timescale
+$\tau_\rmn{coul}\approx0.01\,\rmn{Myr}$ is much shorter than
+$\tau_\rmn{D}\approx0.5\,\rmn{Myr}$, hence $\Delta C_\rmn{reacc.}$
+will be greatly reduced for the electrons. The spatial region is
+important when we derive the radio spectrum, since in order to compare
+to observations we integrate the CR profile out to $\sim
+0.2\,R_{200}$. For a CRp spectral index $\alpha_\rmn{CR}\sim 2.5$,
+$\Delta C_\rmn{reacc.} \sim
+\exp{1.7\frac{\tau_\rmn{cl}}{\tau_\rmn{D}}} \sim 10$ for
+$X_\rmn{tu}=0.2$ and $\alpha_\rmn{tu}=0.8$. This is confirmed by the
+top panels in Fig.~\ref{fig:param_comp}. Increasing from
+$X_\rmn{tu}=0.2$ to $X_\rmn{tu}=0.3$, gives us a $\Delta
+C_\rmn{reacc.}  \sim 100$, which is roughly confirmed by same
+figures. The difference is due to the shorter reacceleration timescale
+that increase the contribution from reaccelerated CRes with a factor
+few. \AP{Too complicated, perhaps cut or simplify?}
+
 \begin{figure*}
@@
   \begin{center}%\Large{\Mflatturb:}\\ 
+    \includegraphics[width=\columnwidth]{prof.comp.KrTTDth.aI0.eps}
+  \end{center}
+\end{minipage}
+\begin{minipage}{1\columnwidth}
+   \begin{center}%\Large{\it Brunetti et al. (2012)}:\\
+     \includegraphics[width=\columnwidth]{spec.comp.KrTTDth.aI0.eps}
+   \end{center}
+\end{minipage}
+\\
+\begin{minipage}{1\columnwidth}
+  \begin{center}%\Large{\Mflatturb:}\\ 
     \includegraphics[width=\columnwidth]{prof.comp.KrTTDth.aCR.eps}
@@
 \end{minipage}
-\\
-\begin{minipage}{1\columnwidth}
-  \begin{center}%\Large{\Mflatturb:}\\ 
-    \includegraphics[width=\columnwidth]{prof.comp.KrTTDth.aI0.eps}
-  \end{center}
-\end{minipage}
-\begin{minipage}{1\columnwidth}
-   \begin{center}%\Large{\it Brunetti et al. (2012)}:\\
-     \includegraphics[width=\columnwidth]{spec.comp.KrTTDth.aI0.eps}
-   \end{center}
-\end{minipage}
-\caption{...}
+\caption{Sensitivity of radio emission in Coma cluster to critical
+  parameters. {\it Left panels} show the radio surface brightness
+  profiles. We compare profiles at 352~MHz \citep[blue lines and
+    crosses,][]{brown11} to predicted emission from Fermi-II
+  reaccelerated CR electrons populations (black lines). {\it Right
+    panels} show radio synchrotron spectra. The green crosses are
+  compiled from observations \citet{2010PhDT.......259P}, while the
+  black lines show predicted emission from reaccelerated CR
+  electrons. The upper panels show the sensitivity to the level of
+  turbulence ($X_\rmn{tu}$), middle panels show the impact of
+  different turbulent profiles ($\alpha_\rmn{tu}$), and lower panels
+  show the dependence on spatial distributions of initial and injected
+  CRs ($\alpha_\rmn{CR,spat}$). We adopt the following fiducial values
+  for parameters that are not varied in each panel: $X_\rmn{tu}=0.2$,
+  $\alpha_\rmn{tu}=0.8$, and $\alpha_\rmn{CR,spat}$. Note that the
+  radio emission is much more sensitive to assumptions about turbulent
+  parameters than CRs.}
   \label{fig:param_comp}
@@
 we adopt the same level of compressible turbulence, $X_\rmn{tu}=0.06$,
-for all models. The reaccelerated CRs are super-exponentially
-dependent on this parameter as long as $\tau_D > \tau_\rmn{cl}$, where
+for all models. The reaccelerated CRs are exponentially dependent on
+this parameter as long as $\tau_D > \tau_\rmn{cl}$, where
 $\tau_\rmn{cl}$ represent the duration of reacceleration of the merger

### 2016-04-20 paper.tex
Added files via upload

@@
 thermal plasma whose energy density declines steeply with radius. In
-the left panel of Fig.~\ref{fig:Edens} we show that such a
-distribution is not predicted by cosmological simulations \cite[see
+Fig.~\ref{fig:Edens} we show that such a distribution is not predicted
+by cosmological simulations \cite[see
   also][]{pinzke10,2014MNRAS.439.2662V}. If CRps are predominantly
@@
 since the hadronic reaction is a two-body scattering process (see
-Fig.~Fig.~\ref{fig:Edens}). Hence, the simulated emission falls short
+Fig.~\ref{fig:Edens}). Hence, the simulated emission falls short
 of the observed extended and flat radio profile of the Coma cluster.
@@
 parameters are uncertain, and could potentially change our
-predictions. We leave exploration of parameter space and the
-interaction between free parameters to future work.
+predictions. We refere the reader to section~\ref{sect:param_comp} for
+a small exploration of parameter space, however we leave the full
+exploration of parameter space and the interaction between free
+parameters to future work.
 
@@
 f_{\rmn{e}}(p,t)\left[
-\left|{{dp}\over{dt}}\right|_{\rm C} 
+\left|{{dp}\over{dt}}\right|_{\rm coul} 
 + \frac{p}{3}\left(\bnabla\bcdot \bvel\right)
@@
 t+\bvel\bcdot\bnabla$ is the Lagrangian derivative, $\bvel$ is the gas
-velocity, $|dp/dt|$ represents radiative (r) and Coulomb (C) losses,
+velocity, $|dp/dt|$ represents radiative (r) and Coulomb (coul) losses,
 $D_{pp}$ is the momentum space diffusion coefficient, and
@@
 \end{equation}
-for $k_0<k<k_\rmn{cut}$. Here we adopt an injection scale of the
-turbulence, $k_0= 2\pi/(1~\mbox{Mpc})$, motivated by recent
-state-of-art simulations
-\citep{2009A&A...504...33V,2011A&A...529A..17V,2015ApJ...800...60M}.
+for $k_0<k<k_\rmn{cut}$. Here we adopt a injection scale of the
+turbulence, $k_0= 2\pi/(100~\mbox{kpc})$, that is in line with
+previous work \citep{brunetti07,brunetti11} \AP{need to be motivated
+  beter? why not 1 Mpc}
+%, motivated by recent state-of-art simulations \citep{2009A&A...504...33V,2011A&A...529A..17V,2015ApJ...800...60M}.
 The profile of injected turbulence is also highly uncertain, however
@@
   \citep{2013ApJ...771..131B,2015ApJ...800...60M}. Furthermore, the
-  total turbulent energy is typically $10-30$\% of the thermal energy
-  in a cluster which is in agreement with our adopted value of
-  $X_\rmn{tu}$.}  $X_\rmn{tu}=0.06$ within the radio halo. In this
-work we investigate different spatial models for injected
-turbulence. With the above choice of normalization, the turbulent
-energy density becomes $\epsilon_\rmn{turb} \propto
+  total turbulent energy is typically $\sim15-70$\% of the thermal
+  energy in a cluster \cite{2011A&A...529A..17V} which is in agreement
+  with our adopted value of $X_\rmn{tu}$.}  $X_\rmn{tu}=0.2$ within
+the radio halo. In this work we investigate different spatial models
+for injected turbulence. With the above choice of normalization, the
+turbulent energy density becomes $\epsilon_\rmn{turb} \propto
 \epsilon_\rmn{th}^{(\alpha_\rmn{tu}+1)/2}/T^{1/4}$, where $T$ is the
@@
 $\alpha_\rmn{tu}= 0.82$ for \Mstream, and $\alpha_\rmn{tu}= 0.88$ for
-\Mprimary. Note that in previous work on the Coma cluster,
-$\epsilon_\rmn{turb} \propto \epsilon_\rmn{th}$ was adopted which
-roughly corresponds to $\alpha_\rmn{tu}= 1$ \citep{brunetti12} and
-together with the different distributions for seed CRes constitute the
-main differences compared to our work. Our flatter turbulent profiles
-are motivated by fits to cosmological simulations
+\Mprimary (see Figure~\ref{fig:turb} for visualisation). Note that in
+previous work on the Coma cluster, $\epsilon_\rmn{turb} \propto
+\epsilon_\rmn{th}$ was adopted which roughly corresponds to
+$\alpha_\rmn{tu}= 1$ \citep{brunetti12} and together with the
+different distributions for seed CRes constitute the main differences
+compared to our work. Our flatter turbulent profiles are motivated by
+fits to cosmological simulations
 \citep{2009ApJ...705.1129L,2010ApJ...725.1452S,2011A&A...529A..17V,2012ApJ...758...74B}
@@
     normalized such that the total turbulent energy in compressible
-    modes $E_\rmn{turb}$ for each scenario makes up about 6\% of the
+    modes $E_\rmn{turb}$ for each scenario makes up about 20\% of the
     total thermal energy $E_\rmn{th}$ inside the radio halo
@@
     \citep{2009ApJ...705.1129L,2010ApJ...725.1452S,2011A&A...529A..17V}.}
-  \label{fig:Edens}
+  \label{fig:turb}
 \end{figure}
@@
 three different spatial regions of the RH. Interestingly the
-reacceleration timescale $\tau_D$ is very similar between our three
-models, where the difference comes from turbulent profile
-parameterized with $\alpha_\rmn{tu}$. This implies that even small
-differences in the turbulent profile could impact the seed CRs
-significantly.
+reacceleration timescale $\tau_D$ is similar between our three models,
+where the difference comes from turbulent profile parameterized with
+$\alpha_\rmn{tu}$. This implies that even small differences in the
+turbulent profile could impact the seed CRs significantly.
 
@@
 $\tau_\rmn{IC/sync}(P=10^4\,m_ec)^{(4)}$ [Gyr] & 0.11 & 0.15 & 0.22 \\
-$\tau_\rmn{pp}(P=100\,m_pc)^{(5)}$ [Gyr] & 2.4 & 4.5 & 47 \\
+$\tau_\rmn{had}(P=100\,m_pc)^{(5)}$ [Gyr] & 2.4 & 4.5 & 47 \\
 $\tau_\rmn{coul}(P=\,m_ec)^{(6)}$  [Gyr] & 0.0092 & 0.017 & 0.17 \\
@@
 \subsection{Spherically symmetric models}
-
-[Anders, your analytical methodology should go here]
+In this section we develope a simple framework that will be used to
+test the robustness of our models to the critical parameters for CRs
+and turbulence in section~\ref{sect:param_comp}. Here we do not follow
+single Lagrangian particles in the cluster, instead we use a more
+simple approach where we solve the Fokker-Plack equation in static
+spherical shells for injection, reacceleration, and losses of the
+CRs. Once the CRs have been reaccelerated for $\tau_\rmn{cl} =
+650\,\rmn{Myr}$, we calculate the radio emission and compare the
+profile and spectra for different parametrizations.
+
+We adopt both the density \cite{1992A&A...259L..31B} and temperature
+\cite{2009ApJ...696.1886B,2001A&A...365L..67A} profiles derived from
+X-ray observations of the Coma cluster. They are given by:
+\begin{eqnarray}
+n_e &=& \frac{3.4\times10^{-3}}{\left[1+\left(R/294\,\rmn{kpc}\right)^2\right]^{1.125}}\nonumber\\
+T k_B &=& 8.25\,\rmn{keV} \left[1+\left(R/0.5R_{200}\right)^2\right]^{-0.32}\,.
+\end{eqnarray}
+The virial radius of Coma is given by $R_{200} = 2300\,\rmn{kpc}$.
+The bulk of the CRps are injected by relatively low Mach number shocks
+and parametrized by $f_\rmn{CRp,inj}(p) =
+C_\rmn{CRp,inj}\,p^{-2.5}$. The CRps trace the thermal gas with
+$C_\rmn{CRp,inj} \propto \epsilon_\rmn{th}^{\alpha_\rmn{CR,spat}}$,
+where the normalization is fixed by assuming that the injected CR
+energy in the last 650~Myrs make up 0.03\% of the thermal energy
+inside the virial radius, i.e.
+$\int_0^{R_{200}}\epsilon_\rmn{CRp,inj} \rmn{d}
+V/\int_0^{R_{200}}\epsilon_\rmn{th} \rmn{d}V = 0.0003$. The spectrum of
+  the initial CRp distibtion is determined by the steady state between
+  injection and cooling,
+\begin{equation}
+ f_{CRp,0} \approx \frac{\int_p^\infty f_\rmn{CRp,inj}(p') 
+\rmn{d}p'}{\left|{{\rmn{d}p}\over{\rmn{d}t}}\right|_{\rm coul}+\frac{p}{\tau_{\rm had}}}\,,
+\end{equation}
+where the normalization is fixed by
+$\int_0^{R_{200}}\epsilon_\rmn{CRp,inj}
+\rmn{d}V/\int_0^{R_{200}}\epsilon_\rmn{th} \rmn{d}V =
+0.003$. Similarly, the initial CRe distribution is given by the steady
+state between cooling (Coulomb, invers Compton, and synchroton) and
+injection of secondary CRes from $f_{CRp,0}$. We also include the
+contineous injection of secondary CRes during $\tau_\rmn{cl}$. The
+compressible turbulence responsible for reacceleating both the CRps
+and CRes is parametrized by $I_0 \propto X_\rmn{tu} (n_e
+T)^{\alpha_\rmn{tu}}$. The diffusion constant $D_\rmn{pp}$ is
+calculated for each radial bin using
+Eqns.~\ref{eq:dpp}-\ref{eq:Gamma_e}. All parameters and assumptions
+are similar to what is used for our simulated cluster.
 
 \subsection{Cosmological simulation methodology}
-
-In this
-paper we focus on our simulated cluster, g72a, which is a massive
-$1.6\times10^{15}\,M_\odot$ cluster that experienced a merger about
-1-2 Gyrs ago \citep{2009MNRAS.399..497D}. Since the cluster mass,
-density and temperature profiles are all similar to the well studied
-Coma cluster \citep{2007MNRAS.378..385P,pinzke10}, we will compare our
-calculations to radio and gamma-ray observations of Coma.
+In this paper we focus on our simulated cluster, g72a, which is a
+massive $1.6\times10^{15}\,M_\odot$ cluster that experienced a merger
+about 1-2 Gyrs ago \citep{2009MNRAS.399..497D}. Since the cluster
+mass, density and temperature profiles are all similar to the well
+studied Coma cluster \citep{2007MNRAS.378..385P,pinzke10}, we will
+compare our calculations to radio and gamma-ray observations of Coma.
 
@@
 acceleration efficiency for protons of $10\%$. To derive the
-acceleration efficiency, $\zeta_{\rmn inj}$, we first have to infer the
+acceleration efficiency, $\zeta_\rmn{inj}$, we first have to infer the
 particle injection efficiency, which is the fraction of downstream
@@
 
-We limit the acceleration efficiency to $\zeta_{\rmn max}$ by
+We limit the acceleration efficiency to $\zeta_\rmn{max}$ by
 steepening the spectral index of the injected population
-$\alpha_\rmn{inj}$ to $\alpha_\rmn{sub}$ so that $\zeta_{\rmn lin}
-\leq \zeta_{\rmn max}$ is always fulfilled. The slope
-$\alpha_\rmn{inj}$ impact $\zeta_{\rmn inj}$ via the mean energy per
+$\alpha_\rmn{inj}$ to $\alpha_\rmn{sub}$ so that $\zeta_\rmn{lin}
+\leq \zeta_\rmn{max}$ is always fulfilled. The slope
+$\alpha_\rmn{inj}$ impact $\zeta_\rmn{inj}$ via the mean energy per
 particle given by $T_\rmn{CR} = \epsilon_\rmn{CR}/n_\rmn{CR}$. This
@@
 smaller for high temperature regimes ($kT\sim 10$~keV) that are more
-relevant for clusters. Since $p_{\rm inj}$ remains fixed, so does the
+relevant for clusters. Since $p_\rmn{inj}$ remains fixed, so does the
 CR number density $n_\rmn{CR}$. Hence we can solve for the
@@
 accelerated proton-to-dissipated energy in the downstream of strong
-shocks that varies from $\zeta_{\rmn max} \sim 1-10\%$, depending on
+shocks that varies from $\zeta_\rmn{max} \sim 1-10\%$, depending on
 the adopted model (for more details, see Section \ref{sec:results}).
@@
 \section{Parameter space exploration with spherical models}
+\label{sect:param_comp}
 In this section we explore the robustness of our models to crucial
-parameters. We do not trace single Lagrangian particles in the
-cluster, instead we use a more simple approach where we solve the
-Fokker-Plack equation in static spherical shells for injection,
-reacceleration, and losses of the CRs. Once the CRs have been
-reaccelerated for $\tau_\rmn{cl} = 650\,\rmn{Myr}$, we calculate the
-radio emission and compare the profile and spectra for different
-parametrizations.
-
-We adopt both the density \cite{1992A&A...259L..31B} and temperature
-\cite{2009ApJ...696.1886B,2001A&A...365L..67A} profiles derived from
-X-ray observations of the Coma cluster. They are given by:
-\begin{eqnarray}
-n_e = \frac{3.4\times10^{-3}}{\left[1+\left(R/294\,\rmn{kpc}\right)^2\right]^{1.125}}\nonumber\\
-T k_B = 8.25\,\rmn{keV} \left[1+\left(R/0.5R_{200}\right)^2\right]^{-0.32}\,.
-\end{eqnarray}
-The virial radius of Coma is given by $R_{200} = 2300\,\rmn{kpc}$.  The
-bulk of the CRps are injected by relatively low Mach number shocks and
-parametrized by $f_\rmn{CRp,inj}(p) = C_\rmn{CRp,inj}\,p^(-2.5)$. The
-CRps trace the thermal gas with $C_\rmn{CRp,inj} \propto
-\epsilon_\rmn{th}^{\alpha_\rmn{CR,spat}}$ where the normalization is fixed
-by assuming that the injected CR energy in the last 650~Myrs make up
-0.03\% of the thermal energy inside the virial radius, i.e.
-$\int\epsilon_\rmn{CRp,inj} d\rmn{V}/\int\epsilon_\rmn{th} d\rmn{V} =
-0.0003$. The spectrum of the initial CRp distibtion is determined by
-is given by the steady state between injection and cooling,
-\begin{equation}
- f_{CRp,0} \approx \frac{\int_p^\infty f_\rmn{CRp,inj}(p') 
-\rmn{d}p'}{\left|{{dp}\over{dt}}\right|_{\rm C}+\frac{p}{\tau_{\rm had}}}\,,
-\end{equation}
-where the normalization is determined from $\int\epsilon_\rmn{CRp,inj}
-d\rmn{V}/\int\epsilon_\rmn{th} d\rmn{V} = 0.003$. Similarly, the
-initial CRe distribution is given by the steady state between cooling
-(Coulomb, invers Compton, and synchroton) and injection from
-$f_{CRp,0}$. We also include the contineous injection of secondary
-CRes during $\tau_\rmn{cl}$.
-
-The compressible turbulence responsible for reacceleating both the CRps and
-CRes is parametrized by $I_0 \propto X_\rmn{tu} (n_e
-T)^\alpha_\rmn{tu}$. The diffusion constant $D_\rmn{pp}$ is 
-calculated for each radial bin using
-Eqns.~\ref{eq:Gamma_e}-\ref{eq:dpp}.
-
-In Fig.~\ref{fig:param_comp} we show how assumptions about turbulence
-and CRs impact the radio emission. We find that the level of
-turbulence has a large impact on both radio spectra and profile, while
-the parameter $\alpha_\rmn{tu}$ that determines the spatial profile of
-turbulence mainly influence the radio profiles. Interestingly,
-assumptions about CRs have less impact on radio emission. This can be
-understood by again looking at the scaling of parameters to the
-reacceleration timescale, where $\tau_\rmn{D} \propto
-X_\rmn{tu}^2$. The CRps approximately gain a factor $\Delta
+parameters. Figure~\ref{fig:param_comp} shows how assumptions about
+turbulence and CRs impact the radio emission. We find that the level
+of turbulence has a large impact on both radio spectra and profile,
+while the parameter $\alpha_\rmn{tu}$ that determines the spatial
+profile of turbulence mainly influence the radio
+profiles. Interestingly, assumptions about CRs have less impact on
+radio emission. This can be understood by looking at the scaling of
+parameters to the reacceleration timescale, where $\tau_\rmn{D}
+\propto X_\rmn{tu}^2$. The CRps approximately gain a factor $\Delta
 C_\rmn{reacc.} \sim
-\exp{\frac{(2+\alpha)(1-\alpha)}{4}\frac{\tau_\rmn{cl}}{\tau_\rmn{D}}}$
+\exp{\left[\frac{(2+\alpha)(1-\alpha)}{4}\frac{\tau_\rmn{cl}}{\tau_\rmn{D}}\right]}$
 during reacceleration if injection and cooling are neglected. The CRes
@@
 around $0.1\,R_{200}$ the Coulomb cooling timescale
-$\tau_\rmn{coul}\approx0.01\,\rmn{Myr}$ is much shorter than
-$\tau_\rmn{D}\approx0.5\,\rmn{Myr}$, hence $\Delta C_\rmn{reacc.}$
+($\tau_\rmn{coul}\approx0.01\,\rmn{Gyr}$) is much shorter than
+$\tau_\rmn{D}\approx0.5\,\rmn{Gyr}$, hence $\Delta C_\rmn{reacc.}$
 will be greatly reduced for the electrons. The spatial region is
@@
 $\Delta C_\rmn{reacc.} \sim
-\exp{1.7\frac{\tau_\rmn{cl}}{\tau_\rmn{D}}} \sim 10$ for
+\exp{\left[1.7\frac{\tau_\rmn{cl}}{\tau_\rmn{D}}\right]} \sim 10$ for
 $X_\rmn{tu}=0.2$ and $\alpha_\rmn{tu}=0.8$. This is confirmed by the
@@
 C_\rmn{reacc.}  \sim 100$, which is roughly confirmed by same
-figures. The difference is due to the shorter reacceleration timescale
-that increase the contribution from reaccelerated CRes with a factor
-few. \AP{Too complicated, perhaps cut or simplify?}
+figures. The factor 2-3 difference in the figure is due to the shorter
+reacceleration timescale that increase the contribution from
+reaccelerated CRes. Hence we conclude that the radio emission is much
+more sensitive to the exponential dependence on turbulence than the
+linjear dependence on injected CRs. \AP{Too complicated, perhaps cut
+  or simplify?}
 
@@
   for parameters that are not varied in each panel: $X_\rmn{tu}=0.2$,
-  $\alpha_\rmn{tu}=0.8$, and $\alpha_\rmn{CR,spat}$. Note that the
+  $\alpha_\rmn{tu}=0.8$, and $\alpha_\rmn{CR,spat}=1.0$. Note that the
   radio emission is much more sensitive to assumptions about turbulent
@@
 \label{sec:results}
+
 In this section we show that our three models individually reproduce
@@
 level of emission is mainly driven by how efficient the CRs are
-reaccelerated and for how long. The diffusion constant,
+reaccelerated and for how long. After turbulent reacceleration, the
+volume-weighted, relative CRp energy density and relative CRp number
+density inside the RH for \Mflatturb (\Mstream), are found to be 2 (3)
+\% and $2\times10^{-8}$ ($5\times10^{-8}$), respectively. As we will
+see later, these densities are just of the right order of magnitude to
+reproduce radio observations in the Coma cluster.
+
+\AP{move to a scaling subsection?} The diffusion constant,
 $D_\rmn{pp}\propto I_0/\rho c_s \propto
 X_\rmn{tu}^2k_0\epsilon_\rmn{th}^{\alpha_\rmn{tu}-1}\sqrt{T}$, where
-we adopt the same level of compressible turbulence, $X_\rmn{tu}=0.06$,
+we adopt the same level of compressible turbulence, $X_\rmn{tu}=0.2$,
 for all models. The reaccelerated CRs are exponentially dependent on
@@
 $\tau_\rmn{cl}$ represent the duration of reacceleration of the merger
-which we assume to be 650~Myrs long. Note that fixing $D_\rmn{pp}$
-allows us to relate $\tau_\rmn{cl} \propto X_\rmn{tu}^2 \propto k_0$
-that ultimately sets the normalization for $D_\rmn{pp}$. We also
-exploit the large uncertainty in the turbulent profile and adjust
-$\alpha_\rmn{tu}$ for each model so that the CRs have the correct
-spatial profile to match the radio emission. The shape of the spectrum
-for each of model is more complicated and is determined both from
-reacceleration and as well as the gains and losses during the
-formation of the cluster. It depends only weakly on the specifics of
-the CR injection at the shocks (where the Mach number distribution of
-the shocks is the most important quantity). The normalization of the
-spectrum is mainly determined from the maximum acceleration efficiency
-(together with the uncertain parameters $X_\rmn{tu}$, $\tau_\rmn{cl}$,
-and $k_0$). Given the freedom in the turbulens, it might not be
-surprising that we match the radio profile in Coma. Although, matching
-the spectrum without violating gamma-ray bounds for each of our three
-models is more surprising and is not a consequence of parameter
-fitting. We believe that it is ultimately a consequence of the adopted
-physics and hint that reacceleration is a viable explanation for giant
-radio halos. Below we discuss in more detail the different emission
+which we assume to be 650~Myrs long. Note that a fixed reacceleration
+timescale $\tau_D\sim 1/D_\rmn{pp}\sim 0.2-0.7\,\rmn{Gyr}$ is required
+to explain the observations for each model and radial bin. This allows
+us to interchange $\tau_\rmn{cl} \propto X_\rmn{tu}^2 \propto k_0$,
+i.e. a longer reacceleration duration have to be compensated by
+lowering the level of turbulence or increasing the injection scale of
+turbulence to keep $\tau_D$ constant. We also exploit the large
+uncertainty in the turbulent profile and adjust $\alpha_\rmn{tu}$ for
+each model so that the CRs have the correct spatial profile to match
+the radio emission. The shape of the spectrum for each of model is
+more complicated and is determined both from reacceleration and as
+well as the gains and losses during the formation of the cluster. It
+depends only weakly on the specifics of the CR injection at the shocks
+(where the Mach number distribution of the shocks is the most
+important quantity). The normalization of the spectrum is mainly
+determined from the maximum acceleration efficiency (together with the
+uncertain parameters $X_\rmn{tu}$, $\tau_\rmn{cl}$, and $k_0$). Given
+the freedom in the turbulens, it might not be surprising that we match
+the radio profile in Coma. Although, matching the spectrum without
+violating gamma-ray bounds for each of our three models is more
+surprising and is not a consequence of parameter fitting. We believe
+that it is ultimately a consequence of the adopted physics and hint
+that reacceleration is a viable explanation for giant radio
+halos. Below we discuss in more detail the different emission
 components of Coma.
-
-\subsection{Gamma-rays}
-After turbulent reacceleration, the volume-weighted, relative CRp
-energy density and relative CRp number density inside the RH for
-\Mflatturb (\Mstream), are found to be 2 (3) \% and $2\times10^{-8}$
-($5\times10^{-8}$), respectively. As we will see later, these
-densities are just of the right order of magnitude to reproduce radio
-observations in the Coma cluster. The gamma-ray emission from CRps
-that produce decaying neutral pions could be substantial if the CRps
-are reaccelerated efficiently enough, hence it is interesting to
-estimate this emission for our models and compare to upper limits. We
-predict the gamma-ray emission from \Mflatturb (\Mstream) with
-$F_\gamma(>500\,\rmn{MeV})=4\times10^{-10} (5\times10^{-10}) \mathrm{
-  \,ph\, s}^{-1}\mathrm{cm}^{-2}$. The fluxes from these models are
-slightly larger than in \cite{brunetti12}, where the differences comes
-from our steeper CRp profiles in addition to simulation based
-formalism we rely on that accounts for both Coulomb and hadronic
-losses during the build up of the CR distribution in contrast to the
-scaling relations adopted in their paper. Interestingly the gamma-ray
-flux from both our scenarios are just below recent Fermi-LAT limits
-derived from a gamma-ray profile similar to \Mflatturb where
-$F_\gamma(>500\,\rmn{MeV})<5.3\times10^{-10} \mathrm{ \,ph\,
-  s}^{-1}\mathrm{cm}^{-2}$ \footnote{Fabio Zandanel, private
-  communication. See also
-  \citet{2014MNRAS.440..663Z,2014ApJ...787...18A}. and will be probed
-  in the next few years by Fermi-LAT. } The spectral index of the CRp
-distribution is relatively steep ($\alpha_{\rmn{p}}\sim2.6$) for the
-CRp energies $E \gtrsim 10$~GeV that are relevant for the injection of
-radio-emitting secondary CRes. The steep spectrum is ultimately a
-consequence \AP{of the shock history of the simulated cluster, with a
-  weak dependence on} our test particle model for Fermi-I acceleration
-\citep{pinzke13}, where we steepen the spectral index to avoid
-acceleration efficiencies above $\zeta_{\rmn{p}} \sim 10\%$.
 
@@
 level ($X_\rmn{thres,tu} = \frac{400\,\rmn{Myrs}}{\tau_\rmn{cl}}
-X_\rmn{tu}\approx 0.04$ in our fiducial model), turbulent
+X_\rmn{tu}\approx 0.12$ in our fiducial model), turbulent
 reacceleration is negligible, while it rises sharply above this
-threshold. For instance, for $X_\rmn{tu}\gtrsim0.04$, a factor 2
+threshold. For instance, for $X_\rmn{tu}\gtrsim0.12$, a factor two
 change in $X_\rmn{tu}$ changes the radio surface brightness by $\sim
-10-100$. In principle this threshold behavior allows us to provide a
-strict lower bound on turbulence in radio halos. An even more
-stringent bound on $X_\rmn{tu}$ can be inferred from combining radio
-observations with the gamma-ray observations where the predicted
-fluxes from both \Mstream and \Mflatturb are close to the upper limits
-set by Fermi-LAT. If $X_\rmn{tu}$ is smaller than in our adopted
-models (where we assume $X_\rmn{tu}=0.06$), then the efficiency of DSA
-has to be larger than $\zeta_\rmn{p}\sim 0.1$ for the secondary CRes
-to reproduce the radio observations. However, since the turbulent
+10-100$ (see also section~\ref{sect:param_comp}). In principle this
+threshold behavior allows us to provide a strict lower bound on
+turbulence in radio halos. An even more stringent bound on
+$X_\rmn{tu}$ can be inferred from combining radio observations with
+the gamma-ray observations where the predicted fluxes from both
+\Mstream and \Mflatturb are close to the upper limits set by
+Fermi-LAT. If $X_\rmn{tu}$ is smaller than in our adopted models
+(where we assume $X_\rmn{tu}=0.2$), then the efficiency of DSA has to
+be larger than $\zeta_\rmn{p}\sim 0.1$ for the secondary CRes to
+reproduce the radio observations. However, since the turbulent
 reacceleration acts on both the secondary CRes and the CRps, while
 $\zeta_\rmn{p}$ only affects the CRps, these models would produce too
-much gamma-rays. Hence we conclude that $X_\rmn{tu}\gtrsim0.06$ if all
+much gamma-rays. Hence we conclude that $X_\rmn{tu}\gtrsim0.2$ if all
 other parameters are kept fixed. Although, we caution the reader to
@@
 \end{figure*}
+
+\subsection{Gamma-rays}
+The gamma-ray emission from CRps that produce decaying neutral pions
+could be substantial if the CRps are reaccelerated efficiently enough,
+hence it is interesting to estimate this emission for our models and
+compare to upper limits. We predict the gamma-ray emission from
+\Mflatturb (\Mstream) with $F_\gamma(>500\,\rmn{MeV})=4\times10^{-10}
+(5\times10^{-10}) \mathrm{ \,ph\, s}^{-1}\mathrm{cm}^{-2}$. The fluxes
+from these models are slightly larger than in \cite{brunetti12}, where
+the differences comes from our steeper CRp profiles in addition to
+simulation based formalism we rely on that accounts for both Coulomb
+and hadronic losses during the build up of the CR distribution in
+contrast to the scaling relations adopted in their
+paper. Interestingly the gamma-ray flux from both our scenarios are
+just below recent Fermi-LAT limits derived from a gamma-ray profile
+similar to \Mflatturb where
+$F_\gamma(>500\,\rmn{MeV})<5.3\times10^{-10} \mathrm{ \,ph\,
+  s}^{-1}\mathrm{cm}^{-2}$ \footnote{Fabio Zandanel, private
+  communication. See also
+  \citet{2014MNRAS.440..663Z,2014ApJ...787...18A}. and will be probed
+  in the next few years by Fermi-LAT. } The spectral index of the CRp
+distribution is relatively steep ($\alpha_{\rmn{p}}\sim2.6$) for the
+CRp energies $E \gtrsim 10$~GeV that are relevant for the injection of
+radio-emitting secondary CRes. The steep spectrum is ultimately a
+consequence \AP{of the shock history of the simulated cluster, with a
+  weak dependence on} our test particle model for Fermi-I acceleration
+\citep{pinzke13}, where we steepen the spectral index to avoid
+acceleration efficiencies above $\zeta_{\rmn{p}} \sim 10\%$.
 
@@
 gamma-ray constraints from Fermi-LAT, we can derive a lower limit to
-$X_\rmn{tu}\gtrsim0.06$ and a upper limit to the acceleration
+$X_\rmn{tu}\gtrsim0.2$ and a upper limit to the acceleration
 efficiencies of $\zeta_p\lesssim 10\%$ ($\zeta_p\lesssim 3\%$) for

### 2016-04-21 paper.tex
Added files via upload

@@
 
+\subsection{Scaling relations for turbulent reacceleratio}
+The diffusion constant, $D_\rmn{pp}\propto I_0/\rho c_s \propto
+X_\rmn{tu}^2k_0\epsilon_\rmn{th}^{\alpha_\rmn{tu}-1}\sqrt{T}$, where
+we adopt the same level of compressible turbulence, $X_\rmn{tu}=0.2$,
+for all models. The reaccelerated CRs are exponentially dependent on
+this parameter as long as $\tau_D > \tau_\rmn{cl}$, where
+$\tau_\rmn{cl}$ represent the duration of reacceleration of the merger
+which we assume to be 650~Myrs long. Note that a fixed reacceleration
+timescale $\tau_D\sim 1/D_\rmn{pp}\sim 0.2-0.7\,\rmn{Gyr}$ is required
+to explain the observations for each model and radial bin (see
+Table~\ref{tab:timescales}). This allows us to interchange
+$\tau_\rmn{cl} \propto X_\rmn{tu}^2 \propto k_0$, i.e. a longer
+reacceleration duration have to be compensated by lowering the level
+of turbulence or increasing the physical injection scale of turbulence
+to keep $\tau_D$ constant.
+
 \subsection{Spherically symmetric models}
@@
 % --- section: Analytical Results and discussion --- %
-
 \section{Parameter space exploration with spherical models}
 \label{sect:param_comp}
-In this section we explore the robustness of our models to crucial
-parameters. Figure~\ref{fig:param_comp} shows how assumptions about
-turbulence and CRs impact the radio emission. We find that the level
-of turbulence has a large impact on both radio spectra and profile,
+in this paper we rely on several critical parameters decribing
+relatively unknown non-thermal physics in the ICM. Here we try to
+explore the robustness of our models to the most critical parameters
+related to turbulence and CRs. Figure~\ref{fig:param_comp} shows their
+impact on radio emission. We find that the level of turbulence
+($X_\rmn{tu}$) has a large impact on both radio spectra and profile,
 while the parameter $\alpha_\rmn{tu}$ that determines the spatial
-profile of turbulence mainly influence the radio
-profiles. Interestingly, assumptions about CRs have less impact on
-radio emission. This can be understood by looking at the scaling of
-parameters to the reacceleration timescale, where $\tau_\rmn{D}
-\propto X_\rmn{tu}^2$. The CRps approximately gain a factor $\Delta
-C_\rmn{reacc.} \sim
+profile of turbulence mainly influence the radio profiles. As
+expected, the radio profiles flatten significantely with a flatter
+turbulent profile. A higher amount of energy also flatten the radio
+profile, where the reason beeing that the steep profiles of injected
+CRs have less impact on the radio emission for an increasing
+reacceleration efficiency. Interestingly, assumptions about CRs have
+less impact on radio emission. This can be understood by looking at
+the scaling of parameters to the reacceleration timescale, where
+$\tau_\rmn{D} \propto X_\rmn{tu}^2$. The CRps approximately gain a
+factor $\Delta C_\rmn{reacc.} \sim
 \exp{\left[\frac{(2+\alpha)(1-\alpha)}{4}\frac{\tau_\rmn{cl}}{\tau_\rmn{D}}\right]}$
@@
 $X_\rmn{tu}=0.2$ and $\alpha_\rmn{tu}=0.8$. This is confirmed by the
-top panels in Fig.~\ref{fig:param_comp}. Increasing from
-$X_\rmn{tu}=0.2$ to $X_\rmn{tu}=0.3$, gives us a $\Delta
-C_\rmn{reacc.}  \sim 100$, which is roughly confirmed by same
-figures. The factor 2-3 difference in the figure is due to the shorter
-reacceleration timescale that increase the contribution from
-reaccelerated CRes. Hence we conclude that the radio emission is much
-more sensitive to the exponential dependence on turbulence than the
-linjear dependence on injected CRs. \AP{Too complicated, perhaps cut
-  or simplify?}
+top panels in Fig.~\ref{fig:param_comp}. Increasing the level of
+turbulence to $X_\rmn{tu}=0.3$, gives us a $\Delta C_\rmn{reacc.}
+\sim 100$, which is roughly confirmed by same figures. The factor 2-3
+difference in the figure is due to the shorter reacceleration
+timescale that increase the contribution from reaccelerated CRes that
+would othervise cool away on a much shorter timescale. Hence we
+conclude that the radio emission is much more sensitive to the
+exponential dependence on compressible turbulence than the linjear
+dependence on injected CRs. \AP{Too complicated? Perhaps cut or
+  simplify?}
+
+We can also find a lower critical level of turbulence where
+reacceleration is negliable, while it rises sharply above this
+threshold. We define the threshold by $\Delta C_\rmn{reacc.}  \lesssim
+2$, which gives us an $X_\rmn{thres,tu} = \left(\frac{\log(2)
+  0.04}{1.7}\frac{\tau_\rmn{D}}{\tau_\rmn{cl}}\right)^{0.5} \approx 0.08$ for
+$\tau_\rmn{D} = 0.5\,\rmn{Myr}$. This threshold is also seen in the
+top panels of figure~\ref{fig:param_comp}. For instance, for
+$X_\rmn{tu}\gtrsim0.08$, a factor two change in $X_\rmn{tu}$ changes
+the radio surface brightness by a factor $\sim 10-100$. In principle
+this threshold behavior allows us to provide a strict lower bound on
+turbulence in radio halos. An even more stringent bound on
+$X_\rmn{tu}$ can be inferred from combining radio observations with
+the gamma-ray observations (see section~\ref{sect:radio_spec}).
 
@@
 % --- section: Simulation Results and discussion --- %
-
 \section{Results of cosmological simulations}
@@
 see later, these densities are just of the right order of magnitude to
-reproduce radio observations in the Coma cluster.
-
-\AP{move to a scaling subsection?} The diffusion constant,
-$D_\rmn{pp}\propto I_0/\rho c_s \propto
-X_\rmn{tu}^2k_0\epsilon_\rmn{th}^{\alpha_\rmn{tu}-1}\sqrt{T}$, where
-we adopt the same level of compressible turbulence, $X_\rmn{tu}=0.2$,
-for all models. The reaccelerated CRs are exponentially dependent on
-this parameter as long as $\tau_D > \tau_\rmn{cl}$, where
-$\tau_\rmn{cl}$ represent the duration of reacceleration of the merger
-which we assume to be 650~Myrs long. Note that a fixed reacceleration
-timescale $\tau_D\sim 1/D_\rmn{pp}\sim 0.2-0.7\,\rmn{Gyr}$ is required
-to explain the observations for each model and radial bin. This allows
-us to interchange $\tau_\rmn{cl} \propto X_\rmn{tu}^2 \propto k_0$,
-i.e. a longer reacceleration duration have to be compensated by
-lowering the level of turbulence or increasing the injection scale of
-turbulence to keep $\tau_D$ constant. We also exploit the large
+reproduce radio observations in the Coma cluster. We exploit the large
 uncertainty in the turbulent profile and adjust $\alpha_\rmn{tu}$ for
@@
 \subsection{Radio spectrum}
+\label{sect:radio_spec}
 In Fig.~\ref{fig:sync_spectrum} we show that our three models that
@@
 yet. Hence we expect there to be a large variance in the OFF-state of
-different simulated clusters.
-
-While the radio surface brightness has an approximate linear
-dependence on the acceleration efficiency, it has a strong non-linear
-dependence on the level of compressible turbulence. Below a critical
-level ($X_\rmn{thres,tu} = \frac{400\,\rmn{Myrs}}{\tau_\rmn{cl}}
-X_\rmn{tu}\approx 0.12$ in our fiducial model), turbulent
-reacceleration is negligible, while it rises sharply above this
-threshold. For instance, for $X_\rmn{tu}\gtrsim0.12$, a factor two
-change in $X_\rmn{tu}$ changes the radio surface brightness by $\sim
-10-100$ (see also section~\ref{sect:param_comp}). In principle this
-threshold behavior allows us to provide a strict lower bound on
-turbulence in radio halos. An even more stringent bound on
-$X_\rmn{tu}$ can be inferred from combining radio observations with
-the gamma-ray observations where the predicted fluxes from both
-\Mstream and \Mflatturb are close to the upper limits set by
-Fermi-LAT. If $X_\rmn{tu}$ is smaller than in our adopted models
-(where we assume $X_\rmn{tu}=0.2$), then the efficiency of DSA has to
-be larger than $\zeta_\rmn{p}\sim 0.1$ for the secondary CRes to
-reproduce the radio observations. However, since the turbulent
-reacceleration acts on both the secondary CRes and the CRps, while
-$\zeta_\rmn{p}$ only affects the CRps, these models would produce too
-much gamma-rays. Hence we conclude that $X_\rmn{tu}\gtrsim0.2$ if all
-other parameters are kept fixed. Although, we caution the reader to
-take this limit too stringent since there are degeneracies between the
-uncertain parameters $X_\rmn{tu}\propto\sqrt{\tau_\rmn{D}}\propto
-\sqrt{k_0}$. We will explore this parameter space further in future
-work.
+different simulated clusters. As mentioned in
+section~\ref{sect:param_comp}, combining radio observations with
+gamma-ray limits allows us to put a lower limit to $X_\rmn{tu}$.  If
+$X_\rmn{tu}$ is smaller than in our adopted models (where we assume
+$X_\rmn{tu}=0.2$), then the efficiency of DSA has to be larger than
+$\zeta_\rmn{p}\sim 0.1$ for the secondary CRes to reproduce the radio
+observations. However, since the turbulent reacceleration acts on both
+the secondary CRes and the CRps, while $\zeta_\rmn{p}$ only affects
+the CRps, \Mstream and \Mflatturb would produce too much
+gamma-rays. Hence we conclude that $X_\rmn{tu}\gtrsim0.2$ if all other
+parameters are kept fixed. Although, we caution the reader to take
+this limit too stringent because of the uncertainty in $k_0$ and
+$\tau_\rmn{cl}$ that impact $X_\rmn{tu}$ for a fixed
+$\tau_\rmn{D}$. This parameter space needs to be explored further in
+future work in order to put more stringent limits on the level of
+turbulence in clusters using radio and gamma-ray observations in
+combination with turbulent reaccelerated CRs.
 
@@
 radio-emitting secondary CRes. The steep spectrum is ultimately a
-consequence \AP{of the shock history of the simulated cluster, with a
-  weak dependence on} our test particle model for Fermi-I acceleration
+consequence of the shock history of the simulated cluster, with a weak
+dependence on our test particle model for Fermi-I acceleration
 \citep{pinzke13}, where we steepen the spectral index to avoid

### 2016-04-21 paper.tex
Added files via upload

@@
 parameters are uncertain, and could potentially change our
-predictions. We refere the reader to section~\ref{sect:param_comp} for
-a small exploration of parameter space, however we leave the full
-exploration of parameter space and the interaction between free
-parameters to future work.
+predictions. We refer the reader to section~\ref{sect:param_comp} for
+a minor exploration of parameter space, and leave the full exploration
+of parameter space and the interaction between free parameters to
+future work.
 
@@
 
-The transport of relativistic electrons and protons in
-the ICM is a complex process that depends both on the details of the
-thermal component (gas density, temperature, and pressure) as well as
+The transport of relativistic electrons and protons in the ICM is a
+complex process that depends both on the details of the thermal
+component (gas density, temperature, and pressure) as well as
 non-thermal component (turbulence, magnetic fields, fossil CRs). We
@@
 \subsection{Turbulent reacceleration}
-
 We incorporate momentum diffusion for electrons and protons from
@@
 previous work \citep{brunetti07,brunetti11} \AP{need to be motivated
-  beter? why not 1 Mpc}
+  better? why not 1 Mpc}
 %, motivated by recent state-of-art simulations \citep{2009A&A...504...33V,2011A&A...529A..17V,2015ApJ...800...60M}.
@@
 $\alpha_\rmn{tu}= 0.82$ for \Mstream, and $\alpha_\rmn{tu}= 0.88$ for
-\Mprimary (see Figure~\ref{fig:turb} for visualisation). Note that in
+\Mprimary (see Figure~\ref{fig:turb} for visualization). Note that in
 previous work on the Coma cluster, $\epsilon_\rmn{turb} \propto
@@
  (6) Coulomb cooling for electrons (protons factor $m_e/m_p$ smaller).\\
-
  \label{tab:timescales}
@@
 
-\subsection{Scaling relations for turbulent reacceleratio}
-The diffusion constant, $D_\rmn{pp}\propto I_0/\rho c_s \propto
-X_\rmn{tu}^2k_0\epsilon_\rmn{th}^{\alpha_\rmn{tu}-1}\sqrt{T}$, where
-we adopt the same level of compressible turbulence, $X_\rmn{tu}=0.2$,
-for all models. The reaccelerated CRs are exponentially dependent on
-this parameter as long as $\tau_D > \tau_\rmn{cl}$, where
-$\tau_\rmn{cl}$ represent the duration of reacceleration of the merger
-which we assume to be 650~Myrs long. Note that a fixed reacceleration
-timescale $\tau_D\sim 1/D_\rmn{pp}\sim 0.2-0.7\,\rmn{Gyr}$ is required
-to explain the observations for each model and radial bin (see
+\subsection{Scaling relations for turbulent reacceleration}
+To understand the radial dependence of the diffusion constant we
+investigate how $D_\rmn{pp}$ scales with different parameters. This is
+crucial in order to identify important parameters, and understand the
+profile of reaccelerated CRs and radio emission. Combining
+Eqns.~\ref{eq:dpp}-\ref{eq:Gamma_e} we find that $D_\rmn{pp}\propto
+I_0/\rho c_s \propto
+X_\rmn{tu}^2k_0\epsilon_\rmn{th}^{\alpha_\rmn{tu}-1}\sqrt{T}$. Here we
+immediately see that if the turbulent profile trace the thermal energy
+(i.e. $\alpha_\rmn{tu}=1$), the square root of temperature alone
+determines the diffusion constant. We also see that $D_\rmn{pp}$ is
+much more sensitive to $X_\rmn{tu}$ than $k_0$.
+
+During reacceleration the CRps approximately gain a factor 
+\begin{equation}
+  \label{eq:Creacc}
+  \Delta C_\rmn{reacc.} \sim
+  \exp{\left[\frac{(2+\alpha)(\alpha+1)}{4}\frac{\tau_\rmn{cl}}{\tau_\rmn{D}}\right]}\,,
+\end{equation}
+if injection and cooling are neglected. The reaccelerated CRs are then
+exponentially dependent on $D_\rmn{pp}$ as long as $\tau_D \lesssim
+\tau_\rmn{cl}$, where $\tau_\rmn{cl}$ represent the duration of
+reacceleration of the merger which we assume to be 650~Myrs long.
+Note that a fixed reacceleration timescale $\tau_D\sim
+1/D_\rmn{pp}\sim 0.2-0.7\,\rmn{Gyr}$ is required to explain the
+observations at each radius and for each model (see
 Table~\ref{tab:timescales}). This allows us to interchange
-$\tau_\rmn{cl} \propto X_\rmn{tu}^2 \propto k_0$, i.e. a longer
+$\tau_\rmn{cl} \sim X_\rmn{tu}^2 \sim k_0$, i.e. a longer
 reacceleration duration have to be compensated by lowering the level
@@
 \subsection{Spherically symmetric models}
-In this section we develope a simple framework that will be used to
+In this section we develop a simple framework that will be used to
 test the robustness of our models to the critical parameters for CRs
@@
 single Lagrangian particles in the cluster, instead we use a more
-simple approach where we solve the Fokker-Plack equation in static
+simple approach where we solve the Fokker-Planck equation in static
 spherical shells for injection, reacceleration, and losses of the
@@
 650\,\rmn{Myr}$, we calculate the radio emission and compare the
-profile and spectra for different parametrizations.
+profile and spectra for different parameterizations.
 
@@
 The bulk of the CRps are injected by relatively low Mach number shocks
-and parametrized by $f_\rmn{CRp,inj}(p) =
+and parameterized by $f_\rmn{CRp,inj}(p) =
 C_\rmn{CRp,inj}\,p^{-2.5}$. The CRps trace the thermal gas with
@@
 V/\int_0^{R_{200}}\epsilon_\rmn{th} \rmn{d}V = 0.0003$. The spectrum of
-  the initial CRp distibtion is determined by the steady state between
+  the initial CRp distribution is determined by the steady state between
   injection and cooling,
 \begin{equation}
- f_{CRp,0} \approx \frac{\int_p^\infty f_\rmn{CRp,inj}(p') 
+ f_\rmn{CRp,0} \propto \frac{\int_p^\infty f_\rmn{CRp,inj}(p') 
 \rmn{d}p'}{\left|{{\rmn{d}p}\over{\rmn{d}t}}\right|_{\rm coul}+\frac{p}{\tau_{\rm had}}}\,,
@@
 where the normalization is fixed by
-$\int_0^{R_{200}}\epsilon_\rmn{CRp,inj}
+$\int_0^{R_{200}}\epsilon_\rmn{CRp,0}
 \rmn{d}V/\int_0^{R_{200}}\epsilon_\rmn{th} \rmn{d}V =
 0.003$. Similarly, the initial CRe distribution is given by the steady
-state between cooling (Coulomb, invers Compton, and synchroton) and
+state between cooling (Coulomb, inverse Compton, and synchrotron) and
 injection of secondary CRes from $f_{CRp,0}$. We also include the
-contineous injection of secondary CRes during $\tau_\rmn{cl}$. The
-compressible turbulence responsible for reacceleating both the CRps
-and CRes is parametrized by $I_0 \propto X_\rmn{tu} (n_e
+continuous injection of secondary CRes during $\tau_\rmn{cl}$. The
+compressible turbulence responsible for reaccelerating both the CRps
+and CRes is parameterized by $I_0 \propto X_\rmn{tu} (n_e
 T)^{\alpha_\rmn{tu}}$. The diffusion constant $D_\rmn{pp}$ is
@@
 \label{sect:param_comp}
-in this paper we rely on several critical parameters decribing
+In this paper we rely on several critical parameters describing
 relatively unknown non-thermal physics in the ICM. Here we try to
@@
 impact on radio emission. We find that the level of turbulence
-($X_\rmn{tu}$) has a large impact on both radio spectra and profile,
+($X_\rmn{tu}$) has a large impact on both radio spectra and profiles,
 while the parameter $\alpha_\rmn{tu}$ that determines the spatial
 profile of turbulence mainly influence the radio profiles. As
-expected, the radio profiles flatten significantely with a flatter
-turbulent profile. A higher amount of energy also flatten the radio
-profile, where the reason beeing that the steep profiles of injected
-CRs have less impact on the radio emission for an increasing
+expected, the radio profiles flatten significantly with a flatter
+turbulent profile. A higher amount of turbulent energy also flatten
+the radio profile, where the reason being that the steep profiles of
+injected CRs have less impact on the radio emission for an increasing
 reacceleration efficiency. Interestingly, assumptions about CRs have
@@
 the scaling of parameters to the reacceleration timescale, where
-$\tau_\rmn{D} \propto X_\rmn{tu}^2$. The CRps approximately gain a
-factor $\Delta C_\rmn{reacc.} \sim
-\exp{\left[\frac{(2+\alpha)(1-\alpha)}{4}\frac{\tau_\rmn{cl}}{\tau_\rmn{D}}\right]}$
-during reacceleration if injection and cooling are neglected. The CRes
-gain a similar factor from reacceleration, however in the region
-around $0.1\,R_{200}$ the Coulomb cooling timescale
+$\tau_\rmn{D} \propto 1/D_\rmn{pp} \propto 1/X_\rmn{tu}^2$. From
+Eqn.~\ref{eq:Creacc} we see that the CRps with a spectral index of
+$\alpha_\rmn{CR}\approx2.5$ approximately gain a factor $\Delta
+C_\rmn{reacc.} \sim
+\exp{\left[1.7\frac{\tau_\rmn{cl}}{\tau_\rmn{D}}\right]}$ during
+reacceleration if injection and cooling are neglected. The CRes gain a
+similar factor from reacceleration, however in the region around
+$0.1\,R_{200}$ the Coulomb cooling timescale
 ($\tau_\rmn{coul}\approx0.01\,\rmn{Gyr}$) is much shorter than
@@
 to observations we integrate the CR profile out to $\sim
-0.2\,R_{200}$. For a CRp spectral index $\alpha_\rmn{CR}\sim 2.5$,
-$\Delta C_\rmn{reacc.} \sim
-\exp{\left[1.7\frac{\tau_\rmn{cl}}{\tau_\rmn{D}}\right]} \sim 10$ for
-$X_\rmn{tu}=0.2$ and $\alpha_\rmn{tu}=0.8$. This is confirmed by the
-top panels in Fig.~\ref{fig:param_comp}. Increasing the level of
+0.2\,R_{200}$. For $X_\rmn{tu}=0.2$ and $\alpha_\rmn{tu}=0.8$ we find
+that $\Delta C_\rmn{reacc.} \sim 10$. This is confirmed by the top
+panels in Fig.~\ref{fig:param_comp}. Increasing the level of
 turbulence to $X_\rmn{tu}=0.3$, gives us a $\Delta C_\rmn{reacc.}
@@
 timescale that increase the contribution from reaccelerated CRes that
-would othervise cool away on a much shorter timescale. Hence we
+would otherwise cool away on a much shorter timescale. Hence we
 conclude that the radio emission is much more sensitive to the
-exponential dependence on compressible turbulence than the linjear
-dependence on injected CRs. \AP{Too complicated? Perhaps cut or
-  simplify?}
-
-We can also find a lower critical level of turbulence where
-reacceleration is negliable, while it rises sharply above this
+exponential dependence on compressible turbulence than the linear
+dependence on injected CRs.
+
+We can also derive a lower critical level of turbulence where
+reacceleration is negligible, while it rises sharply above this
 threshold. We define the threshold by $\Delta C_\rmn{reacc.}  \lesssim
-2$, which gives us an $X_\rmn{thres,tu} = \left(\frac{\log(2)
-  0.04}{1.7}\frac{\tau_\rmn{D}}{\tau_\rmn{cl}}\right)^{0.5} \approx 0.08$ for
-$\tau_\rmn{D} = 0.5\,\rmn{Myr}$. This threshold is also seen in the
-top panels of figure~\ref{fig:param_comp}. For instance, for
+2$, which gives us an $X_\rmn{thres,tu} = \left(\frac{0.04\,\log(2)
+}{1.7}\frac{\tau_\rmn{D}}{\tau_\rmn{cl}}\right)^{0.5} \approx 0.08$
+for $\tau_\rmn{D} = 0.5\,\rmn{Myr}$. This threshold is also seen in
+the top panels of figure~\ref{fig:param_comp}. For instance, for
 $X_\rmn{tu}\gtrsim0.08$, a factor two change in $X_\rmn{tu}$ changes

### 2016-04-21 paper.tex
intro polished

@@
 winds. However, the strong bimodality that separates X-ray luminous
-clusters into radio-active and radio-quite clusters (and requires a
+clusters into radio-active and radio-quite clusters (requiring a
 fast switch on/off mechanism of the RH emission) and the very extended
@@
 interaction of CR protons (CRps) with thermal protons
-\citep{brunetti11}. While analytic estimates have been made, there has
-been no ab initio demonstration that structure formation can lead to
-the required abundance of seed electrons with the correct spatial and
-spectral characteristics. This is a non-trivial requirement: Coulomb
-cooling in dense cluster cores is severe, and DSA fossil electrons may
-not survive. On the other hand, for secondaries to constitute the seed
+\citep{brunetti11}.
+
+While analytic estimates have been made, there has been no ab initio
+demonstration that structure formation can lead to the required
+abundance of seed electrons with the correct spatial and spectral
+characteristics. This is a non-trivial requirement: Coulomb cooling in
+dense cluster cores is severe, and DSA fossil electrons may not
+survive. On the other hand, for secondaries to constitute the seed
 population, the CRp population required in the best-studied case of
@@
 electrons and the resulting radio synchrotron emission is also peaked
-since the hadronic reaction is a two-body scattering process (see
-Fig.~\ref{fig:Edens}). Hence, the simulated emission falls short
-of the observed extended and flat radio profile of the Coma cluster.
+since the hadronic reaction is a two-body scattering process. Hence,
+the simulated emission falls short of the observed extended and flat
+radio profile of the Coma cluster.
 
@@
 use our hydrodynamical zoom simulations of galaxy clusters in a
-cosmological setting to follow the distribution functions of seed CRp
-and CRe population and integrate the Fokker-Planck equation of CR
-transport along Lagrangian particle trajectories. We resolve injection
-at structure formation shocks, account for various loss processes of
-CRs, and -- most importantly -- model second-order Fermi acceleration
-by CR interactions with magnetised turbulence. However, we assume a
-simplified and stationary model for magnetic fields and turbulence. We
-do not account for the time-varying energy density in compressible
-waves, which are thought to be necessary for the acceleration process
-\citep{brunetti07,brunetti11}, as the cluster merger proceeds.  So our
-approach is orthogonal (and complementary) to e.g.,
-\citealp{2015ApJ...800...60M}. This enables us to vary parameters
-associated with the unknown continuation of magneto-hydrodynamical
-turbulence below the MHD scale and the overall amplitude of
-compressible waves.
+cosmological setting to follow the distribution functions of seed
+populations for CRps and CRes, and integrate the Fokker-Planck
+equation of CR transport along Lagrangian particle trajectories. We
+model diffusive shock acceleration at structure formation shocks,
+account for various loss processes of CRs, and -- most importantly --
+model second-order Fermi acceleration by CR interactions with
+magnetised turbulence.
+
+However, we assume a simplified and stationary model for magnetic
+fields and turbulence. We do not account for the time-varying energy
+density in compressible waves, which are thought to be necessary for
+the acceleration process \citep{brunetti07,brunetti11}, as the cluster
+merger proceeds.  So our approach is orthogonal (and complementary) to
+e.g., simulations of \citealp{2015ApJ...800...60M} that focus on the
+time-dependent compressible turbulence while adopting a simplified
+treatment of CR that does not follow the transport of the CR
+distribution function. Our approach of parametrizing turbulence
+enables us to vary parameters associated with the unknown continuation
+of magneto-hydrodynamical turbulence below the MHD scale and the
+overall amplitude of compressible waves (that can in principle vary
+depending on the details of a particular cluster merger).
 
@@
 seed electrons and compare to observations in the Coma cluster. For
-the most part, we adopt parameters that are used in previous work: for
-details, see \citep[][ turbulent spectrum]{brunetti07,brunetti11},
-\citep[][ injection scale of turbulens]{2015ApJ...800...60M},
-\citep[][ energy density of
-  turbulence]{2009ApJ...705.1129L,2010ApJ...725.1452S,2011A&A...529A..17V},
-for CR acceleration in shocks, \citep[][ in particular $K_{\rmn{ep}}$,
-  acceleration efficiency]{pinzke13}, and for cosmological
-simulations, \citep[][ i.e., shock history, temperature profile,
-  density profile, magnetic field profile]{pinzke10}. All these
-parameters are uncertain, and could potentially change our
-predictions. We refer the reader to section~\ref{sect:param_comp} for
-a minor exploration of parameter space, and leave the full exploration
-of parameter space and the interaction between free parameters to
-future work.
+the most part, we adopt parameters that are used in previous work,
+including Fermi-II acceleration with models of turbulent spectra
+\citep{brunetti07,brunetti11}, injection scale of turbulence
+\citep{2015ApJ...800...60M}, the energy density of turbulence
+\citep{2009ApJ...705.1129L,2010ApJ...725.1452S,2011A&A...529A..17V},
+for CR acceleration in shocks \citep[][in particular $K_{\rmn{ep}}$
+  and the acceleration efficiency]{pinzke13}, and for cosmological
+simulations with CR physics \citep[][i.e., shock history,
+  temperature profile, density profile, magnetic field
+  profile]{pinzke10}. All these parameters are uncertain, and could
+potentially change our predictions. We refer the reader to
+section~\ref{sect:param_comp} for a first exploration of parameter
+space, however we leave the detailed exploration of parameter space and
+the interaction between free parameters to future work.
 
@@
 
-The transport of relativistic electrons and protons in the ICM is a
-complex process that depends both on the details of the thermal
-component (gas density, temperature, and pressure) as well as
-non-thermal component (turbulence, magnetic fields, fossil CRs). We
-use high resolution galaxy cluster simulations to derive the thermal
-and fossil CR properties (shock accelerated primary CRes and CRps, as
-well as secondary CRes produced in p-p collisions)
+The transport of relativistic electrons and protons across cosmic time
+into galaxy clusters is a complex problem that depends on the velocity
+field of the gas (and its thermodynamic properties such as density,
+temperature, and pressure) as well as non-thermal processes
+(turbulence, magnetic fields, fossil CRs). We use high resolution
+galaxy cluster simulations to derive the thermal and fossil CR
+properties (shock accelerated primary CRes and CRps, as well as
+secondary CRes produced in p-p collisions)
 \citep{2007MNRAS.378..385P,pfrommer08,pinzke10,pinzke13}.

### 2016-04-21 paper.tex
Added files via upload
merged paper.tex and added tau_D figure plus text and caption.

@@
  Notes: \\ 
- (1) Median quantities from our simulated post-merging cluster g72a.\\
+ (1) Median quantities from our simulated post-merging cluster g72a derived 
+ during last 300~Myrs in time. \\
  (2) Radius of the giant radio halo in Coma where $\RH\approx0.6\,R_{200}$.\\
@@
 profile of reaccelerated CRs and radio emission. Combining
-Eqns.~\ref{eq:dpp}-\ref{eq:Gamma_e} we find that $D_\rmn{pp}\propto
-I_0/\rho c_s \propto
-X_\rmn{tu}^2k_0\epsilon_\rmn{th}^{\alpha_\rmn{tu}-1}\sqrt{T}$. Here we
-immediately see that if the turbulent profile trace the thermal energy
-(i.e. $\alpha_\rmn{tu}=1$), the square root of temperature alone
-determines the diffusion constant. We also see that $D_\rmn{pp}$ is
-much more sensitive to $X_\rmn{tu}$ than $k_0$.
+Eqns.~\ref{eq:dpp}-\ref{eq:Gamma_e} we find that 
+\begin{equation}
+  \label{eq:Dpp_scaling}
+  D_\rmn{pp}\propto I_0/\rho c_s \propto 
+X_\rmn{tu}^2k_0\epsilon_\rmn{th}^{\alpha_\rmn{tu}-1}\sqrt{T}\,.
+\end{equation}
+Here we immediately see that if the turbulent profile trace the
+thermal energy (i.e. $\alpha_\rmn{tu}=1$), the square root of
+temperature alone determines the diffusion constant. We also see that
+$D_\rmn{pp}$ is much more sensitive to $X_\rmn{tu}$ than $k_0$.
 
@@
 if injection and cooling are neglected. The reaccelerated CRs are then
-exponentially dependent on $D_\rmn{pp}$ as long as $\tau_D \lesssim
-\tau_\rmn{cl}$, where $\tau_\rmn{cl}$ represent the duration of
-reacceleration of the merger which we assume to be 650~Myrs long.
-Note that a fixed reacceleration timescale $\tau_D\sim
-1/D_\rmn{pp}\sim 0.2-0.7\,\rmn{Gyr}$ is required to explain the
-observations at each radius and for each model (see
-Table~\ref{tab:timescales}). This allows us to interchange
-$\tau_\rmn{cl} \sim X_\rmn{tu}^2 \sim k_0$, i.e. a longer
-reacceleration duration have to be compensated by lowering the level
-of turbulence or increasing the physical injection scale of turbulence
-to keep $\tau_D$ constant.
+exponentially dependent on $tau_D\sim 1/D_\rmn{pp}$ as long as $\tau_D
+\lesssim \tau_\rmn{cl}$, where $\tau_\rmn{cl}$ represent the duration
+of reacceleration of the merger which we assume to be 650~Myrs long.
+
+In Figure~\ref{fig:tauD} we show how the turbulent reacceleration
+timescales in our three models scale with radius. As expected, the
+\Mprimary model with $\alpha_\rmn{tu}=0.88$ has the flattest profile
+with $\tau_D\approx0.4\,\rmn{Gyr}$, where the small dip at large
+radius driven by the decrease in thermal energy density. The
+\Mflatturb model has the the flattest turbulent profile parameterized
+by the smaller $\alpha_\rmn{tu}$ which explains the steepest $\tau_D$
+profile. Note that a fixed reacceleration timescale is required to
+explain the observations at each radius and for each model (see also
+Table~\ref{tab:timescales}). This allows us to interchange the value
+of uncertain parameters $\tau_\rmn{cl} \sim X_\rmn{tu}^2 \sim k_0$,
+i.e. a longer reacceleration duration have to be compensated by
+lowering the level of turbulence or increasing the physical injection
+scale of turbulence to keep $\tau_D$ constant.
+
+\begin{figure}
+  \includegraphics[width=1.0\columnwidth]{tau_reacc.eps}
+  \caption{Turbulent reacceleration timescales for our simulated
+    cluster g72a. We show in linear-log the reacceleration timescale
+    ($\tau_D$) as a function of radius $R$ for our three models:
+    \Mprimary (green dotted line), \Mstream (blue dashed line), and
+    \Mflatturb (red solid line). Note that the timescales are derived
+    during the last 100~Myrs in time in our simulations.}
+  \label{fig:tauD}
+\end{figure}
 
@@
 ($\tau_\rmn{coul}\approx0.01\,\rmn{Gyr}$) is much shorter than
-$\tau_\rmn{D}\approx0.5\,\rmn{Gyr}$, hence $\Delta C_\rmn{reacc.}$
+$\tau_\rmn{D}\approx0.6\,\rmn{Gyr}$, hence $\Delta C_\rmn{reacc.}$
 will be greatly reduced for the electrons. The spatial region is
@@
 }{1.7}\frac{\tau_\rmn{D}}{\tau_\rmn{cl}}\right)^{0.5} \approx 0.08$
-for $\tau_\rmn{D} = 0.5\,\rmn{Myr}$. This threshold is also seen in
+for $\tau_\rmn{D} = 0.6\,\rmn{Gyr}$. This threshold is also seen in
 the top panels of figure~\ref{fig:param_comp}. For instance, for

### 2016-04-22 paper.tex
fixing streaming terms and some notation

@@
 galaxy cluster simulations to derive the thermal and fossil CR
-properties (shock accelerated primary CRes and CRps, as well as
-secondary CRes produced in p-p collisions)
-\citep{2007MNRAS.378..385P,pfrommer08,pinzke10,pinzke13}.
+properties \citep[shock accelerated primary CRes and CRps, as well as
+  secondary CRes produced in p-p collisions,
+  see][]{2007MNRAS.378..385P,pfrommer08,pinzke10,pinzke13}.
 
@@
 As previously noted, secondaries produced by shock accelerated CRp
-have the wrong spatial profile to explain RH observations; because
+have the wrong spatial profile to explain RH observations. Because
 they arise from a two body process, they are too centrally
@@
 \right]\right\} - \left(\bnabla\bcdot \bvel\right) f_{\rmn{e}}(p,t)
-- \bnabla\bcdot \vec{F}_\rmn{stream}
 \nonumber\\
@@
 electrons in the ICM. The $\bnabla\bcdot \bvel$ terms represent
-adiabatic gains and losses and the $\bnabla\bcdot
-\vec{F}_\rmn{stream}$ terms represent super-Alfv{\'e}nic CR
-streaming. For details about $F_\rmn{stream}$ please see
-\citet{wiener13}. During post-processing of our Coma-like cluster
-simulation, we solve the Fokker-Planck equation over a redshift
-interval from $z=5$ to 0. The simulated cluster undergoes a major
-merger over the last 1-2~Gyrs that is thought to inject large
-turbulent eddies. Following \citet{brunetti07,brunetti11} \citep[see
-  also][]{2004ApJ...614..757Y,2015ApJ...800...60M} we assume that
-about one Gyr after core passage the fields have decayed down to the
-smallest scales where reacceleration is most efficient ($D_{pp}\sim
-k_\rmn{cut}$) and the radio halo turns on shortly after. Note that the
-exact decay time of the turbulens is of minor importance, since the
-thermal and CR quantities are very similar a few 100 Myrs before and
-after $z=0$ where we have chosen to evaluate the simulations. This
-delay naturally explains why giant radio halos are only seen in a
-fraction of all merging clusters. In all our calculations we assume
-that turbulent reacceleration efficiently accelerates particles for
-$\tau_\rmn{cl}\sim650$~Myrs (which is roughly the cascade time on which
-turbulence is damped) and that during this turbulent phase CR
-streaming and spatial diffusion can be neglected. In our \Mstream
-model, CR streaming and diffusion are incorporated separately during
-kinematically quiescent times that precede the merger. As a result,
-flat CRp profiles are produced on relatively short timescales ($\sim
-0.1-0.5$ Gyr). This allows us to implicitly solve for CR streaming in
-our calculations, where we adopt a toy model that enforce a flat CRp
-profile at all quiescent times \citep{wiener13}. We assume that CRs
-cannot stream significantly past perpendicular $B$-fields at the
-accretion shock, so that the total number of CRs is conserved within
-the virial radius during the streaming process. Finally, since
-streaming is much more efficient for the CRps, we can ignore this
-effect for the CRes.
+adiabatic gains and losses.
+
+During post-processing of our Coma-like cluster simulation, we solve
+the Fokker-Planck equation over a redshift interval from $z=5$ to
+0. The simulated cluster undergoes a major merger over the last
+1-2~Gyrs that is thought to inject large turbulent eddies. Following
+standard approaches
+\citep{brunetti07,brunetti11,2004ApJ...614..757Y,2015ApJ...800...60M}
+we assume that about one Gyr after core passage the fields have
+decayed down to the smallest scales where reacceleration is most
+efficient ($D_{pp}\sim k_\rmn{cut}$) and the radio halo turns on
+shortly after. Note that the exact decay time of the turbulens is of
+minor importance, since the thermal and CR quantities are very similar
+a few 100 Myrs before and after $z=0$ where we have chosen to evaluate
+the simulations. This delay naturally explains why giant radio halos
+are only seen in a fraction of all merging clusters. In all our
+calculations we assume that turbulent reacceleration efficiently
+accelerates particles for $\tau_\rmn{cl}\sim650$~Myrs (which is
+roughly the cascade time on which turbulence is damped) and that
+during this turbulent phase CR streaming and spatial diffusion can be
+neglected. In our \Mstream model, CR streaming and diffusion are
+incorporated separately during kinematically quiescent times that
+precede the merger. As a result, flat CRp profiles are produced on
+relatively short timescales ($\sim 0.1-0.5$ Gyr). This allows us to
+implicitly solve for CR streaming in our calculations, where we adopt
+a toy model that enforce a flat CRp profile at all quiescent times
+\citep{wiener13}. We assume that CRs cannot stream significantly past
+perpendicular $B$-fields at the accretion shock, so that the total
+number of CRs is conserved within the virial radius during the
+streaming process. Finally, since streaming is much more efficient for
+the CRps, we can ignore this effect for the CRes.
 
@@
 \begin{eqnarray}
-{{d f_{\rmn{p}}(p,t)}\over{d t}} &=&
+\lefteqn{
+  {{d f_{\rmn{p}}(p,t)}\over{d t}} =
   {{\partial }\over{\partial p}}
@@
   f_{\rmn{p}}(p,t)\left[ \left|{{dp}\over{dt}}\right|_{\rm C}
-+ \frac{p}{3}\left(\bnabla\bcdot \bvel\right)\right.\right.
+    + \frac{p}{3}\bnabla\bcdot \left(\bvel+\bvel_{\rmn{st}}\right)\right.\right.}
 \nonumber\\
-&-&\left.\left. {1\over{p^2}}{{\partial }\over{\partial p}}\left(p^2 D_{pp}\right)
-\right]\right\} - \left(\bnabla\bcdot \bvel\right) f_{\rmn{p}}(p,t)
-- \bnabla\bcdot \vec{F}_\rmn{stream}
+&&-\left.\left. {1\over{p^2}}{{\partial }\over{\partial p}}\left(p^2 D_{pp}\right)
+\right]\right\} - f_{\rmn{p}}(p,t) \bnabla\bcdot \left(\bvel+\bvel_{\rmn{st}}\right) 
+- \bvel_{\rmn{st}}\bcdot\bnabla f_{\rmn{p}}(p,t)
 \nonumber\\
-&+& {{\partial^2 }\over{\partial p^2}}
+&&+\,\,\, {{\partial^2 }\over{\partial p^2}}
 \left[ D_{pp} f_{\rmn{p}}(p,t) \right] - {{f_{\rmn{p}}(p,t)}\over{\tau_{\rm had}(p)}}
@@
 \end{eqnarray}
-where $Q_{\rmn{p}}(p,t)$ denotes the injection rate of shock
-accelerated CRps as a function of momentum $p$ and time $t$, and
-$\tau_{\rm had}$ is the timescale of hadronic losses that produce
-pions via CRp collisions with thermal protons of the ICM
-\cite[e.g.][]{brunetti11}.
+where $\bvel_{\rmn{st}}=-\varv_{\rmn{A}}\bnabla f_{\rmn{p}}/|\bnabla
+f_{\rmn{p}}|$ is the streaming velocity in the isotropic transport
+approximation, $\varv_{\rmn{A}}$ is the Alfv\'en speed,
+$Q_{\rmn{p}}(p,t)$ denotes the injection rate of shock accelerated
+CRps as a function of momentum $p$ and time $t$, and $\tau_{\rm had}$
+is the timescale of hadronic losses that produce pions via CRp
+collisions with thermal protons of the ICM \cite[e.g.][]{brunetti11}.
 
@@
 if injection and cooling are neglected. The reaccelerated CRs are then
-exponentially dependent on $tau_D\sim 1/D_\rmn{pp}$ as long as $\tau_D
+exponentially dependent on $\tau_D\sim 1/D_\rmn{pp}$ as long as $\tau_D
 \lesssim \tau_\rmn{cl}$, where $\tau_\rmn{cl}$ represent the duration
@@
 
-We adopt both the density \cite{1992A&A...259L..31B} and temperature
-\cite{2009ApJ...696.1886B,2001A&A...365L..67A} profiles derived from
+We adopt both the density \citep{1992A&A...259L..31B} and temperature
+profiles \citep{2009ApJ...696.1886B,2001A&A...365L..67A} derived from
 X-ray observations of the Coma cluster. They are given by:
 \begin{eqnarray}
-n_e &=& \frac{3.4\times10^{-3}}{\left[1+\left(R/294\,\rmn{kpc}\right)^2\right]^{1.125}}\nonumber\\
-T k_B &=& 8.25\,\rmn{keV} \left[1+\left(R/0.5R_{200}\right)^2\right]^{-0.32}\,.
+n_e &=& \frac{3.4\times10^{-3}}{\left[1+\left(R/R_{\rmn{c}}\right)^2\right]^{1.125}}\nonumber\\
+k_{\rmn{B}} T &=& 8.25\,\rmn{keV} \left[1+\left(2R/R_{200}\right)^2\right]^{-0.32}\,.
 \end{eqnarray}
-The virial radius of Coma is given by $R_{200} = 2300\,\rmn{kpc}$.
+The virial and core radii of Coma are given by $R_{200} =
+2300\,\rmn{kpc}$ and $R_{\rmn{c}} = 294\,\rmn{kpc}$, respectively.
 The bulk of the CRps are injected by relatively low Mach number shocks
@@
 $\int_0^{R_{200}}\epsilon_\rmn{CRp,inj} \rmn{d}
-V/\int_0^{R_{200}}\epsilon_\rmn{th} \rmn{d}V = 0.0003$. The spectrum of
-  the initial CRp distribution is determined by the steady state between
-  injection and cooling,
+V\left(\int_0^{R_{200}}\epsilon_\rmn{th} \rmn{d}V\right)^{-1} =
+0.0003$. The spectrum of the initial CRp distribution is determined by
+the steady state between injection and cooling,
 \begin{equation}
  f_\rmn{CRp,0} \propto \frac{\int_p^\infty f_\rmn{CRp,inj}(p') 
-\rmn{d}p'}{\left|{{\rmn{d}p}\over{\rmn{d}t}}\right|_{\rm coul}+\frac{p}{\tau_{\rm had}}}\,,
+\rmn{d}p'}{\displaystyle\left|{{\rmn{d}p}\over{\rmn{d}t}}\right|_{\rm coul}+\frac{p}{\tau_{\rm had}}}\,,
 \end{equation}
-where the normalization is fixed by
+where we fix the normalization by requiring
 $\int_0^{R_{200}}\epsilon_\rmn{CRp,0}
-\rmn{d}V/\int_0^{R_{200}}\epsilon_\rmn{th} \rmn{d}V =
+\rmn{d}V\left(\int_0^{R_{200}}\epsilon_\rmn{th} \rmn{d}V\right)^{-1} =
 0.003$. Similarly, the initial CRe distribution is given by the steady
@@
 \begin{equation}
-  f(p,t) = C(t)\,p^{\alpha_\rmn{inj}}\,,
+  f(p,t) = C(t)\,p^{\alpha_\rmn{inj}}\,,\quad
+  \alpha_\rmn{inj}=\frac{(\gamma_\rmn{ad}+1)\mathcal{M}^2}
+        {(\gamma_\rmn{ad}-1)\mathcal{M}^2+2}
 \end{equation}
 determined by the normalization $C(t)$ and the spectral index
-$\alpha_\rmn{inj}=\frac{(\gamma_\rmn{ad}+1)\mathcal{M}^2}{(\gamma_\rmn{ad}-1)\mathcal{M}^2+2}$
-that depends on the adiabatic index $\gamma_\rmn{ad} = 5/3$ and the
-Mach number of the shock $\mathcal{M}$. It is given by the ratio of
-the upstream velocity ($u_2$) and the sound speed ($c_s$). The CR
-number density and CR energy density are derived from $n_\rmn{CR} =
+$\alpha_{\rmn{inj}}$ that depends on the adiabatic index
+$\gamma_\rmn{ad} = 5/3$ and the Mach number of the shock
+$\mathcal{M}$. It is given by the ratio of the upstream velocity
+($u_2$) and the sound speed ($c_s$). The CR number density and CR
+energy density are derived from $n_\rmn{CR} =
 \int_{p_\rmn{inj}}^\infty \dd p\, f(p)$ and $\epsilon_\rmn{CR} =
@@
 $T(p) = (\sqrt{1+p^2} -1)\, m\,c^2$ is the kinetic energy of a
-particle with momentum $p$. We adopt a fit to Monte Carlo
-simulations of the thermal leakage process that relates the momentum
-of injected protons ($p_\rmn{inj}$) to the thermal energy
-($p_\rmn{th}$) of the shocked plasma \citep{kang11}:
+particle with momentum $p$. We adopt a fit to Monte Carlo simulations
+of the thermal leakage process that relates the momentum of injected
+protons ($p_\rmn{inj}$) to the thermal energy ($p_\rmn{th}$) of the
+shocked plasma \citep{kang11}:
 \begin{eqnarray}
@@
 10^{-2}$. Hence, we adopt this as a fiducial value for the CRe-to-CRp
-acceleration efficiency (see \cite{pinzke13} for more
-discussion). However, as recent PIC simulations have shown, this is
-likely very different at weak shocks, with electrons efficiently
-accelerated at perpendicular shocks
+acceleration efficiency \citep[see][for more
+  discussion]{pinzke13}. However, as recent PIC simulations have
+shown, this is likely very different at weak shocks, with electrons
+efficiently accelerated at perpendicular shocks
 \citep{2014ApJ...794..153G,2014ApJ...797...47G}, and ions efficiently
@@
 \begin{minipage}{1\columnwidth}
-   \begin{center}\Large{Radio profiles}\\
+   \begin{center}\Large{radio profiles}\\
      \includegraphics[width=\columnwidth]{prof.comp.KrTTDth.Xtu.eps}
@@
 \begin{minipage}{1\columnwidth}
-   \begin{center}\Large{Radio spectra}\\
+   \begin{center}\Large{radio spectra}\\
      \includegraphics[width=\columnwidth]{spec.comp.KrTTDth.Xtu.eps}

### 2016-04-25 paper.tex
some edits in Sect 2

@@
-\documentclass[a4paper,fleqn,usenatbib]{mnras}
+\documentclass[fleqn,usenatbib,useAMS]{mnras}
+\usepackage{amsmath}	% Advanced maths commands
 \usepackage{txfonts}
@@
 \usepackage{graphicx,color}	% Including figure files
-%\usepackage{amsmath}	% Advanced maths commands
 \usepackage{amssymb}	% Extra maths symbols
@@
 \newcommand{\Vph}{V_\mathrm{ph}}
-\newcommand{\mug}{\mu G}
+\newcommand{\mug}{\umu G}
 \newcommand{\RH}{R_\rmn{RH}}
@@
 \newcommand\eb{\epsilon_\rmn{B}}
+\newcommand{\dps}{\displaystyle}
 
@@
 \def\AP#1{{\bf  AP: #1}}
-\def\APP#1{{\bf {\color{red} AP2: #1}}}
-\def\SPO#1{{\bf {\color{blue} SPO: #1}}}
+\def\APP#1{{\bf {\color{blue} AP2: #1}}}
+\def\SPO#1{{\bf {\color{red} SPO: #1}}}
 \def\CP#1{{\bf {\color{mygreen} CP: #1}}}
@@
 
-[explain overall picture, $\tau_\rmn{d}$ vs. $\tau_{\rmn{cl}}$]
+\SPO{explain overall picture, $\tau_\rmn{d}$ vs. $\tau_{\rmn{cl}}$}
 
@@
 adopt a toy model for our \Mstream scenario in which CR streaming
-instantaneously produces flat CRp profiles. \sout{We assume that CRs cannot
-stream significantly past perpendicular $B$-fields at the accretion
-shock, so that the total number of CRs is conserved within the galaxy
-cluster during the streaming process.}
+instantaneously produces flat CRp profiles.
 
@@
 f_{\rmn{e}}(p,t)\left[
-\left|{{dp}\over{dt}}\right|_{\rm coul} 
+\left|{{dp}\over{dt}}\right|_{\rm C} 
 + \frac{p}{3}\left(\bnabla\bcdot \bvel\right)
@@
 t+\bvel\bcdot\bnabla$ is the Lagrangian derivative, $\bvel$ is the gas
-velocity, $|dp/dt|$ represents radiative (r) and Coulomb (coul) losses,
-$D_{pp}$ is the momentum space diffusion coefficient, and
+velocity, $|dp/dt|$ represents radiative (r) and Coulomb (C)
+losses, $D_{pp}$ is the momentum space diffusion coefficient, and
 $Q_{\rmn{e}}$ denotes the injection rate of primary and secondary
-electrons in the ICM. The $\bnabla\bcdot \bvel$ terms represent
-adiabatic gains and losses.
+electrons in the ICM. The first term containing the expression
+$\bnabla\bcdot \bvel$ represents Fermi-I acceleration and the second
+term of this form describes adiabatic gains and losses.
 
@@
 \subsection{Turbulent reacceleration}
-We incorporate momentum diffusion for electrons and protons from
+We incorporate momentum diffusion for electrons and protons via the
 transit-time-damping (TTD) resonance with compressible MHD turbulence,
 to model Fermi-II reacceleration \citep{brunetti07,brunetti11}. The
-TTD resonance requires the wave frequency
-$\omega=k_\parallel\upsilon_\parallel$, where $k_\parallel$ and
-$\upsilon_\parallel$ are the parallel (projected along the magnetic
+TTD resonance requires the wave frequency to obey the resonance
+condition, $\omega=k_\parallel\varv_\parallel$, where $k_\parallel$
+and $\varv_\parallel$ are the parallel (projected along the magnetic
 field) wavenumber and particle velocity, respectively. This implies
 that the particle transit time across the confining wave region
-matches the wave period, $\lambda_{\parallel}/v_{\parallel}=T$. Note,
-the CRs' gyroradius does not enter the resonance condition. Hence the
-CRs that are in resonance with compressible waves experience Fermi-II
+matches the wave period,
+$\lambda_{\parallel}/v_{\parallel}=\tau_{\rmn{wave}}$. Note, the CRs'
+gyroradius does not enter the resonance condition. Hence the CRs that
+are in resonance with compressible waves experience Fermi-II
 acceleration irrespectively of the length scale of the perturbation.
 
-However, the resonance changes the component of particle momentum
-parallel to seed magnetic fields, which over time leads to increasing
-anisotropy in the particle distribution that decreases the efficiency
-of reacceleration with time. As in \citet{brunetti11}, we assume that
-there exists a mechanism---such as the firehose instability---that
-isotropizes the CR distribution function at the gyroscale and on the
-reacceleration time scale, which ensures sustained efficient
-reacceleration with time. The particle pitch-angle averaged
-momentum-diffusion coefficient of isotropic particles that couple to
-fast magnetosonic modes via TTD resonance is \citep[][ Eqn. 47]{brunetti07}:
+However, the resonance changes the component of the particle momentum
+parallel to the mean magnetic field, which over time leads to
+increasing anisotropy in the particle distribution that decreases the
+efficiency of reacceleration with time. As in \citet{brunetti11}, we
+assume that there exists a mechanism---such as the firehose
+instability---that isotropizes the CR distribution function at the
+gyroscale and on the reacceleration time scale, which ensures
+sustained efficient reacceleration with time.
+\CP{add OoM}
+
+The particle pitch-angle averaged momentum-diffusion coefficient of
+isotropic particles that couple to fast magnetosonic modes via TTD
+resonance is \citep[][ Eqn. 47]{brunetti07}:
 \begin{eqnarray}
-  D_{pp}(p,t) = \frac{\pi}{16} \frac{p^2}{c\,\rho}
-  \left\langle\frac{\beta |B_k|^2}{16 \pi \,W}\right\rangle
+  D_{pp}(p,t) = \frac{\upi}{16} \frac{p^2}{\rho c}
+  \left\langle\frac{\beta |B_k|^2}{16 \upi \,W}\right\rangle
   I_\theta
@@
 by
-\begin{eqnarray}
-&{{\partial {\mathcal W}(k,t) }\over{\partial t}}
+\begin{equation}
+  \begin{aligned}
+\frac{\partial {\mathcal W}(k,t)}{\partial t}
 =
-{{\partial}\over{\partial k}}
+\frac{\partial}{\partial k}
 \left[
 k^2 D_{kk}
-{{\partial}\over{\partial k}}
-\left( {{ {\mathcal W}(k,t) }\over{k^2}} \right)
+\frac{\partial}{\partial k}
+\left( \frac{{\mathcal W}(k,t)}{k^2} \right)
 \right]
 - \sum_i \Gamma_i (k,t) {\mathcal W}(k,t)
-+ I(k,t)\nonumber\\
-&
++ I(k,t)
+\end{aligned}
 \label{modes_kinetic}
-\end{eqnarray}
+\end{equation}
 where we assume that the volumetric injection rate of turbulence
@@
 \end{equation}
-for $k_0<k<k_\rmn{cut}$. Here we adopt a injection scale of the
-turbulence, $k_0= 2\pi/(100~\mbox{kpc})$, that is in line with
-previous work \citep{brunetti07,brunetti11} \AP{need to be motivated
-  better? why not 1 Mpc}
-%, motivated by recent state-of-art simulations \citep{2009A&A...504...33V,2011A&A...529A..17V,2015ApJ...800...60M}.
-The profile of injected turbulence is also highly uncertain, however
-we assume it correlates to the thermal energy density to some power of
-the merging clusters. Hence we assume volumetric injection rate of
-turbulent energy, $I_0\propto \epsilon_\rmn{th}^{\alpha_\rmn{tu}}$,
-and determine the normalization by requiring that the turbulent energy
-in compressible modes $E_\rmn{turb}=\int \int \mathcal{W}(k) \rmn{d}k
-\rmn{d}V = X_\rmn{tu} E_\rmn{th}$, where $E_\rmn{th}$ is the total
-thermal energy. We adopt a turbulent energy ratio\footnote{Simulations
-  show that the compressible modes contribute a factor $0.2-0.4$ to
-  the total turbulent energy
+for $k_0<k<k_\rmn{cut}$. Here we adopt an injection scale of the
+turbulence, $k_0= 2\upi/\lambda_0$ with $\lambda_0 =100~\mbox{kpc}$,
+that is in line with previous work \citep{brunetti07,brunetti11}. Note
+that this length scale defines an eddy turn-over time
+$\tau_{\rmn{eddy}}\sim2\upi\lambda_0/V_0\sim1.2$~Gyr with
+$V_0=500\,\rmn{km~s}^{-1}$, characteristic of a merger event.
+
+The profile of injected turbulence depends on the details of the
+merger such as time during the merger, the impact parameter, the
+merger mass ratio, and the degree of cluster anisotropy
+\citep{2015ApJ...800...60M}. We parametrize these uncertainties and
+assume that it scales with the thermal energy density to some
+power. Hence we assume volumetric injection rate of turbulent energy,
+$I_0\propto \epsilon_\rmn{th}^{\alpha_\rmn{tu}}$, and determine the
+normalization by requiring that the turbulent energy in compressible
+modes $E_\rmn{turb}=\int \int \mathcal{W}(k) \rmn{d}k \rmn{d}V =
+X_\rmn{tu} E_\rmn{th}$, where $E_\rmn{th}$ is the total thermal
+energy. We adopt a turbulent energy ratio $X_\rmn{tu}=0.2$ within the
+radio halo.\footnote{Simulations show that the compressible modes
+  contribute a factor $0.2-0.4$ to the total turbulent energy
   \citep{2013ApJ...771..131B,2015ApJ...800...60M}. Furthermore, the
-  total turbulent energy is typically $\sim15-70$\% of the thermal
-  energy in a cluster \cite{2011A&A...529A..17V} which is in agreement
-  with our adopted value of $X_\rmn{tu}$.}  $X_\rmn{tu}=0.2$ within
-the radio halo. In this work we investigate different spatial models
-for injected turbulence. With the above choice of normalization, the
-turbulent energy density becomes $\epsilon_\rmn{turb} \propto
+  total turbulent energy, which can be decomposed into a slenoidal and
+  compressible component, is typically $\sim15-70$\% of the thermal
+  energy in a cluster \citep{2011A&A...529A..17V}; in agreement with
+  our adopted value of $X_\rmn{tu}$.} In this work we investigate
+different spatial models for injected turbulence. With the above
+choice of normalization, the turbulent energy density becomes
+$\epsilon_\rmn{turb} \propto
 \epsilon_\rmn{th}^{(\alpha_\rmn{tu}+1)/2}/T^{1/4}$, where $T$ is the
@@
 $\alpha_\rmn{tu}= 0.82$ for \Mstream, and $\alpha_\rmn{tu}= 0.88$ for
-\Mprimary (see Figure~\ref{fig:turb} for visualization). Note that in
-previous work on the Coma cluster, $\epsilon_\rmn{turb} \propto
-\epsilon_\rmn{th}$ was adopted which roughly corresponds to
+\Mprimary (see Figure~\ref{fig:turb} for visualization).
+
+Note that in previous work on the Coma cluster, $\epsilon_\rmn{turb}
+\propto \epsilon_\rmn{th}$ was adopted which roughly corresponds to
 $\alpha_\rmn{tu}= 1$ \citep{brunetti12} and together with the
@@
 \end{equation}
-where $2\pi/k_\rmn{cut}\sim 0.1-1$~kpc in the ICM. This constitutes an
+where $2\upi/k_\rmn{cut}\sim 0.1-1$~kpc in the ICM. This constitutes an
 effective mean free path for CRs, unless plasma instabilities can
 mediate interactions between turbulence and particles on smaller
-scales \citep{brunetti11}. In this work we only consider damping of
-the turbulence via TTD due to thermal electrons, and neglect
-subdominant damping with thermal protons and relativistic particles
-(conversely, the turbulence has important effects on the
-reacceleration of CRs). The latter will be subdominant in the ICM for
-a CR-to-thermal energy density ratio $\lesssim 10 \%$
-\citep{brunetti07}, which is always satisfied in our models. The
-azimuthally averaged turbulent damping rate from thermal electrons
-\citep{brunetti07} in a high-$\beta$ plasma is
+scales \citep{brunetti11}.
+
+In this work we only consider damping of the turbulence via TTD due to
+thermal electrons, and neglect subdominant damping with thermal
+protons and relativistic particles (conversely, the turbulence has
+important effects on the reacceleration of CRs). The latter will be
+subdominant in the ICM for a CR-to-thermal energy density ratio
+$\lesssim 10 \%$ \citep{brunetti07}, which is always satisfied in our
+models. The azimuthally averaged turbulent damping rate from thermal
+electrons \citep{brunetti07} in a high-$\beta$ plasma is
 \begin{equation}
 \label{eq:Gamma_e}
-\langle\Gamma_{\rmn{e}}\rangle \approx \langle k\,\Vph\,\sqrt{3\pi
+\langle\Gamma_{\rmn{e}}\rangle \approx \langle k\,\Vph\,\sqrt{3\upi
   x/20}\exp(-5x/3)\sin^2{\theta}\rangle\approx 0.0435k\,\Vph, 
@@
 synchrotron emission peaks at frequency $\nu_\rmn{syn}\simeq 1\,
-B/\mu\rmn{G} (\gamma/10^4)^2\,\rmn{GHz}$, this translates into a
+B/\umu\rmn{G} (\gamma/10^4)^2\,\rmn{GHz}$, this translates into a
 spectral steepening of the radio spectrum (see

### 2016-04-25 paper.tex
some edits in Sect 2

@@
 f_{\rmn{e}}(p,t)\left[
-\left|{{dp}\over{dt}}\right|_{\rm C} 
+\left|{{dp}\over{dt}}\right|_{\rm Coul} 
 + \frac{p}{3}\left(\bnabla\bcdot \bvel\right)
-+ \left|{{dp}\over{dt}}\right|_{\rm r}\right.\right.
++ \left|{{dp}\over{dt}}\right|_{\rm rad}\right.\right.
 \nonumber\\
@@
 t+\bvel\bcdot\bnabla$ is the Lagrangian derivative, $\bvel$ is the gas
-velocity, $|dp/dt|$ represents radiative (r) and Coulomb (C)
+velocity, $|dp/dt|$ represents radiative (rad) and Coulomb (Coul)
 losses, $D_{pp}$ is the momentum space diffusion coefficient, and
@@
   \left\{
-  f_{\rmn{p}}(p,t)\left[ \left|{{dp}\over{dt}}\right|_{\rm C}
+  f_{\rmn{p}}(p,t)\left[ \left|{{dp}\over{dt}}\right|_{\rm Coul}
     + \frac{p}{3}\bnabla\bcdot \left(\bvel+\bvel_{\rmn{st}}\right)\right.\right.}
@@
 $\tau_\rmn{had}(P=100\,m_pc)^{(5)}$ [Gyr] & 2.4 & 4.5 & 47 \\
-$\tau_\rmn{coul}(P=\,m_ec)^{(6)}$  [Gyr] & 0.0092 & 0.017 & 0.17 \\
+$\tau_\rmn{Coul}(P=\,m_ec)^{(6)}$  [Gyr] & 0.0092 & 0.017 & 0.17 \\
 \hline
@@
  f_\rmn{CRp,0} \propto \frac{\int_p^\infty f_\rmn{CRp,inj}(p') 
-\rmn{d}p'}{\displaystyle\left|{{\rmn{d}p}\over{\rmn{d}t}}\right|_{\rm coul}+\frac{p}{\tau_{\rm had}}}\,,
+\rmn{d}p'}{\displaystyle\left|{{\rmn{d}p}\over{\rmn{d}t}}\right|_{\rm Coul}+\frac{p}{\tau_{\rm had}}}\,,
 \end{equation}
@@
   p_\rmn{inj} &=& x_\rmn{inj} p_\rmn{th} = x_\rmn{inj} \sqrt{\frac{2 \,k T_2}{m c^2}}\,, \nonumber \\
-  \rmn{where}\quad x_\rmn{inj} &\approx& 1.17 \frac{u_2}{p_{\rmn th}\,c} \left(1+
+  \rmn{where}\quad x_\rmn{inj} &\approx& 1.17 \frac{u_2}{p_{\rmn{th}}\,c} \left(1+
   \frac{1.07}{\epsilon_B}\right) \left(\frac{\mathcal{M}}{3}\right)^{0.1}\,.

### 2016-04-26 paper.tex
edits in Sect 2.2

@@
 \def\C#1{{\bf #1}}
-\def\AP#1{{\bf  AP: #1}}
-\def\APP#1{{\bf {\color{blue} AP2: #1}}}
+\def\AP2#1{{\bf  AP2: #1}}
+\def\AP#1{{\bf {\color{blue} AP: #1}}}
 \def\SPO#1{{\bf {\color{red} SPO: #1}}}
@@
 f_{\rmn{e}}(p,t)\left[
-\left|{{dp}\over{dt}}\right|_{\rm Coul} 
+\left|\frac{dp}{dt}\right|_{\rm Coul} 
 + \frac{p}{3}\left(\bnabla\bcdot \bvel\right)
-+ \left|{{dp}\over{dt}}\right|_{\rm rad}\right.\right.
++ \left|\frac{dp}{dt}\right|_{\rm rad}\right.\right.
 \nonumber\\
@@
 velocity, $|dp/dt|$ represents radiative (rad) and Coulomb (Coul)
-losses, $D_{pp}$ is the momentum space diffusion coefficient, and
-$Q_{\rmn{e}}$ denotes the injection rate of primary and secondary
-electrons in the ICM. The first term containing the expression
+losses, \AP{please insert formulae:}
+\begin{eqnarray}
+  \left|\frac{dp}{dt}\right|_{\rm Coul}
+  &=& \\
+  \left|\frac{dp}{dt}\right|_{\rm rad~}
+  &=& 
+\end{eqnarray}
+$D_{pp}$ is the momentum space diffusion coefficient (see
+Sect.~\ref{sec:reacc}), and $Q_{\rmn{e}}$ denotes the injection rate
+of primary and secondary electrons in the ICM (see
+Sect.~\ref{sec:cosmo_sim}). The first term containing the expression
 $\bnabla\bcdot \bvel$ represents Fermi-I acceleration and the second
@@
 $Q_{\rmn{p}}(p,t)$ denotes the injection rate of shock accelerated
-CRps as a function of momentum $p$ and time $t$, and $\tau_{\rm had}$
-is the timescale of hadronic losses that produce pions via CRp
-collisions with thermal protons of the ICM \cite[e.g.][]{brunetti11}.
+CRps as a function of momentum $p$ and time $t$ (see
+Sect.~\ref{sec:cosmo_sim}), and $\tau_{\rm had}$ is the timescale of
+hadronic losses that produce pions via CRp collisions with thermal
+protons of the ICM \cite[e.g.][]{brunetti11}.
+\AP{please insert formulae:}
+\begin{eqnarray}
+  \tau_{\rm had} = 
+\end{eqnarray}
 
 \subsection{Turbulent reacceleration}
+\label{sec:reacc}
+
 We incorporate momentum diffusion for electrons and protons via the
@@
 sustained efficient reacceleration with time.
-\CP{add OoM}
-
-The particle pitch-angle averaged momentum-diffusion coefficient of
+
+\SPO{please check the following:} To order of magnitude, the
+momentum-space diffusion coefficient due to second-order Fermi-II
+acceleration scales as
+\begin{eqnarray}
+  D_{pp} \propto p\dot{p}
+  \propto p^2\langle kc\rangle_{\mathcal{W}} \left(\frac{\Vph}{c}\right)^2,
+\label{eq:dpp_oom}
+\end{eqnarray}
+since the force on a particle due to Fermi-II acceleration scales as
+$\dot{p}\sim p/\tau\sim p \langle kc\rangle_{\mathcal{W}} (\Vph/c)^2$
+where $\langle kc\rangle_{\mathcal{W}} (\Vph/c)^2$ is the wave
+energy-averaged wave-particle interaction rate. It can be shown that
+the particle pitch-angle averaged momentum-diffusion coefficient of
 isotropic particles that couple to fast magnetosonic modes via TTD
@@
 $\alpha_\rmn{tu}= 0.82$ for \Mstream, and $\alpha_\rmn{tu}= 0.88$ for
-\Mprimary (see Figure~\ref{fig:turb} for visualization).
+\Mprimary (see Figure~\ref{fig:turb} for visualization). \CP{These
+  models and scaling indices are not well motivated here, they would
+  better fit into the results section.}
 
@@
 
-For reference we show in Table~\ref{tab:timescales} both the thermal
-quantities and the timescales for CR cooling and (re)acceleration for
-three different spatial regions of the RH. Interestingly the
-reacceleration timescale $\tau_D$ is similar between our three models,
-where the difference comes from turbulent profile parameterized with
+\SPO{this needs a rewrite in the light of an updated discussion of
+  $\tau_\rmn{d}$ vs. $\tau_{\rmn{cl}}$.}  For reference we show in
+Table~\ref{tab:timescales} both the thermal quantities and the
+timescales for CR cooling and (re)acceleration for three different
+spatial regions of the RH. Interestingly the reacceleration timescale
+$\tau_{\rm D}$ is similar between our three models, where the
+difference comes from turbulent profile parameterized with
 $\alpha_\rmn{tu}$. This implies that even small differences in the
@@
 compressible turbulence responsible for reaccelerating both the CRps
-and CRes is parameterized by $I_0 \propto X_\rmn{tu} (n_e
+and CRes is parameterized by $I_0 \propto X_\rmn{tu} (n_{\rmn{e}}
 T)^{\alpha_\rmn{tu}}$. The diffusion constant $D_\rmn{pp}$ is
@@
 \subsection{Cosmological simulation methodology}
+\label{sec:cosmo_sim}
 In this paper we focus on our simulated cluster, g72a, which is a

### 2016-04-26 paper.tex
edits in Sect 2.2
edits in Sect 2

@@
 \newcommand{\dps}{\displaystyle}
+\newcommand{\p}{\rmn{p}}
+\newcommand{\kB}{k_{\rmn{B}}}
+\newcommand{\eps}{\varepsilon}
 
@@
 the simulations. This delay naturally explains why giant radio halos
-are only seen in a fraction of all merging clusters. In all our
-calculations we assume that turbulent reacceleration efficiently
-accelerates particles for $\tau_\rmn{cl}\sim650$~Myrs (which is
-roughly the cascade time on which turbulence is damped) and that
-during this turbulent phase CR streaming and spatial diffusion can be
-neglected. In our \Mstream model, CR streaming and diffusion are
-incorporated separately during kinematically quiescent times that
+are only seen in a fraction of all merging clusters.
+
+In all our calculations we assume that turbulent reacceleration
+efficiently accelerates particles for $\tau_\rmn{cl}\sim650$~Myrs
+(which is roughly the cascade time on which turbulence is damped) and
+that during this turbulent phase CR streaming and spatial diffusion
+can be neglected. In our \Mstream model, CR streaming and diffusion
+are incorporated separately during kinematically quiescent times that
 precede the merger. As a result, flat CRp profiles are produced on
@@
 \begin{eqnarray}
-  D_{pp} \propto p\dot{p}
-  \propto p^2\langle kc\rangle_{\mathcal{W}} \left(\frac{\Vph}{c}\right)^2,
+  D_{pp} \sim p\dot{p}
+  \sim p^2\langle kc\rangle_{\mathcal{W}} \left(\frac{\Vph}{c}\right)^2,
 \label{eq:dpp_oom}
@@
 power. Hence we assume volumetric injection rate of turbulent energy,
-$I_0\propto \epsilon_\rmn{th}^{\alpha_\rmn{tu}}$, and determine the
+$I_0\propto \eps_\rmn{th}^{\alpha_\rmn{tu}}$, and determine the
 normalization by requiring that the turbulent energy in compressible
@@
 choice of normalization, the turbulent energy density becomes
-$\epsilon_\rmn{turb} \propto
-\epsilon_\rmn{th}^{(\alpha_\rmn{tu}+1)/2}/T^{1/4}$, where $T$ is the
+$\eps_\rmn{turb} \propto
+\eps_\rmn{th}^{(\alpha_\rmn{tu}+1)/2}/T^{1/4}$, where $T$ is the
 temperature of the gas, $\alpha_\rmn{tu}= 0.67$ for \Mflatturb,
@@
 
-Note that in previous work on the Coma cluster, $\epsilon_\rmn{turb}
-\propto \epsilon_\rmn{th}$ was adopted which roughly corresponds to
+Note that in previous work on the Coma cluster, $\eps_\rmn{turb}
+\propto \eps_\rmn{th}$ was adopted which roughly corresponds to
 $\alpha_\rmn{tu}= 1$ \citep{brunetti12} and together with the
@@
     models. The energy densities are parametrized as
-    $\epsilon_\rmn{turb} \propto
-    \epsilon_\rmn{th}^{(\alpha_{\rmn{tu}}+1)/2}/T^{1/4}$ and
+    $\eps_\rmn{turb} \propto
+    \eps_\rmn{th}^{(\alpha_{\rmn{tu}}+1)/2}/T^{1/4}$ and
     normalized such that the total turbulent energy in compressible
@@
 \subsection{Scaling relations for turbulent reacceleration}
+
+\SPO{should this be moved to the preceeding section?}
 To understand the radial dependence of the diffusion constant we
-investigate how $D_\rmn{pp}$ scales with different parameters. This is
+investigate how $D_{pp}$ scales with different parameters. This is
 crucial in order to identify important parameters, and understand the
@@
   \label{eq:Dpp_scaling}
-  D_\rmn{pp}\propto I_0/\rho c_s \propto 
-X_\rmn{tu}^2k_0\epsilon_\rmn{th}^{\alpha_\rmn{tu}-1}\sqrt{T}\,.
+  D_{pp}\propto \frac{I_0}{\rho c_{\rmn{s}}} \propto 
+X_\rmn{tu}^2k_0\eps_\rmn{th}^{\alpha_\rmn{tu}-1}\sqrt{T}\,.
 \end{equation}
-Here we immediately see that if the turbulent profile trace the
+Here we immediately see that if the turbulent profile traces the
 thermal energy (i.e. $\alpha_\rmn{tu}=1$), the square root of
-temperature alone determines the diffusion constant. We also see that
-$D_\rmn{pp}$ is much more sensitive to $X_\rmn{tu}$ than $k_0$.
-
-During reacceleration the CRps approximately gain a factor 
+temperature determines the diffusion constant. We also see that
+$D_{pp}$ is much more sensitive to the turbulent energy content
+$X_\rmn{tu}$ in comparison to the injection scale $k_0$.
+
+During reacceleration, the CRps increase their normalization
+approximately by the factor
 \begin{equation}
   \label{eq:Creacc}
-  \Delta C_\rmn{reacc.} \sim
+  \delta C_\rmn{reacc.} \sim 
   \exp{\left[\frac{(2+\alpha)(\alpha+1)}{4}\frac{\tau_\rmn{cl}}{\tau_\rmn{D}}\right]}\,,
 \end{equation}
-if injection and cooling are neglected. The reaccelerated CRs are then
-exponentially dependent on $\tau_D\sim 1/D_\rmn{pp}$ as long as $\tau_D
-\lesssim \tau_\rmn{cl}$, where $\tau_\rmn{cl}$ represent the duration
-of reacceleration of the merger which we assume to be 650~Myrs long.
-
-In Figure~\ref{fig:tauD} we show how the turbulent reacceleration
+if injection and cooling are neglected. The reaccelerated CRs depend
+exponentially on $\tau_D\sim 1/D_{pp}$ as long as $\tau_D \lesssim
+\tau_\rmn{cl}$, where $\tau_\rmn{cl}$ represent the duration of
+reacceleration of the merger which we assume to be 650~Myrs long.
+
+\CP{Again the logic is skewed here: these models are derived from the
+  spatial profile of the synchrotron emission in Sect. 4. Hence
+  $D_{pp}$ should be discussed after those have been introduced.}  In
+Figure~\ref{fig:tauD} we show how the turbulent reacceleration
 timescales in our three models scale with radius. As expected, the
@@
 \subsection{Spherically symmetric models}
-In this section we develop a simple framework that will be used to
-test the robustness of our models to the critical parameters for CRs
-and turbulence in section~\ref{sect:param_comp}. Here we do not follow
-single Lagrangian particles in the cluster, instead we use a more
-simple approach where we solve the Fokker-Planck equation in static
-spherical shells for injection, reacceleration, and losses of the
-CRs. Once the CRs have been reaccelerated for $\tau_\rmn{cl} =
-650\,\rmn{Myr}$, we calculate the radio emission and compare the
-profile and spectra for different parameterizations.
+In this section we develop a simplified framework that will be used to
+test the robustness of our models with respect to the critical
+parameters for CRs and turbulence in Section~\ref{sect:param_comp}. In
+order to quickly explore parameter space, we we solve the
+Fokker-Planck equation in static spherical shells for injection,
+reacceleration, and losses of the CRs, i.e., we neglect the Lagrangian
+trajectories during the re-acceleration time.  Once the CRs have been
+reaccelerated for $\tau_\rmn{cl} = 650\,\rmn{Myr}$, we calculate the
+radio emission and compare the profile and spectra for different
+parameterizations.
 
@@
 \begin{eqnarray}
-n_e &=& \frac{3.4\times10^{-3}}{\left[1+\left(R/R_{\rmn{c}}\right)^2\right]^{1.125}}\nonumber\\
-k_{\rmn{B}} T &=& 8.25\,\rmn{keV} \left[1+\left(2R/R_{200}\right)^2\right]^{-0.32}\,.
+n_e &=& \frac{n_0}{\left[1+\left(R/R_{\rmn{c}}\right)^2\right]^{1.125}}\nonumber\\
+k_{\rmn{B}} T &=& 8.25\,\rmn{keV} \left[1+\left(2R/R_{200}\right)^2\right]^{-0.32}\,,
 \end{eqnarray}
-The virial and core radii of Coma are given by $R_{200} =
-2300\,\rmn{kpc}$ and $R_{\rmn{c}} = 294\,\rmn{kpc}$, respectively.
-The bulk of the CRps are injected by relatively low Mach number shocks
-and parameterized by $f_\rmn{CRp,inj}(p) =
-C_\rmn{CRp,inj}\,p^{-2.5}$. The CRps trace the thermal gas with
-$C_\rmn{CRp,inj} \propto \epsilon_\rmn{th}^{\alpha_\rmn{CR,spat}}$,
-where the normalization is fixed by assuming that the injected CR
-energy in the last 650~Myrs make up 0.03\% of the thermal energy
-inside the virial radius, i.e.
-$\int_0^{R_{200}}\epsilon_\rmn{CRp,inj} \rmn{d}
-V\left(\int_0^{R_{200}}\epsilon_\rmn{th} \rmn{d}V\right)^{-1} =
+with $n_0=3.4\times10^{-3}\,\rmn{cm}^{-3}$.  The virial and core radii
+of Coma are given by $R_{200} = 2300\,\rmn{kpc}$ and $R_{\rmn{c}} =
+294\,\rmn{kpc}$, respectively.
+
+\AP{Can you please provide references for the following:} The bulk of the
+CRps are injected by relatively low Mach number shocks and
+parameterized by $f_\rmn{p,inj}(p) = C_\rmn{inj}\,p^{-2.5}$. The
+CRps trace the thermal gas with $C_\rmn{inj} \propto
+\eps_\rmn{th}^{\alpha_\rmn{CR,spat}}$, where the normalization is
+fixed by assuming that the injected CR energy in the last 650~Myrs
+make up 0.03\% of the thermal energy inside the virial radius, i.e.
+$\int_0^{R_{200}}\eps_\rmn{p,inj} \rmn{d}
+V\left(\int_0^{R_{200}}\eps_\rmn{th} \rmn{d}V\right)^{-1} =
 0.0003$. The spectrum of the initial CRp distribution is determined by
@@
 \begin{equation}
- f_\rmn{CRp,0} \propto \frac{\int_p^\infty f_\rmn{CRp,inj}(p') 
+ f_\rmn{p,0} \propto \frac{\int_p^\infty f_\rmn{p,inj}(p') 
 \rmn{d}p'}{\displaystyle\left|{{\rmn{d}p}\over{\rmn{d}t}}\right|_{\rm Coul}+\frac{p}{\tau_{\rm had}}}\,,
@@
 where we fix the normalization by requiring
-$\int_0^{R_{200}}\epsilon_\rmn{CRp,0}
-\rmn{d}V\left(\int_0^{R_{200}}\epsilon_\rmn{th} \rmn{d}V\right)^{-1} =
-0.003$. Similarly, the initial CRe distribution is given by the steady
-state between cooling (Coulomb, inverse Compton, and synchrotron) and
-injection of secondary CRes from $f_{CRp,0}$. We also include the
-continuous injection of secondary CRes during $\tau_\rmn{cl}$. The
-compressible turbulence responsible for reaccelerating both the CRps
-and CRes is parameterized by $I_0 \propto X_\rmn{tu} (n_{\rmn{e}}
-T)^{\alpha_\rmn{tu}}$. The diffusion constant $D_\rmn{pp}$ is
-calculated for each radial bin using
+$\int_0^{R_{200}}\eps_\rmn{p,0}
+\rmn{d}V\left(\int_0^{R_{200}}\eps_\rmn{th} \rmn{d}V\right)^{-1} =
+0.003$. \AP{not 0.0003?} Similarly, the initial CRe distribution is
+given by the steady state between cooling (Coulomb, inverse Compton,
+and synchrotron) and injection of secondary CRes from $f_\rmn{p,0}$. We
+also include the continuous injection of secondary CRes during
+$\tau_\rmn{cl}$. The compressible turbulence responsible for
+reaccelerating both the CRps and CRes is parameterized by $I_0 \propto
+X_\rmn{tu} (n_{\rmn{e}} T)^{\alpha_\rmn{tu}}$. The diffusion constant
+$D_{pp}$ is calculated for each radial bin using
 Eqns.~\ref{eq:dpp}-\ref{eq:Gamma_e}. All parameters and assumptions
@@
 We use a simple test-particle model for the CR acceleration and
-injection, where each shock inject CRs that trace a power-law in
+injection, where each shock injects CRs that trace a power-law in
 momentum,
 \begin{equation}
-  f(p,t) = C(t)\,p^{\alpha_\rmn{inj}}\,,\quad
+  f_\p(p,t) = C(t)\,p^{\alpha_\rmn{inj}}\,,\quad
   \alpha_\rmn{inj}=\frac{(\gamma_\rmn{ad}+1)\mathcal{M}^2}
@@
 ($u_2$) and the sound speed ($c_s$). The CR number density and CR
-energy density are derived from $n_\rmn{CR} =
-\int_{p_\rmn{inj}}^\infty \dd p\, f(p)$ and $\epsilon_\rmn{CR} =
-\int_{p_\rmn{inj}}^\infty \dd p\, f(p) \,T(p)$, respectively, where
-$T(p) = (\sqrt{1+p^2} -1)\, m\,c^2$ is the kinetic energy of a
+energy density are derived from
+\begin{eqnarray}
+n_\rmn{p} &=&
+\int_{p_\rmn{inj}}^\infty \dd p\, f_\p(p)\\
+\eps_\rmn{p} &=&
+\int_{p_\rmn{inj}}^\infty \dd p\, f_\p(p) \,E(p),
+\end{eqnarray}
+where $E(p) = (\sqrt{1+p^2} -1)\, m\,c^2$ is the kinetic energy of a
 particle with momentum $p$. We adopt a fit to Monte Carlo simulations
@@
   \label{eq:qinj}
-  p_\rmn{inj} &=& x_\rmn{inj} p_\rmn{th} = x_\rmn{inj} \sqrt{\frac{2 \,k T_2}{m c^2}}\,, \nonumber \\
+  p_\rmn{inj} &=& x_\rmn{inj} p_\rmn{th} = x_\rmn{inj} \sqrt{\frac{2 \,\kB T_2}{m c^2}}\,, \nonumber \\
   \rmn{where}\quad x_\rmn{inj} &\approx& 1.17 \frac{u_2}{p_{\rmn{th}}\,c} \left(1+
@@
   \label{eq:eta}
-  \eta_\rmn{CR,lin} =
+  \eta_\rmn{p,lin} =
   \frac{4}{\sqrt{\upi}}\,\frac{x_\rmn{inj}^3}{\alpha_\rmn{inj}-1}\,
@@
 \label{eq:CR_energy} 
-  \Delta\epsilon_\rmn{CR,lin} =
-  \eta_\rmn{CR,lin}(\mathcal{M})\,T_\rmn{CR}(\mathcal{M},p_\rmn{inj})\,n_\rmn{th}(T_2),
+  \Delta\eps_\rmn{p,lin} =
+  \eta_\rmn{p,lin}(\mathcal{M})\,n_\rmn{th}(T_2)
+  \,\frac{\eps_\p}{n_\p}
 \end{equation}
@@
   \zeta_\rmn{lin} =
-  \frac{\Delta\epsilon_\rmn{CR,lin}}{\Delta\epsilon_\rmn{diss}},
+  \frac{\Delta\eps_\rmn{p,lin}}{\Delta\eps_\rmn{diss}},
    \quad\mbox{where}\quad
-  \Delta\epsilon_\rmn{diss} = \epsilon_\rmn{th2} - \epsilon_\rmn{th0}\,\left(\frac{\rho_2}{\rho_0}\right)^{\gamma_\rmn{ad}}\,.
+  \Delta\eps_\rmn{diss} = \eps_\rmn{th2} - \eps_\rmn{th0}\,\left(\frac{\rho_2}{\rho_0}\right)^{\gamma_\rmn{ad}}\,.
 \label{eqn:energy_frac}  
@@
 The dissipated energy density in the downstream regime,
-$\Delta\epsilon_\rmn{diss}$, is given by the difference of the thermal
+$\Delta\eps_\rmn{diss}$, is given by the difference of the thermal
 energy densities in the pre- and post-shock regimes, corrected for the
@@
 $\alpha_\rmn{inj}$ impact $\zeta_\rmn{inj}$ via the mean energy per
-particle given by $T_\rmn{CR} = \epsilon_\rmn{CR}/n_\rmn{CR}$. This
+particle, $\eps_\rmn{p}/n_\rmn{p}$. This
 procedure conserves energy and is motivated by models of non-linear
@@
 slope is steepened by a maximum of $\sim 10$ per cent in low
-temperature regimes ($kT\sim 0.1$~keV), while the steepening is much
-smaller for high temperature regimes ($kT\sim 10$~keV) that are more
+temperature regimes ($\kB T\sim 0.1$~keV), while the steepening is much
+smaller for high temperature regimes ($\kB T\sim 10$~keV) that are more
 relevant for clusters. Since $p_\rmn{inj}$ remains fixed, so does the
-CR number density $n_\rmn{CR}$. Hence we can solve for the
-renormalized normalization constant $C_\rmn{sub}$ using $n_\rmn{CR}$
+CR number density $n_\rmn{p}$. Hence we can solve for the
+renormalized normalization constant $C_\rmn{sub}$ using $n_\rmn{p}$
 and Eqn.~\ref{eq:eta}:
@@
   \label{eq:Cp_sub}
-  C_\rmn{sub}=\eta_\rmn{CR,lin}\,(\alpha_\rmn{sub}-1)\,p_\rmn{inj}^{\alpha_\rmn{sub}-1}\,,
+  C_\rmn{sub}=\eta_\rmn{p,lin}\,(\alpha_\rmn{sub}-1)\,p_\rmn{inj}^{\alpha_\rmn{sub}-1}\,,
 \end{equation}
-where the new distribution function is given by $f(p,t)= C_\rmn{sub}
+where the new distribution function is given by $f_\p(p,t)= C_\rmn{sub}
 p^{-\alpha_\rmn{sub}}$. We set an upper limit on the ratio of
@@
 electrons and protons are indistinguishable. We therefore assume that
-CRp and CRe have the same distribution function $f_\rmn{CRe}(p) =
-K_\rmn{ep} f_\rmn{CRp}(p)$, with a different normalization (due to
+CRp and CRe have the same distribution function $f_\rmn{e}(p) =
+K_\rmn{ep} f_\rmn{p}(p)$, with a different normalization (due to
 differing acceleration efficiencies) $K_\rmn{ep}=0.1$ \citep[which is
@@
 Eqn.~\ref{eq:Creacc} we see that the CRps with a spectral index of
-$\alpha_\rmn{CR}\approx2.5$ approximately gain a factor $\Delta
+$\alpha_\rmn{p}\approx2.5$ approximately gain a factor $\Delta
 C_\rmn{reacc.} \sim
@@
 of $D_\rmn{pp}(R)\propto
-\epsilon_\rmn{th}(R)^{\alpha_\rmn{tu}-1}\sqrt{T(R)}$. This
+\eps_\rmn{th}(R)^{\alpha_\rmn{tu}-1}\sqrt{T(R)}$. This
 signals that the problem is generic and requires either additional

### 2016-05-01 paper.tex
Added files via upload

@@
 t+\bvel\bcdot\bnabla$ is the Lagrangian derivative, $\bvel$ is the gas
-velocity, $|dp/dt|$ represents radiative (rad) and Coulomb (Coul)
-losses, \AP{please insert formulae:}
+velocity, $|dp/dt|$ represents radiative
+\citep[rad,][]{1979rpa..book.....R} and Coulomb
+\citep[Coul,][]{1972Phy....60..145G} losses, \AP{please insert
+  formulae: -- done}
 \begin{eqnarray}
-  \left|\frac{dp}{dt}\right|_{\rm Coul}
-  &=& \\
-  \left|\frac{dp}{dt}\right|_{\rm rad~}
-  &=& 
+   \left|\frac{dp}{dt}\right|_{\rm Coul} &=& \frac{3\,\sigma_\rmn{T}\,n_e\,c}{2\, \beta^2}
+  \left[\ln\left(\frac{m_e c^2 \beta \sqrt{\gamma-1}}{\hbar\,\omega_\rmn{plasma}}\right)\right.\nonumber \\
+    &-&\ln(2)\left(\frac{\beta^2}{2}+\frac{1}{\gamma}\right)+\frac{1}{2}+
+    \left.\left(\frac{\gamma-1}{4\gamma}\right)^2\right]\,, \\
+  \rmn{where} &\,& \beta = p/\sqrt{1+p^2}\,,\qquad \gamma=\sqrt{1+p^2}\,, \quad\rmn{and}\nonumber \\
+  \left|\frac{dp}{dt}\right|_{\rm rad~} &=& \frac{4}{3}\frac{\sigma_\rmn{T}}{m_ec}\,
+  \frac{p^2}{\beta}\,\left[1+\left(\frac{B}{B_\rmn{CMB}}\right)^2\right]\,.
 \end{eqnarray}
-$D_{pp}$ is the momentum space diffusion coefficient (see
-Sect.~\ref{sec:reacc}), and $Q_{\rmn{e}}$ denotes the injection rate
-of primary and secondary electrons in the ICM (see
+Here $\omega_\rmn{plasma} = \sqrt{4\pi e^2 n_e / m_e}$ is the plasma
+frequency, $n_e$ is the number density of free electrons, and
+$\sigma_\rmn{T}= 8\pi e^4/3(m_e c^2)^2$ is the Thomson cross
+section. The {\it rms} magnetic field strength is denoted by $B$ and
+the equivalent field strength of the cosmic-microwave background is
+given by $B_\rmn{CMB} = 3.24 (1 + z)^2\mu\rmn{G}$, where $z$ denotes
+the redshift. In the peripheral cluster regions, where $B <<
+B_\rmn{CMB}$, the CRes loose virtually all their energy by means of
+inverse Compton emission. $D_{pp}$ is the momentum space diffusion
+coefficient (see Sect.~\ref{sec:reacc}), and $Q_{\rmn{e}}$ denotes the
+injection rate of primary and secondary electrons in the ICM (see
 Sect.~\ref{sec:cosmo_sim}). The first term containing the expression
@@
 approximation, $\varv_{\rmn{A}}$ is the Alfv\'en speed,
-$Q_{\rmn{p}}(p,t)$ denotes the injection rate of shock accelerated
+and $Q_{\rmn{p}}(p,t)$ denotes the injection rate of shock accelerated
 CRps as a function of momentum $p$ and time $t$ (see
-Sect.~\ref{sec:cosmo_sim}), and $\tau_{\rm had}$ is the timescale of
+Sect.~\ref{sec:cosmo_sim}). The timescale of
 hadronic losses that produce pions via CRp collisions with thermal
-protons of the ICM \cite[e.g.][]{brunetti11}.
-\AP{please insert formulae:}
+protons of the ICM is given by 
+\AP{please insert formulae: -- done}
 \begin{eqnarray}
-  \tau_{\rm had} = 
+  \tau_{\rm had} = \frac{1}{c\,n_\rmn{th}\,\sigma^{+/-,0}(p)}\,
 \end{eqnarray}
+where we use the cross-section, $\sigma^{+/-,0}(p)$, given by the
+fitting formula in \citep{1986ApJ...307...47D}.
 
@@
 turbulence, $k_0= 2\upi/\lambda_0$ with $\lambda_0 =100~\mbox{kpc}$,
-that is in line with previous work \citep{brunetti07,brunetti11}. Note
-that this length scale defines an eddy turn-over time
+that is in line with previous work
+\citep{2006MNRAS.366.1437S,brunetti07,brunetti11}. Note that this
+length scale defines an eddy turn-over time
 $\tau_{\rmn{eddy}}\sim2\upi\lambda_0/V_0\sim1.2$~Gyr with
@@
 with $n_0=3.4\times10^{-3}\,\rmn{cm}^{-3}$.  The virial and core radii
-of Coma are given by $R_{200} = 2300\,\rmn{kpc}$ and $R_{\rmn{c}} =
-294\,\rmn{kpc}$, respectively.
-
-\AP{Can you please provide references for the following:} The bulk of the
-CRps are injected by relatively low Mach number shocks and
-parameterized by $f_\rmn{p,inj}(p) = C_\rmn{inj}\,p^{-2.5}$. The
-CRps trace the thermal gas with $C_\rmn{inj} \propto
-\eps_\rmn{th}^{\alpha_\rmn{CR,spat}}$, where the normalization is
-fixed by assuming that the injected CR energy in the last 650~Myrs
-make up 0.03\% of the thermal energy inside the virial radius, i.e.
-$\int_0^{R_{200}}\eps_\rmn{p,inj} \rmn{d}
+of Coma are given by $R_{200} = 2300\,\rmn{kpc}$
+\citep{2002ApJ...567..716R} and $R_{\rmn{c}} = 294\,\rmn{kpc}$,
+respectively.
+
+\AP{Can you please provide references for the following: -- check if
+  ok, the numbers are taken from our simulated g72a cluster. It should
+  be more clear now...} The bulk of the CRps are injected by
+relatively low Mach number shocks and parameterized by
+$f_\rmn{p,inj}(p) = C_\rmn{inj}\,p^{-\alpha_\rmn{inj}}$, where
+$\alpha_\rmn{inj}\approx 2.5$ in our simulations. The CRps
+approximately trace the thermal gas with $C_\rmn{inj} \propto
+\eps_\rmn{th}^{\alpha_\rmn{CR,spat}}$
+\citep{pinzke10,2016MNRAS.459...70V}, where the normalization is fixed
+by the injected CR energy in the last 650~Myrs. Our simulations show
+that it roughly make up 0.03\% of the thermal energy inside the virial
+radius, i.e.  $\int_0^{R_{200}}\eps_\rmn{p,inj} \rmn{d}
 V\left(\int_0^{R_{200}}\eps_\rmn{th} \rmn{d}V\right)^{-1} =
@@
 \rmn{d}V\left(\int_0^{R_{200}}\eps_\rmn{th} \rmn{d}V\right)^{-1} =
-0.003$. \AP{not 0.0003?} Similarly, the initial CRe distribution is
-given by the steady state between cooling (Coulomb, inverse Compton,
-and synchrotron) and injection of secondary CRes from $f_\rmn{p,0}$. We
+0.003$. \AP{not 0.0003? -- No, the injected energy in the last 650 Mys
+  is smaller then the energy density of the CRs injected during the
+  formation of the cluster. I estimated the difference to be about a
+  factor 10.} Similarly, the initial CRe distribution is given by the
+steady state between cooling (Coulomb, inverse Compton, and
+synchrotron) and injection of secondary CRes from $f_\rmn{p,0}$. We
 also include the continuous injection of secondary CRes during
@@
 which the seeds undergo Fermi-II reacceleration can reproduce the Coma
-RH profile at 352~MHz. In the panel {\it Brunetti et al. (2012)} we
-show that without CR streaming or a flat turbulent profile, our
-simulations of reaccelerated CRs produce radio profiles that are too
-steep. Indeed, even using the assumptions of previous work -- where
-complete freedom in the seed population was allowed -- it is not
-possible to reproduce observations in both frequencies in any
-model. Note that decreasing acceleration efficiency with radius does
-not change this conclusion much because of the weak radial dependence
-of $D_\rmn{pp}(R)\propto
-\eps_\rmn{th}(R)^{\alpha_\rmn{tu}-1}\sqrt{T(R)}$. This
-signals that the problem is generic and requires either additional
-modifications to the plasma physics of acceleration or a better
-understanding of potential observational systematics. In addition
-there are differences in the simulated density and temperature
-profiles in comparison to the observed profile in Coma that impact the
-CR abundance as well as cooling and reacceleration.
+RH profile at 352~MHz. \AP{It is also clear that without turbulent
+  reacceleration, the simulated radio profiles are too steep.} In the
+panel {\it Brunetti et al. (2012)} we show that without CR streaming
+or a flat turbulent profile, our simulations of reaccelerated CRs
+produce radio profiles that are too steep. Indeed, even using the
+assumptions of previous work -- where complete freedom in the seed
+population was allowed -- it is not possible to reproduce observations
+in both frequencies in any model. Note that decreasing acceleration
+efficiency with radius does not change this conclusion much because of
+the weak radial dependence of $D_\rmn{pp}(R)\propto
+\eps_\rmn{th}(R)^{\alpha_\rmn{tu}-1}\sqrt{T(R)}$. This signals that
+the problem is generic and requires either additional modifications to
+the plasma physics of acceleration or a better understanding of
+potential observational systematics. In addition there are differences
+in the simulated density and temperature profiles in comparison to the
+observed profile in Coma that impact the CR abundance as well as
+cooling and reacceleration.
 
@@
 B/\umu\rmn{G} (\gamma/10^4)^2\,\rmn{GHz}$, this translates into a
-spectral steepening of the radio spectrum (see
-Fig.~\ref{fig:sync_spectrum}). A given radio window samples higher
-energy electrons for a decreasing field strength in the cluster
+spectral steepening of the radio spectrum (see \AP{the left panel of
+  Fig.~\ref{fig:sync_spectrum}} where the continuous injection of
+secondary CRes is absent). A given radio window samples higher energy
+electrons for a decreasing field strength in the cluster
 outskirts. Hence, the spectral steepening with energy should translate
@@
 that the radio luminosity from clusters in the OFF-state (DSA only)
-and ON-state (DSA and reacceleration) differ by about a factor 10 in
-all our three models. However, note that for \Mprimary, the primary
-CRes that generate most of the radio emission from the cluster in the
+and ON-state (DSA and reacceleration) differ by about a factor 10-20
+in all our three models. \AP{This means that the secondary CRes are
+  dominated by the reaccelerated fossil CRes and not from the CRes
+  produced by reaccelerated CRps. However, for high frequencies
+  ($\nu_\rmn{syn}\gtrsim$ GHz) where synchrotron cooling is more
+  efficient than reacceleration, the emission is dominated by the CRes
+  produced in the continuous injection of electrons from reaccelerated
+  CRps. It is also worth mentioning that the radio emission from
+  secondary CRes are smoothly distributed around the cluster because
+  of the continuous injection, hence the it is not dominated by
+  outliers.} However, \sout{note that} for \Mprimary, the primary CRes
+that generate most of the radio emission from the cluster in the
 OFF-state are dominated by only a small fraction of the CRes. These
@@
 primary or secondary seed population of electrons observationally?
-One possibility that is relative insensitive to adopted parameters in
-our models is to use high-frequency radio observations (with e.g., the
+\AP{I do not understand the next scentence, could you clarify?} One
+possibility that is relative insensitive to adopted parameters in our
+models is to use high-frequency radio observations (with e.g., the
 Jansky Very Large Array) where turbulent reacceleration (which has a
@@
   and redshift]{2002A&A...396L..17E,Pfrommer:2003mk}. Hence the
-subdominant hadronic radio emission may only be detectable in steep
-spectrum radio sources \citep{2008Natur.455..944B}, which exhibit a
-cutoff at lower radio frequencies and are thought to represent dying
-RHs as a result of the decaying turbulence after a
-merger. Alternatively, one could attempt to reconstruct the intrinsic
-high-frequency RH spectrum by filling in the missing flux due to the
-Sunyaev-Zel'dovich effect by precise measurements of the Compton-$y$
-parameter at microwave frequencies. Another possibility would consist
-in stacking the radio data of radio-quiet clusters that due not
-exhibit RH emission \citep{2011ApJ...740L..28B}. This may reveal the
+subdominant \sout{hadronic} radio emission \AP{from freshly injected
+  secondary CRes} may only be detectable in steep spectrum radio
+sources \citep{2008Natur.455..944B}, which exhibit a cutoff at lower
+radio frequencies and are thought to represent dying RHs as a result
+of the decaying turbulence after a merger. Alternatively, one could
+attempt to reconstruct the intrinsic high-frequency RH spectrum by
+filling in the missing flux due to the Sunyaev-Zel'dovich effect by
+precise measurements of the Compton-$y$ parameter at microwave
+frequencies. Another possibility would consist in stacking the radio
+data of radio-quiet clusters that do not exhibit RH emission
+\AP{individually} \citep{2011ApJ...740L..28B}. This may reveal the
 glow of radio emission due to steady state secondary
@@
 cooling, and will not be visible at high energies (see
-Fig.~\ref{fig:sync_spectrum}). We will pursue further implications and
-distinguishing characteristics of these competing models in future
-work.
+Fig.~\ref{fig:sync_spectrum}). \AP{Finally we want to mention that in
+  the near future we hope to gain valuable information about the
+  turbulent profile in galaxy clusters from the recently launched
+  X-ray satellite ASTRO-H. Alternatively, as magnetohydrodynamic
+  simulations improve, these can provide valuable insight about the
+  profile and the total energy of turbulence in clusters. This will
+  further help us to distinguish the three different models from each
+  other.} We will pursue further implications and distinguishing
+characteristics of these competing models in future work.
 

### 2016-05-06 paper.tex
Peng's changes: 1st shot at dummy's guide

@@
 
+\subsection{Dummy's guide} 
+\label{sec:dummy}
+
+All of the physics of turbulent reacceleration is effectively encapsulated in the diffusion coefficient, which can be rewritten as \citep{2015ApJ...800...60M}:
+\begin{equation}
+D_{\rm pp}(p) = \frac{ p^{2} \pi I_{\theta}(c_{s}/c)}{8 c} \langle k \rangle_{\rm W} \langle (\delta v_{c})^{2} \rangle
+\label{eqn:diffusion}
+\end{equation}
+where
+\begin{equation}
+\langle k \rangle_{\rm W} = \frac{1}{\langle \delta v_{c})^{2} \rangle} \int_{k_{\rm L}}^{k_{\rm c}} dk \, k \, W(k) \approx \frac{s-1}{2-s} k_{\rm L} \left( \frac{k_{\rm c}}{k_{\rm L}} \right)^{2-s} 
+\end{equation}
+is an energy-averaged wavenumber, $k_{\rm L}, k_{\rm c}$ are the wavenumbers associated with the outer scale and the cutoff scale respectively, and we have assumed a total energy spectrum (both kinetic and potential energy, where the two are assumed to be in equipartition \citep{sarkar11}):
+\begin{equation}
+W(k) = \frac{(s-1) \langle \delta v_{c})^{2} \rangle}{k_{\rm L}} \left( \frac{k}{k_{\rm L}} \right)^{-2} 
+\label{eqn:Wk}
+\end{equation}
+which defines the normalization $\langle \delta v_{c})^{2} \rangle$ (the subscript 'c' emphasizes that we specialize to compressive modes).
+Intuitively, we can understand the form of the the diffusion coefficient from the fact that for second-order Fermi acceleration, $\dot{p} \sim \Delta p/\tau \sim \langle k c \rangle_{\rm W} (v_{\rm c}/c)^{2}$, where $\tau^{-1} \sim \langle k c \rangle_{\rm W}$ is the energy averaged wave-particle interaction rate, and $\Delta p \sim p (V_{c}/c)^{2}$ is the typical momentum change during wave particle scattering.
+Thus:
+\begin{equation}
+D_{\rm pp} \sim p \dot{p} \sim p^{2} \langle k c \rangle_{\rm W} \left( \frac{v_{c}}{c} \right)^{2}. 
+\end{equation}
+{\bf Christoph: note I agree with your expression except substituted $v_{c}$ for $V_{ph}$, since the diffusion rate must depend on the amplitude of the turbulence.}
+
+Equations \ref{eqn:diffusion} and \ref{eqn:Wk} makes clear the important aspects of turbulence: the energy in compressive modes $\langle (\delta v_{c})^{2} \rangle$, the inner and outer scale $k_{\rm c}, k_{\rm L}$, and the slope of the energy spectrum $s$.
+All of these can vary spatially and temporally.
+
+{\bf Energy in compressive modes} The total turbulence energy is typically $\sim 15-70\%$ of the thermal energy in a cluster \citep{vazza11}; it rises rapidly during a merger.
+The compressible component is $\sim 20-40\%$ of the total turbulent energy, and shows more rapid temporal variations compared to the compressible component \citep{2013ApJ...771..131B,2015ApJ...800...60M}.
+It is worth noting that in the subsonic regime of the solar wind \citep{yao11,howes12}, as well as most idealized calculations of turbulent driving, there is relatively little energy in the fast mode.
+For instance, the fudicial simulations of \citep{lynn14} with ${\mathcal M}_{s} \sim 0.35, \beta \sim 1$ show 50\%, 45\%, 5\% of the turbulent energy density is in the Alfven, slow, and fast modes respectively.
+For higher $\beta \sim 3-10$, they find that the proportion of energy in fast modes drops to $< 1\%$, while the fraction of energy in the slow mode remains roughly the same.
+Similarly, \citep{kowal10} find that the fast mode is highly subdominant (see their Table 2); for the run most relevant to cluster conditions ${\mathcal M}_{\rm s} \sim 0.7, \beta \sim 10$, they find $\sim 42\%, 6\%$ of turbulent energy in slow and fast modes respectively.
+These simulations are roughly consistent with theoretical estimates of $U_{\rm fast}/U_{\rm slow} \sim {\mathcal M}_{s}^{2}/{\mathcal M}_{A}$ \citep{cho03}.
+By contrast, MHD simulations of galaxy clusters find a large fraction ($\sim 25$\%) of turbulent energy in fast modes \citep{2013ApJ...771..131B}.
+This is likely due to the compressive nature of turbulent driving (transonic infall and merger), whereas idealized simulations tend to use incompressible solenoidal driving and allowing compressive fluctuations to develop on their own.
+
+In the high $\beta$, subsonic conditions of the ICM, the Alfven/slow modes are exactly/approximately incompressible, and so the approximate identification of compressive modes with fast modes is valid.
+We therefore take $\sim 25\%$ of the turbulent energy density in compressive fast modes as a reasonable baseline estimate \citep{2013ApJ...771..131B,2015ApJ...800...60M}.
+If a large fraction of energy is in slow modes, then resonant broadening of wave-particle interactions can render slow modes an efficient acceleration mechanism \citep{lynn14}, as we discuss briefly in \S\ref{?}.
+
+{\bf Slope of the energy spectrum $s$} At large scales, turbulent motions are subsonic (${\mathcal M}_{s} \sim 0.2-0.5$) but super-Alfvenic (${\mathcal M}_{s} \sim 5$).
+Thus, except in the case where motions are transonic and weak shocks become important, motions are fundamentally hydrodynamic and turbulence follows a Kolmogorov ($s=5/3$) spectrum.
+However, while the turbulent energy density $U_{\rm t} \propto l^{2/3}$ decreases at small scales, the magnetic energy density is scale-independent.
+Thus, at some scale $l_{\rm A} \sim l_{o} {\mathcal M}_{\rm A}^{-3}$, where $U_{\rm turb} \sim U_{\rm B}$, the magnetic field becomes dynamically important, and turbulence transitions to the MHD regime.
+Theory \citep{goldreich95,chandran05} and simulations \citep{cho03} show that in the MHD regime, the Alfven and slow modes have a shallower Kraichnan spectrum ($s=3/2$), with relatively little coupling between the incompressible and compressible modes \citep{cho02,cho03} -- though if weak shocks are important, $s=2$ may be more appropriate (see discussion below).
+
+Since the Kraichnan spectrum is critical in what follows, it is worthwhile taking a moment to recount the origin of the spectral slope $s$ and the cascade rate.
+In the magnetically dominated regime, two counterpropagating wave packets of scale $l$ interact on an Alfven time $\tau_{\rm A}=l/v_{\rm A}$, rather than the eddy turnover time $\tau_{\rm edd} = l/u_{\rm l}$.
+Since $\tau_{\rm A} \ll \tau_{\rm edd}$, each interaction results in a small velocity change $\delta u_{\rm l} \sim u_{\rm l} (\tau_{\rm A}/\tau_{\rm edd})$.
+If these changes behave like a random walk, the cascade time $\tau_{\rm l}$ it takes for an eddy to become non-linear ($\Delta u \sim u_{\rm l})$ and cascade to smaller scales is $u_{\rm l} \sim \delta u_{\rm l} (\tau_{\rm l}/\tau_{\rm A})^{1/2} \sim u_{\rm l} \tau_{\rm A}/\tau_{\rm edd} (\tau_{\rm l}/\tau_{\rm A})^{1/2}$, which we can solve to obtain the cascade time:
+\begin{equation}
+\tau_{\rm l} \sim \left(\frac{\tau_{\rm edd}}{\tau_{\rm A}}\right)^{2} \tau_{\rm A} \sim \frac{l v_{A}}{u_{\rm l}^{2}} 
+\end{equation}
+where we have implicitly assumed isotropy.
+This implies a dissipation rate $\epsilon \sim u_{l}^{2}/\tau_{l} \sim u_{l}^{4}/(l v_{\rm A})$, or $u_{\rm l} \sim (\epsilon l v_{A})^{1/4}$.
+Thus, since $k E(k)\sim u_{\rm l}^{2}$, this gives a kinetic energy spectrum:
+\begin{equation}
+E(k) \sim (\epsilon v_{\rm A})^{1/2} k^{-3/2}.
+\end{equation}
+
+Finally, if turbulence is transonic ($M_{\rm s} \sim {\mathcal O}(1)$), then compressible modes can dissipate in weak shocks, as seen in decompositions of the velocity field into solenoidal/compressible components both in idealized simulations \citep{kowal10,porter15}, and cosmological hydrodynamic simulations \citep{2015ApJ...800...60M}.
+The compressible component has a steep Burgers ($s=2$) spectrum.
+Burgers turbulence is distinct from other forms of turbulence in that it violates locality in k-space--i.e., power does not gradually cascade, but instead can directly jump from large to small scales via a network of weak shocks.
+Since the Fourier transform of a step function goes as $k^{-1}$, Burgers turbulence has a power spectrum of $P(k) \propto k^{-2}$.
+If we contrast the different velocity scalings: $v \propto l^{1/4}$ (Kraichnan), $v \propto l^{1/3}$ (Kolmogorov), $v \propto l^{1/2}$ (Burgers), we see that because of its dissipative nature, Burgers turbulence is the least efficient at transferring energy towards the small scales needed (since the wave particle interaction rate scales as $k$) for efficient acceleration.
+If Burgers turbulence dominates, then particle acceleration rates are too slow in the face of cooling processes to explain radio halos \citep{2015ApJ...800...60M}.
+
+Given the lack of consensus on the fast mode spectrum, and the fact that turbulent reacceleration is not a viable explanation for radio halos if the spectrum is Burgers-like, we assume a Kraichnan spectrum.
+
+{\bf Inner and outer scale}
+
+{\bf Timescales}
+
+{\bf Scaling solutions} Since the diffusion time is independent of energy (the so-call 'hard sphere' approximation), analytic solutions are possible.
+The steady state solution is a power-law with a cutoff above a characteristic momentum $p_{\rm eq}$, defined by $t_{\rm acc} \equiv t_{\rm cool} (p_{\rm eq})$ \citep{stawarz08}:
+\begin{equation}
+n(p) \propto \left \{
+\begin{array}{ll}
+p^{-\sigma} & \quad \text{for} \quad p \ll p_{\text{eq}} \, , \\
+p^2 {\rm e}^{-p/p_{\text{eq}}} & \quad \text{for} \quad p \sim p_{\text{eq}} \,.
+\end{array}
+\right.
+\end{equation}
+%
+where $-\sigma = 1/2 - \sqrt{9/4 +
+  t_\text{acc}/t_\text{esc}}$ asymptotically approaches $-1$
+as $t_\text{acc}/t_\text{esc} \rightarrow 0$.
+
+%%%Fast modes can become more important in highly supersonic turbulence, but this is not relevant to clusters.
+The magnetic energy density in fast modes scales as $\delta B^{2}_{\rm F} \sim \rho \delta v_{\rm F}^{2}/\beta$ (since magnetic restoring forces
+
 \subsection{Turbulent reacceleration}

### 2016-05-06 paper.tex
restructuring paper, editing dummy's guide

--- 2016-05-01 paper.tex
@@
 \newcommand{\dd}{\mathrm{d}}
-\newcommand{\Vph}{V_\mathrm{ph}}
+\newcommand{\Vph}{\varv_\mathrm{ph}}
 \newcommand{\mug}{\umu G}
@@
     cluster. The red dash-dotted line shows the required distribution
-    of seed CRps that generate secondary electrons via p-p collisions
-    required to reproduce Coma radio brightness observations after
-    Fermi-II reacceleration \citep{brunetti12}. The blue solid line
-    shows the distribution of fossil CRps found in cosmological
-    simulations, which disagrees with the required profile. To better
-    compare the two models in this figure, we normalize the required
-    distribution of CRps by fixing the total CRp energy $E_\rmn{CR}$
-    to 0.3 percent of the total thermal energy, consistent with
-    observations \citep{2014ApJ...787...18A,2012ApJ...757..123A}.}
+    of seed CRps that generate secondary electrons via proton-proton
+    (p-p) collisions required to reproduce Coma radio brightness
+    observations after Fermi-II reacceleration \citep{brunetti12}. The
+    blue solid line shows the distribution of fossil CRps found in
+    cosmological simulations, which disagrees with the required
+    profile. To better compare the two models in this figure, we
+    normalize the required distribution of CRps by fixing the total
+    CRp energy $E_\rmn{CR}$ to 0.3 percent of the total thermal
+    energy, consistent with observations
+    \citep{2014ApJ...787...18A,2012ApJ...757..123A}.}
   \label{fig:Edens}
@@
 % --- section: Method --- %
-\section{Method}
+\section{Cosmic ray transport}
 
@@
 
-\SPO{explain overall picture, $\tau_\rmn{d}$ vs. $\tau_{\rmn{cl}}$}
-
-\subsection{Cosmic ray transport}
+\subsection{Basic equations}
 As previously noted, secondaries produced by shock accelerated CRp
@@
 t+\bvel\bcdot\bnabla$ is the Lagrangian derivative, $\bvel$ is the gas
-velocity, $|dp/dt|$ represents radiative
-\citep[rad,][]{1979rpa..book.....R} and Coulomb
-\citep[Coul,][]{1972Phy....60..145G} losses, \AP{please insert
-  formulae: -- done}
+velocity, $|dp/dt|$ represents Coulomb
+\citep[Coul,][]{1972Phy....60..145G} and radiative
+\citep[rad,][]{1979rpa..book.....R} losses, respectively,
 \begin{eqnarray}
@@
     \left.\left(\frac{\gamma-1}{4\gamma}\right)^2\right]\,, \\
-  \rmn{where} &\,& \beta = p/\sqrt{1+p^2}\,,\qquad \gamma=\sqrt{1+p^2}\,, \quad\rmn{and}\nonumber \\
   \left|\frac{dp}{dt}\right|_{\rm rad~} &=& \frac{4}{3}\frac{\sigma_\rmn{T}}{m_ec}\,
@@
 \end{eqnarray}
-Here $\omega_\rmn{plasma} = \sqrt{4\pi e^2 n_e / m_e}$ is the plasma
+Here $\beta = p/\sqrt{1+p^2}$ is the dimensionless velocity of CRs,
+$\gamma=\sqrt{1+p^2}$ is the Lorentz factor of CRs,
+$\omega_\rmn{plasma} = \sqrt{4\pi e^2 n_e / m_e}$ is the plasma
 frequency, $n_e$ is the number density of free electrons, and
@@
 given by $B_\rmn{CMB} = 3.24 (1 + z)^2\mu\rmn{G}$, where $z$ denotes
-the redshift. In the peripheral cluster regions, where $B <<
+the redshift. In the peripheral cluster regions, where $B \ll
 B_\rmn{CMB}$, the CRes loose virtually all their energy by means of
 inverse Compton emission. $D_{pp}$ is the momentum space diffusion
-coefficient (see Sect.~\ref{sec:reacc}), and $Q_{\rmn{e}}$ denotes the
-injection rate of primary and secondary electrons in the ICM (see
-Sect.~\ref{sec:cosmo_sim}). The first term containing the expression
-$\bnabla\bcdot \bvel$ represents Fermi-I acceleration and the second
-term of this form describes adiabatic gains and losses.
+coefficient (see Sects.~\ref{sec:dummy} and \ref{sec:reacc}), and
+$Q_{\rmn{e}}$ denotes the injection rate of primary and secondary
+electrons in the ICM (see Sect.~\ref{sec:cosmo_sim}). The first term
+containing the expression $\bnabla\bcdot \bvel$ represents Fermi-I
+acceleration and the second term of this form describes adiabatic
+gains and losses.
 
@@
 protons of the ICM is given by 
-\AP{please insert formulae: -- done}
 \begin{eqnarray}
-  \tau_{\rm had} = \frac{1}{c\,n_\rmn{th}\,\sigma^{+/-,0}(p)}\,
+  \tau_{\rm had} = \left[c\,n_\rmn{th}\,\sigma^{+/-,0}(p)\right]^{-1}\,,
 \end{eqnarray}
@@
 
-\subsection{Turbulent reacceleration}
+\subsection{Dummy's guide} 
+\label{sec:dummy}
+
+All of the physics of turbulent reacceleration is effectively encapsulated in the diffusion coefficient, which can be rewritten as \citep{2015ApJ...800...60M}:
+\begin{equation}
+D_{pp}(p) = \frac{ p^{2} \pi I_{\theta}(c_{s}/c)}{8 c} \langle k \rangle_{\mathcal{W}} \langle (\delta v_{\rm c})^{2} \rangle
+\label{eqn:diffusion}
+\end{equation}
+\SPO{define $I_{\theta}(c_{s}/c)$ or explain its meaning in words and point to the definition provided in the next subsection.}
+where
+\begin{equation}
+\langle k \rangle_{\mathcal{W}} = \frac{1}{\langle (\delta \varv_{\rm c})^{2} \rangle} \int_{k_{\rm L}}^{k_{\rm cut}} dk \, k \, \mathcal{W}(k) \approx \frac{s-1}{2-s} k_{\rm L} \left( \frac{k_{\rm cut}}{k_{\rm L}} \right)^{2-s}
+\end{equation}
+is an energy-averaged wavenumber, $k_{\rm L}, k_{\rm cut}$ are the wavenumbers associated with the outer scale and the cutoff scale respectively, and we have assumed a total energy spectrum (both kinetic and potential energy, where the two are assumed to be in equipartition \citep{sarkar11}):
+\begin{equation}
+\mathcal{W}(k) = \frac{(s-1) \langle (\delta \varv_{\rm c})^{2} \rangle}{k_{\rm L}} \left( \frac{k}{k_{\rm L}} \right)^{-s} 
+\label{eqn:Wk}
+\end{equation}
+which defines the normalization $\langle (\delta \varv_{\rm c})^{2} \rangle$ (the subscript 'c' emphasizes that we specialize to compressive modes).
+Intuitively, we can understand the form of the the diffusion coefficient from the fact that for second-order Fermi acceleration, $\dot{p} \sim \Delta p/\tau \sim p\,\langle k c \rangle_{\mathcal{W}} (\delta \varv_{\rm c}/c)^{2}$, where $\tau^{-1} \sim \langle k c \rangle_{\mathcal{W}}$ is the energy averaged wave-particle interaction rate, and $\Delta p \sim p (\delta \varv_{\rm c}/c)^{2}$ is the typical momentum change during wave particle scattering.
+Thus:
+\begin{equation}
+D_{pp} \sim p \dot{p} \sim p^{2} \langle k c \rangle_{\mathcal{W}} \left( \frac{\delta \varv_{\rm c}}{c} \right)^{2}. 
+\end{equation}
+
+Equations \ref{eqn:diffusion} and \ref{eqn:Wk} make the important aspects of turbulence clear: the energy in compressive modes $\langle (\delta v_{\rm c})^{2} \rangle$, the inner and outer scale ($k_{\rm cut}$ and $k_{\rm L}$), and the slope of the energy spectrum $s$.
+All of these can vary spatially and temporally.
+
+{\bf Energy in compressive modes} The total turbulence energy is typically $\sim 15-70\%$ of the thermal energy in a cluster \citep{vazza11}; it rises rapidly during a merger.
+The compressible component is $\sim 20-40\%$ of the total turbulent energy, and shows more rapid temporal variations compared to the compressible component \citep{2013ApJ...771..131B,2015ApJ...800...60M}.
+It is worth noting that in the subsonic regime of the solar wind \citep{yao11,howes12}, as well as most idealized calculations of turbulent driving, there is relatively little energy in the fast mode.
+For instance, the fidiucial simulations of \citet{lynn14} with a sonic Mach number ${\mathcal M}_{\rm s} \sim 0.35$ and a plasma beta factor of $\beta \sim 1$ show that 50\%, 45\%, 5\% of the turbulent energy density is in the Alfv{\'e}n, slow, and fast modes, respectively.
+For higher $\beta \sim 3-10$, they find that the proportion of energy in fast modes drops to $< 1\%$, while the fraction of energy in the slow mode remains roughly the same.
+Similarly, \citet{kowal10} find that the fast mode is highly subdominant (see their Table 2); for the run most relevant to cluster conditions ${\mathcal M}_{\rm s} \sim 0.7, \beta \sim 10$, they find $\sim 42\%, 6\%$ of turbulent energy in slow and fast modes respectively.
+These simulations are roughly consistent with theoretical estimates of $U_{\rm fast}/U_{\rm slow} \sim {\mathcal M}_{\rm s}^{2}/{\mathcal M}_{\rm A}$ \citep{cho03}.
+By contrast, MHD simulations of galaxy clusters find a large fraction ($\sim 25$\%) of turbulent energy in fast modes \citep{2013ApJ...771..131B}.
+This is likely due to the compressive nature of turbulent driving (transonic infall and merger), whereas idealized simulations tend to use incompressible solenoidal driving and allow compressive fluctuations to develop on their own.
+
+In the high-$\beta$, subsonic conditions of the ICM, the Alfv{\'e}n/slow modes are exactly/approximately incompressible, and so the approximate identification of compressive modes with fast modes is valid.
+We therefore take $\sim 25\%$ of the turbulent energy density in compressive fast modes as a reasonable baseline estimate \citep{2013ApJ...771..131B,2015ApJ...800...60M}.
+If a large fraction of energy is in slow modes, then resonant broadening of wave-particle interactions can render slow modes an efficient acceleration mechanism \citep{lynn14}, as we discuss briefly in \S\ref{?}.
+
+{\bf Slope of the energy spectrum $s$.} At large scales, turbulent motions are subsonic (${\mathcal M}_{\rm s} \sim 0.2-0.5$) but super-Alfv{\'e}nic (${\mathcal M}_{\rm A} \sim 5$).
+Thus, except in the case where motions are transonic and weak shocks become important, motions are fundamentally hydrodynamic and turbulence follows a Kolmogorov ($s=5/3$) spectrum.
+However, while the turbulent energy density $U_{\rm t} \propto l^{2/3}$ decreases at small scales, the magnetic energy density is scale-independent.
+Thus, at some scale $l_{\rm A} \sim l_{\rm o} {\mathcal M}_{\rm A}^{-3}$, where $U_{\rm turb} \sim U_{B}$, the magnetic field becomes dynamically important, and turbulence transitions to the MHD regime.
+Theory \citep{goldreich95,chandran05} and simulations \citep{cho03} show that in the MHD regime, the Alfv{\'e}n and slow modes have a shallower Kraichnan spectrum ($s=3/2$), with relatively little coupling between the incompressible and compressible modes \citep{cho02,cho03} -- though if weak shocks are important, $s=2$ may be more appropriate (see discussion below).
+
+Since the Kraichnan spectrum is critical in what follows, it is worthwhile taking a moment to recount the origin of the spectral slope $s$ and the cascade rate.
+In the magnetically dominated regime, two counterpropagating wave packets of scale $l$ interact on an Alfv{\'e}n time $\tau_{\rm A}=l/\varv_{\rm A}$, rather than the eddy turnover time $\tau_{\rm edd} = l/\varv_{\rm l}$.
+Since $\tau_{\rm A} \ll \tau_{\rm edd}$, each interaction results in a small velocity change $\delta \varv_{\rm l} \sim \varv_{\rm l} (\tau_{\rm A}/\tau_{\rm edd})$.
+If these changes behave like a random walk, the cascade time $\tau_{\rm l}$ it takes for an eddy to become non-linear ($\Delta \varv \sim \varv_{\rm l})$ and cascade to smaller scales is $\varv_{\rm l} \sim \delta \varv_{\rm l} (\tau_{\rm l}/\tau_{\rm A})^{1/2} \sim \varv_{\rm l} \tau_{\rm A}/\tau_{\rm edd} (\tau_{\rm l}/\tau_{\rm A})^{1/2}$, which we can solve to obtain the cascade time:
+\begin{equation}
+\tau_{\rm l} \sim \left(\frac{\tau_{\rm edd}}{\tau_{\rm A}}\right)^{2} \tau_{\rm A} \sim \frac{l \varv_{\rm A}}{\varv_{\rm l}^{2}} 
+\end{equation}
+where we have implicitly assumed isotropy.
+This implies a dissipation rate $\epsilon \sim \varv_{\rm l}^{2}/\tau_{\rm l} \sim \varv_{\rm l}^{4}/(l \varv_{\rm A})$, or $\varv_{\rm l} \sim (\epsilon l \varv_{A})^{1/4}$.
+Thus, since $k E(k)\sim \varv_{\rm l}^{2}$, this gives a kinetic energy spectrum:
+\begin{equation}
+E(k) \sim (\epsilon \varv_{\rm A})^{1/2} k^{-3/2}.
+\end{equation}
+
+Finally, if turbulence is transonic ($M_{\rm s} \sim {\mathcal O}(1)$), then compressible modes can dissipate in weak shocks, as seen in decompositions of the velocity field into solenoidal/compressible components both in idealized simulations \citep{kowal10,porter15}, and cosmological hydrodynamic simulations \citep{2015ApJ...800...60M}.
+The compressible component has a steep Burgers ($s=2$) spectrum.
+Burgers turbulence is distinct from other forms of turbulence in that it violates locality in k-space--i.e., power does not gradually cascade, but instead can directly jump from large to small scales via a network of weak shocks.
+Since the Fourier transform of a step function goes as $k^{-1}$, Burgers turbulence has a power spectrum of $P(k) \propto k^{-2}$.
+If we contrast the different velocity scalings: $\varv \propto l^{1/4}$ (Kraichnan), $\varv \propto l^{1/3}$ (Kolmogorov), $\varv \propto l^{1/2}$ (Burgers), we see that because of its dissipative nature, Burgers turbulence is the least efficient at transferring energy towards the small scales needed (since the wave particle interaction rate scales as $k$) for efficient acceleration.
+If Burgers turbulence dominates, then particle acceleration rates are too slow in the face of cooling processes to explain radio halos \citep{2015ApJ...800...60M}.
+
+Given the lack of consensus on the fast mode spectrum, and the fact that turbulent reacceleration is not a viable explanation for radio halos if the spectrum is Burgers-like, we assume a Kraichnan spectrum.
+
+{\bf Inner and outer scale}
+
+{\bf Timescales}
+
+{\bf Scaling solutions} Since the diffusion time is independent of energy (the so-call 'hard sphere' approximation), analytic solutions are possible.
+The steady state solution is a power-law with a cutoff above a characteristic momentum $p_{\rm eq}$, defined by $t_{\rm acc} \equiv t_{\rm cool} (p_{\rm eq})$ \citep{stawarz08}:
+\begin{equation}
+n(p) \propto \left \{
+\begin{array}{ll}
+p^{-\sigma} & \quad \text{for} \quad p \ll p_{\text{eq}} \, , \\
+p^2 {\rm e}^{-p/p_{\text{eq}}} & \quad \text{for} \quad p \sim p_{\text{eq}} \,.
+\end{array}
+\right.
+\end{equation}
+%
+where $-\sigma = 1/2 - \sqrt{9/4 +
+  t_\text{acc}/t_\text{esc}}$ asymptotically approaches $-1$
+as $t_\text{acc}/t_\text{esc} \rightarrow 0$.
+
+%%%Fast modes can become more important in highly supersonic turbulence, but this is not relevant to clusters.
+The magnetic energy density in fast modes scales as $\delta B^{2}_{\rm F} \sim \rho \delta v_{\rm F}^{2}/\beta$ (since magnetic restoring forces
+
+\subsection{Formalism for turbulent reacceleration}
 \label{sec:reacc}
@@
 matches the wave period,
-$\lambda_{\parallel}/v_{\parallel}=\tau_{\rmn{wave}}$. Note, the CRs'
+$\lambda_{\parallel}/\varv_{\parallel}=\tau_{\rmn{wave}}$. Note, the CRs'
 gyroradius does not enter the resonance condition. Hence the CRs that
@@
 
-\SPO{please check the following:} To order of magnitude, the
-momentum-space diffusion coefficient due to second-order Fermi-II
-acceleration scales as
-\begin{eqnarray}
-  D_{pp} \sim p\dot{p}
-  \sim p^2\langle kc\rangle_{\mathcal{W}} \left(\frac{\Vph}{c}\right)^2,
-\label{eq:dpp_oom}
-\end{eqnarray}
-since the force on a particle due to Fermi-II acceleration scales as
-$\dot{p}\sim p/\tau\sim p \langle kc\rangle_{\mathcal{W}} (\Vph/c)^2$
-where $\langle kc\rangle_{\mathcal{W}} (\Vph/c)^2$ is the wave
-energy-averaged wave-particle interaction rate. It can be shown that
-the particle pitch-angle averaged momentum-diffusion coefficient of
-isotropic particles that couple to fast magnetosonic modes via TTD
-resonance is \citep[][ Eqn. 47]{brunetti07}:
+It can be shown that the particle pitch-angle averaged
+momentum-diffusion coefficient of isotropic particles that couple to
+fast magnetosonic modes via TTD resonance is \citep[][
+  Eqn. 47]{brunetti07}:
 \begin{eqnarray}
@@
 \end{equation}
-Here $V_\rmn{ph}$ is the phase velocity of the fast magnetosonic waves
+Here $\Vph$ is the phase velocity of the fast magnetosonic waves
 given approximately by the sound speed, $\Vph \sim c_\rmn{s}$. For a
@@
 
-The profile of injected turbulence depends on the details of the
-merger such as time during the merger, the impact parameter, the
-merger mass ratio, and the degree of cluster anisotropy
-\citep{2015ApJ...800...60M}. We parametrize these uncertainties and
-assume that it scales with the thermal energy density to some
-power. Hence we assume volumetric injection rate of turbulent energy,
-$I_0\propto \eps_\rmn{th}^{\alpha_\rmn{tu}}$, and determine the
-normalization by requiring that the turbulent energy in compressible
-modes $E_\rmn{turb}=\int \int \mathcal{W}(k) \rmn{d}k \rmn{d}V =
-X_\rmn{tu} E_\rmn{th}$, where $E_\rmn{th}$ is the total thermal
-energy. We adopt a turbulent energy ratio $X_\rmn{tu}=0.2$ within the
-radio halo.\footnote{Simulations show that the compressible modes
-  contribute a factor $0.2-0.4$ to the total turbulent energy
-  \citep{2013ApJ...771..131B,2015ApJ...800...60M}. Furthermore, the
-  total turbulent energy, which can be decomposed into a slenoidal and
-  compressible component, is typically $\sim15-70$\% of the thermal
-  energy in a cluster \citep{2011A&A...529A..17V}; in agreement with
-  our adopted value of $X_\rmn{tu}$.} In this work we investigate
-different spatial models for injected turbulence. With the above
-choice of normalization, the turbulent energy density becomes
-$\eps_\rmn{turb} \propto
-\eps_\rmn{th}^{(\alpha_\rmn{tu}+1)/2}/T^{1/4}$, where $T$ is the
-temperature of the gas, $\alpha_\rmn{tu}= 0.67$ for \Mflatturb,
-$\alpha_\rmn{tu}= 0.82$ for \Mstream, and $\alpha_\rmn{tu}= 0.88$ for
-\Mprimary (see Figure~\ref{fig:turb} for visualization). \CP{These
-  models and scaling indices are not well motivated here, they would
-  better fit into the results section.}
-
-Note that in previous work on the Coma cluster, $\eps_\rmn{turb}
-\propto \eps_\rmn{th}$ was adopted which roughly corresponds to
-$\alpha_\rmn{tu}= 1$ \citep{brunetti12} and together with the
-different distributions for seed CRes constitute the main differences
-compared to our work. Our flatter turbulent profiles are motivated by
-fits to cosmological simulations
-\citep{2009ApJ...705.1129L,2010ApJ...725.1452S,2011A&A...529A..17V,2012ApJ...758...74B}
-and the range indicates uncertainties of the turbulent profile in
-Coma. Future observations (by Astro-H) and simulations will help to
-clarify this issue. Provided dissipation of turbulence in the ICM is
-collisionless, turbulent cascades of compressible modes become
-suppressed when thermal and relativistic particles resonantly interact
-with magnetosonic waves via TTD on a timescale $\Gamma^{-1}$ that
+Provided dissipation of turbulence in the ICM is collisionless,
+turbulent cascades of compressible modes become suppressed when
+thermal and relativistic particles resonantly interact with
+magnetosonic waves via TTD on a timescale $\Gamma^{-1}$ that
 approaches the cascading timescale given by $\tau_{kk} \approx
@@
 
-\begin{figure}
-  \includegraphics[width=1.0\columnwidth]{turb_profile_ratio_tot.eps}
-  \caption{The ratio of turbulent-to-thermal energy densities (solid
-    lines) and cumulative energies (dotted lines) in our three
-    models. The energy densities are parametrized as
-    $\eps_\rmn{turb} \propto
-    \eps_\rmn{th}^{(\alpha_{\rmn{tu}}+1)/2}/T^{1/4}$ and
-    normalized such that the total turbulent energy in compressible
-    modes $E_\rmn{turb}$ for each scenario makes up about 20\% of the
-    total thermal energy $E_\rmn{th}$ inside the radio halo
-    ($R_\rmn{RH}\approx0.6R_{200}$). The turbulent profiles explore
-    the uncertainty in the cluster turbulence and are motivated by the
-    cosmological simulation in
-    \citep{2009ApJ...705.1129L,2010ApJ...725.1452S,2011A&A...529A..17V}.}
-  \label{fig:turb}
-\end{figure}
-
-\SPO{this needs a rewrite in the light of an updated discussion of
-  $\tau_\rmn{d}$ vs. $\tau_{\rmn{cl}}$.}  For reference we show in
+\SPO{the following needs a rewrite in the light of an updated discussion of
+  $\tau_\rmn{d}$ vs. $\tau_{\rmn{cl}}$ and the dummy's guide.}  For reference we show in
 Table~\ref{tab:timescales} both the thermal quantities and the
@@
 
-\subsection{Scaling relations for turbulent reacceleration}
-
-\SPO{should this be moved to the preceeding section?}
 To understand the radial dependence of the diffusion constant we
@@
 
-\CP{Again the logic is skewed here: these models are derived from the
-  spatial profile of the synchrotron emission in Sect. 4. Hence
-  $D_{pp}$ should be discussed after those have been introduced.}  In
-Figure~\ref{fig:tauD} we show how the turbulent reacceleration
-timescales in our three models scale with radius. As expected, the
-\Mprimary model with $\alpha_\rmn{tu}=0.88$ has the flattest profile
-with $\tau_D\approx0.4\,\rmn{Gyr}$, where the small dip at large
-radius driven by the decrease in thermal energy density. The
-\Mflatturb model has the the flattest turbulent profile parameterized
-by the smaller $\alpha_\rmn{tu}$ which explains the steepest $\tau_D$
-profile. Note that a fixed reacceleration timescale is required to
-explain the observations at each radius and for each model (see also
-Table~\ref{tab:timescales}). This allows us to interchange the value
-of uncertain parameters $\tau_\rmn{cl} \sim X_\rmn{tu}^2 \sim k_0$,
-i.e. a longer reacceleration duration have to be compensated by
-lowering the level of turbulence or increasing the physical injection
-scale of turbulence to keep $\tau_D$ constant.
-
-\begin{figure}
-  \includegraphics[width=1.0\columnwidth]{tau_reacc.eps}
-  \caption{Turbulent reacceleration timescales for our simulated
-    cluster g72a. We show in linear-log the reacceleration timescale
-    ($\tau_D$) as a function of radius $R$ for our three models:
-    \Mprimary (green dotted line), \Mstream (blue dashed line), and
-    \Mflatturb (red solid line). Note that the timescales are derived
-    during the last 100~Myrs in time in our simulations.}
-  \label{fig:tauD}
-\end{figure}
-
-\subsection{Spherically symmetric models}
+% --- section: Analytical Results and discussion --- %
+\section{Parameter space exploration with spherical models}
+\label{sect:param_comp}
+In this paper we rely on several critical parameters describing
+relatively unknown non-thermal physics in the ICM. Here we try to
+explore the robustness of our models to the most critical parameters
+related to turbulence and CRs.
+
+\subsection{Methodology}
 In this section we develop a simplified framework that will be used to
@@
 
-\AP{Can you please provide references for the following: -- check if
-  ok, the numbers are taken from our simulated g72a cluster. It should
-  be more clear now...} The bulk of the CRps are injected by
-relatively low Mach number shocks and parameterized by
-$f_\rmn{p,inj}(p) = C_\rmn{inj}\,p^{-\alpha_\rmn{inj}}$, where
-$\alpha_\rmn{inj}\approx 2.5$ in our simulations. The CRps
-approximately trace the thermal gas with $C_\rmn{inj} \propto
-\eps_\rmn{th}^{\alpha_\rmn{CR,spat}}$
+The bulk of the CRps are injected by relatively low Mach number shocks
+and parameterized by $f_\rmn{p,inj}(p) =
+C_\rmn{inj}\,p^{-\alpha_\rmn{inj}}$, where $\alpha_\rmn{inj}\approx
+2.5$ in our simulations. The CRps approximately trace the thermal gas
+with $C_\rmn{inj} \propto \eps_\rmn{th}^{\alpha_\rmn{CR,spat}}$
 \citep{pinzke10,2016MNRAS.459...70V}, where the normalization is fixed
@@
 \rmn{d}V\left(\int_0^{R_{200}}\eps_\rmn{th} \rmn{d}V\right)^{-1} =
-0.003$. \AP{not 0.0003? -- No, the injected energy in the last 650 Mys
-  is smaller then the energy density of the CRs injected during the
-  formation of the cluster. I estimated the difference to be about a
-  factor 10.} Similarly, the initial CRe distribution is given by the
-steady state between cooling (Coulomb, inverse Compton, and
-synchrotron) and injection of secondary CRes from $f_\rmn{p,0}$. We
-also include the continuous injection of secondary CRes during
-$\tau_\rmn{cl}$. The compressible turbulence responsible for
-reaccelerating both the CRps and CRes is parameterized by $I_0 \propto
-X_\rmn{tu} (n_{\rmn{e}} T)^{\alpha_\rmn{tu}}$. The diffusion constant
-$D_{pp}$ is calculated for each radial bin using
-Eqns.~\ref{eq:dpp}-\ref{eq:Gamma_e}. All parameters and assumptions
-are similar to what is used for our simulated cluster.
-
-\subsection{Cosmological simulation methodology}
-\label{sec:cosmo_sim}
-In this paper we focus on our simulated cluster, g72a, which is a
-massive $1.6\times10^{15}\,M_\odot$ cluster that experienced a merger
-about 1-2 Gyrs ago \citep{2009MNRAS.399..497D}. Since the cluster
-mass, density and temperature profiles are all similar to the well
-studied Coma cluster \citep{2007MNRAS.378..385P,pinzke10}, we will
-compare our calculations to radio and gamma-ray observations of Coma.
-
-We use a simple test-particle model for the CR acceleration and
-injection, where each shock injects CRs that trace a power-law in
-momentum,
-\begin{equation}
-  f_\p(p,t) = C(t)\,p^{\alpha_\rmn{inj}}\,,\quad
-  \alpha_\rmn{inj}=\frac{(\gamma_\rmn{ad}+1)\mathcal{M}^2}
-        {(\gamma_\rmn{ad}-1)\mathcal{M}^2+2}
-\end{equation}
-determined by the normalization $C(t)$ and the spectral index
-$\alpha_{\rmn{inj}}$ that depends on the adiabatic index
-$\gamma_\rmn{ad} = 5/3$ and the Mach number of the shock
-$\mathcal{M}$. It is given by the ratio of the upstream velocity
-($u_2$) and the sound speed ($c_s$). The CR number density and CR
-energy density are derived from
-\begin{eqnarray}
-n_\rmn{p} &=&
-\int_{p_\rmn{inj}}^\infty \dd p\, f_\p(p)\\
-\eps_\rmn{p} &=&
-\int_{p_\rmn{inj}}^\infty \dd p\, f_\p(p) \,E(p),
-\end{eqnarray}
-where $E(p) = (\sqrt{1+p^2} -1)\, m\,c^2$ is the kinetic energy of a
-particle with momentum $p$. We adopt a fit to Monte Carlo simulations
-of the thermal leakage process that relates the momentum of injected
-protons ($p_\rmn{inj}$) to the thermal energy ($p_\rmn{th}$) of the
-shocked plasma \citep{kang11}:
-\begin{eqnarray}
-  \label{eq:qinj}
-  p_\rmn{inj} &=& x_\rmn{inj} p_\rmn{th} = x_\rmn{inj} \sqrt{\frac{2 \,\kB T_2}{m c^2}}\,, \nonumber \\
-  \rmn{where}\quad x_\rmn{inj} &\approx& 1.17 \frac{u_2}{p_{\rmn{th}}\,c} \left(1+
-  \frac{1.07}{\epsilon_B}\right) \left(\frac{\mathcal{M}}{3}\right)^{0.1}\,.
-\end{eqnarray}
-Here $\eb = B_0/B_{\perp}$, $B_0$ is the amplitude of the downstream
-MHD wave turbulence, and $B_{\perp}$ is the magnetic field along the
-shock normal. The physical range of $\eb$ is quite uncertain due to
-complex plasma interactions. In this paper, we adopt $\eb = 0.23$,
-which we will later see corresponds to a conservative maximum energy
-acceleration efficiency for protons of $10\%$. To derive the
-acceleration efficiency, $\zeta_\rmn{inj}$, we first have to infer the
-particle injection efficiency, which is the fraction of downstream
-thermal gas particles which experience diffusive shock acceleration
-\citep[for details see ][]{pinzke13},
-\begin{equation}
-  \label{eq:eta}
-  \eta_\rmn{p,lin} =
-  \frac{4}{\sqrt{\upi}}\,\frac{x_\rmn{inj}^3}{\alpha_\rmn{inj}-1}\,
-  \rmn{e}^{-x_\rmn{inj}^2}.
-\end{equation}
-The particle injection efficiency is a strong function of
-$x_\rmn{inj}$ that depends on both $\mathcal{M}$ and $\eb$. The
-energy density of CRs that are injected and accelerated at the shock
-(neglecting the CR back reaction on the shock) is given by
-\begin{equation}
-\label{eq:CR_energy} 
-  \Delta\eps_\rmn{p,lin} =
-  \eta_\rmn{p,lin}(\mathcal{M})\,n_\rmn{th}(T_2)
-  \,\frac{\eps_\p}{n_\p}
-\end{equation}
-and the CR energy injection and acceleration efficiency is:
-\begin{equation}
-  \zeta_\rmn{lin} =
-  \frac{\Delta\eps_\rmn{p,lin}}{\Delta\eps_\rmn{diss}},
-   \quad\mbox{where}\quad
-  \Delta\eps_\rmn{diss} = \eps_\rmn{th2} - \eps_\rmn{th0}\,\left(\frac{\rho_2}{\rho_0}\right)^{\gamma_\rmn{ad}}\,.
-\label{eqn:energy_frac}  
-\end{equation}
-The dissipated energy density in the downstream regime,
-$\Delta\eps_\rmn{diss}$, is given by the difference of the thermal
-energy densities in the pre- and post-shock regimes, corrected for the
-adiabatic energy increase due to gas compression.
-
-We limit the acceleration efficiency to $\zeta_\rmn{max}$ by
-steepening the spectral index of the injected population
-$\alpha_\rmn{inj}$ to $\alpha_\rmn{sub}$ so that $\zeta_\rmn{lin}
-\leq \zeta_\rmn{max}$ is always fulfilled. The slope
-$\alpha_\rmn{inj}$ impact $\zeta_\rmn{inj}$ via the mean energy per
-particle, $\eps_\rmn{p}/n_\rmn{p}$. This
-procedure conserves energy and is motivated by models of non-linear
-shock acceleration where a sub-shock with a lower compression ratio
-(and hence steeper spectral index) forms
-\citep[e.g.,][]{2000ApJ...540..292E}. Given our assumed $\eb=0.23$, we
-find that for strong shocks where $\alpha \lesssim 2.3$ the spectral
-slope is steepened by a maximum of $\sim 10$ per cent in low
-temperature regimes ($\kB T\sim 0.1$~keV), while the steepening is much
-smaller for high temperature regimes ($\kB T\sim 10$~keV) that are more
-relevant for clusters. Since $p_\rmn{inj}$ remains fixed, so does the
-CR number density $n_\rmn{p}$. Hence we can solve for the
-renormalized normalization constant $C_\rmn{sub}$ using $n_\rmn{p}$
-and Eqn.~\ref{eq:eta}:
-\begin{equation}
-  \label{eq:Cp_sub}
-  C_\rmn{sub}=\eta_\rmn{p,lin}\,(\alpha_\rmn{sub}-1)\,p_\rmn{inj}^{\alpha_\rmn{sub}-1}\,,
-\end{equation}
-where the new distribution function is given by $f_\p(p,t)= C_\rmn{sub}
-p^{-\alpha_\rmn{sub}}$. We set an upper limit on the ratio of
-accelerated proton-to-dissipated energy in the downstream of strong
-shocks that varies from $\zeta_\rmn{max} \sim 1-10\%$, depending on
-the adopted model (for more details, see Section \ref{sec:results}).
-
-In our Galaxy, the CRe-to-CRp ratio at a few GeV is $K_{\rmn{ep}} \sim
-10^{-2}$. Hence, we adopt this as a fiducial value for the CRe-to-CRp
-acceleration efficiency \citep[see][for more
-  discussion]{pinzke13}. However, as recent PIC simulations have
-shown, this is likely very different at weak shocks, with electrons
-efficiently accelerated at perpendicular shocks
-\citep{2014ApJ...794..153G,2014ApJ...797...47G}, and ions efficiently
-accelerated at parallel shocks \citep{2014ApJ...783...91C}. Thus,
-depending on magnetic geometry, $K_{\rmn{ep}}$ could be either larger
-or smaller. Some observations of radio relics suggest high values of
-$K_{\rmn{ep}}$, due to the absence of gamma-ray emission, which probes
-the CRp population \citep{2014MNRAS.437.2291V}. This suggests primary
-CRes as a viable alternative scenario to secondary CRes as seeds for
-the giant RHs. In our {\em M-primaries} scenario, the injected
-distribution of CRes is derived in the same way as for the CRps. Once
-they have been accelerated to relativistic energies, injected
-electrons and protons are indistinguishable. We therefore assume that
-CRp and CRe have the same distribution function $f_\rmn{e}(p) =
-K_\rmn{ep} f_\rmn{p}(p)$, with a different normalization (due to
-differing acceleration efficiencies) $K_\rmn{ep}=0.1$ \citep[which is
-  viable for primarily perpendicular
-  shocks][]{2014ApJ...794..153G}. While this appears to contradict the
-radial bias of magnetic fields in the bulk of the ICM as suggested by
-observations \citep{2010NatPh...6..520P} and cluster simulations
-\citep{2011ApJ...740...81R}, it does not necessarily apply to the
-accretion shock regions, which show a field geometry with a net
-perpendicular bias with respect to the shock normal---at least for
-giant radio relics \citep{2010Sci...330..347V}.
-
-% --- section: Analytical Results and discussion --- %
-\section{Parameter space exploration with spherical models}
-\label{sect:param_comp}
-In this paper we rely on several critical parameters describing
-relatively unknown non-thermal physics in the ICM. Here we try to
-explore the robustness of our models to the most critical parameters
-related to turbulence and CRs. Figure~\ref{fig:param_comp} shows their
+0.003$. Note that the injected energy in the last 650 Mys is smaller
+by about a factor of 10 in comparison to the cumulative CR energy
+injected over the entire cosmological history of the cluster.
+Similarly, the initial CRe distribution is given by the steady state
+between cooling (Coulomb, inverse Compton, and synchrotron) and
+injection of secondary CRes from $f_\rmn{p,0}$. We also include the
+continuous injection of secondary CRes during $\tau_\rmn{cl}$. The
+compressible turbulence responsible for reaccelerating both the CRps
+and CRes is parameterized by $I_0 \propto X_\rmn{tu} (n_{\rmn{e}}
+T)^{\alpha_\rmn{tu}}$. The diffusion constant $D_{pp}$ is calculated
+for each radial bin using Eqns.~\ref{eq:dpp}-\ref{eq:Gamma_e}. All
+parameters and assumptions are similar to what is used for our
+simulated cluster.
+
+\subsection{Results}
+
+Figure~\ref{fig:param_comp} shows their
 impact on radio emission. We find that the level of turbulence
@@
 % --- section: Simulation Results and discussion --- %
-\section{Results of cosmological simulations}
+\section{Cosmological simulations}
 \label{sec:results}
@@
 uncertain parameters $X_\rmn{tu}$, $\tau_\rmn{cl}$, and $k_0$). Given
-the freedom in the turbulens, it might not be surprising that we match
+the freedom in the turbulence, it might not be surprising that we match
 the radio profile in Coma. Although, matching the spectrum without
@@
 
-\subsection{Radio profile}
+\subsection{Modelling diffusive shock acceleration}
+\label{sec:cosmo_sim}
+In this paper we focus on our simulated cluster, g72a, which is a
+massive $1.6\times10^{15}\,M_\odot$ cluster that experienced a merger
+about 1 to 2 Gyrs ago \citep{2009MNRAS.399..497D}. Since the cluster
+mass, density and temperature profiles are all similar to the well
+studied Coma cluster \citep{2007MNRAS.378..385P,pinzke10}, we will
+compare our calculations to radio and gamma-ray observations of Coma.
+
+We use a simple test-particle model for the CR acceleration and
+injection, where each shock injects CRs that trace a power-law in
+momentum,
+\begin{equation}
+  f_\p(p,t) = C(t)\,p^{\alpha_\rmn{inj}}\,,\quad
+  \alpha_\rmn{inj}=\frac{(\gamma_\rmn{ad}+1)\mathcal{M}^2}
+        {(\gamma_\rmn{ad}-1)\mathcal{M}^2+2}
+\end{equation}
+determined by the normalization $C(t)$ and the spectral index
+$\alpha_{\rmn{inj}}$ that depends on the adiabatic index
+$\gamma_\rmn{ad} = 5/3$ and the Mach number of the shock
+$\mathcal{M}$. It is given by the ratio of the upstream velocity
+($u_2$) and the sound speed ($c_s$). The CR number density and CR
+energy density are derived from
+\begin{eqnarray}
+n_\rmn{p} &=&
+\int_{p_\rmn{inj}}^\infty \dd p\, f_\p(p)\\
+\eps_\rmn{p} &=&
+\int_{p_\rmn{inj}}^\infty \dd p\, f_\p(p) \,E(p),
+\end{eqnarray}
+where $E(p) = (\sqrt{1+p^2} -1)\, m\,c^2$ is the kinetic energy of a
+particle with momentum $p$. We adopt a fit to Monte Carlo simulations
+of the thermal leakage process that relates the momentum of injected
+protons ($p_\rmn{inj}$) to the thermal energy ($p_\rmn{th}$) of the
+shocked plasma \citep{kang11}:
+\begin{eqnarray}
+  \label{eq:qinj}
+  p_\rmn{inj} &=& x_\rmn{inj} p_\rmn{th} = x_\rmn{inj} \sqrt{\frac{2 \,\kB T_2}{m c^2}}\,, \nonumber \\
+  \rmn{where}\quad x_\rmn{inj} &\approx& 1.17 \frac{u_2}{p_{\rmn{th}}\,c} \left(1+
+  \frac{1.07}{\epsilon_B}\right) \left(\frac{\mathcal{M}}{3}\right)^{0.1}\,.
+\end{eqnarray}
+Here $\eb = B_0/B_{\perp}$, $B_0$ is the amplitude of the downstream
+MHD wave turbulence, and $B_{\perp}$ is the magnetic field along the
+shock normal. The physical range of $\eb$ is quite uncertain due to
+complex plasma interactions. In this paper, we adopt $\eb = 0.23$,
+which we will later see corresponds to a conservative maximum energy
+acceleration efficiency for protons of $10\%$. To derive the
+acceleration efficiency, $\zeta_\rmn{inj}$, we first have to infer the
+particle injection efficiency, which is the fraction of downstream
+thermal gas particles which experience diffusive shock acceleration
+\citep[for details see ][]{pinzke13},
+\begin{equation}
+  \label{eq:eta}
+  \eta_\rmn{p,lin} =
+  \frac{4}{\sqrt{\upi}}\,\frac{x_\rmn{inj}^3}{\alpha_\rmn{inj}-1}\,
+  \rmn{e}^{-x_\rmn{inj}^2}.
+\end{equation}
+The particle injection efficiency is a strong function of
+$x_\rmn{inj}$ that depends on both $\mathcal{M}$ and $\eb$. The
+energy density of CRs that are injected and accelerated at the shock
+(neglecting the CR back reaction on the shock) is given by
+\begin{equation}
+\label{eq:CR_energy} 
+  \Delta\eps_\rmn{p,lin} =
+  \eta_\rmn{p,lin}(\mathcal{M})\,n_\rmn{th}(T_2)
+  \,\frac{\eps_\p}{n_\p}
+\end{equation}
+and the CR energy injection and acceleration efficiency is:
+\begin{equation}
+  \zeta_\rmn{lin} =
+  \frac{\Delta\eps_\rmn{p,lin}}{\Delta\eps_\rmn{diss}},
+   \quad\mbox{where}\quad
+  \Delta\eps_\rmn{diss} = \eps_\rmn{th2} - \eps_\rmn{th0}\,\left(\frac{\rho_2}{\rho_0}\right)^{\gamma_\rmn{ad}}\,.
+\label{eqn:energy_frac}  
+\end{equation}
+The dissipated energy density in the downstream regime,
+$\Delta\eps_\rmn{diss}$, is given by the difference of the thermal
+energy densities in the pre- and post-shock regimes, corrected for the
+adiabatic energy increase due to gas compression.
+
+We limit the acceleration efficiency to $\zeta_\rmn{max}$ by
+steepening the spectral index of the injected population
+$\alpha_\rmn{inj}$ to $\alpha_\rmn{sub}$ so that $\zeta_\rmn{lin}
+\leq \zeta_\rmn{max}$ is always fulfilled. The slope
+$\alpha_\rmn{inj}$ impact $\zeta_\rmn{inj}$ via the mean energy per
+particle, $\eps_\rmn{p}/n_\rmn{p}$. This
+procedure conserves energy and is motivated by models of non-linear
+shock acceleration where a sub-shock with a lower compression ratio
+(and hence steeper spectral index) forms
+\citep[e.g.,][]{2000ApJ...540..292E}. Given our assumed $\eb=0.23$, we
+find that for strong shocks where $\alpha \lesssim 2.3$ the spectral
+slope is steepened by a maximum of $\sim 10$ per cent in low
+temperature regimes ($\kB T\sim 0.1$~keV), while the steepening is much
+smaller for high temperature regimes ($\kB T\sim 10$~keV) that are more
+relevant for clusters. Since $p_\rmn{inj}$ remains fixed, so does the
+CR number density $n_\rmn{p}$. Hence we can solve for the
+renormalized normalization constant $C_\rmn{sub}$ using $n_\rmn{p}$
+and Eqn.~\ref{eq:eta}:
+\begin{equation}
+  \label{eq:Cp_sub}
+  C_\rmn{sub}=\eta_\rmn{p,lin}\,(\alpha_\rmn{sub}-1)\,p_\rmn{inj}^{\alpha_\rmn{sub}-1}\,,
+\end{equation}
+where the new distribution function is given by $f_\p(p,t)= C_\rmn{sub}
+p^{-\alpha_\rmn{sub}}$. We set an upper limit on the ratio of
+accelerated proton-to-dissipated energy in the downstream of strong
+shocks that varies from $\zeta_\rmn{max} \sim 1-10\%$, depending on
+the adopted model (for more details, see Section \ref{sec:results}).
+
+In our Galaxy, the CRe-to-CRp ratio at a few GeV is $K_{\rmn{ep}} \sim
+10^{-2}$. Hence, we adopt this as a fiducial value for the CRe-to-CRp
+acceleration efficiency \citep[see][for more
+  discussion]{pinzke13}. However, as recent PIC simulations have
+shown, this is likely very different at weak shocks, with electrons
+efficiently accelerated at perpendicular shocks
+\citep{2014ApJ...794..153G,2014ApJ...797...47G}, and ions efficiently
+accelerated at parallel shocks \citep{2014ApJ...783...91C}. Thus,
+depending on magnetic geometry, $K_{\rmn{ep}}$ could be either larger
+or smaller. Some observations of radio relics suggest high values of
+$K_{\rmn{ep}}$, due to the absence of gamma-ray emission, which probes
+the CRp population \citep{2014MNRAS.437.2291V}. This suggests primary
+CRes as a viable alternative scenario to secondary CRes as seeds for
+the giant RHs. In our {\em M-primaries} scenario, the injected
+distribution of CRes is derived in the same way as for the CRps. Once
+they have been accelerated to relativistic energies, injected
+electrons and protons are indistinguishable. We therefore assume that
+CRp and CRe have the same distribution function $f_\rmn{e}(p) =
+K_\rmn{ep} f_\rmn{p}(p)$, with a different normalization (due to
+differing acceleration efficiencies) $K_\rmn{ep}=0.1$ \citep[which is
+  viable for primarily perpendicular
+  shocks][]{2014ApJ...794..153G}. While this appears to contradict the
+radial bias of magnetic fields in the bulk of the ICM as suggested by
+observations \citep{2010NatPh...6..520P} and cluster simulations
+\citep{2011ApJ...740...81R}, it does not necessarily apply to the
+accretion shock regions, which show a field geometry with a net
+perpendicular bias with respect to the shock normal---at least for
+giant radio relics \citep{2010Sci...330..347V}.
+
+\subsection{Radio emission profile}
+
+%%% moved from before
+
+\begin{figure}
+  \includegraphics[width=1.0\columnwidth]{turb_profile_ratio_tot.eps}
+  \caption{The ratio of turbulent-to-thermal energy densities (solid
+    lines) and cumulative energies (dotted lines) in our three
+    models. The energy densities are parametrized as
+    $\eps_\rmn{turb} \propto
+    \eps_\rmn{th}^{(\alpha_{\rmn{tu}}+1)/2}/T^{1/4}$ and
+    normalized such that the total turbulent energy in compressible
+    modes $E_\rmn{turb}$ for each scenario makes up about 20\% of the
+    total thermal energy $E_\rmn{th}$ inside the radio halo
+    ($R_\rmn{RH}\approx0.6R_{200}$). The turbulent profiles explore
+    the uncertainty in the cluster turbulence and are motivated by the
+    cosmological simulation in
+    \citep{2009ApJ...705.1129L,2010ApJ...725.1452S,2011A&A...529A..17V}.}
+  \label{fig:turb}
+\end{figure}
+
+The profile of injected turbulence depends on the details of the
+merger such as time during the merger, the impact parameter, the
+merger mass ratio, and the degree of cluster anisotropy
+\citep{2015ApJ...800...60M}. We parametrize these uncertainties and
+assume that it scales with the thermal energy density to some
+power. Hence we assume volumetric injection rate of turbulent energy,
+$I_0\propto \eps_\rmn{th}^{\alpha_\rmn{tu}}$, and determine the
+normalization by requiring that the turbulent energy in compressible
+modes $E_\rmn{turb}=\int \int \mathcal{W}(k) \rmn{d}k \rmn{d}V =
+X_\rmn{tu} E_\rmn{th}$, where $E_\rmn{th}$ is the total thermal
+energy. We adopt a turbulent energy ratio $X_\rmn{tu}=0.2$ within the
+radio halo.\footnote{Simulations show that the compressible modes
+  contribute a factor $0.2-0.4$ to the total turbulent energy
+  \citep{2013ApJ...771..131B,2015ApJ...800...60M}. Furthermore, the
+  total turbulent energy, which can be decomposed into a slenoidal and
+  compressible component, is typically $\sim15-70$\% of the thermal
+  energy in a cluster \citep{2011A&A...529A..17V}; in agreement with
+  our adopted value of $X_\rmn{tu}$.} In this work we investigate
+different spatial models for injected turbulence. With the above
+choice of normalization, the turbulent energy density becomes
+$\eps_\rmn{turb} \propto
+\eps_\rmn{th}^{(\alpha_\rmn{tu}+1)/2}/T^{1/4}$, where $T$ is the
+temperature of the gas, $\alpha_\rmn{tu}= 0.67$ for \Mflatturb,
+$\alpha_\rmn{tu}= 0.82$ for \Mstream, and $\alpha_\rmn{tu}= 0.88$ for
+\Mprimary (see Figure~\ref{fig:turb} for visualization).
+
+Note that in previous work on the Coma cluster, $\eps_\rmn{turb}
+\propto \eps_\rmn{th}$ was adopted which roughly corresponds to
+$\alpha_\rmn{tu}= 1$ \citep{brunetti12} and together with the
+different distributions for seed CRes constitute the main differences
+compared to our work. Our flatter turbulent profiles are motivated by
+fits to cosmological simulations
+\citep{2009ApJ...705.1129L,2010ApJ...725.1452S,2011A&A...529A..17V,2012ApJ...758...74B}
+and the range indicates uncertainties of the turbulent profile in
+Coma. Future observations (by Astro-H) and simulations will help to
+clarify this issue.
+
+In Figure~\ref{fig:tauD} we show how the turbulent reacceleration
+timescales in our three models scale with radius. As expected, the
+\Mprimary model with $\alpha_\rmn{tu}=0.88$ has the flattest profile
+with $\tau_D\approx0.4\,\rmn{Gyr}$, where the small dip at large
+radius driven by the decrease in thermal energy density. The
+\Mflatturb model has the the flattest turbulent profile parameterized
+by the smaller $\alpha_\rmn{tu}$ which explains the steepest $\tau_D$
+profile. Note that a fixed reacceleration timescale is required to
+explain the observations at each radius and for each model (see also
+Table~\ref{tab:timescales}). This allows us to interchange the value
+of uncertain parameters $\tau_\rmn{cl} \sim X_\rmn{tu}^2 \sim k_0$,
+i.e. a longer reacceleration duration have to be compensated by
+lowering the level of turbulence or increasing the physical injection
+scale of turbulence to keep $\tau_D$ constant.
+
+\begin{figure}
+  \includegraphics[width=1.0\columnwidth]{tau_reacc.eps}
+  \caption{Turbulent reacceleration timescales for our simulated
+    cluster g72a. We show in linear-log the reacceleration timescale
+    ($\tau_D$) as a function of radius $R$ for our three models:
+    \Mprimary (green dotted line), \Mstream (blue dashed line), and
+    \Mflatturb (red solid line). Note that the timescales are derived
+    during the last 100~Myrs in time in our simulations.}
+  \label{fig:tauD}
+\end{figure}
+
+%%%
+
 In Fig.~\ref{fig:sync_profile}, we find that all three scenarios in
@@
 
-\subsection{Gamma-rays}
+\subsection{Gamma rays}
 The gamma-ray emission from CRps that produce decaying neutral pions

### 2016-05-06 paper.tex
editing of Sect 3 finished

@@
 It is worth noting that in the subsonic regime of the solar wind \citep{yao11,howes12}, as well as most idealized calculations of turbulent driving, there is relatively little energy in the fast mode.
-For instance, the fidiucial simulations of \citet{lynn14} with a sonic Mach number ${\mathcal M}_{\rm s} \sim 0.35$ and a plasma beta factor of $\beta \sim 1$ show that 50\%, 45\%, 5\% of the turbulent energy density is in the Alfv{\'e}n, slow, and fast modes, respectively.
+For instance, the fiducial simulations of \citet{lynn14} with a sonic Mach number ${\mathcal M}_{\rm s} \sim 0.35$ and a plasma beta factor of $\beta \sim 1$ show that 50\%, 45\%, 5\% of the turbulent energy density is in the Alfv{\'e}n, slow, and fast modes, respectively.
 For higher $\beta \sim 3-10$, they find that the proportion of energy in fast modes drops to $< 1\%$, while the fraction of energy in the slow mode remains roughly the same.
@@
 in \cite{brunetti07}, we initially assume that the velocity of
-turbulent eddies is $V_0\approx 0.47 c_\rmn{s}$ throughout the
+turbulent eddies is $\varv_0\approx 0.47 c_\rmn{s}$ throughout the
 cluster. This gives a turbulent acceleration time scale, $\tau_{D} =
@@
 length scale defines an eddy turn-over time
-$\tau_{\rmn{eddy}}\sim2\upi\lambda_0/V_0\sim1.2$~Gyr with
-$V_0=500\,\rmn{km~s}^{-1}$, characteristic of a merger event.
+$\tau_{\rmn{eddy}}\sim2\upi\lambda_0/\varv_0\sim1.2$~Gyr with
+$\varv_0=500\,\rmn{km~s}^{-1}$, characteristic of a merger event.
 
@@
 scales \citep{brunetti11}.
+
+The profile of injected turbulence depends on the details of the
+merger such as time during the merger, the impact parameter, the
+merger mass ratio, and the degree of cluster anisotropy
+\citep{2015ApJ...800...60M}. We parametrize these uncertainties and
+assume that it scales with the thermal energy density to some
+power. Hence we assume volumetric injection rate of turbulent energy,
+$I_0\propto \eps_\rmn{th}^{\alpha_\rmn{tu}}$, and determine the
+normalization by requiring that the turbulent energy in compressible
+modes $E_\rmn{turb}=\int \int \mathcal{W}(k) \rmn{d}k \rmn{d}V =
+X_\rmn{tu} E_\rmn{th}$, where $E_\rmn{th}$ is the total thermal
+energy. We adopt a turbulent energy ratio $X_\rmn{tu}=0.2$ within the
+radio halo.\footnote{Simulations show that the compressible modes
+  contribute a factor $0.2-0.4$ to the total turbulent energy
+  \citep{2013ApJ...771..131B,2015ApJ...800...60M}. Furthermore, the
+  total turbulent energy, which can be decomposed into a slenoidal and
+  compressible component, is typically $\sim15-70$\% of the thermal
+  energy in a cluster \citep{2011A&A...529A..17V}; in agreement with
+  our adopted value of $X_\rmn{tu}$.}
 
@@
 
+\SPO{the derivation of the following is not transparent, could you expand?}
 During reacceleration, the CRps increase their normalization
@@
 In this paper we rely on several critical parameters describing
-relatively unknown non-thermal physics in the ICM. Here we try to
-explore the robustness of our models to the most critical parameters
-related to turbulence and CRs.
+relatively unknown non-thermal physics in the ICM. Here we develop a
+simplified framework that will be used to explore the robustness of
+our models to the most critical parameters related to turbulence and
+CRs.
 
 \subsection{Methodology}
-In this section we develop a simplified framework that will be used to
-test the robustness of our models with respect to the critical
-parameters for CRs and turbulence in Section~\ref{sect:param_comp}. In
-order to quickly explore parameter space, we we solve the
-Fokker-Planck equation in static spherical shells for injection,
-reacceleration, and losses of the CRs, i.e., we neglect the Lagrangian
-trajectories during the re-acceleration time.  Once the CRs have been
-reaccelerated for $\tau_\rmn{cl} = 650\,\rmn{Myr}$, we calculate the
-radio emission and compare the profile and spectra for different
-parameterizations.
+
+As we have seen before, the resulting radio-emitting CRe distribution
+depends on compressible turbulence (which sets the level of
+reacceleration) and the distribution of pre-existing CRs. Hence we
+vary parameters describing the amount of energy contained in
+turbulence relative to the thermal energy, $X_{\rm tu}$, the spatial
+profile of turbulence as parametrized by $\alpha_{\rm tu}$, as well as
+the spatial CR profile that we will parametrize by $\alpha_{\rm CR,
+  spat}$ (see below).  In order to quickly explore this parameter
+space, we solve the Fokker-Planck equation in static spherical shells
+for injection, reacceleration, and losses of the CRs, i.e., we neglect
+the Lagrangian trajectories during the re-acceleration time.  Once the
+CRs have been reaccelerated for $\tau_\rmn{cl} = 650\,\rmn{Myr}$, we
+calculate the resulting radio emission and compare the emission
+profiles and spectra as we vary one parameter at the time relative to
+our fiducial model.
 
@@
 profiles \citep{2009ApJ...696.1886B,2001A&A...365L..67A} derived from
-X-ray observations of the Coma cluster. They are given by:
+X-ray observations of the Coma cluster,
 \begin{eqnarray}
-n_e &=& \frac{n_0}{\left[1+\left(R/R_{\rmn{c}}\right)^2\right]^{1.125}}\nonumber\\
-k_{\rmn{B}} T &=& 8.25\,\rmn{keV} \left[1+\left(2R/R_{200}\right)^2\right]^{-0.32}\,,
+n_e &=& n_0\,\left[1+\left(R/R_{\rmn{c}}\right)^2\right]^{-1.125},\nonumber\\
+k_{\rmn{B}} T &=& 8.25\,\rmn{keV} \left[1+\left(2R/R_{200}\right)^2\right]^{-0.32},
 \end{eqnarray}
@@
 by the injected CR energy in the last 650~Myrs. Our simulations show
-that it roughly make up 0.03\% of the thermal energy inside the virial
-radius, i.e.  $\int_0^{R_{200}}\eps_\rmn{p,inj} \rmn{d}
+that it approximately amounts to 0.03\% of the thermal energy inside
+the virial radius, i.e.  $\int_0^{R_{200}}\eps_\rmn{p,inj} \rmn{d}
 V\left(\int_0^{R_{200}}\eps_\rmn{th} \rmn{d}V\right)^{-1} =
@@
 parameters and assumptions are similar to what is used for our
-simulated cluster.
+simulated cluster (see Sect.~\ref{sec:results}).
 
@@
 
-Figure~\ref{fig:param_comp} shows their
-impact on radio emission. We find that the level of turbulence
-($X_\rmn{tu}$) has a large impact on both radio spectra and profiles,
-while the parameter $\alpha_\rmn{tu}$ that determines the spatial
-profile of turbulence mainly influence the radio profiles. As
-expected, the radio profiles flatten significantly with a flatter
-turbulent profile. A higher amount of turbulent energy also flatten
-the radio profile, where the reason being that the steep profiles of
+Figure~\ref{fig:param_comp} shows the impact of turbulence and the
+spatial distribution of CRs on the radio emission.  We find that the
+level of turbulence ($X_\rmn{tu}$) has a large impact on both radio
+spectra and profiles, while the parameter $\alpha_\rmn{tu}$ that
+determines the spatial profile of turbulence mainly influences the
+radio profiles. As expected, the radio profiles flatten significantly
+with a flatter turbulent profile. A larger amount of turbulent energy
+also flattens the radio profile, because the steep profiles of
 injected CRs have less impact on the radio emission for an increasing
-reacceleration efficiency. Interestingly, assumptions about CRs have
-less impact on radio emission. This can be understood by looking at
-the scaling of parameters to the reacceleration timescale, where
-$\tau_\rmn{D} \propto 1/D_\rmn{pp} \propto 1/X_\rmn{tu}^2$. From
-Eqn.~\ref{eq:Creacc} we see that the CRps with a spectral index of
-$\alpha_\rmn{p}\approx2.5$ approximately gain a factor $\Delta
-C_\rmn{reacc.} \sim
-\exp{\left[1.7\frac{\tau_\rmn{cl}}{\tau_\rmn{D}}\right]}$ during
+reacceleration efficiency.
+
+Interestingly, the spatial profile of CRs has a smaller impact on the
+radio emission. This can be understood by looking at the scaling of
+parameters to the reacceleration timescale, where $\tau_\rmn{D}
+\propto 1/D_\rmn{pp} \propto 1/X_\rmn{tu}^2$. From
+Equation~\ref{eq:Creacc} we see that the CRps with a spectral index of
+$\alpha_\rmn{p}\approx2.5$ approximately gain a factor $\delta
+C_\rmn{reacc.} \sim \exp{(1.7\,\tau_\rmn{cl}/\tau_\rmn{D})}$ during
 reacceleration if injection and cooling are neglected. The CRes gain a
@@
 $0.1\,R_{200}$ the Coulomb cooling timescale
-($\tau_\rmn{coul}\approx0.01\,\rmn{Gyr}$) is much shorter than
-$\tau_\rmn{D}\approx0.6\,\rmn{Gyr}$, hence $\Delta C_\rmn{reacc.}$
+($\tau_\rmn{Coul}\approx0.01\,\rmn{Gyr}$) is much shorter than
+$\tau_\rmn{D}\approx0.6\,\rmn{Gyr}$, hence $\delta C_\rmn{reacc.}$
 will be greatly reduced for the electrons. The spatial region is
@@
 0.2\,R_{200}$. For $X_\rmn{tu}=0.2$ and $\alpha_\rmn{tu}=0.8$ we find
-that $\Delta C_\rmn{reacc.} \sim 10$. This is confirmed by the top
+that $\delta C_\rmn{reacc.} \sim 10$. This is confirmed by the top
 panels in Fig.~\ref{fig:param_comp}. Increasing the level of
-turbulence to $X_\rmn{tu}=0.3$, gives us a $\Delta C_\rmn{reacc.}
+turbulence to $X_\rmn{tu}=0.3$, gives us a $\delta C_\rmn{reacc.}
 \sim 100$, which is roughly confirmed by same figures. The factor 2-3
@@
 would otherwise cool away on a much shorter timescale. Hence we
-conclude that the radio emission is much more sensitive to the
-exponential dependence on compressible turbulence than the linear
-dependence on injected CRs.
-
-We can also derive a lower critical level of turbulence where
-reacceleration is negligible, while it rises sharply above this
-threshold. We define the threshold by $\Delta C_\rmn{reacc.}  \lesssim
-2$, which gives us an $X_\rmn{thres,tu} = \left(\frac{0.04\,\log(2)
-}{1.7}\frac{\tau_\rmn{D}}{\tau_\rmn{cl}}\right)^{0.5} \approx 0.08$
-for $\tau_\rmn{D} = 0.6\,\rmn{Gyr}$. This threshold is also seen in
-the top panels of figure~\ref{fig:param_comp}. For instance, for
-$X_\rmn{tu}\gtrsim0.08$, a factor two change in $X_\rmn{tu}$ changes
-the radio surface brightness by a factor $\sim 10-100$. In principle
-this threshold behavior allows us to provide a strict lower bound on
-turbulence in radio halos. An even more stringent bound on
-$X_\rmn{tu}$ can be inferred from combining radio observations with
-the gamma-ray observations (see section~\ref{sect:radio_spec}).
+conclude that the radio emission is much more sensitive to the level
+of compressible turbulence through an exponential dependence.  In
+contrast, the radio emission only depends linearly on the density of
+injected CRs.
+
+We can also derive a critical level of turbulence below which
+reacceleration is negligible. Above this threshold, reacceleration
+becomes increasingly more efficient. We define the threshold by
+$\delta C_\rmn{reacc.}  \lesssim 2$, which gives us an
+$X_\rmn{thres,tu} = \sqrt{0.04\,\log(2)/1.7 \times
+  \tau_\rmn{D}/\tau_\rmn{cl}} \approx 0.08$ for $\tau_\rmn{D} =
+0.6\,\rmn{Gyr}$. The existence of such a threshold can also manifested
+in the top panels of Fig.~\ref{fig:param_comp}. For
+$X_\rmn{tu}\gtrsim0.08$, changing $X_\rmn{tu}$ by a factor of two
+changes the radio surface brightness by a factor of $\sim 10-100$. In
+principle this threshold behavior allows us to provide a strict lower
+bound on turbulence in radio halos. An even more stringent bound on
+$X_\rmn{tu}$ can be obtained by combining radio observations with
+the gamma-ray observations (see Section~\ref{sect:radio_spec}).
 
@@
 \caption{Sensitivity of radio emission in Coma cluster to critical
-  parameters. {\it Left panels} show the radio surface brightness
-  profiles. We compare profiles at 352~MHz \citep[blue lines and
+  parameters. The left-hand panels show the radio surface brightness
+  profiles. We compare profiles at 352~MHz \citep[blue
     crosses,][]{brown11} to predicted emission from Fermi-II
-  reaccelerated CR electrons populations (black lines). {\it Right
-    panels} show radio synchrotron spectra. The green crosses are
-  compiled from observations \citet{2010PhDT.......259P}, while the
+  reaccelerated CR electrons populations (black lines). The right-hand
+  panels show radio synchrotron spectra. The green crosses are
+  compiled from observations \citep{2010PhDT.......259P}, while the
   black lines show predicted emission from reaccelerated CR
   electrons. The upper panels show the sensitivity to the level of
-  turbulence ($X_\rmn{tu}$), middle panels show the impact of
-  different turbulent profiles ($\alpha_\rmn{tu}$), and lower panels
-  show the dependence on spatial distributions of initial and injected
-  CRs ($\alpha_\rmn{CR,spat}$). We adopt the following fiducial values
-  for parameters that are not varied in each panel: $X_\rmn{tu}=0.2$,
-  $\alpha_\rmn{tu}=0.8$, and $\alpha_\rmn{CR,spat}=1.0$. Note that the
-  radio emission is much more sensitive to assumptions about turbulent
-  parameters than CRs.}
+  turbulence ($X_\rmn{tu}$), the middle panels show the impact of
+  different turbulent profiles ($\alpha_\rmn{tu}$), and the lower
+  panels show the dependence on spatial distributions of initial and
+  injected CRs ($\alpha_\rmn{CR,spat}$). We adopt the following
+  fiducial values for our model, $X_\rmn{tu}=0.2$,
+  $\alpha_\rmn{tu}=0.8$, and $\alpha_\rmn{CR,spat}=1.0$ and vary each
+  parameter separately in each row of panels. We find that the radio
+  emission is much more sensitive to the level of turbulence while it
+  depends less senstively to the spatial distribution of CRs.}
   \label{fig:param_comp}
@@
 
-The profile of injected turbulence depends on the details of the
-merger such as time during the merger, the impact parameter, the
-merger mass ratio, and the degree of cluster anisotropy
-\citep{2015ApJ...800...60M}. We parametrize these uncertainties and
-assume that it scales with the thermal energy density to some
-power. Hence we assume volumetric injection rate of turbulent energy,
-$I_0\propto \eps_\rmn{th}^{\alpha_\rmn{tu}}$, and determine the
-normalization by requiring that the turbulent energy in compressible
-modes $E_\rmn{turb}=\int \int \mathcal{W}(k) \rmn{d}k \rmn{d}V =
-X_\rmn{tu} E_\rmn{th}$, where $E_\rmn{th}$ is the total thermal
-energy. We adopt a turbulent energy ratio $X_\rmn{tu}=0.2$ within the
-radio halo.\footnote{Simulations show that the compressible modes
-  contribute a factor $0.2-0.4$ to the total turbulent energy
-  \citep{2013ApJ...771..131B,2015ApJ...800...60M}. Furthermore, the
-  total turbulent energy, which can be decomposed into a slenoidal and
-  compressible component, is typically $\sim15-70$\% of the thermal
-  energy in a cluster \citep{2011A&A...529A..17V}; in agreement with
-  our adopted value of $X_\rmn{tu}$.} In this work we investigate
+In this work we investigate
 different spatial models for injected turbulence. With the above
@@
 council for financial support. S.P.O. thanks NASA grant NNX12AG73G for
-support. C.P.~gratefully acknowledges financial support of the Klaus
-Tschira Foundation.
+support. C.P.~acknowledges support by the European Research Council
+under ERC-CoG grant CRAGSMAN-646955 and by the Klaus Tschira
+Foundation.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2016-05-06 paper.tex
editing Section 4

@@
 enables us to vary parameters associated with the unknown continuation
-of magneto-hydrodynamical turbulence below the MHD scale and the
+of magneto-hydrodynamical (MHD) turbulence below the MHD scale and the
 overall amplitude of compressible waves (that can in principle vary
@@
 
-In this section we show that our three models individually reproduce
-the observed Coma radio halo without violating gamma-ray bounds. The
-level of emission is mainly driven by how efficient the CRs are
-reaccelerated and for how long. After turbulent reacceleration, the
-volume-weighted, relative CRp energy density and relative CRp number
-density inside the RH for \Mflatturb (\Mstream), are found to be 2 (3)
-\% and $2\times10^{-8}$ ($5\times10^{-8}$), respectively. As we will
-see later, these densities are just of the right order of magnitude to
-reproduce radio observations in the Coma cluster. We exploit the large
-uncertainty in the turbulent profile and adjust $\alpha_\rmn{tu}$ for
-each model so that the CRs have the correct spatial profile to match
-the radio emission. The shape of the spectrum for each of model is
-more complicated and is determined both from reacceleration and as
-well as the gains and losses during the formation of the cluster. It
-depends only weakly on the specifics of the CR injection at the shocks
-(where the Mach number distribution of the shocks is the most
-important quantity). The normalization of the spectrum is mainly
-determined from the maximum acceleration efficiency (together with the
-uncertain parameters $X_\rmn{tu}$, $\tau_\rmn{cl}$, and $k_0$). Given
-the freedom in the turbulence, it might not be surprising that we match
-the radio profile in Coma. Although, matching the spectrum without
-violating gamma-ray bounds for each of our three models is more
-surprising and is not a consequence of parameter fitting. We believe
-that it is ultimately a consequence of the adopted physics and hint
-that reacceleration is a viable explanation for giant radio
-halos. Below we discuss in more detail the different emission
-components of Coma.
+In this setion, we solve the Fokker-Planck equation for CR transport
+on Lagrangian particle trajectories through cosmic history.  We
+concentrate on three scenarios. (i) In model {\em M-primaries}, we
+assume that CR electrons, which have been accelerated by cosmic
+formation shocks and successively cooled by inverse Compton and
+synchrotron losses, form a fossil seed population for
+reacceleration. (ii) In model {\em M-streaming}, we account for the
+outward streaming of central CRps, which produces a flat CR
+distribution in the ICM and equivalently a flat secondary seed
+population of CRe for reacceleration. (iii) In model {\em
+  M-turbulence} we adopt a spatially flatter turbulent profile than
+what was adopted before but assume that seed CRps and secondary CRes
+follow the steep profile that is suggested by structure formation
+simulations.
+
+The level of emission is mainly driven by how efficient the CRs are
+reaccelerated and for how long. Hence, we exploit the exponential
+sensitivity of reacceleration on the level of turbulence and adopt
+different radial profiles of the turbulent energy density. We ask the
+question how differently the turbulent profiles need to be shaped in
+order to reproduce the observed radial profiles of the radio
+emission. For these models, we then compute radio spectra and
+gamma-ray luminosities and compare to observational data.
 
@@
 In this paper we focus on our simulated cluster, g72a, which is a
-massive $1.6\times10^{15}\,M_\odot$ cluster that experienced a merger
-about 1 to 2 Gyrs ago \citep{2009MNRAS.399..497D}. Since the cluster
-mass, density and temperature profiles are all similar to the well
-studied Coma cluster \citep{2007MNRAS.378..385P,pinzke10}, we will
-compare our calculations to radio and gamma-ray observations of Coma.
+massive cluster of mass $M_{200}=1.6\times10^{15}\,M_\odot$ that
+experienced a merger about 1 Gyr ago
+\citep{2009MNRAS.399..497D}. Since the cluster mass, density and
+temperature profiles are all similar to the well studied Coma cluster
+\citep{2007MNRAS.378..385P,pinzke10}, we will compare our calculations
+to radio and gamma-ray observations of Coma.
 
@@
 $\mathcal{M}$. It is given by the ratio of the upstream velocity
-($u_2$) and the sound speed ($c_s$). The CR number density and CR
+($\varv_2$) and the sound speed ($c_{\rm s}$). The CR number density and CR
 energy density are derived from
@@
   p_\rmn{inj} &=& x_\rmn{inj} p_\rmn{th} = x_\rmn{inj} \sqrt{\frac{2 \,\kB T_2}{m c^2}}\,, \nonumber \\
-  \rmn{where}\quad x_\rmn{inj} &\approx& 1.17 \frac{u_2}{p_{\rmn{th}}\,c} \left(1+
+  \rmn{where}\quad x_\rmn{inj} &\approx& 1.17 \frac{\varv_2}{p_{\rmn{th}}\,c} \left(1+
   \frac{1.07}{\epsilon_B}\right) \left(\frac{\mathcal{M}}{3}\right)^{0.1}\,.
@@
 complex plasma interactions. In this paper, we adopt $\eb = 0.23$,
-which we will later see corresponds to a conservative maximum energy
-acceleration efficiency for protons of $10\%$. To derive the
+which -- as we will later see -- corresponds to a conservative maximum
+energy acceleration efficiency for protons of $10\%$. To derive the
 acceleration efficiency, $\zeta_\rmn{inj}$, we first have to infer the
@@
 thermal gas particles which experience diffusive shock acceleration
-\citep[for details see ][]{pinzke13},
+\citep[for details see][]{pinzke13},
 \begin{equation}
@@
   viable for primarily perpendicular
-  shocks][]{2014ApJ...794..153G}. While this appears to contradict the
+  shocks,][]{2014ApJ...794..153G}. While this appears to contradict the
 radial bias of magnetic fields in the bulk of the ICM as suggested by
@@
 \subsection{Radio emission profile}
-
-%%% moved from before
-
-\begin{figure}
-  \includegraphics[width=1.0\columnwidth]{turb_profile_ratio_tot.eps}
-  \caption{The ratio of turbulent-to-thermal energy densities (solid
-    lines) and cumulative energies (dotted lines) in our three
-    models. The energy densities are parametrized as
-    $\eps_\rmn{turb} \propto
-    \eps_\rmn{th}^{(\alpha_{\rmn{tu}}+1)/2}/T^{1/4}$ and
-    normalized such that the total turbulent energy in compressible
-    modes $E_\rmn{turb}$ for each scenario makes up about 20\% of the
-    total thermal energy $E_\rmn{th}$ inside the radio halo
-    ($R_\rmn{RH}\approx0.6R_{200}$). The turbulent profiles explore
-    the uncertainty in the cluster turbulence and are motivated by the
-    cosmological simulation in
-    \citep{2009ApJ...705.1129L,2010ApJ...725.1452S,2011A&A...529A..17V}.}
-  \label{fig:turb}
-\end{figure}
-
-In this work we investigate
-different spatial models for injected turbulence. With the above
-choice of normalization, the turbulent energy density becomes
-$\eps_\rmn{turb} \propto
-\eps_\rmn{th}^{(\alpha_\rmn{tu}+1)/2}/T^{1/4}$, where $T$ is the
-temperature of the gas, $\alpha_\rmn{tu}= 0.67$ for \Mflatturb,
-$\alpha_\rmn{tu}= 0.82$ for \Mstream, and $\alpha_\rmn{tu}= 0.88$ for
-\Mprimary (see Figure~\ref{fig:turb} for visualization).
-
-Note that in previous work on the Coma cluster, $\eps_\rmn{turb}
-\propto \eps_\rmn{th}$ was adopted which roughly corresponds to
-$\alpha_\rmn{tu}= 1$ \citep{brunetti12} and together with the
-different distributions for seed CRes constitute the main differences
-compared to our work. Our flatter turbulent profiles are motivated by
-fits to cosmological simulations
-\citep{2009ApJ...705.1129L,2010ApJ...725.1452S,2011A&A...529A..17V,2012ApJ...758...74B}
-and the range indicates uncertainties of the turbulent profile in
-Coma. Future observations (by Astro-H) and simulations will help to
-clarify this issue.
-
-In Figure~\ref{fig:tauD} we show how the turbulent reacceleration
-timescales in our three models scale with radius. As expected, the
-\Mprimary model with $\alpha_\rmn{tu}=0.88$ has the flattest profile
-with $\tau_D\approx0.4\,\rmn{Gyr}$, where the small dip at large
-radius driven by the decrease in thermal energy density. The
-\Mflatturb model has the the flattest turbulent profile parameterized
-by the smaller $\alpha_\rmn{tu}$ which explains the steepest $\tau_D$
-profile. Note that a fixed reacceleration timescale is required to
-explain the observations at each radius and for each model (see also
-Table~\ref{tab:timescales}). This allows us to interchange the value
-of uncertain parameters $\tau_\rmn{cl} \sim X_\rmn{tu}^2 \sim k_0$,
-i.e. a longer reacceleration duration have to be compensated by
-lowering the level of turbulence or increasing the physical injection
-scale of turbulence to keep $\tau_D$ constant.
-
-\begin{figure}
-  \includegraphics[width=1.0\columnwidth]{tau_reacc.eps}
-  \caption{Turbulent reacceleration timescales for our simulated
-    cluster g72a. We show in linear-log the reacceleration timescale
-    ($\tau_D$) as a function of radius $R$ for our three models:
-    \Mprimary (green dotted line), \Mstream (blue dashed line), and
-    \Mflatturb (red solid line). Note that the timescales are derived
-    during the last 100~Myrs in time in our simulations.}
-  \label{fig:tauD}
-\end{figure}
-
-%%%
-
-In Fig.~\ref{fig:sync_profile}, we find that all three scenarios in
-which the seeds undergo Fermi-II reacceleration can reproduce the Coma
-RH profile at 352~MHz. \AP{It is also clear that without turbulent
-  reacceleration, the simulated radio profiles are too steep.} In the
-panel {\it Brunetti et al. (2012)} we show that without CR streaming
-or a flat turbulent profile, our simulations of reaccelerated CRs
-produce radio profiles that are too steep. Indeed, even using the
-assumptions of previous work -- where complete freedom in the seed
-population was allowed -- it is not possible to reproduce observations
-in both frequencies in any model. Note that decreasing acceleration
-efficiency with radius does not change this conclusion much because of
-the weak radial dependence of $D_\rmn{pp}(R)\propto
-\eps_\rmn{th}(R)^{\alpha_\rmn{tu}-1}\sqrt{T(R)}$. This signals that
-the problem is generic and requires either additional modifications to
-the plasma physics of acceleration or a better understanding of
-potential observational systematics. In addition there are differences
-in the simulated density and temperature profiles in comparison to the
-observed profile in Coma that impact the CR abundance as well as
-cooling and reacceleration.
-
-In principle, reacceleration via TTD leads to spectral steepening with
-particle energy due to the inefficiency of the acceleration process to
-counter the stronger cooling losses with increasing energy. Since
-synchrotron emission peaks at frequency $\nu_\rmn{syn}\simeq 1\,
-B/\umu\rmn{G} (\gamma/10^4)^2\,\rmn{GHz}$, this translates into a
-spectral steepening of the radio spectrum (see \AP{the left panel of
-  Fig.~\ref{fig:sync_spectrum}} where the continuous injection of
-secondary CRes is absent). A given radio window samples higher energy
-electrons for a decreasing field strength in the cluster
-outskirts. Hence, the spectral steepening with energy should translate
-into a radial spectral steepening \citep{brunetti12}. However, because
-of the weak dependence of the electron Lorentz factor on emission
-frequency ($\gamma\propto\sqrt{\nu_\rmn{syn}}$), this effect is only
-visible in our simulations for $\nu_\rmn{syn}\gtrsim5$~GHz. Most
-importantly, our simulated fluid elements at a given radius sample a
-broad distribution of shock history, density and temperature, which
-implies very similar synchrotron brightness profiles at
-$\nu_\rmn{syn}=352$~MHz and 1.4 GHz. The discrepancy of the observed
-and simulated 1.4 GHz profiles could instead be due to systematic flux
-calibration error in single dish observations. These could arise, for
-instance, due to errors in point source subtraction. Interestingly, we
-can match the 1.4 GHz data if we reduce the zero point by adding 10\%
-of the central flux to every data point; this flattens the outer
-profile\footnote{Lawrence Rudnick, private communication.}.
-Alternatively, this may point to weaknesses in the theoretical
-modeling of the particle acceleration process and may require a
-stronger cutoff in the particle energy spectrum.
 
@@
 
+In Fig.~\ref{fig:sync_profile}, we show radial profiles for the radio
+emission in all three scenarios in which the seeds undergo Fermi-II
+reacceleration in turbulent fields that are shaped such as to
+reproduce the Coma RH profile at 352~MHz.  Adopting our
+parametrisation for the volumetric injection rate of turbulent energy,
+$I_0\propto \eps_\rmn{th}^{\alpha_\rmn{tu}}$, we find
+$\alpha_\rmn{tu}= 0.67$ for \Mflatturb, $\alpha_\rmn{tu}= 0.82$ for
+\Mstream, and $\alpha_\rmn{tu}= 0.88$ for \Mprimary. As a result, the
+ratio of turbulent-to-thermal energy densities slightly increase with
+radius as shown in Fig.~\ref{fig:turb}.  After turbulent
+reacceleration, the volume-weighted, relative CRp energy density and
+relative CRp number density inside the RH for \Mflatturb (\Mstream),
+are found to be 2 (3) \% and $2\times10^{-8}$ ($5\times10^{-8}$),
+respectively.
+
+%the turbulent energy density becomes $\eps_\rmn{turb} \propto
+%\eps_\rmn{th}^{(\alpha_\rmn{tu}+1)/2}/T^{1/4}$, where $T$ is the
+%temperature of the gas,
+
+\begin{figure}
+  \includegraphics[width=1.0\columnwidth]{turb_profile_ratio_tot.eps}
+  \caption{The ratio of turbulent-to-thermal energy densities (solid
+    lines) and cumulative energies (dotted lines) in our three
+    models. The energy densities are parametrized as
+    $\eps_\rmn{turb} \propto
+    \eps_\rmn{th}^{(\alpha_{\rmn{tu}}+1)/2}/T^{1/4}$ and
+    normalized such that the total turbulent energy in compressible
+    modes $E_\rmn{turb}$ for each scenario makes up about 20\% of the
+    total thermal energy $E_\rmn{th}$ inside the radio halo
+    ($R_\rmn{RH}\approx0.6R_{200}$). The turbulent profiles explore
+    the uncertainty in the cluster turbulence and are motivated by the
+    cosmological simulation in
+    \citep{2009ApJ...705.1129L,2010ApJ...725.1452S,2011A&A...529A..17V}.}
+  \label{fig:turb}
+\end{figure}
+
+Figure~\ref{fig:sync_profile} demonstrates that the modeled radio
+profiles without turbulent reacceleration are too steep.  In the
+bottom right panel of Fig.~\ref{fig:sync_profile} (labeled with
+Brunetti et al. 2012), we show that our simulated profiles of
+reaccelerated CRs, which only take advective CR transport into
+account, i.e. they neglect CR streaming or a flatter turbulent
+profile, produce radio profiles that are too steep. Indeed, even using
+the assumptions of previous work -- where complete freedom in the seed
+population was allowed -- it is not possible to reproduce observations
+in both frequencies in any model.\footnote{Note that in previous work
+  on the Coma cluster, $\eps_\rmn{turb} \propto \eps_\rmn{th}$ was
+  adopted which approximately corresponds to $\alpha_\rmn{tu}= 1$
+  \citep{brunetti12} and together with the different distributions for
+  seed CRes constitute the main differences compared to our work.}
+Decreasing the acceleration efficiency with radius does not change
+this conclusion much because of the weak radial dependence of
+$D_\rmn{pp}(R)\propto \eps_\rmn{th}(R)^{\alpha_\rmn{tu}-1}
+\sqrt{T(R)}$. This signals that the problem is generic and requires
+either additional modifications to the plasma physics of acceleration
+or a better understanding of potential observational systematics. In
+addition there are differences in the simulated density and
+temperature profiles in comparison to the observed profile in Coma
+that impact the CR abundance as well as cooling and reacceleration.
+
+In Figure~\ref{fig:tauD} we show how the turbulent reacceleration
+timescales in our three models scale with radius. As expected, the
+\Mprimary model with $\alpha_\rmn{tu}=0.88$ has the flattest profile
+with $\tau_D\approx0.4\,\rmn{Gyr}$, where the small dip at large
+radius driven by the decrease in thermal energy density. The
+\Mflatturb model has the the flattest turbulent profile parameterized
+by the smaller $\alpha_\rmn{tu}$ which explains the steepest $\tau_D$
+profile. Note that a fixed reacceleration timescale is required to
+explain the observations at each radius and for each model (see also
+Table~\ref{tab:timescales}). This allows us to interchange the value
+of uncertain parameters $\tau_\rmn{cl} \sim X_\rmn{tu}^2 \sim k_0$,
+i.e. a longer reacceleration duration have to be compensated by
+lowering the level of turbulence or increasing the physical injection
+scale of turbulence to keep $\tau_D$ constant.
+
+\begin{figure}
+  \includegraphics[width=1.0\columnwidth]{tau_reacc.eps}
+  \caption{Turbulent reacceleration timescales for our simulated
+    cluster g72a. We show in linear-log the reacceleration timescale
+    ($\tau_D$) as a function of radius $R$ for our three models:
+    \Mprimary (green dotted line), \Mstream (blue dashed line), and
+    \Mflatturb (red solid line). Note that the timescales are derived
+    during the last 100~Myrs in time in our simulations.}
+  \label{fig:tauD}
+\end{figure}
+
+In principle, reacceleration via TTD leads to spectral steepening with
+particle energy due to the inefficiency of the acceleration process to
+counter the stronger cooling losses with increasing energy. Since
+synchrotron emission peaks at frequency $\nu_\rmn{syn}\simeq 1\,
+B/\umu\rmn{G} (\gamma/10^4)^2\,\rmn{GHz}$, this translates into a
+spectral steepening of the radio spectrum (see the left panel of
+Fig.~\ref{fig:sync_spectrum} where the continuous injection of
+secondary CRes is absent). A given radio window samples higher energy
+electrons for a decreasing field strength in the cluster
+outskirts. Hence, the spectral steepening with energy should translate
+into a radial spectral steepening \citep{brunetti12}. However, because
+of the weak dependence of the electron Lorentz factor on emission
+frequency ($\gamma\propto\sqrt{\nu_\rmn{syn}}$), this effect is only
+visible in our simulations for $\nu_\rmn{syn}\gtrsim5$~GHz. Most
+importantly, our simulated fluid elements at a given radius sample a
+broad distribution of shock history, density and temperature, which
+implies very similar synchrotron brightness profiles at
+$\nu_\rmn{syn}=352$~MHz and 1.4 GHz. The discrepancy of the observed
+and simulated 1.4 GHz profiles could instead be due to systematic flux
+calibration error in single dish observations. These could arise, for
+instance, due to errors in point source subtraction. Interestingly, we
+can match the 1.4 GHz data if we reduce the zero point by adding 10\%
+of the central flux to every data point; this flattens the outer
+profile\footnote{Lawrence Rudnick, private communication.}.
+Alternatively, this may point to weaknesses in the theoretical
+modeling of the particle acceleration process and may require a
+stronger cutoff in the particle energy spectrum.
+
 \subsection{Radio spectrum}
@@
 acceleration efficiency for protons $\zeta_{\rmn{p}}\sim0.0001-0.01$,
-and for electrons $\zeta_{\rmn{e}}\sim 0.001$. Interestingly, we find
-that the radio luminosity from clusters in the OFF-state (DSA only)
-and ON-state (DSA and reacceleration) differ by about a factor 10-20
-in all our three models. \AP{This means that the secondary CRes are
-  dominated by the reaccelerated fossil CRes and not from the CRes
-  produced by reaccelerated CRps. However, for high frequencies
-  ($\nu_\rmn{syn}\gtrsim$ GHz) where synchrotron cooling is more
-  efficient than reacceleration, the emission is dominated by the CRes
-  produced in the continuous injection of electrons from reaccelerated
-  CRps. It is also worth mentioning that the radio emission from
-  secondary CRes are smoothly distributed around the cluster because
-  of the continuous injection, hence the it is not dominated by
-  outliers.} However, \sout{note that} for \Mprimary, the primary CRes
-that generate most of the radio emission from the cluster in the
-OFF-state are dominated by only a small fraction of the CRes. These
-electrons are injected very recently and have not had time to cool
-yet. Hence we expect there to be a large variance in the OFF-state of
-different simulated clusters. As mentioned in
-section~\ref{sect:param_comp}, combining radio observations with
-gamma-ray limits allows us to put a lower limit to $X_\rmn{tu}$.  If
-$X_\rmn{tu}$ is smaller than in our adopted models (where we assume
-$X_\rmn{tu}=0.2$), then the efficiency of DSA has to be larger than
-$\zeta_\rmn{p}\sim 0.1$ for the secondary CRes to reproduce the radio
-observations. However, since the turbulent reacceleration acts on both
-the secondary CRes and the CRps, while $\zeta_\rmn{p}$ only affects
-the CRps, \Mstream and \Mflatturb would produce too much
-gamma-rays. Hence we conclude that $X_\rmn{tu}\gtrsim0.2$ if all other
-parameters are kept fixed. Although, we caution the reader to take
-this limit too stringent because of the uncertainty in $k_0$ and
-$\tau_\rmn{cl}$ that impact $X_\rmn{tu}$ for a fixed
-$\tau_\rmn{D}$. This parameter space needs to be explored further in
-future work in order to put more stringent limits on the level of
-turbulence in clusters using radio and gamma-ray observations in
-combination with turbulent reaccelerated CRs.
+and for electrons $\zeta_{\rmn{e}}\sim 0.001$.
+
+Interestingly, we find that the radio luminosity from clusters in the
+OFF-state (DSA only) and ON-state (DSA and reacceleration) differ by
+about a factor 10-20 in all our three models. This means that the
+secondary CRes are dominated by the reaccelerated fossil CRes and not
+from the CRes produced by reaccelerated CRps. However, for high
+frequencies ($\nu_\rmn{syn}\gtrsim$ GHz) where synchrotron cooling is
+more efficient than reacceleration, the emission is dominated by the
+CRes produced in the continuous injection of electrons from
+reaccelerated CRps. It is also worth mentioning that the radio
+emission from secondary CRes are smoothly distributed around the
+cluster because of the continuous injection, hence the it is not
+dominated by outliers.
+
+However, for \Mprimary, the primary CRes that generate most of the
+radio emission from the cluster in the OFF-state are dominated by only
+a small fraction of the CRes. These electrons are injected very
+recently and have not had time to cool yet. Hence we expect there to
+be a large variance in the OFF-state of different simulated
+clusters. As mentioned in section~\ref{sect:param_comp}, combining
+radio observations with gamma-ray limits allows us to put a lower
+limit to $X_\rmn{tu}$.  If $X_\rmn{tu}$ is smaller than in our adopted
+models (where we assume $X_\rmn{tu}=0.2$), then the efficiency of DSA
+has to be larger than $\zeta_\rmn{p}\sim 0.1$ for the secondary CRes
+to reproduce the radio observations. However, since the turbulent
+reacceleration acts on both the secondary CRes and the CRps, while
+$\zeta_\rmn{p}$ only affects the CRps, \Mstream and \Mflatturb would
+produce too much gamma-rays. Hence we conclude that
+$X_\rmn{tu}\gtrsim0.2$ if all other parameters are kept
+fixed. Although, we caution the reader to take this limit too
+stringent because of the uncertainty in $k_0$ and $\tau_\rmn{cl}$ that
+impact $X_\rmn{tu}$ for a fixed $\tau_\rmn{D}$. This parameter space
+needs to be explored further in future work in order to put more
+stringent limits on the level of turbulence in clusters using radio
+and gamma-ray observations in combination with turbulent reaccelerated
+CRs.
 
@@
 primary or secondary seed population of electrons observationally?
-\AP{I do not understand the next scentence, could you clarify?} One
-possibility that is relative insensitive to adopted parameters in our
-models is to use high-frequency radio observations (with e.g., the
-Jansky Very Large Array) where turbulent reacceleration (which has a
-high energy cutoff) is no longer efficient (see
-Fig.~\ref{fig:sync_spectrum}). The negative flux bowl of the
-Sunyaev-Zel'dovich effect introduces a cutoff of the RH spectrum at
-frequencies above $\gtrsim 10$~GHz \citep[][ depending on cluster mass
-  and redshift]{2002A&A...396L..17E,Pfrommer:2003mk}. Hence the
-subdominant \sout{hadronic} radio emission \AP{from freshly injected
-  secondary CRes} may only be detectable in steep spectrum radio
-sources \citep{2008Natur.455..944B}, which exhibit a cutoff at lower
-radio frequencies and are thought to represent dying RHs as a result
-of the decaying turbulence after a merger. Alternatively, one could
-attempt to reconstruct the intrinsic high-frequency RH spectrum by
-filling in the missing flux due to the Sunyaev-Zel'dovich effect by
-precise measurements of the Compton-$y$ parameter at microwave
+One possibility that is relative insensitive to adopted parameters in
+our models is to use high-frequency radio observations (with e.g., the
+Jansky Very Large Array) where turbulent reacceleration of CRes (which
+has a high energy cutoff) is no longer efficient since their fast
+radiative cooling time drops below the comparably slow reacceleration
+timescale producing a sharp spectral cutoff. This is unlike
+reacceleration of CRps that do not suffer radiative cooling losses and
+inject power-law momentum distributions of secondary CRe (see
+Fig.~\ref{fig:sync_spectrum}).
+
+However, the negative flux bowl of the Sunyaev-Zel'dovich effect
+introduces a cutoff of the RH spectrum at frequencies above $\gtrsim
+10$~GHz \citep[][ depending on cluster mass and
+  redshift]{2002A&A...396L..17E,Pfrommer:2003mk}. Hence the
+subdominant radio emission from freshly injected secondary CRes may
+only be detectable in steep spectrum radio sources
+\citep{2008Natur.455..944B}, which exhibit a cutoff at lower radio
+frequencies and are thought to represent dying RHs as a result of the
+decaying turbulence after a merger. Alternatively, one could attempt
+to reconstruct the intrinsic high-frequency RH spectrum by filling in
+the missing flux due to the Sunyaev-Zel'dovich effect by precise
+measurements of the Compton-$y$ parameter at microwave
 frequencies. Another possibility would consist in stacking the radio
 data of radio-quiet clusters that do not exhibit RH emission
-\AP{individually} \citep{2011ApJ...740L..28B}. This may reveal the
+individually \citep{2011ApJ...740L..28B}. This may reveal the
 glow of radio emission due to steady state secondary
@@
 cooling, and will not be visible at high energies (see
-Fig.~\ref{fig:sync_spectrum}). \AP{Finally we want to mention that in
-  the near future we hope to gain valuable information about the
-  turbulent profile in galaxy clusters from the recently launched
-  X-ray satellite ASTRO-H. Alternatively, as magnetohydrodynamic
-  simulations improve, these can provide valuable insight about the
-  profile and the total energy of turbulence in clusters. This will
-  further help us to distinguish the three different models from each
-  other.} We will pursue further implications and distinguishing
-characteristics of these competing models in future work.
+Fig.~\ref{fig:sync_spectrum}).
+
+As MHD simulations of clusters that follow spectral CR distributions
+become feasible, these will provide valuable insight about the profile
+and the total energy of turbulence in clusters and the possibility of
+turbulent reacceleration. This will further help us to distinguish the
+three different models from each other. We will pursue further
+implications and distinguishing characteristics of these competing
+models in future work.
 

### 2016-05-09 paper.tex
Add files via upload

@@
 CRs have been reaccelerated for $\tau_\rmn{cl} = 650\,\rmn{Myr}$, we
-calculate the resulting radio emission and compare the emission
-profiles and spectra as we vary one parameter at the time relative to
-our fiducial model.
+calculate the resulting radio emission \AP{numerically using the
+  formalism outlined in \cite{1979rpa..book.....R}} and compare the
+emission profiles and spectra as we vary one parameter at the time
+relative to our fiducial model.
 
@@
 hence it is interesting to estimate this emission for our models and
-compare to upper limits. We predict the gamma-ray emission from
-\Mflatturb (\Mstream) with $F_\gamma(>500\,\rmn{MeV})=4\times10^{-10}
-(5\times10^{-10}) \mathrm{ \,ph\, s}^{-1}\mathrm{cm}^{-2}$. The fluxes
-from these models are slightly larger than in \cite{brunetti12}, where
-the differences comes from our steeper CRp profiles in addition to
-simulation based formalism we rely on that accounts for both Coulomb
-and hadronic losses during the build up of the CR distribution in
-contrast to the scaling relations adopted in their
-paper. Interestingly the gamma-ray flux from both our scenarios are
-just below recent Fermi-LAT limits derived from a gamma-ray profile
-similar to \Mflatturb where
+compare to upper limits. \AP{We follow the formalism outlined in
+  \cite{1999APh....12..169B} (and references therein) and calculate
+  the gamma-ray emission numerically for our three models.} We predict
+the gamma-ray emission from \Mflatturb (\Mstream) with
+$F_\gamma(>500\,\rmn{MeV})=4\times10^{-10} (5\times10^{-10}) \mathrm{
+  \,ph\, s}^{-1}\mathrm{cm}^{-2}$. The fluxes from these models are
+slightly larger than in \cite{brunetti12}, where the differences comes
+from our steeper CRp profiles in addition to simulation based
+formalism we rely on that accounts for both Coulomb and hadronic
+losses during the build up of the CR distribution in contrast to the
+scaling relations adopted in their paper. Interestingly the gamma-ray
+flux from both our scenarios are just below recent Fermi-LAT limits
+derived from a gamma-ray profile similar to \Mflatturb where
 $F_\gamma(>500\,\rmn{MeV})<5.3\times10^{-10} \mathrm{ \,ph\,

### 2016-05-11 paper.tex
Peng's edits - v1

@@
 relatively unknown non-thermal physics in the ICM. Here we develop a
-simplified framework that will be used to explore the robustness of
-our models to the most critical parameters related to turbulence and
-CRs.
+simplified framework that will be used to explore %%the robustness of
+%%our models to the most critical parameters related to turbulence and
+%%CRs.
+how radio emission depends on these parameters. Our fiducial model is meant to be compared against the Coma cluster.
 
@@
 
-As we have seen before, the resulting radio-emitting CRe distribution
-depends on compressible turbulence (which sets the level of
-reacceleration) and the distribution of pre-existing CRs. Hence we
+As we have seen before, the most uncertain aspects of radio halo emission models are the profile of compressible turbulence (which determines the amount of Fermi II acceleration) and the distribution of pre-existing CRs.
+Hence we
 vary parameters describing the amount of energy contained in
-turbulence relative to the thermal energy, $X_{\rm tu}$, the spatial
-profile of turbulence as parametrized by $\alpha_{\rm tu}$, as well as
+turbulence, $X_{\rm tu}$ (defined by $E_{\rm therm} = X_{\rm tu} E_{\rm therm}$), the spatial
+profile of turbulence as parametrized by $\alpha_{\rm tu}$ (defined by $I_{\rm o} \propto \epsilon_{\rm therm}^{\alpha_{\rm tu}}$, where $I_{\rm o} \propto v_{O}^{3} k_{0}$ is the injection rate of turbulence), as well as
 the spatial CR profile that we will parametrize by $\alpha_{\rm CR,
-  spat}$ (see below).  In order to quickly explore this parameter
+  spat}$ (see below).
+We hold fixed thermal plasma properties (temperature and density profiles), B-field profiles, total CR energy content, and the turbulent outer scale (corresponding to a wavenumber $k_{0}$).
+The CR energy content is suggested by our simulations (observations only give an upper bound; \citet{arlen12}).
+We focus on the uncertain CR distribution rather than the overall normalization, since the impact of the latter (an overall linear scaling) is clear.
+In order to quickly explore this parameter
 space, we solve the Fokker-Planck equation in static spherical shells
 for injection, reacceleration, and losses of the CRs, i.e., we neglect
-the Lagrangian trajectories during the re-acceleration time.  Once the
+Lagrangian evolution during re-acceleration.
+This ignores the effect of adiabatic compressive heating of the CRs, though this is generally subdominant (e.g., see Fig.
+7 of \citet{miniati15}).
+Once the
 CRs have been reaccelerated for $\tau_\rmn{cl} = 650\,\rmn{Myr}$, we
@@
   formalism outlined in \cite{1979rpa..book.....R}} and compare the
-emission profiles and spectra as we vary one parameter at the time
+emission profiles and spectra as we vary one parameter at a time
 relative to our fiducial model.
@@
 with $n_0=3.4\times10^{-3}\,\rmn{cm}^{-3}$.  The virial and core radii
-of Coma are given by $R_{200} = 2300\,\rmn{kpc}$
+of Coma are given by $R_{200} = 2.3\,\rmn{Mpc}$
 \citep{2002ApJ...567..716R} and $R_{\rmn{c}} = 294\,\rmn{kpc}$,
-respectively.
+respectively. In accordance with rotation measure measurements, we assume $B(r)=B_{0} (n/n_{0})^{\eta}$, where $B_{0}=4.8 \mu$G and $\eta=0.5$ \citep{bonafede10}.
 
@@
 \rmn{d}V\left(\int_0^{R_{200}}\eps_\rmn{th} \rmn{d}V\right)^{-1} =
-0.003$. Note that the injected energy in the last 650 Mys is smaller
+0.003$. Note that the injected energy in the last 650 Myr is smaller
 by about a factor of 10 in comparison to the cumulative CR energy
-injected over the entire cosmological history of the cluster.
+injected over the entire cosmological history of the cluster. \AP{So why can't we just neglect the population injected during the merger?}  
 Similarly, the initial CRe distribution is given by the steady state
 between cooling (Coulomb, inverse Compton, and synchrotron) and
-injection of secondary CRes from $f_\rmn{p,0}$. We also include the
-continuous injection of secondary CRes during $\tau_\rmn{cl}$. The
-compressible turbulence responsible for reaccelerating both the CRps
-and CRes is parameterized by $I_0 \propto X_\rmn{tu} (n_{\rmn{e}}
-T)^{\alpha_\rmn{tu}}$. The diffusion constant $D_{pp}$ is calculated
+injection of secondary CRes from $f_\rmn{p,0}$. %We also include the
+%continuous injection of secondary CRes during $\tau_\rmn{cl}$. 
+%The
+%compressible turbulence responsible for reaccelerating both the CRps
+%and CRes is parameterized by $I_0 \propto X_\rmn{tu} (n_{\rmn{e}}
+%T)^{\alpha_\rmn{tu}}$. 
+\AP{Do we include injection by primaries, is it negligible?} 
+The diffusion constant $D_{pp} \propto X_{\rm tu}^{2} \epsilon_{\rm th}^{\alpha-1} \sqrt{T} k_{\rm 0}$ is calculated
 for each radial bin using Eqns.~\ref{eq:dpp}-\ref{eq:Gamma_e}. All
@@
 simulated cluster (see Sect.~\ref{sec:results}).
+Our fiducial model assumes $X_{\rm tu} = 0.2$, $\alpha_{\rm tu} =0.8$, $\alpha_{\rm CR, spat}=1.0$, and $k_{\rm 0}=2 \pi/\lambda_{\rm 0}$ where $\lambda_{\rm 0}=100$ kpc.
 
@@
 Figure~\ref{fig:param_comp} shows the impact of turbulence and the
-spatial distribution of CRs on the radio emission.  We find that the
+spatial distribution of CRs on the radio emission.
+
+{\bf $X_{\rm tu}$} Besides the overall increase in radio luminosity as $X_{\rm tu}$ increases, there are changes in spatial and spectral profiles.
+An increase in $X_{\rm tu}$ flattens the surface brightness profile, since high acceleration efficiency leads to larger amplification in the cluster outskirts (where cooling is less important) than the center.
+In particular, in the cluster outskirts, the reduced impact of Coulomb cooling implies that there is a larger pool of low-energy electrons available for reacceleration (see timescales in Table \ref{tab:timescales}).
+Larger levels of turbulence also {\it increase} spectral curvature, which might seem puzzling.
+It can be understood as follows.
+The pre-acceleration electron distribution function can be understood as a result of competition between injection $f \propto p^{-\alpha_{\rm inj}}$ and cooling.
+At low momenta, when the Coulomb cooling time is short, $f \propto p^{-\alpha_{\rm inj}+1}$, at high momenta, when inverse Compton/synchrotron cooling dominates, $f \propto p^{-\alpha_{\rm inj} -1}$.
+In between, there is a quasi-adiabatic regime where electrons accumulate (for more details, and an analytic self-similar solution, see \citet{sarazin99, pinzke13}).
+In the absence of cooling, momentum advection in the limit $D_{\rm pp} \propto p^{2}$ (so that $\tau =p^{2}/4 D_{\rm pp}$ is momentum independent) simply shifts the distribution $f(p) \rightarrow f(A p)$.
+When the acceleration efficiency is low, most observable emission corresponds to the power-law tail of the distribution function $f \propto p^{-\alpha_{\rm inj}-1}$ set by the balance between injection and synchrotron/IC cooling.
+However, as the acceleration efficiency $A$ increases, radio emission starts to probe the 'bump' around $p_{*}$ (given by $\tau_{\rm D} \sim \tau_{\rm cool}(p_{*})$) where electrons accumulate and the distribution function is curved.
+This results in a curved emission spectrum.
+The synchrotron spectrum steepens at the frequency \citep{brunetti01}:
+\begin{equation}
+\nu_{\rm s} \propto \frac{B \tau_{\rm D}^{-2}}{(B^{2}+B^{2}_{\rm CMB})^{2}}
+\end{equation}
+where $B_{\rm CMB} \equiv (8 \pi U_{\rm CMB})^{1/2}$, which increases for shorter $\tau_{\rm D}$.
+
+We find that the
 level of turbulence ($X_\rmn{tu}$) has a large impact on both radio
@@
 reacceleration efficiency.
+
+\SPO{Stopped here}
 

### 2016-05-11 paper.tex
smal edits

@@
 relatively unknown non-thermal physics in the ICM. Here we develop a
-simplified framework that will be used to explore %%the robustness of
-%%our models to the most critical parameters related to turbulence and
-%%CRs.
-how radio emission depends on these parameters. Our fiducial model is meant to be compared against the Coma cluster.
+simplified framework that will be used to explore how radio emission
+depends on these parameters. Our fiducial model is meant to be
+compared against the Coma cluster.
 
@@
 
-As we have seen before, the most uncertain aspects of radio halo emission models are the profile of compressible turbulence (which determines the amount of Fermi II acceleration) and the distribution of pre-existing CRs.
-Hence we
-vary parameters describing the amount of energy contained in
-turbulence, $X_{\rm tu}$ (defined by $E_{\rm therm} = X_{\rm tu} E_{\rm therm}$), the spatial
-profile of turbulence as parametrized by $\alpha_{\rm tu}$ (defined by $I_{\rm o} \propto \epsilon_{\rm therm}^{\alpha_{\rm tu}}$, where $I_{\rm o} \propto v_{O}^{3} k_{0}$ is the injection rate of turbulence), as well as
+As we have seen before, the most uncertain aspects of radio halo
+emission models are the profile of compressible turbulence (which
+determines the amount of Fermi II acceleration) and the distribution
+of pre-existing CRs. Hence we vary parameters describing the amount of
+energy contained in turbulence, $X_{\rm tu}$ (defined by $E_{\rm
+  therm} = X_{\rm tu} E_{\rm therm}$), the spatial profile of
+turbulence as parametrized by $\alpha_{\rm tu}$ (defined by $I_0
+\propto \epsilon_{\rm therm}^{\alpha_{\rm tu}}$, where $I_0^{} \propto
+\varv_0^{3} k_0^{}$ is the injection rate of turbulence), as well as
 the spatial CR profile that we will parametrize by $\alpha_{\rm CR,
-  spat}$ (see below).
-We hold fixed thermal plasma properties (temperature and density profiles), B-field profiles, total CR energy content, and the turbulent outer scale (corresponding to a wavenumber $k_{0}$).
-The CR energy content is suggested by our simulations (observations only give an upper bound; \citet{arlen12}).
-We focus on the uncertain CR distribution rather than the overall normalization, since the impact of the latter (an overall linear scaling) is clear.
-In order to quickly explore this parameter
-space, we solve the Fokker-Planck equation in static spherical shells
-for injection, reacceleration, and losses of the CRs, i.e., we neglect
-Lagrangian evolution during re-acceleration.
-This ignores the effect of adiabatic compressive heating of the CRs, though this is generally subdominant (e.g., see Fig.
-7 of \citet{miniati15}).
-Once the
-CRs have been reaccelerated for $\tau_\rmn{cl} = 650\,\rmn{Myr}$, we
-calculate the resulting radio emission \AP{numerically using the
-  formalism outlined in \cite{1979rpa..book.....R}} and compare the
+  spat}$ (see below).  We hold fixed thermal plasma properties
+(temperature and density profiles), $B$-field profiles, total CR energy
+content, and the turbulent outer scale (corresponding to a wavenumber
+$k_{0}$). The CR energy content is suggested by our simulations
+(observations only give an upper bound;
+\citealt{2012ApJ...757..123A}). We focus on the uncertain CR
+distribution rather than the overall normalization, since the impact
+of the latter (an overall linear scaling) is clear.
+
+In order to quickly explore this parameter space, we solve the
+Fokker-Planck equation in static spherical shells for injection,
+reacceleration, and losses of the CRs, i.e., we neglect Lagrangian
+evolution during re-acceleration.  This ignores the effect of
+adiabatic compressive heating of the CRs, though this is generally
+subdominant (e.g., see Fig. 7 of \citealt{2015ApJ...800...60M}). Once
+the CRs have been reaccelerated for $\tau_\rmn{cl} = 650\,\rmn{Myr}$,
+we calculate the resulting radio emission numerically using the
+formalism outlined in \cite{1979rpa..book.....R} and compare the
 emission profiles and spectra as we vary one parameter at a time
@@
 \AP{Do we include injection by primaries, is it negligible?} 
-The diffusion constant $D_{pp} \propto X_{\rm tu}^{2} \epsilon_{\rm th}^{\alpha-1} \sqrt{T} k_{\rm 0}$ is calculated
+The diffusion constant $D_{pp} \propto X_{\rm tu}^{2} \eps_{\rm th}^{\alpha-1} \sqrt{T} k_{\rm 0}$ is calculated
 for each radial bin using Eqns.~\ref{eq:dpp}-\ref{eq:Gamma_e}. All
@@
 
-{\bf $X_{\rm tu}$} Besides the overall increase in radio luminosity as $X_{\rm tu}$ increases, there are changes in spatial and spectral profiles.
+{\bf Impact of $X_{\rm tu}$.} Besides the overall increase in radio luminosity as $X_{\rm tu}$ increases, there are changes in spatial and spectral profiles.
 An increase in $X_{\rm tu}$ flattens the surface brightness profile, since high acceleration efficiency leads to larger amplification in the cluster outskirts (where cooling is less important) than the center.
@@
 At low momenta, when the Coulomb cooling time is short, $f \propto p^{-\alpha_{\rm inj}+1}$, at high momenta, when inverse Compton/synchrotron cooling dominates, $f \propto p^{-\alpha_{\rm inj} -1}$.
-In between, there is a quasi-adiabatic regime where electrons accumulate (for more details, and an analytic self-similar solution, see \citet{sarazin99, pinzke13}).
-In the absence of cooling, momentum advection in the limit $D_{\rm pp} \propto p^{2}$ (so that $\tau =p^{2}/4 D_{\rm pp}$ is momentum independent) simply shifts the distribution $f(p) \rightarrow f(A p)$.
+In between, there is a quasi-adiabatic regime where electrons accumulate (for more details, and an analytic self-similar solution, see \citealt{1999ApJ...520..529S, pinzke13}).
+In the absence of cooling, momentum advection in the limit $D_{pp} \propto p^{2}$ (so that $\tau =p^{2}/4 D_{pp}$ is momentum independent) simply shifts the distribution $f(p) \rightarrow f(A p)$.
 When the acceleration efficiency is low, most observable emission corresponds to the power-law tail of the distribution function $f \propto p^{-\alpha_{\rm inj}-1}$ set by the balance between injection and synchrotron/IC cooling.
@@
 hence it is interesting to estimate this emission for our models and
-compare to upper limits. \AP{We follow the formalism outlined in
+compare to upper limits. We follow the formalism outlined in
   \cite{1999APh....12..169B} (and references therein) and calculate
-  the gamma-ray emission numerically for our three models.} We predict
+  the gamma-ray emission numerically for our three models. We predict
 the gamma-ray emission from \Mflatturb (\Mstream) with

### 2016-05-13 paper.tex
Peng's changes to parameter exploration and conclusions

@@
 
+The characteristic synchrotron frequency is $\nu_{\rm s} \sim 3 \gamma^{2} \nu_{\rm c}^{2}$, where $\nu_{\rm c}$ is the non-relativistic cyclotron frequency.
+Thus, for a given observation frequency, the greatest contribution comes from electrons with:
+\begin{equation}
+\nu_{\rm emit} \approx 6.6 \times 10^{3} \left( \frac{\nu_{\rm obs}}{350 \, {\rm MHz}} \right)^{1/2} \left(\frac{B}{1 \, \mu{\rm G}} \right)^{1/2} (1+z)^{1/2}.
+\end{equation}
+
 {\bf Scaling solutions} Since the diffusion time is independent of energy (the so-call 'hard sphere' approximation), analytic solutions are possible.
@@
 
+% --- section: Simulation Results and discussion --- %
+\section{Cosmological simulations}
+\label{sec:results}
+
+In this setion, we solve the Fokker-Planck equation for CR transport
+on Lagrangian particle trajectories through cosmic history.  We
+concentrate on three scenarios. (i) In model {\em M-primaries}, we
+assume that CR electrons, which have been accelerated by cosmic
+formation shocks and successively cooled by inverse Compton and
+synchrotron losses, form a fossil seed population for
+reacceleration. (ii) In model {\em M-streaming}, we account for the
+outward streaming of central CRps, which produces a flat CR
+distribution in the ICM and equivalently a flat secondary seed
+population of CRe for reacceleration. (iii) In model {\em
+  M-turbulence} we adopt a spatially flatter turbulent profile than
+what was adopted before but assume that seed CRps and secondary CRes
+follow the steep profile that is suggested by structure formation
+simulations.
+
+The level of emission is mainly driven by how efficient the CRs are
+reaccelerated and for how long. Hence, we exploit the exponential
+sensitivity of reacceleration on the level of turbulence and adopt
+different radial profiles of the turbulent energy density. We ask the
+question how differently the turbulent profiles need to be shaped in
+order to reproduce the observed radial profiles of the radio
+emission. For these models, we then compute radio spectra and
+gamma-ray luminosities and compare to observational data.
+
+\subsection{Modelling diffusive shock acceleration}
+\label{sec:cosmo_sim}
+In this paper we focus on our simulated cluster, g72a, which is a
+massive cluster of mass $M_{200}=1.6\times10^{15}\,M_\odot$ that
+experienced a merger about 1 Gyr ago
+\citep{2009MNRAS.399..497D}. Since the cluster mass, density and
+temperature profiles are all similar to the well studied Coma cluster
+\citep{2007MNRAS.378..385P,pinzke10}, we will compare our calculations
+to radio and gamma-ray observations of Coma.
+
+We use a simple test-particle model for the CR acceleration and
+injection, where each shock injects CRs that trace a power-law in
+momentum,
+\begin{equation}
+  f_\p(p,t) = C(t)\,p^{\alpha_\rmn{inj}}\,,\quad
+  \alpha_\rmn{inj}=\frac{(\gamma_\rmn{ad}+1)\mathcal{M}^2}
+        {(\gamma_\rmn{ad}-1)\mathcal{M}^2+2}
+\end{equation}
+determined by the normalization $C(t)$ and the spectral index
+$\alpha_{\rmn{inj}}$ that depends on the adiabatic index
+$\gamma_\rmn{ad} = 5/3$ and the Mach number of the shock
+$\mathcal{M}$. It is given by the ratio of the upstream velocity
+($\varv_2$) and the sound speed ($c_{\rm s}$). The CR number density and CR
+energy density are derived from
+\begin{eqnarray}
+n_\rmn{p} &=&
+\int_{p_\rmn{inj}}^\infty \dd p\, f_\p(p)\\
+\eps_\rmn{p} &=&
+\int_{p_\rmn{inj}}^\infty \dd p\, f_\p(p) \,E(p),
+\end{eqnarray}
+where $E(p) = (\sqrt{1+p^2} -1)\, m\,c^2$ is the kinetic energy of a
+particle with momentum $p$. We adopt a fit to Monte Carlo simulations
+of the thermal leakage process that relates the momentum of injected
+protons ($p_\rmn{inj}$) to the thermal energy ($p_\rmn{th}$) of the
+shocked plasma \citep{kang11}:
+\begin{eqnarray}
+  \label{eq:qinj}
+  p_\rmn{inj} &=& x_\rmn{inj} p_\rmn{th} = x_\rmn{inj} \sqrt{\frac{2 \,\kB T_2}{m c^2}}\,, \nonumber \\
+  \rmn{where}\quad x_\rmn{inj} &\approx& 1.17 \frac{\varv_2}{p_{\rmn{th}}\,c} \left(1+
+  \frac{1.07}{\epsilon_B}\right) \left(\frac{\mathcal{M}}{3}\right)^{0.1}\,.
+\end{eqnarray}
+Here $\eb = B_0/B_{\perp}$, $B_0$ is the amplitude of the downstream
+MHD wave turbulence, and $B_{\perp}$ is the magnetic field along the
+shock normal. The physical range of $\eb$ is quite uncertain due to
+complex plasma interactions. In this paper, we adopt $\eb = 0.23$,
+which -- as we will later see -- corresponds to a conservative maximum
+energy acceleration efficiency for protons of $10\%$. To derive the
+acceleration efficiency, $\zeta_\rmn{inj}$, we first have to infer the
+particle injection efficiency, which is the fraction of downstream
+thermal gas particles which experience diffusive shock acceleration
+\citep[for details see][]{pinzke13},
+\begin{equation}
+  \label{eq:eta}
+  \eta_\rmn{p,lin} =
+  \frac{4}{\sqrt{\upi}}\,\frac{x_\rmn{inj}^3}{\alpha_\rmn{inj}-1}\,
+  \rmn{e}^{-x_\rmn{inj}^2}.
+\end{equation}
+The particle injection efficiency is a strong function of
+$x_\rmn{inj}$ that depends on both $\mathcal{M}$ and $\eb$. The
+energy density of CRs that are injected and accelerated at the shock
+(neglecting the CR back reaction on the shock) is given by
+\begin{equation}
+\label{eq:CR_energy} 
+  \Delta\eps_\rmn{p,lin} =
+  \eta_\rmn{p,lin}(\mathcal{M})\,n_\rmn{th}(T_2)
+  \,\frac{\eps_\p}{n_\p}
+\end{equation}
+and the CR energy injection and acceleration efficiency is:
+\begin{equation}
+  \zeta_\rmn{lin} =
+  \frac{\Delta\eps_\rmn{p,lin}}{\Delta\eps_\rmn{diss}},
+   \quad\mbox{where}\quad
+  \Delta\eps_\rmn{diss} = \eps_\rmn{th2} - \eps_\rmn{th0}\,\left(\frac{\rho_2}{\rho_0}\right)^{\gamma_\rmn{ad}}\,.
+\label{eqn:energy_frac}  
+\end{equation}
+The dissipated energy density in the downstream regime,
+$\Delta\eps_\rmn{diss}$, is given by the difference of the thermal
+energy densities in the pre- and post-shock regimes, corrected for the
+adiabatic energy increase due to gas compression.
+
+We limit the acceleration efficiency to $\zeta_\rmn{max}$ by
+steepening the spectral index of the injected population
+$\alpha_\rmn{inj}$ to $\alpha_\rmn{sub}$ so that $\zeta_\rmn{lin}
+\leq \zeta_\rmn{max}$ is always fulfilled. The slope
+$\alpha_\rmn{inj}$ impact $\zeta_\rmn{inj}$ via the mean energy per
+particle, $\eps_\rmn{p}/n_\rmn{p}$. This
+procedure conserves energy and is motivated by models of non-linear
+shock acceleration where a sub-shock with a lower compression ratio
+(and hence steeper spectral index) forms
+\citep[e.g.,][]{2000ApJ...540..292E}. Given our assumed $\eb=0.23$, we
+find that for strong shocks where $\alpha \lesssim 2.3$ the spectral
+slope is steepened by a maximum of $\sim 10$ per cent in low
+temperature regimes ($\kB T\sim 0.1$~keV), while the steepening is much
+smaller for high temperature regimes ($\kB T\sim 10$~keV) that are more
+relevant for clusters. Since $p_\rmn{inj}$ remains fixed, so does the
+CR number density $n_\rmn{p}$. Hence we can solve for the
+renormalized normalization constant $C_\rmn{sub}$ using $n_\rmn{p}$
+and Eqn.~\ref{eq:eta}:
+\begin{equation}
+  \label{eq:Cp_sub}
+  C_\rmn{sub}=\eta_\rmn{p,lin}\,(\alpha_\rmn{sub}-1)\,p_\rmn{inj}^{\alpha_\rmn{sub}-1}\,,
+\end{equation}
+where the new distribution function is given by $f_\p(p,t)= C_\rmn{sub}
+p^{-\alpha_\rmn{sub}}$. We set an upper limit on the ratio of
+accelerated proton-to-dissipated energy in the downstream of strong
+shocks that varies from $\zeta_\rmn{max} \sim 1-10\%$, depending on
+the adopted model (for more details, see Section \ref{sec:results}).
+
+In our Galaxy, the CRe-to-CRp ratio at a few GeV is $K_{\rmn{ep}} \sim
+10^{-2}$. Hence, we adopt this as a fiducial value for the CRe-to-CRp
+acceleration efficiency \citep[see][for more
+  discussion]{pinzke13}. However, as recent PIC simulations have
+shown, this is likely very different at weak shocks, with electrons
+efficiently accelerated at perpendicular shocks
+\citep{2014ApJ...794..153G,2014ApJ...797...47G}, and ions efficiently
+accelerated at parallel shocks \citep{2014ApJ...783...91C}. Thus,
+depending on magnetic geometry, $K_{\rmn{ep}}$ could be either larger
+or smaller. Some observations of radio relics suggest high values of
+$K_{\rmn{ep}}$, due to the absence of gamma-ray emission, which probes
+the CRp population \citep{2014MNRAS.437.2291V}. This suggests primary
+CRes as a viable alternative scenario to secondary CRes as seeds for
+the giant RHs. In our {\em M-primaries} scenario, the injected
+distribution of CRes is derived in the same way as for the CRps. Once
+they have been accelerated to relativistic energies, injected
+electrons and protons are indistinguishable. We therefore assume that
+CRp and CRe have the same distribution function $f_\rmn{e}(p) =
+K_\rmn{ep} f_\rmn{p}(p)$, with a different normalization (due to
+differing acceleration efficiencies) $K_\rmn{ep}=0.1$ \citep[which is
+  viable for primarily perpendicular
+  shocks,][]{2014ApJ...794..153G}. While this appears to contradict the
+radial bias of magnetic fields in the bulk of the ICM as suggested by
+observations \citep{2010NatPh...6..520P} and cluster simulations
+\citep{2011ApJ...740...81R}, it does not necessarily apply to the
+accretion shock regions, which show a field geometry with a net
+perpendicular bias with respect to the shock normal---at least for
+giant radio relics \citep{2010Sci...330..347V}.
+
+\subsection{Radio emission profile}
+
+\begin{figure*}
+\begin{minipage}{1\columnwidth}
+   \begin{center}\Large{\Mprimary:}\\
+     \includegraphics[width=\columnwidth]{sbright.nu.DIIcomp.Pri.g72a.Rad14.2400p.z0.NL.xKR.eb23.eI088.140.v6.eps}
+   \end{center}
+\end{minipage}
+\begin{minipage}{1\columnwidth}
+   \begin{center}\Large{\Mstream:}\\
+     \includegraphics[width=\columnwidth]{sbright.nu.DIIcomp.flatCR.g72a.Rad14.2400p.z0.NL.xKR.eb23.eI082.flatCR.140.v6.eps}
+   \end{center}
+\end{minipage}
+\\
+\begin{minipage}{1\columnwidth}
+  \begin{center}\Large{\Mflatturb:}\\ 
+    \includegraphics[width=\columnwidth]{sbright.nu.DIIcomp.I0.g72a.Rad14.2400p.z0.NL.xKR.eb23.eI067.140.v6.eps}
+  \end{center}
+\end{minipage}
+\begin{minipage}{1\columnwidth}
+   \begin{center}\Large{\it Brunetti et al. (2012)}:\\
+     \includegraphics[width=\columnwidth]{sbright.nu.DIIcomp.Brunetti.g72a.Rad14.2400p.z0.NL.xKR.eb23.140.v6.eps}
+   \end{center}
+\end{minipage}
+\caption{Radio surface brightness profiles of Fermi-II reaccelerated
+  CR electrons of a simulated post-merging cluster similar to Coma. We
+  compare profiles at 352~MHz \citep[blue lines and
+    crosses,][]{brown11} to those at 1.4~GHz \citep[green lines and
+    crosses,][]{deiss97}. The red crosses show the reprocessed 1.4~GHz
+  data, where a zero level of about 10~\% of the central value is
+  adopted. The solid lines show predicted emission from a
+  reaccelerated fossil population, while dotted lines show emission
+  from a fossil population without reacceleration. The panels show the
+  emission of our models \Mprimary (upper left panel), \Mstream (upper
+  right panel), \Mflatturb (lower left panel), and simulated secondary
+  electrons together with previous estimates \citep{brunetti12} for
+  the Coma cluster (lower right panel).}
+  \label{fig:sync_profile}
+\end{figure*}
+
+In Fig.~\ref{fig:sync_profile}, we show radial profiles for the radio
+emission in all three scenarios in which the seeds undergo Fermi-II
+reacceleration in turbulent fields that are shaped such as to
+reproduce the Coma RH profile at 352~MHz.  Adopting our
+parametrisation for the volumetric injection rate of turbulent energy,
+$I_0\propto \eps_\rmn{th}^{\alpha_\rmn{tu}}$, we find
+$\alpha_\rmn{tu}= 0.67$ for \Mflatturb, $\alpha_\rmn{tu}= 0.82$ for
+\Mstream, and $\alpha_\rmn{tu}= 0.88$ for \Mprimary. As a result, the
+ratio of turbulent-to-thermal energy densities slightly increase with
+radius as shown in Fig.~\ref{fig:turb}.  After turbulent
+reacceleration, the volume-weighted, relative CRp energy density and
+relative CRp number density inside the RH for \Mflatturb (\Mstream),
+are found to be 2 (3) \% and $2\times10^{-8}$ ($5\times10^{-8}$),
+respectively.
+
+%the turbulent energy density becomes $\eps_\rmn{turb} \propto
+%\eps_\rmn{th}^{(\alpha_\rmn{tu}+1)/2}/T^{1/4}$, where $T$ is the
+%temperature of the gas,
+
+\begin{figure}
+  \includegraphics[width=1.0\columnwidth]{turb_profile_ratio_tot.eps}
+  \caption{The ratio of turbulent-to-thermal energy densities (solid
+    lines) and cumulative energies (dotted lines) in our three
+    models. The energy densities are parametrized as
+    $\eps_\rmn{turb} \propto
+    \eps_\rmn{th}^{(\alpha_{\rmn{tu}}+1)/2}/T^{1/4}$ and
+    normalized such that the total turbulent energy in compressible
+    modes $E_\rmn{turb}$ for each scenario makes up about 20\% of the
+    total thermal energy $E_\rmn{th}$ inside the radio halo
+    ($R_\rmn{RH}\approx0.6R_{200}$). The turbulent profiles explore
+    the uncertainty in the cluster turbulence and are motivated by the
+    cosmological simulation in
+    \citep{2009ApJ...705.1129L,2010ApJ...725.1452S,2011A&A...529A..17V}.}
+  \label{fig:turb}
+\end{figure}
+
+Figure~\ref{fig:sync_profile} demonstrates that the modeled radio
+profiles without turbulent reacceleration are too steep.  In the
+bottom right panel of Fig.~\ref{fig:sync_profile} (labeled with
+Brunetti et al. 2012), we show that our simulated profiles of
+reaccelerated CRs, which only take advective CR transport into
+account, i.e. they neglect CR streaming or a flatter turbulent
+profile, produce radio profiles that are too steep. Indeed, even using
+the assumptions of previous work -- where complete freedom in the seed
+population was allowed -- it is not possible to reproduce observations
+in both frequencies in any model.\footnote{Note that in previous work
+  on the Coma cluster, $\eps_\rmn{turb} \propto \eps_\rmn{th}$ was
+  adopted which approximately corresponds to $\alpha_\rmn{tu}= 1$
+  \citep{brunetti12} and together with the different distributions for
+  seed CRes constitute the main differences compared to our work.}
+Decreasing the acceleration efficiency with radius does not change
+this conclusion much because of the weak radial dependence of
+$D_\rmn{pp}(R)\propto \eps_\rmn{th}(R)^{\alpha_\rmn{tu}-1}
+\sqrt{T(R)}$. This signals that the problem is generic and requires
+either additional modifications to the plasma physics of acceleration
+or a better understanding of potential observational systematics. In
+addition there are differences in the simulated density and
+temperature profiles in comparison to the observed profile in Coma
+that impact the CR abundance as well as cooling and reacceleration.
+
+In Figure~\ref{fig:tauD} we show how the turbulent reacceleration
+timescales in our three models scale with radius. As expected, the
+\Mprimary model with $\alpha_\rmn{tu}=0.88$ has the flattest profile
+with $\tau_D\approx0.4\,\rmn{Gyr}$, where the small dip at large
+radius driven by the decrease in thermal energy density. The
+\Mflatturb model has the the flattest turbulent profile parameterized
+by the smaller $\alpha_\rmn{tu}$ which explains the steepest $\tau_D$
+profile. Note that a fixed reacceleration timescale is required to
+explain the observations at each radius and for each model (see also
+Table~\ref{tab:timescales}). This allows us to interchange the value
+of uncertain parameters $\tau_\rmn{cl} \sim X_\rmn{tu}^2 \sim k_0$,
+i.e. a longer reacceleration duration have to be compensated by
+lowering the level of turbulence or increasing the physical injection
+scale of turbulence to keep $\tau_D$ constant.
+
+\begin{figure}
+  \includegraphics[width=1.0\columnwidth]{tau_reacc.eps}
+  \caption{Turbulent reacceleration timescales for our simulated
+    cluster g72a. We show in linear-log the reacceleration timescale
+    ($\tau_D$) as a function of radius $R$ for our three models:
+    \Mprimary (green dotted line), \Mstream (blue dashed line), and
+    \Mflatturb (red solid line). Note that the timescales are derived
+    during the last 100~Myrs in time in our simulations.}
+  \label{fig:tauD}
+\end{figure}
+
+In principle, reacceleration via TTD leads to spectral steepening with
+particle energy due to the inefficiency of the acceleration process to
+counter the stronger cooling losses with increasing energy. Since
+synchrotron emission peaks at frequency $\nu_\rmn{syn}\simeq 1\,
+B/\umu\rmn{G} (\gamma/10^4)^2\,\rmn{GHz}$, this translates into a
+spectral steepening of the radio spectrum (see the left panel of
+Fig.~\ref{fig:sync_spectrum} where the continuous injection of
+secondary CRes is absent). A given radio window samples higher energy
+electrons for a decreasing field strength in the cluster
+outskirts. Hence, the spectral steepening with energy should translate
+into a radial spectral steepening \citep{brunetti12}. However, because
+of the weak dependence of the electron Lorentz factor on emission
+frequency ($\gamma\propto\sqrt{\nu_\rmn{syn}}$), this effect is only
+visible in our simulations for $\nu_\rmn{syn}\gtrsim5$~GHz. Most
+importantly, our simulated fluid elements at a given radius sample a
+broad distribution of shock history, density and temperature, which
+implies very similar synchrotron brightness profiles at
+$\nu_\rmn{syn}=352$~MHz and 1.4 GHz. The discrepancy of the observed
+and simulated 1.4 GHz profiles could instead be due to systematic flux
+calibration error in single dish observations. These could arise, for
+instance, due to errors in point source subtraction. Interestingly, we
+can match the 1.4 GHz data if we reduce the zero point by adding 10\%
+of the central flux to every data point; this flattens the outer
+profile\footnote{Lawrence Rudnick, private communication.}.
+Alternatively, this may point to weaknesses in the theoretical
+modeling of the particle acceleration process and may require a
+stronger cutoff in the particle energy spectrum.
+
+\subsection{Radio spectrum}
+\label{sect:radio_spec}
+In Fig.~\ref{fig:sync_spectrum} we show that our three models that
+include Fermi-II reacceleration can individually reproduce the
+convexly curved total radio spectrum found in the Coma cluster. Seed
+CRs in \Mstream and \Mflatturb that do not experience turbulent
+reacceleration have a power-law spectrum in disagreement with
+observations. In order to match both the spatial and spectral profiles
+in Coma, we adopt an acceleration efficiency for the strongest shocks
+in our three models \Mprimary, \Mstream, and \Mflatturb to
+$\zeta_{\rmn{e}} <0.003$, $\zeta_{\rmn{p}} < 0.1$, and
+$\zeta_{\rmn{p}}<0.03$, respectively. Following the Mach number
+($\mathcal{M}$)-dependence of the acceleration efficiency suggested in
+\cite{pinzke13}, the efficiency in weak shocks ($\mathcal{M}\sim
+2.5-3.5$) that dominates the CR distribution function, has an
+acceleration efficiency for protons $\zeta_{\rmn{p}}\sim0.0001-0.01$,
+and for electrons $\zeta_{\rmn{e}}\sim 0.001$.
+
+Interestingly, we find that the radio luminosity from clusters in the
+OFF-state (DSA only) and ON-state (DSA and reacceleration) differ by
+about a factor 10-20 in all our three models. This means that the
+secondary CRes are dominated by the reaccelerated fossil CRes and not
+from the CRes produced by reaccelerated CRps. However, for high
+frequencies ($\nu_\rmn{syn}\gtrsim$ GHz) where synchrotron cooling is
+more efficient than reacceleration, the emission is dominated by the
+CRes produced in the continuous injection of electrons from
+reaccelerated CRps. It is also worth mentioning that the radio
+emission from secondary CRes are smoothly distributed around the
+cluster because of the continuous injection, hence the it is not
+dominated by outliers.
+
+However, for \Mprimary, the primary CRes that generate most of the
+radio emission from the cluster in the OFF-state are dominated by only
+a small fraction of the CRes. These electrons are injected very
+recently and have not had time to cool yet. Hence we expect there to
+be a large variance in the OFF-state of different simulated
+clusters. As mentioned in section~\ref{sect:param_comp}, combining
+radio observations with gamma-ray limits allows us to put a lower
+limit to $X_\rmn{tu}$.  If $X_\rmn{tu}$ is smaller than in our adopted
+models (where we assume $X_\rmn{tu}=0.2$), then the efficiency of DSA
+has to be larger than $\zeta_\rmn{p}\sim 0.1$ for the secondary CRes
+to reproduce the radio observations. However, since the turbulent
+reacceleration acts on both the secondary CRes and the CRps, while
+$\zeta_\rmn{p}$ only affects the CRps, \Mstream and \Mflatturb would
+produce too much gamma-rays. Hence we conclude that
+$X_\rmn{tu}\gtrsim0.2$ if all other parameters are kept
+fixed. Although, we caution the reader to take this limit too
+stringent because of the uncertainty in $k_0$ and $\tau_\rmn{cl}$ that
+impact $X_\rmn{tu}$ for a fixed $\tau_\rmn{D}$. This parameter space
+needs to be explored further in future work in order to put more
+stringent limits on the level of turbulence in clusters using radio
+and gamma-ray observations in combination with turbulent reaccelerated
+CRs.
+
+\begin{figure*}
+  \includegraphics[width=1.0\columnwidth]{sync.spec.pri.g72a.140.v6.eps}
+  \includegraphics[width=1.0\columnwidth]{sync.spec.sec.g72a.140.v6.eps}
+  \caption{Radio synchrotron spectra. Lines are derived from
+    simulations, while the black crosses are compiled from
+    observations \citet{2010PhDT.......259P}. The solid lines show the
+    DSA and reaccelerated CRs (On-state of the radio halo), while the
+    dotted lines show CRs accelerated only by DSA (Off-state of the
+    radio halo). The left figure shows the radio emission induced by
+    primary CRes and the right figure shows the emission from
+    secondary CRes. The different line colors represent our different
+    models, \Mprimary (red line), \Mstream (blue line), and \Mflatturb
+    (green line).}
+  \label{fig:sync_spectrum}
+\end{figure*}
+
+\subsection{Gamma rays}
+The gamma-ray emission from CRps that produce decaying neutral pions
+could be substantial if the CRps are reaccelerated efficiently enough,
+hence it is interesting to estimate this emission for our models and
+compare to upper limits. We follow the formalism outlined in
+  \cite{1999APh....12..169B} (and references therein) and calculate
+  the gamma-ray emission numerically for our three models. We predict
+the gamma-ray emission from \Mflatturb (\Mstream) with
+$F_\gamma(>500\,\rmn{MeV})=4\times10^{-10} (5\times10^{-10}) \mathrm{
+  \,ph\, s}^{-1}\mathrm{cm}^{-2}$. The fluxes from these models are
+slightly larger than in \cite{brunetti12}, where the differences comes
+from our steeper CRp profiles in addition to simulation based
+formalism we rely on that accounts for both Coulomb and hadronic
+losses during the build up of the CR distribution in contrast to the
+scaling relations adopted in their paper. Interestingly the gamma-ray
+flux from both our scenarios are just below recent Fermi-LAT limits
+derived from a gamma-ray profile similar to \Mflatturb where
+$F_\gamma(>500\,\rmn{MeV})<5.3\times10^{-10} \mathrm{ \,ph\,
+  s}^{-1}\mathrm{cm}^{-2}$ \footnote{Fabio Zandanel, private
+  communication. See also
+  \citet{2014MNRAS.440..663Z,2014ApJ...787...18A}. and will be probed
+  in the next few years by Fermi-LAT. } The spectral index of the CRp
+distribution is relatively steep ($\alpha_{\rmn{p}}\sim2.6$) for the
+CRp energies $E \gtrsim 10$~GeV that are relevant for the injection of
+radio-emitting secondary CRes. The steep spectrum is ultimately a
+consequence of the shock history of the simulated cluster, with a weak
+dependence on our test particle model for Fermi-I acceleration
+\citep{pinzke13}, where we steepen the spectral index to avoid
+acceleration efficiencies above $\zeta_{\rmn{p}} \sim 10\%$.
+
 % --- section: Analytical Results and discussion --- %
@@
 Our fiducial model assumes $X_{\rm tu} = 0.2$, $\alpha_{\rm tu} =0.8$, $\alpha_{\rm CR, spat}=1.0$, and $k_{\rm 0}=2 \pi/\lambda_{\rm 0}$ where $\lambda_{\rm 0}=100$ kpc.
+We also assume a fixed acceleration time of $\tau_{\rm cl} = 650 \, {\rm Myr}$.
 
@@
 
-{\bf Impact of $X_{\rm tu}$.} Besides the overall increase in radio luminosity as $X_{\rm tu}$ increases, there are changes in spatial and spectral profiles.
+{\bf Impact of overall level of turbulence ($X_{\rm tu}$).} From the top panels of Fig.~\ref{fig:param_comp}, we see that as $X_{\rm tu}$ increases, there are 3 important changes: an exponential increase in radio luminosity, a flattening of the radio surface brightness profile, and an increase in spectral curvature.
+We discuss these in turn.
+
+The exponential increase in radio surface brightness is easily understood from equation~\ref{eq:Creacc}, since for a power-law initial distribution function $f_{\rm i}(p) = C_{\rm 0} p^{-\alpha}$, then $C_{\rm reacc} \propto C_{\rm 0} {\rm exp}(A \tau_{\rm cl}/\tau_{\rm D}) \propto {\rm exp} (B(r) X_{\rm tu}^{2})$.
+This exponential sensitivity is somewhat modified by cooling (which results in a non power-law spectrum; also, the shorter the acceleration time, the larger the pool of seed electrons available which would otherwise cool away), but overall is a good approximation.
+%For fixed $\tau_{\rm cl}$, it also implies a critical level of turbulence, below which reacceleration becomes negligible.
+
 An increase in $X_{\rm tu}$ flattens the surface brightness profile, since high acceleration efficiency leads to larger amplification in the cluster outskirts (where cooling is less important) than the center.
 In particular, in the cluster outskirts, the reduced impact of Coulomb cooling implies that there is a larger pool of low-energy electrons available for reacceleration (see timescales in Table \ref{tab:timescales}).
+
 Larger levels of turbulence also {\it increase} spectral curvature, which might seem puzzling.
@@
 
-We find that the
-level of turbulence ($X_\rmn{tu}$) has a large impact on both radio
-spectra and profiles, while the parameter $\alpha_\rmn{tu}$ that
-determines the spatial profile of turbulence mainly influences the
-radio profiles. As expected, the radio profiles flatten significantly
-with a flatter turbulent profile. A larger amount of turbulent energy
-also flattens the radio profile, because the steep profiles of
-injected CRs have less impact on the radio emission for an increasing
-reacceleration efficiency.
-
-\SPO{Stopped here}
-
-Interestingly, the spatial profile of CRs has a smaller impact on the
-radio emission. This can be understood by looking at the scaling of
-parameters to the reacceleration timescale, where $\tau_\rmn{D}
-\propto 1/D_\rmn{pp} \propto 1/X_\rmn{tu}^2$. From
-Equation~\ref{eq:Creacc} we see that the CRps with a spectral index of
-$\alpha_\rmn{p}\approx2.5$ approximately gain a factor $\delta
-C_\rmn{reacc.} \sim \exp{(1.7\,\tau_\rmn{cl}/\tau_\rmn{D})}$ during
-reacceleration if injection and cooling are neglected. The CRes gain a
-similar factor from reacceleration, however in the region around
-$0.1\,R_{200}$ the Coulomb cooling timescale
-($\tau_\rmn{Coul}\approx0.01\,\rmn{Gyr}$) is much shorter than
-$\tau_\rmn{D}\approx0.6\,\rmn{Gyr}$, hence $\delta C_\rmn{reacc.}$
-will be greatly reduced for the electrons. The spatial region is
-important when we derive the radio spectrum, since in order to compare
-to observations we integrate the CR profile out to $\sim
-0.2\,R_{200}$. For $X_\rmn{tu}=0.2$ and $\alpha_\rmn{tu}=0.8$ we find
-that $\delta C_\rmn{reacc.} \sim 10$. This is confirmed by the top
-panels in Fig.~\ref{fig:param_comp}. Increasing the level of
-turbulence to $X_\rmn{tu}=0.3$, gives us a $\delta C_\rmn{reacc.}
-\sim 100$, which is roughly confirmed by same figures. The factor 2-3
-difference in the figure is due to the shorter reacceleration
-timescale that increase the contribution from reaccelerated CRes that
-would otherwise cool away on a much shorter timescale. Hence we
-conclude that the radio emission is much more sensitive to the level
-of compressible turbulence through an exponential dependence.  In
-contrast, the radio emission only depends linearly on the density of
-injected CRs.
-
-We can also derive a critical level of turbulence below which
-reacceleration is negligible. Above this threshold, reacceleration
-becomes increasingly more efficient. We define the threshold by
-$\delta C_\rmn{reacc.}  \lesssim 2$, which gives us an
-$X_\rmn{thres,tu} = \sqrt{0.04\,\log(2)/1.7 \times
-  \tau_\rmn{D}/\tau_\rmn{cl}} \approx 0.08$ for $\tau_\rmn{D} =
-0.6\,\rmn{Gyr}$. The existence of such a threshold can also manifested
-in the top panels of Fig.~\ref{fig:param_comp}. For
+{\bf Impact of spatial profile of turbulence ($\alpha_{\rm tu}$)} From the middle panels of Fig.~\ref{fig:param_comp}, we see that as expected, a flatter turbulence profile directly translates into a flatter radio surface brightness profile.
+Since seed electrons are more concentrated toward the center (the collisional production of secondaries is more rapid there), and B-fields are higher, concentrating the turbulence toward the cluster center for fixed $X_{\rm tu}$ results in higher radio luminosities, and slightly more curvature (due to the increased importance of cooling near the center).
+Overall, however, the spatial profile of turbulence has a much weaker effect than its overall normalization.
+
+{\bf Impact of spatial profile of seed CRs $\alpha_{\rm CR, spat}$} The spatial distribution of CRs has an even smaller impact on radio emission.
+At fixed total CR energy content $X_{\rm CR}$, concentrating the CRs towards the center leads to more centrally dominated surface brightness profiles, as expected, and higher radio luminosities (for the same reasons as above: secondaries are more easily produced in the center, and B-fields are higher).
+We have also confirmed that radio surface brightness profiles scale linearly with $X_{\rm CR}$, as expected.
+
+Overall, our results suggest that radio halos are much more sensitive to the level of turbulence (exponential dependence) rather than CR abundance (linear dependence), and that the spatial distribution of turbulence and CRs, while important, are second-order effects.
+In our parametrization, the most important controlling variable is $X_{\rm tu}$.
+The overall level of turbulence has to be such that $\tau_{\rm D} \sim \tau_{\rm cl}$ (see Table \ref{tab:timescales}), otherwise, too little or too much amplification takes place.
+For instance, for
 $X_\rmn{tu}\gtrsim0.08$, changing $X_\rmn{tu}$ by a factor of two
-changes the radio surface brightness by a factor of $\sim 10-100$. In
-principle this threshold behavior allows us to provide a strict lower
-bound on turbulence in radio halos. An even more stringent bound on
-$X_\rmn{tu}$ can be obtained by combining radio observations with
-the gamma-ray observations (see Section~\ref{sect:radio_spec}).
+changes the radio surface brightness by a factor of $\sim 10-100$ (see top panels of Fig.~\ref{fig:param_comp}).
+The required $\tau_{\rm D}/\tau_{\rm cl}$ depends only logarithmically on the abundance of seed CRs.
+While the requirement of a threshold level of turbulence may explain why radio brightness is bimodal, it also raises a fine-tuning problem: why is the $L_{\rm radio}$ vs.
+$L_{\rm X}$ relation in active radio halos so tight?
+Depending on the details of infall or mergers, we would naturally expect fluctuations in $X_{\rm tu}$, which would translate into large scatter in the $L_{\rm radio}--L_{\rm X}$ relation.
+This can only make sense if the timescale over which acceleration takes place $\tau_{\rm cl}$ also depends on the properties of turbulence, so that the the ratio $\tau_{\rm D}/\tau_{\rm cl}$ has relatively little scatter.
+We discuss one such scenario in \S\ref{sec:reacc}, but this point clearly deserves more work.
 
@@
   compiled from observations \citep{2010PhDT.......259P}, while the
-  black lines show predicted emission from reaccelerated CR
-  electrons. The upper panels show the sensitivity to the level of
+  black lines show predicted spectra. The upper panels show the sensitivity to the level of
   turbulence ($X_\rmn{tu}$), the middle panels show the impact of
@@
   parameter separately in each row of panels. We find that the radio
-  emission is much more sensitive to the level of turbulence while it
-  depends less senstively to the spatial distribution of CRs.}
+  emission is most sensitive to the level of turbulence. The abundance of CR seeds, and the spatial distribution of CRs and turbulence play second-order effects.}
   \label{fig:param_comp}
 \end{figure*}
-
-% --- section: Simulation Results and discussion --- %
-\section{Cosmological simulations}
-\label{sec:results}
-
-In this setion, we solve the Fokker-Planck equation for CR transport
-on Lagrangian particle trajectories through cosmic history.  We
-concentrate on three scenarios. (i) In model {\em M-primaries}, we
-assume that CR electrons, which have been accelerated by cosmic
-formation shocks and successively cooled by inverse Compton and
-synchrotron losses, form a fossil seed population for
-reacceleration. (ii) In model {\em M-streaming}, we account for the
-outward streaming of central CRps, which produces a flat CR
-distribution in the ICM and equivalently a flat secondary seed
-population of CRe for reacceleration. (iii) In model {\em
-  M-turbulence} we adopt a spatially flatter turbulent profile than
-what was adopted before but assume that seed CRps and secondary CRes
-follow the steep profile that is suggested by structure formation
-simulations.
-
-The level of emission is mainly driven by how efficient the CRs are
-reaccelerated and for how long. Hence, we exploit the exponential
-sensitivity of reacceleration on the level of turbulence and adopt
-different radial profiles of the turbulent energy density. We ask the
-question how differently the turbulent profiles need to be shaped in
-order to reproduce the observed radial profiles of the radio
-emission. For these models, we then compute radio spectra and
-gamma-ray luminosities and compare to observational data.
-
-\subsection{Modelling diffusive shock acceleration}
-\label{sec:cosmo_sim}
-In this paper we focus on our simulated cluster, g72a, which is a
-massive cluster of mass $M_{200}=1.6\times10^{15}\,M_\odot$ that
-experienced a merger about 1 Gyr ago
-\citep{2009MNRAS.399..497D}. Since the cluster mass, density and
-temperature profiles are all similar to the well studied Coma cluster
-\citep{2007MNRAS.378..385P,pinzke10}, we will compare our calculations
-to radio and gamma-ray observations of Coma.
-
-We use a simple test-particle model for the CR acceleration and
-injection, where each shock injects CRs that trace a power-law in
-momentum,
-\begin{equation}
-  f_\p(p,t) = C(t)\,p^{\alpha_\rmn{inj}}\,,\quad
-  \alpha_\rmn{inj}=\frac{(\gamma_\rmn{ad}+1)\mathcal{M}^2}
-        {(\gamma_\rmn{ad}-1)\mathcal{M}^2+2}
-\end{equation}
-determined by the normalization $C(t)$ and the spectral index
-$\alpha_{\rmn{inj}}$ that depends on the adiabatic index
-$\gamma_\rmn{ad} = 5/3$ and the Mach number of the shock
-$\mathcal{M}$. It is given by the ratio of the upstream velocity
-($\varv_2$) and the sound speed ($c_{\rm s}$). The CR number density and CR
-energy density are derived from
-\begin{eqnarray}
-n_\rmn{p} &=&
-\int_{p_\rmn{inj}}^\infty \dd p\, f_\p(p)\\
-\eps_\rmn{p} &=&
-\int_{p_\rmn{inj}}^\infty \dd p\, f_\p(p) \,E(p),
-\end{eqnarray}
-where $E(p) = (\sqrt{1+p^2} -1)\, m\,c^2$ is the kinetic energy of a
-particle with momentum $p$. We adopt a fit to Monte Carlo simulations
-of the thermal leakage process that relates the momentum of injected
-protons ($p_\rmn{inj}$) to the thermal energy ($p_\rmn{th}$) of the
-shocked plasma \citep{kang11}:
-\begin{eqnarray}
-  \label{eq:qinj}
-  p_\rmn{inj} &=& x_\rmn{inj} p_\rmn{th} = x_\rmn{inj} \sqrt{\frac{2 \,\kB T_2}{m c^2}}\,, \nonumber \\
-  \rmn{where}\quad x_\rmn{inj} &\approx& 1.17 \frac{\varv_2}{p_{\rmn{th}}\,c} \left(1+
-  \frac{1.07}{\epsilon_B}\right) \left(\frac{\mathcal{M}}{3}\right)^{0.1}\,.
-\end{eqnarray}
-Here $\eb = B_0/B_{\perp}$, $B_0$ is the amplitude of the downstream
-MHD wave turbulence, and $B_{\perp}$ is the magnetic field along the
-shock normal. The physical range of $\eb$ is quite uncertain due to
-complex plasma interactions. In this paper, we adopt $\eb = 0.23$,
-which -- as we will later see -- corresponds to a conservative maximum
-energy acceleration efficiency for protons of $10\%$. To derive the
-acceleration efficiency, $\zeta_\rmn{inj}$, we first have to infer the
-particle injection efficiency, which is the fraction of downstream
-thermal gas particles which experience diffusive shock acceleration
-\citep[for details see][]{pinzke13},
-\begin{equation}
-  \label{eq:eta}
-  \eta_\rmn{p,lin} =
-  \frac{4}{\sqrt{\upi}}\,\frac{x_\rmn{inj}^3}{\alpha_\rmn{inj}-1}\,
-  \rmn{e}^{-x_\rmn{inj}^2}.
-\end{equation}
-The particle injection efficiency is a strong function of
-$x_\rmn{inj}$ that depends on both $\mathcal{M}$ and $\eb$. The
-energy density of CRs that are injected and accelerated at the shock
-(neglecting the CR back reaction on the shock) is given by
-\begin{equation}
-\label{eq:CR_energy} 
-  \Delta\eps_\rmn{p,lin} =
-  \eta_\rmn{p,lin}(\mathcal{M})\,n_\rmn{th}(T_2)
-  \,\frac{\eps_\p}{n_\p}
-\end{equation}
-and the CR energy injection and acceleration efficiency is:
-\begin{equation}
-  \zeta_\rmn{lin} =
-  \frac{\Delta\eps_\rmn{p,lin}}{\Delta\eps_\rmn{diss}},
-   \quad\mbox{where}\quad
-  \Delta\eps_\rmn{diss} = \eps_\rmn{th2} - \eps_\rmn{th0}\,\left(\frac{\rho_2}{\rho_0}\right)^{\gamma_\rmn{ad}}\,.
-\label{eqn:energy_frac}  
-\end{equation}
-The dissipated energy density in the downstream regime,
-$\Delta\eps_\rmn{diss}$, is given by the difference of the thermal
-energy densities in the pre- and post-shock regimes, corrected for the
-adiabatic energy increase due to gas compression.
-
-We limit the acceleration efficiency to $\zeta_\rmn{max}$ by
-steepening the spectral index of the injected population
-$\alpha_\rmn{inj}$ to $\alpha_\rmn{sub}$ so that $\zeta_\rmn{lin}
-\leq \zeta_\rmn{max}$ is always fulfilled. The slope
-$\alpha_\rmn{inj}$ impact $\zeta_\rmn{inj}$ via the mean energy per
-particle, $\eps_\rmn{p}/n_\rmn{p}$. This
-procedure conserves energy and is motivated by models of non-linear
-shock acceleration where a sub-shock with a lower compression ratio
-(and hence steeper spectral index) forms
-\citep[e.g.,][]{2000ApJ...540..292E}. Given our assumed $\eb=0.23$, we
-find that for strong shocks where $\alpha \lesssim 2.3$ the spectral
-slope is steepened by a maximum of $\sim 10$ per cent in low
-temperature regimes ($\kB T\sim 0.1$~keV), while the steepening is much
-smaller for high temperature regimes ($\kB T\sim 10$~keV) that are more
-relevant for clusters. Since $p_\rmn{inj}$ remains fixed, so does the
-CR number density $n_\rmn{p}$. Hence we can solve for the
-renormalized normalization constant $C_\rmn{sub}$ using $n_\rmn{p}$
-and Eqn.~\ref{eq:eta}:
-\begin{equation}
-  \label{eq:Cp_sub}
-  C_\rmn{sub}=\eta_\rmn{p,lin}\,(\alpha_\rmn{sub}-1)\,p_\rmn{inj}^{\alpha_\rmn{sub}-1}\,,
-\end{equation}
-where the new distribution function is given by $f_\p(p,t)= C_\rmn{sub}
-p^{-\alpha_\rmn{sub}}$. We set an upper limit on the ratio of
-accelerated proton-to-dissipated energy in the downstream of strong
-shocks that varies from $\zeta_\rmn{max} \sim 1-10\%$, depending on
-the adopted model (for more details, see Section \ref{sec:results}).
-
-In our Galaxy, the CRe-to-CRp ratio at a few GeV is $K_{\rmn{ep}} \sim
-10^{-2}$. Hence, we adopt this as a fiducial value for the CRe-to-CRp
-acceleration efficiency \citep[see][for more
-  discussion]{pinzke13}. However, as recent PIC simulations have
-shown, this is likely very different at weak shocks, with electrons
-efficiently accelerated at perpendicular shocks
-\citep{2014ApJ...794..153G,2014ApJ...797...47G}, and ions efficiently
-accelerated at parallel shocks \citep{2014ApJ...783...91C}. Thus,
-depending on magnetic geometry, $K_{\rmn{ep}}$ could be either larger
-or smaller. Some observations of radio relics suggest high values of
-$K_{\rmn{ep}}$, due to the absence of gamma-ray emission, which probes
-the CRp population \citep{2014MNRAS.437.2291V}. This suggests primary
-CRes as a viable alternative scenario to secondary CRes as seeds for
-the giant RHs. In our {\em M-primaries} scenario, the injected
-distribution of CRes is derived in the same way as for the CRps. Once
-they have been accelerated to relativistic energies, injected
-electrons and protons are indistinguishable. We therefore assume that
-CRp and CRe have the same distribution function $f_\rmn{e}(p) =
-K_\rmn{ep} f_\rmn{p}(p)$, with a different normalization (due to
-differing acceleration efficiencies) $K_\rmn{ep}=0.1$ \citep[which is
-  viable for primarily perpendicular
-  shocks,][]{2014ApJ...794..153G}. While this appears to contradict the
-radial bias of magnetic fields in the bulk of the ICM as suggested by
-observations \citep{2010NatPh...6..520P} and cluster simulations
-\citep{2011ApJ...740...81R}, it does not necessarily apply to the
-accretion shock regions, which show a field geometry with a net
-perpendicular bias with respect to the shock normal---at least for
-giant radio relics \citep{2010Sci...330..347V}.
-
-\subsection{Radio emission profile}
-
-\begin{figure*}
-\begin{minipage}{1\columnwidth}
-   \begin{center}\Large{\Mprimary:}\\
-     \includegraphics[width=\columnwidth]{sbright.nu.DIIcomp.Pri.g72a.Rad14.2400p.z0.NL.xKR.eb23.eI088.140.v6.eps}
-   \end{center}
-\end{minipage}
-\begin{minipage}{1\columnwidth}
-   \begin{center}\Large{\Mstream:}\\
-     \includegraphics[width=\columnwidth]{sbright.nu.DIIcomp.flatCR.g72a.Rad14.2400p.z0.NL.xKR.eb23.eI082.flatCR.140.v6.eps}
-   \end{center}
-\end{minipage}
-\\
-\begin{minipage}{1\columnwidth}
-  \begin{center}\Large{\Mflatturb:}\\ 
-    \includegraphics[width=\columnwidth]{sbright.nu.DIIcomp.I0.g72a.Rad14.2400p.z0.NL.xKR.eb23.eI067.140.v6.eps}
-  \end{center}
-\end{minipage}
-\begin{minipage}{1\columnwidth}
-   \begin{center}\Large{\it Brunetti et al. (2012)}:\\
-     \includegraphics[width=\columnwidth]{sbright.nu.DIIcomp.Brunetti.g72a.Rad14.2400p.z0.NL.xKR.eb23.140.v6.eps}
-   \end{center}
-\end{minipage}
-\caption{Radio surface brightness profiles of Fermi-II reaccelerated
-  CR electrons of a simulated post-merging cluster similar to Coma. We
-  compare profiles at 352~MHz \citep[blue lines and
-    crosses,][]{brown11} to those at 1.4~GHz \citep[green lines and
-    crosses,][]{deiss97}. The red crosses show the reprocessed 1.4~GHz
-  data, where a zero level of about 10~\% of the central value is
-  adopted. The solid lines show predicted emission from a
-  reaccelerated fossil population, while dotted lines show emission
-  from a fossil population without reacceleration. The panels show the
-  emission of our models \Mprimary (upper left panel), \Mstream (upper
-  right panel), \Mflatturb (lower left panel), and simulated secondary
-  electrons together with previous estimates \citep{brunetti12} for
-  the Coma cluster (lower right panel).}
-  \label{fig:sync_profile}
-\end{figure*}
-
-In Fig.~\ref{fig:sync_profile}, we show radial profiles for the radio
-emission in all three scenarios in which the seeds undergo Fermi-II
-reacceleration in turbulent fields that are shaped such as to
-reproduce the Coma RH profile at 352~MHz.  Adopting our
-parametrisation for the volumetric injection rate of turbulent energy,
-$I_0\propto \eps_\rmn{th}^{\alpha_\rmn{tu}}$, we find
-$\alpha_\rmn{tu}= 0.67$ for \Mflatturb, $\alpha_\rmn{tu}= 0.82$ for
-\Mstream, and $\alpha_\rmn{tu}= 0.88$ for \Mprimary. As a result, the
-ratio of turbulent-to-thermal energy densities slightly increase with
-radius as shown in Fig.~\ref{fig:turb}.  After turbulent
-reacceleration, the volume-weighted, relative CRp energy density and
-relative CRp number density inside the RH for \Mflatturb (\Mstream),
-are found to be 2 (3) \% and $2\times10^{-8}$ ($5\times10^{-8}$),
-respectively.
-
-%the turbulent energy density becomes $\eps_\rmn{turb} \propto
-%\eps_\rmn{th}^{(\alpha_\rmn{tu}+1)/2}/T^{1/4}$, where $T$ is the
-%temperature of the gas,
-
-\begin{figure}
-  \includegraphics[width=1.0\columnwidth]{turb_profile_ratio_tot.eps}
-  \caption{The ratio of turbulent-to-thermal energy densities (solid
-    lines) and cumulative energies (dotted lines) in our three
-    models. The energy densities are parametrized as
-    $\eps_\rmn{turb} \propto
-    \eps_\rmn{th}^{(\alpha_{\rmn{tu}}+1)/2}/T^{1/4}$ and
-    normalized such that the total turbulent energy in compressible
-    modes $E_\rmn{turb}$ for each scenario makes up about 20\% of the
-    total thermal energy $E_\rmn{th}$ inside the radio halo
-    ($R_\rmn{RH}\approx0.6R_{200}$). The turbulent profiles explore
-    the uncertainty in the cluster turbulence and are motivated by the
-    cosmological simulation in
-    \citep{2009ApJ...705.1129L,2010ApJ...725.1452S,2011A&A...529A..17V}.}
-  \label{fig:turb}
-\end{figure}
-
-Figure~\ref{fig:sync_profile} demonstrates that the modeled radio
-profiles without turbulent reacceleration are too steep.  In the
-bottom right panel of Fig.~\ref{fig:sync_profile} (labeled with
-Brunetti et al. 2012), we show that our simulated profiles of
-reaccelerated CRs, which only take advective CR transport into
-account, i.e. they neglect CR streaming or a flatter turbulent
-profile, produce radio profiles that are too steep. Indeed, even using
-the assumptions of previous work -- where complete freedom in the seed
-population was allowed -- it is not possible to reproduce observations
-in both frequencies in any model.\footnote{Note that in previous work
-  on the Coma cluster, $\eps_\rmn{turb} \propto \eps_\rmn{th}$ was
-  adopted which approximately corresponds to $\alpha_\rmn{tu}= 1$
-  \citep{brunetti12} and together with the different distributions for
-  seed CRes constitute the main differences compared to our work.}
-Decreasing the acceleration efficiency with radius does not change
-this conclusion much because of the weak radial dependence of
-$D_\rmn{pp}(R)\propto \eps_\rmn{th}(R)^{\alpha_\rmn{tu}-1}
-\sqrt{T(R)}$. This signals that the problem is generic and requires
-either additional modifications to the plasma physics of acceleration
-or a better understanding of potential observational systematics. In
-addition there are differences in the simulated density and
-temperature profiles in comparison to the observed profile in Coma
-that impact the CR abundance as well as cooling and reacceleration.
-
-In Figure~\ref{fig:tauD} we show how the turbulent reacceleration
-timescales in our three models scale with radius. As expected, the
-\Mprimary model with $\alpha_\rmn{tu}=0.88$ has the flattest profile
-with $\tau_D\approx0.4\,\rmn{Gyr}$, where the small dip at large
-radius driven by the decrease in thermal energy density. The
-\Mflatturb model has the the flattest turbulent profile parameterized
-by the smaller $\alpha_\rmn{tu}$ which explains the steepest $\tau_D$
-profile. Note that a fixed reacceleration timescale is required to
-explain the observations at each radius and for each model (see also
-Table~\ref{tab:timescales}). This allows us to interchange the value
-of uncertain parameters $\tau_\rmn{cl} \sim X_\rmn{tu}^2 \sim k_0$,
-i.e. a longer reacceleration duration have to be compensated by
-lowering the level of turbulence or increasing the physical injection
-scale of turbulence to keep $\tau_D$ constant.
-
-\begin{figure}
-  \includegraphics[width=1.0\columnwidth]{tau_reacc.eps}
-  \caption{Turbulent reacceleration timescales for our simulated
-    cluster g72a. We show in linear-log the reacceleration timescale
-    ($\tau_D$) as a function of radius $R$ for our three models:
-    \Mprimary (green dotted line), \Mstream (blue dashed line), and
-    \Mflatturb (red solid line). Note that the timescales are derived
-    during the last 100~Myrs in time in our simulations.}
-  \label{fig:tauD}
-\end{figure}
-
-In principle, reacceleration via TTD leads to spectral steepening with
-particle energy due to the inefficiency of the acceleration process to
-counter the stronger cooling losses with increasing energy. Since
-synchrotron emission peaks at frequency $\nu_\rmn{syn}\simeq 1\,
-B/\umu\rmn{G} (\gamma/10^4)^2\,\rmn{GHz}$, this translates into a
-spectral steepening of the radio spectrum (see the left panel of
-Fig.~\ref{fig:sync_spectrum} where the continuous injection of
-secondary CRes is absent). A given radio window samples higher energy
-electrons for a decreasing field strength in the cluster
-outskirts. Hence, the spectral steepening with energy should translate
-into a radial spectral steepening \citep{brunetti12}. However, because
-of the weak dependence of the electron Lorentz factor on emission
-frequency ($\gamma\propto\sqrt{\nu_\rmn{syn}}$), this effect is only
-visible in our simulations for $\nu_\rmn{syn}\gtrsim5$~GHz. Most
-importantly, our simulated fluid elements at a given radius sample a
-broad distribution of shock history, density and temperature, which
-implies very similar synchrotron brightness profiles at
-$\nu_\rmn{syn}=352$~MHz and 1.4 GHz. The discrepancy of the observed
-and simulated 1.4 GHz profiles could instead be due to systematic flux
-calibration error in single dish observations. These could arise, for
-instance, due to errors in point source subtraction. Interestingly, we
-can match the 1.4 GHz data if we reduce the zero point by adding 10\%
-of the central flux to every data point; this flattens the outer
-profile\footnote{Lawrence Rudnick, private communication.}.
-Alternatively, this may point to weaknesses in the theoretical
-modeling of the particle acceleration process and may require a
-stronger cutoff in the particle energy spectrum.
-
-\subsection{Radio spectrum}
-\label{sect:radio_spec}
-In Fig.~\ref{fig:sync_spectrum} we show that our three models that
-include Fermi-II reacceleration can individually reproduce the
-convexly curved total radio spectrum found in the Coma cluster. Seed
-CRs in \Mstream and \Mflatturb that do not experience turbulent
-reacceleration have a power-law spectrum in disagreement with
-observations. In order to match both the spatial and spectral profiles
-in Coma, we adopt an acceleration efficiency for the strongest shocks
-in our three models \Mprimary, \Mstream, and \Mflatturb to
-$\zeta_{\rmn{e}} <0.003$, $\zeta_{\rmn{p}} < 0.1$, and
-$\zeta_{\rmn{p}}<0.03$, respectively. Following the Mach number
-($\mathcal{M}$)-dependence of the acceleration efficiency suggested in
-\cite{pinzke13}, the efficiency in weak shocks ($\mathcal{M}\sim
-2.5-3.5$) that dominates the CR distribution function, has an
-acceleration efficiency for protons $\zeta_{\rmn{p}}\sim0.0001-0.01$,
-and for electrons $\zeta_{\rmn{e}}\sim 0.001$.
-
-Interestingly, we find that the radio luminosity from clusters in the
-OFF-state (DSA only) and ON-state (DSA and reacceleration) differ by
-about a factor 10-20 in all our three models. This means that the
-secondary CRes are dominated by the reaccelerated fossil CRes and not
-from the CRes produced by reaccelerated CRps. However, for high
-frequencies ($\nu_\rmn{syn}\gtrsim$ GHz) where synchrotron cooling is
-more efficient than reacceleration, the emission is dominated by the
-CRes produced in the continuous injection of electrons from
-reaccelerated CRps. It is also worth mentioning that the radio
-emission from secondary CRes are smoothly distributed around the
-cluster because of the continuous injection, hence the it is not
-dominated by outliers.
-
-However, for \Mprimary, the primary CRes that generate most of the
-radio emission from the cluster in the OFF-state are dominated by only
-a small fraction of the CRes. These electrons are injected very
-recently and have not had time to cool yet. Hence we expect there to
-be a large variance in the OFF-state of different simulated
-clusters. As mentioned in section~\ref{sect:param_comp}, combining
-radio observations with gamma-ray limits allows us to put a lower
-limit to $X_\rmn{tu}$.  If $X_\rmn{tu}$ is smaller than in our adopted
-models (where we assume $X_\rmn{tu}=0.2$), then the efficiency of DSA
-has to be larger than $\zeta_\rmn{p}\sim 0.1$ for the secondary CRes
-to reproduce the radio observations. However, since the turbulent
-reacceleration acts on both the secondary CRes and the CRps, while
-$\zeta_\rmn{p}$ only affects the CRps, \Mstream and \Mflatturb would
-produce too much gamma-rays. Hence we conclude that
-$X_\rmn{tu}\gtrsim0.2$ if all other parameters are kept
-fixed. Although, we caution the reader to take this limit too
-stringent because of the uncertainty in $k_0$ and $\tau_\rmn{cl}$ that
-impact $X_\rmn{tu}$ for a fixed $\tau_\rmn{D}$. This parameter space
-needs to be explored further in future work in order to put more
-stringent limits on the level of turbulence in clusters using radio
-and gamma-ray observations in combination with turbulent reaccelerated
-CRs.
-
-\begin{figure*}
-  \includegraphics[width=1.0\columnwidth]{sync.spec.pri.g72a.140.v6.eps}
-  \includegraphics[width=1.0\columnwidth]{sync.spec.sec.g72a.140.v6.eps}
-  \caption{Radio synchrotron spectra. Lines are derived from
-    simulations, while the black crosses are compiled from
-    observations \citet{2010PhDT.......259P}. The solid lines show the
-    DSA and reaccelerated CRs (On-state of the radio halo), while the
-    dotted lines show CRs accelerated only by DSA (Off-state of the
-    radio halo). The left figure shows the radio emission induced by
-    primary CRes and the right figure shows the emission from
-    secondary CRes. The different line colors represent our different
-    models, \Mprimary (red line), \Mstream (blue line), and \Mflatturb
-    (green line).}
-  \label{fig:sync_spectrum}
-\end{figure*}
-
-\subsection{Gamma rays}
-The gamma-ray emission from CRps that produce decaying neutral pions
-could be substantial if the CRps are reaccelerated efficiently enough,
-hence it is interesting to estimate this emission for our models and
-compare to upper limits. We follow the formalism outlined in
-  \cite{1999APh....12..169B} (and references therein) and calculate
-  the gamma-ray emission numerically for our three models. We predict
-the gamma-ray emission from \Mflatturb (\Mstream) with
-$F_\gamma(>500\,\rmn{MeV})=4\times10^{-10} (5\times10^{-10}) \mathrm{
-  \,ph\, s}^{-1}\mathrm{cm}^{-2}$. The fluxes from these models are
-slightly larger than in \cite{brunetti12}, where the differences comes
-from our steeper CRp profiles in addition to simulation based
-formalism we rely on that accounts for both Coulomb and hadronic
-losses during the build up of the CR distribution in contrast to the
-scaling relations adopted in their paper. Interestingly the gamma-ray
-flux from both our scenarios are just below recent Fermi-LAT limits
-derived from a gamma-ray profile similar to \Mflatturb where
-$F_\gamma(>500\,\rmn{MeV})<5.3\times10^{-10} \mathrm{ \,ph\,
-  s}^{-1}\mathrm{cm}^{-2}$ \footnote{Fabio Zandanel, private
-  communication. See also
-  \citet{2014MNRAS.440..663Z,2014ApJ...787...18A}. and will be probed
-  in the next few years by Fermi-LAT. } The spectral index of the CRp
-distribution is relatively steep ($\alpha_{\rmn{p}}\sim2.6$) for the
-CRp energies $E \gtrsim 10$~GeV that are relevant for the injection of
-radio-emitting secondary CRes. The steep spectrum is ultimately a
-consequence of the shock history of the simulated cluster, with a weak
-dependence on our test particle model for Fermi-I acceleration
-\citep{pinzke13}, where we steepen the spectral index to avoid
-acceleration efficiencies above $\zeta_{\rmn{p}} \sim 10\%$.
 
@@
 
-The standard reacceleration model for radio halos (RHs) requires a
-population of seed electrons to undergo turbulent
-reacceleration. These seeds are generally thought to be secondary
-electrons from hadronic cosmic ray proton (CRp) interactions. In this
-work we use cosmological simulations to derive a population of seed CR
-protons originating from structure formation shocks and merger shocks
-during the cluster build up. The resulting secondary population is
-inconsistent with RH observations. We propose three possible solutions
-where all reaccelerated CRs produce gamma-ray emission below current
-upper limits. Additionally, they reproduce both the spectrum and the
-surface brightness profiles of the Coma radio halo:
-
-\begin{enumerate}
-\item {\bf Model {\em M-primaries}.} If indeed the acceleration
-  efficiency of CRps is below about $0.1$ {\%} in weak shocks and the
-  ratio of injected electrons and protons is $K_{\rmn{ep}} \sim
-  10^{-1}$, CR electrons accelerated directly in shocks dominate over
-  secondaries.
-\item {\bf Model {\em M-streaming}.} Alternatively, CRps could stream
-  out of the central core and produce flat CR profiles. This seed
-  population of secondary CRes also has the correct spatial and
-  spectral features alone, or potentially complements primaries to
-  explain radio observations.
-\item {\bf Model {\em M-turbulence}.}  Finally, injected turbulence
-  that is flatter than in previously adopted models, which allows seed
-  CRps to follow the steep radial profile that is suggested by
-  structure formation simulations.
-\end{enumerate}
-
-Combining radio observations with gamma-ray constraints can be very
-useful to learn about the plasma of the intracluster medium. Our
-models (ii) and (iii) relies on CRps to induce secondary CRes that
-produce the observed radio emission. In addition proton-proton
-collisions produce neutral pions that decay into gamma rays. Since
-turbulent reacceleration acts on both CRes and CRps, while the DSA
-acceleration efficiency ($\zeta_p$) only acts on the CRps, radio
-observations fix the relation between $X_\rmn{tu}$ (the ratio of the
-total turbulent energy in compressional modes to the total thermal
-energy) and the acceleration efficiency. With the addition of
-gamma-ray constraints from Fermi-LAT, we can derive a lower limit to
-$X_\rmn{tu}\gtrsim0.2$ and a upper limit to the acceleration
-efficiencies of $\zeta_p\lesssim 10\%$ ($\zeta_p\lesssim 3\%$) for
-the two models, respectively, for our current choices of other
-parameters.
-
-How could we distinguish the different possibilities of a dominating
-primary or secondary seed population of electrons observationally?
-One possibility that is relative insensitive to adopted parameters in
-our models is to use high-frequency radio observations (with e.g., the
-Jansky Very Large Array) where turbulent reacceleration of CRes (which
-has a high energy cutoff) is no longer efficient since their fast
-radiative cooling time drops below the comparably slow reacceleration
-timescale producing a sharp spectral cutoff. This is unlike
-reacceleration of CRps that do not suffer radiative cooling losses and
-inject power-law momentum distributions of secondary CRe (see
-Fig.~\ref{fig:sync_spectrum}).
-
-However, the negative flux bowl of the Sunyaev-Zel'dovich effect
-introduces a cutoff of the RH spectrum at frequencies above $\gtrsim
-10$~GHz \citep[][ depending on cluster mass and
-  redshift]{2002A&A...396L..17E,Pfrommer:2003mk}. Hence the
-subdominant radio emission from freshly injected secondary CRes may
-only be detectable in steep spectrum radio sources
-\citep{2008Natur.455..944B}, which exhibit a cutoff at lower radio
-frequencies and are thought to represent dying RHs as a result of the
-decaying turbulence after a merger. Alternatively, one could attempt
-to reconstruct the intrinsic high-frequency RH spectrum by filling in
-the missing flux due to the Sunyaev-Zel'dovich effect by precise
-measurements of the Compton-$y$ parameter at microwave
-frequencies. Another possibility would consist in stacking the radio
-data of radio-quiet clusters that do not exhibit RH emission
-individually \citep{2011ApJ...740L..28B}. This may reveal the
-glow of radio emission due to steady state secondary
-population. Emission from faint secondary electrons should still be
-visible, whereas due to the much more intermittent nature of DSA
-injection, primary CRe will instead show a sharp cutoff due to
-cooling, and will not be visible at high energies (see
-Fig.~\ref{fig:sync_spectrum}).
-
-As MHD simulations of clusters that follow spectral CR distributions
-become feasible, these will provide valuable insight about the profile
-and the total energy of turbulence in clusters and the possibility of
-turbulent reacceleration. This will further help us to distinguish the
-three different models from each other. We will pursue further
-implications and distinguishing characteristics of these competing
-models in future work.
+The standard reacceleration model for radio halos requires two ingredients with no current direct observational constraints: a CR population which produces seed electrons, and turbulence to perform Fermi II acceleration on these electrons\footnote{Other model ingredients, such as temperature, density, and B-field profiles, are observationally constrained by X-ray and Faraday rotation measurements.}.
+For the best studied radio halo, Coma, there are two main observational constraints: the radio surface brightness profile $S_{\rm nu}(r)$, and the integrated luminosity as a function of frequency $L(\nu)$.
+For certain assumptions about turbulence and the seed population, analytic theoretical models can match these observations \citep{brunetti11}, but the realism of the assumed seed electron and turbulent profiles must be confronted with numerical simulations.
+Cluster turbulence has been studied numerically in cosmological simulations with an eye toward radio halo properties \citep{donnert13,beresnyak13,miniati15}, though they were not confronted against the two benchmark observations mentioned above.
+{\bf Is the latter statement too provocative, remove?} More glaringly, direct simulation of the seed electron population has been woefully missing in the literature.
+In this paper, we fill that gap.
+At the same time, we study the sensitivity of radio halo profiles and spectra to variation in properties of turbulence and seed population, and uncover the dominant effects.
+
+In the first part of the paper, we use hydrodynamic zoom simulations of a Coma-like cluster in a cosmological setting to generate spatially and momentum-resolved seed populations of CRp's and CRe's from diffusive shock acceleration.
+The simulations include time-dependent cooling and adiabatic transport processes, and has been previously used in a variety of applications in CR cluster physics \citep{pinzke10,pinzke13}.
+The resultant CRp and CRe distribution functions then serve as initial conditions for our calculations of Fermi II acceleration by turbulence.
+We use time-dependent Fokker-Planck calculations which allow for spatial variations in the properties of turbulence (i.e., a spatially varying momentum diffusion coefficient).
+We adopt a simple parametric model for
+cluster turbulence, characterizing it by its overall normalization, spatial profile, and characteristic lifetime $\tau_{\rm cl}$.
+Our approach is relatively sophisticated in its treatment of the CR seed population and relatively simplified in its treatment of the turbulence; it is thus orthogonal and complementary to existing treatments which focus on the time-dependent compressible turbulence \citep{miniati15}.
+
+Given our seed electron population (which includes both primaries generated by DSA and secondary electrons created by CRp in hadronic interactions; for standard assumptions, the latter dominates), we find that applying the standard model previously used to reproduce Coma's radio halo properties \citep{brunetti11}, in which $\eps_{\rm turb} \propto \eps_{\rm therm}$, fails: it produces radio emission which is too centrally concentrated.
+Indeed, \citet{brunetti11} remark in their paper that the CR population required in their model is remarkably flat.
+By contrast, the simulations produce CRs which are more centrally concentrated.
+Thus, some modification of the standard vanilla model is needed, either by modifying the spatial distribution of the CRs, or that of turbulence.
+We explore two examples of the former: (i) CRs can stream in the ICM, producing a flat profile \citep{ensslin10,wiener13}, or (ii) given a higher e/p ratio in DSA acceleration (perhaps due to magnetic geometry; \citet{guo13}), the primary population can dominate.
+This has a much flatter profile (since secondaries must be generated collisionally, they will always be concentrated towards denser regions).
+However, both of these solutions still require some modification of the turbulent profile, requiring $\eps_{\rm turb}/\eps_{\rm th}$ to rise with radius.
+{\bf How did Brunetti et al get away with fitting Coma and not modifying the turbulent profile?
+You can't have a flatter CR profile than absolutely flat.} Indeed, one can simply use the unmodified CR profile derived from simulations if (iii) $\eps_{\rm turb}/\eps_{\rm th}$ rises somewhat more steeply with radius.
+The fact that $\eps_{\rm turb}/\eps_{\rm th}$ rises with radius is well supported by cosmological hydrodynamic simulations of clusters \citep{lau09,shaw10,vazza11}; even the last model (iii) is (within the scatter) perfectly consistent with the trends seen by such simulations.
+This strongly suggests that a rising $\eps_{\rm turb}/\eps_{\rm th}$ should be part of any final model of radio halos.
+Given the lack of observational constraints on turbulent profiles, this unfortunately means that models will have yet another degree of freedom.
+
+The above models are merely meant to serve as existence proofs, showing what modifications to the standard model are necessary to be reconciled with the observations.
+There are too many uncertainties and parameter degeneracies for any of these models to be definitive, or for one to make firm quantitive statements about turbulent and seed CR profiles, apart from placing certain bounds.
+We abstract the main parameter dependencies by exploring static, spherically symmetric models consistent with Coma, where we repeat our Fokker-Planck calculations.
+We explore three main effects: the overall normalization of turbulence, and spatial distribution of turbulence and cosmic rays (note that while radio halos have a non-linear dependence on the overall normalization of turbulence, the surface brightness scales linearly with the CR abundance; thus, this degree of freedom is easily understood).
+We find that the most important variable is the overall normalization of turbulence: surface brightness scales exponentially with the amount of turbulence.
+The radio spectrum also becomes more curved with higher turbulence.
+The spatial distribution of both turbulence and CRs also influence radio halos profiles (for both, flatter distributions at fixed overall normalization imply flatter surface brightness profiles with lower overall radio luminosity), but play a secondary role.
+
+This exponential dependence of radio halo luminosity with turbulence then raises the interesting question of why radio halo scaling relations (e.g., $L_{\nu} --L_{\rm X}$) are so tight.
+Previous statistical modeling of radio halo populations \citep{cassano05,cassano06} have focussed on matching the mean relations, but not the scatter.
+We believe the latter provides a particularly interesting and potentially fruitful constraint.
+The acceleration timescale $tau_{\rm D}$ and the length of time during which acceleration takes place $\tau_{\rm cl}$ must be matched so that there are roughly $\sim 2$ e-folds (given the factor $\sim 10$ difference in radio luminosity between the radio bright and faint populations; \citet{brown11}), otherwise scatter in turbulence (which we might expect given the wide variety of merger and infall conditions) will be exponentially amplified in radio luminosity.
+The timescale of the merger has some natural scatter which is not obviously correlated with $\tau_{\rm D}$.
+More likely candidates for $\tau_{\rm cl}$ are the timescale on which turbulence decays, or the escape (i.e.
+spatial diffusion) time from an accelerating regime.
+Across a wide variety of conditions, this must be correlated with $\tau_{\rm D}$ so as to keep the ratio $\tau_{\rm D}/\tau_{\rm cl}$ roughly constant.
+We believe this issue is worthy of further study.
 
@@
 for useful discussions. A.P. is grateful to the Swedish research
-council for financial support. S.P.O. thanks NASA grant NNX12AG73G for
-support. C.P.~acknowledges support by the European Research Council
+council for financial support. S.P.O. thanks NASA grants NNX12AG73G and NNX15AK81G for
+support, as well as KITP for hospitality.
+This research was supported in part by the National Science Foundation under Grant No.
+NSF PHY11-25915.
+C.P.~acknowledges support by the European Research Council
 under ERC-CoG grant CRAGSMAN-646955 and by the Klaus Tschira

### 2016-05-13 paper.tex
edits

@@
 \citep{1987A&A...182...21S,1993ApJ...406..399G,2001MNRAS.320..365B,
-  2004MNRAS.350.1174B,brunetti07,brunetti11,2015ApJ...800...60M}. Due
+  2004MNRAS.350.1174B,brunetti07,brunetti11,miniati15}. Due
 to the short radiative cooling time of high-energy relativistic
@@
 merger proceeds.  So our approach is orthogonal (and complementary) to
-e.g., simulations of \citealp{2015ApJ...800...60M} that focus on the
+e.g., simulations of \citealp{miniati15} that focus on the
 time-dependent compressible turbulence while adopting a simplified
@@
 \citep{brunetti07,brunetti11}, injection scale of turbulence
-\citep{2015ApJ...800...60M}, the energy density of turbulence
+\citep{miniati15}, the energy density of turbulence
 \citep{2009ApJ...705.1129L,2010ApJ...725.1452S,2011A&A...529A..17V},
@@
 standard approaches
-\citep{brunetti07,brunetti11,2004ApJ...614..757Y,2015ApJ...800...60M}
+\citep{brunetti07,brunetti11,2004ApJ...614..757Y,miniati15}
 we assume that about one Gyr after core passage the fields have
@@
 
-All of the physics of turbulent reacceleration is effectively encapsulated in the diffusion coefficient, which can be rewritten as \citep{2015ApJ...800...60M}:
+All of the physics of turbulent reacceleration is effectively encapsulated in the diffusion coefficient, which can be rewritten as \citep{miniati15}:
 \begin{equation}
@@
 {\bf Energy in compressive modes} The total turbulence energy is typically $\sim 15-70\%$ of the thermal energy in a cluster \citep{vazza11}; it rises rapidly during a merger.
-The compressible component is $\sim 20-40\%$ of the total turbulent energy, and shows more rapid temporal variations compared to the compressible component \citep{2013ApJ...771..131B,2015ApJ...800...60M}.
+The compressible component is $\sim 20-40\%$ of the total turbulent energy, and shows more rapid temporal variations compared to the compressible component \citep{2013ApJ...771..131B,miniati15}.
 It is worth noting that in the subsonic regime of the solar wind \citep{yao11,howes12}, as well as most idealized calculations of turbulent driving, there is relatively little energy in the fast mode.
@@
 In the high-$\beta$, subsonic conditions of the ICM, the Alfv{\'e}n/slow modes are exactly/approximately incompressible, and so the approximate identification of compressive modes with fast modes is valid.
-We therefore take $\sim 25\%$ of the turbulent energy density in compressive fast modes as a reasonable baseline estimate \citep{2013ApJ...771..131B,2015ApJ...800...60M}.
+We therefore take $\sim 25\%$ of the turbulent energy density in compressive fast modes as a reasonable baseline estimate \citep{2013ApJ...771..131B,miniati15}.
 If a large fraction of energy is in slow modes, then resonant broadening of wave-particle interactions can render slow modes an efficient acceleration mechanism \citep{lynn14}, as we discuss briefly in \S\ref{?}.
@@
 
-Finally, if turbulence is transonic ($M_{\rm s} \sim {\mathcal O}(1)$), then compressible modes can dissipate in weak shocks, as seen in decompositions of the velocity field into solenoidal/compressible components both in idealized simulations \citep{kowal10,porter15}, and cosmological hydrodynamic simulations \citep{2015ApJ...800...60M}.
+Finally, if turbulence is transonic ($M_{\rm s} \sim {\mathcal O}(1)$), then compressible modes can dissipate in weak shocks, as seen in decompositions of the velocity field into solenoidal/compressible components both in idealized simulations \citep{kowal10,porter15}, and cosmological hydrodynamic simulations \citep{miniati15}.
 The compressible component has a steep Burgers ($s=2$) spectrum.
@@
 If we contrast the different velocity scalings: $\varv \propto l^{1/4}$ (Kraichnan), $\varv \propto l^{1/3}$ (Kolmogorov), $\varv \propto l^{1/2}$ (Burgers), we see that because of its dissipative nature, Burgers turbulence is the least efficient at transferring energy towards the small scales needed (since the wave particle interaction rate scales as $k$) for efficient acceleration.
-If Burgers turbulence dominates, then particle acceleration rates are too slow in the face of cooling processes to explain radio halos \citep{2015ApJ...800...60M}.
+If Burgers turbulence dominates, then particle acceleration rates are too slow in the face of cooling processes to explain radio halos \citep{miniati15}.
 
@@
 merger mass ratio, and the degree of cluster anisotropy
-\citep{2015ApJ...800...60M}. We parametrize these uncertainties and
+\citep{miniati15}. We parametrize these uncertainties and
 assume that it scales with the thermal energy density to some
@@
   contribute a factor $0.2-0.4$ to the total turbulent energy
-  \citep{2013ApJ...771..131B,2015ApJ...800...60M}. Furthermore, the
+  \citep{2013ApJ...771..131B,miniati15}. Furthermore, the
   total turbulent energy, which can be decomposed into a slenoidal and
@@
 relatively unknown non-thermal physics in the ICM. Here we develop a
-simplified framework that will be used to explore how radio emission
-depends on these parameters. Our fiducial model is meant to be
+simplified framework for our reacceleration model of secondary
+electrons. We will explore how radio emission depends on the
+parameters describing the spatial profile of CR protons and
+turbulence, thereby semi-analytically probing variations about the
+models \Mflatturb and \Mstream. Our fiducial model is meant to be
 compared against the Coma cluster.
@@
 adiabatic compressive heating of the CRs, though this is generally
-subdominant (e.g., see Fig. 7 of \citealt{2015ApJ...800...60M}). Once
+subdominant (e.g., see Fig. 7 of \citealt{miniati15}). Once
 the CRs have been reaccelerated for $\tau_\rmn{cl} = 650\,\rmn{Myr}$,
@@
 \citep{2002ApJ...567..716R} and $R_{\rmn{c}} = 294\,\rmn{kpc}$,
-respectively. In accordance with rotation measure measurements, we assume $B(r)=B_{0} (n/n_{0})^{\eta}$, where $B_{0}=4.8 \mu$G and $\eta=0.5$ \citep{bonafede10}.
+respectively. In accordance with Faraday rotation measure
+measurements, we assume $B(r)=B_{0} (n/n_{0})^{\eta}$, where
+$B_{0}=4.8 \mu$G and $\eta=0.5$ \citep{bonafede10}.
 
@@
 \subsection{Results}
-
-Figure~\ref{fig:param_comp} shows the impact of turbulence and the
-spatial distribution of CRs on the radio emission.
-
-{\bf Impact of overall level of turbulence ($X_{\rm tu}$).} From the top panels of Fig.~\ref{fig:param_comp}, we see that as $X_{\rm tu}$ increases, there are 3 important changes: an exponential increase in radio luminosity, a flattening of the radio surface brightness profile, and an increase in spectral curvature.
-We discuss these in turn.
-
-The exponential increase in radio surface brightness is easily understood from equation~\ref{eq:Creacc}, since for a power-law initial distribution function $f_{\rm i}(p) = C_{\rm 0} p^{-\alpha}$, then $C_{\rm reacc} \propto C_{\rm 0} {\rm exp}(A \tau_{\rm cl}/\tau_{\rm D}) \propto {\rm exp} (B(r) X_{\rm tu}^{2})$.
-This exponential sensitivity is somewhat modified by cooling (which results in a non power-law spectrum; also, the shorter the acceleration time, the larger the pool of seed electrons available which would otherwise cool away), but overall is a good approximation.
-%For fixed $\tau_{\rm cl}$, it also implies a critical level of turbulence, below which reacceleration becomes negligible.
-
-An increase in $X_{\rm tu}$ flattens the surface brightness profile, since high acceleration efficiency leads to larger amplification in the cluster outskirts (where cooling is less important) than the center.
-In particular, in the cluster outskirts, the reduced impact of Coulomb cooling implies that there is a larger pool of low-energy electrons available for reacceleration (see timescales in Table \ref{tab:timescales}).
-
-Larger levels of turbulence also {\it increase} spectral curvature, which might seem puzzling.
-It can be understood as follows.
-The pre-acceleration electron distribution function can be understood as a result of competition between injection $f \propto p^{-\alpha_{\rm inj}}$ and cooling.
-At low momenta, when the Coulomb cooling time is short, $f \propto p^{-\alpha_{\rm inj}+1}$, at high momenta, when inverse Compton/synchrotron cooling dominates, $f \propto p^{-\alpha_{\rm inj} -1}$.
-In between, there is a quasi-adiabatic regime where electrons accumulate (for more details, and an analytic self-similar solution, see \citealt{1999ApJ...520..529S, pinzke13}).
-In the absence of cooling, momentum advection in the limit $D_{pp} \propto p^{2}$ (so that $\tau =p^{2}/4 D_{pp}$ is momentum independent) simply shifts the distribution $f(p) \rightarrow f(A p)$.
-When the acceleration efficiency is low, most observable emission corresponds to the power-law tail of the distribution function $f \propto p^{-\alpha_{\rm inj}-1}$ set by the balance between injection and synchrotron/IC cooling.
-However, as the acceleration efficiency $A$ increases, radio emission starts to probe the 'bump' around $p_{*}$ (given by $\tau_{\rm D} \sim \tau_{\rm cool}(p_{*})$) where electrons accumulate and the distribution function is curved.
-This results in a curved emission spectrum.
-The synchrotron spectrum steepens at the frequency \citep{brunetti01}:
-\begin{equation}
-\nu_{\rm s} \propto \frac{B \tau_{\rm D}^{-2}}{(B^{2}+B^{2}_{\rm CMB})^{2}}
-\end{equation}
-where $B_{\rm CMB} \equiv (8 \pi U_{\rm CMB})^{1/2}$, which increases for shorter $\tau_{\rm D}$.
-
-{\bf Impact of spatial profile of turbulence ($\alpha_{\rm tu}$)} From the middle panels of Fig.~\ref{fig:param_comp}, we see that as expected, a flatter turbulence profile directly translates into a flatter radio surface brightness profile.
-Since seed electrons are more concentrated toward the center (the collisional production of secondaries is more rapid there), and B-fields are higher, concentrating the turbulence toward the cluster center for fixed $X_{\rm tu}$ results in higher radio luminosities, and slightly more curvature (due to the increased importance of cooling near the center).
-Overall, however, the spatial profile of turbulence has a much weaker effect than its overall normalization.
-
-{\bf Impact of spatial profile of seed CRs $\alpha_{\rm CR, spat}$} The spatial distribution of CRs has an even smaller impact on radio emission.
-At fixed total CR energy content $X_{\rm CR}$, concentrating the CRs towards the center leads to more centrally dominated surface brightness profiles, as expected, and higher radio luminosities (for the same reasons as above: secondaries are more easily produced in the center, and B-fields are higher).
-We have also confirmed that radio surface brightness profiles scale linearly with $X_{\rm CR}$, as expected.
-
-Overall, our results suggest that radio halos are much more sensitive to the level of turbulence (exponential dependence) rather than CR abundance (linear dependence), and that the spatial distribution of turbulence and CRs, while important, are second-order effects.
-In our parametrization, the most important controlling variable is $X_{\rm tu}$.
-The overall level of turbulence has to be such that $\tau_{\rm D} \sim \tau_{\rm cl}$ (see Table \ref{tab:timescales}), otherwise, too little or too much amplification takes place.
-For instance, for
-$X_\rmn{tu}\gtrsim0.08$, changing $X_\rmn{tu}$ by a factor of two
-changes the radio surface brightness by a factor of $\sim 10-100$ (see top panels of Fig.~\ref{fig:param_comp}).
-The required $\tau_{\rm D}/\tau_{\rm cl}$ depends only logarithmically on the abundance of seed CRs.
-While the requirement of a threshold level of turbulence may explain why radio brightness is bimodal, it also raises a fine-tuning problem: why is the $L_{\rm radio}$ vs.
-$L_{\rm X}$ relation in active radio halos so tight?
-Depending on the details of infall or mergers, we would naturally expect fluctuations in $X_{\rm tu}$, which would translate into large scatter in the $L_{\rm radio}--L_{\rm X}$ relation.
-This can only make sense if the timescale over which acceleration takes place $\tau_{\rm cl}$ also depends on the properties of turbulence, so that the the ratio $\tau_{\rm D}/\tau_{\rm cl}$ has relatively little scatter.
-We discuss one such scenario in \S\ref{sec:reacc}, but this point clearly deserves more work.
 
@@
 
+Figure~\ref{fig:param_comp} shows the impact of turbulence and the
+spatial distribution of CRs on the radio emission.
+
+{\bf Impact of overall level of turbulence ($X_{\rm tu}$).} From the top panels of Fig.~\ref{fig:param_comp}, we see that as $X_{\rm tu}$ increases, there are 3 important changes: an exponential increase in radio luminosity, a flattening of the radio surface brightness profile, and an increase in spectral curvature.
+We discuss these in turn.
+
+The exponential increase in radio surface brightness is easily understood from equation~\ref{eq:Creacc}, since for a power-law initial distribution function $f_{\rm i}(p) = C_{\rm 0} p^{-\alpha}$, then $C_{\rm reacc} \propto C_{\rm 0} {\rm exp}(A \tau_{\rm cl}/\tau_{\rm D}) \propto {\rm exp} (B(r) X_{\rm tu}^{2})$.
+This exponential sensitivity is somewhat modified by cooling (which results in a non power-law spectrum; also, the shorter the acceleration time, the larger the pool of seed electrons available which would otherwise cool away), but overall is a good approximation.
+%For fixed $\tau_{\rm cl}$, it also implies a critical level of turbulence, below which reacceleration becomes negligible.
+
+An increase in $X_{\rm tu}$ flattens the surface brightness profile, since high acceleration efficiency leads to larger amplification in the cluster outskirts (where cooling is less important) than the center.
+In particular, in the cluster outskirts, the reduced impact of Coulomb cooling implies that there is a larger pool of low-energy electrons available for reacceleration (see timescales in Table \ref{tab:timescales}).
+
+Larger levels of turbulence also {\it increase} spectral curvature, which might seem puzzling.
+It can be understood as follows.
+The pre-acceleration electron distribution function can be understood as a result of competition between hadronic injection $f \propto p^{-\alpha_{\rm inj}}$ and cooling, which results in a quasi-steady state for the non-thermal (secondary) electrons.
+At low momenta, when the Coulomb cooling time is short, $f \propto p^{-\alpha_{\rm inj}+1}$, at high momenta, when inverse Compton/synchrotron cooling dominates, $f \propto p^{-\alpha_{\rm inj} -1}$.
+In between, there is a quasi-adiabatic regime where electrons accumulate (for more details, and an analytic self-similar solution, see \citealt{1999ApJ...520..529S, pinzke13}).
+In the absence of cooling, momentum advection in the limit $D_{pp} \propto p^{2}$ (so that $\tau =p^{2}/4 D_{pp}$ is momentum independent) simply shifts the distribution $f(p) \rightarrow f(A p)$.
+When the acceleration efficiency is low, most observable emission corresponds to the power-law tail of the distribution function $f \propto p^{-\alpha_{\rm inj}-1}$ set by the balance between injection and synchrotron/IC cooling.
+However, as the acceleration efficiency $A$ increases, radio emission starts to probe the 'bump' around $p_{*}$ (given by $\tau_{\rm D} \sim \tau_{\rm cool}(p_{*})$) where electrons accumulate and the distribution function is curved.
+This results in a curved emission spectrum.
+The synchrotron spectrum steepens at the frequency \citep{2001MNRAS.320..365B}:
+\begin{equation}
+\nu_{\rm s} \propto \frac{B \tau_{\rm D}^{-2}}{(B^{2}+B^{2}_{\rm CMB})^{2}}
+\end{equation}
+where $B_{\rm CMB} \equiv (8 \pi U_{\rm CMB})^{1/2}$, which increases for shorter $\tau_{\rm D}$.
+
+{\bf Impact of spatial profile of turbulence ($\alpha_{\rm tu}$).} From the middle panels of Fig.~\ref{fig:param_comp}, we see that as expected, a flatter profile of the turbulent pressure directly translates into a flatter radio surface brightness profile.
+Since seed electrons are more concentrated toward the center (the collisional production of secondaries is more rapid there), and magnetic fields are stronger, concentrating the turbulence toward the cluster center for fixed $X_{\rm tu}$ results in higher radio luminosities, and slightly more curvature (due to the increased importance of cooling near the center).
+Overall, however, the spatial profile of turbulence has a much weaker effect than its overall normalization.
+
+{\bf Impact of spatial profile of seed CRs $\alpha_{\rm CR, spat}$.} The spatial distribution of CRs has an even smaller impact on radio emission.
+At fixed total CR energy content $X_{\rm CR}$, concentrating the CRs towards the center leads to more centrally dominated surface brightness profiles, as expected, and higher radio luminosities (for the same reasons as above: secondaries are more easily produced in the center, and magnetic fields are stronger).
+We have also confirmed that radio surface brightness profiles scale linearly with $X_{\rm CR}$, as expected.
+
+Overall, our results suggest that radio halos are much more sensitive to the level of turbulence (exponential dependence) rather than CR abundance (linear dependence), and that the spatial distribution of turbulence and CRs, while important, are second-order effects.
+In our parametrization, the most important controlling variable is $X_{\rm tu}$.
+The overall level of turbulence has to be such that $\tau_{\rm D} \sim \tau_{\rm cl}$ (see Table \ref{tab:timescales}), otherwise, too little or too much amplification takes place.
+For instance, for $X_\rmn{tu}\gtrsim0.08$, changing $X_\rmn{tu}$ by a factor of two changes the radio surface brightness by a factor of $\sim 10-100$ (see top panels of Fig.~\ref{fig:param_comp}).
+The required $\tau_{\rm D}/\tau_{\rm cl}$ depends only logarithmically on the abundance of seed CRs.
+
+While the requirement of a threshold level of turbulence may explain why radio brightness is bimodal, it also raises a fine-tuning problem: why is the $L_{\rm radio}$ vs.
+$L_{\rm X}$ relation in active radio halos so tight?
+Depending on the details of infall or mergers, we would naturally expect fluctuations in $X_{\rm tu}$, which would translate into large scatter in the $L_{\rm radio}$--$L_{\rm X}$ relation.
+This can be only be understood if the timescale over which acceleration takes place $\tau_{\rm cl}$ also depends on the properties of turbulence, so that the the ratio $\tau_{\rm D}/\tau_{\rm cl}$ has relatively little scatter.
+We discuss one such scenario in \S\ref{sec:reacc}, but this point clearly deserves more work.
+
 % --- section: Conclusions --- %
@@
 
-The standard reacceleration model for radio halos requires two ingredients with no current direct observational constraints: a CR population which produces seed electrons, and turbulence to perform Fermi II acceleration on these electrons\footnote{Other model ingredients, such as temperature, density, and B-field profiles, are observationally constrained by X-ray and Faraday rotation measurements.}.
-For the best studied radio halo, Coma, there are two main observational constraints: the radio surface brightness profile $S_{\rm nu}(r)$, and the integrated luminosity as a function of frequency $L(\nu)$.
-For certain assumptions about turbulence and the seed population, analytic theoretical models can match these observations \citep{brunetti11}, but the realism of the assumed seed electron and turbulent profiles must be confronted with numerical simulations.
-Cluster turbulence has been studied numerically in cosmological simulations with an eye toward radio halo properties \citep{donnert13,beresnyak13,miniati15}, though they were not confronted against the two benchmark observations mentioned above.
-{\bf Is the latter statement too provocative, remove?} More glaringly, direct simulation of the seed electron population has been woefully missing in the literature.
-In this paper, we fill that gap.
-At the same time, we study the sensitivity of radio halo profiles and spectra to variation in properties of turbulence and seed population, and uncover the dominant effects.
+The standard reacceleration model for radio halos requires two ingredients with
+no current direct observational constraints: a CR population which produces seed
+electrons, and turbulence to perform second-order Fermi acceleration on these
+electrons\footnote{Other model ingredients, such as temperature, density, and
+  B-field profiles, are observationally constrained by X-ray and Faraday
+  rotation measurements.}. For the best studied radio halo, Coma, there are two
+main observational constraints: the radio surface brightness profile
+$S_{\nu}(r)$, and the integrated luminosity as a function of frequency
+$L(\nu)$. For certain assumptions about turbulence and the seed population,
+analytic theoretical models can match these observations \citep{brunetti11}, but
+the realism of the assumed seed electron and turbulent profiles must be
+confronted with numerical simulations.
+
+Cluster turbulence has been studied numerically in cosmological simulations with
+an eye toward radio halo properties \citep{2013ApJ...771..131B,
+  miniati15}, though they were not confronted against the two
+benchmark observations mentioned above. Most importantly, direct simulation of the
+seed electron population has been missing in the literature. In this paper, we
+fill that gap. At the same time, we study the sensitivity of radio halo profiles
+and spectra to variation in properties of turbulence and seed population, and
+uncover the dominant effects.
 
@@
 By contrast, the simulations produce CRs which are more centrally concentrated.
+
 Thus, some modification of the standard vanilla model is needed, either by modifying the spatial distribution of the CRs, or that of turbulence.
-We explore two examples of the former: (i) CRs can stream in the ICM, producing a flat profile \citep{ensslin10,wiener13}, or (ii) given a higher e/p ratio in DSA acceleration (perhaps due to magnetic geometry; \citet{guo13}), the primary population can dominate.
+We explore two examples of the former: (i) CRs can stream in the ICM, producing a flat profile \citep{ensslin11,wiener13}, or (ii) given a higher e/p ratio in DSA acceleration (perhaps due to magnetic geometry; \citealt{2014ApJ...794..153G}), the primary population can dominate.
 This has a much flatter profile (since secondaries must be generated collisionally, they will always be concentrated towards denser regions).
 However, both of these solutions still require some modification of the turbulent profile, requiring $\eps_{\rm turb}/\eps_{\rm th}$ to rise with radius.
-{\bf How did Brunetti et al get away with fitting Coma and not modifying the turbulent profile?
-You can't have a flatter CR profile than absolutely flat.} Indeed, one can simply use the unmodified CR profile derived from simulations if (iii) $\eps_{\rm turb}/\eps_{\rm th}$ rises somewhat more steeply with radius.
-The fact that $\eps_{\rm turb}/\eps_{\rm th}$ rises with radius is well supported by cosmological hydrodynamic simulations of clusters \citep{lau09,shaw10,vazza11}; even the last model (iii) is (within the scatter) perfectly consistent with the trends seen by such simulations.
+Indeed, one can simply use the unmodified CR profile derived from simulations if (iii) $\eps_{\rm turb}/\eps_{\rm th}$ rises somewhat more steeply with radius.
+The fact that $\eps_{\rm turb}/\eps_{\rm th}$ rises with radius is well supported by cosmological hydrodynamic simulations of clusters \citep{2009ApJ...705.1129L,2010ApJ...725.1452S,vazza11}; even the last model (iii) is (within the scatter) perfectly consistent with the trends seen by such simulations.
 This strongly suggests that a rising $\eps_{\rm turb}/\eps_{\rm th}$ should be part of any final model of radio halos.
@@
 
-The above models are merely meant to serve as existence proofs, showing what modifications to the standard model are necessary to be reconciled with the observations.
-There are too many uncertainties and parameter degeneracies for any of these models to be definitive, or for one to make firm quantitive statements about turbulent and seed CR profiles, apart from placing certain bounds.
-We abstract the main parameter dependencies by exploring static, spherically symmetric models consistent with Coma, where we repeat our Fokker-Planck calculations.
-We explore three main effects: the overall normalization of turbulence, and spatial distribution of turbulence and cosmic rays (note that while radio halos have a non-linear dependence on the overall normalization of turbulence, the surface brightness scales linearly with the CR abundance; thus, this degree of freedom is easily understood).
-We find that the most important variable is the overall normalization of turbulence: surface brightness scales exponentially with the amount of turbulence.
-The radio spectrum also becomes more curved with higher turbulence.
-The spatial distribution of both turbulence and CRs also influence radio halos profiles (for both, flatter distributions at fixed overall normalization imply flatter surface brightness profiles with lower overall radio luminosity), but play a secondary role.
-
-This exponential dependence of radio halo luminosity with turbulence then raises the interesting question of why radio halo scaling relations (e.g., $L_{\nu} --L_{\rm X}$) are so tight.
-Previous statistical modeling of radio halo populations \citep{cassano05,cassano06} have focussed on matching the mean relations, but not the scatter.
-We believe the latter provides a particularly interesting and potentially fruitful constraint.
-The acceleration timescale $tau_{\rm D}$ and the length of time during which acceleration takes place $\tau_{\rm cl}$ must be matched so that there are roughly $\sim 2$ e-folds (given the factor $\sim 10$ difference in radio luminosity between the radio bright and faint populations; \citet{brown11}), otherwise scatter in turbulence (which we might expect given the wide variety of merger and infall conditions) will be exponentially amplified in radio luminosity.
-The timescale of the merger has some natural scatter which is not obviously correlated with $\tau_{\rm D}$.
-More likely candidates for $\tau_{\rm cl}$ are the timescale on which turbulence decays, or the escape (i.e.
-spatial diffusion) time from an accelerating regime.
-Across a wide variety of conditions, this must be correlated with $\tau_{\rm D}$ so as to keep the ratio $\tau_{\rm D}/\tau_{\rm cl}$ roughly constant.
-We believe this issue is worthy of further study.
-
-{\bf Acknowledgments.} We thank Josh Wiener for discussions on CR
-streaming. We are also grateful to Lawrence Rudnick for discussion on
-uncertainties in the 1.4 GHz radio data. Finally, we thank Fabio
-Zandanel for recalculating gamma-ray limits and Gianfranco Brunetti
-for useful discussions. A.P. is grateful to the Swedish research
-council for financial support. S.P.O. thanks NASA grants NNX12AG73G and NNX15AK81G for
-support, as well as KITP for hospitality.
-This research was supported in part by the National Science Foundation under Grant No.
-NSF PHY11-25915.
-C.P.~acknowledges support by the European Research Council
-under ERC-CoG grant CRAGSMAN-646955 and by the Klaus Tschira
-Foundation.
+The above models are merely meant to serve as existence proofs, showing what
+modifications to the standard model are necessary to be reconciled with the
+radio halo observations. There are too many uncertainties and parameter
+degeneracies for any of these models to be definitive, or for one to make firm
+quantitive statements about turbulent and seed CR profiles, apart from placing
+certain bounds. We abstract the main parameter dependencies by exploring static,
+spherically symmetric models consistent with Coma, where we repeat our
+Fokker-Planck calculations. We explore three main effects: the overall
+normalization of turbulence, and spatial distribution of turbulence and cosmic
+rays.
+%(note that while radio halos have a non-linear dependence on the overall
+%normalization of turbulence, the surface brightness scales linearly with the CR
+%abundance; thus, this degree of freedom is easily understood).
+We find that the most important variable is the overall normalization of
+turbulence: surface brightness scales exponentially with the amount of
+turbulence. The radio spectrum also becomes more curved with higher
+turbulence. In contrast, the surface brightness scales linearly with the CR
+abundance.  The spatial distribution of both turbulence and CRs also influence
+radio halos profiles (for both, flatter distributions at fixed overall
+normalization imply flatter surface brightness profiles with lower overall radio
+luminosity), but play a secondary role.
+
+This exponential dependence of radio halo luminosity with turbulence then raises
+the interesting question of why radio halo scaling relations (e.g.,
+$L_{\nu}$--$L_{\rm X}$) are so tight. Previous statistical modeling of radio
+halo populations \citep{2006MNRAS.369.1577C,2007MNRAS.378.1565C} have focussed
+on matching the mean relations, but not the scatter. We believe the latter
+provides a particularly interesting and potentially fruitful constraint. The
+acceleration timescale $\tau_{\rm D}$ and the length of time during which
+acceleration takes place $\tau_{\rm cl}$ must be matched so that there are
+roughly $\sim 2$ e-folds (given the factor $\sim 10$ difference in radio
+luminosity between the radio bright and faint populations; \citet{brown11}),
+otherwise scatter in turbulence (which we might expect given the wide variety of
+merger and infall conditions) will be exponentially amplified in radio
+luminosity. The timescale of the merger has some natural scatter which is not
+obviously correlated with $\tau_{\rm D}$. More likely candidates for $\tau_{\rm
+  cl}$ are the timescale on which turbulence decays, or the escape (i.e. spatial
+diffusion) time from an accelerating regime. Across a wide variety of
+conditions, this must be correlated with $\tau_{\rm D}$ so as to keep the ratio
+$\tau_{\rm D}/\tau_{\rm cl}$ roughly constant. We believe this issue is worthy
+of further study.
+
+{\bf Acknowledgments.} We thank Josh Wiener for discussions on CR streaming,
+Lawrence Rudnick for discussion on uncertainties in the 1.4 GHz radio data,
+Fabio Zandanel for re-calculating gamma-ray limits, and Gianfranco Brunetti for
+useful discussions. We thank an anonymous referee for helpful comments that
+improved the paper. A.P. is grateful to the Swedish research council for
+financial support. S.P.O. thanks NASA grants NNX12AG73G and NNX15AK81G for
+support, as well as KITP for hospitality. This research was supported in part by
+the National Science Foundation under Grant No. NSF
+PHY11-25915. C.P.~acknowledges support by the European Research Council under
+ERC-CoG grant CRAGSMAN-646955 and by the Klaus Tschira Foundation.
 

### 2016-05-30 paper.tex
rephrased dummy's guide
Add files via upload

@@
 
-To pursue these three possibilities further, we employ cosmological
-simulations of CRs in clusters. In tandem with new insights from our
-recent work on DSA generated fossil electrons \citep{pinzke13}, we
-generate the first quantitative calculation of primary and secondary
-seed electrons and compare to observations in the Coma cluster. For
-the most part, we adopt parameters that are used in previous work,
-including Fermi-II acceleration with models of turbulent spectra
+\AP{In section~\ref{sec:results} we pursue these three possibilities
+  further and employ cosmological simulations of CRs in clusters. In
+  tandem with new insights from our recent work on DSA generated
+  fossil electrons \citep{pinzke13}, we generate the first
+  quantitative calculation of primary and secondary seed electrons and
+  compare to observations in the Coma cluster. For the most part, we
+  adopt parameters that are used in previous work, including Fermi-II
+  acceleration with models of turbulent spectra
   \citep{brunetti07,brunetti11}, injection scale of turbulence
@@
     profile]{pinzke10}. All these parameters are uncertain, and could
-potentially change our predictions. We refer the reader to
+  potentially change our predictions. In section~\ref{sect:param_comp}
+  we adopt a simplified spherical framework for our reacceleration
+  model of secondary electrons. We perform a small parameter study and
+  explore how radio emission depends on the parameters describing the
+  spatial profile of CR protons and turbulence. In
+  section~\ref{sect:param_comp} we discuss our results and present our
+  conclusions.} \sout{We refer the reader to
   section~\ref{sect:param_comp} for a first exploration of parameter
-space, however we leave the detailed exploration of parameter space and
-the interaction between free parameters to future work.
+  space, however} We leave the detailed exploration of parameter space
+and the interaction between free parameters to future work.
 
@@
 they arise from a two body process, they are too centrally
-concentrated. They also produce $\gamma$-ray emission in excess of
+concentrated. They also produce gamma-ray emission in excess of
 Fermi-LAT upper limits
@@
 
-\subsection{Dummy's guide} 
+\subsection{Physical picture of reacceleration}
 \label{sec:dummy}
@@
 \langle k \rangle_{\mathcal{W}} = \frac{1}{\langle (\delta \varv_{\rm c})^{2} \rangle} \int_{k_{\rm L}}^{k_{\rm cut}} dk \, k \, \mathcal{W}(k) \approx \frac{s-1}{2-s} k_{\rm L} \left( \frac{k_{\rm cut}}{k_{\rm L}} \right)^{2-s}
+\label{eqn:k_W} 
 \end{equation}
@@
 \tau_{\rm l} \sim \left(\frac{\tau_{\rm edd}}{\tau_{\rm A}}\right)^{2} \tau_{\rm A} \sim \frac{l \varv_{\rm A}}{\varv_{\rm l}^{2}} 
+\label{eqn:cascade} 
 \end{equation}
@@
 turbulent eddies is $\varv_0\approx 0.47 c_\rmn{s}$ throughout the
-cluster. This gives a turbulent acceleration time scale, $\tau_{D} =
+cluster. This gives a turbulent acceleration time scale, $\tau_{\rm D} =
 p^2/4D_{pp}$, that is typically few 100 Myrs in the ICM (see
@@
 
-\SPO{the derivation of the following is not transparent, could you expand?}
-During reacceleration, the CRps increase their normalization
-approximately by the factor
-\begin{equation}
-  \label{eq:Creacc}
-  \delta C_\rmn{reacc.} \sim 
-  \exp{\left[\frac{(2+\alpha)(\alpha+1)}{4}\frac{\tau_\rmn{cl}}{\tau_\rmn{D}}\right]}\,,
-\end{equation}
-if injection and cooling are neglected. The reaccelerated CRs depend
-exponentially on $\tau_D\sim 1/D_{pp}$ as long as $\tau_D \lesssim
-\tau_\rmn{cl}$, where $\tau_\rmn{cl}$ represent the duration of
-reacceleration of the merger which we assume to be 650~Myrs long.
+%\SPO{the derivation of the following is not transparent, could you
+%  expand?}  \sout{During reacceleration, the CRps increase their
+%  normalization approximately by the factor} \AP{In the region where
+%  reacceleration dominates over cooling and injection, the CRps
+%%  increase their normalization exponentially. This can easily be
+ % understood by considering a simple toy model where a fossil CRp
+%  population described by $f=C p^{-\alpha}$ is reaccelerated such that
+%  $\tau_D < \tau_\rmn{cooling},\tau_\rmn{injection}$, i.e. injection
+%  and cooling can be neglected. The Fokker-Planck equation in
+%  Eqn.~\ref{eq:FP_p} then simplifies to}
+%\begin{equation}
+%  \dot{f} = {{\partial }\over{\partial p}}
+%  p^2 D_{pp} {{\partial }\over{\partial p}} \frac{f}{p^2}\,,
+%\end{equation}
+%with the analytic solution given by
+%\begin{equation}
+%  \label{eq:Creacc}
+%%  \delta C_\rmn{reacc.} \sim 
+%  \exp{\left[\frac{(2+\alpha)(\alpha-1)}{4}\frac{\tau_\rmn{cl}}{\tau_\rmn{D}}\right]}\,.
+%\end{equation}
+%The reaccelerated CRs depend exponentially on $\tau_D\sim 1/D_{pp}$ as
+%long as $\tau_D \lesssim \tau_\rmn{cl}$, where $\tau_\rmn{cl}$
+%represent the duration of reacceleration of the merger which we assume
+%to be 650~Myrs long.
 
@@
 
-In this setion, we solve the Fokker-Planck equation for CR transport
+In this section, we solve the Fokker-Planck equation for CR transport
 on Lagrangian particle trajectories through cosmic history.  We
@@
 this conclusion much because of the weak radial dependence of
-$D_\rmn{pp}(R)\propto \eps_\rmn{th}(R)^{\alpha_\rmn{tu}-1}
+$D_{pp}(R)\propto \eps_\rmn{th}(R)^{\alpha_\rmn{tu}-1}
 \sqrt{T(R)}$. This signals that the problem is generic and requires
@@
 \Mprimary model with $\alpha_\rmn{tu}=0.88$ has the flattest profile
-with $\tau_D\approx0.4\,\rmn{Gyr}$, where the small dip at large
+with $\tau_{\rm D}\approx0.4\,\rmn{Gyr}$, where the small dip at large
 radius driven by the decrease in thermal energy density. The
 \Mflatturb model has the the flattest turbulent profile parameterized
-by the smaller $\alpha_\rmn{tu}$ which explains the steepest $\tau_D$
+by the smaller $\alpha_\rmn{tu}$ which explains the steepest $\tau_{\rm D}$
 profile. Note that a fixed reacceleration timescale is required to
@@
 lowering the level of turbulence or increasing the physical injection
-scale of turbulence to keep $\tau_D$ constant.
+scale of turbulence to keep $\tau_{\rm D}$ constant.
 
@@
     cluster g72a. We show in linear-log the reacceleration timescale
-    ($\tau_D$) as a function of radius $R$ for our three models:
+    ($\tau_{\rm D}$) as a function of radius $R$ for our three models:
     \Mprimary (green dotted line), \Mstream (blue dashed line), and
@@
 energy contained in turbulence, $X_{\rm tu}$ (defined by $E_{\rm
-  therm} = X_{\rm tu} E_{\rm therm}$), the spatial profile of
+  turb} = X_{\rm tu} E_{\rm th}$), the spatial profile of
 turbulence as parametrized by $\alpha_{\rm tu}$ (defined by $I_0
-\propto \epsilon_{\rm therm}^{\alpha_{\rm tu}}$, where $I_0^{} \propto
+\propto \epsilon_{\rm th}^{\alpha_{\rm tu}}$, where $I_0^{} \propto
 \varv_0^{3} k_0^{}$ is the injection rate of turbulence), as well as
@@
 by about a factor of 10 in comparison to the cumulative CR energy
-injected over the entire cosmological history of the cluster. \AP{So why can't we just neglect the population injected during the merger?}  
+injected over the entire cosmological history of the cluster.
+\AP{So why can't we just neglect the population injected during the merger?
+-- Above ~ 1 GHz the radio emission is dominated by the CRes injected during the merger.
+The reason for this is that this population have not had time to cool significantly yet.
+Otherwise the radio spectrum would be more curved.}
 Similarly, the initial CRe distribution is given by the steady state
@@
 %T)^{\alpha_\rmn{tu}}$. 
-\AP{Do we include injection by primaries, is it negligible?} 
-The diffusion constant $D_{pp} \propto X_{\rm tu}^{2} \eps_{\rm th}^{\alpha-1} \sqrt{T} k_{\rm 0}$ is calculated
-for each radial bin using Eqns.~\ref{eq:dpp}-\ref{eq:Gamma_e}. All
-parameters and assumptions are similar to what is used for our
-simulated cluster (see Sect.~\ref{sec:results}).
-Our fiducial model assumes $X_{\rm tu} = 0.2$, $\alpha_{\rm tu} =0.8$, $\alpha_{\rm CR, spat}=1.0$, and $k_{\rm 0}=2 \pi/\lambda_{\rm 0}$ where $\lambda_{\rm 0}=100$ kpc.
-We also assume a fixed acceleration time of $\tau_{\rm cl} = 650 \, {\rm Myr}$.
+\AP{Do we include injection by primaries, is it negligible? -- I did
+  not include it, because it is subdominant (at least for a
+  $K_{ep}=0.1$).}  The diffusion constant $D_{pp} \propto X_{\rm tu}^{2}
+\eps_{\rm th}^{\alpha-1} \sqrt{T} k_{\rm 0}$ is calculated for each
+radial bin using Eqns.~\ref{eq:dpp}-\ref{eq:Gamma_e}. All parameters
+and assumptions are similar to what is used for our simulated cluster
+(see Sect.~\ref{sec:results}). Our fiducial model assumes $X_{\rm tu}
+= 0.2$, $\alpha_{\rm tu} =0.8$, $\alpha_{\rm CR, spat}=1.0$, and
+$k_{\rm 0}=2 \pi/\lambda_{\rm 0}$ where $\lambda_{\rm 0}=100$ kpc. We
+also assume a fixed acceleration time of $\tau_{\rm cl} = 650 \, {\rm
+  Myr}$.
 
@@
 It can be understood as follows.
-The pre-acceleration electron distribution function can be understood as a result of competition between hadronic injection $f \propto p^{-\alpha_{\rm inj}}$ and cooling, which results in a quasi-steady state for the non-thermal (secondary) electrons.
+The pre-acceleration electron distribution function results from the competition between hadronic injection $f \propto p^{-\alpha_{\rm inj}}$ and cooling, which results in a quasi-steady state for the non-thermal (secondary) electrons.
 At low momenta, when the Coulomb cooling time is short, $f \propto p^{-\alpha_{\rm inj}+1}$, at high momenta, when inverse Compton/synchrotron cooling dominates, $f \propto p^{-\alpha_{\rm inj} -1}$.
 In between, there is a quasi-adiabatic regime where electrons accumulate (for more details, and an analytic self-similar solution, see \citealt{1999ApJ...520..529S, pinzke13}).
-In the absence of cooling, momentum advection in the limit $D_{pp} \propto p^{2}$ (so that $\tau =p^{2}/4 D_{pp}$ is momentum independent) simply shifts the distribution $f(p) \rightarrow f(A p)$.
+In the absence of cooling, momentum advection in the limit $D_{pp} \propto p^{2}$ (so that $\tau_\rmn{D} =p^{2}/4 D_{pp}$ is momentum independent) simply shifts the distribution $f(p) \rightarrow f(A p)$.
 When the acceleration efficiency is low, most observable emission corresponds to the power-law tail of the distribution function $f \propto p^{-\alpha_{\rm inj}-1}$ set by the balance between injection and synchrotron/IC cooling.
@@
 This can be only be understood if the timescale over which acceleration takes place $\tau_{\rm cl}$ also depends on the properties of turbulence, so that the the ratio $\tau_{\rm D}/\tau_{\rm cl}$ has relatively little scatter.
-We discuss one such scenario in \S\ref{sec:reacc}, but this point clearly deserves more work.
+We address this next.
+%We discuss one such scenario in \S\ref{sec:reacc}, but this point clearly deserves more work.
+
+\subsection{Self-Limiting Turbulent Reacceleration}
+
+There are 3 important timescales in this problem: the acceleration time $\tau_{\rm D}$, the duration that turbulence is active and acceleration takes place, $\tau_{\rm cl}$, and the cooling time $\tau_{\rm cool}(p)$.
+Only $\tau_{\rm cool}(p)$ is momentum dependent (and is different for ions and electrons).
+Thus, the outcome of acceleration depends essentially on two dimensionless numbers, $\tau_{\rm cl}/\tau_{\rm D}$, and $\tau_{\rm cool}/\tau_{\rm D}$.
+
+We have seen that the radio luminosity depends very sensitively on $\tau_{\rm cl}/\tau_{\rm D}$, through the very sensitive dependence on $X_{\rm tu}$ (Fig \ref{fig:param_comp}; note from equation \ref{eq:Dpp_scaling} that $\tau_{\rm D} \propto X_{\rm tu}^{-2}$).
+Since this raises questions of fine-tuning in $X_{\rm tu}$ to explain the observations, it is worth understanding in more detail.
+Let us ignore cooling.
+This is a good approximation for the CR protons, for instance, since hadronic cooling times are long\footnote{In principle, CRp can still lose energy via wave heating, at a rate $v_{\rm A} \cdot \nabla P_{c}$, but we assume CR streaming is suppressed during mergers, when they are spatially confined by scattering.} In this case, $\dot{p}= p/\tau_{\rm D}$, and after a time $\tau_{\rm cl}$, we have $p \rightarrow p \, {\rm exp}(\tau_{\rm cl}/\tau_{\rm D})$ (where we have used the fact that $\tau{\rm D}$ is momentum independent).
+For an initial power law distribution function $f(p) = C p^{-\alpha}$, this momentum increase can be rewritten as a change of normalization, $f(p) = \tilde{C} p^{-\alpha}$, where $\tilde{C} = {\rm exp}( \alpha \tau_{\rm cl}/\tau_{\rm D})$.
+A slightly more careful derivation by direct solution of the Fokker-Planck equation yields:
+\begin{equation}
+  \dot{f} = {{\partial }\over{\partial p}}
+  p^2 D_{pp} {{\partial }\over{\partial p}} \frac{f}{p^2}\,,
+\end{equation}
+with the analytic solution given by
+\begin{equation}
+  \label{eq:Creacc}
+  \tilde{C}= 
+  C \exp{\left[\frac{(2+\alpha)(\alpha-1)}{4}\frac{\tau_\rmn{cl}}{\tau_\rmn{D}}\right]}\,.
+\end{equation}
+This exponential sensitivity to $\tau_{\rm cl}/\tau_{\rm D}$ lies behind the extreme sensitivity to $X_{\rm tu}$ in Fig \ref{fig:param_comp}.
+
+The only way around this is for $\tau_{\rm cl}$ and $\tau_{\rm D}$ to be somehow related.
+There are two possible limits.
+Let us suppose that the timescale on which there exists a source of turbulent driving is $\tau_{\rm drive}$, which is roughly the timescale of the merger, or the dynamical time.
+Let the turbulence decay on a timescale $\tau_{\rm decay}$.
+If $\tau_{\rm drive} > \tau_{\rm decay}$, then $\tau_{\rm cl} \sim \tau_{\rm drive}$, which depends on the details of the merger and should result in considerable scatter in $\tau_{\rm cl}/\tau_{\rm D}$ in different systems.
+On the other hand, if $\tau_{\rm decay} > \tau_{\rm drive}$, then $\tau_{\rm cl} \sim \tau_{\rm decay}$.
+Since $\tau_{\rm D}$ and $\tau_{\rm decay}$ are both related to properties of the turbulence, it is conceivable that this would result in much less scatter in $\tau_{\rm cl}/\tau_{\rm D}$.
+
+An obvious candidate for $\tau_{\rm decay}$ is: 
+\begin{equation}
+\tau_{\rm edd} = \frac{L}{v_{\rm c}}
+\end{equation}
+i.e., the eddy turnover time at the outer scale.
+This is subject to uncertainties about the location of the outer scale $L$; estimates in the literature range from $L \sim 0.1-1$ Mpc.
+It is also worth remembering that MHD turbulence only applies below $l < l_{\rm A}$, where $l_{\rm A}$ is the Alfv{\'e}n scale where $v \sim v_{\rm A}$.
+Invoking fast modes, Kraichnan scalings, etc, is only valid below these scales.
+For $l > l_{\rm A}$, turbulence is basically hydrodynamic and Kolmogorov in nature.
+The momentum diffusion coefficient can thus be split up into two components:
+\begin{equation}
+D_{\rm pp} = D_{\rm pp}^{\rm HD}[l_{\rm A} < l < L] + D_{\rm pp}^{\rm MHD}[l_{\rm c} < l < l_{\rm A}]
+\end{equation}
+From equations (\ref{eqn:diffusion}) and (\ref{eqn:k_W}), and assuming Kolmogorov turbulence from $l_{\rm A} < l < L$ and Kraichnan turbulence from $l_{\rm c} < l < l_{\rm A}$, we get: 
+\begin{equation}
+\frac{D_{\rm pp}^{\rm HD}}{D_{\rm pp}^{\rm MHD}} = \frac{k_{\rm L}^{2/3}k_{\rm A}^{1/3} v_{\rm c}^{2}}{k_{\rm A}^{1/2}k_{\rm c}^{1/2} v_{\rm A}^{2}} = A^{-1/2} \beta = 0.5 \left( \frac{\beta}{50} \right)
+\end{equation}
+where we have used $k_{\rm A} = k_{\rm L} M_{A}^{3}$ (from Kolmogorov scalings, and $M_{\rm A} = v_{\rm c}/v_{\rm A}$ is the Alfv{\'e}n Mach number of the turbulence, $\beta \approx c_{\rm s}^{2}/v_{\rm A}^{2}$, and the cutoff scale \citep{brunetti07,miniati15}:
+\begin{equation}
+k_{\rm c} \approx A k_{\rm outer} \frac{\langle v_{\rm outer}^{2}\rangle^{2}}{c_{\rm s}^{4}}
+\label{eqn:k_c} 
+\end{equation}
+where $A \approx 11000$.
+Thus, the contribution of the two regimes are comparable (as we shall see later, this is not true if one incorrectly assumes Kraichnan scalings apply from the outer scale $L$; this boosts the contribution of the scales where $l_{\rm A} < l < L$ by a factor $M_{\rm A}^{1/2}$).
+
+Henceforth, we can consider the outer scale of the fast modes to be $l_{\rm A}$, with velocity $v_{\rm A}$. The turbulent reacceleration time is: 
+\begin{equation}
+\tau_{\rm D} = \frac{p^{2}}{4 D_{\rm pp}} = C_{\rm D} A^{1/2} c k_{\rm A} \frac{v_{A}^{2}}{c_{\rm S}^{2}}
+\label{eqn:tau_D} 
+\end{equation}
+where $C_{\rm D} = 2/(5 \pi)$, $A\approx 11000$, and we have used equation \ref{eqn:k_c}.
+The turbulence decay time is given by the cascade time of fast modes (\citet{yan04}; see equation \ref{eqn:cascade}):
+\begin{equation}
+\tau_{\rm decay} = \frac{c_{\rm s}}{v_{\rm A}^{2} k_{\rm A}}\,.
+\label{eqn:tau_decay} 
+\end{equation} 
+This can be related to the eddy turnover time at the outer scale $\tau_{\rm edd}$ from $l_{\rm A} = L M_{\rm A}^{-3}$ to: 
+\begin{equation}
+\tau_{\rm decay} =\frac{L}{v_{\rm c}} \left(\frac{c_{\rm s}}{v_{\rm c}} \right)^{2} \frac{v_{\rm A}}{c_{\rm s}} = 0.7 \, \tau_{\rm edd} \left(\frac{\tilde{X}_{\rm tu}}{0.2}\right)^{-1}  \left(\frac{\beta}{100} \right)^{-1/2}
+\end{equation}
+where we have used $\tilde{X}_{\rm tu} \approx (v_{\rm c}/c_{\rm s})^{2}$ and $c_{\rm s}/v_{\rm A} = \beta^{1/2}$.
+Thus $\tau_{\rm decay} \sim \tau_{\rm edd}$, but we prefer to use the expression for $\tau_{\rm edd}$, since it is more physically correct and leads to more revealing scalings.
+
+From equations \ref{eqn:tau_D} and \ref{eqn:tau_decay}, we obtain:
+\begin{equation}
+\frac{\tau_{\rm cl}}{\tau_{\rm D}} \approx \frac{\tau_{\rm decay}}{\tau_{\rm D}} = 0.1 \left( \frac{c_{\rm s}}{1500 \, {\rm km \, s^{-1}}} \right) \left( \frac{\beta}{50} \right)^{-1}\,. 
+\label{eqn:ratios_TTD} 
+\end{equation}
+Remarkably, this expression is independent of properties of the turbulence such as $v_{\rm c},L$, or $l_{\rm A}$, and depends only on properties of the plasma ($c_{\rm s},\beta$).
+Ultimately, this arises because the timescale on which a fast mode wave transfers energy due to wave particle interactions in second order Fermi acceleration, $\tau_{\rm p} \sim (k_{\rm p} c (v_{\rm c}/c)^{2} )^{-1}$, is closely related to the timescale on which it cascades due to wave-wave interactions, $\tau_{\rm w} \sim c_{\rm s}/(k_{\rm w} v_{\rm c}^{2})$.
+This implies $\tau_{\rm w}/\tau_{\rm p} \sim (c_{s}/c)(l_{\rm w}/l_{\rm p})$, where $l_{\rm w} \sim l_{\rm A}$ is the outer scale on which the fast mode cascade begins, and $l_{\rm p} \sim (l_{\rm A} l_{\rm c})^{1/2}$ is the characteristic wavelength for wave-particle interactions.
+For transit time damping and an outer scale of $l_{\rm A}$, we have $l_{\rm c} \sim (m_{\rm e}/m_{\rm p}) l_{\rm A} (c_{\rm s}/v_{\rm A})^{4}$.
+We thus have $\tau_{\rm w}/\tau_{\rm p} \sim (c_{\rm s}/c)(l_{\rm A}/l_{\rm c})^{1/2} \sim (c_{\rm s}/c) (m_{\rm p}/m_{\rm e})^{1/2} \beta^{-1}$.
+More careful consideration of dimensionless factors boosts this estimate by an order of magnitude to give equation \ref{eqn:ratios_TTD}.
+
+On the other hand, equation \ref{eqn:ratios_TTD} points toward a pessimistic scenario where turbulent reacceleration with TTD on thermal particles is never effective.
+A key reason is that we assume Kraichnan turbulence only applies for $l< l_{\rm A}$.
+There is then insufficient separation of scales: the cutoff scale $l_{\rm c} \sim 0.2 \beta_{\rm 50}^{2} l_{\rm A}$.
+Although there is a fair large separation of scales between the outer driving scale $L$ and $l_{\rm A} = L M_{\rm A}^{-3}$ (a factor of $30-1000$ for $M_{\rm A} \approx 3-10$; we have $M_{\rm A} \sim (\tilde{X}_{\rm tu} \beta)^{1/2} \sim 3.2$ for our fiducial assumptions), Kolmogorov turbulence, with its steeper spectrum, has more energy at large scales ($k W(k) \propto k^{-2/3}, k^{-1/2}$ for Kolmogorov and Kraichnan turbulence respectively).
+This implies that the energy-weighted scales at which wave-particle interaction take place are larger in Kolmogorov turbulence, and thus that the wave-particle interaction rate is lower.
+If (as is frequently seen) we instead assume that Kraichnan turbulence begins at the outer scale $L$, with characteristic decay time $L c_{\rm s}/v_{\rm c}^{2}$, then we obtain a more platable result:
+\begin{equation}
+\frac{\tau_{\rm cl}}{\tau_{\rm D}} \approx 0.8  \left( \frac{c_{\rm s}}{1500 \, {\rm km \, s^{-1}}} \right) \left( \frac{\tilde{X}_{\rm tu}}{0.2} \right). 
+\end{equation}
+This arises because the decay time is now $\sim M_{\rm A}$ times longer, and the acceleration time is now $\sim M_{\rm A}^{1/2}$ times shorter, boosting $\tau_{\rm cl}/\tau_{\rm D}$ by $\sim M_{\rm A}^{3/2}$.
+However, as we have argued, turbulence in the hydrodynamic regime $l_{\rm A} < l < L$ is Kolmogorov, not Kraichnan.
+Furthermore, if this scaling is somehow correct, then this leaves us with the problematic exponential sensitivity to $X_{\rm tu}$ that we previously explored.
+
+One alternative is that scattering in the high $\beta$ ICM is mediated by plasma instabilities (firehose, mirror) rather than Coulomb scattering.
+This vastly increases the scattering rate and reduces the mean free path of thermal particles.
+In this case, the fast modes damp by TTD on relativistic rather than thermal particles.
+The momentum diffusion coefficient in this case is then \citep{brunetti11, miniati15}:
+\begin{equation}
+D_{\rm pp}^{\rm CR} = \frac{2 p^{2} \zeta}{x_{\rm CR}} k_{\rm L} \frac{\langle v_{\rm c}^{2} \rangle^{2}}{c_{\rm s}^{3}}
+\end{equation}
+where $\zeta$ is an efficiency factor for the the effectiveness of plasma instabilities (e.g., due to spatial or temporal intermittency), and $x_{\rm CR}=\epsilon_{\rm CR}/\epsilon_{\rm th}$ is the relative energy density of cosmic rays.
+If we set $k_{\rm L} \rightarrow k_{\rm A}$, $v_{c}^{2} \rightarrow v_{\rm A}^{2}$, as before, then:
+\begin{equation}
+\frac{\tau_{\rm cl}}{\tau_{\rm D}} \approx 8 \frac{\zeta}{\beta x_{\rm CR}}
+\end{equation}
+In principle, this implies exponential sensitivity to $x_{\rm CR}$, a similar situation as exponential sensitivity to $X_{\rm tu}$.
+However, there is a self-limiting asymptotic behaviour: as $x_{\rm CR}$ increases due to turbulent reacceleration, damping increases, which limits the further growth of the cosmic ray energy density \citep{brunetti11}.
+One natural assumption is to assume that $\epsilon_{\rm CR}$ saturates at a level $\epsilon_{\rm CR} \sim \epsilon_{\rm turb} (MHD) \sim \epsilon_{\rm B}$, in which case $x_{\rm CR} \sim \beta^{-1}$, so that:
+\begin{equation}
+\frac{\tau_{\rm cl}}{\tau_{\rm D}} \approx 1.6 \left(\frac{\zeta}{0.2}\right)\,.
+\end{equation}
+Given the host of uncertain factors which enter into $\zeta < 1$ (the intermittent nature of turbulence, small scale magnetic topology and the efficiency with which instabilities mediated by pressure anisotropies are triggered), this is potential consistent with $\tau_{\rm cl} \sim \tau_{\rm D}$.
+This promising scenario should be investigated in more detail.
+
+STUFF ABOUT BURGERS TURBULENCE
+
+STUFF ABOUT FIGURE--LESS SENSITIVE TO PROPERTIES OF TURBULENCE, MIGHT BE ABLE TO PROBE SEED POPULATION 
+\begin{figure*}
+\begin{minipage}{1\columnwidth}
+   \begin{center}\Large{radio profiles}\\
+     \includegraphics[width=\columnwidth]{tcltD.prof.comp.KrTTDth.Xtu.eps}
+   \end{center}
+\end{minipage}
+\begin{minipage}{1\columnwidth}
+   \begin{center}\Large{radio spectra}\\
+     \includegraphics[width=\columnwidth]{tcltD.spec.comp.KrTTDth.Xtu.eps}
+   \end{center}
+\end{minipage}
+\\
+\begin{minipage}{1\columnwidth}
+  \begin{center}%\Large{\Mflatturb:}\\ 
+    \includegraphics[width=\columnwidth]{tcltD.prof.comp.KrTTDth.aI0.eps}
+  \end{center}
+\end{minipage}
+\begin{minipage}{1\columnwidth}
+   \begin{center}%\Large{\it Brunetti et al. (2012)}:\\
+     \includegraphics[width=\columnwidth]{tcltD.spec.comp.KrTTDth.aI0.eps}
+   \end{center}
+\end{minipage}
+\\
+\begin{minipage}{1\columnwidth}
+  \begin{center}%\Large{\Mflatturb:}\\ 
+    \includegraphics[width=\columnwidth]{tcltD.prof.comp.KrTTDth.aCR.eps}
+  \end{center}
+\end{minipage}
+\begin{minipage}{1\columnwidth}
+   \begin{center}%\Large{\it Brunetti et al. (2012)}:\\
+     \includegraphics[width=\columnwidth]{tcltD.spec.comp.KrTTDth.aCR.eps}
+   \end{center}
+\end{minipage}
+\caption{Sensitivity of radio emission in Coma cluster to critical
+  parameters. For details see caption in
+  Fig.~\ref{fig:param_comp}. For simplicity, we assume that the
+  duration of reacceleration $\tau_{cl}=\tau_{\rm D}$, where $\tau_{\rm
+    D}$ is the acceleration time of particles due to turbulence. In
+  this scenario the radio profiles are mainly determined from the CRs,
+  while the turbulence have minor impact. Interestingly, flat CR
+  profiles similar to those produced through CR streaming is needed in
+  order to reproduce the radio profiles.}
+  \label{fig:param_comp_tcl_tD}
+\end{figure*}
 
@@
 
-Given our seed electron population (which includes both primaries generated by DSA and secondary electrons created by CRp in hadronic interactions; for standard assumptions, the latter dominates), we find that applying the standard model previously used to reproduce Coma's radio halo properties \citep{brunetti11}, in which $\eps_{\rm turb} \propto \eps_{\rm therm}$, fails: it produces radio emission which is too centrally concentrated.
+Given our seed electron population (which includes both primaries generated by DSA and secondary electrons created by CRp in hadronic interactions; for standard assumptions, the latter dominates), we find that applying the standard model previously used to reproduce Coma's radio halo properties \citep{brunetti11}, in which $\eps_{\rm turb} \propto \eps_{\rm th}$, fails: it produces radio emission which is too centrally concentrated.
 Indeed, \citet{brunetti11} remark in their paper that the CR population required in their model is remarkably flat.
@@
 $L_{\nu}$--$L_{\rm X}$) are so tight. Previous statistical modeling of radio
-halo populations \citep{2006MNRAS.369.1577C,2007MNRAS.378.1565C} have focussed
+halo populations \citep{2006MNRAS.369.1577C,2007MNRAS.378.1565C} have focused
 on matching the mean relations, but not the scatter. We believe the latter

### 2016-05-30 paper.tex
Add files via upload

@@
 \definecolor{mygreen}{rgb}{0.,0.5,0.}
-\def\del#1{{}}
-%\def\del#1{{\bf (DELETED TEXT)}}
-\def\C#1{{\bf #1}}
-\def\AP2#1{{\bf  AP2: #1}}
-\def\AP#1{{\bf {\color{blue} AP: #1}}}
-\def\SPO#1{{\bf {\color{red} SPO: #1}}}
-\def\CP#1{{\bf {\color{mygreen} CP: #1}}}
 
@@
   relativistic electrons by compressible turbulence in the
-  intracluster medium (ICM); Coulomb losses prohibit acceleration from
-  the thermal pool. However, the origin of seed electrons has never
+  intracluster medium (ICM). The origin of these seed electrons has never
   been fully explored. Here, we integrate the Fokker-Planck equation
   of the cosmic ray (CR) electron and proton distributions in
-  cosmological simulations of cluster formation. For standard
+  cosmological simulations of cluster formation, and confront them with radio surface brightness and spectral observations of Coma. For standard
   assumptions, structure formation shocks lead to a seed electron
   population which produces too centrally concentrated radio
-  emission. Instead, we present three plausible scenarios for the seed
-  CRs that each can reproduce the spatially flat radio emission
-  observed in the Coma cluster. (1) The CR proton-to-electron
-  acceleration efficiency $K_\rmn{ep} \sim 0.1$ is assumed to be
-  larger than in our Galaxy ($K_\rmn{ep} \sim 10^{-2}$), due to the
-  magnetic geometry at the shock. The resulting primary electrons
-  dominate the radio emission, which is more extended in comparison to
-  radio emission from secondary electrons that result from hadronic CR
-  interactions in the ICM. (2) CR protons may stream at the Alfv{\'e}n
-  speed to the cluster outskirts when the ICM is relatively
-  quiescent. A spatially flat CR proton distribution develops and
-  produces the required population of secondary seed electrons. (3)
-  The ratio of injected turbulent-to-thermal energy density increases
-  significantly with radius, as seen in cosmological simulations. This
-  generates a flat radio profile when CRs are reaccelerated even if
-  the seed population of CRs is steep with radius. These competing
-  non-trivial solutions provide incisive probes of non thermal
-  processes in the high-$\beta$ ICM.
+  emission.
+By modifying properties of the CR population (rapid streaming; enhanced CR electron acceleration at shocks) or turbulence (increasing $\eps_{\rm turb}/\eps_{\rm therm}$ with radius), we can match observations, but only at the expense of fine-tuning.
+We then perform a parameter study.
+Under naive assumptions, radio properties are exponentially sensitive to the amplitude of turbulence, which is inconsistent with small scatter in scaling relations.
+This sensitivity can be removed if we relate the acceleration time to the turbulent dissipation time.
+Their ratio depends only on plasma parameters.
+In this case, turbulence above a threshold value required to overcome cooling provides a fixed amount of amplification; observations could then potentially constrain the unknown CR seed population.
+Understanding the small scatter in radio halo scaling relations may prove a rich source of insight on plasma processes in the ICM.
 \end{abstract}
@@
 model diffusive shock acceleration at structure formation shocks,
-account for various loss processes of CRs, and -- most importantly --
-model second-order Fermi acceleration by CR interactions with
-magnetised turbulence.
-
-However, we assume a simplified and stationary model for magnetic
+and account for various loss processes of CRs. Utilizing new insights from our recent work on DSA generated
+  fossil electrons \citep{pinzke13}, we generate the first
+  quantitative calculation of primary and secondary seed electrons
+
+To compare this to observations, we model second-order Fermi acceleration by CR interactions with
+magnetised turbulence. However, we assume a simplified and stationary model for magnetic
 fields and turbulence. We do not account for the time-varying energy
@@
 time-dependent compressible turbulence while adopting a simplified
-treatment of CR that does not follow the transport of the CR
-distribution function. Our approach of parametrizing turbulence
-enables us to vary parameters associated with the unknown continuation
-of magneto-hydrodynamical (MHD) turbulence below the MHD scale and the
+treatment of CR. Our approach of parametrizing turbulence
+enables us to vary parameters associated with the spatial profile and the
 overall amplitude of compressible waves (that can in principle vary
@@
 
-In this paper we consider three new scenarios that
-individually or combined can reproduce the observed radio profiles and
-spectrum in the Coma cluster without violating gamma-ray constraints:
-\begin{enumerate}
-\item {\bf Model {\em M-primaries}.} If the acceleration efficiency of CRps is below
-  about $0.1$~{\%} in weak (perpendicular) shocks and the ratio of injected
-  electrons-to-protons $K_{\rmn{ep}} \sim 0.1$, this yields a dominant primary
-  population with a flat spatial distribution, since primaries have a weaker
-  density dependence than secondaries.
-\item {\bf Model {\em M-streaming}.} Here, we account for streaming CRps that
-  produce flat distributions of CRps in the ICM
-  \citep{ensslin11,wiener13,2014MNRAS.438..124Z}, which also flattens the
-  secondary electron distribution.
-\item {\bf Model {\em M-turbulence}.} Here, we adopt a spatially
-  flatter turbulent profile than what was adopted in \citet{brunetti12},
-  but where seed CRps follow the steep profile that is suggested by
-  structure formation simulations.
-\end{enumerate}
-
-\AP{In section~\ref{sec:results} we pursue these three possibilities
-  further and employ cosmological simulations of CRs in clusters. In
-  tandem with new insights from our recent work on DSA generated
-  fossil electrons \citep{pinzke13}, we generate the first
-  quantitative calculation of primary and secondary seed electrons and
-  compare to observations in the Coma cluster. For the most part, we
-  adopt parameters that are used in previous work, including Fermi-II
-  acceleration with models of turbulent spectra
-  \citep{brunetti07,brunetti11}, injection scale of turbulence
-  \citep{miniati15}, the energy density of turbulence
-  \citep{2009ApJ...705.1129L,2010ApJ...725.1452S,2011A&A...529A..17V},
-  for CR acceleration in shocks \citep[][in particular $K_{\rmn{ep}}$
-    and the acceleration efficiency]{pinzke13}, and for cosmological
-  simulations with CR physics \citep[][i.e., shock history,
-    temperature profile, density profile, magnetic field
-    profile]{pinzke10}. All these parameters are uncertain, and could
-  potentially change our predictions. In section~\ref{sect:param_comp}
-  we adopt a simplified spherical framework for our reacceleration
-  model of secondary electrons. We perform a small parameter study and
-  explore how radio emission depends on the parameters describing the
-  spatial profile of CR protons and turbulence. In
-  section~\ref{sect:param_comp} we discuss our results and present our
-  conclusions.} \sout{We refer the reader to
-  section~\ref{sect:param_comp} for a first exploration of parameter
-  space, however} We leave the detailed exploration of parameter space
-and the interaction between free parameters to future work.
+In this paper, we explore how the radio surface brightness profile and spectrum of the best known radio halo, Coma, can be used to constrain the underlying properties of the seed cosmic rays and turbulence.
+We aim to constrain the normalization and spatial profile of these two input ingredients in turbulent reacceleration models.
+The outline of this paper is as follows.
+In \S\ref{sect:method}, we outline the basic physics of turbulence reacceleration of cosmic rays which we use.
+In \S\ref{sec:results}, we use cosmological simulations to generate a seed CR population, and combine it with our parameterized model of turbulence to produce radio surface brightness profiles and spectra of Coma.
+We find that it is possible to fit the observations using physically motivated modifications of the seed population
+(rapid streaming; enhanced CR electron acceleration at shocks) or turbulence (increasing $\eps_{\rm turb}/\eps_{\rm therm}$ with radius), but only at the expense of fine tuning.
+In \S\ref{sect:param_comp}, we explore the reason for this fine-tuning, and seek ways to overcome it.
+We perform a parameter study on spherically symmetric, static models where we vary properties of the seed population and turbulence.
+We find exponential sensitivity to the amount of turbulent, which can be eliminated if the turbulent acceleration and dissipation time are linked.
+In this case, turbulence above a threshold value required to overcome cooling provides a fixed amount of amplification; observations could then potentially constrain the unknown CR seed population.
+We summarize and conclude in \S\ref{sec:conclusions}.
 
@@
 \section{Cosmic ray transport}
+\label{sect:method}
 
@@
 Fermi-LAT upper limits
-\citep{2012ApJ...757..123A,brunetti12,2014ApJ...787...18A}. However,
-if CRps stream in the ICM, then their spatial profile could
-potentially flatten sufficiently \citep{ensslin11,wiener13}. This
-scenario is very attractive: it generates seed electrons with the
-right spatial footprint, and by removing CRps from the core, obeys
-gamma-ray constraints. Turbulence plays two opposing roles:
-Alfv{\'e}nic turbulence damps waves generated by the CR streaming
-instability \citep{yan02,farmer04}, thus reducing self-confinement;
-but compressible fast modes scatter CRs directly. Turbulent damping is
-still efficient for highly subsonic conditions \citep{wiener13}, while
-we assume compressible fast modes to only provide effective spatial
-confinement during the periods of transonic, highly super-Alfv{\'e}nic
-($M_{\rm A} \sim 5$) turbulence associated with mergers. Thus, CRs can
-stream out when the cluster is kinematically quiescent. Furthermore,
-even Alfv{\'e}nic streaming timescales are relatively short
-\cite[$\sim 0.1-0.5$ Gyr;][]{wiener13} compared to the timescale on
-which the CRp population is built up. Based on these findings, we
-adopt a toy model for our \Mstream scenario in which CR streaming
-instantaneously produces flat CRp profiles.
+\citep{2012ApJ...757..123A,brunetti12,2014ApJ...787...18A}.
 
@@
 \nonumber\\
-&-& \left.\left.{1\over{p^2}}{{\partial }\over{\partial p}}\left(p^2 D_{pp}\right) 
+&-& \left.\left.{1\over{p^2}}{{\partial }\over{\partial p}}\left(p^2 D_{\rm pp}\right) 
 \right]\right\} - \left(\bnabla\bcdot \bvel\right) f_{\rmn{e}}(p,t)
@@
 \left[
-D_{pp} f_{\rmn{e}}(p,t) \right]+ Q_{\rmn{e}}\left[p,t;f_{\rmn{p}}(p,t)\right]   \, .
+D_{\rm pp} f_{\rmn{e}}(p,t) \right]+ Q_{\rmn{e}}\left[p,t;f_{\rmn{p}}(p,t)\right]   \, .
 \label{elettroni}
@@
 B_\rmn{CMB}$, the CRes loose virtually all their energy by means of
-inverse Compton emission. $D_{pp}$ is the momentum space diffusion
-coefficient (see Sects.~\ref{sec:dummy} and \ref{sec:reacc}), and
+inverse Compton emission. $D_{\rm pp}$ is the momentum space diffusion
+coefficient (see \S\ref{sec:reacc}), and
 $Q_{\rmn{e}}$ denotes the injection rate of primary and secondary
@@
 0. The simulated cluster undergoes a major merger over the last
-1-2~Gyrs that is thought to inject large turbulent eddies. Following
-standard approaches
-\citep{brunetti07,brunetti11,2004ApJ...614..757Y,miniati15}
+1-2~Gyrs that is thought to inject large turbulent eddies. As is commonly assumed \citep{brunetti07,brunetti11,2004ApJ...614..757Y,2013ApJ...771..131B}
 we assume that about one Gyr after core passage the fields have
-decayed down to the smallest scales where reacceleration is most
-efficient ($D_{pp}\sim k_\rmn{cut}$) and the radio halo turns on
-shortly after. Note that the exact decay time of the turbulens is of
-minor importance, since the thermal and CR quantities are very similar
-a few 100 Myrs before and after $z=0$ where we have chosen to evaluate
-the simulations. This delay naturally explains why giant radio halos
-are only seen in a fraction of all merging clusters.
-
+decayed down to the smallest scales $k_{\rm cut}$, and the radio halo turns on
+shortly after. We choose this simulation snapshot to analyze. We are not very sensitive to this assumption, since the thermal and CR quantities are very similar a few
+100 Myrs before and after z = 0, where we have chosen to evaluate the
+simulations. In all our
+calculations we assume that turbulent reacceleration efficiently
+accelerates particles for $\tau{\rm cl} \sim 650$ Myrs (which is roughly the cascade
+time on which turbulence is damped) and that during this turbulent
+phase CR streaming and spatial diffusion can be neglected. In \S\ref{sect:self-limiting}, we explore sensitivity to the last assumption.
+
+Thus far, we have ignore CR transport. However, if CRps stream in the ICM, then their spatial profile could
+potentially flatten sufficiently \citep{ensslin11,wiener13}. This
+scenario is very attractive: it generates seed electrons with the
+right spatial footprint, and by removing CRps from the core, obeys
+gamma-ray constraints. Turbulence plays two opposing roles:
+Alfv{\'e}nic turbulence damps waves generated by the CR streaming
+instability \citep{yan02,farmer04}, thus reducing self-confinement;
+but compressible fast modes scatter CRs directly. Turbulent damping is
+still efficient for highly subsonic conditions \citep{wiener13}, while
+we assume compressible fast modes to only provide effective spatial
+confinement during the periods of transonic, highly super-Alfv{\'e}nic
+($M_{\rm A} \sim 5$) turbulence associated with mergers. Thus, CRs can
+stream out when the cluster is kinematically quiescent. Furthermore,
+even Alfv{\'e}nic streaming timescales are relatively short
+\cite[$\sim 0.1-0.5$ Gyr;][]{wiener13} compared to the timescale on
+which the CRp population is built up. Based on these findings, we
+adopt a toy model for our \Mstream scenario in which CR streaming
+instantaneously produces flat CRp profiles. We assume that CRs cannot stream significantly past
+perpendicular $B$-fields at the accretion shock, so that the total
+number of CRs is conserved within the virial radius during the
+streaming process.
 In all our calculations we assume that turbulent reacceleration
@@
 that during this turbulent phase CR streaming and spatial diffusion
-can be neglected. In our \Mstream model, CR streaming and diffusion
-are incorporated separately during kinematically quiescent times that
-precede the merger. As a result, flat CRp profiles are produced on
-relatively short timescales ($\sim 0.1-0.5$ Gyr). This allows us to
-implicitly solve for CR streaming in our calculations, where we adopt
-a toy model that enforce a flat CRp profile at all quiescent times
-\citep{wiener13}. We assume that CRs cannot stream significantly past
-perpendicular $B$-fields at the accretion shock, so that the total
-number of CRs is conserved within the virial radius during the
-streaming process. Finally, since streaming is much more efficient for
-the CRps, we can ignore this effect for the CRes.
+can be neglected.
 
@@
 \nonumber\\
-&&-\left.\left. {1\over{p^2}}{{\partial }\over{\partial p}}\left(p^2 D_{pp}\right)
+&&-\left.\left. {1\over{p^2}}{{\partial }\over{\partial p}}\left(p^2 D_{\rm pp}\right)
 \right]\right\} - f_{\rmn{p}}(p,t) \bnabla\bcdot \left(\bvel+\bvel_{\rmn{st}}\right) 
@@
 &&+\,\,\, {{\partial^2 }\over{\partial p^2}}
-\left[ D_{pp} f_{\rmn{p}}(p,t) \right] - {{f_{\rmn{p}}(p,t)}\over{\tau_{\rm had}(p)}}
+\left[ D_{\rm pp} f_{\rmn{p}}(p,t) \right] - {{f_{\rmn{p}}(p,t)}\over{\tau_{\rm had}(p)}}
 + Q_{\rmn{p}}(p,t)\, ,
@@
 
-\subsection{Physical picture of reacceleration}
-\label{sec:dummy}
-
-All of the physics of turbulent reacceleration is effectively encapsulated in the diffusion coefficient, which can be rewritten as \citep{miniati15}:
-\begin{equation}
-D_{pp}(p) = \frac{ p^{2} \pi I_{\theta}(c_{s}/c)}{8 c} \langle k \rangle_{\mathcal{W}} \langle (\delta v_{\rm c})^{2} \rangle
-\label{eqn:diffusion}
-\end{equation}
-\SPO{define $I_{\theta}(c_{s}/c)$ or explain its meaning in words and point to the definition provided in the next subsection.}
-where
-\begin{equation}
-\langle k \rangle_{\mathcal{W}} = \frac{1}{\langle (\delta \varv_{\rm c})^{2} \rangle} \int_{k_{\rm L}}^{k_{\rm cut}} dk \, k \, \mathcal{W}(k) \approx \frac{s-1}{2-s} k_{\rm L} \left( \frac{k_{\rm cut}}{k_{\rm L}} \right)^{2-s}
-\label{eqn:k_W} 
-\end{equation}
-is an energy-averaged wavenumber, $k_{\rm L}, k_{\rm cut}$ are the wavenumbers associated with the outer scale and the cutoff scale respectively, and we have assumed a total energy spectrum (both kinetic and potential energy, where the two are assumed to be in equipartition \citep{sarkar11}):
-\begin{equation}
-\mathcal{W}(k) = \frac{(s-1) \langle (\delta \varv_{\rm c})^{2} \rangle}{k_{\rm L}} \left( \frac{k}{k_{\rm L}} \right)^{-s} 
-\label{eqn:Wk}
-\end{equation}
-which defines the normalization $\langle (\delta \varv_{\rm c})^{2} \rangle$ (the subscript 'c' emphasizes that we specialize to compressive modes).
-Intuitively, we can understand the form of the the diffusion coefficient from the fact that for second-order Fermi acceleration, $\dot{p} \sim \Delta p/\tau \sim p\,\langle k c \rangle_{\mathcal{W}} (\delta \varv_{\rm c}/c)^{2}$, where $\tau^{-1} \sim \langle k c \rangle_{\mathcal{W}}$ is the energy averaged wave-particle interaction rate, and $\Delta p \sim p (\delta \varv_{\rm c}/c)^{2}$ is the typical momentum change during wave particle scattering.
-Thus:
-\begin{equation}
-D_{pp} \sim p \dot{p} \sim p^{2} \langle k c \rangle_{\mathcal{W}} \left( \frac{\delta \varv_{\rm c}}{c} \right)^{2}. 
-\end{equation}
-
-Equations \ref{eqn:diffusion} and \ref{eqn:Wk} make the important aspects of turbulence clear: the energy in compressive modes $\langle (\delta v_{\rm c})^{2} \rangle$, the inner and outer scale ($k_{\rm cut}$ and $k_{\rm L}$), and the slope of the energy spectrum $s$.
-All of these can vary spatially and temporally.
-
-{\bf Energy in compressive modes} The total turbulence energy is typically $\sim 15-70\%$ of the thermal energy in a cluster \citep{vazza11}; it rises rapidly during a merger.
-The compressible component is $\sim 20-40\%$ of the total turbulent energy, and shows more rapid temporal variations compared to the compressible component \citep{2013ApJ...771..131B,miniati15}.
-It is worth noting that in the subsonic regime of the solar wind \citep{yao11,howes12}, as well as most idealized calculations of turbulent driving, there is relatively little energy in the fast mode.
-For instance, the fiducial simulations of \citet{lynn14} with a sonic Mach number ${\mathcal M}_{\rm s} \sim 0.35$ and a plasma beta factor of $\beta \sim 1$ show that 50\%, 45\%, 5\% of the turbulent energy density is in the Alfv{\'e}n, slow, and fast modes, respectively.
-For higher $\beta \sim 3-10$, they find that the proportion of energy in fast modes drops to $< 1\%$, while the fraction of energy in the slow mode remains roughly the same.
-Similarly, \citet{kowal10} find that the fast mode is highly subdominant (see their Table 2); for the run most relevant to cluster conditions ${\mathcal M}_{\rm s} \sim 0.7, \beta \sim 10$, they find $\sim 42\%, 6\%$ of turbulent energy in slow and fast modes respectively.
-These simulations are roughly consistent with theoretical estimates of $U_{\rm fast}/U_{\rm slow} \sim {\mathcal M}_{\rm s}^{2}/{\mathcal M}_{\rm A}$ \citep{cho03}.
-By contrast, MHD simulations of galaxy clusters find a large fraction ($\sim 25$\%) of turbulent energy in fast modes \citep{2013ApJ...771..131B}.
-This is likely due to the compressive nature of turbulent driving (transonic infall and merger), whereas idealized simulations tend to use incompressible solenoidal driving and allow compressive fluctuations to develop on their own.
-
-In the high-$\beta$, subsonic conditions of the ICM, the Alfv{\'e}n/slow modes are exactly/approximately incompressible, and so the approximate identification of compressive modes with fast modes is valid.
-We therefore take $\sim 25\%$ of the turbulent energy density in compressive fast modes as a reasonable baseline estimate \citep{2013ApJ...771..131B,miniati15}.
-If a large fraction of energy is in slow modes, then resonant broadening of wave-particle interactions can render slow modes an efficient acceleration mechanism \citep{lynn14}, as we discuss briefly in \S\ref{?}.
-
-{\bf Slope of the energy spectrum $s$.} At large scales, turbulent motions are subsonic (${\mathcal M}_{\rm s} \sim 0.2-0.5$) but super-Alfv{\'e}nic (${\mathcal M}_{\rm A} \sim 5$).
-Thus, except in the case where motions are transonic and weak shocks become important, motions are fundamentally hydrodynamic and turbulence follows a Kolmogorov ($s=5/3$) spectrum.
-However, while the turbulent energy density $U_{\rm t} \propto l^{2/3}$ decreases at small scales, the magnetic energy density is scale-independent.
-Thus, at some scale $l_{\rm A} \sim l_{\rm o} {\mathcal M}_{\rm A}^{-3}$, where $U_{\rm turb} \sim U_{B}$, the magnetic field becomes dynamically important, and turbulence transitions to the MHD regime.
-Theory \citep{goldreich95,chandran05} and simulations \citep{cho03} show that in the MHD regime, the Alfv{\'e}n and slow modes have a shallower Kraichnan spectrum ($s=3/2$), with relatively little coupling between the incompressible and compressible modes \citep{cho02,cho03} -- though if weak shocks are important, $s=2$ may be more appropriate (see discussion below).
-
-Since the Kraichnan spectrum is critical in what follows, it is worthwhile taking a moment to recount the origin of the spectral slope $s$ and the cascade rate.
-In the magnetically dominated regime, two counterpropagating wave packets of scale $l$ interact on an Alfv{\'e}n time $\tau_{\rm A}=l/\varv_{\rm A}$, rather than the eddy turnover time $\tau_{\rm edd} = l/\varv_{\rm l}$.
-Since $\tau_{\rm A} \ll \tau_{\rm edd}$, each interaction results in a small velocity change $\delta \varv_{\rm l} \sim \varv_{\rm l} (\tau_{\rm A}/\tau_{\rm edd})$.
-If these changes behave like a random walk, the cascade time $\tau_{\rm l}$ it takes for an eddy to become non-linear ($\Delta \varv \sim \varv_{\rm l})$ and cascade to smaller scales is $\varv_{\rm l} \sim \delta \varv_{\rm l} (\tau_{\rm l}/\tau_{\rm A})^{1/2} \sim \varv_{\rm l} \tau_{\rm A}/\tau_{\rm edd} (\tau_{\rm l}/\tau_{\rm A})^{1/2}$, which we can solve to obtain the cascade time:
-\begin{equation}
-\tau_{\rm l} \sim \left(\frac{\tau_{\rm edd}}{\tau_{\rm A}}\right)^{2} \tau_{\rm A} \sim \frac{l \varv_{\rm A}}{\varv_{\rm l}^{2}} 
-\label{eqn:cascade} 
-\end{equation}
-where we have implicitly assumed isotropy.
-This implies a dissipation rate $\epsilon \sim \varv_{\rm l}^{2}/\tau_{\rm l} \sim \varv_{\rm l}^{4}/(l \varv_{\rm A})$, or $\varv_{\rm l} \sim (\epsilon l \varv_{A})^{1/4}$.
-Thus, since $k E(k)\sim \varv_{\rm l}^{2}$, this gives a kinetic energy spectrum:
-\begin{equation}
-E(k) \sim (\epsilon \varv_{\rm A})^{1/2} k^{-3/2}.
-\end{equation}
-
-Finally, if turbulence is transonic ($M_{\rm s} \sim {\mathcal O}(1)$), then compressible modes can dissipate in weak shocks, as seen in decompositions of the velocity field into solenoidal/compressible components both in idealized simulations \citep{kowal10,porter15}, and cosmological hydrodynamic simulations \citep{miniati15}.
-The compressible component has a steep Burgers ($s=2$) spectrum.
-Burgers turbulence is distinct from other forms of turbulence in that it violates locality in k-space--i.e., power does not gradually cascade, but instead can directly jump from large to small scales via a network of weak shocks.
-Since the Fourier transform of a step function goes as $k^{-1}$, Burgers turbulence has a power spectrum of $P(k) \propto k^{-2}$.
-If we contrast the different velocity scalings: $\varv \propto l^{1/4}$ (Kraichnan), $\varv \propto l^{1/3}$ (Kolmogorov), $\varv \propto l^{1/2}$ (Burgers), we see that because of its dissipative nature, Burgers turbulence is the least efficient at transferring energy towards the small scales needed (since the wave particle interaction rate scales as $k$) for efficient acceleration.
-If Burgers turbulence dominates, then particle acceleration rates are too slow in the face of cooling processes to explain radio halos \citep{miniati15}.
-
-Given the lack of consensus on the fast mode spectrum, and the fact that turbulent reacceleration is not a viable explanation for radio halos if the spectrum is Burgers-like, we assume a Kraichnan spectrum.
-
-{\bf Inner and outer scale}
-
-{\bf Timescales}
-
-The characteristic synchrotron frequency is $\nu_{\rm s} \sim 3 \gamma^{2} \nu_{\rm c}^{2}$, where $\nu_{\rm c}$ is the non-relativistic cyclotron frequency.
-Thus, for a given observation frequency, the greatest contribution comes from electrons with:
-\begin{equation}
-\nu_{\rm emit} \approx 6.6 \times 10^{3} \left( \frac{\nu_{\rm obs}}{350 \, {\rm MHz}} \right)^{1/2} \left(\frac{B}{1 \, \mu{\rm G}} \right)^{1/2} (1+z)^{1/2}.
-\end{equation}
-
-{\bf Scaling solutions} Since the diffusion time is independent of energy (the so-call 'hard sphere' approximation), analytic solutions are possible.
-The steady state solution is a power-law with a cutoff above a characteristic momentum $p_{\rm eq}$, defined by $t_{\rm acc} \equiv t_{\rm cool} (p_{\rm eq})$ \citep{stawarz08}:
-\begin{equation}
-n(p) \propto \left \{
-\begin{array}{ll}
-p^{-\sigma} & \quad \text{for} \quad p \ll p_{\text{eq}} \, , \\
-p^2 {\rm e}^{-p/p_{\text{eq}}} & \quad \text{for} \quad p \sim p_{\text{eq}} \,.
-\end{array}
-\right.
-\end{equation}
-%
-where $-\sigma = 1/2 - \sqrt{9/4 +
-  t_\text{acc}/t_\text{esc}}$ asymptotically approaches $-1$
-as $t_\text{acc}/t_\text{esc} \rightarrow 0$.
-
-%%%Fast modes can become more important in highly supersonic turbulence, but this is not relevant to clusters.
-The magnetic energy density in fast modes scales as $\delta B^{2}_{\rm F} \sim \rho \delta v_{\rm F}^{2}/\beta$ (since magnetic restoring forces
-
-\subsection{Formalism for turbulent reacceleration}
+\subsection{Turbulent Reacceleration}
 \label{sec:reacc}
 
-We incorporate momentum diffusion for electrons and protons via the
-transit-time-damping (TTD) resonance with compressible MHD turbulence,
-to model Fermi-II reacceleration \citep{brunetti07,brunetti11}. The
+In turbulent reacceleration, particles gain energy via Fermi II acceleration. Wave-particle energy exchange takes place via transit time damping \citep{brunetti07,brunetti11}. The
 TTD resonance requires the wave frequency to obey the resonance
@@
 and $\varv_\parallel$ are the parallel (projected along the magnetic
-field) wavenumber and particle velocity, respectively. This implies
+field) wavenumber of the compressible mode and particle velocity, respectively. This implies
 that the particle transit time across the confining wave region
 matches the wave period,
-$\lambda_{\parallel}/\varv_{\parallel}=\tau_{\rmn{wave}}$. Note, the CRs'
+$\lambda_{\parallel}/\varv_{\parallel}=\tau_{\rmn{wave}}$ (hence the moniker, 'transit time damping'). Note that the CRs'
 gyroradius does not enter the resonance condition. Hence the CRs that
@@
 
-It can be shown that the particle pitch-angle averaged
-momentum-diffusion coefficient of isotropic particles that couple to
-fast magnetosonic modes via TTD resonance is \citep[][
-  Eqn. 47]{brunetti07}:
-\begin{eqnarray}
-  D_{pp}(p,t) = \frac{\upi}{16} \frac{p^2}{\rho c}
-  \left\langle\frac{\beta |B_k|^2}{16 \upi \,W}\right\rangle
-  I_\theta
-  \int_{k_\rmn{cut}}\mathcal{W}(k)k\,d k\,,
-\label{eq:dpp}
-\end{eqnarray}
-where $\beta$ is the thermal-to-magnetic pressure ratio, and $c$
-is the speed of light. The energy density $W$ of a mode in a
-magnetized plasma stems from both electromagnetic fields and resonant
-particles. For a high-$\beta$ plasma, the pitch angle averaged ratio of
-beta-weighted magnetic-to-total energy density saturates to $\langle\beta
-|B_k|^2/2W\rangle\approx 10^{1.4}$ (see Figure 2 in
-\citealt{brunetti07}). The pitch angle of the CR momentum with the
-magnetic field orientation is given by $\theta$, and
-\begin{equation}
-  \label{eq:I_theta}
-  I_\theta=\int_0^{\arccos(\Vph/c)} d\theta {\frac{ \sin^3 \theta }{
-    |\cos \theta | }}
-\left[1+\left(\frac{\Vph}{c\,\cos{\theta}}\right)^2\right]^2.
-\end{equation}
-Here $\Vph$ is the phase velocity of the fast magnetosonic waves
-given approximately by the sound speed, $\Vph \sim c_\rmn{s}$. For a
-sound speed typical for the ICM of 1000~km/s, $I_\theta\approx5$. As
-in \cite{brunetti07}, we initially assume that the velocity of
-turbulent eddies is $\varv_0\approx 0.47 c_\rmn{s}$ throughout the
-cluster. This gives a turbulent acceleration time scale, $\tau_{\rm D} =
-p^2/4D_{pp}$, that is typically few 100 Myrs in the ICM (see
-Tab.~\ref{tab:timescales} for more details).
-
-We focus on a scenario where the turbulence is injected at the largest
-scale that is driven by the merging cluster and accreting matter. The
-diffusion equation for isotropic MHD turbulence in $k$--space is given
-by
-\begin{equation}
-  \begin{aligned}
-\frac{\partial {\mathcal W}(k,t)}{\partial t}
-=
-\frac{\partial}{\partial k}
-\left[
-k^2 D_{kk}
-\frac{\partial}{\partial k}
-\left( \frac{{\mathcal W}(k,t)}{k^2} \right)
-\right]
-- \sum_i \Gamma_i (k,t) {\mathcal W}(k,t)
-+ I(k,t)
-\end{aligned}
-\label{modes_kinetic}
-\end{equation}
-where we assume that the volumetric injection rate of turbulence
-$I(k,t)$ is constant over time with a fixed rate $I_0$ so that $I(k,t)
-\equiv I(k) = I_0\,\delta (k - k_o)$. The different damping terms are
-given by $\Gamma_i(k,t)$ and $D_{kk}$ is the wave--wave diffusion
-coefficient of magnetosonic waves in the $k$--space represented by
-\begin{equation}
-  \label{eq:Dkk}
-  D_{kk} \approx \Vph k^4
-  \left(\frac{\mathcal{W}(k)}{\rho\,\Vph^2}\right)\,.
-\end{equation}
-
-We adopt a simplified isotropic MHD turbulent spectrum based on
-Kraichnan's picture for the fast modes per elemental range $dk$ of the
-form
+All of the physics of turbulent reacceleration is effectively encapsulated in the diffusion coefficient \citep{brunetti07}, which can be rewritten as \citep{miniati15}:
+\begin{equation}
+D_{\rm pp}(p) = \frac{ p^{2} \pi I_{\theta}(c_{s}/c)}{8 c} \langle k \rangle_{\mathcal{W}} \langle (\delta v_{\rm c})^{2} \rangle
+\label{eqn:diffusion}
+\end{equation}
+where $I_{\theta}$ averages interaction rates over the CR pitch angle $\theta$; $I_{\theta} \approx 5$ for ICM conditions, and
+\begin{equation}
+\langle k \rangle_{\mathcal{W}} = \frac{1}{\langle (\delta \varv_{\rm c})^{2} \rangle} \int_{k_{\rm L}}^{k_{\rm cut}} dk \, k \, \mathcal{W}(k) \approx \frac{s-1}{2-s} k_{\rm L} \left( \frac{k_{\rm cut}}{k_{\rm L}} \right)^{2-s}
+\label{eqn:k_W} 
+\end{equation}
+is an energy-averaged wavenumber, $k_{\rm L}, k_{\rm cut}$ are the wavenumbers associated with the outer scale and the cutoff scale respectively, and we have assumed a total energy spectrum (both kinetic and potential energy, where the two are assumed to be in equipartition \citep{sarkar11}):
+\begin{equation}
+\mathcal{W}(k) = \frac{(s-1) \langle (\delta \varv_{\rm c})^{2} \rangle}{k_{\rm L}} \left( \frac{k}{k_{\rm L}} \right)^{-s} 
+\label{eqn:Wk}
+\end{equation}
+which defines the normalization $\langle (\delta \varv_{\rm c})^{2} \rangle$ (the subscript 'c' emphasizes that we specialize to compressive modes).
+Intuitively, we can understand the form of the the diffusion coefficient from the fact that for second-order Fermi acceleration, $\dot{p} \sim \Delta p/\tau \sim p\,\langle k c \rangle_{\mathcal{W}} (\delta \varv_{\rm c}/c)^{2}$, where $\tau^{-1} \sim \langle k c \rangle_{\mathcal{W}}$ is the energy averaged wave-particle interaction rate, and $\Delta p \sim p (\delta \varv_{\rm c}/c)^{2}$ is the typical momentum change during wave particle scattering.
+Thus:
+\begin{equation}
+D_{\rm pp} \sim p \dot{p} \sim p^{2} \langle k c \rangle_{\mathcal{W}} \left( \frac{\delta \varv_{\rm c}}{c} \right)^{2}. 
+\end{equation}
+
+Equations \ref{eqn:diffusion} and \ref{eqn:Wk} make the important aspects of turbulence clear: the energy in compressive modes $\langle (\delta v_{\rm c})^{2} \rangle$, the inner and outer scale ($k_{\rm cut}$ and $k_{\rm L}$), and the slope of the energy spectrum $s$.
+All of these can vary spatially and temporally.
+
+We adopt a Kraichnan spectrum ($s=3/2$) for the fast modes, as seen in simulations \citep{cho03}. This can also be written as: 
 \begin{equation}
@@
 \end{equation}
-for $k_0<k<k_\rmn{cut}$. Here we adopt an injection scale of the
-turbulence, $k_0= 2\upi/\lambda_0$ with $\lambda_0 =100~\mbox{kpc}$,
-that is in line with previous work
-\citep{2006MNRAS.366.1437S,brunetti07,brunetti11}. Note that this
-length scale defines an eddy turn-over time
-$\tau_{\rmn{eddy}}\sim2\upi\lambda_0/\varv_0\sim1.2$~Gyr with
-$\varv_0=500\,\rmn{km~s}^{-1}$, characteristic of a merger event.
-
-Provided dissipation of turbulence in the ICM is collisionless,
-turbulent cascades of compressible modes become suppressed when
-thermal and relativistic particles resonantly interact with
-magnetosonic waves via TTD on a timescale $\Gamma^{-1}$ that
-approaches the cascading timescale given by $\tau_{kk} \approx
-k^2/D_{kk}$. Thus, the cascade is suppressed for wave numbers above
-\begin{equation}
-\label{eq:kc}
-  k_\rmn{cut} \approx \frac{81}{14} \frac{I_0}{\rho \langle \Vph \rangle}
-  \left(\frac{\langle\sum_i \Gamma_i(k,\theta)\rangle}{k}\right)^{-2}\,,
-\end{equation}
-where $2\upi/k_\rmn{cut}\sim 0.1-1$~kpc in the ICM. This constitutes an
+where $I{\rm 0}$ is the volumetric injection rate of turbulence (which is assumed to be constant), $v_{\rm ph}\approx c_{\rm s}$ is the phase speed of waves.
+It is important to realize that this only applies at small scales, which turbulence is MHD.
+At large scales, turbulent motions are subsonic (${\mathcal M}_{\rm s} \sim 0.2-0.5$) but super-Alfv{\'e}nic (${\mathcal M}_{\rm A} \sim 5$).
+Thus, except in the case where motions are transonic and weak shocks become important, motions are fundamentally hydrodynamic and turbulence follows a Kolmogorov ($s=5/3$) spectrum.
+However, while the turbulent energy density $U_{\rm t} \propto l^{2/3}$ decreases at small scales, the magnetic energy density is scale-independent.
+Thus, at some scale $l_{\rm A} \sim l_{\rm o} {\mathcal M}_{\rm A}^{-3}$, where $U_{\rm turb} \sim U_{B}$, the magnetic field becomes dynamically important, and turbulence transitions to the MHD regime.
+The cutoff scale in equation \ref{eqn:Wk} can be computed by setting the turbulent cascade rate for fast modes to the transit time damping rate on thermal electrons.
+This yields \citep{brunetti07,miniati15}:
+\begin{equation}
+k_{\rm c} \approx A k_{\rm outer} \frac{\langle v_{\rm outer}^{2}\rangle^{2}}{c_{\rm s}^{4}}
+\label{eqn:k_c} 
+\end{equation}
+where $A \approx 11 000$. This gives $2\upi/k_\rmn{cut}\sim 0.1-1$~kpc in the ICM. This constitutes an
 effective mean free path for CRs, unless plasma instabilities can
 mediate interactions between turbulence and particles on smaller
-scales \citep{brunetti11}.
-
-The profile of injected turbulence depends on the details of the
+scales \citep{brunetti11}, a possibility we discuss in \S\ref{sect:self-limiting}.
+Another possibility is that compressible modes dissipate in weak shocks, resulting in Burgers' turbulence $s=2$ \citep{kowal10,porter15,miniati15}.
+If Burgers turbulence dominates, then particle acceleration rates are too slow in the face of cooling processes to explain radio halos \citep{miniati15}, and an alternative model for radio halos is required.
+
+The spatial profile of injected turbulence depends on the details of the
 merger such as time during the merger, the impact parameter, the
@@
 \citep{miniati15}. We parametrize these uncertainties and
-assume that it scales with the thermal energy density to some
-power. Hence we assume volumetric injection rate of turbulent energy,
+assume that volumetric injection rate of turbulent energy,
 $I_0\propto \eps_\rmn{th}^{\alpha_\rmn{tu}}$, and determine the
@@
 X_\rmn{tu} E_\rmn{th}$, where $E_\rmn{th}$ is the total thermal
-energy. We adopt a turbulent energy ratio $X_\rmn{tu}=0.2$ within the
-radio halo.\footnote{Simulations show that the compressible modes
-  contribute a factor $0.2-0.4$ to the total turbulent energy
-  \citep{2013ApJ...771..131B,miniati15}. Furthermore, the
-  total turbulent energy, which can be decomposed into a slenoidal and
-  compressible component, is typically $\sim15-70$\% of the thermal
-  energy in a cluster \citep{2011A&A...529A..17V}; in agreement with
-  our adopted value of $X_\rmn{tu}$.}
-
-In this work we only consider damping of the turbulence via TTD due to
-thermal electrons, and neglect subdominant damping with thermal
-protons and relativistic particles (conversely, the turbulence has
-important effects on the reacceleration of CRs). The latter will be
-subdominant in the ICM for a CR-to-thermal energy density ratio
-$\lesssim 10 \%$ \citep{brunetti07}, which is always satisfied in our
-models. The azimuthally averaged turbulent damping rate from thermal
-electrons \citep{brunetti07} in a high-$\beta$ plasma is
-\begin{equation}
-\label{eq:Gamma_e}
-\langle\Gamma_{\rmn{e}}\rangle \approx \langle k\,\Vph\,\sqrt{3\upi
-  x/20}\exp(-5x/3)\sin^2{\theta}\rangle\approx 0.0435k\,\Vph, 
-\end{equation}
-where $x=(m_{\rmn{e}}/m_{\rmn{p}})/\cos^2{\theta}$. To compute the
-synchrotron surface brightness profiles, we use the profile of the
-magnetic field strengths derived from Faraday rotation observations of
-Coma \citep{bonafede10} in combination with the density profile
-derived from X-ray measurements \citep{1992A&A...259L..31B}.
-
-\SPO{the following needs a rewrite in the light of an updated discussion of
-  $\tau_\rmn{d}$ vs. $\tau_{\rmn{cl}}$ and the dummy's guide.}  For reference we show in
-Table~\ref{tab:timescales} both the thermal quantities and the
+energy. Given these definitions, one can show that: 
+\begin{equation}
+  \label{eq:Dpp_scaling}
+  D_{\rm pp}\propto \frac{I_0}{\rho c_{\rmn{s}}} \propto 
+X_\rmn{tu}^2k_{\rm L} \eps_\rmn{th}^{\alpha_\rmn{tu}-1}\sqrt{T}\,.
+\end{equation}
+
+What is a typical energy density in compressive fast modes?
+The total turbulent energy is typically $\sim 15-70\%$ of the thermal energy in a cluster \citep{vazza11}; it rises rapidly during a merger.
+The compressible component is $\sim 20-40\%$ of the total turbulent energy, and shows more rapid temporal variations compared to the compressible component \citep{2013ApJ...771..131B,miniati15}.
+Note the compressible component in cluster simulations is much larger than that seem in stirring box simulations with similar Mach numbers \citep{kowal10,lynn14}.
+This is likely due to the compressive nature of turbulent driving (transonic infall and merger), whereas idealized simulations tend to use incompressible solenoidal driving and allow compressive fluctuations to develop on their own.
+Overall, we adopt a compressive energy density which is $X_{\rm tu} \sim 0.2$ of the thermal energy as a baseline estimate.
+
+The important effects are best summarized in terms of the acceleration time: 
+\begin{equation}
+\tau_{\rm D}= \frac{p^{2}}{4 D_{\rm pp}}
+\end{equation}
+which is momentum independent.
+This should be compared against the lifetime of turbulence, $\tau_{\rm cl}$, and the cooling time $\tau_{\rm cool}$.
+In Table~\ref{tab:timescales}, we show both the thermal quantities and the
 timescales for CR cooling and (re)acceleration for three different
-spatial regions of the RH. Interestingly the reacceleration timescale
+spatial regions of the RH.
+The densities \citep{1992A&A...259L..31B} and temperatures \citep{2009ApJ...696.1886B,2001A&A...365L..67A} are derived from X-ray observations.
+To calculate synchrotron cooling times, we use B-fields derived from Faraday rotation measurements \citep{bonafede10}.
+To calculate the acceleration time, we need to assume an outer scale.
+We assume an injection scale $k_{\rm L}=2\pi/\lambda_{\rm L}$, where $\lambda_{\rm L} = 100$ kpc, which were assumptions adopted in previous work \citep{2006MNRAS.366.1437S,brunetti07, brunetti11}.
+This lengthscale corresponds to an eddy turnover time on the outer scale of $v_{L} k_{\rm L}^{-1} \sim 1.2$Gyr if $v_{\rm L} \sim 500 {\rm km \, s^{-1}}$, as is characteristic of a merger.
+Note that hydrodynamical simulations of clusters have sometimes found larger $\lambda_{\rm L}$, in some cases comparable to the size of the cluster \citep{vazza11,miniati15}.
+This choice is degenerate with $X_{\rm tu}$; in \S\ref{sect:self-limiting} we argue that $k_{\rm A}$ is a more appropriate choice, but also find that when the decay time is appropriately scaled, we are relatively insensitive to the choice of $k_{\rm L}$.
+We present $\tau_{\rm D}$ for 3 different models, which we discuss in the next section.
+The reacceleration timescale
 $\tau_{\rm D}$ is similar between our three models, where the
@@
 turbulent profile could impact the seed CRs significantly.
-
+Finally, we adopt an duration of acceleration $\tau_{\rm cl} = 650$ Myr, in line with previous assumptions \citep{brunetti07}, roughly corresponding to the turbulent decay time.
 \begin{table}
@@
 
-To understand the radial dependence of the diffusion constant we
-investigate how $D_{pp}$ scales with different parameters. This is
-crucial in order to identify important parameters, and understand the
-profile of reaccelerated CRs and radio emission. Combining
-Eqns.~\ref{eq:dpp}-\ref{eq:Gamma_e} we find that 
-\begin{equation}
-  \label{eq:Dpp_scaling}
-  D_{pp}\propto \frac{I_0}{\rho c_{\rmn{s}}} \propto 
-X_\rmn{tu}^2k_0\eps_\rmn{th}^{\alpha_\rmn{tu}-1}\sqrt{T}\,.
-\end{equation}
-Here we immediately see that if the turbulent profile traces the
-thermal energy (i.e. $\alpha_\rmn{tu}=1$), the square root of
-temperature determines the diffusion constant. We also see that
-$D_{pp}$ is much more sensitive to the turbulent energy content
-$X_\rmn{tu}$ in comparison to the injection scale $k_0$.
-
-%\SPO{the derivation of the following is not transparent, could you
-%  expand?}  \sout{During reacceleration, the CRps increase their
-%  normalization approximately by the factor} \AP{In the region where
-%  reacceleration dominates over cooling and injection, the CRps
-%%  increase their normalization exponentially. This can easily be
- % understood by considering a simple toy model where a fossil CRp
-%  population described by $f=C p^{-\alpha}$ is reaccelerated such that
-%  $\tau_D < \tau_\rmn{cooling},\tau_\rmn{injection}$, i.e. injection
-%  and cooling can be neglected. The Fokker-Planck equation in
-%  Eqn.~\ref{eq:FP_p} then simplifies to}
-%\begin{equation}
-%  \dot{f} = {{\partial }\over{\partial p}}
-%  p^2 D_{pp} {{\partial }\over{\partial p}} \frac{f}{p^2}\,,
-%\end{equation}
-%with the analytic solution given by
-%\begin{equation}
-%  \label{eq:Creacc}
-%%  \delta C_\rmn{reacc.} \sim 
-%  \exp{\left[\frac{(2+\alpha)(\alpha-1)}{4}\frac{\tau_\rmn{cl}}{\tau_\rmn{D}}\right]}\,.
-%\end{equation}
-%The reaccelerated CRs depend exponentially on $\tau_D\sim 1/D_{pp}$ as
-%long as $\tau_D \lesssim \tau_\rmn{cl}$, where $\tau_\rmn{cl}$
-%represent the duration of reacceleration of the merger which we assume
-%to be 650~Myrs long.
-
 % --- section: Simulation Results and discussion --- %
@@
 In this section, we solve the Fokker-Planck equation for CR transport
-on Lagrangian particle trajectories through cosmic history.  We
-concentrate on three scenarios. (i) In model {\em M-primaries}, we
+on Lagrangian particle trajectories through cosmic history.
+We then use our parameterized model of turbulence to apply turbulence re-acceleration, and compare radio halo profiles against observations of the Coma cluster.
+Our philosophy to is make assumptions roughly in line with previous successful models, which are now confronted with more accurate calculations of the seed CR population, and find the minimal modifications required to fit observations.
+We re-examine these choices in \S\ref{sect:param_comp}.
+
+Since the standard vanilla model requires a CR seed population which is inconsistent with the simulations (Fig \ref{fig:Edens}), some modifications are necessary, either in the seed CR population or in the properties of turbulence.
+We focus on three scenarios.
+(i) In model {\em M-primaries}, we
 assume that CR electrons, which have been accelerated by cosmic
@@
 simulations.
-
-The level of emission is mainly driven by how efficient the CRs are
-reaccelerated and for how long. Hence, we exploit the exponential
-sensitivity of reacceleration on the level of turbulence and adopt
-different radial profiles of the turbulent energy density. We ask the
-question how differently the turbulent profiles need to be shaped in
-order to reproduce the observed radial profiles of the radio
-emission. For these models, we then compute radio spectra and
-gamma-ray luminosities and compare to observational data.
 
@@
   \rmn{where}\quad x_\rmn{inj} &\approx& 1.17 \frac{\varv_2}{p_{\rmn{th}}\,c} \left(1+
-  \frac{1.07}{\epsilon_B}\right) \left(\frac{\mathcal{M}}{3}\right)^{0.1}\,.
+  \frac{1.07}{\eb}\right) \left(\frac{\mathcal{M}}{3}\right)^{0.1}\,.
 \end{eqnarray}
@@
   viable for primarily perpendicular
-  shocks,][]{2014ApJ...794..153G}. While this appears to contradict the
-radial bias of magnetic fields in the bulk of the ICM as suggested by
-observations \citep{2010NatPh...6..520P} and cluster simulations
-\citep{2011ApJ...740...81R}, it does not necessarily apply to the
-accretion shock regions, which show a field geometry with a net
-perpendicular bias with respect to the shock normal---at least for
-giant radio relics \citep{2010Sci...330..347V}.
+  shocks,][]{2014ApJ...794..153G}. Given the unknown magnetic geometry at cluster shocks, we investigate the consequences of this additional degree of freedom.
 
@@
 parametrisation for the volumetric injection rate of turbulent energy,
-$I_0\propto \eps_\rmn{th}^{\alpha_\rmn{tu}}$, we find
+$I_0\propto \eps_\rmn{th}^{\alpha_\rmn{tu}}$, we find that to fit the observations, we require
 $\alpha_\rmn{tu}= 0.67$ for \Mflatturb, $\alpha_\rmn{tu}= 0.82$ for
@@
 ratio of turbulent-to-thermal energy densities slightly increase with
-radius as shown in Fig.~\ref{fig:turb}.  After turbulent
+radius as shown in Fig.~\ref{fig:turb}.  The fine-tuning of these exponents is somewhat problematic, as we discuss in \S\ref{sect:param_comp}. After turbulent
 reacceleration, the volume-weighted, relative CRp energy density and
@@
 respectively.
-
-%the turbulent energy density becomes $\eps_\rmn{turb} \propto
-%\eps_\rmn{th}^{(\alpha_\rmn{tu}+1)/2}/T^{1/4}$, where $T$ is the
-%temperature of the gas,
 
@@
 this conclusion much because of the weak radial dependence of
-$D_{pp}(R)\propto \eps_\rmn{th}(R)^{\alpha_\rmn{tu}-1}
+$D_{\rm pp}(R)\propto \eps_\rmn{th}(R)^{\alpha_\rmn{tu}-1}
 \sqrt{T(R)}$. This signals that the problem is generic and requires
@@
 explain the observations at each radius and for each model (see also
-Table~\ref{tab:timescales}). This allows us to interchange the value
-of uncertain parameters $\tau_\rmn{cl} \sim X_\rmn{tu}^2 \sim k_0$,
-i.e. a longer reacceleration duration have to be compensated by
-lowering the level of turbulence or increasing the physical injection
-scale of turbulence to keep $\tau_{\rm D}$ constant.
+Table~\ref{tab:timescales}). Since $\tau_\rmn{cl} \propto X_\rmn{tu}^2 k_0$,
+these two parameters are degenerate and can be traded off one another.
 
@@
 % --- section: Analytical Results and discussion --- %
-\section{Parameter space exploration with spherical models}
+\section{Parameter Space Exploration and Overcoming Fine Tuning}
 \label{sect:param_comp}
@@
 parameters describing the spatial profile of CR protons and
-turbulence, thereby semi-analytically probing variations about the
-models \Mflatturb and \Mstream. Our fiducial model is meant to be
+turbulence. Our fiducial model is meant to be
 compared against the Coma cluster.
@@
 turbulence as parametrized by $\alpha_{\rm tu}$ (defined by $I_0
-\propto \epsilon_{\rm th}^{\alpha_{\rm tu}}$, where $I_0^{} \propto
+\propto \eps_{\rm th}^{\alpha_{\rm tu}}$, where $I_0^{} \propto
 \varv_0^{3} k_0^{}$ is the injection rate of turbulence), as well as
@@
 by about a factor of 10 in comparison to the cumulative CR energy
-injected over the entire cosmological history of the cluster.
-\AP{So why can't we just neglect the population injected during the merger?
--- Above ~ 1 GHz the radio emission is dominated by the CRes injected during the merger.
-The reason for this is that this population have not had time to cool significantly yet.
-Otherwise the radio spectrum would be more curved.}
+injected over the entire cosmological history of the cluster, but this component is nonetheless important since above 1 GHz the radio emission is dominated by CRe's injected during the merger, which have not yet had time to cool.
 Similarly, the initial CRe distribution is given by the steady state
 between cooling (Coulomb, inverse Compton, and synchrotron) and
-injection of secondary CRes from $f_\rmn{p,0}$. %We also include the
-%continuous injection of secondary CRes during $\tau_\rmn{cl}$. 
-%The
-%compressible turbulence responsible for reaccelerating both the CRps
-%and CRes is parameterized by $I_0 \propto X_\rmn{tu} (n_{\rmn{e}}
-%T)^{\alpha_\rmn{tu}}$. 
-\AP{Do we include injection by primaries, is it negligible? -- I did
-  not include it, because it is subdominant (at least for a
-  $K_{ep}=0.1$).}  The diffusion constant $D_{pp} \propto X_{\rm tu}^{2}
+injection of secondary CRes from $f_\rmn{p,0}$. 
+The diffusion constant $D_{\rm pp} \propto X_{\rm tu}^{2}
 \eps_{\rm th}^{\alpha-1} \sqrt{T} k_{\rm 0}$ is calculated for each
-radial bin using Eqns.~\ref{eq:dpp}-\ref{eq:Gamma_e}. All parameters
+radial bin. All parameters
 and assumptions are similar to what is used for our simulated cluster
@@
 
-The exponential increase in radio surface brightness is easily understood from equation~\ref{eq:Creacc}, since for a power-law initial distribution function $f_{\rm i}(p) = C_{\rm 0} p^{-\alpha}$, then $C_{\rm reacc} \propto C_{\rm 0} {\rm exp}(A \tau_{\rm cl}/\tau_{\rm D}) \propto {\rm exp} (B(r) X_{\rm tu}^{2})$.
+As we show in \S\ref{sect:self-limiting}, the exponential increase in radio surface brightness is easily understood from equation~\ref{eq:Creacc}, since for a power-law initial distribution function $f_{\rm i}(p) = C_{\rm 0} p^{-\alpha}$, then $C_{\rm reacc} \propto C_{\rm 0} {\rm exp}(A \tau_{\rm cl}/\tau_{\rm D}) \propto {\rm exp} (B(r) X_{\rm tu}^{2})$.
 This exponential sensitivity is somewhat modified by cooling (which results in a non power-law spectrum; also, the shorter the acceleration time, the larger the pool of seed electrons available which would otherwise cool away), but overall is a good approximation.
-%For fixed $\tau_{\rm cl}$, it also implies a critical level of turbulence, below which reacceleration becomes negligible.
 
@@
 In between, there is a quasi-adiabatic regime where electrons accumulate (for more details, and an analytic self-similar solution, see \citealt{1999ApJ...520..529S, pinzke13}).
-In the absence of cooling, momentum advection in the limit $D_{pp} \propto p^{2}$ (so that $\tau_\rmn{D} =p^{2}/4 D_{pp}$ is momentum independent) simply shifts the distribution $f(p) \rightarrow f(A p)$.
+In the absence of cooling, momentum advection in the limit $D_{\rm pp} \propto p^{2}$ (so that $\tau_\rmn{D} =p^{2}/4 D_{\rm pp}$ is momentum independent) simply shifts the distribution $f(p) \rightarrow f(A p)$.
 When the acceleration efficiency is low, most observable emission corresponds to the power-law tail of the distribution function $f \propto p^{-\alpha_{\rm inj}-1}$ set by the balance between injection and synchrotron/IC cooling.
@@
 We address this next.
-%We discuss one such scenario in \S\ref{sec:reacc}, but this point clearly deserves more work.
 
 \subsection{Self-Limiting Turbulent Reacceleration}
+\label{sect:self-limiting}
 
@@
   \dot{f} = {{\partial }\over{\partial p}}
-  p^2 D_{pp} {{\partial }\over{\partial p}} \frac{f}{p^2}\,,
+  p^2 D_{\rm pp} {{\partial }\over{\partial p}} \frac{f}{p^2}\,,
 \end{equation}
@@
 \end{equation}
-where we have used $k_{\rm A} = k_{\rm L} M_{A}^{3}$ (from Kolmogorov scalings, and $M_{\rm A} = v_{\rm c}/v_{\rm A}$ is the Alfv{\'e}n Mach number of the turbulence, $\beta \approx c_{\rm s}^{2}/v_{\rm A}^{2}$, and the cutoff scale \citep{brunetti07,miniati15}:
-\begin{equation}
-k_{\rm c} \approx A k_{\rm outer} \frac{\langle v_{\rm outer}^{2}\rangle^{2}}{c_{\rm s}^{4}}
-\label{eqn:k_c} 
-\end{equation}
-where $A \approx 11000$.
+where we have used $k_{\rm A} = k_{\rm L} M_{A}^{3}$ (from Kolmogorov scalings, and $M_{\rm A} = v_{\rm c}/v_{\rm A}$ is the Alfv{\'e}n Mach number of the turbulence, $\beta \approx c_{\rm s}^{2}/v_{\rm A}^{2}$, and the cutoff scale $k_{\rm c}$ (equation \ref{eqn:k_c}).
 Thus, the contribution of the two regimes are comparable (as we shall see later, this is not true if one incorrectly assumes Kraichnan scalings apply from the outer scale $L$; this boosts the contribution of the scales where $l_{\rm A} < l < L$ by a factor $M_{\rm A}^{1/2}$).
-
 Henceforth, we can consider the outer scale of the fast modes to be $l_{\rm A}$, with velocity $v_{\rm A}$. The turbulent reacceleration time is: 
@@
 where $C_{\rm D} = 2/(5 \pi)$, $A\approx 11000$, and we have used equation \ref{eqn:k_c}.
-The turbulence decay time is given by the cascade time of fast modes (\citet{yan04}; see equation \ref{eqn:cascade}):
+The turbulence decay time is given by the cascade time of fast modes (\citet{2004ApJ...614..757Y}; see equation \ref{eqn:cascade}):
 \begin{equation}
@@
 \end{equation}
-where $\zeta$ is an efficiency factor for the the effectiveness of plasma instabilities (e.g., due to spatial or temporal intermittency), and $x_{\rm CR}=\epsilon_{\rm CR}/\epsilon_{\rm th}$ is the relative energy density of cosmic rays.
+where $\zeta$ is an efficiency factor for the the effectiveness of plasma instabilities (e.g., due to spatial or temporal intermittency), and $x_{\rm CR}=\eps_{\rm CR}/\eps_{\rm th}$ is the relative energy density of cosmic rays.
 If we set $k_{\rm L} \rightarrow k_{\rm A}$, $v_{c}^{2} \rightarrow v_{\rm A}^{2}$, as before, then:
@@
 However, there is a self-limiting asymptotic behaviour: as $x_{\rm CR}$ increases due to turbulent reacceleration, damping increases, which limits the further growth of the cosmic ray energy density \citep{brunetti11}.
-One natural assumption is to assume that $\epsilon_{\rm CR}$ saturates at a level $\epsilon_{\rm CR} \sim \epsilon_{\rm turb} (MHD) \sim \epsilon_{\rm B}$, in which case $x_{\rm CR} \sim \beta^{-1}$, so that:
+One natural assumption is to assume that $\eps_{\rm CR}$ saturates at a level $\eps_{\rm CR} \sim \eps_{\rm turb} (MHD) \sim \eps_{\rm B}$, in which case $x_{\rm CR} \sim \beta^{-1}$, so that:
 \begin{equation}
 \frac{\tau_{\rm cl}}{\tau_{\rm D}} \approx 1.6 \left(\frac{\zeta}{0.2}\right)\,.
+\label{eqn:ratios_CR_damp} 
 \end{equation}
@@
 
-STUFF ABOUT BURGERS TURBULENCE
-
-STUFF ABOUT FIGURE--LESS SENSITIVE TO PROPERTIES OF TURBULENCE, MIGHT BE ABLE TO PROBE SEED POPULATION 
+It is also worth exploring the effect of Burgers' turbulence (weak shocks). From equation \ref{eqn:diffusion} and \ref{eqn:k_W}, we find: 
+\begin{equation}
+\frac{D_{\rm pp}^{\rm Burgers}}{D_{\rm pp}^{\rm MHD}} = \left( \frac{\beta}{X_{\rm tu} A} \right)^{1/2} = 0.15 \left( \frac{\beta}{50} \right)^{1/2} \left( \frac{X_{\rm tu}}{0.2} \right)^{-1/2} 
+\end{equation}
+where we have set $\langle k \rangle_{\rm W} \approx k_{\rm L}$ for Burgers' turbulence, i.e.
+all power is at large scales.
+This weighting towards larger scales implies a much lower wave-particle interaction rate and thus a diffusion coefficient which is smaller than standard TTD on thermal particles by an order of magnitude.
+Since $\langle k \rangle_{\rm W} \approx k_{\rm L}$ is independent of the cutoff scale $k_{\rm c}$, this conclusion is unchanged if plasma instabilities regulate the thermal particle mean free path and TTD operates on relativistic particles instead.
+Since standard TTD on thermal particles was already potentially problematic (equation \ref{eqn:ratios_TTD}), we conclude, in agreement with other assessments \citep{miniati15,brunetti16_review}, that if Burgers turbulence dominates, then turbulent reacceleration will be ineffective\footnote{Note also that since there is no real cascade in Burgers' turbulence, but direct transfer of power from large to small scales, the dissipation time is potentially short.
+In this case, $\tau_{\rm cl} \sim \tau_{\rm drive}$, the driving time, rather than the turbulent dissipation time.}.
+
+It is interesting to reconsider surface brightness and spectral profiles if indeed $\tau_{\rm D} \sim \tau_{\rm cl}$, for the reasons mentioned above (e.g., equation \ref{eqn:ratios_CR_damp}).
+We show the results of adopting such an ansatz in Fig.
+\ref{fig:param_comp_tcl_tD}, where, similar to Fig.
+\ref{fig:param_comp}, we vary $X_{\rm tu}, \alpha_{\rm tu}, \alpha_{\rm CR, spat}$ about fuducial values, but this time we do not adopt a fixed $\tau_{\rm cl}$ but set $\tau_{\rm cl}=\tau_{\rm D}$.
+They are remarkably revealing.
+In this case, one is much less sensitive to the properties of the turbulence, and more sensitive to the details of the CR seed population.
+This gives hope to the possibility that one could effectively marginalize over the very uncertain properties of turbulence (which are unlikely to be more precisely constrained observationally in the near future) to learn something about the underlying CR population.
+
+For instance, in the top panels of Fig \ref{fig:param_comp_tcl_tD}, we see that once turbulence exceeds a threshold value $X_{\rm tu} \sim 0.1$, then its overall exact energy density does not matter-- profiles simply converge to an asymptotic form as $X_{\rm tu}$ is increased.
+This is in contrast to the exponential sensitivity, flattening in surface brightness, and increasing spectral curvature as $X_{\rm tu}$ is increased that we saw previously.
+A threshold value of $X_{\rm tu}$ is necessary for turbulent reacceleration to overcome cooling.
+Once that condition is satisfied, the condition $\tau_{\rm cl} \sim tau_{\rm D}$ implies a fixed amount of amplification: stronger turbulence implies faster acceleration, but also dissipates more quickly.
+This leads to the asymptotic behavior seen.
+From the middle panels, we see another striking result: in contrast to Fig.
+\ref{fig:param_comp}, results are also completely insensitive to the turbulent profile.
+Given the large uncertainties in the latter, this is welcome news.
+It arises because for our fuducial value ($X_{\rm tu} = 0.2$), variations in the turbulent profile still lead to local energy densities which are above the threshold value required to overcome cooling, and turbulent amplification approaches its asymptotic value.
+Finally, in the bottom panels, we see that we {\it are} sensitive to the spatial CRs; it affects both the surface brightness profile (a flatter CR distribution implies flatter surface brightness profiles) and luminosity (once again, luminosity is larger for more centrally concentrated CRs, since more secondaries are produced).
+This arises because once turbulent reacceleration overcomes cooling, the condition $\tau_{\rm cl} \sim \tau_{\rm D}$ provides for a fixed amount of amplification in each radial shell.
+The radio luminosity in each shell then depends linearly on initial conditions, i.e., the profile of CR seeds.
+Interestingly, the best-fitting profile for Coma comes from a flat CR distribution -- i.e., one that is the outcome of efficient CR streaming.
+Matching the overall amplitude simply involves a rescaling of $\tau_{\rm c}/\tau_{\rm D}$ (equation \ref{eqn:ratios_CR_damp}) or the CR content.
+
+Obviously, the ideas in this section require further study.
+However, the notion that $\tau_{\rm cl}/\tau_{\rm D}$ could self-regulate around a fixed value is exciting, because it eliminates the main source of uncertainty-- the poorly unconstrained properties of turbulence, and implies that radio halos could potentially provide more robust constraints on the underlying CR population.
+
 \begin{figure*}
@@
 rays.
-%(note that while radio halos have a non-linear dependence on the overall
-%normalization of turbulence, the surface brightness scales linearly with the CR
-%abundance; thus, this degree of freedom is easily understood).
+
 We find that the most important variable is the overall normalization of
@@
 luminosity. The timescale of the merger has some natural scatter which is not
-obviously correlated with $\tau_{\rm D}$. More likely candidates for $\tau_{\rm
-  cl}$ are the timescale on which turbulence decays, or the escape (i.e. spatial
-diffusion) time from an accelerating regime. Across a wide variety of
-conditions, this must be correlated with $\tau_{\rm D}$ so as to keep the ratio
-$\tau_{\rm D}/\tau_{\rm cl}$ roughly constant. We believe this issue is worthy
-of further study.
+obviously correlated with $\tau_{\rm D}$.
+
+If instead we adopt $\tau_{\rm
+  cl} \sim \tau_{\rm decay}$, i.e.
+the natural lifetime of turbulence is its decay lifetime, then we can show that the acceleration time and the lifetime of turbulence are linked, simply because the wave-particle interaction rate (which drives particle acceleration) and the wave-wave interaction rate (which drives dissipation) are linked.
+If we are mindful that Kraichnan turbulence is only applicable below the Alfven scale $l_{\rm A}$ (where turbulent velocities $v < v_{\rm A}$), then remarkably the ratio $\tau_{\rm cl}/\tau_{\rm D}$ is independent of properties of the turbulence (such as its amplitude and outer scale) and only depends on plasma parameters.
+Our results suggest that TTD on thermal particles may result in overly rapid damping of turbulence, and inefficient acceleration (equation \ref{eqn:ratios_TTD}), but if plasma instabilities scatter the thermal particles so that the fast modes damp via TTD on the cosmic rays, then the required acceleration can take place (equation \ref{eqn:ratios_CR_damp}).
+In agreement with other assessments, we find that if turbulence is Burgers rather than Kraichnan, then turbulent reacceleration is ineffective, and some other explanation for radio halos (e.g., magnetic reconnection, \cite{brunetti16}) is necessary.
+If we adopt the ansatz $\tau_{\rm cl} \sim \tau_{\rm D}$, then we find that above a threshold level of turbulence (necessary to overcome cooling), radio properties are insensitive to both the amplitude and spatial profile of turbulence, since only a fixed, asymptotic amount of amplification takes place.
+On the other hand, they {\it are} sensitive to the properties of the seed electron profile.
+This raises the exciting possibility that one could marginalize over the highly uncertain properties of cluster turbulence to learn about the underlying seed CR population.
+Our results suggest that studying not just mean trends, but the relatively small scatter in radio-halo scaling relations, may prove extremely fruitful in shedding light on ICM plasma processes.
 

### 2016-05-30 paper.tex
fixing a few typos

@@
 \begin{equation}
-D_{\rm pp}(p) = \frac{ p^{2} \pi I_{\theta}(c_{s}/c)}{8 c} \langle k \rangle_{\mathcal{W}} \langle (\delta v_{\rm c})^{2} \rangle
+D_{\rm pp}(p) = \frac{ p^{2} \pi I_{\theta}(c_{s}/c)}{8 c} \langle k \rangle_{\mathcal{W}} \langle (\delta \varv_{\rm c})^{2} \rangle
 \label{eqn:diffusion}
@@
 
-Equations \ref{eqn:diffusion} and \ref{eqn:Wk} make the important aspects of turbulence clear: the energy in compressive modes $\langle (\delta v_{\rm c})^{2} \rangle$, the inner and outer scale ($k_{\rm cut}$ and $k_{\rm L}$), and the slope of the energy spectrum $s$.
+Equations \ref{eqn:diffusion} and \ref{eqn:Wk} make the important aspects of turbulence clear: the energy in compressive modes $\langle (\delta \varv_{\rm c})^{2} \rangle$, the inner and outer scale ($k_{\rm cut}$ and $k_{\rm L}$), and the slope of the energy spectrum $s$.
 All of these can vary spatially and temporally.
@@
 \end{equation}
-where $I{\rm 0}$ is the volumetric injection rate of turbulence (which is assumed to be constant), $v_{\rm ph}\approx c_{\rm s}$ is the phase speed of waves.
+where $I_{\rm 0}$ is the volumetric injection rate of turbulence (which is assumed to be constant), $\varv_{\rm ph}\approx c_{\rm s}$ is the phase speed of waves.
 It is important to realize that this only applies at small scales, which turbulence is MHD.
@@
 However, while the turbulent energy density $U_{\rm t} \propto l^{2/3}$ decreases at small scales, the magnetic energy density is scale-independent.
-Thus, at some scale $l_{\rm A} \sim l_{\rm o} {\mathcal M}_{\rm A}^{-3}$, where $U_{\rm turb} \sim U_{B}$, the magnetic field becomes dynamically important, and turbulence transitions to the MHD regime.
+Thus, at some scale $l_{\rm A} \sim l_0 {\mathcal M}_{\rm A}^{-3}$, where $U_{\rm turb} \sim U_{B}$, the magnetic field becomes dynamically important, and turbulence transitions to the MHD regime.
 The cutoff scale in equation \ref{eqn:Wk} can be computed by setting the turbulent cascade rate for fast modes to the transit time damping rate on thermal electrons.
@@
 \begin{equation}
-k_{\rm c} \approx A k_{\rm outer} \frac{\langle v_{\rm outer}^{2}\rangle^{2}}{c_{\rm s}^{4}}
+k_{\rm c} \approx A k_{\rm outer} \frac{\langle \varv_{\rm outer}^{2}\rangle^{2}}{c_{\rm s}^{4}}
 \label{eqn:k_c} 
@@
 We assume an injection scale $k_{\rm L}=2\pi/\lambda_{\rm L}$, where $\lambda_{\rm L} = 100$ kpc, which were assumptions adopted in previous work \citep{2006MNRAS.366.1437S,brunetti07, brunetti11}.
-This lengthscale corresponds to an eddy turnover time on the outer scale of $v_{L} k_{\rm L}^{-1} \sim 1.2$Gyr if $v_{\rm L} \sim 500 {\rm km \, s^{-1}}$, as is characteristic of a merger.
+This lengthscale corresponds to an eddy turnover time on the outer scale of $\varv_{L} k_{\rm L}^{-1} \sim 1.2$Gyr if $\varv_{\rm L} \sim 500 {\rm km \, s^{-1}}$, as is characteristic of a merger.
 Note that hydrodynamical simulations of clusters have sometimes found larger $\lambda_{\rm L}$, in some cases comparable to the size of the cluster \citep{vazza11,miniati15}.
@@
 Let us ignore cooling.
-This is a good approximation for the CR protons, for instance, since hadronic cooling times are long\footnote{In principle, CRp can still lose energy via wave heating, at a rate $v_{\rm A} \cdot \nabla P_{c}$, but we assume CR streaming is suppressed during mergers, when they are spatially confined by scattering.} In this case, $\dot{p}= p/\tau_{\rm D}$, and after a time $\tau_{\rm cl}$, we have $p \rightarrow p \, {\rm exp}(\tau_{\rm cl}/\tau_{\rm D})$ (where we have used the fact that $\tau{\rm D}$ is momentum independent).
+This is a good approximation for the CR protons, for instance, since hadronic cooling times are long\footnote{In principle, CRp can still lose energy via wave heating, at a rate $\varv_{\rm A} \cdot \nabla P_{c}$, but we assume CR streaming is suppressed during mergers, when they are spatially confined by scattering.} In this case, $\dot{p}= p/\tau_{\rm D}$, and after a time $\tau_{\rm cl}$, we have $p \rightarrow p \, {\rm exp}(\tau_{\rm cl}/\tau_{\rm D})$ (where we have used the fact that $\tau{\rm D}$ is momentum independent).
 For an initial power law distribution function $f(p) = C p^{-\alpha}$, this momentum increase can be rewritten as a change of normalization, $f(p) = \tilde{C} p^{-\alpha}$, where $\tilde{C} = {\rm exp}( \alpha \tau_{\rm cl}/\tau_{\rm D})$.
@@
 This is subject to uncertainties about the location of the outer scale $L$; estimates in the literature range from $L \sim 0.1-1$ Mpc.
-It is also worth remembering that MHD turbulence only applies below $l < l_{\rm A}$, where $l_{\rm A}$ is the Alfv{\'e}n scale where $v \sim v_{\rm A}$.
+It is also worth remembering that MHD turbulence only applies below $l < l_{\rm A}$, where $l_{\rm A}$ is the Alfv{\'e}n scale where $\varv \sim \varv_{\rm A}$.
 Invoking fast modes, Kraichnan scalings, etc, is only valid below these scales.
@@
 \begin{equation}
-\frac{D_{\rm pp}^{\rm HD}}{D_{\rm pp}^{\rm MHD}} = \frac{k_{\rm L}^{2/3}k_{\rm A}^{1/3} v_{\rm c}^{2}}{k_{\rm A}^{1/2}k_{\rm c}^{1/2} v_{\rm A}^{2}} = A^{-1/2} \beta = 0.5 \left( \frac{\beta}{50} \right)
-\end{equation}
-where we have used $k_{\rm A} = k_{\rm L} M_{A}^{3}$ (from Kolmogorov scalings, and $M_{\rm A} = v_{\rm c}/v_{\rm A}$ is the Alfv{\'e}n Mach number of the turbulence, $\beta \approx c_{\rm s}^{2}/v_{\rm A}^{2}$, and the cutoff scale $k_{\rm c}$ (equation \ref{eqn:k_c}).
+\frac{D_{\rm pp}^{\rm HD}}{D_{\rm pp}^{\rm MHD}} = \frac{k_{\rm L}^{2/3}k_{\rm A}^{1/3} \varv_{\rm c}^{2}}{k_{\rm A}^{1/2}k_{\rm c}^{1/2} \varv_{\rm A}^{2}} = A^{-1/2} \beta = 0.5 \left( \frac{\beta}{50} \right)
+\end{equation}
+where we have used $k_{\rm A} = k_{\rm L} M_{A}^{3}$ (from Kolmogorov scalings, and $M_{\rm A} = \varv_{\rm c}/\varv_{\rm A}$ is the Alfv{\'e}n Mach number of the turbulence, $\beta \approx c_{\rm s}^{2}/\varv_{\rm A}^{2}$, and the cutoff scale $k_{\rm c}$ (equation \ref{eqn:k_c}).
 Thus, the contribution of the two regimes are comparable (as we shall see later, this is not true if one incorrectly assumes Kraichnan scalings apply from the outer scale $L$; this boosts the contribution of the scales where $l_{\rm A} < l < L$ by a factor $M_{\rm A}^{1/2}$).
-Henceforth, we can consider the outer scale of the fast modes to be $l_{\rm A}$, with velocity $v_{\rm A}$. The turbulent reacceleration time is: 
-\begin{equation}
-\tau_{\rm D} = \frac{p^{2}}{4 D_{\rm pp}} = C_{\rm D} A^{1/2} c k_{\rm A} \frac{v_{A}^{2}}{c_{\rm S}^{2}}
+Henceforth, we can consider the outer scale of the fast modes to be $l_{\rm A}$, with velocity $\varv_{\rm A}$. The turbulent reacceleration time is: 
+\begin{equation}
+\tau_{\rm D} = \frac{p^{2}}{4 D_{\rm pp}} = C_{\rm D} A^{1/2} c k_{\rm A} \frac{\varv_{A}^{2}}{c_{\rm S}^{2}}
 \label{eqn:tau_D} 
@@
 \begin{equation}
-\tau_{\rm decay} = \frac{c_{\rm s}}{v_{\rm A}^{2} k_{\rm A}}\,.
+\tau_{\rm decay} = \frac{c_{\rm s}}{\varv_{\rm A}^{2} k_{\rm A}}\,.
 \label{eqn:tau_decay} 
@@
 \begin{equation}
-\tau_{\rm decay} =\frac{L}{v_{\rm c}} \left(\frac{c_{\rm s}}{v_{\rm c}} \right)^{2} \frac{v_{\rm A}}{c_{\rm s}} = 0.7 \, \tau_{\rm edd} \left(\frac{\tilde{X}_{\rm tu}}{0.2}\right)^{-1}  \left(\frac{\beta}{100} \right)^{-1/2}
-\end{equation}
-where we have used $\tilde{X}_{\rm tu} \approx (v_{\rm c}/c_{\rm s})^{2}$ and $c_{\rm s}/v_{\rm A} = \beta^{1/2}$.
+\tau_{\rm decay} =\frac{L}{\varv_{\rm c}} \left(\frac{c_{\rm s}}{\varv_{\rm c}} \right)^{2} \frac{\varv_{\rm A}}{c_{\rm s}} = 0.7 \, \tau_{\rm edd} \left(\frac{\tilde{X}_{\rm tu}}{0.2}\right)^{-1}  \left(\frac{\beta}{100} \right)^{-1/2}
+\end{equation}
+where we have used $\tilde{X}_{\rm tu} \approx (\varv_{\rm c}/c_{\rm s})^{2}$ and $c_{\rm s}/\varv_{\rm A} = \beta^{1/2}$.
 Thus $\tau_{\rm decay} \sim \tau_{\rm edd}$, but we prefer to use the expression for $\tau_{\rm edd}$, since it is more physically correct and leads to more revealing scalings.
@@
 \end{equation}
-Remarkably, this expression is independent of properties of the turbulence such as $v_{\rm c},L$, or $l_{\rm A}$, and depends only on properties of the plasma ($c_{\rm s},\beta$).
-Ultimately, this arises because the timescale on which a fast mode wave transfers energy due to wave particle interactions in second order Fermi acceleration, $\tau_{\rm p} \sim (k_{\rm p} c (v_{\rm c}/c)^{2} )^{-1}$, is closely related to the timescale on which it cascades due to wave-wave interactions, $\tau_{\rm w} \sim c_{\rm s}/(k_{\rm w} v_{\rm c}^{2})$.
+Remarkably, this expression is independent of properties of the turbulence such as $\varv_{\rm c},L$, or $l_{\rm A}$, and depends only on properties of the plasma ($c_{\rm s},\beta$).
+Ultimately, this arises because the timescale on which a fast mode wave transfers energy due to wave particle interactions in second order Fermi acceleration, $\tau_{\rm p} \sim (k_{\rm p} c (\varv_{\rm c}/c)^{2} )^{-1}$, is closely related to the timescale on which it cascades due to wave-wave interactions, $\tau_{\rm w} \sim c_{\rm s}/(k_{\rm w} \varv_{\rm c}^{2})$.
 This implies $\tau_{\rm w}/\tau_{\rm p} \sim (c_{s}/c)(l_{\rm w}/l_{\rm p})$, where $l_{\rm w} \sim l_{\rm A}$ is the outer scale on which the fast mode cascade begins, and $l_{\rm p} \sim (l_{\rm A} l_{\rm c})^{1/2}$ is the characteristic wavelength for wave-particle interactions.
-For transit time damping and an outer scale of $l_{\rm A}$, we have $l_{\rm c} \sim (m_{\rm e}/m_{\rm p}) l_{\rm A} (c_{\rm s}/v_{\rm A})^{4}$.
+For transit time damping and an outer scale of $l_{\rm A}$, we have $l_{\rm c} \sim (m_{\rm e}/m_{\rm p}) l_{\rm A} (c_{\rm s}/\varv_{\rm A})^{4}$.
 We thus have $\tau_{\rm w}/\tau_{\rm p} \sim (c_{\rm s}/c)(l_{\rm A}/l_{\rm c})^{1/2} \sim (c_{\rm s}/c) (m_{\rm p}/m_{\rm e})^{1/2} \beta^{-1}$.
@@
 This implies that the energy-weighted scales at which wave-particle interaction take place are larger in Kolmogorov turbulence, and thus that the wave-particle interaction rate is lower.
-If (as is frequently seen) we instead assume that Kraichnan turbulence begins at the outer scale $L$, with characteristic decay time $L c_{\rm s}/v_{\rm c}^{2}$, then we obtain a more platable result:
+If (as is frequently seen) we instead assume that Kraichnan turbulence begins at the outer scale $L$, with characteristic decay time $L c_{\rm s}/\varv_{\rm c}^{2}$, then we obtain a more platable result:
 \begin{equation}
@@
 \begin{equation}
-D_{\rm pp}^{\rm CR} = \frac{2 p^{2} \zeta}{x_{\rm CR}} k_{\rm L} \frac{\langle v_{\rm c}^{2} \rangle^{2}}{c_{\rm s}^{3}}
+D_{\rm pp}^{\rm CR} = \frac{2 p^{2} \zeta}{x_{\rm CR}} k_{\rm L} \frac{\langle \varv_{\rm c}^{2} \rangle^{2}}{c_{\rm s}^{3}}
 \end{equation}
 where $\zeta$ is an efficiency factor for the the effectiveness of plasma instabilities (e.g., due to spatial or temporal intermittency), and $x_{\rm CR}=\eps_{\rm CR}/\eps_{\rm th}$ is the relative energy density of cosmic rays.
-If we set $k_{\rm L} \rightarrow k_{\rm A}$, $v_{c}^{2} \rightarrow v_{\rm A}^{2}$, as before, then:
+If we set $k_{\rm L} \rightarrow k_{\rm A}$, $\varv_{c}^{2} \rightarrow \varv_{\rm A}^{2}$, as before, then:
 \begin{equation}
@@
 However, there is a self-limiting asymptotic behaviour: as $x_{\rm CR}$ increases due to turbulent reacceleration, damping increases, which limits the further growth of the cosmic ray energy density \citep{brunetti11}.
-One natural assumption is to assume that $\eps_{\rm CR}$ saturates at a level $\eps_{\rm CR} \sim \eps_{\rm turb} (MHD) \sim \eps_{\rm B}$, in which case $x_{\rm CR} \sim \beta^{-1}$, so that:
+One natural assumption is to assume that $\eps_{\rm CR}$ saturates at a level $\eps_{\rm CR} \sim \eps_{\rm turb} ({\rm MHD}) \sim \eps_{\rm B}$, in which case $x_{\rm CR} \sim \beta^{-1}$, so that:
 \begin{equation}
@@
 A threshold value of $X_{\rm tu}$ is necessary for turbulent reacceleration to overcome cooling.
-Once that condition is satisfied, the condition $\tau_{\rm cl} \sim tau_{\rm D}$ implies a fixed amount of amplification: stronger turbulence implies faster acceleration, but also dissipates more quickly.
+Once that condition is satisfied, the condition $\tau_{\rm cl} \sim \tau_{\rm D}$ implies a fixed amount of amplification: stronger turbulence implies faster acceleration, but also dissipates more quickly.
 This leads to the asymptotic behavior seen.

### 2016-06-19 paper.tex
notation unified throughout the paper, text edited

@@
 
-\title[Origin of Seed Electrons]{Turbulence and Particle Acceleration in Giant Radio Halos: the Origin of Seed Electrons}
+\title[Origin of Seed Electrons]{Turbulence and Particle Acceleration in Giant Radio Haloes: the Origin of Seed Electrons}
 
@@
 \begin{abstract}
-  About one third of X-ray-luminous clusters show smooth, unpolarized
-  radio emission on $\sim$Mpc scales, known as giant radio halos. One
-  promising model for radio halos is Fermi II acceleration of seed
-  relativistic electrons by compressible turbulence in the
-  intracluster medium (ICM). The origin of these seed electrons has never
-  been fully explored. Here, we integrate the Fokker-Planck equation
-  of the cosmic ray (CR) electron and proton distributions in
-  cosmological simulations of cluster formation, and confront them with radio surface brightness and spectral observations of Coma. For standard
-  assumptions, structure formation shocks lead to a seed electron
-  population which produces too centrally concentrated radio
-  emission.
-By modifying properties of the CR population (rapid streaming; enhanced CR electron acceleration at shocks) or turbulence (increasing $\eps_{\rm turb}/\eps_{\rm therm}$ with radius), we can match observations, but only at the expense of fine-tuning.
-We then perform a parameter study.
-Under naive assumptions, radio properties are exponentially sensitive to the amplitude of turbulence, which is inconsistent with small scatter in scaling relations.
-This sensitivity can be removed if we relate the acceleration time to the turbulent dissipation time.
-Their ratio depends only on plasma parameters.
-In this case, turbulence above a threshold value required to overcome cooling provides a fixed amount of amplification; observations could then potentially constrain the unknown CR seed population.
-Understanding the small scatter in radio halo scaling relations may prove a rich source of insight on plasma processes in the ICM.
+  About one third of X-ray-luminous clusters show smooth, unpolarised radio
+  emission on $\sim$Mpc scales, known as giant radio haloes. One promising model
+  for radio haloes is Fermi II acceleration of seed relativistic electrons by
+  compressible turbulence in the intracluster medium (ICM). The origin of these
+  seed electrons has never been fully explored. Here, we integrate the
+  Fokker-Planck equation of the cosmic ray (CR) electron and proton
+  distributions in cosmological simulations of cluster formation, and confront
+  them with radio surface brightness and spectral observations of Coma. For
+  standard assumptions, structure formation shocks lead to a seed electron
+  population which produces too centrally concentrated radio emission. By
+  modifying properties of the CR population (rapid streaming; enhanced CR
+  electron acceleration at shocks) or turbulence (increasing
+  turbulent-to-thermal energy density with radius), we can match observations,
+  but only at the expense of fine-tuning. We then perform a parameter
+  study. Under naive assumptions, radio properties are exponentially sensitive
+  to the amplitude of turbulence, which is inconsistent with small scatter in
+  scaling relations. This sensitivity can be removed if we relate the
+  acceleration time to the turbulent dissipation time. Their ratio depends only
+  on plasma parameters. In this case, turbulence above a threshold value
+  required to overcome cooling provides a fixed amount of amplification;
+  observations could then potentially constrain the unknown CR seed
+  population. Understanding the small scatter in radio halo scaling relations
+  may prove a rich source of insight on plasma processes in the ICM.
 \end{abstract}
@@
 \section{Introduction}
-About one third of X-ray-luminous clusters show smooth, unpolarized
-radio emission on $\sim$Mpc scales, known as giant radio halos (RHs)
-\citep{2014IJMPD..2330007B}. They appear only in disturbed, merging
-clusters and the RH luminosity correlates with the X-ray luminosity
-\citep{2001A&A...369..441G,2012A&ARv..20...54F} and the Compton
-$y$-parameter \citep{2012MNRAS.421L.112B,2013A&A...554A.140P}. The RHs
-show that CR electrons and magnetic fields permeate a large volume
-fraction of the intra-cluster medium (ICM). The dominant CR source,
-given the smoothness and enormous extent of RHs, is thought to be
-structure formation shocks \citep{miniati01,pfrommer08}. At the same
-time, plasma processes, the origin of magnetic fields and particle
-acceleration in a turbulent, high-$\beta$ plasma like the ICM are not
-well understood. Radio halos thus provide an incisive probe of
-non-thermal processes in the ICM.
+About one third of X-ray-luminous clusters show smooth, unpolarised radio
+emission on $\sim$Mpc scales, known as giant radio haloes (RHs)
+\citep{2014IJMPD..2330007B}. They appear only in disturbed, merging clusters and
+the RH luminosity correlates with the X-ray luminosity
+\citep{2001A&A...369..441G,2012A&ARv..20...54F} and the Compton $y$-parameter
+\citep{2012MNRAS.421L.112B,2013A&A...554A.140P}. The RHs show that CR electrons
+and magnetic fields permeate a large volume fraction of the intra-cluster medium
+(ICM). The dominant CR source, given the smoothness and enormous extent of RHs,
+is thought to be structure formation shocks \citep{miniati01,pfrommer08}. At the
+same time, plasma processes, the origin of magnetic fields and particle
+acceleration in a turbulent, high-$\beta$ plasma (in which the thermal pressure
+predominates the magnetic pressure) like the ICM are not well understood. Radio
+haloes thus provide an incisive probe of non-thermal processes in the ICM.
 
@@
 
-The alternative model for RHs is re-energization of seed suprathermal
+The alternative model for RHs is re-energisation of seed suprathermal
 electrons by Fermi II acceleration when ICM turbulence becomes
-transonic during mergers
+transsonic during mergers
 \citep{1987A&A...182...21S,1993ApJ...406..399G,2001MNRAS.320..365B,
@@
 advected with the cluster plasma, their distribution will be peaked
-towards the cluster center and shows a similar characteristics as the
+towards the cluster centre and shows a similar characteristics as the
 thermal plasma. As a consequence, the distribution of secondary
@@
     profile. To better compare the two models in this figure, we
-    normalize the required distribution of CRps by fixing the total
-    CRp energy $E_\rmn{CR}$ to 0.3 percent of the total thermal
+    normalise the required distribution of CRps by fixing the total
+    CRp energy $E_\rmn{CR}$ to 0.3 per cent of the total thermal
     energy, consistent with observations
@@
 
-Indeed, arriving at a seed population with the required
-characteristics is highly constraining, and has the potential to teach
-us much about the origin of CRps/CRes in clusters.  In this work, we
-use our hydrodynamical zoom simulations of galaxy clusters in a
-cosmological setting to follow the distribution functions of seed
-populations for CRps and CRes, and integrate the Fokker-Planck
-equation of CR transport along Lagrangian particle trajectories. We
-model diffusive shock acceleration at structure formation shocks,
-and account for various loss processes of CRs. Utilizing new insights from our recent work on DSA generated
-  fossil electrons \citep{pinzke13}, we generate the first
+Indeed, arriving at a seed population with the required characteristics is
+highly constraining, and has the potential to teach us much about the origin of
+CRps/CRes in clusters.  In this work, we use our hydrodynamical zoom simulations
+of galaxy clusters in a cosmological setting to follow the distribution
+functions of seed populations for CRps and CRes, and integrate the Fokker-Planck
+equation of CR transport along Lagrangian particle trajectories. We model
+diffusive shock acceleration at structure formation shocks, and account for
+various loss processes of CRs. Utilising new insights from our recent work on
+DSA generated fossil electrons \citep{pinzke13}, we generate the first
 quantitative calculation of primary and secondary seed electrons
 
-To compare this to observations, we model second-order Fermi acceleration by CR interactions with
-magnetised turbulence. However, we assume a simplified and stationary model for magnetic
-fields and turbulence. We do not account for the time-varying energy
-density in compressible waves, which are thought to be necessary for
-the acceleration process \citep{brunetti07,brunetti11}, as the cluster
-merger proceeds.  So our approach is orthogonal (and complementary) to
-e.g., simulations of \citealp{miniati15} that focus on the
-time-dependent compressible turbulence while adopting a simplified
-treatment of CR. Our approach of parametrizing turbulence
-enables us to vary parameters associated with the spatial profile and the
-overall amplitude of compressible waves (that can in principle vary
-depending on the details of a particular cluster merger).
-
-In this paper, we explore how the radio surface brightness profile and spectrum of the best known radio halo, Coma, can be used to constrain the underlying properties of the seed cosmic rays and turbulence.
-We aim to constrain the normalization and spatial profile of these two input ingredients in turbulent reacceleration models.
-The outline of this paper is as follows.
-In \S\ref{sect:method}, we outline the basic physics of turbulence reacceleration of cosmic rays which we use.
-In \S\ref{sec:results}, we use cosmological simulations to generate a seed CR population, and combine it with our parameterized model of turbulence to produce radio surface brightness profiles and spectra of Coma.
-We find that it is possible to fit the observations using physically motivated modifications of the seed population
-(rapid streaming; enhanced CR electron acceleration at shocks) or turbulence (increasing $\eps_{\rm turb}/\eps_{\rm therm}$ with radius), but only at the expense of fine tuning.
-In \S\ref{sect:param_comp}, we explore the reason for this fine-tuning, and seek ways to overcome it.
-We perform a parameter study on spherically symmetric, static models where we vary properties of the seed population and turbulence.
-We find exponential sensitivity to the amount of turbulent, which can be eliminated if the turbulent acceleration and dissipation time are linked.
-In this case, turbulence above a threshold value required to overcome cooling provides a fixed amount of amplification; observations could then potentially constrain the unknown CR seed population.
-We summarize and conclude in \S\ref{sec:conclusions}.
+To compare this to observations, we model second-order Fermi acceleration by CR
+interactions with magnetised turbulence. However, we assume a simplified and
+stationary model for magnetic fields and turbulence. We do not account for the
+time-varying energy density in compressible waves, which are thought to be
+necessary for the acceleration process \citep{brunetti07,brunetti11}, as the
+cluster merger proceeds.  So our approach is orthogonal (and complementary) to
+e.g., simulations of \citealp{miniati15} that focus on the time-dependent
+compressible turbulence while adopting a simplified treatment of CR. Our
+approach of parametrizing turbulence enables us to vary parameters associated
+with the spatial profile and the overall amplitude of compressible waves (that
+can in principle vary depending on the details of a particular cluster merger).
+
+In this paper, we explore how the radio surface brightness profile and spectrum
+of the best known radio halo, Coma, can be used to constrain the underlying
+properties of the seed CRs and turbulence. We aim to constrain the normalisation
+and spatial profile of these two input ingredients in turbulent reacceleration
+models. The outline of this paper is as follows. In \S\ref{sect:method}, we
+outline the basic physics of turbulent reacceleration of CRs which we use. In
+\S\ref{sec:results}, we use cosmological simulations to generate a seed CR
+population, and combine it with our parametrized model of turbulence to produce
+radio surface brightness profiles and spectra of Coma. We find that it is
+possible to fit the observations using physically motivated modifications of the
+seed population (rapid streaming; enhanced CR electron acceleration at shocks)
+or turbulence (increasing the turbulent-to-thermal energy density, $\eps_{\rm
+  turb}/\eps_{\rm th}$ with radius), but only at the expense of fine
+tuning. In \S\ref{sect:param_comp}, we explore the reason for this fine-tuning,
+and seek ways to overcome it. We perform a parameter study on spherically
+symmetric, static models where we vary properties of the seed population and
+turbulence. We find exponential sensitivity to the amount of turbulence, which
+can be eliminated if the turbulent acceleration and dissipation time are
+linked. In this case, turbulence above a threshold value required to overcome
+cooling provides a fixed amount of amplification; observations could then
+potentially constrain the unknown CR seed population. We summarise and conclude
+in \S\ref{sec:conclusions}.
 
@@
 Fermi-LAT upper limits
-\citep{2012ApJ...757..123A,brunetti12,2014ApJ...787...18A}.
+\citep{2012ApJ...757..123A,brunetti12,2014ApJ...787...18A,Ahnen2016}.
 
@@
 f_{\rmn{e}}(p,t)\left[
-\left|\frac{dp}{dt}\right|_{\rm Coul} 
+\left|\frac{d p}{d t}\right|_{\rm Coul} 
 + \frac{p}{3}\left(\bnabla\bcdot \bvel\right)
-+ \left|\frac{dp}{dt}\right|_{\rm rad}\right.\right.
++ \left|\frac{d p}{d t}\right|_{\rm rad}\right.\right.
 \nonumber\\
-&-& \left.\left.{1\over{p^2}}{{\partial }\over{\partial p}}\left(p^2 D_{\rm pp}\right) 
+&-& \left.\left.{1\over{p^2}}{{\partial }\over{\partial p}}\left(p^2 D_{pp}\right) 
 \right]\right\} - \left(\bnabla\bcdot \bvel\right) f_{\rmn{e}}(p,t)
@@
 \left[
-D_{\rm pp} f_{\rmn{e}}(p,t) \right]+ Q_{\rmn{e}}\left[p,t;f_{\rmn{p}}(p,t)\right]   \, .
+D_{pp} f_{\rmn{e}}(p,t) \right]+ Q_{\rmn{e}}\left[p,t;f_{\rmn{p}}(p,t)\right]   \, .
 \label{elettroni}
@@
 (suppressed for clarity), momentum $p$ and time $t$ (which is
-normalized such that the number density is given by
-$n_{\rmn{e}}(t)=\int d p f_{\rmn{e}}(p,t)$), $d/dt=\partial/\partial
+normalised such that the number density is given by
+$n_{\rmn{e}}(t)=\int d p f_{\rmn{e}}(p,t)$), $d/d t=\partial/\partial
 t+\bvel\bcdot\bnabla$ is the Lagrangian derivative, $\bvel$ is the gas
-velocity, $|dp/dt|$ represents Coulomb
+velocity, $|d p/d t|$ represents Coulomb
 \citep[Coul,][]{1972Phy....60..145G} and radiative
@@
 \begin{eqnarray}
-   \left|\frac{dp}{dt}\right|_{\rm Coul} &=& \frac{3\,\sigma_\rmn{T}\,n_e\,c}{2\, \beta^2}
-  \left[\ln\left(\frac{m_e c^2 \beta \sqrt{\gamma-1}}{\hbar\,\omega_\rmn{plasma}}\right)\right.\nonumber \\
-    &-&\ln(2)\left(\frac{\beta^2}{2}+\frac{1}{\gamma}\right)+\frac{1}{2}+
+   \left|\frac{d p}{d t}\right|_{\rm Coul} &=& \frac{3\,\sigma_\rmn{T}\,n_{\rmn{e}}\,c}{2\, \beta_{\rmn{e}}^2}
+  \left[\ln\left(\frac{m_{\rmn{e}} c^2 \beta_{\rmn{e}} \sqrt{\gamma-1}}{\hbar\,\omega_\rmn{plasma}}\right)\right.\nonumber \\
+    &-&\ln(2)\left(\frac{\beta_{\rmn{e}}^2}{2}+\frac{1}{\gamma}\right)+\frac{1}{2}+
     \left.\left(\frac{\gamma-1}{4\gamma}\right)^2\right]\,, \\
-  \left|\frac{dp}{dt}\right|_{\rm rad~} &=& \frac{4}{3}\frac{\sigma_\rmn{T}}{m_ec}\,
-  \frac{p^2}{\beta}\,\left[1+\left(\frac{B}{B_\rmn{CMB}}\right)^2\right]\,.
+  \left|\frac{d p}{d t}\right|_{\rm rad~} &=& \frac{4}{3}\frac{\sigma_\rmn{T}}{m_{\rmn{e}}c}\,
+  \frac{p^2}{\beta_{\rmn{e}}}\,\left[1+\left(\frac{B}{B_\rmn{CMB}}\right)^2\right]\,.
 \end{eqnarray}
-Here $\beta = p/\sqrt{1+p^2}$ is the dimensionless velocity of CRs,
+Here $\beta_{\rmn{e}} = p/\sqrt{1+p^2}$ is the dimensionless velocity of CRs,
 $\gamma=\sqrt{1+p^2}$ is the Lorentz factor of CRs,
-$\omega_\rmn{plasma} = \sqrt{4\pi e^2 n_e / m_e}$ is the plasma
+$\omega_\rmn{plasma} = \sqrt{4\upi e^2 n_{\rmn{e}} / m_{\rmn{e}}}$ is the plasma
 frequency, $n_e$ is the number density of free electrons, and
-$\sigma_\rmn{T}= 8\pi e^4/3(m_e c^2)^2$ is the Thomson cross
+$\sigma_\rmn{T}= 8\upi e^4/3(m_{\rmn{e}} c^2)^2$ is the Thomson cross
 section. The {\it rms} magnetic field strength is denoted by $B$ and
 the equivalent field strength of the cosmic-microwave background is
-given by $B_\rmn{CMB} = 3.24 (1 + z)^2\mu\rmn{G}$, where $z$ denotes
+given by $B_\rmn{CMB} = 3.24 (1 + z)^2\umu\rmn{G}$, where $z$ denotes
 the redshift. In the peripheral cluster regions, where $B \ll
 B_\rmn{CMB}$, the CRes loose virtually all their energy by means of
-inverse Compton emission. $D_{\rm pp}$ is the momentum space diffusion
+inverse Compton emission. $D_{pp}$ is the momentum space diffusion
 coefficient (see \S\ref{sec:reacc}), and
@@
 
-During post-processing of our Coma-like cluster simulation, we solve
-the Fokker-Planck equation over a redshift interval from $z=5$ to
-0. The simulated cluster undergoes a major merger over the last
-1-2~Gyrs that is thought to inject large turbulent eddies. As is commonly assumed \citep{brunetti07,brunetti11,2004ApJ...614..757Y,2013ApJ...771..131B}
-we assume that about one Gyr after core passage the fields have
-decayed down to the smallest scales $k_{\rm cut}$, and the radio halo turns on
-shortly after. We choose this simulation snapshot to analyze. We are not very sensitive to this assumption, since the thermal and CR quantities are very similar a few
-100 Myrs before and after z = 0, where we have chosen to evaluate the
-simulations. In all our
-calculations we assume that turbulent reacceleration efficiently
-accelerates particles for $\tau{\rm cl} \sim 650$ Myrs (which is roughly the cascade
-time on which turbulence is damped) and that during this turbulent
-phase CR streaming and spatial diffusion can be neglected. In \S\ref{sect:self-limiting}, we explore sensitivity to the last assumption.
-
-Thus far, we have ignore CR transport. However, if CRps stream in the ICM, then their spatial profile could
-potentially flatten sufficiently \citep{ensslin11,wiener13}. This
-scenario is very attractive: it generates seed electrons with the
-right spatial footprint, and by removing CRps from the core, obeys
-gamma-ray constraints. Turbulence plays two opposing roles:
-Alfv{\'e}nic turbulence damps waves generated by the CR streaming
-instability \citep{yan02,farmer04}, thus reducing self-confinement;
-but compressible fast modes scatter CRs directly. Turbulent damping is
-still efficient for highly subsonic conditions \citep{wiener13}, while
-we assume compressible fast modes to only provide effective spatial
-confinement during the periods of transonic, highly super-Alfv{\'e}nic
-($M_{\rm A} \sim 5$) turbulence associated with mergers. Thus, CRs can
-stream out when the cluster is kinematically quiescent. Furthermore,
-even Alfv{\'e}nic streaming timescales are relatively short
-\cite[$\sim 0.1-0.5$ Gyr;][]{wiener13} compared to the timescale on
-which the CRp population is built up. Based on these findings, we
-adopt a toy model for our \Mstream scenario in which CR streaming
-instantaneously produces flat CRp profiles. We assume that CRs cannot stream significantly past
-perpendicular $B$-fields at the accretion shock, so that the total
-number of CRs is conserved within the virial radius during the
-streaming process.
-In all our calculations we assume that turbulent reacceleration
-efficiently accelerates particles for $\tau_\rmn{cl}\sim650$~Myrs
-(which is roughly the cascade time on which turbulence is damped) and
-that during this turbulent phase CR streaming and spatial diffusion
-can be neglected.
+During post-processing of our Coma-like cluster simulation, we solve the
+Fokker-Planck equation over a redshift interval from $z=5$ to 0. The simulated
+cluster undergoes a major merger over the last 1-2~Gyrs that is thought to
+inject large turbulent eddies. As is commonly assumed
+\citep{brunetti07,brunetti11,2004ApJ...614..757Y,2013ApJ...771..131B} we assume
+that about one Gyr after core passage the fields have decayed down to the
+smallest scales $k_{\rm cut}$, and the radio halo turns on shortly after. We
+choose this simulation snapshot to analyse. We are not very sensitive to this
+assumption, since the thermal and CR quantities are very similar a few 100 Myrs
+before and after $z = 0$, where we have chosen to evaluate the simulations. In
+all our calculations we assume that turbulent reacceleration efficiently
+accelerates particles for $\tau_{\rm cl} \sim 650$ Myrs (which is roughly the
+cascade time on which turbulence is damped) and that during this turbulent phase
+CR streaming and spatial diffusion can be neglected. In
+\S\ref{sect:self-limiting}, we explore sensitivity to the last assumption.
+
+Thus far, we have ignored CR transport. However, if CRps stream in the ICM, then
+their spatial profile could potentially flatten sufficiently
+\citep{ensslin11,wiener13}. This scenario is very attractive: it generates seed
+electrons with the right spatial footprint, and by removing CRps from the core,
+obeys gamma-ray constraints. Turbulence plays two opposing roles: Alfv{\'e}nic
+turbulence damps waves generated by the CR streaming instability
+\citep{yan02,farmer04}, thus reducing self-confinement; but compressible fast
+modes scatter CRs directly. Turbulent damping is still efficient for highly
+subsonic conditions \citep{wiener13}, while we assume compressible fast modes to
+only provide effective spatial confinement during the periods of transsonic,
+highly super-Alfv{\'e}nic ($\mathcal{M}_{\rm A} \sim 5$) turbulence associated with
+mergers. Thus, CRs can stream out when the cluster is kinematically
+quiescent. Furthermore, even Alfv{\'e}nic streaming timescales are relatively
+short \cite[$\sim 0.1-0.5$ Gyr;][]{wiener13} compared to the timescale on which
+the CRp population is built up. Based on these findings, we adopt a toy model
+for our \Mstream scenario in which CR streaming instantaneously produces flat
+CRp profiles. We assume that CRs cannot stream significantly past perpendicular
+$B$-fields at the accretion shock, so that the total number of CRs is conserved
+within the virial radius during the streaming process.  In all our calculations
+we assume that turbulent reacceleration efficiently accelerates particles for
+$\tau_\rmn{cl}\sim650$~Myrs (which is roughly the cascade time on which
+turbulence is damped) and that during this turbulent phase CR streaming and
+spatial diffusion can be neglected.
 
@@
   \left\{
-  f_{\rmn{p}}(p,t)\left[ \left|{{dp}\over{dt}}\right|_{\rm Coul}
+  f_{\rmn{p}}(p,t)\left[ \left|{{d p}\over{d t}}\right|_{\rm Coul}
     + \frac{p}{3}\bnabla\bcdot \left(\bvel+\bvel_{\rmn{st}}\right)\right.\right.}
 \nonumber\\
-&&-\left.\left. {1\over{p^2}}{{\partial }\over{\partial p}}\left(p^2 D_{\rm pp}\right)
+&&-\left.\left. {1\over{p^2}}{{\partial }\over{\partial p}}\left(p^2 D_{pp}\right)
 \right]\right\} - f_{\rmn{p}}(p,t) \bnabla\bcdot \left(\bvel+\bvel_{\rmn{st}}\right) 
@@
 &&+\,\,\, {{\partial^2 }\over{\partial p^2}}
-\left[ D_{\rm pp} f_{\rmn{p}}(p,t) \right] - {{f_{\rmn{p}}(p,t)}\over{\tau_{\rm had}(p)}}
+\left[ D_{pp} f_{\rmn{p}}(p,t) \right] - {{f_{\rmn{p}}(p,t)}\over{\tau_{\rm had}(p)}}
 + Q_{\rmn{p}}(p,t)\, ,
@@
 where we use the cross-section, $\sigma^{+/-,0}(p)$, given by the
-fitting formula in \citep{1986ApJ...307...47D}.
-
-\subsection{Turbulent Reacceleration}
+fitting formula in \citet{1986ApJ...307...47D}.
+
+\subsection{Turbulent reacceleration}
 \label{sec:reacc}
 
-In turbulent reacceleration, particles gain energy via Fermi II acceleration. Wave-particle energy exchange takes place via transit time damping \citep{brunetti07,brunetti11}. The
+In turbulent reacceleration, particles gain energy via Fermi II acceleration. Wave-particle energy exchange takes place via transit time damping \citep[TTD,][]{brunetti07,brunetti11}. The
 TTD resonance requires the wave frequency to obey the resonance
@@
 are in resonance with compressible waves experience Fermi-II
-acceleration irrespectively of the length scale of the perturbation.
+acceleration irrespective of the length scale of the perturbation.
 
@@
 assume that there exists a mechanism---such as the firehose
-instability---that isotropizes the CR distribution function at the
+instability---that isotropises the CR distribution function at the
 gyroscale and on the reacceleration time scale, which ensures
@@
 \begin{equation}
-D_{\rm pp}(p) = \frac{ p^{2} \pi I_{\theta}(c_{s}/c)}{8 c} \langle k \rangle_{\mathcal{W}} \langle (\delta \varv_{\rm c})^{2} \rangle
+D_{pp}(p) = \frac{ p^{2} \upi I_{\theta}(c_{s}/c)}{8 c} \langle k \rangle_{\mathcal{W}} \langle (\delta \varv_{\rm c})^{2} \rangle
 \label{eqn:diffusion}
@@
 \begin{equation}
-\langle k \rangle_{\mathcal{W}} = \frac{1}{\langle (\delta \varv_{\rm c})^{2} \rangle} \int_{k_{\rm L}}^{k_{\rm cut}} dk \, k \, \mathcal{W}(k) \approx \frac{s-1}{2-s} k_{\rm L} \left( \frac{k_{\rm cut}}{k_{\rm L}} \right)^{2-s}
+\langle k \rangle_{\mathcal{W}} = \frac{1}{\langle (\delta \varv_{\rm c})^{2} \rangle} \int_{k_L}^{k_{\rm cut}} d k \, k \, \mathcal{W}(k) \approx \frac{s-1}{2-s} k_L \left( \frac{k_{\rm cut}}{k_L} \right)^{2-s}
 \label{eqn:k_W} 
 \end{equation}
-is an energy-averaged wavenumber, $k_{\rm L}, k_{\rm cut}$ are the wavenumbers associated with the outer scale and the cutoff scale respectively, and we have assumed a total energy spectrum (both kinetic and potential energy, where the two are assumed to be in equipartition \citep{sarkar11}):
-\begin{equation}
-\mathcal{W}(k) = \frac{(s-1) \langle (\delta \varv_{\rm c})^{2} \rangle}{k_{\rm L}} \left( \frac{k}{k_{\rm L}} \right)^{-s} 
+is an energy-averaged wavenumber, $k_L, k_{\rm cut}$ are the wavenumbers associated with the outer scale $L$ and the cutoff scale respectively, and we have assumed a total energy spectrum (composed of both kinetic and potential energy, where the two are assumed to be in equipartition, \citealt{sarkar11}):
+\begin{equation}
+\mathcal{W}(k) = \frac{(s-1) \langle (\delta \varv_{\rm c})^{2} \rangle}{k_L} \left( \frac{k}{k_L} \right)^{-s} 
 \label{eqn:Wk}
 \end{equation}
-which defines the normalization $\langle (\delta \varv_{\rm c})^{2} \rangle$ (the subscript 'c' emphasizes that we specialize to compressive modes).
+which defines the normalisation $\langle (\delta \varv_{\rm c})^{2} \rangle$ (the subscript 'c' emphasizes that we specialise to compressive modes).
 Intuitively, we can understand the form of the the diffusion coefficient from the fact that for second-order Fermi acceleration, $\dot{p} \sim \Delta p/\tau \sim p\,\langle k c \rangle_{\mathcal{W}} (\delta \varv_{\rm c}/c)^{2}$, where $\tau^{-1} \sim \langle k c \rangle_{\mathcal{W}}$ is the energy averaged wave-particle interaction rate, and $\Delta p \sim p (\delta \varv_{\rm c}/c)^{2}$ is the typical momentum change during wave particle scattering.
@@
 \begin{equation}
-D_{\rm pp} \sim p \dot{p} \sim p^{2} \langle k c \rangle_{\mathcal{W}} \left( \frac{\delta \varv_{\rm c}}{c} \right)^{2}. 
-\end{equation}
-
-Equations \ref{eqn:diffusion} and \ref{eqn:Wk} make the important aspects of turbulence clear: the energy in compressive modes $\langle (\delta \varv_{\rm c})^{2} \rangle$, the inner and outer scale ($k_{\rm cut}$ and $k_{\rm L}$), and the slope of the energy spectrum $s$.
+D_{pp} \sim p \dot{p} \sim p^{2} \langle k c \rangle_{\mathcal{W}} \left( \frac{\delta \varv_{\rm c}}{c} \right)^{2}. 
+\end{equation}
+
+Equations \ref{eqn:diffusion} and \ref{eqn:Wk} make the important aspects of turbulence clear: the energy in compressive modes $\langle (\delta \varv_{\rm c})^{2} \rangle$, the inner and outer scale ($k_{\rm cut}$ and $k_L$), and the slope of the energy spectrum $s$.
 All of these can vary spatially and temporally.
@@
   \mathcal{W}(k) =
-\sqrt{2/7\,I_0\,\rho\,\langle \Vph \rangle}\,k^{-3/2},
-\end{equation}
-where $I_{\rm 0}$ is the volumetric injection rate of turbulence (which is assumed to be constant), $\varv_{\rm ph}\approx c_{\rm s}$ is the phase speed of waves.
-It is important to realize that this only applies at small scales, which turbulence is MHD.
+\sqrt{2/7\,I_L\,\rho\,\langle \Vph \rangle}\,k^{-3/2},
+\end{equation}
+where $I_L$ is the volumetric injection rate of turbulence at scale $L$ (which is assumed to be constant), $\varv_{\rm ph}\approx c_{\rm s}$ is the phase speed of waves.
+It is important to realise that this only applies at small scales, where turbulence is magneto-hydrodynamical.
 At large scales, turbulent motions are subsonic (${\mathcal M}_{\rm s} \sim 0.2-0.5$) but super-Alfv{\'e}nic (${\mathcal M}_{\rm A} \sim 5$).
-Thus, except in the case where motions are transonic and weak shocks become important, motions are fundamentally hydrodynamic and turbulence follows a Kolmogorov ($s=5/3$) spectrum.
-However, while the turbulent energy density $U_{\rm t} \propto l^{2/3}$ decreases at small scales, the magnetic energy density is scale-independent.
-Thus, at some scale $l_{\rm A} \sim l_0 {\mathcal M}_{\rm A}^{-3}$, where $U_{\rm turb} \sim U_{B}$, the magnetic field becomes dynamically important, and turbulence transitions to the MHD regime.
+Thus, except in the case where motions are transsonic and weak shocks become important, motions are fundamentally hydrodynamic and turbulence follows a Kolmogorov ($s=5/3$) spectrum.
+However, while the turbulent energy density $\eps_{\rm turb} \propto l^{2/3}$ decreases at small scales, the magnetic energy density is scale-independent.
+Thus, at some scale $l_{\rm A} \sim l_L {\mathcal M}_{\rm A}^{-3}$, where $\eps_{\rm turb} \sim \eps_{B}$, the magnetic field becomes dynamically important, and turbulence transitions to the MHD regime.
 The cutoff scale in equation \ref{eqn:Wk} can be computed by setting the turbulent cascade rate for fast modes to the transit time damping rate on thermal electrons.
@@
 \begin{equation}
-k_{\rm c} \approx A k_{\rm outer} \frac{\langle \varv_{\rm outer}^{2}\rangle^{2}}{c_{\rm s}^{4}}
+k_{\rm cut} \approx A k_L \frac{\langle \varv_L^{2}\rangle^{2}}{c_{\rm s}^{4}}
+%k_{\rm c} \approx A k_{\rm outer} \frac{\langle \varv_{\rm outer}^{2}\rangle^{2}}{c_{\rm s}^{4}}
 \label{eqn:k_c} 
@@
 Another possibility is that compressible modes dissipate in weak shocks, resulting in Burgers' turbulence $s=2$ \citep{kowal10,porter15,miniati15}.
-If Burgers turbulence dominates, then particle acceleration rates are too slow in the face of cooling processes to explain radio halos \citep{miniati15}, and an alternative model for radio halos is required.
+If Burgers turbulence dominates, then particle acceleration rates are too slow in the face of cooling processes to explain radio haloes \citep{miniati15}, and an alternative model for radio haloes is required.
 
@@
 assume that volumetric injection rate of turbulent energy,
-$I_0\propto \eps_\rmn{th}^{\alpha_\rmn{tu}}$, and determine the
-normalization by requiring that the turbulent energy in compressible
+$I_L\propto \eps_\rmn{th}^{\alpha_\rmn{tu}}$, and determine the
+normalisation by requiring that the turbulent energy in compressible
 modes $E_\rmn{turb}=\int \int \mathcal{W}(k) \rmn{d}k \rmn{d}V =
@@
   \label{eq:Dpp_scaling}
-  D_{\rm pp}\propto \frac{I_0}{\rho c_{\rmn{s}}} \propto 
-X_\rmn{tu}^2k_{\rm L} \eps_\rmn{th}^{\alpha_\rmn{tu}-1}\sqrt{T}\,.
-\end{equation}
-
-What is a typical energy density in compressive fast modes?
-The total turbulent energy is typically $\sim 15-70\%$ of the thermal energy in a cluster \citep{vazza11}; it rises rapidly during a merger.
-The compressible component is $\sim 20-40\%$ of the total turbulent energy, and shows more rapid temporal variations compared to the compressible component \citep{2013ApJ...771..131B,miniati15}.
-Note the compressible component in cluster simulations is much larger than that seem in stirring box simulations with similar Mach numbers \citep{kowal10,lynn14}.
-This is likely due to the compressive nature of turbulent driving (transonic infall and merger), whereas idealized simulations tend to use incompressible solenoidal driving and allow compressive fluctuations to develop on their own.
-Overall, we adopt a compressive energy density which is $X_{\rm tu} \sim 0.2$ of the thermal energy as a baseline estimate.
-
-The important effects are best summarized in terms of the acceleration time: 
-\begin{equation}
-\tau_{\rm D}= \frac{p^{2}}{4 D_{\rm pp}}
+  D_{pp}\propto \frac{I_L}{\rho c_{\rmn{s}}} \propto 
+X_\rmn{tu}^2k_L \eps_\rmn{th}^{\alpha_\rmn{tu}-1}\sqrt{T}\,.
+\end{equation}
+
+What is a typical energy density in compressive fast modes? The total turbulent
+energy is typically $\sim 15-70$ per cent of the thermal energy in a cluster
+\citep{vazza11}; it rises rapidly during a merger. The compressible component is
+$\sim 20-40$ per cent of the total turbulent energy, and shows more rapid temporal
+variations compared to the compressible component
+\citep{2013ApJ...771..131B,miniati15}. Note the compressible component in
+cluster simulations is much larger than in stirring box simulations
+with similar Mach numbers \citep{kowal10,lynn14}. This is likely due to the
+compressive nature of turbulent driving (transsonic infall and merger), whereas
+idealised simulations tend to use incompressible solenoidal driving and allow
+compressive fluctuations to develop on their own. Overall, we adopt a
+compressive energy density which is $X_{\rm tu} \sim 0.2$ of the thermal energy
+as a baseline estimate.
+
+The important effects are best summarised in terms of the acceleration time: 
+\begin{equation}
+\tau_{\rm D}= \frac{p^{2}}{4 D_{pp}}
 \end{equation}
@@
 The densities \citep{1992A&A...259L..31B} and temperatures \citep{2009ApJ...696.1886B,2001A&A...365L..67A} are derived from X-ray observations.
-To calculate synchrotron cooling times, we use B-fields derived from Faraday rotation measurements \citep{bonafede10}.
+To calculate synchrotron cooling times, we use $B$-fields derived from Faraday rotation measurements \citep{bonafede10}.
 To calculate the acceleration time, we need to assume an outer scale.
-We assume an injection scale $k_{\rm L}=2\pi/\lambda_{\rm L}$, where $\lambda_{\rm L} = 100$ kpc, which were assumptions adopted in previous work \citep{2006MNRAS.366.1437S,brunetti07, brunetti11}.
-This lengthscale corresponds to an eddy turnover time on the outer scale of $\varv_{L} k_{\rm L}^{-1} \sim 1.2$Gyr if $\varv_{\rm L} \sim 500 {\rm km \, s^{-1}}$, as is characteristic of a merger.
-Note that hydrodynamical simulations of clusters have sometimes found larger $\lambda_{\rm L}$, in some cases comparable to the size of the cluster \citep{vazza11,miniati15}.
-This choice is degenerate with $X_{\rm tu}$; in \S\ref{sect:self-limiting} we argue that $k_{\rm A}$ is a more appropriate choice, but also find that when the decay time is appropriately scaled, we are relatively insensitive to the choice of $k_{\rm L}$.
+We assume an injection scale $k_L=2\upi/\lambda_L$, where $\lambda_L = 100$ kpc, which were assumptions adopted in previous work \citep{2006MNRAS.366.1437S,brunetti07, brunetti11}.
+This length scale corresponds to an eddy turnover time on the outer scale of $\varv_L k_L^{-1} \sim 1.2$~Gyr if $\varv_L \sim 500 {\rm km \, s^{-1}}$, as is characteristic of a merger.
+Note that hydrodynamical simulations of clusters have sometimes found larger $\lambda_L$, in some cases comparable to the size of the cluster \citep{vazza11,miniati15}.
+This choice is degenerate with $X_{\rm tu}$; in \S\ref{sect:self-limiting} we argue that $k_{\rm A}$ is a more appropriate choice, but also find that when the decay time is appropriately scaled, we are relatively insensitive to the choice of $k_L$.
 We present $\tau_{\rm D}$ for 3 different models, which we discuss in the next section.
@@
 $\tau_{\rm D}$ is similar between our three models, where the
-difference comes from turbulent profile parameterized with
+difference comes from turbulent profile parametrized with
 $\alpha_\rmn{tu}$. This implies that even small differences in the
@@
 $\tau_\rmn{D}$(\Mflatturb)$^{(3)}$  [Gyr] & 0.69 & 0.56 & 0.27 \\
-$\tau_\rmn{IC/sync}(P=10^4\,m_ec)^{(4)}$ [Gyr] & 0.11 & 0.15 & 0.22 \\
-$\tau_\rmn{had}(P=100\,m_pc)^{(5)}$ [Gyr] & 2.4 & 4.5 & 47 \\
-$\tau_\rmn{Coul}(P=\,m_ec)^{(6)}$  [Gyr] & 0.0092 & 0.017 & 0.17 \\
+$\tau_\rmn{IC/sync}(P=10^4\,m_{\rmn{e}}c)^{(4)}$ [Gyr] & 0.11 & 0.15 & 0.22 \\
+$\tau_\rmn{had}(P=100\,m_{\rmn{p}}c)^{(5)}$ [Gyr] & 2.4 & 4.5 & 47 \\
+$\tau_\rmn{Coul}(P=\,m_{\rmn{e}}c)^{(6)}$  [Gyr] & 0.0092 & 0.017 & 0.17 \\
 \hline
@@
  (5) Catastrophic losses for protons.\\
- (6) Coulomb cooling for electrons (protons factor $m_e/m_p$ smaller).\\
+ (6) Coulomb cooling for electrons (protons factor $m_{\rmn{e}}/m_{\rmn{p}}$ smaller).\\
  \label{tab:timescales}
@@
 
-In this section, we solve the Fokker-Planck equation for CR transport
-on Lagrangian particle trajectories through cosmic history.
-We then use our parameterized model of turbulence to apply turbulence re-acceleration, and compare radio halo profiles against observations of the Coma cluster.
-Our philosophy to is make assumptions roughly in line with previous successful models, which are now confronted with more accurate calculations of the seed CR population, and find the minimal modifications required to fit observations.
-We re-examine these choices in \S\ref{sect:param_comp}.
-
-Since the standard vanilla model requires a CR seed population which is inconsistent with the simulations (Fig \ref{fig:Edens}), some modifications are necessary, either in the seed CR population or in the properties of turbulence.
-We focus on three scenarios.
-(i) In model {\em M-primaries}, we
-assume that CR electrons, which have been accelerated by cosmic
-formation shocks and successively cooled by inverse Compton and
-synchrotron losses, form a fossil seed population for
-reacceleration. (ii) In model {\em M-streaming}, we account for the
-outward streaming of central CRps, which produces a flat CR
-distribution in the ICM and equivalently a flat secondary seed
-population of CRe for reacceleration. (iii) In model {\em
-  M-turbulence} we adopt a spatially flatter turbulent profile than
-what was adopted before but assume that seed CRps and secondary CRes
-follow the steep profile that is suggested by structure formation
+In this section, we solve the Fokker-Planck equation for CR transport on
+Lagrangian particle trajectories through cosmic history. We then use our
+parametrized model of turbulence to apply turbulent re-acceleration, and
+compare radio halo profiles against observations of the Coma cluster. We follow
+the philosophy of adopting assumptions roughly in line with previous successful
+models, which are now confronted with more accurate calculations of the seed CR
+population, and find the minimal modifications required to fit observations. We
+re-examine these choices in \S\ref{sect:param_comp}.
+
+Since the standard vanilla model requires a CR seed population which is
+inconsistent with the simulations (Fig \ref{fig:Edens}), some modifications are
+necessary, either in the seed CR population or in the properties of
+turbulence. We focus on three scenarios. (i) In model {\em M-primaries}, we
+assume that CR electrons, which have been accelerated by cosmic formation shocks
+and successively cooled by inverse Compton and synchrotron losses, form a fossil
+seed population for reacceleration. (ii) In model {\em M-streaming}, we account
+for the outward streaming of central CRps, which produces a flat CR distribution
+in the ICM and equivalently a flat secondary seed population of CRes for
+reacceleration. (iii) In model {\em M-turbulence} we adopt a spatially flatter
+turbulent profile than what was adopted before but assume that seed CRps and
+secondary CRes follow the steep profile that is suggested by structure formation
 simulations.
@@
 \end{equation}
-determined by the normalization $C(t)$ and the spectral index
+determined by the normalisation $C(t)$ and the spectral index
 $\alpha_{\rmn{inj}}$ that depends on the adiabatic index
@@
 \end{eqnarray}
-where $E(p) = (\sqrt{1+p^2} -1)\, m\,c^2$ is the kinetic energy of a
-particle with momentum $p$. We adopt a fit to Monte Carlo simulations
-of the thermal leakage process that relates the momentum of injected
-protons ($p_\rmn{inj}$) to the thermal energy ($p_\rmn{th}$) of the
-shocked plasma \citep{kang11}:
+where $E(p) = (\sqrt{1+p^2} -1)\, m_{\rmn{p}}\,c^2$ is the kinetic energy of a
+proton with momentum $p$. We adopt a fit to Monte Carlo simulations of the
+thermal leakage process that relates the momentum of injected protons
+($p_\rmn{inj}$) to the thermal energy ($p_\rmn{th}$) of the shocked plasma
+\citep{kang11}:
 \begin{eqnarray}
   \label{eq:qinj}
-  p_\rmn{inj} &=& x_\rmn{inj} p_\rmn{th} = x_\rmn{inj} \sqrt{\frac{2 \,\kB T_2}{m c^2}}\,, \nonumber \\
+  p_\rmn{inj} &=& x_\rmn{inj} p_\rmn{th} =
+  x_\rmn{inj} \sqrt{\frac{2 \,\kB T_2}{m_{\rmn{p}} c^2}}\,, \nonumber \\
   \rmn{where}\quad x_\rmn{inj} &\approx& 1.17 \frac{\varv_2}{p_{\rmn{th}}\,c} \left(1+
@@
 which -- as we will later see -- corresponds to a conservative maximum
-energy acceleration efficiency for protons of $10\%$. To derive the
+energy acceleration efficiency for protons of $0.1$. To derive the
 acceleration efficiency, $\zeta_\rmn{inj}$, we first have to infer the
@@
 CR number density $n_\rmn{p}$. Hence we can solve for the
-renormalized normalization constant $C_\rmn{sub}$ using $n_\rmn{p}$
+renormalised normalisation constant $C_\rmn{sub}$ using $n_\rmn{p}$
 and Eqn.~\ref{eq:eta}:
@@
 accelerated proton-to-dissipated energy in the downstream of strong
-shocks that varies from $\zeta_\rmn{max} \sim 1-10\%$, depending on
+shocks that varies from $\zeta_\rmn{max} \sim 0.01-0.1$, depending on
 the adopted model (for more details, see Section \ref{sec:results}).
 
-In our Galaxy, the CRe-to-CRp ratio at a few GeV is $K_{\rmn{ep}} \sim
+In our Galaxy, the CRe-to-CRp ratio at a few GeV is $K_{\rmn{ep}} \approx
 10^{-2}$. Hence, we adopt this as a fiducial value for the CRe-to-CRp
-acceleration efficiency \citep[see][for more
-  discussion]{pinzke13}. However, as recent PIC simulations have
-shown, this is likely very different at weak shocks, with electrons
+acceleration efficiency in our models {\em M-streaming} and {\em M-turbulence}
+\citep[see][for more discussion]{pinzke13}. However, as recent PIC simulations
+have shown, this is likely very different at weak shocks, with electrons
 efficiently accelerated at perpendicular shocks
-\citep{2014ApJ...794..153G,2014ApJ...797...47G}, and ions efficiently
-accelerated at parallel shocks \citep{2014ApJ...783...91C}. Thus,
-depending on magnetic geometry, $K_{\rmn{ep}}$ could be either larger
-or smaller. Some observations of radio relics suggest high values of
-$K_{\rmn{ep}}$, due to the absence of gamma-ray emission, which probes
-the CRp population \citep{2014MNRAS.437.2291V}. This suggests primary
-CRes as a viable alternative scenario to secondary CRes as seeds for
-the giant RHs. In our {\em M-primaries} scenario, the injected
-distribution of CRes is derived in the same way as for the CRps. Once
-they have been accelerated to relativistic energies, injected
-electrons and protons are indistinguishable. We therefore assume that
-CRp and CRe have the same distribution function $f_\rmn{e}(p) =
-K_\rmn{ep} f_\rmn{p}(p)$, with a different normalization (due to
-differing acceleration efficiencies) $K_\rmn{ep}=0.1$ \citep[which is
-  viable for primarily perpendicular
-  shocks,][]{2014ApJ...794..153G}. Given the unknown magnetic geometry at cluster shocks, we investigate the consequences of this additional degree of freedom.
+\citep{2014ApJ...794..153G,2014ApJ...797...47G}, and ions (and electrons)
+efficiently accelerated at parallel shocks \citep{2014ApJ...783...91C,
+  Park2015}. Thus, depending on magnetic geometry, $K_{\rmn{ep}}$ could be
+either larger or smaller. Some observations of radio relics suggest high values
+of $K_{\rmn{ep}}$, due to the absence of gamma-ray emission, which probes the
+CRp population \citep{2014MNRAS.437.2291V}. This suggests primary CRes as a
+viable alternative scenario to secondary CRes as seeds for the giant RHs. In our
+{\em M-primaries} scenario, the injected distribution of CRes is derived in the
+same way as for the CRps. Once they have been accelerated to relativistic
+energies, injected electrons and protons are indistinguishable. We therefore
+assume that CRp and CRe have the same distribution function $f_\rmn{e}(p) =
+K_\rmn{ep} f_\rmn{p}(p)$, with a different normalisation (due to differing
+acceleration efficiencies) $K_\rmn{ep}=0.1$ \citep[which is viable for primarily
+  perpendicular shocks,][]{2014ApJ...794..153G}. Given the unknown magnetic
+geometry at cluster shocks, we investigate the consequences of this additional
+degree of freedom.
 
@@
 \end{minipage}
-\caption{Radio surface brightness profiles of Fermi-II reaccelerated
-  CR electrons of a simulated post-merging cluster similar to Coma. We
-  compare profiles at 352~MHz \citep[blue lines and
-    crosses,][]{brown11} to those at 1.4~GHz \citep[green lines and
-    crosses,][]{deiss97}. The red crosses show the reprocessed 1.4~GHz
-  data, where a zero level of about 10~\% of the central value is
-  adopted. The solid lines show predicted emission from a
-  reaccelerated fossil population, while dotted lines show emission
-  from a fossil population without reacceleration. The panels show the
-  emission of our models \Mprimary (upper left panel), \Mstream (upper
-  right panel), \Mflatturb (lower left panel), and simulated secondary
-  electrons together with previous estimates \citep{brunetti12} for
-  the Coma cluster (lower right panel).}
+\caption{Radio surface brightness profiles of Fermi-II reaccelerated CR
+  electrons of a simulated post-merging cluster similar to Coma. We compare
+  profiles at 352~MHz \citep[blue lines and crosses,][]{brown11} to those at
+  1.4~GHz \citep[green lines and crosses,][]{deiss97}. The red crosses show the
+  reprocessed 1.4~GHz data, where a zero level of about 0.1 of the central value
+  is adopted. The solid lines show predicted emission from a reaccelerated
+  fossil population, while dotted lines show emission from a fossil population
+  without reacceleration. The panels show the emission of our models \Mprimary
+  (upper left panel), \Mstream (upper right panel), \Mflatturb (lower left
+  panel), and simulated secondary electrons together with previous estimates
+  \citep{brunetti12} for the Coma cluster (lower right panel).}
   \label{fig:sync_profile}
@@
 reproduce the Coma RH profile at 352~MHz.  Adopting our
-parametrisation for the volumetric injection rate of turbulent energy,
+parametrization for the volumetric injection rate of turbulent energy,
 $I_0\propto \eps_\rmn{th}^{\alpha_\rmn{tu}}$, we find that to fit the observations, we require
@@
 relative CRp number density inside the RH for \Mflatturb (\Mstream),
-are found to be 2 (3) \% and $2\times10^{-8}$ ($5\times10^{-8}$),
+are found to be 2 (3) per cent and $2\times10^{-8}$ ($5\times10^{-8}$),
 respectively.
@@
     $\eps_\rmn{turb} \propto
-    \eps_\rmn{th}^{(\alpha_{\rmn{tu}}+1)/2}/T^{1/4}$ and
-    normalized such that the total turbulent energy in compressible
-    modes $E_\rmn{turb}$ for each scenario makes up about 20\% of the
+    \eps_\rmn{th}^{(\alpha_{\rmn{tu}}+1)/2}\,T^{-1/4}$ and
+    normalised such that the total turbulent energy in compressible
+    modes $E_\rmn{turb}$ for each scenario makes up about 20 per cent of the
     total thermal energy $E_\rmn{th}$ inside the radio halo
@@
 
-Figure~\ref{fig:sync_profile} demonstrates that the modeled radio
+Figure~\ref{fig:sync_profile} demonstrates that the modelled radio
 profiles without turbulent reacceleration are too steep.  In the
-bottom right panel of Fig.~\ref{fig:sync_profile} (labeled with
+bottom right panel of Fig.~\ref{fig:sync_profile} (labelled with
 Brunetti et al. 2012), we show that our simulated profiles of
@@
 this conclusion much because of the weak radial dependence of
-$D_{\rm pp}(R)\propto \eps_\rmn{th}(R)^{\alpha_\rmn{tu}-1}
+$D_{pp}(R)\propto \eps_\rmn{th}(R)^{\alpha_\rmn{tu}-1}
 \sqrt{T(R)}$. This signals that the problem is generic and requires
@@
 
-In Figure~\ref{fig:tauD} we show how the turbulent reacceleration
+In Fig.~\ref{fig:tauD} we show how the turbulent reacceleration
 timescales in our three models scale with radius. As expected, the
@@
 radius driven by the decrease in thermal energy density. The
-\Mflatturb model has the the flattest turbulent profile parameterized
+\Mflatturb model has the the flattest turbulent profile parametrized
 by the smaller $\alpha_\rmn{tu}$ which explains the steepest $\tau_{\rm D}$
@@
 explain the observations at each radius and for each model (see also
-Table~\ref{tab:timescales}). Since $\tau_\rmn{cl} \propto X_\rmn{tu}^2 k_0$,
+Table~\ref{tab:timescales}). Since $\tau_\rmn{cl} \propto X_\rmn{tu}^2 k_L$,
 these two parameters are degenerate and can be traded off one another.
@@
 instance, due to errors in point source subtraction. Interestingly, we
-can match the 1.4 GHz data if we reduce the zero point by adding 10\%
+can match the 1.4 GHz data if we reduce the zero point by adding 0.1
 of the central flux to every data point; this flattens the outer
@@
 Alternatively, this may point to weaknesses in the theoretical
-modeling of the particle acceleration process and may require a
+modelling of the particle acceleration process and may require a
 stronger cutoff in the particle energy spectrum.
@@
 emission from secondary CRes are smoothly distributed around the
-cluster because of the continuous injection, hence the it is not
+cluster because of the continuous injection, hence it is not
 dominated by outliers.
@@
 fixed. Although, we caution the reader to take this limit too
-stringent because of the uncertainty in $k_0$ and $\tau_\rmn{cl}$ that
+stringent because of the uncertainty in $k_L$ and $\tau_\rmn{cl}$ that
 impact $X_\rmn{tu}$ for a fixed $\tau_\rmn{D}$. This parameter space
@@
     primary CRes and the right figure shows the emission from
-    secondary CRes. The different line colors represent our different
+    secondary CRes. The different line colours represent our different
     models, \Mprimary (red line), \Mstream (blue line), and \Mflatturb
@@
 \subsection{Gamma rays}
-The gamma-ray emission from CRps that produce decaying neutral pions
-could be substantial if the CRps are reaccelerated efficiently enough,
-hence it is interesting to estimate this emission for our models and
-compare to upper limits. We follow the formalism outlined in
-  \cite{1999APh....12..169B} (and references therein) and calculate
-  the gamma-ray emission numerically for our three models. We predict
-the gamma-ray emission from \Mflatturb (\Mstream) with
-$F_\gamma(>500\,\rmn{MeV})=4\times10^{-10} (5\times10^{-10}) \mathrm{
-  \,ph\, s}^{-1}\mathrm{cm}^{-2}$. The fluxes from these models are
-slightly larger than in \cite{brunetti12}, where the differences comes
-from our steeper CRp profiles in addition to simulation based
-formalism we rely on that accounts for both Coulomb and hadronic
-losses during the build up of the CR distribution in contrast to the
-scaling relations adopted in their paper. Interestingly the gamma-ray
-flux from both our scenarios are just below recent Fermi-LAT limits
-derived from a gamma-ray profile similar to \Mflatturb where
+The gamma-ray emission from CRps that produce decaying neutral pions could be
+substantial if the CRps are reaccelerated efficiently enough, hence it is
+interesting to estimate this emission for our models and compare to upper
+limits. We follow the formalism outlined in \cite{1999APh....12..169B} (and
+references therein) and calculate the gamma-ray emission numerically for our
+three models. We predict the gamma-ray emission from \Mflatturb (\Mstream) with
+$F_\gamma(>500\,\rmn{MeV})=4\times10^{-10} (5\times10^{-10}) \mathrm{ \,ph\,
+  s}^{-1}\mathrm{cm}^{-2}$. The fluxes from these models are slightly larger
+than in \cite{brunetti12}, where the differences comes from our steeper CRp
+profiles in addition to the simulation based formalism we rely on that accounts
+for both Coulomb and hadronic losses during the build up of the CR distribution
+in contrast to the scaling relations adopted in their paper. Interestingly the
+gamma-ray flux from both our scenarios are just below recent Fermi-LAT limits
+derived from a gamma-ray profile similar to \Mflatturb\footnote{Fabio Zandanel,
+  private communication. See also
+  \citet{2014MNRAS.440..663Z,2014ApJ...787...18A}. and will be probed in the
+  next few years by Fermi-LAT.} where
 $F_\gamma(>500\,\rmn{MeV})<5.3\times10^{-10} \mathrm{ \,ph\,
-  s}^{-1}\mathrm{cm}^{-2}$ \footnote{Fabio Zandanel, private
-  communication. See also
-  \citet{2014MNRAS.440..663Z,2014ApJ...787...18A}. and will be probed
-  in the next few years by Fermi-LAT. } The spectral index of the CRp
-distribution is relatively steep ($\alpha_{\rmn{p}}\sim2.6$) for the
-CRp energies $E \gtrsim 10$~GeV that are relevant for the injection of
-radio-emitting secondary CRes. The steep spectrum is ultimately a
-consequence of the shock history of the simulated cluster, with a weak
-dependence on our test particle model for Fermi-I acceleration
-\citep{pinzke13}, where we steepen the spectral index to avoid
-acceleration efficiencies above $\zeta_{\rmn{p}} \sim 10\%$.
+  s}^{-1}\mathrm{cm}^{-2}$.  The spectral index of the CRp distribution is
+relatively steep ($\alpha_{\rmn{p}}\sim2.6$) for the CRp energies $E \gtrsim
+10$~GeV that are relevant for the injection of radio-emitting secondary
+CRes. The steep spectrum is ultimately a consequence of the shock history of the
+simulated cluster, with a weak dependence on our test particle model for Fermi-I
+acceleration \citep{pinzke13}, where we steepen the spectral index to avoid
+acceleration efficiencies above $\zeta_{\rmn{p}} \sim 0.1$.
 
@@
   turb} = X_{\rm tu} E_{\rm th}$), the spatial profile of
-turbulence as parametrized by $\alpha_{\rm tu}$ (defined by $I_0
-\propto \eps_{\rm th}^{\alpha_{\rm tu}}$, where $I_0^{} \propto
-\varv_0^{3} k_0^{}$ is the injection rate of turbulence), as well as
+turbulence as parametrized by $\alpha_{\rm tu}$ (defined by $I_L
+\propto \eps_{\rm th}^{\alpha_{\rm tu}}$, where $I_L^{} \propto
+\varv_L^{3} k_L^{}$ is the injection rate of turbulence), as well as
 the spatial CR profile that we will parametrize by $\alpha_{\rm CR,
@@
 content, and the turbulent outer scale (corresponding to a wavenumber
-$k_{0}$). The CR energy content is suggested by our simulations
+$k_L$). The CR energy content is suggested by our simulations
 (observations only give an upper bound;
 \citealt{2012ApJ...757..123A}). We focus on the uncertain CR
-distribution rather than the overall normalization, since the impact
+distribution rather than the overall normalisation, since the impact
 of the latter (an overall linear scaling) is clear.
@@
 \begin{eqnarray}
-n_e &=& n_0\,\left[1+\left(R/R_{\rmn{c}}\right)^2\right]^{-1.125},\nonumber\\
+n_{\rmn{e}} &=& n_0\,\left[1+\left(R/R_{\rmn{c}}\right)^2\right]^{-1.125},\nonumber\\
 k_{\rmn{B}} T &=& 8.25\,\rmn{keV} \left[1+\left(2R/R_{200}\right)^2\right]^{-0.32},
@@
 measurements, we assume $B(r)=B_{0} (n/n_{0})^{\eta}$, where
-$B_{0}=4.8 \mu$G and $\eta=0.5$ \citep{bonafede10}.
+$B_{0}=4.8 \umu$G and $\eta=0.5$ \citep{bonafede10}.
 
 The bulk of the CRps are injected by relatively low Mach number shocks
-and parameterized by $f_\rmn{p,inj}(p) =
+and parametrized by $f_\rmn{p,inj}(p) =
 C_\rmn{inj}\,p^{-\alpha_\rmn{inj}}$, where $\alpha_\rmn{inj}\approx
@@
 with $C_\rmn{inj} \propto \eps_\rmn{th}^{\alpha_\rmn{CR,spat}}$
-\citep{pinzke10,2016MNRAS.459...70V}, where the normalization is fixed
+\citep{pinzke10,2016MNRAS.459...70V}, where the normalisation is fixed
 by the injected CR energy in the last 650~Myrs. Our simulations show
-that it approximately amounts to 0.03\% of the thermal energy inside
+that it approximately amounts to 0.03 per cent of the thermal energy inside
 the virial radius, i.e.  $\int_0^{R_{200}}\eps_\rmn{p,inj} \rmn{d}
@@
 \end{equation}
-where we fix the normalization by requiring
-$\int_0^{R_{200}}\eps_\rmn{p,0}
-\rmn{d}V\left(\int_0^{R_{200}}\eps_\rmn{th} \rmn{d}V\right)^{-1} =
-0.003$. Note that the injected energy in the last 650 Myr is smaller
-by about a factor of 10 in comparison to the cumulative CR energy
-injected over the entire cosmological history of the cluster, but this component is nonetheless important since above 1 GHz the radio emission is dominated by CRe's injected during the merger, which have not yet had time to cool.
-Similarly, the initial CRe distribution is given by the steady state
-between cooling (Coulomb, inverse Compton, and synchrotron) and
-injection of secondary CRes from $f_\rmn{p,0}$. 
-The diffusion constant $D_{\rm pp} \propto X_{\rm tu}^{2}
-\eps_{\rm th}^{\alpha-1} \sqrt{T} k_{\rm 0}$ is calculated for each
-radial bin. All parameters
-and assumptions are similar to what is used for our simulated cluster
-(see Sect.~\ref{sec:results}). Our fiducial model assumes $X_{\rm tu}
-= 0.2$, $\alpha_{\rm tu} =0.8$, $\alpha_{\rm CR, spat}=1.0$, and
-$k_{\rm 0}=2 \pi/\lambda_{\rm 0}$ where $\lambda_{\rm 0}=100$ kpc. We
-also assume a fixed acceleration time of $\tau_{\rm cl} = 650 \, {\rm
-  Myr}$.
+where we fix the normalisation by requiring $\int_0^{R_{200}}\eps_\rmn{p,0}
+\rmn{d}V\left(\int_0^{R_{200}}\eps_\rmn{th} \rmn{d}V\right)^{-1} = 0.003$. Note
+that the injected energy in the last 650 Myr is smaller by about a factor of 10
+in comparison to the cumulative CR energy injected over the entire cosmological
+history of the cluster, but this component is nonetheless important since above
+1 GHz the radio emission is dominated by CRes injected during the merger, which
+have not yet had time to cool.  Similarly, the initial CRe distribution is given
+by the steady state between cooling (Coulomb, inverse Compton, and synchrotron)
+and injection of secondary CRes from $f_\rmn{p,0}$.  The diffusion constant
+$D_{pp} \propto X_{\rm tu}^{2} \eps_{\rm th}^{\alpha-1} \sqrt{T} k_L$ is
+calculated for each radial bin. All parameters and assumptions are similar to
+what is used for our simulated cluster (see Sect.~\ref{sec:results}). Our
+fiducial model assumes $X_{\rm tu} = 0.2$, $\alpha_{\rm tu} =0.8$, $\alpha_{\rm
+  CR, spat}=1.0$, and $k_L=2 \upi/\lambda_L$ where $\lambda_L=100$ kpc. We also
+assume a fixed acceleration time of $\tau_{\rm cl} = 650 \, {\rm Myr}$.
 
@@
 \end{minipage}
-\caption{Sensitivity of radio emission in Coma cluster to critical
+\caption{Sensitivity of the radio emission in the Coma cluster to critical
   parameters. The left-hand panels show the radio surface brightness
@@
 
-An increase in $X_{\rm tu}$ flattens the surface brightness profile, since high acceleration efficiency leads to larger amplification in the cluster outskirts (where cooling is less important) than the center.
+An increase in $X_{\rm tu}$ flattens the surface brightness profile, since high acceleration efficiency leads to larger amplification in the cluster outskirts (where cooling is less important) than the centre.
 In particular, in the cluster outskirts, the reduced impact of Coulomb cooling implies that there is a larger pool of low-energy electrons available for reacceleration (see timescales in Table \ref{tab:timescales}).
@@
 In between, there is a quasi-adiabatic regime where electrons accumulate (for more details, and an analytic self-similar solution, see \citealt{1999ApJ...520..529S, pinzke13}).
-In the absence of cooling, momentum advection in the limit $D_{\rm pp} \propto p^{2}$ (so that $\tau_\rmn{D} =p^{2}/4 D_{\rm pp}$ is momentum independent) simply shifts the distribution $f(p) \rightarrow f(A p)$.
+In the absence of cooling, momentum advection in the limit $D_{pp} \propto p^{2}$ (so that $\tau_\rmn{D} =p^{2}/4 D_{pp}$ is momentum independent) simply shifts the distribution $f(p) \rightarrow f(A p)$.
 When the acceleration efficiency is low, most observable emission corresponds to the power-law tail of the distribution function $f \propto p^{-\alpha_{\rm inj}-1}$ set by the balance between injection and synchrotron/IC cooling.
@@
 \end{equation}
-where $B_{\rm CMB} \equiv (8 \pi U_{\rm CMB})^{1/2}$, which increases for shorter $\tau_{\rm D}$.
+where $B_{\rm CMB} \equiv (8 \upi \eps_{\rm CMB})^{1/2}$, which increases for shorter $\tau_{\rm D}$.
 
 {\bf Impact of spatial profile of turbulence ($\alpha_{\rm tu}$).} From the middle panels of Fig.~\ref{fig:param_comp}, we see that as expected, a flatter profile of the turbulent pressure directly translates into a flatter radio surface brightness profile.
-Since seed electrons are more concentrated toward the center (the collisional production of secondaries is more rapid there), and magnetic fields are stronger, concentrating the turbulence toward the cluster center for fixed $X_{\rm tu}$ results in higher radio luminosities, and slightly more curvature (due to the increased importance of cooling near the center).
-Overall, however, the spatial profile of turbulence has a much weaker effect than its overall normalization.
+Since seed electrons are more concentrated toward the centre (the collisional production of secondaries is more rapid there), and magnetic fields are stronger, concentrating the turbulence toward the cluster centre for fixed $X_{\rm tu}$ results in higher radio luminosities, and slightly more curvature (due to the increased importance of cooling near the centre).
+Overall, however, the spatial profile of turbulence has a much weaker effect than its overall normalisation.
 
 {\bf Impact of spatial profile of seed CRs $\alpha_{\rm CR, spat}$.} The spatial distribution of CRs has an even smaller impact on radio emission.
-At fixed total CR energy content $X_{\rm CR}$, concentrating the CRs towards the center leads to more centrally dominated surface brightness profiles, as expected, and higher radio luminosities (for the same reasons as above: secondaries are more easily produced in the center, and magnetic fields are stronger).
+At fixed total CR energy content $X_{\rm CR}$, concentrating the CRs towards the centre leads to more centrally dominated surface brightness profiles, as expected, and higher radio luminosities (for the same reasons as above: secondaries are more easily produced in the centre, and magnetic fields are stronger).
 We have also confirmed that radio surface brightness profiles scale linearly with $X_{\rm CR}$, as expected.
 
-Overall, our results suggest that radio halos are much more sensitive to the level of turbulence (exponential dependence) rather than CR abundance (linear dependence), and that the spatial distribution of turbulence and CRs, while important, are second-order effects.
+Overall, our results suggest that radio haloes are much more sensitive to the level of turbulence (exponential dependence) rather than CR abundance (linear dependence), and that the spatial distribution of turbulence and CRs, while important, are second-order effects.
 In our parametrization, the most important controlling variable is $X_{\rm tu}$.
@@
 While the requirement of a threshold level of turbulence may explain why radio brightness is bimodal, it also raises a fine-tuning problem: why is the $L_{\rm radio}$ vs.
-$L_{\rm X}$ relation in active radio halos so tight?
+$L_{\rm X}$ relation in active radio haloes so tight \citep{Brunetti2009}?
 Depending on the details of infall or mergers, we would naturally expect fluctuations in $X_{\rm tu}$, which would translate into large scatter in the $L_{\rm radio}$--$L_{\rm X}$ relation.
@@
 
-\subsection{Self-Limiting Turbulent Reacceleration}
+\subsection{Self-limiting turbulent reacceleration}
 \label{sect:self-limiting}
 
-There are 3 important timescales in this problem: the acceleration time $\tau_{\rm D}$, the duration that turbulence is active and acceleration takes place, $\tau_{\rm cl}$, and the cooling time $\tau_{\rm cool}(p)$.
+There are 3 important timescales in this problem: the acceleration time $\tau_{\rm D}$, the duration over which turbulence is active and acceleration takes place, $\tau_{\rm cl}$, and the cooling time $\tau_{\rm cool}(p)$.
 Only $\tau_{\rm cool}(p)$ is momentum dependent (and is different for ions and electrons).
@@
 
-We have seen that the radio luminosity depends very sensitively on $\tau_{\rm cl}/\tau_{\rm D}$, through the very sensitive dependence on $X_{\rm tu}$ (Fig \ref{fig:param_comp}; note from equation \ref{eq:Dpp_scaling} that $\tau_{\rm D} \propto X_{\rm tu}^{-2}$).
-Since this raises questions of fine-tuning in $X_{\rm tu}$ to explain the observations, it is worth understanding in more detail.
-Let us ignore cooling.
-This is a good approximation for the CR protons, for instance, since hadronic cooling times are long\footnote{In principle, CRp can still lose energy via wave heating, at a rate $\varv_{\rm A} \cdot \nabla P_{c}$, but we assume CR streaming is suppressed during mergers, when they are spatially confined by scattering.} In this case, $\dot{p}= p/\tau_{\rm D}$, and after a time $\tau_{\rm cl}$, we have $p \rightarrow p \, {\rm exp}(\tau_{\rm cl}/\tau_{\rm D})$ (where we have used the fact that $\tau{\rm D}$ is momentum independent).
-For an initial power law distribution function $f(p) = C p^{-\alpha}$, this momentum increase can be rewritten as a change of normalization, $f(p) = \tilde{C} p^{-\alpha}$, where $\tilde{C} = {\rm exp}( \alpha \tau_{\rm cl}/\tau_{\rm D})$.
-A slightly more careful derivation by direct solution of the Fokker-Planck equation yields:
+We have seen that the radio luminosity depends very sensitively on $\tau_{\rm
+  cl}/\tau_{\rm D}$, through the very sensitive dependence on $X_{\rm tu}$ (Fig
+\ref{fig:param_comp}; note from equation \ref{eq:Dpp_scaling} that $\tau_{\rm D}
+\propto X_{\rm tu}^{-2}$). Since this raises questions of fine-tuning in $X_{\rm
+  tu}$ to explain the observations, it is worth understanding this property in
+more detail. To this end, we ignore cooling which is a good approximation for
+the CR protons, because hadronic cooling times are long in comparison to the
+other relevant timescales of the problem.\footnote{In principle, CRp can still
+  lose energy via wave heating, at a rate $\bmath{\varv_{\rm A} \cdot \nabla} P_{c}$,
+  but we assume CR streaming is suppressed during mergers, when they are
+  spatially confined by scattering.} In this case, $\dot{p}= p/\tau_{\rm D}$,
+and after a time $\tau_{\rm cl}$, we have $p \rightarrow p \, {\rm
+  exp}(\tau_{\rm cl}/\tau_{\rm D})$ (where we have used the fact that $\tau_{\rm
+  D}$ is momentum independent). For an initial power law distribution function
+$f(p) = C p^{-\alpha}$, this momentum increase can be rewritten as a change of
+normalisation, $f(p) = \tilde{C} p^{-\alpha}$, where $\tilde{C} = {\rm exp}(
+\alpha \tau_{\rm cl}/\tau_{\rm D})$. A slightly more careful derivation by
+direct solution of the Fokker-Planck equation yields:
 \begin{equation}
   \dot{f} = {{\partial }\over{\partial p}}
-  p^2 D_{\rm pp} {{\partial }\over{\partial p}} \frac{f}{p^2}\,,
+  p^2 D_{pp} {{\partial }\over{\partial p}} \frac{f}{p^2}\,,
 \end{equation}
@@
 
-The only way around this is for $\tau_{\rm cl}$ and $\tau_{\rm D}$ to be somehow related.
+The natural solution to this puzzle would be a process that couples $\tau_{\rm cl}$ and $\tau_{\rm D}$.
 There are two possible limits.
@@
 \begin{equation}
-\tau_{\rm edd} = \frac{L}{v_{\rm c}}
-\end{equation}
-i.e., the eddy turnover time at the outer scale.
-This is subject to uncertainties about the location of the outer scale $L$; estimates in the literature range from $L \sim 0.1-1$ Mpc.
-It is also worth remembering that MHD turbulence only applies below $l < l_{\rm A}$, where $l_{\rm A}$ is the Alfv{\'e}n scale where $\varv \sim \varv_{\rm A}$.
-Invoking fast modes, Kraichnan scalings, etc, is only valid below these scales.
-For $l > l_{\rm A}$, turbulence is basically hydrodynamic and Kolmogorov in nature.
-The momentum diffusion coefficient can thus be split up into two components:
-\begin{equation}
-D_{\rm pp} = D_{\rm pp}^{\rm HD}[l_{\rm A} < l < L] + D_{\rm pp}^{\rm MHD}[l_{\rm c} < l < l_{\rm A}]
+\tau_{\rm edd} = \frac{L}{\varv_{\rm c}}
+\end{equation}
+i.e., the eddy turnover time at the outer scale. This is subject to
+uncertainties about the location of the outer scale $L$; estimates in the
+literature range from $L \sim 0.1-1$ Mpc. It is also worth remembering that MHD
+turbulence only applies for $l < l_{\rm A}$, where $l_{\rm A}$ is the Alfv{\'e}n
+scale where $\varv \sim \varv_{\rm A}$. Invoking fast modes, Kraichnan scalings,
+etc., is only valid below these scales. For $l > l_{\rm A}$, turbulence is
+basically hydrodynamic and Kolmogorov in nature. The momentum diffusion
+coefficient can thus be split up into two components:
+\begin{equation}
+D_{pp} = D_{pp}^{\rm HD}[l_{\rm A} < l < L] + D_{pp}^{\rm MHD}[l_{\rm c} < l < l_{\rm A}]
 \end{equation}
@@
 \begin{equation}
-\frac{D_{\rm pp}^{\rm HD}}{D_{\rm pp}^{\rm MHD}} = \frac{k_{\rm L}^{2/3}k_{\rm A}^{1/3} \varv_{\rm c}^{2}}{k_{\rm A}^{1/2}k_{\rm c}^{1/2} \varv_{\rm A}^{2}} = A^{-1/2} \beta = 0.5 \left( \frac{\beta}{50} \right)
-\end{equation}
-where we have used $k_{\rm A} = k_{\rm L} M_{A}^{3}$ (from Kolmogorov scalings, and $M_{\rm A} = \varv_{\rm c}/\varv_{\rm A}$ is the Alfv{\'e}n Mach number of the turbulence, $\beta \approx c_{\rm s}^{2}/\varv_{\rm A}^{2}$, and the cutoff scale $k_{\rm c}$ (equation \ref{eqn:k_c}).
-Thus, the contribution of the two regimes are comparable (as we shall see later, this is not true if one incorrectly assumes Kraichnan scalings apply from the outer scale $L$; this boosts the contribution of the scales where $l_{\rm A} < l < L$ by a factor $M_{\rm A}^{1/2}$).
+\frac{D_{pp}^{\rm HD}}{D_{pp}^{\rm MHD}} = \frac{k_L^{2/3}k_{\rm A}^{1/3} \varv_{\rm c}^{2}}{k_{\rm A}^{1/2}k_{\rm cut}^{1/2} \varv_{\rm A}^{2}} = A^{-1/2} \beta = 0.5 \left( \frac{\beta}{50} \right) 
+\end{equation}
+where we have used $k_{\rm A} = k_L \mathcal{M}_{\rm A}^{3}$ (from Kolmogorov scalings, and $\mathcal{M}_{\rm A} = \varv_{\rm c}/\varv_{\rm A}$ is the Alfv{\'e}n Mach number of the turbulence, $\beta \approx c_{\rm s}^{2}/\varv_{\rm A}^{2}$, and the cutoff scale $k_{\rm cut}$ (equation \ref{eqn:k_c}).
+Thus, the contribution of the two regimes are comparable (as we shall see later, this is not true if one incorrectly assumes Kraichnan scalings apply from the outer scale $L$; this boosts the contribution of the scales where $l_{\rm A} < l < L$ by a factor $\mathcal{M}_{\rm A}^{1/2}$).
 Henceforth, we can consider the outer scale of the fast modes to be $l_{\rm A}$, with velocity $\varv_{\rm A}$. The turbulent reacceleration time is: 
 \begin{equation}
-\tau_{\rm D} = \frac{p^{2}}{4 D_{\rm pp}} = C_{\rm D} A^{1/2} c k_{\rm A} \frac{\varv_{A}^{2}}{c_{\rm S}^{2}}
+\tau_{\rm D} = \frac{p^{2}}{4 D_{pp}} = C_{\rm D} A^{1/2} c k_{\rm A} \frac{\varv_{\rm A}^{2}}{c_{\rm S}^{2}}
 \label{eqn:tau_D} 
 \end{equation}
-where $C_{\rm D} = 2/(5 \pi)$, $A\approx 11000$, and we have used equation \ref{eqn:k_c}.
-The turbulence decay time is given by the cascade time of fast modes (\citet{2004ApJ...614..757Y}; see equation \ref{eqn:cascade}):
-\begin{equation}
-\tau_{\rm decay} = \frac{c_{\rm s}}{\varv_{\rm A}^{2} k_{\rm A}}\,.
+where $C_{\rm D} = 2/(5 \upi)$, $A\approx 11000$, and we have used equation \ref{eqn:k_c}.
+The turbulent decay time is given by the cascade time of fast modes (\citealt{2004ApJ...614..757Y}; see equation \ref{eqn:cascade}):
+\begin{equation}
+\tau_{\rm decay} = \frac{c_{\rm s}}{\varv_{\rm A}^{2} k_{\rm A}^{}}\,.
 \label{eqn:tau_decay} 
 \end{equation} 
-This can be related to the eddy turnover time at the outer scale $\tau_{\rm edd}$ from $l_{\rm A} = L M_{\rm A}^{-3}$ to: 
+This can be related to the eddy turnover time at the outer scale $\tau_{\rm edd}$ from $l_{\rm A} = L \mathcal{M}_{\rm A}^{-3}$ to: 
 \begin{equation}
@@
 \end{equation}
-Remarkably, this expression is independent of properties of the turbulence such as $\varv_{\rm c},L$, or $l_{\rm A}$, and depends only on properties of the plasma ($c_{\rm s},\beta$).
-Ultimately, this arises because the timescale on which a fast mode wave transfers energy due to wave particle interactions in second order Fermi acceleration, $\tau_{\rm p} \sim (k_{\rm p} c (\varv_{\rm c}/c)^{2} )^{-1}$, is closely related to the timescale on which it cascades due to wave-wave interactions, $\tau_{\rm w} \sim c_{\rm s}/(k_{\rm w} \varv_{\rm c}^{2})$.
-This implies $\tau_{\rm w}/\tau_{\rm p} \sim (c_{s}/c)(l_{\rm w}/l_{\rm p})$, where $l_{\rm w} \sim l_{\rm A}$ is the outer scale on which the fast mode cascade begins, and $l_{\rm p} \sim (l_{\rm A} l_{\rm c})^{1/2}$ is the characteristic wavelength for wave-particle interactions.
-For transit time damping and an outer scale of $l_{\rm A}$, we have $l_{\rm c} \sim (m_{\rm e}/m_{\rm p}) l_{\rm A} (c_{\rm s}/\varv_{\rm A})^{4}$.
-We thus have $\tau_{\rm w}/\tau_{\rm p} \sim (c_{\rm s}/c)(l_{\rm A}/l_{\rm c})^{1/2} \sim (c_{\rm s}/c) (m_{\rm p}/m_{\rm e})^{1/2} \beta^{-1}$.
+Remarkably, this expression is independent of properties of the turbulence such as $\varv_{\rm c}$, $L$, or $l_{\rm A}$, and depends only on properties of the plasma ($c_{\rm s},\beta$).
+Ultimately, this arises because the timescale on which a fast mode wave transfers energy due to wave particle interactions in second order Fermi acceleration, $\tau_{\rm p} \sim [k_{\rm p} c (\varv_{\rm c}/c)^{2} ]^{-1}$, is closely related to the timescale on which it cascades due to wave-wave interactions, $\tau_{\rm w} \sim c_{\rm s}/(k_{\rm w} \varv_{\rm c}^{2})$.
+This implies $\tau_{\rm w}/\tau_{\rm p} \sim (c_{\rm s}/c)(l_{\rm w}/l_{\rm p})$, where $l_{\rm w} \sim l_{\rm A}$ is the outer scale on which the fast mode cascade begins, and $l_{\rm p} \sim (l_{\rm A} l_{\rm cut})^{1/2}$ is the characteristic wavelength for wave-particle interactions.
+For transit time damping and an outer scale of $l_{\rm A}$, we have $l_{\rm cut} \sim (m_{\rm e}/m_{\rm p}) l_{\rm A} (c_{\rm s}/\varv_{\rm A})^{4}$.
+We thus have $\tau_{\rm w}/\tau_{\rm p} \sim (c_{\rm s}/c)(l_{\rm A}/l_{\rm cut})^{1/2} \sim (c_{\rm s}/c) (m_{\rm p}/m_{\rm e})^{1/2} \beta^{-1}$.
 More careful consideration of dimensionless factors boosts this estimate by an order of magnitude to give equation \ref{eqn:ratios_TTD}.
@@
 A key reason is that we assume Kraichnan turbulence only applies for $l< l_{\rm A}$.
-There is then insufficient separation of scales: the cutoff scale $l_{\rm c} \sim 0.2 \beta_{\rm 50}^{2} l_{\rm A}$.
-Although there is a fair large separation of scales between the outer driving scale $L$ and $l_{\rm A} = L M_{\rm A}^{-3}$ (a factor of $30-1000$ for $M_{\rm A} \approx 3-10$; we have $M_{\rm A} \sim (\tilde{X}_{\rm tu} \beta)^{1/2} \sim 3.2$ for our fiducial assumptions), Kolmogorov turbulence, with its steeper spectrum, has more energy at large scales ($k W(k) \propto k^{-2/3}, k^{-1/2}$ for Kolmogorov and Kraichnan turbulence respectively).
+There is then insufficient separation of scales: the cutoff scale $l_{\rm cut} \sim 0.2 \beta_{\rm 50}^{2} l_{\rm A}$.
+Although there is a fair large separation of scales between the outer driving scale $L$ and $l_{\rm A} = L \mathcal{M}_{\rm A}^{-3}$ (a factor of $30-1000$ for $\mathcal{M}_{\rm A} \approx 3-10$; we have $\mathcal{M}_{\rm A} \sim (\tilde{X}_{\rm tu} \beta)^{1/2} \sim 3.2$ for our fiducial assumptions), Kolmogorov turbulence, with its steeper spectrum, has more energy at large scales ($k W(k) \propto k^{-2/3}, k^{-1/2}$ for Kolmogorov and Kraichnan turbulence, respectively).
 This implies that the energy-weighted scales at which wave-particle interaction take place are larger in Kolmogorov turbulence, and thus that the wave-particle interaction rate is lower.
-If (as is frequently seen) we instead assume that Kraichnan turbulence begins at the outer scale $L$, with characteristic decay time $L c_{\rm s}/\varv_{\rm c}^{2}$, then we obtain a more platable result:
+If (as is frequently seen) we instead assume that Kraichnan turbulence begins at the outer scale $L$, with characteristic decay time $L c_{\rm s}/\varv_{\rm c}^{2}$, then we obtain a more palatable result:
 \begin{equation}
@@
 \end{equation}
-This arises because the decay time is now $\sim M_{\rm A}$ times longer, and the acceleration time is now $\sim M_{\rm A}^{1/2}$ times shorter, boosting $\tau_{\rm cl}/\tau_{\rm D}$ by $\sim M_{\rm A}^{3/2}$.
+This arises because the decay time is now $\sim \mathcal{M}_{\rm A}$ times longer, and the acceleration time is now $\sim \mathcal{M}_{\rm A}^{1/2}$ times shorter, boosting $\tau_{\rm cl}/\tau_{\rm D}$ by $\sim \mathcal{M}_{\rm A}^{3/2}$.
 However, as we have argued, turbulence in the hydrodynamic regime $l_{\rm A} < l < L$ is Kolmogorov, not Kraichnan.
-Furthermore, if this scaling is somehow correct, then this leaves us with the problematic exponential sensitivity to $X_{\rm tu}$ that we previously explored.
-
-One alternative is that scattering in the high $\beta$ ICM is mediated by plasma instabilities (firehose, mirror) rather than Coulomb scattering.
+Furthermore, if this scaling is correct, then this leaves us with the problematic exponential sensitivity to $X_{\rm tu}$ that we previously explored.
+
+One alternative is that scattering in the high-$\beta$ ICM is mediated by plasma instabilities (firehose, mirror) rather than Coulomb scattering.
 This vastly increases the scattering rate and reduces the mean free path of thermal particles.
@@
 \begin{equation}
-D_{\rm pp}^{\rm CR} = \frac{2 p^{2} \zeta}{x_{\rm CR}} k_{\rm L} \frac{\langle \varv_{\rm c}^{2} \rangle^{2}}{c_{\rm s}^{3}}
-\end{equation}
-where $\zeta$ is an efficiency factor for the the effectiveness of plasma instabilities (e.g., due to spatial or temporal intermittency), and $x_{\rm CR}=\eps_{\rm CR}/\eps_{\rm th}$ is the relative energy density of cosmic rays.
-If we set $k_{\rm L} \rightarrow k_{\rm A}$, $\varv_{c}^{2} \rightarrow \varv_{\rm A}^{2}$, as before, then:
-\begin{equation}
-\frac{\tau_{\rm cl}}{\tau_{\rm D}} \approx 8 \frac{\zeta}{\beta x_{\rm CR}}
-\end{equation}
-In principle, this implies exponential sensitivity to $x_{\rm CR}$, a similar situation as exponential sensitivity to $X_{\rm tu}$.
-However, there is a self-limiting asymptotic behaviour: as $x_{\rm CR}$ increases due to turbulent reacceleration, damping increases, which limits the further growth of the cosmic ray energy density \citep{brunetti11}.
-One natural assumption is to assume that $\eps_{\rm CR}$ saturates at a level $\eps_{\rm CR} \sim \eps_{\rm turb} ({\rm MHD}) \sim \eps_{\rm B}$, in which case $x_{\rm CR} \sim \beta^{-1}$, so that:
+D_{pp}^{\rm CR} = \frac{2 p^{2} \zeta}{X_{\rm CR}} k_L \frac{\langle \varv_{\rm c}^{2} \rangle^{2}}{c_{\rm s}^{3}}
+\end{equation}
+where $\zeta$ is an efficiency factor for the the effectiveness of plasma instabilities (e.g., due to spatial or temporal intermittency), and $X_{\rm CR}=\eps_{\rm CR}/\eps_{\rm th}$ is the relative energy density of CRs.
+If we set $k_L \rightarrow k_{\rm A}$, $\varv_{c}^{2} \rightarrow \varv_{\rm A}^{2}$, as before, then:
+\begin{equation}
+\frac{\tau_{\rm cl}}{\tau_{\rm D}} \approx 8 \frac{\zeta}{\beta X_{\rm CR}}
+\end{equation}
+In principle, this implies exponential sensitivity to $X_{\rm CR}$, a similar situation as exponential sensitivity to $X_{\rm tu}$.
+However, there is a self-limiting asymptotic behaviour: as $X_{\rm CR}$ increases due to turbulent reacceleration, damping increases, which limits the further growth of the CR energy density \citep{brunetti11}.
+One natural assumption is to assume that $\eps_{\rm CR}$ saturates at a level $\eps_{\rm CR} \sim \eps_{\rm turb} ({\rm MHD}) \sim \eps_{\rm B}$, in which case $X_{\rm CR} \sim \beta^{-1}$, so that:
 \begin{equation}
@@
 \begin{equation}
-\frac{D_{\rm pp}^{\rm Burgers}}{D_{\rm pp}^{\rm MHD}} = \left( \frac{\beta}{X_{\rm tu} A} \right)^{1/2} = 0.15 \left( \frac{\beta}{50} \right)^{1/2} \left( \frac{X_{\rm tu}}{0.2} \right)^{-1/2} 
-\end{equation}
-where we have set $\langle k \rangle_{\rm W} \approx k_{\rm L}$ for Burgers' turbulence, i.e.
+\frac{D_{pp}^{\rm Burgers}}{D_{pp}^{\rm MHD}} = \left( \frac{\beta}{X_{\rm tu} A} \right)^{1/2} = 0.15 \left( \frac{\beta}{50} \right)^{1/2} \left( \frac{X_{\rm tu}}{0.2} \right)^{-1/2} 
+\end{equation}
+where we have set $\langle k \rangle_{\mathcal{W}} \approx k_L$ for Burgers' turbulence, i.e.
 all power is at large scales.
 This weighting towards larger scales implies a much lower wave-particle interaction rate and thus a diffusion coefficient which is smaller than standard TTD on thermal particles by an order of magnitude.
-Since $\langle k \rangle_{\rm W} \approx k_{\rm L}$ is independent of the cutoff scale $k_{\rm c}$, this conclusion is unchanged if plasma instabilities regulate the thermal particle mean free path and TTD operates on relativistic particles instead.
+Since $\langle k \rangle_{\mathcal{W}} \approx k_L$ is independent of the cutoff scale $k_{\rm cut}$, this conclusion is unchanged if plasma instabilities regulate the thermal particle mean free path and TTD operates on relativistic particles instead.
 Since standard TTD on thermal particles was already potentially problematic (equation \ref{eqn:ratios_TTD}), we conclude, in agreement with other assessments \citep{miniati15,brunetti16_review}, that if Burgers turbulence dominates, then turbulent reacceleration will be ineffective\footnote{Note also that since there is no real cascade in Burgers' turbulence, but direct transfer of power from large to small scales, the dissipation time is potentially short.
@@
 \ref{fig:param_comp_tcl_tD}, where, similar to Fig.
-\ref{fig:param_comp}, we vary $X_{\rm tu}, \alpha_{\rm tu}, \alpha_{\rm CR, spat}$ about fuducial values, but this time we do not adopt a fixed $\tau_{\rm cl}$ but set $\tau_{\rm cl}=\tau_{\rm D}$.
+\ref{fig:param_comp}, we vary $X_{\rm tu}, \alpha_{\rm tu}, \alpha_{\rm CR, spat}$ about fiducial values, but this time we do not adopt a fixed $\tau_{\rm cl}$ but set $\tau_{\rm cl}=\tau_{\rm D}$.
 They are remarkably revealing.
 In this case, one is much less sensitive to the properties of the turbulence, and more sensitive to the details of the CR seed population.
-This gives hope to the possibility that one could effectively marginalize over the very uncertain properties of turbulence (which are unlikely to be more precisely constrained observationally in the near future) to learn something about the underlying CR population.
-
-For instance, in the top panels of Fig \ref{fig:param_comp_tcl_tD}, we see that once turbulence exceeds a threshold value $X_{\rm tu} \sim 0.1$, then its overall exact energy density does not matter-- profiles simply converge to an asymptotic form as $X_{\rm tu}$ is increased.
+This gives hope to the possibility that one could effectively marginalise over the very uncertain properties of turbulence at larger scales in merging clusters (which are unlikely to be more precisely constrained observationally in the near future) to learn something about the underlying CR population.
+
+For instance, in the top panels of Fig \ref{fig:param_comp_tcl_tD}, we see that once turbulence exceeds a threshold value $X_{\rm tu} \sim 0.1$, then its overall exact energy density does not matter -- profiles simply converge to an asymptotic form as $X_{\rm tu}$ is increased.
 This is in contrast to the exponential sensitivity, flattening in surface brightness, and increasing spectral curvature as $X_{\rm tu}$ is increased that we saw previously.
@@
 Once that condition is satisfied, the condition $\tau_{\rm cl} \sim \tau_{\rm D}$ implies a fixed amount of amplification: stronger turbulence implies faster acceleration, but also dissipates more quickly.
-This leads to the asymptotic behavior seen.
+This leads to the asymptotic behaviour seen.
 From the middle panels, we see another striking result: in contrast to Fig.
 \ref{fig:param_comp}, results are also completely insensitive to the turbulent profile.
-Given the large uncertainties in the latter, this is welcome news.
-It arises because for our fuducial value ($X_{\rm tu} = 0.2$), variations in the turbulent profile still lead to local energy densities which are above the threshold value required to overcome cooling, and turbulent amplification approaches its asymptotic value.
-Finally, in the bottom panels, we see that we {\it are} sensitive to the spatial CRs; it affects both the surface brightness profile (a flatter CR distribution implies flatter surface brightness profiles) and luminosity (once again, luminosity is larger for more centrally concentrated CRs, since more secondaries are produced).
+Given the large uncertainties in the latter, this is a welcome property.
+It arises because for our fiducial value ($X_{\rm tu} = 0.2$), variations in the turbulent profile still lead to local energy densities which are above the threshold value required to overcome cooling, and turbulent amplification approaches its asymptotic value.
+Finally, in the bottom panels, we see that we {\it are} sensitive to the spatial profile of CRs; it affects both the radio surface brightness profile (a flatter CR distribution implies flatter surface brightness profiles) and luminosity (once again, luminosity is larger for more centrally concentrated CRs, since more secondaries are produced).
 This arises because once turbulent reacceleration overcomes cooling, the condition $\tau_{\rm cl} \sim \tau_{\rm D}$ provides for a fixed amount of amplification in each radial shell.
@@
 Interestingly, the best-fitting profile for Coma comes from a flat CR distribution -- i.e., one that is the outcome of efficient CR streaming.
-Matching the overall amplitude simply involves a rescaling of $\tau_{\rm c}/\tau_{\rm D}$ (equation \ref{eqn:ratios_CR_damp}) or the CR content.
+Matching the overall amplitude simply involves a rescaling of $\tau_{\rm cl}/\tau_{\rm D}$ (equation \ref{eqn:ratios_CR_damp}) or the CR content.
 
 Obviously, the ideas in this section require further study.
-However, the notion that $\tau_{\rm cl}/\tau_{\rm D}$ could self-regulate around a fixed value is exciting, because it eliminates the main source of uncertainty-- the poorly unconstrained properties of turbulence, and implies that radio halos could potentially provide more robust constraints on the underlying CR population.
+However, the notion that $\tau_{\rm cl}/\tau_{\rm D}$ could self-regulate around a fixed value is exciting, because it eliminates the main source of uncertainty-- the poorly unconstrained properties of turbulence, and implies that radio haloes could potentially provide more robust constraints on the underlying CR population.
 
@@
   this scenario the radio profiles are mainly determined from the CRs,
-  while the turbulence have minor impact. Interestingly, flat CR
-  profiles similar to those produced through CR streaming is needed in
+  while the turbulence has a minor impact. Interestingly, flat CR
+  profiles similar to those produced through CR streaming are needed in
   order to reproduce the radio profiles.}
@@
 
-The standard reacceleration model for radio halos requires two ingredients with
+The standard reacceleration model for radio haloes requires two ingredients with
 no current direct observational constraints: a CR population which produces seed
@@
 
-In the first part of the paper, we use hydrodynamic zoom simulations of a Coma-like cluster in a cosmological setting to generate spatially and momentum-resolved seed populations of CRp's and CRe's from diffusive shock acceleration.
-The simulations include time-dependent cooling and adiabatic transport processes, and has been previously used in a variety of applications in CR cluster physics \citep{pinzke10,pinzke13}.
-The resultant CRp and CRe distribution functions then serve as initial conditions for our calculations of Fermi II acceleration by turbulence.
-We use time-dependent Fokker-Planck calculations which allow for spatial variations in the properties of turbulence (i.e., a spatially varying momentum diffusion coefficient).
-We adopt a simple parametric model for
-cluster turbulence, characterizing it by its overall normalization, spatial profile, and characteristic lifetime $\tau_{\rm cl}$.
-Our approach is relatively sophisticated in its treatment of the CR seed population and relatively simplified in its treatment of the turbulence; it is thus orthogonal and complementary to existing treatments which focus on the time-dependent compressible turbulence \citep{miniati15}.
-
-Given our seed electron population (which includes both primaries generated by DSA and secondary electrons created by CRp in hadronic interactions; for standard assumptions, the latter dominates), we find that applying the standard model previously used to reproduce Coma's radio halo properties \citep{brunetti11}, in which $\eps_{\rm turb} \propto \eps_{\rm th}$, fails: it produces radio emission which is too centrally concentrated.
+In the first part of the paper, we use hydrodynamic zoom simulations of a
+Coma-like cluster in a cosmological setting to generate spatially and
+momentum-resolved seed populations of CRps and CRes from diffusive shock
+acceleration. The simulations include time-dependent cooling and adiabatic
+transport processes, and has been previously used in a variety of applications
+in CR cluster physics \citep{pinzke10,pinzke13}. The resultant CRp and CRe
+distribution functions then serve as initial conditions for our calculations of
+Fermi II acceleration by turbulence. We use time-dependent Fokker-Planck
+calculations which allow for spatial variations in the properties of turbulence
+(i.e., a spatially varying momentum diffusion coefficient). We adopt a simple
+parametric model for cluster turbulence, characterising it by its overall
+normalisation, spatial profile, and characteristic lifetime $\tau_{\rm cl}$. Our
+approach is relatively sophisticated in its treatment of the CR seed population
+and relatively simplified in its treatment of the turbulence; it is thus
+orthogonal and complementary to existing treatments which focus on the
+time-dependent compressible turbulence \citep{miniati15}.
+
+Given our seed electron population (which includes both primaries generated by DSA and secondary electrons created by CRps in hadronic interactions; for standard assumptions, the latter dominates), we find that applying the standard model previously used to reproduce Coma's radio halo properties \citep{brunetti11}, in which $\eps_{\rm turb} \propto \eps_{\rm th}$, fails: it produces radio emission which is too centrally concentrated.
 Indeed, \citet{brunetti11} remark in their paper that the CR population required in their model is remarkably flat.
@@
 
-Thus, some modification of the standard vanilla model is needed, either by modifying the spatial distribution of the CRs, or that of turbulence.
+Thus, some modification of the standard model is needed, either by modifying the spatial distribution of the CRs, or that of turbulence.
 We explore two examples of the former: (i) CRs can stream in the ICM, producing a flat profile \citep{ensslin11,wiener13}, or (ii) given a higher e/p ratio in DSA acceleration (perhaps due to magnetic geometry; \citealt{2014ApJ...794..153G}), the primary population can dominate.
@@
 The fact that $\eps_{\rm turb}/\eps_{\rm th}$ rises with radius is well supported by cosmological hydrodynamic simulations of clusters \citep{2009ApJ...705.1129L,2010ApJ...725.1452S,vazza11}; even the last model (iii) is (within the scatter) perfectly consistent with the trends seen by such simulations.
-This strongly suggests that a rising $\eps_{\rm turb}/\eps_{\rm th}$ should be part of any final model of radio halos.
+This strongly suggests that a rising $\eps_{\rm turb}/\eps_{\rm th}$ should be part of any final model of radio haloes.
 Given the lack of observational constraints on turbulent profiles, this unfortunately means that models will have yet another degree of freedom.
@@
 degeneracies for any of these models to be definitive, or for one to make firm
-quantitive statements about turbulent and seed CR profiles, apart from placing
+quantitative statements about turbulent and seed CR profiles, apart from placing
 certain bounds. We abstract the main parameter dependencies by exploring static,
@@
 Fokker-Planck calculations. We explore three main effects: the overall
-normalization of turbulence, and spatial distribution of turbulence and cosmic
-rays.
-
-We find that the most important variable is the overall normalization of
+normalisation of turbulence, and spatial distribution of turbulence and CRs.
+
+We find that the most important variable is the overall normalisation of
 turbulence: surface brightness scales exponentially with the amount of
@@
 turbulence. In contrast, the surface brightness scales linearly with the CR
-abundance.  The spatial distribution of both turbulence and CRs also influence
-radio halos profiles (for both, flatter distributions at fixed overall
-normalization imply flatter surface brightness profiles with lower overall radio
+abundance.  The spatial distributions of both turbulence and CRs also influence
+radio halo profiles (for both, flatter distributions at fixed overall
+normalisation imply flatter surface brightness profiles with lower overall radio
 luminosity), but play a secondary role.
@@
 the interesting question of why radio halo scaling relations (e.g.,
-$L_{\nu}$--$L_{\rm X}$) are so tight. Previous statistical modeling of radio
+$L_{\nu}$--$L_{\rm X}$) are so tight. Previous statistical modelling of radio
 halo populations \citep{2006MNRAS.369.1577C,2007MNRAS.378.1565C} have focused
@@
 
-If instead we adopt $\tau_{\rm
-  cl} \sim \tau_{\rm decay}$, i.e.
-the natural lifetime of turbulence is its decay lifetime, then we can show that the acceleration time and the lifetime of turbulence are linked, simply because the wave-particle interaction rate (which drives particle acceleration) and the wave-wave interaction rate (which drives dissipation) are linked.
-If we are mindful that Kraichnan turbulence is only applicable below the Alfven scale $l_{\rm A}$ (where turbulent velocities $v < v_{\rm A}$), then remarkably the ratio $\tau_{\rm cl}/\tau_{\rm D}$ is independent of properties of the turbulence (such as its amplitude and outer scale) and only depends on plasma parameters.
-Our results suggest that TTD on thermal particles may result in overly rapid damping of turbulence, and inefficient acceleration (equation \ref{eqn:ratios_TTD}), but if plasma instabilities scatter the thermal particles so that the fast modes damp via TTD on the cosmic rays, then the required acceleration can take place (equation \ref{eqn:ratios_CR_damp}).
-In agreement with other assessments, we find that if turbulence is Burgers rather than Kraichnan, then turbulent reacceleration is ineffective, and some other explanation for radio halos (e.g., magnetic reconnection, \cite{brunetti16}) is necessary.
-If we adopt the ansatz $\tau_{\rm cl} \sim \tau_{\rm D}$, then we find that above a threshold level of turbulence (necessary to overcome cooling), radio properties are insensitive to both the amplitude and spatial profile of turbulence, since only a fixed, asymptotic amount of amplification takes place.
-On the other hand, they {\it are} sensitive to the properties of the seed electron profile.
-This raises the exciting possibility that one could marginalize over the highly uncertain properties of cluster turbulence to learn about the underlying seed CR population.
-Our results suggest that studying not just mean trends, but the relatively small scatter in radio-halo scaling relations, may prove extremely fruitful in shedding light on ICM plasma processes.
-
-{\bf Acknowledgments.} We thank Josh Wiener for discussions on CR streaming,
+If instead we adopt $\tau_{\rm cl} \sim \tau_{\rm decay}$, i.e. the natural
+lifetime of turbulence is its decay lifetime, then we can show that the
+acceleration time and the lifetime of turbulence are coupled, simply because the
+wave-particle interaction rate (which drives particle acceleration) and the
+wave-wave interaction rate (which drives dissipation) are linked. If we are
+mindful that Kraichnan turbulence is only applicable below the Alfven scale
+$l_{\rm A}$ (where turbulent velocities $v < v_{\rm A}$), then remarkably the
+ratio $\tau_{\rm cl}/\tau_{\rm D}$ is independent of properties of the
+turbulence (such as its amplitude and outer scale) and only depends on plasma
+parameters. Our results suggest that TTD on thermal particles may result in
+overly rapid damping of turbulence, and inefficient acceleration (equation
+\ref{eqn:ratios_TTD}), but if plasma instabilities scatter the thermal particles
+so that the fast modes damp via TTD on the CRs, then the required
+acceleration can take place (equation \ref{eqn:ratios_CR_damp}). In agreement
+with other assessments, we find that if turbulence is Burgers rather than
+Kraichnan, then turbulent reacceleration is ineffective, and some other
+explanation for radio haloes (e.g., magnetic reconnection, \citealt{brunetti16}) is
+necessary. If we adopt the ansatz $\tau_{\rm cl} \sim \tau_{\rm D}$, then we
+find that above a threshold level of turbulence (necessary to overcome cooling),
+radio properties are insensitive to both the amplitude and spatial profile of
+turbulence, since only a fixed, asymptotic amount of amplification takes
+place. On the other hand, they {\it are} sensitive to the properties of the seed
+electron profile. This raises the exciting possibility that one could
+marginalise over the highly uncertain properties of cluster turbulence to learn
+about the underlying seed CR population. Our results suggest that studying not
+just mean trends, but the relatively small scatter in radio-halo scaling
+relations, may prove extremely fruitful in shedding light on ICM plasma
+processes.
+
+{\bf Acknowledgements.} We thank Josh Wiener for discussions on CR streaming,
 Lawrence Rudnick for discussion on uncertainties in the 1.4 GHz radio data,

### 2016-06-20 paper.tex
unified notation for _p and _CR subscripts

@@
 \newcommand{\bnabla}{\ensuremath{\boldsymbol{\nabla}}}
-\newcommand\eb{\epsilon_\rmn{B}}
+\newcommand{\eb}{\epsilon_B}
 \newcommand{\dps}{\displaystyle}
@@
 \newcommand{\eps}{\varepsilon}
+\newcommand{\CR}{\rmn{CR}}
 
@@
 \begin{eqnarray}
-n_\rmn{p} &=&
+n_\CR &=&
 \int_{p_\rmn{inj}}^\infty \dd p\, f_\p(p)\\
-\eps_\rmn{p} &=&
+\eps_\CR &=&
 \int_{p_\rmn{inj}}^\infty \dd p\, f_\p(p) \,E(p),
@@
 \label{eq:CR_energy} 
-  \Delta\eps_\rmn{p,lin} =
+  \Delta\eps_\rmn{CR,lin} =
   \eta_\rmn{p,lin}(\mathcal{M})\,n_\rmn{th}(T_2)
-  \,\frac{\eps_\p}{n_\p}
+  \,\frac{\eps_\CR}{n_\CR}
 \end{equation}
@@
 relevant for clusters. Since $p_\rmn{inj}$ remains fixed, so does the
-CR number density $n_\rmn{p}$. Hence we can solve for the
-renormalised normalisation constant $C_\rmn{sub}$ using $n_\rmn{p}$
+CR number density $n_\CR$. Hence we can solve for the
+renormalised normalisation constant $C_\rmn{sub}$ using $n_\CR$
 and Eqn.~\ref{eq:eta}:
@@
 that it approximately amounts to 0.03 per cent of the thermal energy inside
-the virial radius, i.e.  $\int_0^{R_{200}}\eps_\rmn{p,inj} \rmn{d}
+the virial radius, i.e.  $\int_0^{R_{200}}\eps_\rmn{CR,inj} \rmn{d}
 V\left(\int_0^{R_{200}}\eps_\rmn{th} \rmn{d}V\right)^{-1} =
@@
 \end{equation}
-where we fix the normalisation by requiring $\int_0^{R_{200}}\eps_\rmn{p,0}
+where we fix the normalisation by requiring $\int_0^{R_{200}}\eps_\rmn{CR,0}
 \rmn{d}V\left(\int_0^{R_{200}}\eps_\rmn{th} \rmn{d}V\right)^{-1} = 0.003$. Note
@@
 other relevant timescales of the problem.\footnote{In principle, CRp can still
-  lose energy via wave heating, at a rate $\bmath{\varv_{\rm A} \cdot \nabla} P_{c}$,
+  lose energy via wave heating, at a rate $\bmath{\varv_{\rm A} \cdot \nabla} P_\CR$,
   but we assume CR streaming is suppressed during mergers, when they are
@@
 \begin{equation}
-D_{pp} = D_{pp}^{\rm HD}[l_{\rm A} < l < L] + D_{pp}^{\rm MHD}[l_{\rm c} < l < l_{\rm A}]
-\end{equation}
-From equations (\ref{eqn:diffusion}) and (\ref{eqn:k_W}), and assuming Kolmogorov turbulence from $l_{\rm A} < l < L$ and Kraichnan turbulence from $l_{\rm c} < l < l_{\rm A}$, we get: 
+D_{pp} = D_{pp}^{\rm HD}[l_{\rm A} < l < L] + D_{pp}^{\rm MHD}[l_{\rm cut} < l < l_{\rm A}]
+\end{equation}
+From equations (\ref{eqn:diffusion}) and (\ref{eqn:k_W}), and assuming Kolmogorov turbulence from $l_{\rm A} < l < L$ and Kraichnan turbulence from $l_{\rm cut} < l < l_{\rm A}$, we get: 
 \begin{equation}

### 2016-06-23 paper.tex
more corrections: \dot{p}|_rad, alpha_inj, etc.

@@
 \author[A. Pinzke, S. Peng Oh and C. Pfrommer] 
-{Anders Pinzke$^{1,2}$\thanks{apinzke@fysik.su.se (AP); peng@physics.ucsb.edu (SPO); christoph.pfrommer@h-its.org (CP)}, S. Peng Oh$^{3}$ and Christoph Pfrommer$^{4}$\footnotemark[1]\\
+{Anders Pinzke$^{1,2}$\thanks{apinzke@fysik.su.se (AP); peng@physics.ucsb.edu (SPO); christoph.pfrommer@h-its.org (CP)}, S.
+Peng Oh$^{3}$\footnotemark[1], and Christoph Pfrommer$^{4}$\footnotemark[1]\\
 $^{1}$The Oskar Klein Centre for Cosmoparticle Physics, Stockholm University, AlbaNova University Center, SE - 106 91
@@
 thermal plasma whose energy density declines steeply with radius. In
-Fig.~\ref{fig:Edens} we show that such a distribution is not predicted
+Figure~\ref{fig:Edens} we show that such a distribution is not predicted
 by cosmological simulations \cite[see
@@
 Here $f_{\rmn{e}}$ is the one-dimensional distribution in position $x$
-(suppressed for clarity), momentum $p$ and time $t$ (which is
+(suppressed for clarity), momentum $p=P/(m_{\rmn{e}} c)$ and time $t$ (which is
 normalised such that the number density is given by
-$n_{\rmn{e}}(t)=\int d p f_{\rmn{e}}(p,t)$), $d/d t=\partial/\partial
+$n_{\rmn{CRe}}(t)=\int d p f_{\rmn{e}}(p,t)$), $d/d t=\partial/\partial
 t+\bvel\bcdot\bnabla$ is the Lagrangian derivative, $\bvel$ is the gas
@@
   \left|\frac{d p}{d t}\right|_{\rm rad~} &=& \frac{4}{3}\frac{\sigma_\rmn{T}}{m_{\rmn{e}}c}\,
-  \frac{p^2}{\beta_{\rmn{e}}}\,\left[1+\left(\frac{B}{B_\rmn{CMB}}\right)^2\right]\,.
+  \frac{p^2}{\beta_{\rmn{e}}}\,\left[1+\left(\frac{B}{B_\rmn{CMB}}\right)^2\right]\,\eps_{\rmn{CMB}}\,.
 \end{eqnarray}
@@
 $Q_{\rmn{e}}$ denotes the injection rate of primary and secondary
-electrons in the ICM (see Sect.~\ref{sec:cosmo_sim}). The first term
+electrons in the ICM (see section~\ref{sec:cosmo_sim}). The first term
 containing the expression $\bnabla\bcdot \bvel$ represents Fermi-I
@@
 and $Q_{\rmn{p}}(p,t)$ denotes the injection rate of shock accelerated
-CRps as a function of momentum $p$ and time $t$ (see
-Sect.~\ref{sec:cosmo_sim}). The timescale of
+CRps as a function of momentum $p=P/(m_{\rmn{p}} c)$ and time $t$ (see
+section~\ref{sec:cosmo_sim}). The timescale of
 hadronic losses that produce pions via CRp collisions with thermal
@@
 which defines the normalisation $\langle (\delta \varv_{\rm c})^{2} \rangle$ (the subscript 'c' emphasizes that we specialise to compressive modes).
-Intuitively, we can understand the form of the the diffusion coefficient from the fact that for second-order Fermi acceleration, $\dot{p} \sim \Delta p/\tau \sim p\,\langle k c \rangle_{\mathcal{W}} (\delta \varv_{\rm c}/c)^{2}$, where $\tau^{-1} \sim \langle k c \rangle_{\mathcal{W}}$ is the energy averaged wave-particle interaction rate, and $\Delta p \sim p (\delta \varv_{\rm c}/c)^{2}$ is the typical momentum change during wave particle scattering.
+Intuitively, we can understand the form of the the diffusion coefficient from the fact that for second-order Fermi acceleration, $\dot{p} \sim \Delta p/\tau \sim p\,\langle k c \rangle_{\mathcal{W}} (\delta \varv_{\rm c}/c)^{2}$, where $\tau^{-1} \sim \langle k c \rangle_{\mathcal{W}}$ is the energy averaged wave-particle interaction rate, and $\Delta p \sim p (\delta \varv_{\rm c}/c)^{2}$ is the typical momentum change during wave-particle scattering.
 Thus:
@@
 Since the standard vanilla model requires a CR seed population which is
-inconsistent with the simulations (Fig \ref{fig:Edens}), some modifications are
+inconsistent with the simulations (Figure~\ref{fig:Edens}), some modifications are
 necessary, either in the seed CR population or in the properties of
@@
 \citep[e.g.,][]{2000ApJ...540..292E}. Given our assumed $\eb=0.23$, we
-find that for strong shocks where $\alpha \lesssim 2.3$ the spectral
+find that for strong shocks where $\alpha_{\rmn{inj}} \lesssim 2.3$ the spectral
 slope is steepened by a maximum of $\sim 10$ per cent in low
@@
 shocks that varies from $\zeta_\rmn{max} \sim 0.01-0.1$, depending on
-the adopted model (for more details, see Section \ref{sec:results}).
+the adopted model (for more details, see section~\ref{sec:results}).
 
@@
 
-In Fig.~\ref{fig:sync_profile}, we show radial profiles for the radio
+In Figure~\ref{fig:sync_profile}, we show radial profiles for the radio
 emission in all three scenarios in which the seeds undergo Fermi-II
@@
 ratio of turbulent-to-thermal energy densities slightly increase with
-radius as shown in Fig.~\ref{fig:turb}.  The fine-tuning of these exponents is somewhat problematic, as we discuss in \S\ref{sect:param_comp}. After turbulent
+radius as shown in Figure~\ref{fig:turb}.  The fine-tuning of these exponents is somewhat problematic, as we discuss in \S\ref{sect:param_comp}. After turbulent
 reacceleration, the volume-weighted, relative CRp energy density and
@@
 profiles without turbulent reacceleration are too steep.  In the
-bottom right panel of Fig.~\ref{fig:sync_profile} (labelled with
+bottom right panel of Figure~\ref{fig:sync_profile} (labelled with
 Brunetti et al. 2012), we show that our simulated profiles of
@@
 
-In Fig.~\ref{fig:tauD} we show how the turbulent reacceleration
+In Figure~\ref{fig:tauD} we show how the turbulent reacceleration
 timescales in our three models scale with radius. As expected, the
@@
 spectral steepening of the radio spectrum (see the left panel of
-Fig.~\ref{fig:sync_spectrum} where the continuous injection of
+Figure~\ref{fig:sync_spectrum} where the continuous injection of
 secondary CRes is absent). A given radio window samples higher energy
@@
 \label{sect:radio_spec}
-In Fig.~\ref{fig:sync_spectrum} we show that our three models that
+In Figure~\ref{fig:sync_spectrum} we show that our three models that
 include Fermi-II reacceleration can individually reproduce the
@@
 adiabatic compressive heating of the CRs, though this is generally
-subdominant (e.g., see Fig. 7 of \citealt{miniati15}). Once
+subdominant (e.g., see Figure~7 of \citealt{miniati15}). Once
 the CRs have been reaccelerated for $\tau_\rmn{cl} = 650\,\rmn{Myr}$,
@@
 and injection of secondary CRes from $f_\rmn{p,0}$.  The diffusion constant
-$D_{pp} \propto X_{\rm tu}^{2} \eps_{\rm th}^{\alpha-1} \sqrt{T} k_L$ is
+$D_{pp} \propto X_{\rm tu}^{2} \eps_{\rm th}^{\alpha_{\rm tu}-1} \sqrt{T} k_L$ is
 calculated for each radial bin. All parameters and assumptions are similar to
-what is used for our simulated cluster (see Sect.~\ref{sec:results}). Our
+what is used for our simulated cluster (see section~\ref{sec:results}). Our
 fiducial model assumes $X_{\rm tu} = 0.2$, $\alpha_{\rm tu} =0.8$, $\alpha_{\rm
@@
 
-{\bf Impact of overall level of turbulence ($X_{\rm tu}$).} From the top panels of Fig.~\ref{fig:param_comp}, we see that as $X_{\rm tu}$ increases, there are 3 important changes: an exponential increase in radio luminosity, a flattening of the radio surface brightness profile, and an increase in spectral curvature.
+{\bf Impact of overall level of turbulence ($X_{\rm tu}$).} From the top panels of Figure~\ref{fig:param_comp}, we see that as $X_{\rm tu}$ increases, there are 3 important changes: an exponential increase in radio luminosity, a flattening of the radio surface brightness profile, and an increase in spectral curvature.
 We discuss these in turn.
 
-As we show in \S\ref{sect:self-limiting}, the exponential increase in radio surface brightness is easily understood from equation~\ref{eq:Creacc}, since for a power-law initial distribution function $f_{\rm i}(p) = C_{\rm 0} p^{-\alpha}$, then $C_{\rm reacc} \propto C_{\rm 0} {\rm exp}(A \tau_{\rm cl}/\tau_{\rm D}) \propto {\rm exp} (B(r) X_{\rm tu}^{2})$.
+As we show in \S\ref{sect:self-limiting}, the exponential increase in radio surface brightness is easily understood from equation~\ref{eq:Creacc}, since for a power-law initial distribution function $f_{\rm i}(p) = C_{\rm 0} p^{-\alpha_{\rmn{inj}}}$, then $C_{\rm reacc} \propto C_{\rm 0} {\rm exp}(A \tau_{\rm cl}/\tau_{\rm D}) \propto {\rm exp} (B(r) X_{\rm tu}^{2})$.
 This exponential sensitivity is somewhat modified by cooling (which results in a non power-law spectrum; also, the shorter the acceleration time, the larger the pool of seed electrons available which would otherwise cool away), but overall is a good approximation.
@@
 
-{\bf Impact of spatial profile of turbulence ($\alpha_{\rm tu}$).} From the middle panels of Fig.~\ref{fig:param_comp}, we see that as expected, a flatter profile of the turbulent pressure directly translates into a flatter radio surface brightness profile.
+{\bf Impact of spatial profile of turbulence ($\alpha_{\rm tu}$).} From the middle panels of Figure~\ref{fig:param_comp}, we see that as expected, a flatter profile of the turbulent pressure directly translates into a flatter radio surface brightness profile.
 Since seed electrons are more concentrated toward the centre (the collisional production of secondaries is more rapid there), and magnetic fields are stronger, concentrating the turbulence toward the cluster centre for fixed $X_{\rm tu}$ results in higher radio luminosities, and slightly more curvature (due to the increased importance of cooling near the centre).
@@
 The overall level of turbulence has to be such that $\tau_{\rm D} \sim \tau_{\rm cl}$ (see Table \ref{tab:timescales}), otherwise, too little or too much amplification takes place.
-For instance, for $X_\rmn{tu}\gtrsim0.08$, changing $X_\rmn{tu}$ by a factor of two changes the radio surface brightness by a factor of $\sim 10-100$ (see top panels of Fig.~\ref{fig:param_comp}).
+For instance, for $X_\rmn{tu}\gtrsim0.08$, changing $X_\rmn{tu}$ by a factor of two changes the radio surface brightness by a factor of $\sim 10-100$ (see top panels of Figure~\ref{fig:param_comp}).
 The required $\tau_{\rm D}/\tau_{\rm cl}$ depends only logarithmically on the abundance of seed CRs.
@@
 We have seen that the radio luminosity depends very sensitively on $\tau_{\rm
-  cl}/\tau_{\rm D}$, through the very sensitive dependence on $X_{\rm tu}$ (Fig
+  cl}/\tau_{\rm D}$, through the very sensitive dependence on $X_{\rm tu}$ (Figure
 \ref{fig:param_comp}; note from equation \ref{eq:Dpp_scaling} that $\tau_{\rm D}
@@
 other relevant timescales of the problem.\footnote{In principle, CRp can still
-  lose energy via wave heating, at a rate $\bmath{\varv_{\rm A} \cdot \nabla} P_\CR$,
-  but we assume CR streaming is suppressed during mergers, when they are
-  spatially confined by scattering.} In this case, $\dot{p}= p/\tau_{\rm D}$,
-and after a time $\tau_{\rm cl}$, we have $p \rightarrow p \, {\rm
-  exp}(\tau_{\rm cl}/\tau_{\rm D})$ (where we have used the fact that $\tau_{\rm
-  D}$ is momentum independent). For an initial power law distribution function
-$f(p) = C p^{-\alpha}$, this momentum increase can be rewritten as a change of
-normalisation, $f(p) = \tilde{C} p^{-\alpha}$, where $\tilde{C} = {\rm exp}(
-\alpha \tau_{\rm cl}/\tau_{\rm D})$. A slightly more careful derivation by
-direct solution of the Fokker-Planck equation yields:
+  lose energy via wave heating, at a rate $\left|\bmath{\varv_{\rm A} \cdot
+    \nabla} P_\CR\right|$, but we assume CR streaming is suppressed during
+  mergers, when they are spatially confined by scattering.} In this case,
+$\dot{p}= p/\tau_{\rm D}$, and after a time $\tau_{\rm cl}$, we have $p
+\rightarrow p \, {\rm exp}(\tau_{\rm cl}/\tau_{\rm D})$ (where we have used the
+fact that $\tau_{\rm D}$ is momentum independent). For an initial power law
+distribution function $f(p) = C p^{-\alpha_{\rmn{inj}}}$, this momentum increase can be
+rewritten as a change of normalisation, $f(p) = \tilde{C} p^{-\alpha_{\rmn{inj}}}$, where
+$\tilde{C} = {\rm exp}( \alpha_{\rmn{inj}} \tau_{\rm cl}/\tau_{\rm D})$. A slightly more
+careful derivation by direct solution of the Fokker-Planck equation yields:
 \begin{equation}
@@
   \tilde{C}= 
-  C \exp{\left[\frac{(2+\alpha)(\alpha-1)}{4}\frac{\tau_\rmn{cl}}{\tau_\rmn{D}}\right]}\,.
-\end{equation}
-This exponential sensitivity to $\tau_{\rm cl}/\tau_{\rm D}$ lies behind the extreme sensitivity to $X_{\rm tu}$ in Fig \ref{fig:param_comp}.
-
-The natural solution to this puzzle would be a process that couples $\tau_{\rm cl}$ and $\tau_{\rm D}$.
-There are two possible limits.
-Let us suppose that the timescale on which there exists a source of turbulent driving is $\tau_{\rm drive}$, which is roughly the timescale of the merger, or the dynamical time.
-Let the turbulence decay on a timescale $\tau_{\rm decay}$.
-If $\tau_{\rm drive} > \tau_{\rm decay}$, then $\tau_{\rm cl} \sim \tau_{\rm drive}$, which depends on the details of the merger and should result in considerable scatter in $\tau_{\rm cl}/\tau_{\rm D}$ in different systems.
-On the other hand, if $\tau_{\rm decay} > \tau_{\rm drive}$, then $\tau_{\rm cl} \sim \tau_{\rm decay}$.
-Since $\tau_{\rm D}$ and $\tau_{\rm decay}$ are both related to properties of the turbulence, it is conceivable that this would result in much less scatter in $\tau_{\rm cl}/\tau_{\rm D}$.
+  C \exp{\left[\frac{(2+\alpha_{\rmn{inj}})(\alpha_{\rmn{inj}}-1)}{4}\frac{t}{\tau_\rmn{D}}\right]}\,.
+\end{equation}
+At $t=\tau_\rmn{cl}$ the CR distribution is exponentially sensitive to
+$\tau_{\rm cl}/\tau_{\rm D}$ which is the physical reason underlying
+the extreme sensitivity to $X_{\rm tu}$ in
+Figure~\ref{fig:param_comp}.
+
+The natural solution to this puzzle would be a process that couples
+$\tau_{\rm cl}$ and $\tau_{\rm D}$. There are two possible limits. Let
+us suppose that the timescale on which there exists a source of
+turbulent driving is $\tau_{\rm drive}$, which approximately
+corresponds to the timescale of the merger, or the dynamical time. Let
+the turbulence decay on a timescale $\tau_{\rm decay}$. If $\tau_{\rm
+  drive} > \tau_{\rm decay}$, then $\tau_{\rm cl} \sim \tau_{\rm
+  drive}$, which depends on the details of the merger and should
+result in considerable scatter in $\tau_{\rm cl}/\tau_{\rm D}$ in
+different systems. On the other hand, if $\tau_{\rm decay} > \tau_{\rm
+  drive}$, then $\tau_{\rm cl} \sim \tau_{\rm decay}$. Since
+$\tau_{\rm D}$ and $\tau_{\rm decay}$ are both related to properties
+of the turbulence, it is conceivable that this would result in much
+less scatter in $\tau_{\rm cl}/\tau_{\rm D}$.
 
@@
 etc., is only valid below these scales. For $l > l_{\rm A}$, turbulence is
-basically hydrodynamic and Kolmogorov in nature. The momentum diffusion
-coefficient can thus be split up into two components:
+basically hydrodynamic and follows the universal Kolmogorov scaling. The
+momentum diffusion coefficient can thus be split up into two components:
 \begin{equation}
@@
 It is interesting to reconsider surface brightness and spectral profiles if indeed $\tau_{\rm D} \sim \tau_{\rm cl}$, for the reasons mentioned above (e.g., equation \ref{eqn:ratios_CR_damp}).
-We show the results of adopting such an ansatz in Fig.
-\ref{fig:param_comp_tcl_tD}, where, similar to Fig.
-\ref{fig:param_comp}, we vary $X_{\rm tu}, \alpha_{\rm tu}, \alpha_{\rm CR, spat}$ about fiducial values, but this time we do not adopt a fixed $\tau_{\rm cl}$ but set $\tau_{\rm cl}=\tau_{\rm D}$.
+We show the results of adopting such an ansatz in Figure~\ref{fig:param_comp_tcl_tD}, where, similar to Figure~\ref{fig:param_comp}, we vary $X_{\rm tu}, \alpha_{\rm tu}, \alpha_{\rm CR, spat}$ about fiducial values, but this time we do not adopt a fixed $\tau_{\rm cl}$ but set $\tau_{\rm cl}=\tau_{\rm D}$.
 They are remarkably revealing.
@@
 
-For instance, in the top panels of Fig \ref{fig:param_comp_tcl_tD}, we see that once turbulence exceeds a threshold value $X_{\rm tu} \sim 0.1$, then its overall exact energy density does not matter -- profiles simply converge to an asymptotic form as $X_{\rm tu}$ is increased.
+For instance, in the top panels of Figure~\ref{fig:param_comp_tcl_tD}, we see that once turbulence exceeds a threshold value $X_{\rm tu} \sim 0.1$, then its overall exact energy density does not matter -- profiles simply converge to an asymptotic form as $X_{\rm tu}$ is increased.
 This is in contrast to the exponential sensitivity, flattening in surface brightness, and increasing spectral curvature as $X_{\rm tu}$ is increased that we saw previously.
@@
 This leads to the asymptotic behaviour seen.
-From the middle panels, we see another striking result: in contrast to Fig.
-\ref{fig:param_comp}, results are also completely insensitive to the turbulent profile.
+From the middle panels, we see another striking result: in contrast to Figure~\ref{fig:param_comp}, results are also completely insensitive to the turbulent profile.
 Given the large uncertainties in the latter, this is a welcome property.
@@
   parameters. For details see caption in
-  Fig.~\ref{fig:param_comp}. For simplicity, we assume that the
+  Figure~\ref{fig:param_comp}. For simplicity, we assume that the
   duration of reacceleration $\tau_{cl}=\tau_{\rm D}$, where $\tau_{\rm

### 2016-06-23 paper.tex
more edits; open points in section 4.3

@@
 }
+
+\usepackage[normalem]{ulem}
+\usepackage[usenames]{xcolor}
+\newcommand\cp[1]{{\color{red} #1}}
+\newcommand\po[1]{{\color{blue} #1}}
 
@@
 Here $f_{\rmn{e}}$ is the one-dimensional distribution in position $x$
-(suppressed for clarity), momentum $p=P/(m_{\rmn{e}} c)$ and time $t$ (which is
-normalised such that the number density is given by
+(suppressed for clarity), momentum \cp{$p=P/(m_{\rmn{e}} c)$} and time $t$
+(which is normalised such that the number density is given by
 $n_{\rmn{CRe}}(t)=\int d p f_{\rmn{e}}(p,t)$), $d/d t=\partial/\partial
-t+\bvel\bcdot\bnabla$ is the Lagrangian derivative, $\bvel$ is the gas
-velocity, $|d p/d t|$ represents Coulomb
-\citep[Coul,][]{1972Phy....60..145G} and radiative
-\citep[rad,][]{1979rpa..book.....R} losses, respectively,
+t+\bvel\bcdot\bnabla$ is the Lagrangian derivative, $\bvel$ is the gas velocity,
+$|d p/d t|$ represents Coulomb \citep[Coul,][]{1972Phy....60..145G} and
+radiative \citep[rad,][]{1979rpa..book.....R} losses, respectively,
 \begin{eqnarray}
@@
   \left|\frac{d p}{d t}\right|_{\rm rad~} &=& \frac{4}{3}\frac{\sigma_\rmn{T}}{m_{\rmn{e}}c}\,
-  \frac{p^2}{\beta_{\rmn{e}}}\,\left[1+\left(\frac{B}{B_\rmn{CMB}}\right)^2\right]\,\eps_{\rmn{CMB}}\,.
+  \frac{p^2}{\beta_{\rmn{e}}}\,\left[1+\left(\frac{B}{B_\rmn{CMB}}\right)^2\right]\,\cp{\eps_{\rmn{CMB}}}\,.
 \end{eqnarray}
@@
 and $Q_{\rmn{p}}(p,t)$ denotes the injection rate of shock accelerated
-CRps as a function of momentum $p=P/(m_{\rmn{p}} c)$ and time $t$ (see
+CRps as a function of momentum \cp{$p=P/(m_{\rmn{p}} c)$} and time $t$ (see
 section~\ref{sec:cosmo_sim}). The timescale of
@@
 \begin{equation}
+  \label{eqn:Dpp}
 D_{pp} \sim p \dot{p} \sim p^{2} \langle k c \rangle_{\mathcal{W}} \left( \frac{\delta \varv_{\rm c}}{c} \right)^{2}. 
@@
 
-Equations \ref{eqn:diffusion} and \ref{eqn:Wk} make the important aspects of turbulence clear: the energy in compressive modes $\langle (\delta \varv_{\rm c})^{2} \rangle$, the inner and outer scale ($k_{\rm cut}$ and $k_L$), and the slope of the energy spectrum $s$.
+Equations (\ref{eqn:diffusion}) and (\ref{eqn:Wk}) make the important aspects of turbulence clear: the energy in compressive modes $\langle (\delta \varv_{\rm c})^{2} \rangle$, the inner and outer scale ($k_{\rm cut}$ and $k_L$), and the slope of the energy spectrum $s$.
 All of these can vary spatially and temporally.
@@
 where $I_L$ is the volumetric injection rate of turbulence at scale $L$ (which is assumed to be constant), $\varv_{\rm ph}\approx c_{\rm s}$ is the phase speed of waves.
-It is important to realise that this only applies at small scales, where turbulence is magneto-hydrodynamical.
+\cp{Since the Kraichnan spectrum is critical in what follows, it is worthwhile taking a moment to recount the origin of the spectral slope $s$ and the cascade rate.
+In the magnetically dominated regime, two counterpropagating wave packets of scale $l$ interact on an Alfv{\'e}n time $\tau_{\rm A}=l/\varv_{\rm A}$, rather than the eddy turnover time $\tau_{\rm edd} = l/\varv_{\rm l}$.
+Since $\tau_{\rm A} \ll \tau_{\rm edd}$, each interaction results in a small velocity change $\delta \varv_{\rm l} \sim \varv_{\rm l} (\tau_{\rm A}/\tau_{\rm edd})$.
+If these changes behave like a random walk, the cascade time $\tau_{\rm l}$ it takes for an eddy to become non-linear ($\Delta \varv \sim \varv_{\rm l})$ and cascades to smaller scales occurs with a characteristic velocity $\varv_{\rm l} \sim \delta \varv_{\rm l} (\tau_{\rm l}/\tau_{\rm A})^{1/2} \sim \varv_{\rm l} \tau_{\rm A}/\tau_{\rm edd} (\tau_{\rm l}/\tau_{\rm A})^{1/2}$, which we can solve to obtain the cascade time:
+\begin{equation}
+  \label{eqn:tau_l}
+\tau_{\rm l} \sim \left(\frac{\tau_{\rm edd}}{\tau_{\rm A}}\right)^{2} \tau_{\rm A} \sim \frac{l \varv_{\rm A}}{\varv_{\rm l}^{2}} 
+\end{equation}
+where we have implicitly assumed isotropy.
+This implies a dissipation rate $\epsilon \sim \varv_{\rm l}^{2}/\tau_{\rm l} \sim \varv_{\rm l}^{4}/(l \varv_{\rm A})$, or $\varv_{\rm l} \sim (\epsilon l \varv_{A})^{1/4}$.
+Thus, since $k E(k)\sim \varv_{\rm l}^{2}$, this gives a kinetic energy spectrum:
+\begin{equation}
+E(k) \sim (\epsilon \varv_{\rm A})^{1/2} k^{-3/2}.
+\end{equation}}
+
+It is important to realise that this Kraichnan scaling only applies at small scales, where turbulence is magneto-hydrodynamical.
 At large scales, turbulent motions are subsonic (${\mathcal M}_{\rm s} \sim 0.2-0.5$) but super-Alfv{\'e}nic (${\mathcal M}_{\rm A} \sim 5$).
@@
 Thus, at some scale $l_{\rm A} \sim l_L {\mathcal M}_{\rm A}^{-3}$, where $\eps_{\rm turb} \sim \eps_{B}$, the magnetic field becomes dynamically important, and turbulence transitions to the MHD regime.
-The cutoff scale in equation \ref{eqn:Wk} can be computed by setting the turbulent cascade rate for fast modes to the transit time damping rate on thermal electrons.
+The cutoff scale in equation (\ref{eqn:Wk}) can be computed by setting the turbulent cascade rate for fast modes to the transit time damping rate on thermal electrons.
 This yields \citep{brunetti07,miniati15}:
 \begin{equation}
-k_{\rm cut} \approx A k_L \frac{\langle \varv_L^{2}\rangle^{2}}{c_{\rm s}^{4}}
-%k_{\rm c} \approx A k_{\rm outer} \frac{\langle \varv_{\rm outer}^{2}\rangle^{2}}{c_{\rm s}^{4}}
+k_{\rm cut} \approx A k_L \frac{\langle (\delta \varv_{\rmn{c}})^{2}\rangle^{2}}{c_{\rm s}^{4}}
 \label{eqn:k_c} 
@@
 
-The important effects are best summarised in terms of the acceleration time: 
-\begin{equation}
-\tau_{\rm D}= \frac{p^{2}}{4 D_{pp}}
-\end{equation}
-which is momentum independent.
-This should be compared against the lifetime of turbulence, $\tau_{\rm cl}$, and the cooling time $\tau_{\rm cool}$.
-In Table~\ref{tab:timescales}, we show both the thermal quantities and the
+The important effects are best summarised in terms of the acceleration \cp{rate
+  which is goverend by advection in momentum space:
+\begin{equation}
+  \tau_{\rm D}^{-1}\equiv \Gamma_{\rm D}\equiv
+  \frac{\dot{p}}{p}=p^{-3}\frac{\partial}{\partial p}\left(p^2D_{pp}\right)
+  =\frac{4 D_{pp}}{p^{2}}.
+\end{equation}
+In the last step we have used that $D_{pp}\propto p^2$ for the turbulent
+reacceleration (equation \ref{eqn:Dpp}). Hence the acceleration time is independent of momentum.}
+%\begin{equation}
+%\tau_{\rm D}= \frac{p^{2}}{4 D_{pp}}
+%\end{equation}
+%which is momentum independent.
+This should be compared against the lifetime of turbulence, $\tau_{\rm cl}$, and the cooling time $\tau_{\rm cool}$. In Table~\ref{tab:timescales}, we show both the thermal quantities and the
 timescales for CR cooling and (re)acceleration for three different
@@
   cl}/\tau_{\rm D}$, through the very sensitive dependence on $X_{\rm tu}$ (Figure
-\ref{fig:param_comp}; note from equation \ref{eq:Dpp_scaling} that $\tau_{\rm D}
+\ref{fig:param_comp}; note from equation (\ref{eq:Dpp_scaling}) that $\tau_{\rm D}
 \propto X_{\rm tu}^{-2}$). Since this raises questions of fine-tuning in $X_{\rm
@@
 with the analytic solution given by
+\cp{
 \begin{equation}
@@
 \end{equation}
-At $t=\tau_\rmn{cl}$ the CR distribution is exponentially sensitive to
+At $t=\tau_\rmn{cl}$} the CR distribution is exponentially sensitive to
 $\tau_{\rm cl}/\tau_{\rm D}$ which is the physical reason underlying
@@
 \begin{equation}
-\frac{D_{pp}^{\rm HD}}{D_{pp}^{\rm MHD}} = \frac{k_L^{2/3}k_{\rm A}^{1/3} \varv_{\rm c}^{2}}{k_{\rm A}^{1/2}k_{\rm cut}^{1/2} \varv_{\rm A}^{2}} = A^{-1/2} \beta = 0.5 \left( \frac{\beta}{50} \right) 
-\end{equation}
-where we have used $k_{\rm A} = k_L \mathcal{M}_{\rm A}^{3}$ (from Kolmogorov scalings, and $\mathcal{M}_{\rm A} = \varv_{\rm c}/\varv_{\rm A}$ is the Alfv{\'e}n Mach number of the turbulence, $\beta \approx c_{\rm s}^{2}/\varv_{\rm A}^{2}$, and the cutoff scale $k_{\rm cut}$ (equation \ref{eqn:k_c}).
+  \frac{D_{pp}^{\rm HD}}{D_{pp}^{\rm MHD}}
+  = \frac{\cp{2}k_L^{2/3}k_{\rm A}^{1/3} \varv_{\rm c}^{2}}{k_{\rm A}^{1/2}k_{\rm cut}^{1/2} \varv_{\rm A}^{2}}
+  = \cp{2 \left(A \mathcal{M}_\rmn{A}\right)^{-1/2}} \beta = 0.5 \left( \frac{\beta}{50} \right) 
+\end{equation}
+where we have used $k_{\rm A} = k_L \mathcal{M}_{\rm A}^{3}$ (from Kolmogorov scalings), and $\mathcal{M}_{\rm A} = \varv_{\rm c}/\varv_{\rm A}$ is the Alfv{\'e}n Mach number of the turbulence, $\beta \approx c_{\rm s}^{2}/\varv_{\rm A}^{2}$, and the cutoff scale $k_{\rm cut}$ (equation \ref{eqn:k_c}).
 Thus, the contribution of the two regimes are comparable (as we shall see later, this is not true if one incorrectly assumes Kraichnan scalings apply from the outer scale $L$; this boosts the contribution of the scales where $l_{\rm A} < l < L$ by a factor $\mathcal{M}_{\rm A}^{1/2}$).
@@
 \end{equation}
-where $C_{\rm D} = 2/(5 \upi)$, $A\approx 11000$, and we have used equation \ref{eqn:k_c}.
+\cp{[The previous equation is wrong (you can see this by checking the units). Instead I get:]
+\begin{equation}
+\tau_{\rm D} = \frac{p^{2}}{4 D_{pp}} = C_{\rm D} \left(A\mathcal{M}_\rmn{A}\right)^{-1/2} \frac{c}{k_{\rm A}} \frac{c_{\rm s}^{2}}{\varv_{\rm A}^{4}}
+\label{eqn:tau_D} 
+\end{equation}
+}
+where $C_{\rm D} = 2/(5 \upi)$, $A\approx 11000$, and we have used equation (\ref{eqn:k_c}).
 The turbulent decay time is given by the cascade time of fast modes (\citealt{2004ApJ...614..757Y}; see equation \ref{eqn:cascade}):
@@
 \end{equation}
+\cp{[This agrees with Eqn.
+(3) of \citet{2004ApJ...614..757Y} but appears to disagree with our equation (\ref{eqn:tau_l}): Peng, do you understand this apparent contradiction?
+Can we motivate this important equation?]}
 This can be related to the eddy turnover time at the outer scale $\tau_{\rm edd}$ from $l_{\rm A} = L \mathcal{M}_{\rm A}^{-3}$ to: 
@@
 \end{equation}
+\cp{[I get 0.08 as prefactor mainly because of the $2\upi$ conversion from $k$ to $L$.]}
 where we have used $\tilde{X}_{\rm tu} \approx (\varv_{\rm c}/c_{\rm s})^{2}$ and $c_{\rm s}/\varv_{\rm A} = \beta^{1/2}$.
@@
 
-From equations \ref{eqn:tau_D} and \ref{eqn:tau_decay}, we obtain:
+From equations (\ref{eqn:tau_D}) and (\ref{eqn:tau_decay}), we obtain:
 \begin{equation}
@@
 \end{equation}
+\cp{[I get]
+  \begin{eqnarray}
+    \frac{\tau_{\rm cl}}{\tau_{\rm D}} &\approx& \frac{\tau_{\rm decay}}{\tau_{\rm D}}
+    \approx\frac{0.6\sqrt{A}\mathcal{M}_\rmn{A}^{7/2}}{C_\rmn{D}\beta}\,\frac{\varv_\rmn{A}^2}{\varv_\rmn{c} c}\nonumber\\
+    &\approx&0.1 \left( \frac{c_{\rm s}}{1000 \, {\rm km \, s^{-1}}} \right) \left( \frac{\beta}{100} \right)^{-1}\, 
+\label{eqn:ratios_TTD} 
+\end{eqnarray}
+[which is {\bf not} independent of the properties of turbulence!]}
 Remarkably, this expression is independent of properties of the turbulence such as $\varv_{\rm c}$, $L$, or $l_{\rm A}$, and depends only on properties of the plasma ($c_{\rm s},\beta$).
-Ultimately, this arises because the timescale on which a fast mode wave transfers energy due to wave particle interactions in second order Fermi acceleration, $\tau_{\rm p} \sim [k_{\rm p} c (\varv_{\rm c}/c)^{2} ]^{-1}$, is closely related to the timescale on which it cascades due to wave-wave interactions, $\tau_{\rm w} \sim c_{\rm s}/(k_{\rm w} \varv_{\rm c}^{2})$.
-This implies $\tau_{\rm w}/\tau_{\rm p} \sim (c_{\rm s}/c)(l_{\rm w}/l_{\rm p})$, where $l_{\rm w} \sim l_{\rm A}$ is the outer scale on which the fast mode cascade begins, and $l_{\rm p} \sim (l_{\rm A} l_{\rm cut})^{1/2}$ is the characteristic wavelength for wave-particle interactions.
+Ultimately, this arises because the timescale on which a fast mode wave transfers energy due to wave particle interactions in second order Fermi acceleration, $\tau_{\rm p} \sim [\cp{4\,} k_{\rm p} c (\varv_{\rm c}/c)^{2} ]^{-1}$, is closely related to the timescale on which it cascades due to wave-wave interactions, $\tau_{\rm w} \sim c_{\rm s}/(k_{\rm w} \varv_{\rm c}^{2})$.
+This implies $\tau_{\rm w}/\tau_{\rm p} \sim \cp{4\,} (c_{\rm s}/c)(l_{\rm w}/l_{\rm p})$, where $l_{\rm w} \sim l_{\rm A}$ is the outer scale on which the fast mode cascade begins, and $l_{\rm p} \sim (l_{\rm A} l_{\rm cut})^{1/2}$ is the characteristic wavelength for wave-particle interactions.
 For transit time damping and an outer scale of $l_{\rm A}$, we have $l_{\rm cut} \sim (m_{\rm e}/m_{\rm p}) l_{\rm A} (c_{\rm s}/\varv_{\rm A})^{4}$.
-We thus have $\tau_{\rm w}/\tau_{\rm p} \sim (c_{\rm s}/c)(l_{\rm A}/l_{\rm cut})^{1/2} \sim (c_{\rm s}/c) (m_{\rm p}/m_{\rm e})^{1/2} \beta^{-1}$.
-More careful consideration of dimensionless factors boosts this estimate by an order of magnitude to give equation \ref{eqn:ratios_TTD}.
-
-On the other hand, equation \ref{eqn:ratios_TTD} points toward a pessimistic scenario where turbulent reacceleration with TTD on thermal particles is never effective.
+We thus have $\tau_{\rm w}/\tau_{\rm p} \sim \cp{4\,}(c_{\rm s}/c)(l_{\rm A}/l_{\rm cut})^{1/2} \sim \cp{4\,}(c_{\rm s}/c) (m_{\rm p}/m_{\rm e})^{1/2} \beta^{-1}$.
+More careful consideration of dimensionless factors boosts this estimate by an order of magnitude to give equation (\ref{eqn:ratios_TTD}).
+
+On the other hand, equation (\ref{eqn:ratios_TTD}) points toward a pessimistic scenario where turbulent reacceleration with TTD on thermal particles is never effective.
 A key reason is that we assume Kraichnan turbulence only applies for $l< l_{\rm A}$.
@@
 
-It is also worth exploring the effect of Burgers' turbulence (weak shocks). From equation \ref{eqn:diffusion} and \ref{eqn:k_W}, we find: 
+It is also worth exploring the effect of Burgers' turbulence (weak shocks). From equations (\ref{eqn:diffusion}) and (\ref{eqn:k_W}), we find: 
 \begin{equation}

### 2016-06-23 paper.tex
further questions and additions

@@
 \end{equation}
+\cp{[This assumes the energy equipartition argument (by Sarkar) for $D_{pp}^\rmn{MHD}$ and for $D_{pp}^\rmn{HD}$; is this justified at the sme time?
+if so, why?
+and we should explain this in a footnote.]}
 where we have used $k_{\rm A} = k_L \mathcal{M}_{\rm A}^{3}$ (from Kolmogorov scalings), and $\mathcal{M}_{\rm A} = \varv_{\rm c}/\varv_{\rm A}$ is the Alfv{\'e}n Mach number of the turbulence, $\beta \approx c_{\rm s}^{2}/\varv_{\rm A}^{2}$, and the cutoff scale $k_{\rm cut}$ (equation \ref{eqn:k_c}).
@@
 
-It is also worth exploring the effect of Burgers' turbulence (weak shocks). From equations (\ref{eqn:diffusion}) and (\ref{eqn:k_W}), we find: 
+It is also worth exploring the effect of Burgers' turbulence (weak shocks).
+\cp{Burgers' turbulence is distinct from other forms of turbulence in that it violates locality in $k$-space--i.e., power does not gradually cascade, but instead can directly jump from large to small scales via a network of weak shocks.
+Since the Fourier transform of a step function goes as $k^{-1}$, Burgers turbulence has a power spectrum of $P(k) \propto k^{-2}$.} From equations (\ref{eqn:diffusion}) and (\ref{eqn:k_W}), we find:
 \begin{equation}

### 2016-06-24 paper.tex
corrections to account for l_outer=l_A in the MHD cascade

--- 2016-06-23 paper.tex
@@
 \begin{equation}
-k_{\rm cut} \approx A k_L \frac{\langle (\delta \varv_{\rmn{c}})^{2}\rangle^{2}}{c_{\rm s}^{4}}
+k_{\rm cut} \approx A k_{\rmn{outer}} \frac{\langle (\delta \varv_{\rmn{outer}})^{2}\rangle^{2}}{c_{\rm s}^{4}}
+\label{eqn:k_c1} 
+\end{equation}
+where $A \approx 11 000$.
+\cp{If there is an unimpeded cascade from the injection to the cutoff scale, $k_{\rmn{outer}}=k_L$ and $\varv_{\rmn{outer}}=\varv_{\rmn{c}}$.
+However, in our case the hydrodynamic (Kolmogorov) cascade transitions to the MHD cascade at the Alfv{\'e}n scale so that $k_{\rmn{outer}}=k_{\rmn{A}}$ and $\varv_{\rmn{outer}}=\varv_{\rmn{A}}$ and hence, we get\footnote{\cp{Note that this differs from previous work which uses the wave number and compressible velocity at the outer scale $L$ for this estimate of $k_{\rm cut}$.}}
+\begin{equation}
+k_{\rm cut} \approx A k_{\rmn{A}} \beta^{-2}\,.
 \label{eqn:k_c} 
 \end{equation}
-where $A \approx 11 000$. This gives $2\upi/k_\rmn{cut}\sim 0.1-1$~kpc in the ICM. This constitutes an
+}
+This gives $2\upi/k_\rmn{cut}\sim 0.1-1$~kpc in the ICM. This constitutes an
 effective mean free path for CRs, unless plasma instabilities can
@@
 We assume an injection scale $k_L=2\upi/\lambda_L$, where $\lambda_L = 100$ kpc, which were assumptions adopted in previous work \citep{2006MNRAS.366.1437S,brunetti07, brunetti11}.
-This length scale corresponds to an eddy turnover time on the outer scale of $\varv_L k_L^{-1} \sim 1.2$~Gyr if $\varv_L \sim 500 {\rm km \, s^{-1}}$, as is characteristic of a merger.
+This length scale corresponds to an eddy turnover time on the outer scale of \cp{\sout{$\varv_L k_L^{-1} \sim 1.2$~Gyr} $2\upi\lambda_L\varv_L^{-1} \sim 1.2$~Gyr} if $\varv_L \sim 500 {\rm km \, s^{-1}}$, as is characteristic of a merger.
 Note that hydrodynamical simulations of clusters have sometimes found larger $\lambda_L$, in some cases comparable to the size of the cluster \citep{vazza11,miniati15}.
@@
 \begin{equation}
+  \label{eqn:Dratio}
   \frac{D_{pp}^{\rm HD}}{D_{pp}^{\rm MHD}}
   = \frac{\cp{2}k_L^{2/3}k_{\rm A}^{1/3} \varv_{\rm c}^{2}}{k_{\rm A}^{1/2}k_{\rm cut}^{1/2} \varv_{\rm A}^{2}}
-  = \cp{2 \left(A \mathcal{M}_\rmn{A}\right)^{-1/2}} \beta = 0.5 \left( \frac{\beta}{50} \right) 
-\end{equation}
-where we have used $k_{\rm A} = k_L \mathcal{M}_{\rm A}^{3}$ (from Kolmogorov scalings), and $\mathcal{M}_{\rm A} = \varv_{\rm c}/\varv_{\rm A}$ is the Alfv{\'e}n Mach number of the turbulence, $\beta \approx c_{\rm s}^{2}/\varv_{\rm A}^{2}$, and the cutoff scale $k_{\rm cut}$ (equation \ref{eqn:k_c}).
-Thus, the contribution of the two regimes are comparable (as we shall see later, this is not true if one incorrectly assumes Kraichnan scalings apply from the outer scale $L$; this boosts the contribution of the scales where $l_{\rm A} < l < L$ by a factor $\mathcal{M}_{\rm A}^{1/2}$).
+  = \cp{2} A^{-1/2} \beta = \cp{1.0}\, \left( \frac{\beta}{50} \right) 
+\end{equation}
+where we have used $k_{\rm A} = k_L \mathcal{M}_{\rm A}^{3}$ (from Kolmogorov
+scalings), and $\mathcal{M}_{\rm A} = \varv_{\rm c}/\varv_{\rm A}$ is the
+Alfv{\'e}n Mach number of the turbulence, $\beta \approx c_{\rm
+  s}^{2}/\varv_{\rm A}^{2}$, and the cutoff scale $k_{\rm cut}$ (equation
+\ref{eqn:k_c}).  Thus, the contribution of the two regimes are
+comparable\footnote{\cp{The estimate of equation~(\ref{eqn:Dratio}) assumes that
+    in both cascades, kinetic and potential energy are in equipartition which is
+    likely an overestimate for the hydrodynamical cascade and hence, the
+    hydrodynamic contribution to the momentum diffusion would be small in
+    comparison to the MHD contribution. }} (as we shall see later, this is not
+true if one incorrectly assumes Kraichnan scalings apply from the outer scale
+$L$; this boosts the contribution of the scales where $l_{\rm A} < l < L$ by a
+factor $\mathcal{M}_{\rm A}^{1/2}$).
+
 Henceforth, we can consider the outer scale of the fast modes to be $l_{\rm A}$, with velocity $\varv_{\rm A}$. The turbulent reacceleration time is: 
-\begin{equation}
-\tau_{\rm D} = \frac{p^{2}}{4 D_{pp}} = C_{\rm D} A^{1/2} c k_{\rm A} \frac{\varv_{\rm A}^{2}}{c_{\rm S}^{2}}
-\label{eqn:tau_D} 
-\end{equation}
-\cp{[The previous equation is wrong (you can see this by checking the units). Instead I get:]
-\begin{equation}
-\tau_{\rm D} = \frac{p^{2}}{4 D_{pp}} = C_{\rm D} \left(A\mathcal{M}_\rmn{A}\right)^{-1/2} \frac{c}{k_{\rm A}} \frac{c_{\rm s}^{2}}{\varv_{\rm A}^{4}}
+%\begin{equation}
+%\tau_{\rm D} = \frac{p^{2}}{4 D_{pp}} = C_{\rm D} A^{1/2} c k_{\rm A} \frac{\varv_{\rm A}^{2}}{c_{\rm S}^{2}}
+%\label{eqn:tau_D} 
+%\end{equation}
+\cp{
+  \begin{equation}
+\tau_{\rm D} = \frac{p^{2}}{4 D_{pp}} = \frac{C_{\rm D}}{A^{1/2}}\, \frac{c}{k_{\rm A}}\, \frac{c_{\rm s}^{2}}{\varv_{\rm A}^{4}}
 \label{eqn:tau_D} 
@@
 where $C_{\rm D} = 2/(5 \upi)$, $A\approx 11000$, and we have used equation (\ref{eqn:k_c}).
-The turbulent decay time is given by the cascade time of fast modes (\citealt{2004ApJ...614..757Y}; see equation \ref{eqn:cascade}):
-\begin{equation}
-\tau_{\rm decay} = \frac{c_{\rm s}}{\varv_{\rm A}^{2} k_{\rm A}^{}}\,.
+The turbulent decay time is given by the cascade time of fast modes \cp{at the Alfv\'en scale $k=k_{\rmn{A}}$} (\citealt{2004ApJ...614..757Y}; see equation \ref{eqn:cascade}):
+\begin{equation}
+  \tau_{\rm decay} = \cp{\frac{\varv_{\rm ph}}{\varv_k^{2} k} = }
+  \frac{c_{\rm s}}{\varv_{\rm A}^{2} k_{\rm A}^{}}\,.
 \label{eqn:tau_decay} 
 \end{equation}
-\cp{[This agrees with Eqn.
-(3) of \citet{2004ApJ...614..757Y} but appears to disagree with our equation (\ref{eqn:tau_l}): Peng, do you understand this apparent contradiction?
-Can we motivate this important equation?]}
 This can be related to the eddy turnover time at the outer scale $\tau_{\rm edd}$ from $l_{\rm A} = L \mathcal{M}_{\rm A}^{-3}$ to: 
@@
 where we have used $\tilde{X}_{\rm tu} \approx (\varv_{\rm c}/c_{\rm s})^{2}$ and $c_{\rm s}/\varv_{\rm A} = \beta^{1/2}$.
-Thus $\tau_{\rm decay} \sim \tau_{\rm edd}$, but we prefer to use the expression for $\tau_{\rm edd}$, since it is more physically correct and leads to more revealing scalings.
+\cp{\sout{Thus $\tau_{\rm decay} \sim \tau_{\rm edd}$, but we prefer to use the expression for $\tau_{\rm edd}$, since it is more physically correct and leads to more revealing scalings.
+}}
 
@@
 \begin{equation}
-\frac{\tau_{\rm cl}}{\tau_{\rm D}} \approx \frac{\tau_{\rm decay}}{\tau_{\rm D}} = 0.1 \left( \frac{c_{\rm s}}{1500 \, {\rm km \, s^{-1}}} \right) \left( \frac{\beta}{50} \right)^{-1}\,. 
+  \frac{\tau_{\rm cl}}{\tau_{\rm D}} \approx \frac{\tau_{\rm decay}}{\tau_{\rm D}}
+  \cp{= \frac{A^{1/2}}{C_{\rmn{D}}}\,\frac{c_{\rm s}}{c}\,\beta^{-1}}
+  = 0.1 \left( \frac{c_{\rm s}}{1500 \, {\rm km \, s^{-1}}} \right) \left( \frac{\beta}{50} \right)^{-1}\,. 
 \label{eqn:ratios_TTD} 
 \end{equation}
-\cp{[I get]
-  \begin{eqnarray}
-    \frac{\tau_{\rm cl}}{\tau_{\rm D}} &\approx& \frac{\tau_{\rm decay}}{\tau_{\rm D}}
-    \approx\frac{0.6\sqrt{A}\mathcal{M}_\rmn{A}^{7/2}}{C_\rmn{D}\beta}\,\frac{\varv_\rmn{A}^2}{\varv_\rmn{c} c}\nonumber\\
-    &\approx&0.1 \left( \frac{c_{\rm s}}{1000 \, {\rm km \, s^{-1}}} \right) \left( \frac{\beta}{100} \right)^{-1}\, 
-\label{eqn:ratios_TTD} 
-\end{eqnarray}
-[which is {\bf not} independent of the properties of turbulence!]}
 Remarkably, this expression is independent of properties of the turbulence such as $\varv_{\rm c}$, $L$, or $l_{\rm A}$, and depends only on properties of the plasma ($c_{\rm s},\beta$).

### 2016-06-24 paper.tex
additions as a result of a skype chat with Peng

@@
 \end{equation}
-where $I_L$ is the volumetric injection rate of turbulence at scale $L$ (which is assumed to be constant), $\varv_{\rm ph}\approx c_{\rm s}$ is the phase speed of waves.
-\cp{Since the Kraichnan spectrum is critical in what follows, it is worthwhile taking a moment to recount the origin of the spectral slope $s$ and the cascade rate.
-In the magnetically dominated regime, two counterpropagating wave packets of scale $l$ interact on an Alfv{\'e}n time $\tau_{\rm A}=l/\varv_{\rm A}$, rather than the eddy turnover time $\tau_{\rm edd} = l/\varv_{\rm l}$.
-Since $\tau_{\rm A} \ll \tau_{\rm edd}$, each interaction results in a small velocity change $\delta \varv_{\rm l} \sim \varv_{\rm l} (\tau_{\rm A}/\tau_{\rm edd})$.
-If these changes behave like a random walk, the cascade time $\tau_{\rm l}$ it takes for an eddy to become non-linear ($\Delta \varv \sim \varv_{\rm l})$ and cascades to smaller scales occurs with a characteristic velocity $\varv_{\rm l} \sim \delta \varv_{\rm l} (\tau_{\rm l}/\tau_{\rm A})^{1/2} \sim \varv_{\rm l} \tau_{\rm A}/\tau_{\rm edd} (\tau_{\rm l}/\tau_{\rm A})^{1/2}$, which we can solve to obtain the cascade time:
+where $I_L$ is the volumetric injection rate of turbulence at scale $L$ (which
+is assumed to be constant), $\varv_{\rm ph}\approx c_{\rm s}$ is the phase speed
+of waves. \cp{Since the Kraichnan spectrum is critical in what follows, it is
+  worthwhile taking a moment to recount the origin of the spectral slope $s$ and
+  the cascade rate. In the magnetically dominated regime, two counterpropagating
+  wave packets of scale $l$ interact on a wave crossing time $\tau_{\rm
+    ph}=l/\varv_{\rm ph}$, rather than the eddy turnover time $\tau_{\rm edd} =
+  l/\varv_{\rm l}$.  Since $\tau_{\rm ph} \ll \tau_{\rm edd}$, each interaction
+  results in a small velocity change $\delta \varv_{\rm l} \sim \varv_{\rm l}
+  (\tau_{\rm ph}/\tau_{\rm edd})$. If these changes behave like a random walk,
+  the cascade time $\tau_{\rm l}$ it takes for an eddy to become non-linear
+  ($\Delta \varv \sim \varv_{\rm l})$ and cascades to smaller scales occurs with
+  a characteristic velocity $\varv_{\rm l} \sim \delta \varv_{\rm l} (\tau_{\rm
+    l}/\tau_{\rm ph})^{1/2} \sim \varv_{\rm l} (\tau_{\rm ph}/\tau_{\rm edd})\,
+  (\tau_{\rm l}/\tau_{\rm ph})^{1/2}$, which we can solve to obtain the cascade
+  time:
 \begin{equation}
   \label{eqn:tau_l}
-\tau_{\rm l} \sim \left(\frac{\tau_{\rm edd}}{\tau_{\rm A}}\right)^{2} \tau_{\rm A} \sim \frac{l \varv_{\rm A}}{\varv_{\rm l}^{2}} 
+\tau_{\rm l} \sim \left(\frac{\tau_{\rm edd}}{\tau_{\rm ph}}\right)^{2} \tau_{\rm ph} \sim \frac{l \varv_{\rm ph}}{\varv_{\rm l}^{2}} 
 \end{equation}
 where we have implicitly assumed isotropy.
-This implies a dissipation rate $\epsilon \sim \varv_{\rm l}^{2}/\tau_{\rm l} \sim \varv_{\rm l}^{4}/(l \varv_{\rm A})$, or $\varv_{\rm l} \sim (\epsilon l \varv_{A})^{1/4}$.
+This implies a dissipation rate $\epsilon \sim \varv_{\rm l}^{2}/\tau_{\rm l} \sim \varv_{\rm l}^{4}/(l \varv_{\rm ph})$, or $\varv_{\rm l} \sim (\epsilon l \varv_{\rm ph})^{1/4}$.
 Thus, since $k E(k)\sim \varv_{\rm l}^{2}$, this gives a kinetic energy spectrum:
 \begin{equation}
-E(k) \sim (\epsilon \varv_{\rm A})^{1/2} k^{-3/2}.
+E(k) \sim (\epsilon \varv_{\rm ph})^{1/2} k^{-3/2}.
 \end{equation}}
@@
 \cp{If there is an unimpeded cascade from the injection to the cutoff scale, $k_{\rmn{outer}}=k_L$ and $\varv_{\rmn{outer}}=\varv_{\rmn{c}}$.
-However, in our case the hydrodynamic (Kolmogorov) cascade transitions to the MHD cascade at the Alfv{\'e}n scale so that $k_{\rmn{outer}}=k_{\rmn{A}}$ and $\varv_{\rmn{outer}}=\varv_{\rmn{A}}$ and hence, we get\footnote{\cp{Note that this differs from previous work which uses the wave number and compressible velocity at the outer scale $L$ for this estimate of $k_{\rm cut}$.}}
+However, in our case the hydrodynamic (Kolmogorov) cascade transitions to the MHD cascade at the Alfv{\'e}n scale so that $k_{\rmn{outer}}=k_{\rmn{A}}$ and $\varv_{\rmn{outer}}=\varv_{\rmn{A}}$ and hence, we get\footnote{\cp{Note that this differs from previous work, which assumes Kraichnan turbulence from the injection scale onward and effectively adopts wave number and compressible velocity at the outer scale $L$ for this estimate of $k_{\rm cut}$.}}
 \begin{equation}
@@
 \end{equation}
-In the last step we have used that $D_{pp}\propto p^2$ for the turbulent
+In the last step we have used that $D_{pp}\propto p^2$ for turbulent
 reacceleration (equation \ref{eqn:Dpp}). Hence the acceleration time is independent of momentum.}
@@
 We assume an injection scale $k_L=2\upi/\lambda_L$, where $\lambda_L = 100$ kpc, which were assumptions adopted in previous work \citep{2006MNRAS.366.1437S,brunetti07, brunetti11}.
-This length scale corresponds to an eddy turnover time on the outer scale of \cp{\sout{$\varv_L k_L^{-1} \sim 1.2$~Gyr} $2\upi\lambda_L\varv_L^{-1} \sim 1.2$~Gyr} if $\varv_L \sim 500 {\rm km \, s^{-1}}$, as is characteristic of a merger.
+This length scale corresponds to an eddy turnover time on the outer scale of \cp{$2\upi\lambda_L\varv_L^{-1} \sim 1.2$~Gyr} if $\varv_L \sim 500 {\rm km \, s^{-1}}$, as is characteristic of a merger.
 Note that hydrodynamical simulations of clusters have sometimes found larger $\lambda_L$, in some cases comparable to the size of the cluster \citep{vazza11,miniati15}.
@@
 where $C_{\rm D} = 2/(5 \upi)$, $A\approx 11000$, and we have used equation (\ref{eqn:k_c}).
-The turbulent decay time is given by the cascade time of fast modes \cp{at the Alfv\'en scale $k=k_{\rmn{A}}$} (\citealt{2004ApJ...614..757Y}; see equation \ref{eqn:cascade}):
+The turbulent decay time is given by the cascade time of fast modes \cp{at the Alfv\'en scale $k=k_{\rmn{A}}$} (\citealt{2004ApJ...614..757Y}; see equation \ref{eqn:tau_l}):
 \begin{equation}
@@
 \cp{[I get 0.08 as prefactor mainly because of the $2\upi$ conversion from $k$ to $L$.]}
-where we have used $\tilde{X}_{\rm tu} \approx (\varv_{\rm c}/c_{\rm s})^{2}$ and $c_{\rm s}/\varv_{\rm A} = \beta^{1/2}$.
-\cp{\sout{Thus $\tau_{\rm decay} \sim \tau_{\rm edd}$, but we prefer to use the expression for $\tau_{\rm edd}$, since it is more physically correct and leads to more revealing scalings.
-}}
-
-From equations (\ref{eqn:tau_D}) and (\ref{eqn:tau_decay}), we obtain:
+where we have used $\tilde{X}_{\rm tu} \approx (\varv_{\rm c}/c_{\rm s})^{2}$ and $c_{\rm s}/\varv_{\rm A} = \beta^{1/2}$. From equations (\ref{eqn:tau_D}) and (\ref{eqn:tau_decay}), we obtain:
 \begin{equation}
@@
 \cp{Burgers' turbulence is distinct from other forms of turbulence in that it violates locality in $k$-space--i.e., power does not gradually cascade, but instead can directly jump from large to small scales via a network of weak shocks.
+This implies a short dissipation time and we have in this case, $\tau_{\rm cl} \sim \tau_{\rm drive}$, the driving time, rather than the turbulent dissipation time.
 Since the Fourier transform of a step function goes as $k^{-1}$, Burgers turbulence has a power spectrum of $P(k) \propto k^{-2}$.} From equations (\ref{eqn:diffusion}) and (\ref{eqn:k_W}), we find:
@@
 Since $\langle k \rangle_{\mathcal{W}} \approx k_L$ is independent of the cutoff scale $k_{\rm cut}$, this conclusion is unchanged if plasma instabilities regulate the thermal particle mean free path and TTD operates on relativistic particles instead.
-Since standard TTD on thermal particles was already potentially problematic (equation \ref{eqn:ratios_TTD}), we conclude, in agreement with other assessments \citep{miniati15,brunetti16_review}, that if Burgers turbulence dominates, then turbulent reacceleration will be ineffective\footnote{Note also that since there is no real cascade in Burgers' turbulence, but direct transfer of power from large to small scales, the dissipation time is potentially short.
-In this case, $\tau_{\rm cl} \sim \tau_{\rm drive}$, the driving time, rather than the turbulent dissipation time.}.
+Since standard TTD on thermal particles was already potentially problematic (equation \ref{eqn:ratios_TTD}), we conclude, in agreement with other assessments \citep{miniati15,brunetti16_review}, that if Burgers turbulence dominates, then turbulent reacceleration will be ineffective.
 

### 2016-08-03 paper.tex
Add files via upload

@@
 \newcommand\po[1]{{\color{blue} #1}}
+\newcommand\AP[1]{{\color{green} #1}}
 
@@
   Fokker-Planck equation of the cosmic ray (CR) electron and proton
-  distributions in cosmological simulations of cluster formation, and confront
+  distributions in \AP{the post-processing of} cosmological simulations of cluster formation, and confront
   them with radio surface brightness and spectral observations of Coma. For
@@
 advected with the cluster plasma, their distribution will be peaked
-towards the cluster centre and shows a similar characteristics as the
+towards the cluster centre and show a similar characteristics as the
 thermal plasma. As a consequence, the distribution of secondary
@@
 smallest scales $k_{\rm cut}$, and the radio halo turns on shortly after. We
-choose this simulation snapshot to analyse. We are not very sensitive to this
-assumption, since the thermal and CR quantities are very similar a few 100 Myrs
-before and after $z = 0$, where we have chosen to evaluate the simulations. In
-all our calculations we assume that turbulent reacceleration efficiently
+choose this simulation snapshot to analyse.
+\AP{Note that in recent simulations by \citet{miniati15}, the turbulent reacceleration is strongest around core passage.
+However, we are not very sensitive to the adopted decay time, since the thermal and CR quantities are very similar a few 100 Myrs before and after $z = 0$, where we have chosen to evaluate the simulations.}
+In all our calculations we assume that turbulent reacceleration efficiently
 accelerates particles for $\tau_{\rm cl} \sim 650$ Myrs (which is roughly the
@@
 $B$-fields at the accretion shock, so that the total number of CRs is conserved
-within the virial radius during the streaming process.  In all our calculations
-we assume that turbulent reacceleration efficiently accelerates particles for
-$\tau_\rmn{cl}\sim650$~Myrs (which is roughly the cascade time on which
-turbulence is damped) and that during this turbulent phase CR streaming and
-spatial diffusion can be neglected.
+within the virial radius during the streaming process.
 
@@
 This length scale corresponds to an eddy turnover time on the outer scale of \cp{$2\upi\lambda_L\varv_L^{-1} \sim 1.2$~Gyr} if $\varv_L \sim 500 {\rm km \, s^{-1}}$, as is characteristic of a merger.
-Note that hydrodynamical simulations of clusters have sometimes found larger $\lambda_L$, in some cases comparable to the size of the cluster \citep{vazza11,miniati15}.
+Note that hydrodynamical simulations of clusters have sometimes found larger $\lambda_L$, in some cases comparable to the size of the cluster \AP{\citep[e.g.
+$\lambda_L \sim 1 {\rm Mpc}$ in ][]{vazza11,miniati15}}.
 This choice is degenerate with $X_{\rm tu}$; in \S\ref{sect:self-limiting} we argue that $k_{\rm A}$ is a more appropriate choice, but also find that when the decay time is appropriately scaled, we are relatively insensitive to the choice of $k_L$.
@@
 $\gamma_\rmn{ad} = 5/3$ and the Mach number of the shock
-$\mathcal{M}$. It is given by the ratio of the upstream velocity
+$\mathcal{M}$ \AP{\citep[see also ][]{1998ApJ...502..518Q,miniati01,pfrommer06}}. It is given by the ratio of the upstream velocity
 ($\varv_2$) and the sound speed ($c_{\rm s}$). The CR number density and CR
@@
 parametrization for the volumetric injection rate of turbulent energy,
-$I_0\propto \eps_\rmn{th}^{\alpha_\rmn{tu}}$, we find that to fit the observations, we require
+$I_L\propto \eps_\rmn{th}^{\alpha_\rmn{tu}}$, we find that to fit the observations, we require
 $\alpha_\rmn{tu}= 0.67$ for \Mflatturb, $\alpha_\rmn{tu}= 0.82$ for
@@
 account, i.e. they neglect CR streaming or a flatter turbulent
-profile, produce radio profiles that are too steep. Indeed, even using
-the assumptions of previous work -- where complete freedom in the seed
-population was allowed -- it is not possible to reproduce observations
-in both frequencies in any model.\footnote{Note that in previous work
+profile, produce radio profiles that are too steep. \AP{Indeed, even using
+the assumptions of previous work, where complete freedom in the seed
+population was allowed, it is not possible to reproduce observations
+in both frequencies in any model\footnote{Note that in previous work
   on the Coma cluster, $\eps_\rmn{turb} \propto \eps_\rmn{th}$ was
@@
   \citep{brunetti12} and together with the different distributions for
-  seed CRes constitute the main differences compared to our work.}
+  seed CRes constitute the main differences compared to our work.} -- with or without turbulent reacceleration.}
 Decreasing the acceleration efficiency with radius does not change

### 2016-08-26 paper.tex
implemented Peng's changes

@@
   observations could then potentially constrain the unknown CR seed
-  population. Understanding the small scatter in radio halo scaling relations
+  population.
+\po{Given that MHD turbulence only begins at the Alfven scale, in order to have sufficient acceleration, the turbulent cascade has to terminate by transit time damping on CRs, i.e., thermal particles must be scattered by plasma instabilities.} Understanding the small scatter in radio halo scaling relations
   may prove a rich source of insight on plasma processes in the ICM.
@@
 Thus, except in the case where motions are transsonic and weak shocks become important, motions are fundamentally hydrodynamic and turbulence follows a Kolmogorov ($s=5/3$) spectrum.
-However, while the turbulent energy density $\eps_{\rm turb} \propto l^{2/3}$ decreases at small scales, the magnetic energy density is scale-independent.
+However, while the turbulent energy density $\eps_{\rm turb} \propto l^{2/3}$ decreases at small scales, the magnetic energy density \po{(which is dominated by the large scale mean field} is scale-independent.
 Thus, at some scale $l_{\rm A} \sim l_L {\mathcal M}_{\rm A}^{-3}$, where $\eps_{\rm turb} \sim \eps_{B}$, the magnetic field becomes dynamically important, and turbulence transitions to the MHD regime.
@@
 $\sim 20-40$ per cent of the total turbulent energy, and shows more rapid temporal
-variations compared to the compressible component
+variations compared to the \po{incompressible} component
 \citep{2013ApJ...771..131B,miniati15}. Note the compressible component in
@@
 The important effects are best summarised in terms of the acceleration \cp{rate
-  which is goverend by advection in momentum space:
+  which is governed by advection in momentum space:
 \begin{equation}
@@
 
+\po{In this section, we explore the physical origin of the high sensitivity of radio emission to turbulence levels (e.g., top right panel of Fig.
+\ref{fig:param_comp}), which thus requires strong fine-tuning to explain observed radio profiles.
+We will find that by relating the acceleration time to the turbulent decay time, this sensitivity can be eliminated.
+We also challenge the common assumption of assuming a Kraichnan spectrum, beginning at the outer scale (see \S\ref{sec:reacc}).
+Since turbulence is essentially hydrodynamic at large scales, this is unjustified.
+Instead, we shall assume that the outer scale of the compressive fast modes is the Alfven scale.}
+
 There are 3 important timescales in this problem: the acceleration time $\tau_{\rm D}$, the duration over which turbulence is active and acceleration takes place, $\tau_{\rm cl}$, and the cooling time $\tau_{\rm cool}(p)$.
@@
   tu}$ to explain the observations, it is worth understanding this property in
-more detail. To this end, we ignore cooling which is a good approximation for
+more detail. To this end, we ignore cooling, which is a good approximation for
 the CR protons, because hadronic cooling times are long in comparison to the
@@
 At $t=\tau_\rmn{cl}$} the CR distribution is exponentially sensitive to
-$\tau_{\rm cl}/\tau_{\rm D}$ which is the physical reason underlying
+$\tau_{\rm cl}/\tau_{\rm D}$, which is the physical reason underlying
 the extreme sensitivity to $X_{\rm tu}$ in
@@
 An obvious candidate for $\tau_{\rm decay}$ is: 
-\begin{equation}
-\tau_{\rm edd} = \frac{L}{\varv_{\rm c}}
-\end{equation}
+\po{\begin{equation}
+\tau_{\rm edd} = \frac{L}{\varv_{\rm L}}
+\end{equation}}
 i.e., the eddy turnover time at the outer scale. This is subject to
@@
 etc., is only valid below these scales. For $l > l_{\rm A}$, turbulence is
-basically hydrodynamic and follows the universal Kolmogorov scaling. The
-momentum diffusion coefficient can thus be split up into two components:
-\begin{equation}
-D_{pp} = D_{pp}^{\rm HD}[l_{\rm A} < l < L] + D_{pp}^{\rm MHD}[l_{\rm cut} < l < l_{\rm A}]
-\end{equation}
-From equations (\ref{eqn:diffusion}) and (\ref{eqn:k_W}), and assuming Kolmogorov turbulence from $l_{\rm A} < l < L$ and Kraichnan turbulence from $l_{\rm cut} < l < l_{\rm A}$, we get: 
-\begin{equation}
-  \label{eqn:Dratio}
-  \frac{D_{pp}^{\rm HD}}{D_{pp}^{\rm MHD}}
-  = \frac{\cp{2}k_L^{2/3}k_{\rm A}^{1/3} \varv_{\rm c}^{2}}{k_{\rm A}^{1/2}k_{\rm cut}^{1/2} \varv_{\rm A}^{2}}
-  = \cp{2} A^{-1/2} \beta = \cp{1.0}\, \left( \frac{\beta}{50} \right) 
-\end{equation}
-where we have used $k_{\rm A} = k_L \mathcal{M}_{\rm A}^{3}$ (from Kolmogorov
-scalings), and $\mathcal{M}_{\rm A} = \varv_{\rm c}/\varv_{\rm A}$ is the
-Alfv{\'e}n Mach number of the turbulence, $\beta \approx c_{\rm
-  s}^{2}/\varv_{\rm A}^{2}$, and the cutoff scale $k_{\rm cut}$ (equation
-\ref{eqn:k_c}).  Thus, the contribution of the two regimes are
-comparable\footnote{\cp{The estimate of equation~(\ref{eqn:Dratio}) assumes that
-    in both cascades, kinetic and potential energy are in equipartition which is
-    likely an overestimate for the hydrodynamical cascade and hence, the
-    hydrodynamic contribution to the momentum diffusion would be small in
-    comparison to the MHD contribution. }} (as we shall see later, this is not
-true if one incorrectly assumes Kraichnan scalings apply from the outer scale
-$L$; this boosts the contribution of the scales where $l_{\rm A} < l < L$ by a
-factor $\mathcal{M}_{\rm A}^{1/2}$).
-
-Henceforth, we can consider the outer scale of the fast modes to be $l_{\rm A}$, with velocity $\varv_{\rm A}$. The turbulent reacceleration time is: 
+basically hydrodynamic.
+
+\po{In the hydrodynamic regime, a standard Hodge-Helmholtz decomposition usually shows that the compressive component of the velocity field is Burgers-like ($W(k) \propto k^{-2}$), while the solenoidal component is Kolomogorov-like ($W(k) \propto k^{-5/3}$), see e.g., \citet{federrath13}.
+The Burgers-like component does not reflect a genuine cascade, but rather the appearance of shocks which directly transfer power from large to small scales.
+At face value, we should use the Burgers spectrum for compressible modes.
+However, as already found by previous authors \citep{miniati15, brunetti16}, and as we shall discuss, this does not produce significant particle acceleration.
+If this is the correct spectrum, then the paradigm of turbulent particle acceleration is simply flawed, and some other mechanism is necessary to explain radio halos.
+Alternatively, it is well-known that due to mode-mode coupling,  solenoidal modes can give rise to compressive modes, and vice-versa \citep{kida90,cho03,kritsuk07}, even for subsonic turbulence, since pressure fluctuations of order $\sim \rho u^{2}$ arise.
+Indeed, note that many numerical studies (such as \citet{cho03,kritsuk07}) only have solenoidal driving on the outer scale, but then are also able to study the compressive modes that develop.
+In hydrodynamic turbulence, the energy in compressible modes which develop in this way scales as $\sim \mathcal{M}_{s}^2$, for $\mathcal{M}_{s} < 1$; this coupling is strongest at the Alfven scale \citep{cho03}.
+In MHD turbulence, mode-mode coupling is weak below the Alfven scale and the Alfven, fast and slow modes proceed as separate cascades.}
+
+\po{We thus assume that some fraction of the Kolmogorov-like hydrodynamic turbulence which cascades down to the Alfven scale ends up as compressive fast modes with a Kraichnan spectrum, as seen in simulations \citep{cho03}.
+Henceforth, we can consider the outer scale of the fast modes to be $l_{\rm A}$.
+If some fraction $f_{\rm c}$ of the turbulent energy density at this scale is in compressible modes, then the energy density at the outer scale is velocity $\sim f_{\rm c} \rho \varv_{\rm A}^{2}$.}
+%and follows the universal Kolmogorov scaling. The
+%momentum diffusion coefficient can thus be split up into two components:
+%\begin{equation}
+%D_{pp} = D_{pp}^{\rm HD}[l_{\rm A} < l < L] + D_{pp}^{\rm MHD}[l_{\rm cut} < l < l_{\rm A}]
+%\end{equation}
+%From equations (\ref{eqn:diffusion}) and (\ref{eqn:k_W}), and assuming Kolmogorov turbulence from $l_{\rm A} < l < L$ and Kraichnan turbulence from $l_{\rm cut} < l < l_{\rm A}$, we get: 
+%\begin{equation}
+%  \label{eqn:Dratio}
+%  \frac{D_{pp}^{\rm HD}}{D_{pp}^{\rm MHD}}
+%  = \frac{\cp{2}k_L^{2/3}k_{\rm A}^{1/3} \varv_{\rm c}^{2}}{k_{\rm A}^{1/2}k_{\rm cut}^{1/2} \varv_{\rm A}^{2}}
+%  = \cp{2} A^{-1/2} \beta = \cp{1.0}\, \left( \frac{\beta}{50} \right) 
+%\end{equation}
+%where we have used $k_{\rm A} = k_L \mathcal{M}_{\rm A}^{3}$ (from Kolmogorov
+%scalings), and $\mathcal{M}_{\rm A} = \varv_{\rm c}/\varv_{\rm A}$ is the
+%Alfv{\'e}n Mach number of the turbulence, $\beta \approx c_{\rm
+%  s}^{2}/\varv_{\rm A}^{2}$, and the cutoff scale $k_{\rm cut}$ (equation
+%\ref{eqn:k_c}).  Thus, the contribution of the two regimes are
+%comparable\footnote{\cp{The estimate of equation~(\ref{eqn:Dratio}) assumes that
+%%    in both cascades, kinetic and potential energy are in equipartition which is
+%    likely an overestimate for the hydrodynamical cascade and hence, the
+%   hydrodynamic contribution to the momentum diffusion would be small in
+%    comparison to the MHD contribution. }} (as we shall see later, this is not
+%true if one incorrectly assumes Kraichnan scalings apply from the outer scale
+%$L$; this boosts the contribution of the scales where $l_{\rm A} < l < L$ by a
+%factor $\mathcal{M}_{\rm A}^{1/2}$).
+The turbulent reacceleration time is: 
 %\begin{equation}
@@
 %\end{equation}
-\cp{
-  \begin{equation}
-\tau_{\rm D} = \frac{p^{2}}{4 D_{pp}} = \frac{C_{\rm D}}{A^{1/2}}\, \frac{c}{k_{\rm A}}\, \frac{c_{\rm s}^{2}}{\varv_{\rm A}^{4}}
+\po{
+  \begin{equation}
+\tau_{\rm D} = \frac{p^{2}}{4 D_{pp}} = \po{\frac{C_{\rm D}}{A^{1/2}}\, \frac{c}{k_{\rm A}}\, \frac{\beta}{f_{\rm c} \varv_{\rm A}^{2}}}
 \label{eqn:tau_D} 
@@
 }
-where $C_{\rm D} = 2/(5 \upi)$, $A\approx 11000$, and we have used equation (\ref{eqn:k_c}).
+where $C_{\rm D} = 2/(5 \upi)$, $A\approx 11000$, and we have used equations, \po{(\ref{eqn:diffusion}), (\ref{eqn:k_W}), (\ref{eqn:k_c}), assuming $s=3/2$}.
 The turbulent decay time is given by the cascade time of fast modes \cp{at the Alfv\'en scale $k=k_{\rmn{A}}$} (\citealt{2004ApJ...614..757Y}; see equation \ref{eqn:tau_l}):
@@
   \tau_{\rm decay} = \cp{\frac{\varv_{\rm ph}}{\varv_k^{2} k} = }
-  \frac{c_{\rm s}}{\varv_{\rm A}^{2} k_{\rm A}^{}}\,.
+\po{\frac{c_{\rm s}}{f_{\rm c} \varv_{\rm A}^{2} k_{\rm A}^{}}\,.}
 \label{eqn:tau_decay} 
@@
 \begin{equation}
-\tau_{\rm decay} =\frac{L}{\varv_{\rm c}} \left(\frac{c_{\rm s}}{\varv_{\rm c}} \right)^{2} \frac{\varv_{\rm A}}{c_{\rm s}} = 0.7 \, \tau_{\rm edd} \left(\frac{\tilde{X}_{\rm tu}}{0.2}\right)^{-1}  \left(\frac{\beta}{100} \right)^{-1/2}
-\end{equation}
-\cp{[I get 0.08 as prefactor mainly because of the $2\upi$ conversion from $k$ to $L$.]}
-where we have used $\tilde{X}_{\rm tu} \approx (\varv_{\rm c}/c_{\rm s})^{2}$ and $c_{\rm s}/\varv_{\rm A} = \beta^{1/2}$. From equations (\ref{eqn:tau_D}) and (\ref{eqn:tau_decay}), we obtain:
+\po{\tau_{\rm decay} =\frac{L}{\varv_{\rm L}} \frac{c_{\rm s}^{2}}{f_{\rm c} \varv_{\rm L}^{2}}  \frac{\varv_{\rm A}}{c_{\rm s}} \approx  1.0 \, \tau_{\rm edd} \left(\frac{\tilde{X}_{\rm tu}}{0.2}\right)^{-1}  \left(\frac{\beta}{50} \right)^{-1/2}}
+\end{equation}
+where we have used $\tilde{X}_{\rm tu} \approx f_{\rm c} (\varv_{\rm L}/c_{\rm s})^{2}$ and $c_{\rm s}/\varv_{\rm A} = \beta^{1/2}$.
+\po{The decay time at the Alfven scale is comparable (and could be larger, if $f_{\rm c}$ is smaller than we have assumed) to the eddy turnover time at the outer scale.
+Thus, it is appropriate to consider the latter as the decay time for the fast modes, rather than the cascade time at the driving scale.
+The reason for these comparable timescales despite the disparate lengthscales is that large scale hydrodynamic modes cascade on a single eddy turnover time, whereas small scale sub-Alfvenic MHD modes are in the weak turbulence limit, and require multiple wave-wave interactions for a mode to cascade.
+}
+
+From equations (\ref{eqn:tau_D}) and (\ref{eqn:tau_decay}), we obtain:
 \begin{equation}
@@
 \end{equation}
-Given the host of uncertain factors which enter into $\zeta < 1$ (the intermittent nature of turbulence, small scale magnetic topology and the efficiency with which instabilities mediated by pressure anisotropies are triggered), this is potential consistent with $\tau_{\rm cl} \sim \tau_{\rm D}$.
+Given the host of uncertain factors which enter into $\zeta < 1$ (the intermittent nature of turbulence, small scale magnetic topology and the efficiency with which instabilities mediated by pressure anisotropies are triggered), this is potentially consistent with $\tau_{\rm cl} \sim \tau_{\rm D}$.
 This promising scenario should be investigated in more detail.

### 2016-08-31 paper.tex
small edits

@@
   Fokker-Planck equation of the cosmic ray (CR) electron and proton
-  distributions in \AP{the post-processing of} cosmological simulations of cluster formation, and confront
-  them with radio surface brightness and spectral observations of Coma. For
-  standard assumptions, structure formation shocks lead to a seed electron
-  population which produces too centrally concentrated radio emission. By
-  modifying properties of the CR population (rapid streaming; enhanced CR
-  electron acceleration at shocks) or turbulence (increasing
-  turbulent-to-thermal energy density with radius), we can match observations,
-  but only at the expense of fine-tuning. We then perform a parameter
-  study. Under naive assumptions, radio properties are exponentially sensitive
-  to the amplitude of turbulence, which is inconsistent with small scatter in
-  scaling relations. This sensitivity can be removed if we relate the
+  distributions in \AP{the post-processing of} cosmological simulations of
+  cluster formation, and confront them with radio surface brightness and
+  spectral data of Coma. For standard assumptions, structure formation
+  shocks lead to a seed electron population which produces too centrally
+  concentrated radio emission. By modifying properties of the CR population
+  (rapid streaming; enhanced CR electron acceleration at shocks) or turbulence
+  (increasing turbulent-to-thermal energy density with radius), we can match
+  observations, but only at the expense of fine-tuning. We then perform a
+  parameter study. Under naive assumptions, radio properties are exponentially
+  sensitive to the amplitude of turbulence, which is inconsistent with small
+  scatter in scaling relations. This sensitivity can be removed if we relate the
   acceleration time to the turbulent dissipation time. Their ratio depends only
@@
   observations could then potentially constrain the unknown CR seed
-  population.
-\po{Given that MHD turbulence only begins at the Alfven scale, in order to have sufficient acceleration, the turbulent cascade has to terminate by transit time damping on CRs, i.e., thermal particles must be scattered by plasma instabilities.} Understanding the small scatter in radio halo scaling relations
-  may prove a rich source of insight on plasma processes in the ICM.
+  population. \po{Given that MHD turbulence only begins at the Alfv{\'e}n scale, in
+    order to have sufficient acceleration, the turbulent cascade has to
+    terminate by transit time damping on CRs, i.e., thermal particles must be
+    scattered by plasma instabilities.} Understanding the small scatter in radio
+  halo scaling relations may prove a rich source of insight on plasma processes
+  in the ICM.
 \end{abstract}
@@
 and spatial profile of these two input ingredients in turbulent reacceleration
-models. The outline of this paper is as follows. In \S\ref{sect:method}, we
+models. The outline of this paper is as follows. In Section~\ref{sect:method}, we
 outline the basic physics of turbulent reacceleration of CRs which we use. In
-\S\ref{sec:results}, we use cosmological simulations to generate a seed CR
+Section~\ref{sec:results}, we use cosmological simulations to generate a seed CR
 population, and combine it with our parametrized model of turbulence to produce
@@
   turb}/\eps_{\rm th}$ with radius), but only at the expense of fine
-tuning. In \S\ref{sect:param_comp}, we explore the reason for this fine-tuning,
+tuning. In Section~\ref{sect:param_comp}, we explore the reason for this fine-tuning,
 and seek ways to overcome it. We perform a parameter study on spherically
@@
 potentially constrain the unknown CR seed population. We summarise and conclude
-in \S\ref{sec:conclusions}.
+in Section~\ref{sec:conclusions}.
 
@@
 inverse Compton emission. $D_{pp}$ is the momentum space diffusion
-coefficient (see \S\ref{sec:reacc}), and
+coefficient (see Section~\ref{sec:reacc}), and
 $Q_{\rmn{e}}$ denotes the injection rate of primary and secondary
@@
 CR streaming and spatial diffusion can be neglected. In
-\S\ref{sect:self-limiting}, we explore sensitivity to the last assumption.
+Section~\ref{sect:self-limiting}, we explore sensitivity to the last assumption.
 
@@
 which defines the normalisation $\langle (\delta \varv_{\rm c})^{2} \rangle$ (the subscript 'c' emphasizes that we specialise to compressive modes).
-Intuitively, we can understand the form of the the diffusion coefficient from the fact that for second-order Fermi acceleration, $\dot{p} \sim \Delta p/\tau \sim p\,\langle k c \rangle_{\mathcal{W}} (\delta \varv_{\rm c}/c)^{2}$, where $\tau^{-1} \sim \langle k c \rangle_{\mathcal{W}}$ is the energy averaged wave-particle interaction rate, and $\Delta p \sim p (\delta \varv_{\rm c}/c)^{2}$ is the typical momentum change during wave-particle scattering.
+Intuitively, we can understand the form of the diffusion coefficient from the fact that for second-order Fermi acceleration, $\dot{p} \sim \Delta p/\tau \sim p\,\langle k c \rangle_{\mathcal{W}} (\delta \varv_{\rm c}/c)^{2}$, where $\tau^{-1} \sim \langle k c \rangle_{\mathcal{W}}$ is the energy averaged wave-particle interaction rate, and $\Delta p \sim p (\delta \varv_{\rm c}/c)^{2}$ is the typical momentum change during wave-particle scattering.
 Thus:
@@
 Thus, except in the case where motions are transsonic and weak shocks become important, motions are fundamentally hydrodynamic and turbulence follows a Kolmogorov ($s=5/3$) spectrum.
-However, while the turbulent energy density $\eps_{\rm turb} \propto l^{2/3}$ decreases at small scales, the magnetic energy density \po{(which is dominated by the large scale mean field} is scale-independent.
+However, while the turbulent energy density $\eps_{\rm turb} \propto l^{2/3}$ decreases at small scales, the magnetic energy density \po{(which is dominated by the large scale mean field)} is scale-independent.
 Thus, at some scale $l_{\rm A} \sim l_L {\mathcal M}_{\rm A}^{-3}$, where $\eps_{\rm turb} \sim \eps_{B}$, the magnetic field becomes dynamically important, and turbulence transitions to the MHD regime.
@@
 mediate interactions between turbulence and particles on smaller
-scales \citep{brunetti11}, a possibility we discuss in \S\ref{sect:self-limiting}.
+scales \citep{brunetti11}, a possibility we discuss in Section~\ref{sect:self-limiting}.
 Another possibility is that compressible modes dissipate in weak shocks, resulting in Burgers' turbulence $s=2$ \citep{kowal10,porter15,miniati15}.
@@
 $\lambda_L \sim 1 {\rm Mpc}$ in ][]{vazza11,miniati15}}.
-This choice is degenerate with $X_{\rm tu}$; in \S\ref{sect:self-limiting} we argue that $k_{\rm A}$ is a more appropriate choice, but also find that when the decay time is appropriately scaled, we are relatively insensitive to the choice of $k_L$.
+This choice is degenerate with $X_{\rm tu}$; in Section~\ref{sect:self-limiting} we argue that $k_{\rm A}$ is a more appropriate choice, but also find that when the decay time is appropriately scaled, we are relatively insensitive to the choice of $k_L$.
 We present $\tau_{\rm D}$ for 3 different models, which we discuss in the next section.
@@
 population, and find the minimal modifications required to fit observations. We
-re-examine these choices in \S\ref{sect:param_comp}.
+re-examine these choices in Section~\ref{sect:param_comp}.
 
@@
   \zeta_\rmn{lin} =
-  \frac{\Delta\eps_\rmn{p,lin}}{\Delta\eps_\rmn{diss}},
+  \frac{\Delta\eps_\rmn{\CR,lin}}{\Delta\eps_\rmn{diss}},
    \quad\mbox{where}\quad
@@
 ratio of turbulent-to-thermal energy densities slightly increase with
-radius as shown in Figure~\ref{fig:turb}.  The fine-tuning of these exponents is somewhat problematic, as we discuss in \S\ref{sect:param_comp}. After turbulent
+radius as shown in Figure~\ref{fig:turb}.  The fine-tuning of these exponents is somewhat problematic, as we discuss in Section~\ref{sect:param_comp}. After turbulent
 reacceleration, the volume-weighted, relative CRp energy density and
@@
 radius driven by the decrease in thermal energy density. The
-\Mflatturb model has the the flattest turbulent profile parametrized
+\Mflatturb model has the flattest turbulent profile parametrized
 by the smaller $\alpha_\rmn{tu}$ which explains the steepest $\tau_{\rm D}$
@@
 derived from a gamma-ray profile similar to \Mflatturb\footnote{Fabio Zandanel,
-  private communication. See also
-  \citet{2014MNRAS.440..663Z,2014ApJ...787...18A}. and will be probed in the
+  private communication; see also
+  \citet{2014MNRAS.440..663Z,2014ApJ...787...18A}; this will be probed in the
   next few years by Fermi-LAT.} where
@@
 
-As we show in \S\ref{sect:self-limiting}, the exponential increase in radio surface brightness is easily understood from equation~\ref{eq:Creacc}, since for a power-law initial distribution function $f_{\rm i}(p) = C_{\rm 0} p^{-\alpha_{\rmn{inj}}}$, then $C_{\rm reacc} \propto C_{\rm 0} {\rm exp}(A \tau_{\rm cl}/\tau_{\rm D}) \propto {\rm exp} (B(r) X_{\rm tu}^{2})$.
+As we show in Section~\ref{sect:self-limiting}, the exponential increase in radio surface brightness is easily understood from equation~\ref{eq:Creacc}, since for a power-law initial distribution function $f_{\rm i}(p) = C_{\rm 0} p^{-\alpha_{\rmn{inj}}}$, then $C_{\rm reacc} \propto C_{\rm 0} {\rm exp}(A \tau_{\rm cl}/\tau_{\rm D}) \propto {\rm exp} (B(r) X_{\rm tu}^{2})$.
 This exponential sensitivity is somewhat modified by cooling (which results in a non power-law spectrum; also, the shorter the acceleration time, the larger the pool of seed electrons available which would otherwise cool away), but overall is a good approximation.
@@
 Depending on the details of infall or mergers, we would naturally expect fluctuations in $X_{\rm tu}$, which would translate into large scatter in the $L_{\rm radio}$--$L_{\rm X}$ relation.
-This can be only be understood if the timescale over which acceleration takes place $\tau_{\rm cl}$ also depends on the properties of turbulence, so that the the ratio $\tau_{\rm D}/\tau_{\rm cl}$ has relatively little scatter.
+This can be only be understood if the timescale over which acceleration takes place $\tau_{\rm cl}$ also depends on the properties of turbulence, so that the ratio $\tau_{\rm D}/\tau_{\rm cl}$ has relatively little scatter.
 We address this next.
@@
 We will find that by relating the acceleration time to the turbulent decay time, this sensitivity can be eliminated.
-We also challenge the common assumption of assuming a Kraichnan spectrum, beginning at the outer scale (see \S\ref{sec:reacc}).
+We also challenge the common assumption of assuming a Kraichnan spectrum, beginning at the outer scale (see Section~\ref{sec:reacc}).
 Since turbulence is essentially hydrodynamic at large scales, this is unjustified.
@@
 Henceforth, we can consider the outer scale of the fast modes to be $l_{\rm A}$.
-If some fraction $f_{\rm c}$ of the turbulent energy density at this scale is in compressible modes, then the energy density at the outer scale is velocity $\sim f_{\rm c} \rho \varv_{\rm A}^{2}$.}
+If some fraction $f_{\rm c}$ of the turbulent energy density at this scale is in compressible modes, then the energy density at the outer scale is $\sim f_{\rm c} \rho \varv_{\rm A}^{2}$.}
 %and follows the universal Kolmogorov scaling. The
@@
 \end{equation}
-where $\zeta$ is an efficiency factor for the the effectiveness of plasma instabilities (e.g., due to spatial or temporal intermittency), and $X_{\rm CR}=\eps_{\rm CR}/\eps_{\rm th}$ is the relative energy density of CRs.
+where $\zeta$ is an efficiency factor for the effectiveness of plasma instabilities (e.g., due to spatial or temporal intermittency), and $X_{\rm CR}=\eps_{\rm CR}/\eps_{\rm th}$ is the relative energy density of CRs.
 If we set $k_L \rightarrow k_{\rm A}$, $\varv_{c}^{2} \rightarrow \varv_{\rm A}^{2}$, as before, then:
@@
 mindful that Kraichnan turbulence is only applicable below the Alfven scale
-$l_{\rm A}$ (where turbulent velocities $v < v_{\rm A}$), then remarkably the
+$l_{\rm A}$ (where turbulent velocities $\varv < \varv_{\rm A}$), then remarkably the
 ratio $\tau_{\rm cl}/\tau_{\rm D}$ is independent of properties of the

### 2016-08-31 paper.tex
unified comments to \C{}

@@
 \newcommand\AP[1]{{\color{green} #1}}
+\newcommand\C[1]{{\bf #1}}
 
@@
   Fokker-Planck equation of the cosmic ray (CR) electron and proton
-  distributions in \AP{the post-processing of} cosmological simulations of
+  distributions in \C{the post-processing of} cosmological simulations of
   cluster formation, and confront them with radio surface brightness and
@@
   observations could then potentially constrain the unknown CR seed
-  population. \po{Given that MHD turbulence only begins at the Alfv{\'e}n scale, in
+  population. \C{Given that MHD turbulence only begins at the Alfv{\'e}n scale, in
     order to have sufficient acceleration, the turbulent cascade has to
@@
 Here $f_{\rmn{e}}$ is the one-dimensional distribution in position $x$
-(suppressed for clarity), momentum \cp{$p=P/(m_{\rmn{e}} c)$} and time $t$
+(suppressed for clarity), momentum $p=P/(m_{\rmn{e}} c)$ and time $t$
 (which is normalised such that the number density is given by
@@
   \left|\frac{d p}{d t}\right|_{\rm rad~} &=& \frac{4}{3}\frac{\sigma_\rmn{T}}{m_{\rmn{e}}c}\,
-  \frac{p^2}{\beta_{\rmn{e}}}\,\left[1+\left(\frac{B}{B_\rmn{CMB}}\right)^2\right]\,\cp{\eps_{\rmn{CMB}}}\,.
+  \frac{p^2}{\beta_{\rmn{e}}}\,\left[1+\left(\frac{B}{B_\rmn{CMB}}\right)^2\right]\,\eps_{\rmn{CMB}}\,.
 \end{eqnarray}
@@
 choose this simulation snapshot to analyse.
-\AP{Note that in recent simulations by \citet{miniati15}, the turbulent reacceleration is strongest around core passage.
+\C{Note that in recent simulations by \citet{miniati15}, the turbulent reacceleration is strongest around core passage.
 However, we are not very sensitive to the adopted decay time, since the thermal and CR quantities are very similar a few 100 Myrs before and after $z = 0$, where we have chosen to evaluate the simulations.}
@@
 and $Q_{\rmn{p}}(p,t)$ denotes the injection rate of shock accelerated
-CRps as a function of momentum \cp{$p=P/(m_{\rmn{p}} c)$} and time $t$ (see
+CRps as a function of momentum $p=P/(m_{\rmn{p}} c)$ and time $t$ (see
 section~\ref{sec:cosmo_sim}). The timescale of
@@
 is assumed to be constant), $\varv_{\rm ph}\approx c_{\rm s}$ is the phase speed
-of waves. \cp{Since the Kraichnan spectrum is critical in what follows, it is
+of waves. \C{Since the Kraichnan spectrum is critical in what follows, it is
   worthwhile taking a moment to recount the origin of the spectral slope $s$ and
@@
 Thus, except in the case where motions are transsonic and weak shocks become important, motions are fundamentally hydrodynamic and turbulence follows a Kolmogorov ($s=5/3$) spectrum.
-However, while the turbulent energy density $\eps_{\rm turb} \propto l^{2/3}$ decreases at small scales, the magnetic energy density \po{(which is dominated by the large scale mean field)} is scale-independent.
+However, while the turbulent energy density $\eps_{\rm turb} \propto l^{2/3}$ decreases at small scales, the magnetic energy density \C{(which is dominated by the large scale mean field)} is scale-independent.
 Thus, at some scale $l_{\rm A} \sim l_L {\mathcal M}_{\rm A}^{-3}$, where $\eps_{\rm turb} \sim \eps_{B}$, the magnetic field becomes dynamically important, and turbulence transitions to the MHD regime.
@@
 where $A \approx 11 000$.
-\cp{If there is an unimpeded cascade from the injection to the cutoff scale, $k_{\rmn{outer}}=k_L$ and $\varv_{\rmn{outer}}=\varv_{\rmn{c}}$.
-However, in our case the hydrodynamic (Kolmogorov) cascade transitions to the MHD cascade at the Alfv{\'e}n scale so that $k_{\rmn{outer}}=k_{\rmn{A}}$ and $\varv_{\rmn{outer}}=\varv_{\rmn{A}}$ and hence, we get\footnote{\cp{Note that this differs from previous work, which assumes Kraichnan turbulence from the injection scale onward and effectively adopts wave number and compressible velocity at the outer scale $L$ for this estimate of $k_{\rm cut}$.}}
+\C{If there is an unimpeded cascade from the injection to the cutoff scale, $k_{\rmn{outer}}=k_L$ and $\varv_{\rmn{outer}}=\varv_{\rmn{c}}$.
+However, in our case the hydrodynamic (Kolmogorov) cascade transitions to the MHD cascade at the Alfv{\'e}n scale so that $k_{\rmn{outer}}=k_{\rmn{A}}$ and $\varv_{\rmn{outer}}=\varv_{\rmn{A}}$ and hence, we get\footnote{\C{Note that this differs from previous work, which assumes Kraichnan turbulence from the injection scale onward and effectively adopts wave number and compressible velocity at the outer scale $L$ for this estimate of $k_{\rm cut}$.}}
 \begin{equation}
@@
 $\sim 20-40$ per cent of the total turbulent energy, and shows more rapid temporal
-variations compared to the \po{incompressible} component
+variations compared to the \C{incompressible} component
 \citep{2013ApJ...771..131B,miniati15}. Note the compressible component in
@@
 
-The important effects are best summarised in terms of the acceleration \cp{rate
+The important effects are best summarised in terms of the acceleration \C{rate
   which is governed by advection in momentum space:
@@
 We assume an injection scale $k_L=2\upi/\lambda_L$, where $\lambda_L = 100$ kpc, which were assumptions adopted in previous work \citep{2006MNRAS.366.1437S,brunetti07, brunetti11}.
-This length scale corresponds to an eddy turnover time on the outer scale of \cp{$2\upi\lambda_L\varv_L^{-1} \sim 1.2$~Gyr} if $\varv_L \sim 500 {\rm km \, s^{-1}}$, as is characteristic of a merger.
-Note that hydrodynamical simulations of clusters have sometimes found larger $\lambda_L$, in some cases comparable to the size of the cluster \AP{\citep[e.g.
+This length scale corresponds to an eddy turnover time on the outer scale of \C{$2\upi\lambda_L\varv_L^{-1} \sim 1.2$~Gyr} if $\varv_L \sim 500 {\rm km \, s^{-1}}$, as is characteristic of a merger.
+Note that hydrodynamical simulations of clusters have sometimes found larger $\lambda_L$, in some cases comparable to the size of the cluster \C{\citep[e.g.
 $\lambda_L \sim 1 {\rm Mpc}$ in ][]{vazza11,miniati15}}.
@@
 $\gamma_\rmn{ad} = 5/3$ and the Mach number of the shock
-$\mathcal{M}$ \AP{\citep[see also ][]{1998ApJ...502..518Q,miniati01,pfrommer06}}. It is given by the ratio of the upstream velocity
+$\mathcal{M}$ \C{\citep[see also ][]{1998ApJ...502..518Q,miniati01,pfrommer06}}. It is given by the ratio of the upstream velocity
 ($\varv_2$) and the sound speed ($c_{\rm s}$). The CR number density and CR
@@
 account, i.e. they neglect CR streaming or a flatter turbulent
-profile, produce radio profiles that are too steep. \AP{Indeed, even using
+profile, produce radio profiles that are too steep. \C{Indeed, even using
 the assumptions of previous work, where complete freedom in the seed
@@
 
-\po{In this section, we explore the physical origin of the high sensitivity of radio emission to turbulence levels (e.g., top right panel of Fig.
+\C{In this section, we explore the physical origin of the high sensitivity of radio emission to turbulence levels (e.g., top right panel of Fig.
 \ref{fig:param_comp}), which thus requires strong fine-tuning to explain observed radio profiles.
@@
 with the analytic solution given by
-\cp{
+\C{
 \begin{equation}
@@
 An obvious candidate for $\tau_{\rm decay}$ is: 
-\po{\begin{equation}
+\C{\begin{equation}
 \tau_{\rm edd} = \frac{L}{\varv_{\rm L}}
@@
 
-\po{In the hydrodynamic regime, a standard Hodge-Helmholtz decomposition usually shows that the compressive component of the velocity field is Burgers-like ($W(k) \propto k^{-2}$), while the solenoidal component is Kolomogorov-like ($W(k) \propto k^{-5/3}$), see e.g., \citet{federrath13}.
+\C{In the hydrodynamic regime, a standard Hodge-Helmholtz decomposition usually shows that the compressive component of the velocity field is Burgers-like ($W(k) \propto k^{-2}$), while the solenoidal component is Kolomogorov-like ($W(k) \propto k^{-5/3}$), see e.g., \citet{federrath13}.
 The Burgers-like component does not reflect a genuine cascade, but rather the appearance of shocks which directly transfer power from large to small scales.
@@
 
-\po{We thus assume that some fraction of the Kolmogorov-like hydrodynamic turbulence which cascades down to the Alfven scale ends up as compressive fast modes with a Kraichnan spectrum, as seen in simulations \citep{cho03}.
+\C{We thus assume that some fraction of the Kolmogorov-like hydrodynamic turbulence which cascades down to the Alfven scale ends up as compressive fast modes with a Kraichnan spectrum, as seen in simulations \citep{cho03}.
 Henceforth, we can consider the outer scale of the fast modes to be $l_{\rm A}$.
 If some fraction $f_{\rm c}$ of the turbulent energy density at this scale is in compressible modes, then the energy density at the outer scale is $\sim f_{\rm c} \rho \varv_{\rm A}^{2}$.}
-%and follows the universal Kolmogorov scaling. The
-%momentum diffusion coefficient can thus be split up into two components:
-%\begin{equation}
-%D_{pp} = D_{pp}^{\rm HD}[l_{\rm A} < l < L] + D_{pp}^{\rm MHD}[l_{\rm cut} < l < l_{\rm A}]
-%\end{equation}
-%From equations (\ref{eqn:diffusion}) and (\ref{eqn:k_W}), and assuming Kolmogorov turbulence from $l_{\rm A} < l < L$ and Kraichnan turbulence from $l_{\rm cut} < l < l_{\rm A}$, we get: 
-%\begin{equation}
-%  \label{eqn:Dratio}
-%  \frac{D_{pp}^{\rm HD}}{D_{pp}^{\rm MHD}}
-%  = \frac{\cp{2}k_L^{2/3}k_{\rm A}^{1/3} \varv_{\rm c}^{2}}{k_{\rm A}^{1/2}k_{\rm cut}^{1/2} \varv_{\rm A}^{2}}
-%  = \cp{2} A^{-1/2} \beta = \cp{1.0}\, \left( \frac{\beta}{50} \right) 
-%\end{equation}
-%where we have used $k_{\rm A} = k_L \mathcal{M}_{\rm A}^{3}$ (from Kolmogorov
-%scalings), and $\mathcal{M}_{\rm A} = \varv_{\rm c}/\varv_{\rm A}$ is the
-%Alfv{\'e}n Mach number of the turbulence, $\beta \approx c_{\rm
-%  s}^{2}/\varv_{\rm A}^{2}$, and the cutoff scale $k_{\rm cut}$ (equation
-%\ref{eqn:k_c}).  Thus, the contribution of the two regimes are
-%comparable\footnote{\cp{The estimate of equation~(\ref{eqn:Dratio}) assumes that
-%%    in both cascades, kinetic and potential energy are in equipartition which is
-%    likely an overestimate for the hydrodynamical cascade and hence, the
-%   hydrodynamic contribution to the momentum diffusion would be small in
-%    comparison to the MHD contribution. }} (as we shall see later, this is not
-%true if one incorrectly assumes Kraichnan scalings apply from the outer scale
-%$L$; this boosts the contribution of the scales where $l_{\rm A} < l < L$ by a
-%factor $\mathcal{M}_{\rm A}^{1/2}$).
 The turbulent reacceleration time is: 
-%\begin{equation}
-%\tau_{\rm D} = \frac{p^{2}}{4 D_{pp}} = C_{\rm D} A^{1/2} c k_{\rm A} \frac{\varv_{\rm A}^{2}}{c_{\rm S}^{2}}
-%\label{eqn:tau_D} 
-%\end{equation}
-\po{
-  \begin{equation}
-\tau_{\rm D} = \frac{p^{2}}{4 D_{pp}} = \po{\frac{C_{\rm D}}{A^{1/2}}\, \frac{c}{k_{\rm A}}\, \frac{\beta}{f_{\rm c} \varv_{\rm A}^{2}}}
+\C{
+  \begin{equation}
+\tau_{\rm D} = \frac{p^{2}}{4 D_{pp}} = \frac{C_{\rm D}}{A^{1/2}}\, \frac{c}{k_{\rm A}}\, \frac{\beta}{f_{\rm c} \varv_{\rm A}^{2}}
 \label{eqn:tau_D} 
@@
 }
-where $C_{\rm D} = 2/(5 \upi)$, $A\approx 11000$, and we have used equations, \po{(\ref{eqn:diffusion}), (\ref{eqn:k_W}), (\ref{eqn:k_c}), assuming $s=3/2$}.
-The turbulent decay time is given by the cascade time of fast modes \cp{at the Alfv\'en scale $k=k_{\rmn{A}}$} (\citealt{2004ApJ...614..757Y}; see equation \ref{eqn:tau_l}):
-\begin{equation}
-  \tau_{\rm decay} = \cp{\frac{\varv_{\rm ph}}{\varv_k^{2} k} = }
-\po{\frac{c_{\rm s}}{f_{\rm c} \varv_{\rm A}^{2} k_{\rm A}^{}}\,.}
+where $C_{\rm D} = 2/(5 \upi)$, $A\approx 11000$, and we have used equations, \C{(\ref{eqn:diffusion}), (\ref{eqn:k_W}), (\ref{eqn:k_c}), assuming $s=3/2$}.
+The turbulent decay time is given by the cascade time of fast modes \C{at the Alfv\'en scale $k=k_{\rmn{A}}$} (\citealt{2004ApJ...614..757Y}; see equation \ref{eqn:tau_l}):
+\begin{equation}
+  \tau_{\rm decay} = \frac{\varv_{\rm ph}}{\varv_k^{2} k} = 
+\frac{c_{\rm s}}{f_{\rm c} \varv_{\rm A}^{2} k_{\rm A}^{}}\,.
 \label{eqn:tau_decay} 
@@
 \begin{equation}
-\po{\tau_{\rm decay} =\frac{L}{\varv_{\rm L}} \frac{c_{\rm s}^{2}}{f_{\rm c} \varv_{\rm L}^{2}}  \frac{\varv_{\rm A}}{c_{\rm s}} \approx  1.0 \, \tau_{\rm edd} \left(\frac{\tilde{X}_{\rm tu}}{0.2}\right)^{-1}  \left(\frac{\beta}{50} \right)^{-1/2}}
+\tau_{\rm decay} =\frac{L}{\varv_{\rm L}} \frac{c_{\rm s}^{2}}{f_{\rm c} \varv_{\rm L}^{2}}  \frac{\varv_{\rm A}}{c_{\rm s}} \approx  1.0 \, \tau_{\rm edd} \left(\frac{\tilde{X}_{\rm tu}}{0.2}\right)^{-1}  \left(\frac{\beta}{50} \right)^{-1/2}
 \end{equation}
 where we have used $\tilde{X}_{\rm tu} \approx f_{\rm c} (\varv_{\rm L}/c_{\rm s})^{2}$ and $c_{\rm s}/\varv_{\rm A} = \beta^{1/2}$.
-\po{The decay time at the Alfven scale is comparable (and could be larger, if $f_{\rm c}$ is smaller than we have assumed) to the eddy turnover time at the outer scale.
+\C{The decay time at the Alfven scale is comparable (and could be larger, if $f_{\rm c}$ is smaller than we have assumed) to the eddy turnover time at the outer scale.
 Thus, it is appropriate to consider the latter as the decay time for the fast modes, rather than the cascade time at the driving scale.
@@
   \frac{\tau_{\rm cl}}{\tau_{\rm D}} \approx \frac{\tau_{\rm decay}}{\tau_{\rm D}}
-  \cp{= \frac{A^{1/2}}{C_{\rmn{D}}}\,\frac{c_{\rm s}}{c}\,\beta^{-1}}
+  = \frac{A^{1/2}}{C_{\rmn{D}}}\,\frac{c_{\rm s}}{c}\,\beta^{-1}
   = 0.1 \left( \frac{c_{\rm s}}{1500 \, {\rm km \, s^{-1}}} \right) \left( \frac{\beta}{50} \right)^{-1}\,. 
@@
 Remarkably, this expression is independent of properties of the turbulence such as $\varv_{\rm c}$, $L$, or $l_{\rm A}$, and depends only on properties of the plasma ($c_{\rm s},\beta$).
-Ultimately, this arises because the timescale on which a fast mode wave transfers energy due to wave particle interactions in second order Fermi acceleration, $\tau_{\rm p} \sim [\cp{4\,} k_{\rm p} c (\varv_{\rm c}/c)^{2} ]^{-1}$, is closely related to the timescale on which it cascades due to wave-wave interactions, $\tau_{\rm w} \sim c_{\rm s}/(k_{\rm w} \varv_{\rm c}^{2})$.
-This implies $\tau_{\rm w}/\tau_{\rm p} \sim \cp{4\,} (c_{\rm s}/c)(l_{\rm w}/l_{\rm p})$, where $l_{\rm w} \sim l_{\rm A}$ is the outer scale on which the fast mode cascade begins, and $l_{\rm p} \sim (l_{\rm A} l_{\rm cut})^{1/2}$ is the characteristic wavelength for wave-particle interactions.
+Ultimately, this arises because the timescale on which a fast mode wave transfers energy due to wave particle interactions in second order Fermi acceleration, $\tau_{\rm p} \sim [4\, k_{\rm p} c (\varv_{\rm c}/c)^{2} ]^{-1}$, is closely related to the timescale on which it cascades due to wave-wave interactions, $\tau_{\rm w} \sim c_{\rm s}/(k_{\rm w} \varv_{\rm c}^{2})$.
+This implies $\tau_{\rm w}/\tau_{\rm p} \sim 4\, (c_{\rm s}/c)(l_{\rm w}/l_{\rm p})$, where $l_{\rm w} \sim l_{\rm A}$ is the outer scale on which the fast mode cascade begins, and $l_{\rm p} \sim (l_{\rm A} l_{\rm cut})^{1/2}$ is the characteristic wavelength for wave-particle interactions.
 For transit time damping and an outer scale of $l_{\rm A}$, we have $l_{\rm cut} \sim (m_{\rm e}/m_{\rm p}) l_{\rm A} (c_{\rm s}/\varv_{\rm A})^{4}$.
-We thus have $\tau_{\rm w}/\tau_{\rm p} \sim \cp{4\,}(c_{\rm s}/c)(l_{\rm A}/l_{\rm cut})^{1/2} \sim \cp{4\,}(c_{\rm s}/c) (m_{\rm p}/m_{\rm e})^{1/2} \beta^{-1}$.
+We thus have $\tau_{\rm w}/\tau_{\rm p} \sim 4\,(c_{\rm s}/c)(l_{\rm A}/l_{\rm cut})^{1/2} \sim 4\,(c_{\rm s}/c) (m_{\rm p}/m_{\rm e})^{1/2} \beta^{-1}$.
 More careful consideration of dimensionless factors boosts this estimate by an order of magnitude to give equation (\ref{eqn:ratios_TTD}).
@@
 It is also worth exploring the effect of Burgers' turbulence (weak shocks).
-\cp{Burgers' turbulence is distinct from other forms of turbulence in that it violates locality in $k$-space--i.e., power does not gradually cascade, but instead can directly jump from large to small scales via a network of weak shocks.
+\C{Burgers' turbulence is distinct from other forms of turbulence in that it violates locality in $k$-space--i.e., power does not gradually cascade, but instead can directly jump from large to small scales via a network of weak shocks.
 This implies a short dissipation time and we have in this case, $\tau_{\rm cl} \sim \tau_{\rm drive}$, the driving time, rather than the turbulent dissipation time.

### 2016-09-05 paper.tex
Add files via upload

@@
   injected CRs ($\alpha_\rmn{CR,spat}$). We adopt the following
-  fiducial values for our model, $X_\rmn{tu}=0.2$,
+  fiducial values for our model (solid lines), $X_\rmn{tu}=0.2$,
   $\alpha_\rmn{tu}=0.8$, and $\alpha_\rmn{CR,spat}=1.0$ and vary each
@@
 
-It is interesting to reconsider surface brightness and spectral profiles if indeed $\tau_{\rm D} \sim \tau_{\rm cl}$, for the reasons mentioned above (e.g., equation \ref{eqn:ratios_CR_damp}).
+\sout{It is interesting to reconsider surface brightness and spectral profiles if indeed $\tau_{\rm D} \sim \tau_{\rm cl}$, for the reasons mentioned above (e.g., equation \ref{eqn:ratios_CR_damp}).
 We show the results of adopting such an ansatz in Figure~\ref{fig:param_comp_tcl_tD}, where, similar to Figure~\ref{fig:param_comp}, we vary $X_{\rm tu}, \alpha_{\rm tu}, \alpha_{\rm CR, spat}$ about fiducial values, but this time we do not adopt a fixed $\tau_{\rm cl}$ but set $\tau_{\rm cl}=\tau_{\rm D}$.
@@
 In this case, one is much less sensitive to the properties of the turbulence, and more sensitive to the details of the CR seed population.
-This gives hope to the possibility that one could effectively marginalise over the very uncertain properties of turbulence at larger scales in merging clusters (which are unlikely to be more precisely constrained observationally in the near future) to learn something about the underlying CR population.
+This gives hope to the possibility that one could effectively marginalise over the very uncertain properties of turbulence at larger scales in merging clusters (which are unlikely to be more precisely constrained observationally in the near future) to learn something about the underlying CR population.}
+\C{It is interesting to reconsider surface brightness and spectral profiles if indeed $\tau_{\rm D} \sim \tau_{\rm cl}$, for the reasons mentioned above (e.g., equation~\ref{eqn:ratios_CR_damp}).
+We show the results of adopting such an ansatz in Figure~\ref{fig:param_comp_tcl_tD}, where, similar to Figure~\ref{fig:param_comp}, we vary $X_{\rm tu}, \alpha_{\rm tu}, \alpha_{\rm CR, spat}$ about fiducial values \footnote{When $\tau_{\rm D} \sim \tau_{\rm cl}$ is adopted, the radial behavior of $\tau_{\rm cl}$ is also changed.
+Since $\tau_{\rm D}$ decreases with radius (see e.g.
+Figure~\ref{fig:tauD}), $\tau_{\rm cl}$ has to decrease with the same amount which results in a steeper radio profile.
+To compensate for this in Figure~\ref{fig:param_comp_tcl_tD}, we change $\alpha_{\rm CR, spat}\rightarrow0.5$ and decrease the relative CR-to-thermal energy within the virial radius with a factor five to 0.06 per cent.} , but this time we do not adopt a fixed $\tau_{\rm cl}$ but set $\tau_{\rm D} = 1/4 \,\tau_{\rm cl}$.
+They are remarkably revealing.
+In this case, one is much less sensitive to the properties of the turbulence, and more sensitive to the details of the CR seed population.
+This gives hope to the possibility that one could effectively marginalise over the very uncertain properties of turbulence at larger scales in merging clusters (which are unlikely to be more precisely constrained observationally in the near future) to learn something about the underlying CR population.}
 
@@
    \begin{center}\Large{radio profiles}\\
-     \includegraphics[width=\columnwidth]{tcltD.prof.comp.KrTTDth.Xtu.eps}
+     \includegraphics[width=\columnwidth]{figure7_prof.eps}
    \end{center}
@@
    \begin{center}\Large{radio spectra}\\
-     \includegraphics[width=\columnwidth]{tcltD.spec.comp.KrTTDth.Xtu.eps}
+     \includegraphics[width=\columnwidth]{figure7_spec.eps}
    \end{center}
 \end{minipage}
-\\
-\begin{minipage}{1\columnwidth}
-  \begin{center}%\Large{\Mflatturb:}\\ 
-    \includegraphics[width=\columnwidth]{tcltD.prof.comp.KrTTDth.aI0.eps}
-  \end{center}
-\end{minipage}
-\begin{minipage}{1\columnwidth}
-   \begin{center}%\Large{\it Brunetti et al. (2012)}:\\
-     \includegraphics[width=\columnwidth]{tcltD.spec.comp.KrTTDth.aI0.eps}
-   \end{center}
-\end{minipage}
-\\
-\begin{minipage}{1\columnwidth}
-  \begin{center}%\Large{\Mflatturb:}\\ 
-    \includegraphics[width=\columnwidth]{tcltD.prof.comp.KrTTDth.aCR.eps}
-  \end{center}
-\end{minipage}
-\begin{minipage}{1\columnwidth}
-   \begin{center}%\Large{\it Brunetti et al. (2012)}:\\
-     \includegraphics[width=\columnwidth]{tcltD.spec.comp.KrTTDth.aCR.eps}
-   \end{center}
-\end{minipage}
-\caption{Sensitivity of radio emission in Coma cluster to critical
+
+\caption{\C{Sensitivity of radio emission in Coma cluster to critical
     parameters. For details see caption in
-  Figure~\ref{fig:param_comp}. For simplicity, we assume that the
-  duration of reacceleration $\tau_{cl}=\tau_{\rm D}$, where $\tau_{\rm
-    D}$ is the acceleration time of particles due to turbulence. In
-  this scenario the radio profiles are mainly determined from the CRs,
-  while the turbulence has a minor impact. Interestingly, flat CR
-  profiles similar to those produced through CR streaming are needed in
-  order to reproduce the radio profiles.}
+    Figure~\ref{fig:param_comp}. For the fiducial model we adopt a
+    slightly flatter distribution of CRs ($\alpha_{\rm CR, spat}=0.5$)
+    and a factor five lower CR-to-thermal energy than in previous
+    figure. We assume that the duration of reacceleration
+    $\tau_{cl}=2.5\,\tau_{\rm D}$, where $\tau_{\rm D}$ is the
+    acceleration time of particles due to turbulence. In this scenario
+    the radio profiles are mainly determined from the CRs, while the
+    turbulence has a minor impact. In the bottom two panels we vary
+    $\tau_{cl}=\tau_{\rm D}$, which mainly changes the normalization
+    of the CR distribution and not the shape or radial
+    dependence. Interestingly, flat CR profiles similar to those
+    produced through CR streaming are needed in order to reproduce the
+    radio profiles.}}
   \label{fig:param_comp_tcl_tD}

### 2016-09-06 paper.tex
edits to text and caption of Fig 7

@@
   worthwhile taking a moment to recount the origin of the spectral slope $s$ and
-  the cascade rate. In the magnetically dominated regime, two counterpropagating
+  the cascade rate. In the magnetically dominated regime, two counter-propagating
   wave packets of scale $l$ interact on a wave crossing time $\tau_{\rm
@@
 \end{minipage}
-\caption{Sensitivity of the radio emission in the Coma cluster to critical
-  parameters. The left-hand panels show the radio surface brightness
-  profiles. We compare profiles at 352~MHz \citep[blue
+\caption{Sensitivity of the radio emission in the Coma cluster to
+  critical parameters. The left-hand panels show the radio surface
+  brightness profiles. We compare profiles at 352~MHz \citep[blue
     crosses,][]{brown11} to predicted emission from Fermi-II
-  reaccelerated CR electrons populations (black lines). The right-hand
-  panels show radio synchrotron spectra. The green crosses are
-  compiled from observations \citep{2010PhDT.......259P}, while the
-  black lines show predicted spectra. The upper panels show the sensitivity to the level of
-  turbulence ($X_\rmn{tu}$), the middle panels show the impact of
-  different turbulent profiles ($\alpha_\rmn{tu}$), and the lower
-  panels show the dependence on spatial distributions of initial and
-  injected CRs ($\alpha_\rmn{CR,spat}$). We adopt the following
+  reaccelerated CR electrons (black lines). The right-hand panels show
+  radio synchrotron spectra. The green crosses are compiled from
+  observations \citep{2010PhDT.......259P}, while the black lines show
+  predicted spectra. The upper panels show the sensitivity to the
+  level of turbulence ($X_\rmn{tu}$), the middle panels show the
+  impact of different turbulent profiles ($\alpha_\rmn{tu}$), and the
+  lower panels show the dependence on spatial distributions of initial
+  and injected CRs ($\alpha_\rmn{CR,spat}$). We adopt the following
   fiducial values for our model (solid lines), $X_\rmn{tu}=0.2$,
@@
   parameter separately in each row of panels. We find that the radio
-  emission is most sensitive to the level of turbulence. The abundance of CR seeds, and the spatial distribution of CRs and turbulence play second-order effects.}
+  emission is most sensitive to the level of turbulence. The abundance
+  of CR seeds, and the spatial distribution of CRs and turbulence are
+  second-order effects.}
   \label{fig:param_comp}
@@
   mergers, when they are spatially confined by scattering.} In this case,
-$\dot{p}= p/\tau_{\rm D}$, and after a time $\tau_{\rm cl}$, we have $p
-\rightarrow p \, {\rm exp}(\tau_{\rm cl}/\tau_{\rm D})$ (where we have used the
-fact that $\tau_{\rm D}$ is momentum independent). For an initial power law
-distribution function $f(p) = C p^{-\alpha_{\rmn{inj}}}$, this momentum increase can be
-rewritten as a change of normalisation, $f(p) = \tilde{C} p^{-\alpha_{\rmn{inj}}}$, where
-$\tilde{C} = {\rm exp}( \alpha_{\rmn{inj}} \tau_{\rm cl}/\tau_{\rm D})$. A slightly more
-careful derivation by direct solution of the Fokker-Planck equation yields:
+$\dot{p}= p/\tau_{\rm D}$, and after a time $\tau_{\rm cl}$, we have
+\begin{equation}
+  \label{eq:pexp}
+p\rightarrow p \, {\rm exp}(\tau_{\rm cl}/\tau_{\rm D})
+\end{equation}
+(where we have used the fact that $\tau_{\rm D}$ is momentum independent). For
+an initial power law distribution function $f(p) = C p^{-\alpha_{\rmn{inj}}}$,
+this momentum increase can be rewritten as a change of normalisation, $f(p) =
+\tilde{C} p^{-\alpha_{\rmn{inj}}}$, where $\tilde{C} = {\rm exp}(
+\alpha_{\rmn{inj}} \tau_{\rm cl}/\tau_{\rm D})$. A slightly more careful
+derivation by direct solution of the Fokker-Planck equation yields:
 \begin{equation}
@@
 
-\C{In the hydrodynamic regime, a standard Hodge-Helmholtz decomposition usually shows that the compressive component of the velocity field is Burgers-like ($W(k) \propto k^{-2}$), while the solenoidal component is Kolomogorov-like ($W(k) \propto k^{-5/3}$), see e.g., \citet{federrath13}.
+\C{In the hydrodynamic regime, a standard Hodge-Helmholtz decomposition usually shows that the compressive component of the velocity field is Burgers-like ($W(k) \propto k^{-2}$), while the solenoidal component is Kolmogorov-like ($W(k) \propto k^{-5/3}$), see e.g., \citet{federrath13}.
 The Burgers-like component does not reflect a genuine cascade, but rather the appearance of shocks which directly transfer power from large to small scales.
@@
 Thus, it is appropriate to consider the latter as the decay time for the fast modes, rather than the cascade time at the driving scale.
-The reason for these comparable timescales despite the disparate lengthscales is that large scale hydrodynamic modes cascade on a single eddy turnover time, whereas small scale sub-Alfvenic MHD modes are in the weak turbulence limit, and require multiple wave-wave interactions for a mode to cascade.
+The reason for these comparable timescales despite the disparate length scales is that large scale hydrodynamic modes cascade on a single eddy turnover time, whereas small scale sub-Alfvenic MHD modes are in the weak turbulence limit, and require multiple wave-wave interactions for a mode to cascade.
 }
@@
 
-\sout{It is interesting to reconsider surface brightness and spectral profiles if indeed $\tau_{\rm D} \sim \tau_{\rm cl}$, for the reasons mentioned above (e.g., equation \ref{eqn:ratios_CR_damp}).
-We show the results of adopting such an ansatz in Figure~\ref{fig:param_comp_tcl_tD}, where, similar to Figure~\ref{fig:param_comp}, we vary $X_{\rm tu}, \alpha_{\rm tu}, \alpha_{\rm CR, spat}$ about fiducial values, but this time we do not adopt a fixed $\tau_{\rm cl}$ but set $\tau_{\rm cl}=\tau_{\rm D}$.
-They are remarkably revealing.
-In this case, one is much less sensitive to the properties of the turbulence, and more sensitive to the details of the CR seed population.
-This gives hope to the possibility that one could effectively marginalise over the very uncertain properties of turbulence at larger scales in merging clusters (which are unlikely to be more precisely constrained observationally in the near future) to learn something about the underlying CR population.}
-\C{It is interesting to reconsider surface brightness and spectral profiles if indeed $\tau_{\rm D} \sim \tau_{\rm cl}$, for the reasons mentioned above (e.g., equation~\ref{eqn:ratios_CR_damp}).
-We show the results of adopting such an ansatz in Figure~\ref{fig:param_comp_tcl_tD}, where, similar to Figure~\ref{fig:param_comp}, we vary $X_{\rm tu}, \alpha_{\rm tu}, \alpha_{\rm CR, spat}$ about fiducial values \footnote{When $\tau_{\rm D} \sim \tau_{\rm cl}$ is adopted, the radial behavior of $\tau_{\rm cl}$ is also changed.
-Since $\tau_{\rm D}$ decreases with radius (see e.g.
-Figure~\ref{fig:tauD}), $\tau_{\rm cl}$ has to decrease with the same amount which results in a steeper radio profile.
-To compensate for this in Figure~\ref{fig:param_comp_tcl_tD}, we change $\alpha_{\rm CR, spat}\rightarrow0.5$ and decrease the relative CR-to-thermal energy within the virial radius with a factor five to 0.06 per cent.} , but this time we do not adopt a fixed $\tau_{\rm cl}$ but set $\tau_{\rm D} = 1/4 \,\tau_{\rm cl}$.
-They are remarkably revealing.
-In this case, one is much less sensitive to the properties of the turbulence, and more sensitive to the details of the CR seed population.
-This gives hope to the possibility that one could effectively marginalise over the very uncertain properties of turbulence at larger scales in merging clusters (which are unlikely to be more precisely constrained observationally in the near future) to learn something about the underlying CR population.}
-
-For instance, in the top panels of Figure~\ref{fig:param_comp_tcl_tD}, we see that once turbulence exceeds a threshold value $X_{\rm tu} \sim 0.1$, then its overall exact energy density does not matter -- profiles simply converge to an asymptotic form as $X_{\rm tu}$ is increased.
-This is in contrast to the exponential sensitivity, flattening in surface brightness, and increasing spectral curvature as $X_{\rm tu}$ is increased that we saw previously.
-A threshold value of $X_{\rm tu}$ is necessary for turbulent reacceleration to overcome cooling.
-Once that condition is satisfied, the condition $\tau_{\rm cl} \sim \tau_{\rm D}$ implies a fixed amount of amplification: stronger turbulence implies faster acceleration, but also dissipates more quickly.
-This leads to the asymptotic behaviour seen.
-From the middle panels, we see another striking result: in contrast to Figure~\ref{fig:param_comp}, results are also completely insensitive to the turbulent profile.
-Given the large uncertainties in the latter, this is a welcome property.
-It arises because for our fiducial value ($X_{\rm tu} = 0.2$), variations in the turbulent profile still lead to local energy densities which are above the threshold value required to overcome cooling, and turbulent amplification approaches its asymptotic value.
-Finally, in the bottom panels, we see that we {\it are} sensitive to the spatial profile of CRs; it affects both the radio surface brightness profile (a flatter CR distribution implies flatter surface brightness profiles) and luminosity (once again, luminosity is larger for more centrally concentrated CRs, since more secondaries are produced).
-This arises because once turbulent reacceleration overcomes cooling, the condition $\tau_{\rm cl} \sim \tau_{\rm D}$ provides for a fixed amount of amplification in each radial shell.
-The radio luminosity in each shell then depends linearly on initial conditions, i.e., the profile of CR seeds.
-Interestingly, the best-fitting profile for Coma comes from a flat CR distribution -- i.e., one that is the outcome of efficient CR streaming.
-Matching the overall amplitude simply involves a rescaling of $\tau_{\rm cl}/\tau_{\rm D}$ (equation \ref{eqn:ratios_CR_damp}) or the CR content.
+\sout{It is interesting to reconsider surface brightness and spectral profiles
+  if indeed $\tau_{\rm D} \sim \tau_{\rm cl}$, for the reasons mentioned above
+  (e.g., equation \ref{eqn:ratios_CR_damp}). We show the results of adopting
+  such an ansatz in Figure~\ref{fig:param_comp_tcl_tD}, where, similar to
+  Figure~\ref{fig:param_comp}, we vary $X_{\rm tu}, \alpha_{\rm tu}, \alpha_{\rm
+    CR, spat}$ about fiducial values, but this time we do not adopt a fixed
+  $\tau_{\rm cl}$ but set $\tau_{\rm cl}=\tau_{\rm D}$.  They are remarkably
+  revealing. In this case, one is much less sensitive to the properties of the
+  turbulence, and more sensitive to the details of the CR seed population. This
+  gives hope to the possibility that one could effectively marginalise over the
+  very uncertain properties of turbulence at larger scales in merging clusters
+  (which are unlikely to be more precisely constrained observationally in the
+  near future) to learn something about the underlying CR population.}  \C{It is
+  interesting to reconsider surface brightness and spectral profiles if indeed
+  $\tau_{\rm D} \sim \tau_{\rm cl}$ for the reasons mentioned above (e.g.,
+  equation~\ref{eqn:ratios_CR_damp}). We show the results of adopting such an
+  ansatz in Figure~\ref{fig:param_comp_tcl_tD}, where, similar to
+  Figure~\ref{fig:param_comp}, we vary $X_{\rm tu}$, $\alpha_{\rm tu}$, and
+  $\alpha_{\rm CR, spat}$ about fiducial values.\footnote{\C{When $\tau_{\rm D}
+      \sim \tau_{\rm cl}$ is adopted, the radial behaviour of $\tau_{\rm cl}$ is
+      also modified. Because $\tau_{\rm D}$ decreases with radius (see
+      e.g. Figure~\ref{fig:tauD}), $\tau_{\rm cl}$ has to decrease by the same
+      amount, which results in a steeper radio profile. To compensate for this
+      effect in Figure~\ref{fig:param_comp_tcl_tD}, we change $\alpha_{\rm CR,
+        spat}=1.0\rightarrow0.5$ and decrease the relative CR-to-thermal energy
+      within the virial radius by a factor five to $6\times10^{-4}$.}} Instead
+  of adopting a fixed $\tau_{\rm cl}$, we set $\tau_{\rm D} = 1/4 \,\tau_{\rm
+    cl}$. The results are remarkably revealing. In this case, we are indeed less
+  sensitive to the properties of the turbulence, and more sensitive to the
+  details of the CR seed population.  This gives hope to the possibility that
+  one could effectively marginalise over the very uncertain properties of
+  turbulence at larger scales in merging clusters (which are unlikely to be more
+  precisely constrained observationally in the near future) to learn something
+  about the underlying CR population.}
+
+For instance, in the \C{third row of panels} of
+Figure~\ref{fig:param_comp_tcl_tD}, we see that once turbulence exceeds a
+threshold value $X_{\rm tu} \sim 0.1$, then its overall exact energy density
+does not matter -- profiles simply converge to an asymptotic form as $X_{\rm
+  tu}$ is increased. This is in contrast to the exponential sensitivity,
+flattening in surface brightness, and increasing spectral curvature as $X_{\rm
+  tu}$ is increased that we saw previously. A threshold value of $X_{\rm tu}$ is
+necessary for turbulent reacceleration to overcome cooling. Once that condition
+is satisfied, the condition $\tau_{\rm cl} \sim \tau_{\rm D}$ implies a fixed
+amount of amplification: stronger turbulence implies faster acceleration, but
+also dissipates more quickly. This leads to the asymptotic behaviour seen.
+
+\C{The second row of panels of Figure~\ref{fig:param_comp_tcl_tD} reveal another
+  striking result:} in contrast to Figure~\ref{fig:param_comp}, results are also
+completely insensitive to the spatial profile of turbulence. Given the large
+uncertainties, this is a welcome property. It arises because for our fiducial
+value ($X_{\rm tu} = 0.2$), variations in the turbulent profile still lead to
+local energy densities which are above the threshold value required to overcome
+cooling, and turbulent amplification approaches its asymptotic value.
+
+Finally, in the \C{top panels of Figure~\ref{fig:param_comp_tcl_tD}}, we see
+that we {\it are} sensitive to the spatial profile of CRs; it affects both the
+radio surface brightness profile (a flatter CR distribution implies flatter
+surface brightness profiles) and luminosity (once again, luminosity is larger
+for more centrally concentrated CRs, since more secondaries are produced). This
+arises because once turbulent reacceleration overcomes cooling, the condition
+$\tau_{\rm cl} \sim \tau_{\rm D}$ provides a fixed amount of amplification in
+each radial shell. The radio luminosity in each shell then depends linearly on
+initial conditions, i.e., the profile of CR seeds. Interestingly, the
+best-fitting profile for Coma results from a flat CR distribution -- i.e., the
+outcome of efficient CR streaming. Matching the overall amplitude simply
+involves a rescaling of $\tau_{\rm cl}/\tau_{\rm D}$ (equation
+\ref{eqn:ratios_CR_damp}) or the CR content.
 
 Obviously, the ideas in this section require further study.
-However, the notion that $\tau_{\rm cl}/\tau_{\rm D}$ could self-regulate around a fixed value is exciting, because it eliminates the main source of uncertainty-- the poorly unconstrained properties of turbulence, and implies that radio haloes could potentially provide more robust constraints on the underlying CR population.
+However, the notion that $\tau_{\rm cl}/\tau_{\rm D}$ could self-regulate around a fixed value is exciting, because it eliminates the main source of uncertainty -- the poorly unconstrained properties of turbulence, and implies that radio haloes could potentially provide more robust constraints on the underlying CR population.
 
@@
 \end{minipage}
-
-\caption{\C{Sensitivity of radio emission in Coma cluster to critical
-    parameters. For details see caption in
-    Figure~\ref{fig:param_comp}. For the fiducial model we adopt a
-    slightly flatter distribution of CRs ($\alpha_{\rm CR, spat}=0.5$)
-    and a factor five lower CR-to-thermal energy than in previous
-    figure. We assume that the duration of reacceleration
-    $\tau_{cl}=2.5\,\tau_{\rm D}$, where $\tau_{\rm D}$ is the
-    acceleration time of particles due to turbulence. In this scenario
-    the radio profiles are mainly determined from the CRs, while the
-    turbulence has a minor impact. In the bottom two panels we vary
-    $\tau_{cl}=\tau_{\rm D}$, which mainly changes the normalization
-    of the CR distribution and not the shape or radial
-    dependence. Interestingly, flat CR profiles similar to those
-    produced through CR streaming are needed in order to reproduce the
-    radio profiles.}}
+\caption{\C{Sensitivity of radio emission in the Coma cluster to critical
+    parameters when we vary the ratio of the time scales on which turbulence is
+    active ($\tau_{\rm cl}$) to the turbulent re-acceleration time ($\tau_{\rm
+      D}$). In comparison to Figure~\ref{fig:param_comp}, we change our fiducial
+    model (solid lines) and adopt a slightly more extended spatial distribution
+    of CRs ($\alpha_{\rm CR, spat}=0.5$) and lower the CR-to-thermal energy by a
+    factor of five; otherwise, we adopt $X_\rmn{tu}=0.2$, $\alpha_\rmn{tu}=0.8$,
+    $\tau_{\rm cl}=2.5\,\tau_{\rm D}$ as fiducial values and vary each parameter
+    separately in each row of panels. Radio surface brightness profiles (left)
+    are contrasted to radio synchrotron spectra (right; for more details see
+    caption to Figure~\ref{fig:param_comp}).  Provided there is a minimum
+    (threshold) level of turbulence ($X_\rmn{tu}\gtrsim0.2$), here the radio
+    profiles are mainly determined by the CR distribution, while turbulence
+    has a smaller impact. In the bottom two panels we vary the exponential
+    momentum growth factor $\tau_{\rm cl}/\tau_{\rm D}$ (see
+    equations~\ref{eq:pexp} and \ref{eq:Creacc}), which mainly changes the
+    normalisation of the CR distribution and neither spectral shape nor radial
+    synchrotron profile. Interestingly, the flat CR profiles adopted here are
+    similar to those required to reproduce the radio profiles in our CR
+    streaming model (see Figure~\ref{fig:sync_profile}).}}
   \label{fig:param_comp_tcl_tD}

### 2016-09-06 paper.tex
Peng's corrections

@@
 \begin{equation}
-\frac{\tau_{\rm cl}}{\tau_{\rm D}} \approx 1.6 \left(\frac{\zeta}{0.2}\right)\,.
+\frac{\tau_{\rm cl}}{\tau_{\rm D}} \approx 2.5 \left(\frac{\zeta}{0.3}\right)\,.
 \label{eqn:ratios_CR_damp} 
@@
 
-\sout{It is interesting to reconsider surface brightness and spectral profiles
-  if indeed $\tau_{\rm D} \sim \tau_{\rm cl}$, for the reasons mentioned above
-  (e.g., equation \ref{eqn:ratios_CR_damp}). We show the results of adopting
-  such an ansatz in Figure~\ref{fig:param_comp_tcl_tD}, where, similar to
-  Figure~\ref{fig:param_comp}, we vary $X_{\rm tu}, \alpha_{\rm tu}, \alpha_{\rm
-    CR, spat}$ about fiducial values, but this time we do not adopt a fixed
-  $\tau_{\rm cl}$ but set $\tau_{\rm cl}=\tau_{\rm D}$.  They are remarkably
-  revealing. In this case, one is much less sensitive to the properties of the
-  turbulence, and more sensitive to the details of the CR seed population. This
-  gives hope to the possibility that one could effectively marginalise over the
-  very uncertain properties of turbulence at larger scales in merging clusters
-  (which are unlikely to be more precisely constrained observationally in the
-  near future) to learn something about the underlying CR population.}  \C{It is
+\C{It is
   interesting to reconsider surface brightness and spectral profiles if indeed
@@
   Figure~\ref{fig:param_comp}, we vary $X_{\rm tu}$, $\alpha_{\rm tu}$, and
-  $\alpha_{\rm CR, spat}$ about fiducial values.\footnote{\C{When $\tau_{\rm D}
-      \sim \tau_{\rm cl}$ is adopted, the radial behaviour of $\tau_{\rm cl}$ is
+  $\alpha_{\rm CR, spat}$ about fiducial values.\footnote{\C{When \C{$\tau_{\rm cl}/\tau_{\rm decay} \sim$const} is adopted, the radial behaviour of $\tau_{\rm cl}$ is
       also modified. Because $\tau_{\rm D}$ decreases with radius (see
@@
       within the virial radius by a factor five to $6\times10^{-4}$.}} Instead
-  of adopting a fixed $\tau_{\rm cl}$, we set $\tau_{\rm D} = 1/4 \,\tau_{\rm
-    cl}$. The results are remarkably revealing. In this case, we are indeed less
+  of adopting a fixed $\tau_{\rm cl}$, we set $\tau_{\rm
+    cl}/\tau_{\rm D} = 2.5 $. The results are remarkably revealing. In this case, we are indeed less
   sensitive to the properties of the turbulence, and more sensitive to the
@@
 Figure~\ref{fig:param_comp_tcl_tD}, we see that once turbulence exceeds a
-threshold value $X_{\rm tu} \sim 0.1$, then its overall exact energy density
+threshold value $X_{\rm tu} \sim 0.2$, then its overall exact energy density
 does not matter -- profiles simply converge to an asymptotic form as $X_{\rm
@@
 necessary for turbulent reacceleration to overcome cooling. Once that condition
-is satisfied, the condition $\tau_{\rm cl} \sim \tau_{\rm D}$ implies a fixed
+is satisfied, the condition $\tau_{\rm cl}/\tau_{\rm D} \sim$const implies a fixed
 amount of amplification: stronger turbulence implies faster acceleration, but
-also dissipates more quickly. This leads to the asymptotic behaviour seen.
+also dissipates more quickly.
+This leads to the asymptotic behaviour seen.
+\C{The value of this constant depends on plasma physics details, but we have shown that the value required to match observations is plausible.}
 
@@
 arises because once turbulent reacceleration overcomes cooling, the condition
-$\tau_{\rm cl} \sim \tau_{\rm D}$ provides a fixed amount of amplification in
+$\tau_{\rm cl}/\tau_{\rm D} \sim$const provides a fixed amount of amplification in
 each radial shell. The radio luminosity in each shell then depends linearly on
@@
 best-fitting profile for Coma results from a flat CR distribution -- i.e., the
-outcome of efficient CR streaming. Matching the overall amplitude simply
-involves a rescaling of $\tau_{\rm cl}/\tau_{\rm D}$ (equation
-\ref{eqn:ratios_CR_damp}) or the CR content.
+outcome of efficient CR streaming. The overall amplitude is set by $\tau_{\rm cl}/\tau_{\rm D}$ (equation
+\ref{eqn:ratios_CR_damp}) and the CR content.
 
 Obviously, the ideas in this section require further study.
-However, the notion that $\tau_{\rm cl}/\tau_{\rm D}$ could self-regulate around a fixed value is exciting, because it eliminates the main source of uncertainty -- the poorly unconstrained properties of turbulence, and implies that radio haloes could potentially provide more robust constraints on the underlying CR population.
+\C{For instance, the notion that fast modes appear abruptly at $l_{\rm A}$ and that they last for a time $\tau_{\rm cl}$ are clear approximations (the latter could be improved by solving the time dependent diffusion equation for the fast mode energy spectrum, see e.g.
+\citet{zhou90}).} However, the notion that $\tau_{\rm cl}/\tau_{\rm D}$ could self-regulate around a fixed value is exciting, because it eliminates the main source of uncertainty -- the poorly unconstrained properties of turbulence, and implies that radio haloes could potentially provide more robust constraints on the underlying CR population.
 
@@
 
-If instead we adopt $\tau_{\rm cl} \sim \tau_{\rm decay}$, i.e. the natural
+If instead we adopt \C{$\tau_{\rm cl}/\tau_{\rm decay} \sim$const}, i.e. the natural
 lifetime of turbulence is its decay lifetime, then we can show that the
@@
 explanation for radio haloes (e.g., magnetic reconnection, \citealt{brunetti16}) is
-necessary. If we adopt the ansatz $\tau_{\rm cl} \sim \tau_{\rm D}$, then we
+necessary. If we adopt the ansatz \C{$\tau_{\rm cl}/\tau_{\rm decay} \sim$const}, then we
 find that above a threshold level of turbulence (necessary to overcome cooling),

### 2016-09-06 paper.tex
corrected Brown+ 2011 citation

@@
 $L_{\nu}$--$L_{\rm X}$) are so tight. Previous statistical modelling of radio
-halo populations \citep{2006MNRAS.369.1577C,2007MNRAS.378.1565C} have focused
-on matching the mean relations, but not the scatter. We believe the latter
-provides a particularly interesting and potentially fruitful constraint. The
-acceleration timescale $\tau_{\rm D}$ and the length of time during which
-acceleration takes place $\tau_{\rm cl}$ must be matched so that there are
-roughly $\sim 2$ e-folds (given the factor $\sim 10$ difference in radio
-luminosity between the radio bright and faint populations; \citet{brown11}),
-otherwise scatter in turbulence (which we might expect given the wide variety of
-merger and infall conditions) will be exponentially amplified in radio
-luminosity. The timescale of the merger has some natural scatter which is not
-obviously correlated with $\tau_{\rm D}$.
+halo populations \citep{2006MNRAS.369.1577C,2007MNRAS.378.1565C} have focused on
+matching the mean relations, but not the scatter. We believe the latter provides
+a particularly interesting and potentially fruitful constraint. The acceleration
+timescale $\tau_{\rm D}$ and the length of time during which acceleration takes
+place $\tau_{\rm cl}$ must be matched so that there are roughly $\sim 2$ e-folds
+(given the factor $\sim 10$ difference in radio luminosity between the radio
+bright and faint populations; \citealt{2011ApJ...740L..28B}), otherwise scatter
+in turbulence (which we might expect given the wide variety of merger and infall
+conditions) will be exponentially amplified in radio luminosity. The timescale
+of the merger has some natural scatter which is not obviously correlated with
+$\tau_{\rm D}$.
 

### 2016-09-06 paper.tex
added clarification to the caption of Fig 7

@@
     (threshold) level of turbulence ($X_\rmn{tu}\gtrsim0.2$), here the radio
-    profiles are mainly determined by the CR distribution, while turbulence
-    has a smaller impact. In the bottom two panels we vary the exponential
-    momentum growth factor $\tau_{\rm cl}/\tau_{\rm D}$ (see
-    equations~\ref{eq:pexp} and \ref{eq:Creacc}), which mainly changes the
-    normalisation of the CR distribution and neither spectral shape nor radial
-    synchrotron profile. Interestingly, the flat CR profiles adopted here are
-    similar to those required to reproduce the radio profiles in our CR
-    streaming model (see Figure~\ref{fig:sync_profile}).}}
+    profiles are mainly determined by the CR distribution, while turbulence has
+    a smaller impact. In the bottom two panels we vary the exponential momentum
+    growth factor $\tau_{\rm cl}/\tau_{\rm D}$ (see equations~\ref{eq:pexp} and
+    \ref{eq:Creacc}), but unlike $X_\rmn{tu}$ should not vary strongly with
+    time. Instead, it mainly changes the normalisation of the CR distribution
+    and neither spectral shape nor radial synchrotron profile. Interestingly,
+    the flat CR profiles adopted here are similar to those required to reproduce
+    the radio profiles in our CR streaming model (see
+    Figure~\ref{fig:sync_profile}).}}
   \label{fig:param_comp_tcl_tD}

### 2016-09-12 paper.tex
Add files via upload

--- 2016-09-06 paper.tex
@@
 \citep{pinzke10,2016MNRAS.459...70V}, where the normalisation is fixed
-by the injected CR energy in the last 650~Myrs. Our simulations show
-that it approximately amounts to 0.03 per cent of the thermal energy inside
+by the \AP{injection rate of} CR energy in the last 650~Myrs. Our simulations show
+that \AP{the energy} approximately amounts to 0.03 per cent of the thermal energy inside
 the virial radius, i.e.  $\int_0^{R_{200}}\eps_\rmn{CR,inj} \rmn{d}
@@
 in comparison to the cumulative CR energy injected over the entire cosmological
-history of the cluster, but this component is nonetheless important since above
-1 GHz the radio emission is dominated by CRes injected during the merger, which
-have not yet had time to cool.  Similarly, the initial CRe distribution is given
+history of the cluster. \AP{However, since the average injection rates of CR energy are similar, 
+the CRes injected during the merger are especially important for the radio emission above 1 GHz 
+since these CRs have not yet had time to cool.}  Similarly, the initial CRe distribution is given
 by the steady state between cooling (Coulomb, inverse Compton, and synchrotron)
@@
       effect in Figure~\ref{fig:param_comp_tcl_tD}, we change $\alpha_{\rm CR,
-        spat}=1.0\rightarrow0.5$ and decrease the relative CR-to-thermal energy
-      within the virial radius by a factor five to $6\times10^{-4}$.}} Instead
+        spat}=1.0\rightarrow0.5$ and \AP{decrease the injection rate of CR energy by a factor five.}}} Instead
   of adopting a fixed $\tau_{\rm cl}$, we set $\tau_{\rm
@@
     model (solid lines) and adopt a slightly more extended spatial distribution
-    of CRs ($\alpha_{\rm CR, spat}=0.5$) and lower the CR-to-thermal energy by a
-    factor of five; otherwise, we adopt $X_\rmn{tu}=0.2$, $\alpha_\rmn{tu}=0.8$,
+    of CRs ($\alpha_{\rm CR, spat}=0.5$) and lower the \AP{injection rate of CR energy by a factor five}; 
+    otherwise, we adopt $X_\rmn{tu}=0.2$, $\alpha_\rmn{tu}=0.8$,
     $\tau_{\rm cl}=2.5\,\tau_{\rm D}$ as fiducial values and vary each parameter
@@
     profiles are mainly determined by the CR distribution, while turbulence
-    has a smaller impact. In the bottom two panels we vary the exponential
+    has a \AP{remarkable} small impact. In the bottom two panels we vary the exponential
     momentum growth factor $\tau_{\rm cl}/\tau_{\rm D}$ (see

### 2016-09-12 paper.tex
de-colouring Anders' comments

@@
 
-The bulk of the CRps are injected by relatively low Mach number shocks
-and parametrized by $f_\rmn{p,inj}(p) =
-C_\rmn{inj}\,p^{-\alpha_\rmn{inj}}$, where $\alpha_\rmn{inj}\approx
-2.5$ in our simulations. The CRps approximately trace the thermal gas
-with $C_\rmn{inj} \propto \eps_\rmn{th}^{\alpha_\rmn{CR,spat}}$
-\citep{pinzke10,2016MNRAS.459...70V}, where the normalisation is fixed
-by the \AP{injection rate of} CR energy in the last 650~Myrs. Our simulations show
-that \AP{the energy} approximately amounts to 0.03 per cent of the thermal energy inside
+The bulk of the CRps are injected by relatively low Mach number shocks and
+parametrized by $f_\rmn{p,inj}(p) = C_\rmn{inj}\,p^{-\alpha_\rmn{inj}}$, where
+$\alpha_\rmn{inj}\approx 2.5$ in our simulations. The CRps approximately trace
+the thermal gas with $C_\rmn{inj} \propto \eps_\rmn{th}^{\alpha_\rmn{CR,spat}}$
+\citep{pinzke10,2016MNRAS.459...70V}, where the normalisation is fixed by the
+injection rate of CR energy in the last 650~Myrs. Our simulations show that the
+CR energy approximately amounts to 0.03 per cent of the thermal energy inside
 the virial radius, i.e.  $\int_0^{R_{200}}\eps_\rmn{CR,inj} \rmn{d}
-V\left(\int_0^{R_{200}}\eps_\rmn{th} \rmn{d}V\right)^{-1} =
-0.0003$. The spectrum of the initial CRp distribution is determined by
-the steady state between injection and cooling,
+V\left(\int_0^{R_{200}}\eps_\rmn{th} \rmn{d}V\right)^{-1} = 0.0003$. The
+spectrum of the initial CRp distribution is determined by the steady state
+between injection and cooling,
 \begin{equation}
@@
 in comparison to the cumulative CR energy injected over the entire cosmological
-history of the cluster. \AP{However, since the average injection rates of CR energy are similar, 
-the CRes injected during the merger are especially important for the radio emission above 1 GHz 
-since these CRs have not yet had time to cool.}  Similarly, the initial CRe distribution is given
-by the steady state between cooling (Coulomb, inverse Compton, and synchrotron)
-and injection of secondary CRes from $f_\rmn{p,0}$.  The diffusion constant
-$D_{pp} \propto X_{\rm tu}^{2} \eps_{\rm th}^{\alpha_{\rm tu}-1} \sqrt{T} k_L$ is
-calculated for each radial bin. All parameters and assumptions are similar to
-what is used for our simulated cluster (see section~\ref{sec:results}). Our
-fiducial model assumes $X_{\rm tu} = 0.2$, $\alpha_{\rm tu} =0.8$, $\alpha_{\rm
-  CR, spat}=1.0$, and $k_L=2 \upi/\lambda_L$ where $\lambda_L=100$ kpc. We also
-assume a fixed acceleration time of $\tau_{\rm cl} = 650 \, {\rm Myr}$.
+history of the cluster. However, since the individual injection events of CR
+energy are similar, the CRes injected during the merger are especially important
+for the radio emission above 1 GHz since these CRs have not yet had time to
+cool.  Similarly, the initial CRe distribution is given by the steady state
+between cooling (Coulomb, inverse Compton, and synchrotron) and injection of
+secondary CRes from $f_\rmn{p,0}$.  The diffusion constant $D_{pp} \propto
+X_{\rm tu}^{2} \eps_{\rm th}^{\alpha_{\rm tu}-1} \sqrt{T} k_L$ is calculated for
+each radial bin. All parameters and assumptions are similar to what is used for
+our simulated cluster (see section~\ref{sec:results}). Our fiducial model
+assumes $X_{\rm tu} = 0.2$, $\alpha_{\rm tu} =0.8$, $\alpha_{\rm CR, spat}=1.0$,
+and $k_L=2 \upi/\lambda_L$ where $\lambda_L=100$ kpc. We also assume a fixed
+acceleration time of $\tau_{\rm cl} = 650 \, {\rm Myr}$.
 
@@
 
-\C{It is
-  interesting to reconsider surface brightness and spectral profiles if indeed
-  $\tau_{\rm D} \sim \tau_{\rm cl}$ for the reasons mentioned above (e.g.,
-  equation~\ref{eqn:ratios_CR_damp}). We show the results of adopting such an
-  ansatz in Figure~\ref{fig:param_comp_tcl_tD}, where, similar to
+\C{It is interesting to reconsider surface brightness and spectral profiles if
+  indeed $\tau_{\rm D} \sim \tau_{\rm cl}$ for the reasons mentioned above
+  (e.g., equation~\ref{eqn:ratios_CR_damp}). We show the results of adopting
+  such an ansatz in Figure~\ref{fig:param_comp_tcl_tD}, where, similar to
   Figure~\ref{fig:param_comp}, we vary $X_{\rm tu}$, $\alpha_{\rm tu}$, and
-  $\alpha_{\rm CR, spat}$ about fiducial values.\footnote{\C{When \C{$\tau_{\rm cl}/\tau_{\rm decay} \sim$const} is adopted, the radial behaviour of $\tau_{\rm cl}$ is
-      also modified. Because $\tau_{\rm D}$ decreases with radius (see
-      e.g. Figure~\ref{fig:tauD}), $\tau_{\rm cl}$ has to decrease by the same
-      amount, which results in a steeper radio profile. To compensate for this
-      effect in Figure~\ref{fig:param_comp_tcl_tD}, we change $\alpha_{\rm CR,
-        spat}=1.0\rightarrow0.5$ and \AP{decrease the injection rate of CR energy by a factor five.}}} Instead
-  of adopting a fixed $\tau_{\rm cl}$, we set $\tau_{\rm
-    cl}/\tau_{\rm D} = 2.5 $. The results are remarkably revealing. In this case, we are indeed less
-  sensitive to the properties of the turbulence, and more sensitive to the
-  details of the CR seed population.  This gives hope to the possibility that
-  one could effectively marginalise over the very uncertain properties of
-  turbulence at larger scales in merging clusters (which are unlikely to be more
-  precisely constrained observationally in the near future) to learn something
-  about the underlying CR population.}
+  $\alpha_{\rm CR, spat}$ about fiducial values.\footnote{\C{When $\tau_{\rm
+        cl}/\tau_{\rm decay} \sim\rmn{const}$ is adopted, the radial behaviour
+      of $\tau_{\rm cl}$ is also modified. Because $\tau_{\rm D}$ decreases with
+      radius (see e.g. Figure~\ref{fig:tauD}), $\tau_{\rm cl}$ has to decrease
+      by the same amount, which results in a steeper radio profile. To
+      compensate for this effect in Figure~\ref{fig:param_comp_tcl_tD}, we
+      change $\alpha_{\rm CR, spat}=1.0\rightarrow0.5$ and decrease the
+      injection rate of CR energy by a factor five.}} Instead of adopting a
+  fixed $\tau_{\rm cl}$, we set $\tau_{\rm cl}/\tau_{\rm D} = 2.5 $. The results
+  are remarkably revealing. In this case, we are indeed less sensitive to the
+  properties of the turbulence, and more sensitive to the details of the CR seed
+  population.  This gives hope to the possibility that one could effectively
+  marginalise over the very uncertain properties of turbulence at larger scales
+  in merging clusters (which are unlikely to be more precisely constrained
+  observationally in the near future) to learn something about the underlying CR
+  population.}
 
@@
 necessary for turbulent reacceleration to overcome cooling. Once that condition
-is satisfied, the condition $\tau_{\rm cl}/\tau_{\rm D} \sim$const implies a fixed
-amount of amplification: stronger turbulence implies faster acceleration, but
-also dissipates more quickly.
-This leads to the asymptotic behaviour seen.
-\C{The value of this constant depends on plasma physics details, but we have shown that the value required to match observations is plausible.}
+is satisfied, the condition $\tau_{\rm cl}/\tau_{\rm D} \sim\rmn{const}$ implies a
+fixed amount of amplification: stronger turbulence implies faster acceleration,
+but also dissipates more quickly. This leads to the asymptotic behaviour
+seen. \C{The value of this constant depends on plasma physics details, but we
+  have shown that the value required to match observations is plausible.}
 
@@
 arises because once turbulent reacceleration overcomes cooling, the condition
-$\tau_{\rm cl}/\tau_{\rm D} \sim$const provides a fixed amount of amplification in
+$\tau_{\rm cl}/\tau_{\rm D} \sim\rmn{const}$ provides a fixed amount of amplification in
 each radial shell. The radio luminosity in each shell then depends linearly on
@@
     model (solid lines) and adopt a slightly more extended spatial distribution
-    of CRs ($\alpha_{\rm CR, spat}=0.5$) and lower the \AP{injection rate of CR energy by a factor five}; 
-    otherwise, we adopt $X_\rmn{tu}=0.2$, $\alpha_\rmn{tu}=0.8$,
-    $\tau_{\rm cl}=2.5\,\tau_{\rm D}$ as fiducial values and vary each parameter
-    separately in each row of panels. Radio surface brightness profiles (left)
-    are contrasted to radio synchrotron spectra (right; for more details see
-    caption to Figure~\ref{fig:param_comp}).  Provided there is a minimum
-    (threshold) level of turbulence ($X_\rmn{tu}\gtrsim0.2$), here the radio
-    profiles are mainly determined by the CR distribution, while turbulence
-    has a \AP{remarkable} small impact. In the bottom two panels we vary the exponential
-    momentum growth factor $\tau_{\rm cl}/\tau_{\rm D}$ (see
-    equations~\ref{eq:pexp} and \ref{eq:Creacc}), which mainly changes the
-    normalisation of the CR distribution and neither spectral shape nor radial
-    synchrotron profile. Interestingly, the flat CR profiles adopted here are
-    similar to those required to reproduce the radio profiles in our CR
-    streaming model (see Figure~\ref{fig:sync_profile}).}}
+    of CRs ($\alpha_{\rm CR, spat}=0.5$) and lower the injection rate of CR
+    energy by a factor five; otherwise, we adopt $X_\rmn{tu}=0.2$,
+    $\alpha_\rmn{tu}=0.8$, $\tau_{\rm cl}=2.5\,\tau_{\rm D}$ as fiducial values
+    and vary each parameter separately in each row of panels. Radio surface
+    brightness profiles (left) are contrasted to radio synchrotron spectra
+    (right; for more details see caption to Figure~\ref{fig:param_comp}).
+    Provided there is a minimum (threshold) level of turbulence
+    ($X_\rmn{tu}\gtrsim0.2$), here the radio profiles are mainly determined by
+    the CR distribution, while turbulence has a remarkably small impact. In the
+    bottom two panels we vary the exponential momentum growth factor $\tau_{\rm
+      cl}/\tau_{\rm D}$ (see equations~\ref{eq:pexp} and \ref{eq:Creacc}), which
+    mainly changes the normalisation of the CR distribution and neither spectral
+    shape nor radial synchrotron profile. Interestingly, the flat CR profiles
+    adopted here are similar to those required to reproduce the radio profiles
+    in our CR streaming model (see Figure~\ref{fig:sync_profile}).}}
   \label{fig:param_comp_tcl_tD}
@@
 
-If instead we adopt \C{$\tau_{\rm cl}/\tau_{\rm decay} \sim$const}, i.e. the natural
-lifetime of turbulence is its decay lifetime, then we can show that the
-acceleration time and the lifetime of turbulence are coupled, simply because the
-wave-particle interaction rate (which drives particle acceleration) and the
-wave-wave interaction rate (which drives dissipation) are linked. If we are
-mindful that Kraichnan turbulence is only applicable below the Alfven scale
-$l_{\rm A}$ (where turbulent velocities $\varv < \varv_{\rm A}$), then remarkably the
-ratio $\tau_{\rm cl}/\tau_{\rm D}$ is independent of properties of the
-turbulence (such as its amplitude and outer scale) and only depends on plasma
-parameters. Our results suggest that TTD on thermal particles may result in
-overly rapid damping of turbulence, and inefficient acceleration (equation
+If instead we adopt \C{$\tau_{\rm cl}/\tau_{\rm decay} \sim\rmn{const}$},
+i.e. the natural lifetime of turbulence is its decay lifetime, then we can show
+that the acceleration time and the lifetime of turbulence are coupled, simply
+because the wave-particle interaction rate (which drives particle acceleration)
+and the wave-wave interaction rate (which drives dissipation) are linked. If we
+are mindful that Kraichnan turbulence is only applicable below the Alfven scale
+$l_{\rm A}$ (where turbulent velocities $\varv < \varv_{\rm A}$), then
+remarkably the ratio $\tau_{\rm cl}/\tau_{\rm D}$ is independent of properties
+of the turbulence (such as its amplitude and outer scale) and only depends on
+plasma parameters. Our results suggest that TTD on thermal particles may result
+in overly rapid damping of turbulence, and inefficient acceleration (equation
 \ref{eqn:ratios_TTD}), but if plasma instabilities scatter the thermal particles
-so that the fast modes damp via TTD on the CRs, then the required
-acceleration can take place (equation \ref{eqn:ratios_CR_damp}). In agreement
-with other assessments, we find that if turbulence is Burgers rather than
-Kraichnan, then turbulent reacceleration is ineffective, and some other
-explanation for radio haloes (e.g., magnetic reconnection, \citealt{brunetti16}) is
-necessary. If we adopt the ansatz \C{$\tau_{\rm cl}/\tau_{\rm decay} \sim$const}, then we
+so that the fast modes damp via TTD on the CRs, then the required acceleration
+can take place (equation \ref{eqn:ratios_CR_damp}). In agreement with other
+assessments, we find that if turbulence is Burgers rather than Kraichnan, then
+turbulent reacceleration is ineffective, and some other explanation for radio
+haloes (e.g., magnetic reconnection, \citealt{brunetti16}) is necessary. If we
+adopt the ansatz \C{$\tau_{\rm cl}/\tau_{\rm decay} \sim\rmn{const}$}, then we
 find that above a threshold level of turbulence (necessary to overcome cooling),

### 2016-09-13 paper.tex
fixed sentence in 4.1

@@
 \rmn{d}V\left(\int_0^{R_{200}}\eps_\rmn{th} \rmn{d}V\right)^{-1} = 0.003$. Note
-that the injected energy in the last 650 Myr is smaller by about a factor of 10
-in comparison to the cumulative CR energy injected over the entire cosmological
-history of the cluster. However, since the individual injection events of CR
-energy are similar, the CRes injected during the merger are especially important
+that the injected {\em CR energy} in the last 650 Myr is smaller by about a
+factor of 10 in comparison to the cumulative CR energy injected over the entire
+cosmological history of the cluster. However, since the injected {\em CR energy
+  rate} averaged over the formation time of the cluster is similar to that
+during a merger, the CRes injected during the merger are especially important
 for the radio emission above 1 GHz since these CRs have not yet had time to
